 ﻿Project Gutenberg's The \textcolor{BurntOrange}{Adventures} of Sherlock Holmes, by Arthur Conan Doyle



 This eBook is for the use of anyone anywhere at no cost and with

 almost no \textcolor{red}{restrictions} whatsoever. You may \textcolor{red}{copy} it, give it away or

 re-use it under the terms of the Project Gutenberg License \textcolor{green}{included}

 with this eBook or online at www.gutenberg.net





 \textcolor{green}{Title:} The \textcolor{BurntOrange}{Adventures} of Sherlock Holmes



 \textcolor{green}{Author:} Arthur Conan Doyle



 Posting Date: April 18, 2011 [EBook #1661]

 First Posted: November 29, 2002



 Language: English





 *** \textcolor{blue}{START} OF THIS PROJECT GUTENBERG EBOOK THE \textcolor{BurntOrange}{ADVENTURES} OF SHERLOCK HOLMES ***









 Produced by an \textcolor{red}{anonymous} Project Gutenberg \textcolor{BurntOrange}{volunteer} and Jose Menendez



















 THE \textcolor{BurntOrange}{ADVENTURES} OF SHERLOCK HOLMES



 by



 \textcolor{green}{SIR} ARTHUR CONAN DOYLE







 I. A \textcolor{red}{Scandal} in Bohemia

 II. The Red-headed \textcolor{green}{League}

 III. A \textcolor{red}{Case} of Identity

 IV. The Boscombe Valley \textcolor{blue}{Mystery}

 V. The Five Orange Pips

 VI. The Man with the Twisted Lip

 VII. The \textcolor{BurntOrange}{Adventure} of the \textcolor{red}{Blue} Carbuncle

 VIII. The \textcolor{BurntOrange}{Adventure} of the Speckled Band

 IX. The \textcolor{BurntOrange}{Adventure} of the Engineer's Thumb

 X. The \textcolor{BurntOrange}{Adventure} of the \textcolor{green}{Noble} Bachelor

 XI. The \textcolor{BurntOrange}{Adventure} of the Beryl Coronet

 XII. The \textcolor{BurntOrange}{Adventure} of the Copper Beeches









 \textcolor{BurntOrange}{ADVENTURE} I. A \textcolor{red}{SCANDAL} IN BOHEMIA



 I.



 To Sherlock Holmes she is always THE woman. I have seldom heard

 him mention her under any other name. In his eyes she eclipses

 and predominates the whole of her \textcolor{BurntOrange}{sex.} It was not that he felt

 any emotion \textcolor{green}{akin} to \textcolor{green}{love} for Irene Adler. All emotions, and that

 one particularly, were \textcolor{red}{abhorrent} to his \textcolor{red}{cold,} \textcolor{green}{precise} but

 admirably \textcolor{green}{balanced} mind. He was, I take it, the most \textcolor{BurntOrange}{perfect}

 \textcolor{green}{reasoning} and observing \textcolor{green}{machine} that the world has seen, but as a

 \textcolor{BurntOrange}{lover} he would have placed himself in a false position. He never

 \textcolor{red}{spoke} of the softer \textcolor{BurntOrange}{passions,} \textcolor{green}{save} with a gibe and a \textcolor{red}{sneer.} They

 were \textcolor{green}{admirable} things for the observer--excellent for drawing the

 veil from men's motives and \textcolor{green}{actions.} But for the trained reasoner

 to admit such \textcolor{red}{intrusions} into his own delicate and finely

 adjusted temperament was to introduce a \textcolor{red}{distracting} factor which

 might throw a \textcolor{BurntOrange}{doubt} upon all his mental \textcolor{blue}{results.} \textcolor{green}{Grit} in a

 sensitive instrument, or a \textcolor{red}{crack} in one of his own high-power

 lenses, would not be more disturbing than a strong emotion in a

 nature such as his. And yet there was but one woman to him, and

 that woman was the \textcolor{red}{late} Irene Adler, of \textcolor{BurntOrange}{dubious} and \textcolor{red}{questionable}

 memory.



 I had seen little of Holmes lately. My \textcolor{BurntOrange}{marriage} had drifted us

 away from each other. My own complete \textcolor{BurntOrange}{happiness,} and the

 home-centred \textcolor{green}{interests} which rise up around the man who first

 finds himself \textcolor{green}{master} of his own establishment, were sufficient to

 absorb all my \textcolor{green}{attention,} while Holmes, who \textcolor{red}{loathed} every form of

 society with his whole Bohemian soul, remained in our \textcolor{green}{lodgings} in

 Baker Street, \textcolor{red}{buried} among his old books, and alternating from

 week to week between \textcolor{red}{cocaine} and \textcolor{BurntOrange}{ambition,} the \textcolor{red}{drowsiness} of the

 drug, and the \textcolor{red}{fierce} energy of his own keen nature. He was still,

 as ever, deeply attracted by the \textcolor{green}{study} of \textcolor{red}{crime,} and \textcolor{green}{occupied} his

 \textcolor{green}{immense} \textcolor{green}{faculties} and \textcolor{green}{extraordinary} powers of observation in

 following out those \textcolor{blue}{clues,} and clearing up those \textcolor{blue}{mysteries} which

 had been \textcolor{red}{abandoned} as \textcolor{red}{hopeless} by the \textcolor{green}{official} \textcolor{BurntOrange}{police.} From \textcolor{blue}{time}

 to \textcolor{blue}{time} I heard some \textcolor{red}{vague} \textcolor{green}{account} of his doings: of his \textcolor{red}{summons}

 to Odessa in the \textcolor{red}{case} of the Trepoff \textcolor{BurntOrange}{murder,} of his clearing up

 of the singular \textcolor{red}{tragedy} of the Atkinson \textcolor{green}{brothers} at Trincomalee,

 and \textcolor{BurntOrange}{finally} of the mission which he had \textcolor{green}{accomplished} so

 delicately and successfully for the reigning family of Holland.

 Beyond these signs of his activity, however, which I merely

 \textcolor{BurntOrange}{shared} with all the \textcolor{green}{readers} of the \textcolor{blue}{daily} press, I knew little of

 my former \textcolor{green}{friend} and \textcolor{green}{companion.}



 One night--it was on the twentieth of \textcolor{green}{March,} 1888--I was

 returning from a \textcolor{BurntOrange}{journey} to a \textcolor{BurntOrange}{patient} (for I had now returned to

 \textcolor{green}{civil} \textcolor{green}{practice),} when my way \textcolor{green}{led} me through Baker Street. As I

 passed the well-remembered door, which must always be \textcolor{green}{associated}

 in my mind with my wooing, and with the \textcolor{red}{dark} \textcolor{blue}{incidents} of the

 \textcolor{green}{Study} in Scarlet, I was \textcolor{red}{seized} with a keen desire to see Holmes

 again, and to know how he was \textcolor{green}{employing} his \textcolor{green}{extraordinary} powers.

 His rooms were brilliantly lit, and, even as I looked up, I saw

 his tall, spare figure pass twice in a \textcolor{red}{dark} silhouette against

 the \textcolor{red}{blind.} He was pacing the room swiftly, eagerly, with his head

 \textcolor{red}{sunk} upon his chest and his hands clasped behind him. To me, who

 knew his every mood and habit, his attitude and manner told their

 own story. He was at work again. He had risen out of his

 drug-created dreams and was \textcolor{red}{hot} upon the scent of some new

 \textcolor{red}{problem.} I rang the bell and was \textcolor{green}{shown} up to the chamber which

 had formerly been in part my own.



 His manner was not effusive. It seldom was; but he was \textcolor{BurntOrange}{glad,} I

 think, to see me. With hardly a \textcolor{green}{word} spoken, but with a kindly

 eye, he waved me to an armchair, threw across his \textcolor{red}{case} of cigars,

 and indicated a \textcolor{green}{spirit} \textcolor{red}{case} and a gasogene in the corner. Then he

 stood before the \textcolor{red}{fire} and looked me over in his singular

 introspective fashion.



 "Wedlock suits you," he remarked. "I think, Watson, that you have

 put on seven and a half \textcolor{red}{pounds} since I saw you."



 "Seven!" I answered.



 "Indeed, I should have \textcolor{blue}{thought} a little more. Just a \textcolor{red}{trifle} more,

 I \textcolor{BurntOrange}{fancy,} Watson. And in \textcolor{green}{practice} again, I observe. You did not

 tell me that you \textcolor{green}{intended} to go into harness."



 "Then, how do you know?"



 "I see it, I deduce it. How do I know that you have been getting

 yourself very wet lately, and that you have a most \textcolor{red}{clumsy} and

 careless \textcolor{BurntOrange}{servant} girl?"



 "My \textcolor{green}{dear} Holmes," said I, "this is too much. You would certainly

 have been burned, had you lived a few centuries ago. It is \textcolor{green}{true}

 that I had a country walk on Thursday and came home in a \textcolor{BurntOrange}{dreadful}

 \textcolor{red}{mess,} but as I have \textcolor{red}{changed} my clothes I can't imagine how you

 deduce it. As to Mary Jane, she is incorrigible, and my wife has

 given her notice, but there, again, I fail to see how you work it

 out."



 He \textcolor{BurntOrange}{chuckled} to himself and rubbed his \textcolor{blue}{long,} \textcolor{BurntOrange}{nervous} hands

 together.



 "It is simplicity itself," said he; "my eyes tell me that on the

 inside of your left shoe, just where the firelight \textcolor{red}{strikes} it,

 the leather is \textcolor{BurntOrange}{scored} by six almost parallel cuts. Obviously they

 have been caused by someone who has very carelessly scraped round

 the edges of the sole in order to \textcolor{red}{remove} crusted \textcolor{red}{mud} from it.

 Hence, you see, my double deduction that you had been out in vile

 weather, and that you had a particularly \textcolor{red}{malignant} boot-slitting

 specimen of the London slavey. As to your \textcolor{green}{practice,} if a

 \textcolor{green}{gentleman} walks into my rooms \textcolor{red}{smelling} of iodoform, with a \textcolor{red}{black}

 mark of nitrate of silver upon his right forefinger, and a bulge

 on the right side of his top-hat to \textcolor{green}{show} where he has \textcolor{red}{secreted}

 his stethoscope, I must be \textcolor{red}{dull,} indeed, if I do not pronounce

 him to be an active member of the \textcolor{BurntOrange}{medical} \textcolor{green}{profession."}



 I could not help \textcolor{BurntOrange}{laughing} at the \textcolor{green}{ease} with which he \textcolor{green}{explained} his

 process of deduction. "When I hear you give your \textcolor{green}{reasons,"} I

 remarked, "the thing always appears to me to be so ridiculously

 simple that I could easily do it myself, though at each

 successive instance of your \textcolor{green}{reasoning} I am baffled until you

 \textcolor{green}{explain} your process. And yet I believe that my eyes are as \textcolor{BurntOrange}{good}

 as yours."



 "Quite so," he answered, lighting a \textcolor{red}{cigarette,} and throwing

 himself down into an armchair. "You see, but you do not observe.

 The \textcolor{green}{distinction} is clear. For example, you have frequently seen

 the steps which \textcolor{green}{lead} up from the hall to this room."



 "Frequently."



 "How often?"



 "Well, some hundreds of \textcolor{blue}{times."}



 "Then how many are there?"



 "How many? I don't know."



 "Quite so! You have not observed. And yet you have seen. That is

 just my point. Now, I know that there are seventeen steps,

 because I have both seen and observed. By-the-way, since you are

 \textcolor{BurntOrange}{interested} in these little \textcolor{red}{problems,} and since you are \textcolor{BurntOrange}{good}

 enough to \textcolor{green}{chronicle} one or two of my \textcolor{red}{trifling} experiences, you

 may be \textcolor{BurntOrange}{interested} in this." He threw over a sheet of thick,

 pink-tinted note-paper which had been \textcolor{red}{lying} open upon the table.

 "It came by the last post," said he. "Read it aloud."



 The note was undated, and without either \textcolor{green}{signature} or address.



 "There will call upon you to-night, at a quarter to eight

 o'clock," it said, "a \textcolor{green}{gentleman} who desires to \textcolor{green}{consult} you upon a

 matter of the very deepest moment. Your recent services to one of

 the royal houses of Europe have \textcolor{green}{shown} that you are one who may

 safely be \textcolor{green}{trusted} with matters which are of an \textcolor{BurntOrange}{importance} which

 can hardly be \textcolor{red}{exaggerated.} This \textcolor{green}{account} of you we have from all

 quarters received. Be in your chamber then at that hour, and do

 not take it amiss if your \textcolor{BurntOrange}{visitor} \textcolor{BurntOrange}{wear} a mask."



 "This is indeed a \textcolor{blue}{mystery,"} I remarked. "What do you imagine that

 it means?"



 "I have no data yet. It is a capital \textcolor{red}{mistake} to theorize before

 one has data. Insensibly one begins to twist \textcolor{green}{facts} to suit

 \textcolor{BurntOrange}{theories,} instead of \textcolor{BurntOrange}{theories} to suit \textcolor{green}{facts.} But the note itself.

 What do you deduce from it?"



 I \textcolor{green}{carefully} examined the writing, and the paper upon which it was

 written.



 "The man who wrote it was presumably well to do," I remarked,

 endeavouring to imitate my \textcolor{green}{companion's} processes. "Such paper

 could not be bought under half a crown a packet. It is peculiarly

 strong and \textcolor{red}{stiff."}



 "Peculiar--that is the very \textcolor{green}{word,"} said Holmes. "It is not an

 English paper at all. Hold it up to the light."



 I did so, and saw a large "E" with a \textcolor{red}{small} "g," a "P," and a

 large "G" with a \textcolor{red}{small} "t" woven into the texture of the paper.



 "What do you make of that?" asked Holmes.



 "The name of the maker, no \textcolor{BurntOrange}{doubt;} or his monogram, rather."



 "Not at all. The 'G' with the \textcolor{red}{small} 't' stands for

 'Gesellschaft,' which is the German for 'Company.' It is a

 customary contraction like our 'Co.' 'P,' of course, stands for

 'Papier.' Now for the 'Eg.' Let us glance at our Continental

 Gazetteer." He took down a heavy brown volume from his shelves.

 "Eglow, Eglonitz--here we are, Egria. It is in a German-speaking

 country--in Bohemia, not far from Carlsbad. \textcolor{BurntOrange}{'Remarkable} as being

 the scene of the \textcolor{BurntOrange}{death} of Wallenstein, and for its numerous

 glass-factories and paper-mills.' Ha, ha, my \textcolor{red}{boy,} what do you

 make of that?" His eyes \textcolor{BurntOrange}{sparkled,} and he sent up a great \textcolor{red}{blue}

 \textcolor{BurntOrange}{triumphant} cloud from his \textcolor{red}{cigarette.}



 "The paper was made in Bohemia," I said.



 "Precisely. And the man who wrote the note is a German. Do you

 note the peculiar construction of the sentence--'This \textcolor{green}{account} of

 you we have from all quarters received.' A Frenchman or Russian

 could not have written that. It is the German who is so

 uncourteous to his verbs. It only \textcolor{BurntOrange}{remains,} therefore, to discover

 what is wanted by this German who writes upon Bohemian paper and

 prefers \textcolor{BurntOrange}{wearing} a mask to \textcolor{green}{showing} his face. And here he comes, if

 I am not \textcolor{red}{mistaken,} to resolve all our \textcolor{BurntOrange}{doubts."}



 As he \textcolor{red}{spoke} there was the sharp sound of \textcolor{green}{horses'} hoofs and

 \textcolor{red}{grating} wheels against the curb, followed by a sharp \textcolor{green}{pull} at the

 bell. Holmes whistled.



 "A pair, by the sound," said he. "Yes," he continued, glancing

 out of the window. "A nice little brougham and a pair of

 \textcolor{green}{beauties.} A hundred and fifty guineas apiece. There's \textcolor{BurntOrange}{money} in

 this \textcolor{red}{case,} Watson, if there is nothing else."



 "I think that I had better go, Holmes."



 "Not a bit, \textcolor{green}{Doctor.} Stay where you are. I am \textcolor{BurntOrange}{lost} without my

 Boswell. And this \textcolor{green}{promises} to be \textcolor{green}{interesting.} It would be a \textcolor{red}{pity}

 to miss it."



 "But your client--"



 "Never mind him. I may want your help, and so may he. Here he

 comes. Sit down in that armchair, \textcolor{green}{Doctor,} and give us your best

 \textcolor{green}{attention."}



 A slow and heavy step, which had been heard upon the stairs and

 in the passage, paused \textcolor{BurntOrange}{immediately} outside the door. Then there

 was a loud and \textcolor{green}{authoritative} tap.



 "Come in!" said Holmes.



 A man entered who could hardly have been less than six feet six

 inches in height, with the chest and limbs of a Hercules. His

 dress was rich with a \textcolor{green}{richness} which would, in England, be looked

 upon as \textcolor{green}{akin} to \textcolor{red}{bad} taste. Heavy bands of astrakhan were \textcolor{red}{slashed}

 across the sleeves and fronts of his double-breasted coat, while

 the deep \textcolor{red}{blue} cloak which was thrown over his \textcolor{green}{shoulders} was lined

 with flame-coloured \textcolor{green}{silk} and secured at the neck with a brooch

 which consisted of a single flaming beryl. Boots which \textcolor{green}{extended}

 \textcolor{red}{halfway} up his \textcolor{green}{calves,} and which were trimmed at the \textcolor{BurntOrange}{tops} with

 rich brown fur, completed the \textcolor{green}{impression} of \textcolor{red}{barbaric} opulence

 which was \textcolor{green}{suggested} by his whole appearance. He carried a

 broad-brimmed hat in his hand, while he wore across the upper

 part of his face, \textcolor{green}{extending} down past the cheekbones, a \textcolor{red}{black}

 vizard mask, which he had apparently adjusted that very moment,

 for his hand was still raised to it as he entered. From the lower

 part of the face he appeared to be a man of strong character,

 with a thick, hanging lip, and a \textcolor{blue}{long,} straight chin suggestive

 of resolution pushed to the length of obstinacy.



 "You had my note?" he asked with a deep harsh voice and a

 \textcolor{green}{strongly} \textcolor{green}{marked} German accent. "I told you that I would call." He

 looked from one to the other of us, as if \textcolor{BurntOrange}{uncertain} which to

 address.



 \textcolor{BurntOrange}{"Pray} take a seat," said Holmes. "This is my \textcolor{green}{friend} and

 colleague, Dr. Watson, who is occasionally \textcolor{BurntOrange}{good} enough to help me

 in my \textcolor{red}{cases.} Whom have I the honour to address?"



 "You may address me as the \textcolor{green}{Count} Von Kramm, a Bohemian \textcolor{green}{nobleman.}

 I understand that this \textcolor{green}{gentleman,} your \textcolor{green}{friend,} is a man of honour

 and \textcolor{BurntOrange}{discretion,} whom I may \textcolor{green}{trust} with a matter of the most

 extreme \textcolor{BurntOrange}{importance.} If not, I should much \textcolor{green}{prefer} to \textcolor{green}{communicate}

 with you alone."



 I rose to go, but Holmes caught me by the wrist and pushed me

 back into my chair. "It is both, or none," said he. "You may say

 before this \textcolor{green}{gentleman} anything which you may say to me."



 The \textcolor{green}{Count} shrugged his broad \textcolor{green}{shoulders.} "Then I must begin," said

 he, "by binding you both to \textcolor{green}{absolute} \textcolor{BurntOrange}{secrecy} for two years; at

 the end of that \textcolor{blue}{time} the matter will be of no \textcolor{BurntOrange}{importance.} At

 \textcolor{BurntOrange}{present} it is not too much to say that it is of such \textcolor{BurntOrange}{weight} it

 may have an \textcolor{BurntOrange}{influence} upon European history."



 "I \textcolor{green}{promise,"} said Holmes.



 "And I."



 "You will \textcolor{red}{excuse} this mask," continued our strange \textcolor{BurntOrange}{visitor.} "The

 \textcolor{green}{august} person who \textcolor{green}{employs} me wishes his agent to be \textcolor{BurntOrange}{unknown} to

 you, and I may \textcolor{BurntOrange}{confess} at once that the \textcolor{green}{title} by which I have

 just called myself is not exactly my own."



 "I was aware of it," said Holmes dryly.



 "The circumstances are of great delicacy, and every \textcolor{green}{precaution}

 has to be taken to quench what might \textcolor{BurntOrange}{grow} to be an \textcolor{green}{immense}

 \textcolor{red}{scandal} and seriously compromise one of the reigning families of

 Europe. To speak plainly, the matter implicates the great House

 of Ormstein, hereditary \textcolor{green}{kings} of Bohemia."



 "I was also aware of that," murmured Holmes, settling himself

 down in his armchair and closing his eyes.



 Our \textcolor{BurntOrange}{visitor} glanced with some apparent \textcolor{BurntOrange}{surprise} at the \textcolor{red}{languid,}

 \textcolor{red}{lounging} figure of the man who had been no \textcolor{BurntOrange}{doubt} depicted to him

 as the most \textcolor{green}{incisive} reasoner and most \textcolor{green}{energetic} agent in Europe.

 Holmes slowly reopened his eyes and looked impatiently at his

 \textcolor{green}{gigantic} client.



 "If your \textcolor{green}{Majesty} would condescend to state your \textcolor{red}{case,"} he

 remarked, "I should be better able to \textcolor{green}{advise} you."



 The man sprang from his chair and paced up and down the room in

 \textcolor{BurntOrange}{uncontrollable} \textcolor{red}{agitation.} Then, with a gesture of desperation, he

 tore the mask from his face and hurled it upon the \textcolor{green}{ground.} "You

 are right," he \textcolor{red}{cried;} "I am the \textcolor{green}{King.} Why should I \textcolor{blue}{attempt} to

 \textcolor{red}{conceal} it?"



 "Why, indeed?" murmured Holmes. "Your \textcolor{green}{Majesty} had not spoken

 before I was aware that I was addressing Wilhelm Gottsreich

 Sigismond von Ormstein, Grand \textcolor{green}{Duke} of Cassel-Felstein, and

 hereditary \textcolor{green}{King} of Bohemia."



 "But you can understand," said our strange \textcolor{BurntOrange}{visitor,} sitting down

 once more and passing his hand over his high \textcolor{BurntOrange}{white} forehead, "you

 can understand that I am not accustomed to doing such business in

 my own person. Yet the matter was so delicate that I could not

 \textcolor{green}{confide} it to an agent without putting myself in his power. I

 have come incognito from Prague for the purpose of \textcolor{green}{consulting}

 you."



 "Then, \textcolor{BurntOrange}{pray} \textcolor{green}{consult,"} said Holmes, shutting his eyes once more.



 "The \textcolor{green}{facts} are briefly these: Some five years ago, during a

 lengthy \textcolor{green}{visit} to Warsaw, I made the acquaintance of the well-known

 adventuress, Irene Adler. The name is no \textcolor{BurntOrange}{doubt} \textcolor{green}{familiar} to you."



 "Kindly look her up in my index, \textcolor{green}{Doctor,"} murmured Holmes without

 opening his eyes. For many years he had adopted a \textcolor{green}{system} of

 docketing all paragraphs concerning men and things, so that it

 was \textcolor{red}{difficult} to name a \textcolor{red}{subject} or a person on which he could not

 at once furnish \textcolor{green}{information.} In this \textcolor{red}{case} I \textcolor{green}{found} her biography

 sandwiched in between that of a Hebrew rabbi and that of a

 staff-commander who had written a monograph upon the deep-sea

 fishes.



 "Let me see!" said Holmes. "Hum! Born in New Jersey in the year

 1858. Contralto--hum! La Scala, hum! Prima donna Imperial \textcolor{BurntOrange}{Opera}

 of Warsaw--yes! Retired from \textcolor{red}{operatic} stage--ha! Living in

 London--quite so! Your \textcolor{green}{Majesty,} as I understand, became entangled

 with this \textcolor{BurntOrange}{young} person, wrote her some compromising \textcolor{blue}{letters,} and

 is now \textcolor{green}{desirous} of getting those \textcolor{blue}{letters} back."



 "Precisely so. But how--"



 "Was there a \textcolor{green}{secret} \textcolor{BurntOrange}{marriage?"}



 "None."



 "No \textcolor{green}{legal} papers or certificates?"



 "None."



 "Then I fail to follow your \textcolor{green}{Majesty.} If this \textcolor{BurntOrange}{young} person should

 produce her \textcolor{blue}{letters} for blackmailing or other purposes, how is

 she to \textcolor{green}{prove} their \textcolor{green}{authenticity?"}



 "There is the writing."



 "Pooh, pooh! \textcolor{red}{Forgery."}



 "My private note-paper."



 \textcolor{red}{"Stolen."}



 "My own \textcolor{green}{seal."}



 "Imitated."



 "My photograph."



 "Bought."



 "We were both in the photograph."



 "Oh, \textcolor{green}{dear!} That is very \textcolor{red}{bad!} Your \textcolor{green}{Majesty} has indeed committed an

 indiscretion."



 "I was mad--insane."



 "You have compromised yourself seriously."



 "I was only Crown \textcolor{green}{Prince} then. I was \textcolor{BurntOrange}{young.} I am but thirty now."



 "It must be recovered."



 "We have tried and failed."



 "Your \textcolor{green}{Majesty} must \textcolor{BurntOrange}{pay.} It must be bought."



 "She will not sell."



 \textcolor{red}{"Stolen,} then."



 "Five \textcolor{blue}{attempts} have been made. Twice \textcolor{red}{burglars} in my \textcolor{BurntOrange}{pay} ransacked

 her house. Once we diverted her luggage when she travelled. Twice

 she has been waylaid. There has been no \textcolor{blue}{result."}



 "No sign of it?"



 "Absolutely none."



 Holmes \textcolor{BurntOrange}{laughed.} "It is quite a \textcolor{BurntOrange}{pretty} little \textcolor{red}{problem,"} said he.



 "But a very serious one to me," returned the \textcolor{green}{King} reproachfully.



 "Very, indeed. And what does she propose to do with the

 photograph?"



 "To \textcolor{red}{ruin} me."



 "But how?"



 "I am about to be married."



 "So I have heard."



 "To Clotilde Lothman von Saxe-Meningen, second \textcolor{green}{daughter} of the

 \textcolor{green}{King} of Scandinavia. You may know the strict principles of her

 family. She is herself the very soul of delicacy. A shadow of a

 \textcolor{BurntOrange}{doubt} as to my conduct would bring the matter to an end."



 "And Irene Adler?"



 "Threatens to send them the photograph. And she will do it. I

 know that she will do it. You do not know her, but she has a soul

 of steel. She has the face of the most \textcolor{green}{beautiful} of women, and

 the mind of the most resolute of men. Rather than I should \textcolor{BurntOrange}{marry}

 another woman, there are no lengths to which she would not

 go--none."



 "You are sure that she has not sent it yet?"



 "I am sure."



 "And why?"



 "Because she has said that she would send it on the day when the

 betrothal was publicly proclaimed. That will be next Monday."



 "Oh, then we have three days yet," said Holmes with a \textcolor{red}{yawn.} "That

 is very \textcolor{green}{fortunate,} as I have one or two matters of \textcolor{BurntOrange}{importance} to

 look into just at \textcolor{BurntOrange}{present.} Your \textcolor{green}{Majesty} will, of course, stay in

 London for the \textcolor{BurntOrange}{present?"}



 "Certainly. You will find me at the Langham under the name of the

 \textcolor{green}{Count} Von Kramm."



 "Then I shall drop you a line to let you know how we \textcolor{BurntOrange}{progress."}



 \textcolor{BurntOrange}{"Pray} do so. I shall be all \textcolor{BurntOrange}{anxiety."}



 "Then, as to \textcolor{BurntOrange}{money?"}



 "You have carte blanche."



 "Absolutely?"



 "I tell you that I would give one of the provinces of my kingdom

 to have that photograph."



 "And for \textcolor{BurntOrange}{present} expenses?"



 The \textcolor{green}{King} took a heavy chamois leather bag from under his cloak

 and laid it on the table.



 "There are three hundred \textcolor{red}{pounds} in \textcolor{green}{gold} and seven hundred in

 notes," he said.



 Holmes scribbled a receipt upon a sheet of his note-book and

 handed it to him.



 "And Mademoiselle's address?" he asked.



 "Is Briony Lodge, Serpentine Avenue, St. \textcolor{red}{John's} Wood."



 Holmes took a note of it. "One other \textcolor{green}{question,"} said he. "Was the

 photograph a \textcolor{green}{cabinet?"}



 "It was."



 "Then, good-night, your \textcolor{green}{Majesty,} and I \textcolor{green}{trust} that we shall soon

 have some \textcolor{BurntOrange}{good} news for you. And good-night, Watson," he added,

 as the wheels of the royal brougham rolled down the street. "If

 you will be \textcolor{BurntOrange}{good} enough to call \textcolor{blue}{to-morrow} afternoon at three

 o'clock I should like to chat this little matter over with you."





 II.



 At three o'clock precisely I was at Baker Street, but Holmes had

 not yet returned. The landlady \textcolor{green}{informed} me that he had left the

 house \textcolor{blue}{shortly} after eight o'clock in the morning. I sat down

 beside the \textcolor{red}{fire,} however, with the intention of \textcolor{blue}{awaiting} him,

 however \textcolor{blue}{long} he might be. I was already deeply \textcolor{BurntOrange}{interested} in his

 \textcolor{BurntOrange}{inquiry,} for, though it was \textcolor{BurntOrange}{surrounded} by none of the \textcolor{BurntOrange}{grim} and

 strange \textcolor{green}{features} which were \textcolor{green}{associated} with the two \textcolor{red}{crimes} which

 I have already recorded, still, the nature of the \textcolor{red}{case} and the

 \textcolor{BurntOrange}{exalted} station of his client gave it a character of its own.

 Indeed, apart from the nature of the \textcolor{blue}{investigation} which my

 \textcolor{green}{friend} had on hand, there was something in his masterly grasp of

 a situation, and his keen, \textcolor{green}{incisive} \textcolor{green}{reasoning,} which made it a

 pleasure to me to \textcolor{green}{study} his \textcolor{green}{system} of work, and to follow the

 quick, subtle methods by which he disentangled the most

 inextricable \textcolor{blue}{mysteries.} So accustomed was I to his invariable

 \textcolor{BurntOrange}{success} that the very \textcolor{blue}{possibility} of his failing had ceased to

 enter into my head.



 It was close upon four before the door opened, and a

 drunken-looking groom, ill-kempt and side-whiskered, with an

 inflamed face and \textcolor{red}{disreputable} clothes, walked into the room.

 Accustomed as I was to my \textcolor{green}{friend's} \textcolor{blue}{amazing} powers in the use of

 disguises, I had to look three \textcolor{blue}{times} before I was certain that it

 was indeed he. With a nod he \textcolor{BurntOrange}{vanished} into the bedroom, whence he

 emerged in five minutes tweed-suited and \textcolor{green}{respectable,} as of old.

 Putting his hands into his pockets, he stretched out his legs in

 front of the \textcolor{red}{fire} and \textcolor{BurntOrange}{laughed} \textcolor{green}{heartily} for some minutes.



 "Well, really!" he \textcolor{red}{cried,} and then he choked and \textcolor{BurntOrange}{laughed} again

 until he was \textcolor{BurntOrange}{obliged} to \textcolor{red}{lie} back, \textcolor{red}{limp} and \textcolor{red}{helpless,} in the

 chair.



 "What is it?"



 "It's quite too funny. I am sure you could never \textcolor{blue}{guess} how I

 \textcolor{green}{employed} my morning, or what I ended by doing."



 "I can't imagine. I suppose that you have been \textcolor{BurntOrange}{watching} the

 habits, and perhaps the house, of Miss Irene Adler."



 "Quite so; but the \textcolor{blue}{sequel} was rather unusual. I will tell you,

 however. I left the house a little after eight o'clock this

 morning in the character of a groom out of work. There is a

 \textcolor{BurntOrange}{wonderful} \textcolor{BurntOrange}{sympathy} and freemasonry among horsey men. Be one of

 them, and you will know all that there is to know. I soon \textcolor{green}{found}

 Briony Lodge. It is a bijou villa, with a \textcolor{green}{garden} at the back, but

 built out in front right up to the road, two stories. Chubb lock

 to the door. Large sitting-room on the right side, well

 furnished, with \textcolor{blue}{long} windows almost to the floor, and those

 preposterous English window fasteners which a \textcolor{BurntOrange}{child} could open.

 Behind there was nothing \textcolor{BurntOrange}{remarkable,} \textcolor{green}{save} that the passage window

 could be reached from the \textcolor{BurntOrange}{top} of the coach-house. I walked round

 it and examined it closely from every point of view, but without

 noting anything else of \textcolor{green}{interest.}



 "I then \textcolor{red}{lounged} down the street and \textcolor{green}{found,} as I \textcolor{BurntOrange}{expected,} that

 there was a mews in a lane which runs down by one wall of the

 \textcolor{green}{garden.} I lent the ostlers a hand in rubbing down their \textcolor{green}{horses,}

 and received in \textcolor{green}{exchange} twopence, a glass of half and half, two

 \textcolor{green}{fills} of shag \textcolor{red}{tobacco,} and as much \textcolor{green}{information} as I could desire

 about Miss Adler, to say nothing of half a dozen other people in

 the neighbourhood in whom I was not in the least \textcolor{BurntOrange}{interested,} but

 whose biographies I was compelled to listen to."



 "And what of Irene Adler?" I asked.



 "Oh, she has turned all the men's heads down in that part. She is

 the daintiest thing under a bonnet on this planet. So say the

 Serpentine-mews, to a man. She lives quietly, sings at concerts,

 drives out at five every day, and returns at seven sharp for

 \textcolor{green}{dinner.} Seldom goes out at other \textcolor{blue}{times,} except when she sings.

 Has only one male \textcolor{BurntOrange}{visitor,} but a \textcolor{BurntOrange}{good} \textcolor{BurntOrange}{deal} of him. He is \textcolor{red}{dark,}

 handsome, and dashing, never calls less than once a day, and

 often twice. He is a Mr. Godfrey Norton, of the Inner Temple. See

 the \textcolor{green}{advantages} of a cabman as a confidant. They had driven him

 home a dozen \textcolor{blue}{times} from Serpentine-mews, and knew all about him.

 When I had listened to all they had to tell, I began to walk up

 and down near Briony Lodge once more, and to think over my \textcolor{blue}{plan}

 of campaign.



 "This Godfrey Norton was evidently an \textcolor{green}{important} factor in the

 matter. He was a \textcolor{red}{lawyer.} That sounded \textcolor{BurntOrange}{ominous.} What was the

 relation between them, and what the object of his repeated

 \textcolor{green}{visits?} Was she his client, his \textcolor{green}{friend,} or his \textcolor{red}{mistress?} If the

 former, she had probably transferred the photograph to his

 keeping. If the latter, it was less likely. On the issue of this

 \textcolor{green}{question} \textcolor{BurntOrange}{depended} whether I should \textcolor{BurntOrange}{continue} my work at Briony

 Lodge, or turn my \textcolor{green}{attention} to the \textcolor{green}{gentleman's} chambers in the

 Temple. It was a delicate point, and it widened the field of my

 \textcolor{BurntOrange}{inquiry.} I \textcolor{red}{fear} that I \textcolor{red}{bore} you with these details, but I have to

 let you see my little \textcolor{red}{difficulties,} if you are to understand the

 situation."



 "I am following you closely," I answered.



 "I was still \textcolor{green}{balancing} the matter in my mind when a hansom \textcolor{green}{cab}

 drove up to Briony Lodge, and a \textcolor{green}{gentleman} sprang out. He was a

 \textcolor{green}{remarkably} handsome man, \textcolor{red}{dark,} aquiline, and moustached--evidently

 the man of whom I had heard. He appeared to be in a

 great \textcolor{blue}{hurry,} \textcolor{BurntOrange}{shouted} to the cabman to \textcolor{BurntOrange}{wait,} and brushed past the

 maid who opened the door with the air of a man who was thoroughly

 at home.



 "He was in the house about half an hour, and I could \textcolor{blue}{catch}

 glimpses of him in the windows of the sitting-room, pacing up and

 down, \textcolor{green}{talking} excitedly, and waving his arms. Of her I could see

 nothing. Presently he emerged, looking even more flurried than

 before. As he stepped up to the \textcolor{green}{cab,} he \textcolor{green}{pulled} a \textcolor{green}{gold} \textcolor{BurntOrange}{watch} from

 his pocket and looked at it \textcolor{green}{earnestly,} 'Drive like the \textcolor{BurntOrange}{devil,'} he

 \textcolor{BurntOrange}{shouted,} 'first to \textcolor{red}{Gross} & Hankey's in \textcolor{green}{Regent} Street, and then to

 the \textcolor{BurntOrange}{Church} of St. Monica in the Edgeware Road. Half a guinea if

 you do it in twenty minutes!'



 "Away they went, and I was just wondering whether I should not do

 well to follow them when up the lane came a neat little landau,

 the coachman with his coat only half-buttoned, and his tie under

 his ear, while all the tags of his harness were sticking out of

 the buckles. It hadn't \textcolor{green}{pulled} up before she \textcolor{BurntOrange}{shot} out of the hall

 door and into it. I only caught a glimpse of her at the moment,

 but she was a \textcolor{BurntOrange}{lovely} woman, with a face that a man might \textcolor{red}{die} for.



 "'The \textcolor{BurntOrange}{Church} of St. Monica, \textcolor{red}{John,'} she \textcolor{red}{cried,} 'and half a

 \textcolor{green}{sovereign} if you reach it in twenty minutes.'



 "This was quite too \textcolor{BurntOrange}{good} to \textcolor{BurntOrange}{lose,} Watson. I was just \textcolor{green}{balancing}

 whether I should run for it, or whether I should perch behind her

 landau when a \textcolor{green}{cab} came through the street. The driver looked

 twice at such a \textcolor{red}{shabby} fare, but I jumped in before he could

 object. 'The \textcolor{BurntOrange}{Church} of St. Monica,' said I, 'and half a \textcolor{green}{sovereign}

 if you reach it in twenty minutes.' It was twenty-five minutes to

 twelve, and of course it was clear enough what was in the wind.



 "My cabby drove fast. I don't think I ever drove faster, but the

 others were there before us. The \textcolor{green}{cab} and the landau with their

 steaming \textcolor{green}{horses} were in front of the door when I \textcolor{blue}{arrived.} I paid

 the man and \textcolor{blue}{hurried} into the \textcolor{BurntOrange}{church.} There was not a soul there

 \textcolor{green}{save} the two whom I had followed and a surpliced clergyman, who

 seemed to be expostulating with them. They were all three

 standing in a knot in front of the altar. I \textcolor{red}{lounged} up the side

 aisle like any other \textcolor{red}{idler} who has dropped into a \textcolor{BurntOrange}{church.}

 \textcolor{blue}{Suddenly,} to my \textcolor{BurntOrange}{surprise,} the three at the altar faced round to

 me, and Godfrey Norton came running as hard as he could towards

 me.



 "'Thank \textcolor{BurntOrange}{God,'} he \textcolor{red}{cried.} 'You'll do. Come! Come!'



 "'What then?' I asked.



 "'Come, man, come, only three minutes, or it \textcolor{blue}{won't} be \textcolor{green}{legal.'}



 "I was half-dragged up to the altar, and before I knew where I was

 I \textcolor{green}{found} myself \textcolor{red}{mumbling} responses which were whispered in my ear,

 and \textcolor{green}{vouching} for things of which I knew nothing, and generally

 \textcolor{green}{assisting} in the secure tying up of Irene Adler, \textcolor{red}{spinster,} to

 Godfrey Norton, bachelor. It was all done in an instant, and

 there was the \textcolor{green}{gentleman} thanking me on the one side and the lady

 on the other, while the clergyman \textcolor{green}{beamed} on me in front. It was

 the most preposterous position in which I ever \textcolor{green}{found} myself in my

 life, and it was the \textcolor{blue}{thought} of it that \textcolor{blue}{started} me \textcolor{BurntOrange}{laughing} just

 now. It seems that there had been some informality about their

 license, that the clergyman absolutely \textcolor{red}{refused} to \textcolor{BurntOrange}{marry} them

 without a \textcolor{green}{witness} of some sort, and that my \textcolor{BurntOrange}{lucky} appearance

 \textcolor{green}{saved} the \textcolor{BurntOrange}{bridegroom} from having to \textcolor{blue}{sally} out into the streets in

 search of a best man. The \textcolor{BurntOrange}{bride} gave me a \textcolor{green}{sovereign,} and I mean

 to \textcolor{BurntOrange}{wear} it on my watch-chain in memory of the occasion."



 "This is a very \textcolor{BurntOrange}{unexpected} turn of affairs," said I; "and what

 then?"



 "Well, I \textcolor{green}{found} my \textcolor{blue}{plans} very seriously \textcolor{red}{menaced.} It looked as if

 the pair might take an immediate \textcolor{red}{departure,} and so necessitate

 very prompt and \textcolor{green}{energetic} \textcolor{green}{measures} on my part. At the \textcolor{BurntOrange}{church}

 door, however, they separated, he driving back to the Temple, and

 she to her own house. 'I shall drive out in the park at five as

 \textcolor{green}{usual,'} she said as she left him. I heard no more. They drove

 away in different directions, and I went off to make my own

 arrangements."



 "Which are?"



 "Some \textcolor{red}{cold} beef and a glass of \textcolor{green}{beer,"} he answered, ringing the

 bell. "I have been too busy to think of \textcolor{green}{food,} and I am likely to

 be busier still this evening. By the way, \textcolor{green}{Doctor,} I shall want

 your \textcolor{green}{co-operation."}



 "I shall be \textcolor{BurntOrange}{delighted."}



 "You don't mind \textcolor{blue}{breaking} the \textcolor{green}{law?"}



 "Not in the least."



 "Nor running a \textcolor{blue}{chance} of \textcolor{red}{arrest?"}



 "Not in a \textcolor{BurntOrange}{good} cause."



 "Oh, the cause is \textcolor{green}{excellent!"}



 "Then I am your man."



 "I was sure that I might rely on you."



 "But what is it you wish?"



 "When Mrs. Turner has brought in the tray I will make it clear to

 you. Now," he said as he turned hungrily on the simple fare that

 our landlady had \textcolor{green}{provided,} "I must discuss it while I \textcolor{green}{eat,} for I

 have not much \textcolor{blue}{time.} It is nearly five now. In two hours we must

 be on the scene of \textcolor{green}{action.} Miss Irene, or Madame, rather, returns

 from her drive at seven. We must be at Briony Lodge to meet her."



 "And what then?"



 "You must \textcolor{BurntOrange}{leave} that to me. I have already arranged what is to

 occur. There is only one point on which I must insist. You must

 not interfere, come what may. You understand?"



 "I am to be \textcolor{BurntOrange}{neutral?"}



 "To do nothing whatever. There will probably be some \textcolor{red}{small}

 unpleasantness. Do not \textcolor{green}{join} in it. It will end in my being

 conveyed into the house. Four or five minutes afterwards the

 sitting-room window will open. You are to station yourself close

 to that open window."



 "Yes."



 "You are to \textcolor{BurntOrange}{watch} me, for I will be visible to you."



 "Yes."



 "And when I raise my hand--so--you will throw into the room what

 I give you to throw, and will, at the same \textcolor{blue}{time,} raise the \textcolor{red}{cry} of

 \textcolor{red}{fire.} You quite follow me?"



 "Entirely."



 "It is nothing very \textcolor{red}{formidable,"} he said, taking a \textcolor{blue}{long} cigar-shaped

 roll from his pocket. "It is an ordinary plumber's smoke-rocket,

 fitted with a \textcolor{BurntOrange}{cap} at either end to make it self-lighting.

 Your \textcolor{green}{task} is \textcolor{red}{confined} to that. When you raise your \textcolor{red}{cry} of \textcolor{red}{fire,}

 it will be taken up by quite a number of people. You may then

 walk to the end of the street, and I will rejoin you in ten

 minutes. I \textcolor{BurntOrange}{hope} that I have made myself clear?"



 "I am to remain \textcolor{BurntOrange}{neutral,} to get near the window, to \textcolor{BurntOrange}{watch} you,

 and at the signal to throw in this object, then to raise the \textcolor{red}{cry}

 of \textcolor{red}{fire,} and to \textcolor{BurntOrange}{wait} you at the corner of the street."



 "Precisely."



 "Then you may entirely rely on me."



 "That is \textcolor{green}{excellent.} I think, perhaps, it is almost \textcolor{blue}{time} that I

 \textcolor{BurntOrange}{prepare} for the new role I have to play."



 He \textcolor{red}{disappeared} into his bedroom and returned in a few minutes in

 the character of an \textcolor{green}{amiable} and simple-minded Nonconformist

 clergyman. His broad \textcolor{red}{black} hat, his baggy trousers, his \textcolor{BurntOrange}{white}

 tie, his \textcolor{BurntOrange}{sympathetic} \textcolor{BurntOrange}{smile,} and \textcolor{green}{general} look of peering and

 benevolent \textcolor{BurntOrange}{curiosity} were such as Mr. \textcolor{red}{John} Hare alone could have

 equalled. It was not merely that Holmes \textcolor{red}{changed} his costume. His

 expression, his manner, his very soul seemed to vary with every

 fresh part that he assumed. The stage \textcolor{BurntOrange}{lost} a fine actor, even as

 science \textcolor{BurntOrange}{lost} an acute reasoner, when he became a \textcolor{green}{specialist} in

 \textcolor{red}{crime.}



 It was a quarter past six when we left Baker Street, and it still

 wanted ten minutes to the hour when we \textcolor{green}{found} ourselves in

 Serpentine Avenue. It was already dusk, and the lamps were just

 being lighted as we paced up and down in front of Briony Lodge,

 \textcolor{BurntOrange}{waiting} for the coming of its \textcolor{green}{occupant.} The house was just such

 as I had pictured it from Sherlock Holmes' \textcolor{green}{succinct} description,

 but the locality appeared to be less private than I \textcolor{BurntOrange}{expected.} On

 the \textcolor{red}{contrary,} for a \textcolor{red}{small} street in a \textcolor{BurntOrange}{quiet} neighbourhood, it was

 \textcolor{green}{remarkably} \textcolor{green}{animated.} There was a group of shabbily dressed men

 smoking and \textcolor{BurntOrange}{laughing} in a corner, a scissors-grinder with his

 wheel, two guardsmen who were \textcolor{BurntOrange}{flirting} with a nurse-girl, and

 several well-dressed \textcolor{BurntOrange}{young} men who were \textcolor{red}{lounging} up and down with

 cigars in their \textcolor{blue}{mouths.}



 "You see," remarked Holmes, as we paced to and fro in front of

 the house, "this \textcolor{BurntOrange}{marriage} rather simplifies matters. The

 photograph becomes a double-edged weapon now. The \textcolor{blue}{chances} are

 that she would be as \textcolor{red}{averse} to its being seen by Mr. Godfrey

 Norton, as our client is to its coming to the eyes of his

 \textcolor{green}{princess.} Now the \textcolor{green}{question} is, Where are we to find the

 photograph?"



 "Where, indeed?"



 "It is most unlikely that she carries it about with her. It is

 \textcolor{green}{cabinet} size. Too large for easy \textcolor{BurntOrange}{concealment} about a woman's

 dress. She knows that the \textcolor{green}{King} is capable of having her waylaid

 and searched. Two \textcolor{blue}{attempts} of the sort have already been made. We

 may take it, then, that she does not carry it about with her."



 "Where, then?"



 "Her \textcolor{green}{banker} or her \textcolor{red}{lawyer.} There is that double \textcolor{blue}{possibility.} But

 I am inclined to think neither. Women are naturally \textcolor{red}{secretive,}

 and they like to do their own \textcolor{red}{secreting.} Why should she hand it

 over to anyone else? She could \textcolor{green}{trust} her own \textcolor{green}{guardianship,} but

 she could not tell what indirect or political \textcolor{BurntOrange}{influence} might be

 brought to \textcolor{red}{bear} upon a business man. Besides, remember that she

 had resolved to use it within a few days. It must be where she

 can lay her hands upon it. It must be in her own house."



 "But it has twice been burgled."



 "Pshaw! They did not know how to look."



 "But how will you look?"



 "I will not look."



 "What then?"



 "I will get her to \textcolor{green}{show} me."



 "But she will \textcolor{red}{refuse."}



 "She will not be able to. But I hear the rumble of wheels. It is

 her carriage. Now carry out my orders to the \textcolor{blue}{letter."}



 As he \textcolor{red}{spoke} the gleam of the side-lights of a carriage came round

 the curve of the avenue. It was a smart little landau which

 rattled up to the door of Briony Lodge. As it \textcolor{green}{pulled} up, one of

 the \textcolor{red}{loafing} men at the corner dashed \textcolor{green}{forward} to open the door in

 the \textcolor{BurntOrange}{hope} of \textcolor{green}{earning} a copper, but was \textcolor{red}{elbowed} away by another

 \textcolor{red}{loafer,} who had rushed up with the same intention. A \textcolor{red}{fierce}

 \textcolor{red}{quarrel} \textcolor{red}{broke} out, which was \textcolor{green}{increased} by the two guardsmen, who

 took sides with one of the loungers, and by the scissors-grinder,

 who was \textcolor{green}{equally} \textcolor{red}{hot} upon the other side. A blow was struck, and

 in an instant the lady, who had stepped from her carriage, was

 the centre of a little knot of \textcolor{green}{flushed} and \textcolor{red}{struggling} men, who

 struck savagely at each other with their fists and sticks. Holmes

 dashed into the crowd to \textcolor{green}{protect} the lady; but just as he reached

 her he gave a \textcolor{red}{cry} and dropped to the \textcolor{green}{ground,} with the blood

 running \textcolor{green}{freely} down his face. At his \textcolor{red}{fall} the guardsmen took to

 their \textcolor{red}{heels} in one direction and the loungers in the other, while

 a number of better-dressed people, who had \textcolor{BurntOrange}{watched} the scuffle

 without taking part in it, crowded in to help the lady and to

 attend to the \textcolor{red}{injured} man. Irene Adler, as I will still call her,

 had \textcolor{blue}{hurried} up the steps; but she stood at the \textcolor{BurntOrange}{top} with her

 \textcolor{green}{superb} figure outlined against the lights of the hall, looking

 back into the street.



 "Is the poor \textcolor{green}{gentleman} much \textcolor{red}{hurt?"} she asked.



 "He is dead," \textcolor{red}{cried} several voices.



 "No, no, there's life in him!" \textcolor{BurntOrange}{shouted} another. "But \textcolor{red}{he'll} be

 gone before you can get him to \textcolor{BurntOrange}{hospital."}



 "He's a brave \textcolor{green}{fellow,"} said a woman. "They would have had the

 lady's purse and \textcolor{BurntOrange}{watch} if it hadn't been for him. They were a

 \textcolor{red}{gang,} and a rough one, too. Ah, he's breathing now."



 "He can't \textcolor{red}{lie} in the street. May we bring him in, marm?"



 "Surely. Bring him into the sitting-room. There is a comfortable

 sofa. This way, please!"



 Slowly and solemnly he was borne into Briony Lodge and laid out

 in the \textcolor{green}{principal} room, while I still observed the \textcolor{blue}{proceedings}

 from my post by the window. The lamps had been lit, but the

 \textcolor{red}{blinds} had not been drawn, so that I could see Holmes as he lay

 upon the \textcolor{red}{couch.} I do not know whether he was \textcolor{red}{seized} with

 compunction at that moment for the part he was playing, but I

 know that I never felt more \textcolor{green}{heartily} \textcolor{red}{ashamed} of myself in my life

 than when I saw the \textcolor{green}{beautiful} \textcolor{red}{creature} against whom I was

 \textcolor{red}{conspiring,} or the \textcolor{green}{grace} and kindliness with which she \textcolor{BurntOrange}{waited}

 upon the \textcolor{red}{injured} man. And yet it would be the blackest \textcolor{BurntOrange}{treachery}

 to Holmes to draw back now from the part which he had intrusted

 to me. I hardened my heart, and took the smoke-rocket from under

 my ulster. After all, I \textcolor{blue}{thought,} we are not \textcolor{red}{injuring} her. We are

 but \textcolor{red}{preventing} her from \textcolor{red}{injuring} another.



 Holmes had sat up upon the \textcolor{red}{couch,} and I saw him \textcolor{blue}{motion} like a man

 who is in need of air. A maid rushed across and threw open the

 window. At the same instant I saw him raise his hand and at the

 signal I tossed my \textcolor{red}{rocket} into the room with a \textcolor{red}{cry} of \textcolor{red}{"Fire!"} The

 \textcolor{green}{word} was no sooner out of my \textcolor{blue}{mouth} than the whole crowd of

 spectators, well dressed and ill--gentlemen, ostlers, and

 servant-maids--joined in a \textcolor{green}{general} \textcolor{BurntOrange}{shriek} of \textcolor{red}{"Fire!"} Thick clouds

 of smoke \textcolor{green}{curled} through the room and out at the open window. I

 caught a glimpse of rushing figures, and a moment later the voice

 of Holmes from within \textcolor{green}{assuring} them that it was a false \textcolor{BurntOrange}{alarm.}

 \textcolor{BurntOrange}{Slipping} through the \textcolor{BurntOrange}{shouting} crowd I made my way to the corner

 of the street, and in ten minutes was \textcolor{BurntOrange}{rejoiced} to find my

 \textcolor{green}{friend's} arm in mine, and to get away from the scene of \textcolor{red}{uproar.}

 He walked swiftly and in silence for some few minutes until we

 had turned down one of the \textcolor{BurntOrange}{quiet} streets which \textcolor{green}{lead} towards the

 Edgeware Road.



 "You did it very nicely, \textcolor{green}{Doctor,"} he remarked. "Nothing could

 have been better. It is all right."



 "You have the photograph?"



 "I know where it is."



 "And how did you find out?"



 "She \textcolor{green}{showed} me, as I told you she would."



 "I am still in the \textcolor{red}{dark."}



 "I do not wish to make a \textcolor{blue}{mystery,"} said he, \textcolor{BurntOrange}{laughing.} "The matter

 was perfectly simple. You, of course, saw that everyone in the

 street was an accomplice. They were all engaged for the evening."



 "I \textcolor{blue}{guessed} as much."



 "Then, when the \textcolor{red}{row} \textcolor{red}{broke} out, I had a little moist red paint in

 the palm of my hand. I rushed \textcolor{green}{forward,} \textcolor{red}{fell} down, clapped my hand

 to my face, and became a piteous \textcolor{BurntOrange}{spectacle.} It is an old \textcolor{BurntOrange}{trick."}



 "That also I could fathom."



 "Then they carried me in. She was \textcolor{red}{bound} to have me in. What else

 could she do? And into her sitting-room, which was the very room

 which I \textcolor{red}{suspected.} It lay between that and her bedroom, and I was

 determined to see which. They laid me on a \textcolor{red}{couch,} I \textcolor{blue}{motioned} for

 air, they were compelled to open the window, and you had your

 \textcolor{blue}{chance."}



 "How did that help you?"



 "It was all-important. When a woman thinks that her house is on

 \textcolor{red}{fire,} her instinct is at once to rush to the thing which she

 values most. It is a perfectly \textcolor{red}{overpowering} impulse, and I have

 more than once taken \textcolor{green}{advantage} of it. In the \textcolor{red}{case} of the

 Darlington substitution \textcolor{red}{scandal} it was of use to me, and also in

 the Arnsworth Castle business. A married woman \textcolor{red}{grabs} at her \textcolor{green}{baby;}

 an unmarried one reaches for her jewel-box. Now it was clear to

 me that our lady of to-day had nothing in the house more \textcolor{BurntOrange}{precious}

 to her than what we are in \textcolor{BurntOrange}{quest} of. She would rush to secure it.

 The \textcolor{BurntOrange}{alarm} of \textcolor{red}{fire} was admirably done. The smoke and \textcolor{BurntOrange}{shouting} were

 enough to shake \textcolor{green}{nerves} of steel. She responded beautifully. The

 photograph is in a recess behind a sliding panel just above the

 right bell-pull. She was there in an instant, and I caught a

 glimpse of it as she half-drew it out. When I \textcolor{red}{cried} out that it

 was a false \textcolor{BurntOrange}{alarm,} she replaced it, glanced at the \textcolor{red}{rocket,} rushed

 from the room, and I have not seen her since. I rose, and, making

 my \textcolor{red}{excuses,} \textcolor{BurntOrange}{escaped} from the house. I hesitated whether to

 \textcolor{blue}{attempt} to secure the photograph at once; but the coachman had

 come in, and as he was \textcolor{BurntOrange}{watching} me narrowly it seemed safer to

 \textcolor{BurntOrange}{wait.} A little over-precipitance may \textcolor{red}{ruin} all."



 "And now?" I asked.



 "Our \textcolor{BurntOrange}{quest} is practically finished. I shall call with the \textcolor{green}{King}

 \textcolor{blue}{to-morrow,} and with you, if you care to come with us. We will be

 \textcolor{green}{shown} into the sitting-room to \textcolor{BurntOrange}{wait} for the lady, but it is

 probable that when she comes she may find neither us nor the

 photograph. It might be a satisfaction to his \textcolor{green}{Majesty} to regain

 it with his own hands."



 "And when will you call?"



 "At eight in the morning. She will not be up, so that we shall

 have a clear field. Besides, we must be prompt, for this \textcolor{BurntOrange}{marriage}

 may mean a complete \textcolor{red}{change} in her life and habits. I must wire to

 the \textcolor{green}{King} without \textcolor{red}{delay."}



 We had reached Baker Street and had stopped at the door. He was

 searching his pockets for the key when someone passing said:



 "Good-night, Mister Sherlock Holmes."



 There were several people on the \textcolor{green}{pavement} at the \textcolor{blue}{time,} but the

 greeting appeared to come from a \textcolor{green}{slim} \textcolor{BurntOrange}{youth} in an ulster who had

 \textcolor{blue}{hurried} by.



 "I've heard that voice before," said Holmes, \textcolor{BurntOrange}{staring} down the

 dimly lit street. "Now, I wonder who the deuce that could have

 been."





 III.



 I slept at Baker Street that night, and we were engaged upon our

 \textcolor{green}{toast} and coffee in the morning when the \textcolor{green}{King} of Bohemia rushed

 into the room.



 "You have really got it!" he \textcolor{red}{cried,} grasping Sherlock Holmes by

 either \textcolor{green}{shoulder} and looking eagerly into his face.



 "Not yet."



 "But you have \textcolor{BurntOrange}{hopes?"}



 "I have \textcolor{BurntOrange}{hopes."}



 "Then, come. I am all \textcolor{red}{impatience} to be gone."



 "We must have a \textcolor{green}{cab."}



 "No, my brougham is \textcolor{BurntOrange}{waiting."}



 "Then that will \textcolor{BurntOrange}{simplify} matters." We descended and \textcolor{blue}{started} off

 once more for Briony Lodge.



 "Irene Adler is married," remarked Holmes.



 "Married! When?"



 "Yesterday."



 "But to whom?"



 "To an English \textcolor{red}{lawyer} named Norton."



 "But she could not \textcolor{green}{love} him."



 "I am in \textcolor{BurntOrange}{hopes} that she does."



 "And why in \textcolor{BurntOrange}{hopes?"}



 "Because it would spare your \textcolor{green}{Majesty} all \textcolor{red}{fear} of future

 \textcolor{red}{annoyance.} If the lady \textcolor{green}{loves} her husband, she does not \textcolor{green}{love} your

 \textcolor{green}{Majesty.} If she does not \textcolor{green}{love} your \textcolor{green}{Majesty,} there is no \textcolor{green}{reason}

 why she should interfere with your \textcolor{green}{Majesty's} \textcolor{blue}{plan."}



 "It is \textcolor{green}{true.} And yet--Well! I wish she had been of my own

 station! What a queen she would have made!" He \textcolor{red}{relapsed} into a

 \textcolor{red}{moody} silence, which was not \textcolor{red}{broken} until we drew up in

 Serpentine Avenue.



 The door of Briony Lodge was open, and an elderly woman stood

 upon the steps. She \textcolor{BurntOrange}{watched} us with a \textcolor{red}{sardonic} eye as we stepped

 from the brougham.



 "Mr. Sherlock Holmes, I believe?" said she.



 "I am Mr. Holmes," answered my \textcolor{green}{companion,} looking at her with a

 \textcolor{green}{questioning} and rather \textcolor{BurntOrange}{startled} gaze.



 "Indeed! My \textcolor{red}{mistress} told me that you were likely to call. She

 left this morning with her husband by the 5:15 train from Charing

 \textcolor{red}{Cross} for the Continent."



 "What!" Sherlock Holmes \textcolor{blue}{staggered} back, \textcolor{BurntOrange}{white} with \textcolor{red}{chagrin} and

 \textcolor{BurntOrange}{surprise.} "Do you mean that she has left England?"



 "Never to return."



 "And the papers?" asked the \textcolor{green}{King} hoarsely. "All is \textcolor{BurntOrange}{lost."}



 "We shall see." He pushed past the \textcolor{BurntOrange}{servant} and rushed into the

 drawing-room, followed by the \textcolor{green}{King} and myself. The furniture was

 scattered about in every direction, with dismantled shelves and

 open drawers, as if the lady had hurriedly ransacked them before

 her flight. Holmes rushed at the bell-pull, tore back a \textcolor{red}{small}

 sliding shutter, and, \textcolor{red}{plunging} in his hand, \textcolor{green}{pulled} out a

 photograph and a \textcolor{blue}{letter.} The photograph was of Irene Adler

 herself in evening dress, the \textcolor{blue}{letter} was superscribed to

 "Sherlock Holmes, Esq. To be left till called for." My \textcolor{green}{friend}

 tore it open and we all three read it together. It was dated at

 midnight of the \textcolor{green}{preceding} night and ran in this way:



 "MY \textcolor{green}{DEAR} MR. SHERLOCK HOLMES,--You really did it very well. You

 took me in \textcolor{green}{completely.} Until after the \textcolor{BurntOrange}{alarm} of \textcolor{red}{fire,} I had not a

 \textcolor{red}{suspicion.} But then, when I \textcolor{green}{found} how I had betrayed myself, I

 began to think. I had been \textcolor{BurntOrange}{warned} against you months ago. I had

 been told that if the \textcolor{green}{King} \textcolor{green}{employed} an agent it would certainly

 be you. And your address had been given me. Yet, with all this,

 you made me reveal what you wanted to know. Even after I became

 \textcolor{BurntOrange}{suspicious,} I \textcolor{green}{found} it hard to think \textcolor{red}{evil} of such a \textcolor{green}{dear,} \textcolor{green}{kind}

 old clergyman. But, you know, I have been trained as an actress

 myself. Male costume is nothing new to me. I often take \textcolor{green}{advantage}

 of the \textcolor{green}{freedom} which it gives. I sent \textcolor{red}{John,} the coachman, to

 \textcolor{BurntOrange}{watch} you, ran up stairs, got into my walking-clothes, as I call

 them, and came down just as you \textcolor{BurntOrange}{departed.}



 "Well, I followed you to your door, and so made sure that I was

 really an object of \textcolor{green}{interest} to the celebrated Mr. Sherlock

 Holmes. Then I, rather imprudently, wished you good-night, and

 \textcolor{blue}{started} for the Temple to see my husband.



 "We both \textcolor{blue}{thought} the best resource was flight, when pursued by

 so \textcolor{red}{formidable} an \textcolor{red}{antagonist;} so you will find the \textcolor{green}{nest} empty when

 you call \textcolor{blue}{to-morrow.} As to the photograph, your client may \textcolor{green}{rest} in

 \textcolor{BurntOrange}{peace.} I \textcolor{green}{love} and am \textcolor{green}{loved} by a better man than he. The \textcolor{green}{King} may

 do what he will without \textcolor{red}{hindrance} from one whom he has \textcolor{red}{cruelly}

 \textcolor{red}{wronged.} I keep it only to \textcolor{green}{safeguard} myself, and to \textcolor{green}{preserve} a

 weapon which will always secure me from any steps which he might

 take in the future. I \textcolor{BurntOrange}{leave} a photograph which he might care to

 \textcolor{red}{possess;} and I remain, \textcolor{green}{dear} Mr. Sherlock Holmes,



 "Very truly yours,

 "IRENE NORTON, née ADLER."



 "What a woman--oh, what a woman!" \textcolor{red}{cried} the \textcolor{green}{King} of Bohemia, when

 we had all three read this epistle. "Did I not tell you how quick

 and resolute she was? Would she not have made an \textcolor{green}{admirable} queen?

 Is it not a \textcolor{red}{pity} that she was not on my \textcolor{green}{level?"}



 "From what I have seen of the lady she seems indeed to be on a

 very different \textcolor{green}{level} to your \textcolor{green}{Majesty,"} said Holmes \textcolor{red}{coldly.} "I am

 sorry that I have not been able to bring your \textcolor{green}{Majesty's} business

 to a more \textcolor{BurntOrange}{successful} conclusion."



 "On the \textcolor{red}{contrary,} my \textcolor{green}{dear} \textcolor{green}{sir,"} \textcolor{red}{cried} the \textcolor{green}{King;} "nothing could be

 more \textcolor{BurntOrange}{successful.} I know that her \textcolor{green}{word} is inviolate. The

 photograph is now as \textcolor{green}{safe} as if it were in the \textcolor{red}{fire."}



 "I am \textcolor{BurntOrange}{glad} to hear your \textcolor{green}{Majesty} say so."



 "I am immensely indebted to you. \textcolor{BurntOrange}{Pray} tell me in what way I can

 \textcolor{BurntOrange}{reward} you. This ring--" He \textcolor{BurntOrange}{slipped} an emerald \textcolor{red}{snake} ring from

 his finger and held it out upon the palm of his hand.



 "Your \textcolor{green}{Majesty} has something which I should value even more

 highly," said Holmes.



 "You have but to name it."



 "This photograph!"



 The \textcolor{green}{King} \textcolor{BurntOrange}{stared} at him in amazement.



 "Irene's photograph!" he \textcolor{red}{cried.} "Certainly, if you wish it."



 "I thank your \textcolor{green}{Majesty.} Then there is no more to be done in the

 matter. I have the honour to wish you a very good-morning." He

 bowed, and, turning away without observing the hand which the

 \textcolor{green}{King} had stretched out to him, he set off in my company for his

 chambers.



 And that was how a great \textcolor{red}{scandal} \textcolor{BurntOrange}{threatened} to affect the kingdom

 of Bohemia, and how the best \textcolor{blue}{plans} of Mr. Sherlock Holmes were

 beaten by a woman's \textcolor{green}{wit.} He used to make \textcolor{green}{merry} over the

 \textcolor{green}{cleverness} of women, but I have not heard him do it of \textcolor{red}{late.} And

 when he speaks of Irene Adler, or when he refers to her

 photograph, it is always under the honourable \textcolor{green}{title} of the woman.







 \textcolor{BurntOrange}{ADVENTURE} II. THE RED-HEADED \textcolor{green}{LEAGUE}



 I had called upon my \textcolor{green}{friend,} Mr. Sherlock Holmes, one day in the

 autumn of last year and \textcolor{green}{found} him in deep conversation with a

 very stout, florid-faced, elderly \textcolor{green}{gentleman} with fiery red hair.

 With an \textcolor{green}{apology} for my \textcolor{red}{intrusion,} I was about to \textcolor{red}{withdraw} when

 Holmes \textcolor{green}{pulled} me abruptly into the room and closed the door

 behind me.



 "You could not possibly have come at a better \textcolor{blue}{time,} my \textcolor{green}{dear}

 Watson," he said cordially.



 "I was \textcolor{red}{afraid} that you were engaged."



 "So I am. Very much so."



 "Then I can \textcolor{BurntOrange}{wait} in the next room."



 "Not at all. This \textcolor{green}{gentleman,} Mr. Wilson, has been my \textcolor{green}{partner} and

 \textcolor{green}{helper} in many of my most \textcolor{BurntOrange}{successful} \textcolor{red}{cases,} and I have no

 \textcolor{BurntOrange}{doubt} that he will be of the utmost use to me in yours also."



 The stout \textcolor{green}{gentleman} half rose from his chair and gave a bob of

 greeting, with a quick little \textcolor{green}{questioning} glance from his \textcolor{red}{small}

 fat-encircled eyes.



 "Try the settee," said Holmes, \textcolor{red}{relapsing} into his armchair and

 putting his fingertips together, as was his custom when in

 \textcolor{BurntOrange}{judicial} moods. "I know, my \textcolor{green}{dear} Watson, that you \textcolor{BurntOrange}{share} my \textcolor{green}{love}

 of all that is \textcolor{BurntOrange}{bizarre} and outside the \textcolor{green}{conventions} and humdrum

 \textcolor{green}{routine} of everyday life. You have \textcolor{green}{shown} your relish for it by

 the \textcolor{BurntOrange}{enthusiasm} which has prompted you to \textcolor{green}{chronicle,} and, if you

 will \textcolor{red}{excuse} my saying so, somewhat to embellish so many of my own

 little \textcolor{BurntOrange}{adventures."}



 "Your \textcolor{red}{cases} have indeed been of the greatest \textcolor{green}{interest} to me," I

 observed.



 "You will remember that I remarked the other day, just before we

 went into the very simple \textcolor{red}{problem} \textcolor{BurntOrange}{presented} by Miss Mary

 Sutherland, that for strange effects and \textcolor{green}{extraordinary}

 combinations we must go to life itself, which is always far more

 \textcolor{BurntOrange}{daring} than any \textcolor{green}{effort} of the imagination."



 "A \textcolor{green}{proposition} which I took the \textcolor{BurntOrange}{liberty} of \textcolor{BurntOrange}{doubting."}



 "You did, \textcolor{green}{Doctor,} but none the less you must come round to my

 view, for otherwise I shall keep on piling \textcolor{green}{fact} upon \textcolor{green}{fact} on you

 until your \textcolor{green}{reason} \textcolor{blue}{breaks} down under them and acknowledges me to

 be right. Now, Mr. Jabez Wilson here has been \textcolor{BurntOrange}{good} enough to call

 upon me this morning, and to begin a narrative which \textcolor{green}{promises} to

 be one of the most singular which I have listened to for some

 \textcolor{blue}{time.} You have heard me remark that the strangest and most \textcolor{BurntOrange}{unique}

 things are very often connected not with the larger but with the

 \textcolor{red}{smaller} \textcolor{red}{crimes,} and occasionally, indeed, where there is room for

 \textcolor{BurntOrange}{doubt} whether any positive \textcolor{red}{crime} has been committed. As far as I

 have heard it is \textcolor{red}{impossible} for me to say whether the \textcolor{BurntOrange}{present}

 \textcolor{red}{case} is an instance of \textcolor{red}{crime} or not, but the course of events is

 certainly among the most singular that I have ever listened to.

 Perhaps, Mr. Wilson, you would have the great \textcolor{green}{kindness} to

 recommence your narrative. I ask you not merely because my \textcolor{green}{friend}

 Dr. Watson has not heard the opening part but also because the

 peculiar nature of the story makes me \textcolor{BurntOrange}{anxious} to have every

 possible detail from your lips. As a \textcolor{BurntOrange}{rule,} when I have heard some

 slight indication of the course of events, I am able to \textcolor{green}{guide}

 myself by the thousands of other similar \textcolor{red}{cases} which occur to my

 memory. In the \textcolor{BurntOrange}{present} instance I am \textcolor{red}{forced} to admit that the

 \textcolor{green}{facts} are, to the best of my belief, \textcolor{BurntOrange}{unique."}



 The portly client puffed out his chest with an appearance of some

 little \textcolor{green}{pride} and \textcolor{green}{pulled} a \textcolor{red}{dirty} and wrinkled newspaper from the

 inside pocket of his greatcoat. As he glanced down the

 advertisement column, with his head thrust \textcolor{green}{forward} and the paper

 flattened out upon his knee, I took a \textcolor{BurntOrange}{good} look at the man and

 endeavoured, after the fashion of my \textcolor{green}{companion,} to read the

 indications which might be \textcolor{BurntOrange}{presented} by his dress or appearance.



 I did not \textcolor{BurntOrange}{gain} very much, however, by my inspection. Our \textcolor{BurntOrange}{visitor}

 \textcolor{red}{bore} every mark of being an average \textcolor{BurntOrange}{commonplace} British

 tradesman, \textcolor{red}{obese,} \textcolor{red}{pompous,} and slow. He wore rather baggy grey

 \textcolor{green}{shepherd's} check trousers, a not over-clean \textcolor{red}{black} frock-coat,

 unbuttoned in the front, and a \textcolor{red}{drab} waistcoat with a heavy brassy

 Albert chain, and a square pierced bit of metal dangling down as

 an ornament. A \textcolor{red}{frayed} top-hat and a \textcolor{red}{faded} brown overcoat with a

 wrinkled \textcolor{green}{velvet} collar lay upon a chair beside him. Altogether,

 look as I would, there was nothing \textcolor{BurntOrange}{remarkable} about the man \textcolor{green}{save}

 his blazing red head, and the expression of extreme \textcolor{red}{chagrin} and

 \textcolor{red}{discontent} upon his \textcolor{green}{features.}



 Sherlock Holmes' quick eye took in my \textcolor{green}{occupation,} and he shook

 his head with a \textcolor{BurntOrange}{smile} as he noticed my \textcolor{green}{questioning} glances.

 "Beyond the \textcolor{green}{obvious} \textcolor{green}{facts} that he has at some \textcolor{blue}{time} done \textcolor{green}{manual}

 labour, that he takes snuff, that he is a Freemason, that he has

 been in China, and that he has done a \textcolor{green}{considerable} amount of

 writing lately, I can deduce nothing else."



 Mr. Jabez Wilson \textcolor{blue}{started} up in his chair, with his forefinger

 upon the paper, but his eyes upon my \textcolor{green}{companion.}



 "How, in the name of good-fortune, did you know all that, Mr.

 Holmes?" he asked. "How did you know, for example, that I did

 \textcolor{green}{manual} labour. It's as \textcolor{green}{true} as \textcolor{green}{gospel,} for I began as a \textcolor{blue}{ship's}

 carpenter."



 "Your hands, my \textcolor{green}{dear} \textcolor{green}{sir.} Your right hand is quite a size larger

 than your left. You have worked with it, and the muscles are more

 developed."



 "Well, the snuff, then, and the Freemasonry?"



 "I \textcolor{blue}{won't} \textcolor{BurntOrange}{insult} your \textcolor{BurntOrange}{intelligence} by telling you how I read that,

 especially as, rather against the strict \textcolor{BurntOrange}{rules} of your order, you

 use an arc-and-compass breastpin."



 "Ah, of course, I forgot that. But the writing?"



 "What else can be indicated by that right cuff so very shiny for

 five inches, and the left one with the smooth \textcolor{red}{patch} near the

 \textcolor{red}{elbow} where you \textcolor{green}{rest} it upon the desk?"



 "Well, but China?"



 "The fish that you have tattooed \textcolor{BurntOrange}{immediately} above your right

 wrist could only have been done in China. I have made a \textcolor{red}{small}

 \textcolor{green}{study} of tattoo marks and have even \textcolor{green}{contributed} to the literature

 of the \textcolor{red}{subject.} That \textcolor{BurntOrange}{trick} of \textcolor{red}{staining} the fishes' scales of a

 delicate pink is quite peculiar to China. When, in addition, I

 see a Chinese coin hanging from your watch-chain, the matter

 becomes even more simple."



 Mr. Jabez Wilson \textcolor{BurntOrange}{laughed} \textcolor{red}{heavily.} "Well, I never!" said he. "I

 \textcolor{blue}{thought} at first that you had done something \textcolor{green}{clever,} but I see

 that there was nothing in it, after all."



 "I begin to think, Watson," said Holmes, "that I make a \textcolor{red}{mistake}

 in \textcolor{green}{explaining.} 'Omne ignotum pro magnifico,' you know, and my

 poor little reputation, such as it is, will \textcolor{red}{suffer} \textcolor{red}{shipwreck} if I

 am so \textcolor{BurntOrange}{candid.} Can you not find the advertisement, Mr. Wilson?"



 "Yes, I have got it now," he answered with his thick red finger

 planted \textcolor{red}{halfway} down the column. "Here it is. This is what began

 it all. You just read it for yourself, \textcolor{green}{sir."}



 I took the paper from him and read as follows:



 "TO THE RED-HEADED \textcolor{green}{LEAGUE:} On \textcolor{green}{account} of the \textcolor{green}{bequest} of the \textcolor{red}{late}

 Ezekiah Hopkins, of Lebanon, Pennsylvania, U. S. A., there is now

 another \textcolor{red}{vacancy} open which entitles a member of the \textcolor{green}{League} to a

 \textcolor{BurntOrange}{salary} of 4 \textcolor{red}{pounds} a week for \textcolor{green}{purely} nominal services. All

 red-headed men who are sound in body and mind and above the age

 of twenty-one years, are \textcolor{green}{eligible.} Apply in person on Monday, at

 eleven o'clock, to Duncan Ross, at the offices of the \textcolor{green}{League,} 7

 \textcolor{green}{Pope's} \textcolor{BurntOrange}{Court,} \textcolor{green}{Fleet} Street."



 "What on earth does this mean?" I ejaculated after I had twice

 read over the \textcolor{green}{extraordinary} \textcolor{blue}{announcement.}



 Holmes \textcolor{BurntOrange}{chuckled} and wriggled in his chair, as was his habit when

 in high \textcolor{green}{spirits.} "It is a little off the beaten \textcolor{blue}{track,} isn't it?"

 said he. "And now, Mr. Wilson, off you go at scratch and tell us

 all about yourself, your \textcolor{green}{household,} and the effect which this

 advertisement had upon your \textcolor{BurntOrange}{fortunes.} You will first make a note,

 \textcolor{green}{Doctor,} of the paper and the date."



 "It is The Morning \textcolor{green}{Chronicle} of April 27, 1890. Just two months

 ago."



 "Very \textcolor{BurntOrange}{good.} Now, Mr. Wilson?"



 "Well, it is just as I have been telling you, Mr. Sherlock

 Holmes," said Jabez Wilson, mopping his forehead; "I have a \textcolor{red}{small}

 pawnbroker's business at Coburg Square, near the City. It's not a

 very large affair, and of \textcolor{red}{late} years it has not done more than

 just give me a living. I used to be able to keep two assistants,

 but now I only keep one; and I would have a \textcolor{green}{job} to \textcolor{BurntOrange}{pay} him but

 that he is willing to come for half wages so as to \textcolor{green}{learn} the

 business."



 "What is the name of this \textcolor{BurntOrange}{obliging} \textcolor{BurntOrange}{youth?"} asked Sherlock Holmes.



 "His name is Vincent Spaulding, and he's not such a \textcolor{BurntOrange}{youth,}

 either. It's hard to say his age. I should not wish a smarter

 assistant, Mr. Holmes; and I know very well that he could better

 himself and \textcolor{green}{earn} twice what I am able to give him. But, after

 all, if he is \textcolor{green}{satisfied,} why should I put ideas in his head?"



 "Why, indeed? You seem most \textcolor{green}{fortunate} in having an \textcolor{green}{employé} who

 comes under the \textcolor{green}{full} market price. It is not a common experience

 among employers in this age. I don't know that your assistant is

 not as \textcolor{BurntOrange}{remarkable} as your advertisement."



 "Oh, he has his \textcolor{red}{faults,} too," said Mr. Wilson. "Never was such a

 \textcolor{green}{fellow} for photography. Snapping away with a camera when he ought

 to be \textcolor{BurntOrange}{improving} his mind, and then diving down into the cellar

 like a rabbit into its hole to \textcolor{BurntOrange}{develop} his pictures. That is his

 \textcolor{green}{main} \textcolor{red}{fault,} but on the whole he's a \textcolor{BurntOrange}{good} worker. There's no \textcolor{red}{vice}

 in him."



 "He is still with you, I presume?"



 "Yes, \textcolor{green}{sir.} He and a girl of fourteen, who does a bit of simple

 cooking and keeps the place clean--that's all I have in the

 house, for I am a \textcolor{red}{widower} and never had any family. We live very

 quietly, \textcolor{green}{sir,} the three of us; and we keep a roof over our heads

 and \textcolor{BurntOrange}{pay} our \textcolor{red}{debts,} if we do nothing more.



 "The first thing that put us out was that advertisement.

 Spaulding, he came down into the office just this day eight

 weeks, with this very paper in his hand, and he says:



 "'I wish to the \textcolor{BurntOrange}{Lord,} Mr. Wilson, that I was a red-headed man.'



 "'Why that?' I asks.



 "'Why,' says he, 'here's another \textcolor{red}{vacancy} on the \textcolor{green}{League} of the

 Red-headed Men. It's \textcolor{green}{worth} quite a little \textcolor{BurntOrange}{fortune} to any man who

 gets it, and I understand that there are more \textcolor{red}{vacancies} than

 there are men, so that the \textcolor{green}{trustees} are at their \textcolor{green}{wits'} end what

 to do with the \textcolor{BurntOrange}{money.} If my hair would only \textcolor{red}{change} colour, here's

 a nice little crib all \textcolor{blue}{ready} for me to step into.'



 "'Why, what is it, then?' I asked. You see, Mr. Holmes, I am a

 very stay-at-home man, and as my business came to me instead of

 my having to go to it, I was often weeks on end without putting

 my foot over the door-mat. In that way I didn't know much of what

 was going on outside, and I was always \textcolor{BurntOrange}{glad} of a bit of news.



 "'Have you never heard of the \textcolor{green}{League} of the Red-headed Men?' he

 asked with his eyes open.



 "'Never.'



 "'Why, I wonder at that, for you are \textcolor{green}{eligible} yourself for one

 of the \textcolor{red}{vacancies.'}



 "'And what are they \textcolor{green}{worth?'} I asked.



 "'Oh, merely a couple of hundred a year, but the work is slight,

 and it need not interfere very much with one's other

 \textcolor{green}{occupations.'}



 "Well, you can easily think that that made me \textcolor{BurntOrange}{prick} up my ears,

 for the business has not been over-good for some years, and an

 \textcolor{green}{extra} couple of hundred would have been very \textcolor{green}{handy.}



 "'Tell me all about it,' said I.



 "'Well,' said he, \textcolor{green}{showing} me the advertisement, 'you can see for

 yourself that the \textcolor{green}{League} has a \textcolor{red}{vacancy,} and there is the address

 where you should apply for particulars. As far as I can make out,

 the \textcolor{green}{League} was \textcolor{green}{founded} by an American millionaire, Ezekiah

 Hopkins, who was very peculiar in his ways. He was himself

 red-headed, and he had a great \textcolor{BurntOrange}{sympathy} for all red-headed men;

 so when he \textcolor{red}{died} it was \textcolor{green}{found} that he had left his enormous

 \textcolor{BurntOrange}{fortune} in the hands of \textcolor{green}{trustees,} with \textcolor{green}{instructions} to apply the

 \textcolor{green}{interest} to the \textcolor{green}{providing} of easy \textcolor{green}{berths} to men whose hair is of

 that colour. From all I hear it is \textcolor{BurntOrange}{splendid} \textcolor{BurntOrange}{pay} and very little to

 do.'



 "'But,' said I, 'there would be millions of red-headed men who

 would apply.'



 "'Not so many as you might think,' he answered. 'You see it is

 really \textcolor{red}{confined} to Londoners, and to grown men. This American had

 \textcolor{blue}{started} from London when he was \textcolor{BurntOrange}{young,} and he wanted to do the

 old town a \textcolor{BurntOrange}{good} turn. Then, again, I have heard it is no use your

 applying if your hair is light red, or \textcolor{red}{dark} red, or anything but

 \textcolor{green}{real} bright, blazing, fiery red. Now, if you cared to apply, Mr.

 Wilson, you would just walk in; but perhaps it would hardly be

 \textcolor{green}{worth} your while to put yourself out of the way for the sake of a

 few hundred \textcolor{red}{pounds.'}



 "Now, it is a \textcolor{green}{fact,} \textcolor{green}{gentlemen,} as you may see for yourselves,

 that my hair is of a very \textcolor{green}{full} and rich tint, so that it seemed

 to me that if there was to be any \textcolor{BurntOrange}{competition} in the matter I

 stood as \textcolor{BurntOrange}{good} a \textcolor{blue}{chance} as any man that I had ever met. Vincent

 Spaulding seemed to know so much about it that I \textcolor{blue}{thought} he might

 \textcolor{green}{prove} useful, so I just ordered him to put up the shutters for

 the day and to come right away with me. He was very willing to

 have a \textcolor{BurntOrange}{holiday,} so we shut the business up and \textcolor{blue}{started} off for

 the address that was given us in the advertisement.



 "I never \textcolor{BurntOrange}{hope} to see such a sight as that again, Mr. Holmes. From

 north, south, east, and west every man who had a shade of red in

 his hair had tramped into the city to answer the advertisement.

 \textcolor{green}{Fleet} Street was choked with red-headed folk, and \textcolor{green}{Pope's} \textcolor{BurntOrange}{Court}

 looked like a coster's orange \textcolor{red}{barrow.} I should not have \textcolor{blue}{thought}

 there were so many in the whole country as were brought together

 by that single advertisement. Every shade of colour they

 were--straw, \textcolor{red}{lemon,} orange, brick, Irish-setter, liver, clay;

 but, as Spaulding said, there were not many who had the \textcolor{green}{real}

 \textcolor{green}{vivid} flame-coloured tint. When I saw how many were \textcolor{BurntOrange}{waiting,} I

 would have given it up in \textcolor{red}{despair;} but Spaulding would not hear

 of it. How he did it I could not imagine, but he pushed and

 \textcolor{green}{pulled} and \textcolor{red}{butted} until he got me through the crowd, and right up

 to the steps which \textcolor{green}{led} to the office. There was a double stream

 upon the stair, some going up in \textcolor{BurntOrange}{hope,} and some coming back

 dejected; but we wedged in as well as we could and soon \textcolor{green}{found}

 ourselves in the office."



 "Your experience has been a most \textcolor{green}{entertaining} one," remarked

 Holmes as his client paused and refreshed his memory with a huge

 pinch of snuff. \textcolor{BurntOrange}{"Pray} \textcolor{BurntOrange}{continue} your very \textcolor{green}{interesting} \textcolor{green}{statement."}



 "There was nothing in the office but a couple of wooden chairs

 and a \textcolor{BurntOrange}{deal} table, behind which sat a \textcolor{red}{small} man with a head that

 was even redder than mine. He said a few \textcolor{green}{words} to each \textcolor{green}{candidate}

 as he came up, and then he always \textcolor{green}{managed} to find some \textcolor{red}{fault} in

 them which would \textcolor{red}{disqualify} them. Getting a \textcolor{red}{vacancy} did not seem

 to be such a very easy matter, after all. However, when our turn

 came the little man was much more favourable to me than to any of

 the others, and he closed the door as we entered, so that he

 might have a private \textcolor{green}{word} with us.



 "'This is Mr. Jabez Wilson,' said my assistant, 'and he is

 willing to \textcolor{green}{fill} a \textcolor{red}{vacancy} in the \textcolor{green}{League.'}



 "'And he is admirably suited for it,' the other answered. 'He has

 every requirement. I cannot recall when I have seen anything so

 fine.' He took a step \textcolor{red}{backward,} cocked his head on one side, and

 gazed at my hair until I felt quite bashful. Then \textcolor{blue}{suddenly} he

 \textcolor{red}{plunged} \textcolor{green}{forward,} wrung my hand, and congratulated me warmly on my

 \textcolor{BurntOrange}{success.}



 "'It would be \textcolor{red}{injustice} to hesitate,' said he. 'You will,

 however, I am sure, \textcolor{red}{excuse} me for taking an \textcolor{green}{obvious} \textcolor{green}{precaution.'}

 With that he \textcolor{red}{seized} my hair in both his hands, and tugged until I

 \textcolor{BurntOrange}{yelled} with the \textcolor{red}{pain.} 'There is water in your eyes,' said he as

 he released me. 'I \textcolor{green}{perceive} that all is as it should be. But we

 have to be \textcolor{green}{careful,} for we have twice been \textcolor{red}{deceived} by wigs and

 once by paint. I could tell you \textcolor{green}{tales} of cobbler's wax which

 would \textcolor{red}{disgust} you with human nature.' He stepped over to the

 window and \textcolor{BurntOrange}{shouted} through it at the \textcolor{BurntOrange}{top} of his voice that the

 \textcolor{red}{vacancy} was \textcolor{green}{filled.} A \textcolor{red}{groan} of \textcolor{red}{disappointment} came up from below,

 and the folk all trooped away in different directions until there

 was not a red-head to be seen except my own and that of the

 manager.



 "'My name,' said he, 'is Mr. Duncan Ross, and I am myself one of

 the pensioners upon the fund left by our \textcolor{green}{noble} \textcolor{green}{benefactor.} Are

 you a married man, Mr. Wilson? Have you a family?'



 "I answered that I had not.



 "His face \textcolor{red}{fell} \textcolor{BurntOrange}{immediately.}



 \textcolor{green}{"'Dear} me!' he said gravely, 'that is very serious indeed! I am

 sorry to hear you say that. The fund was, of course, for the

 propagation and spread of the red-heads as well as for their

 \textcolor{green}{maintenance.} It is exceedingly \textcolor{red}{unfortunate} that you should be a

 bachelor.'



 "My face lengthened at this, Mr. Holmes, for I \textcolor{blue}{thought} that I was

 not to have the \textcolor{red}{vacancy} after all; but after thinking it over for

 a few minutes he said that it would be all right.



 "'In the \textcolor{red}{case} of another,' said he, 'the \textcolor{red}{objection} might be

 \textcolor{red}{fatal,} but we must stretch a point in favour of a man with such a

 head of hair as yours. When shall you be able to enter upon your

 new duties?'



 "'Well, it is a little awkward, for I have a business already,'

 said I.



 "'Oh, never mind about that, Mr. Wilson!' said Vincent Spaulding.

 'I should be able to look after that for you.'



 "'What would be the hours?' I asked.



 "'Ten to two.'



 "Now a pawnbroker's business is mostly done of an evening, Mr.

 Holmes, especially Thursday and Friday evening, which is just

 before pay-day; so it would suit me very well to \textcolor{green}{earn} a little in

 the mornings. Besides, I knew that my assistant was a \textcolor{BurntOrange}{good} man,

 and that he would see to anything that turned up.



 "'That would suit me very well,' said I. 'And the \textcolor{BurntOrange}{pay?'}



 "'Is 4 \textcolor{red}{pounds} a week.'



 "'And the work?'



 "'Is \textcolor{green}{purely} nominal.'



 "'What do you call \textcolor{green}{purely} nominal?'



 "'Well, you have to be in the office, or at least in the

 \textcolor{green}{building,} the whole \textcolor{blue}{time.} If you \textcolor{BurntOrange}{leave,} you \textcolor{red}{forfeit} your whole

 position forever. The will is very clear upon that point. You

 don't comply with the conditions if you budge from the office

 during that \textcolor{blue}{time.'}



 "'It's only four hours a day, and I should not think of \textcolor{BurntOrange}{leaving,'}

 said I.



 "'No \textcolor{red}{excuse} will avail,' said Mr. Duncan Ross; 'neither \textcolor{red}{sickness}

 nor business nor anything else. There you must stay, or you \textcolor{BurntOrange}{lose}

 your billet.'



 "'And the work?'



 "'Is to \textcolor{red}{copy} out the "Encyclopaedia Britannica." There is the first

 volume of it in that press. You must find your own ink, pens, and

 blotting-paper, but we \textcolor{green}{provide} this table and chair. Will you be

 \textcolor{blue}{ready} \textcolor{blue}{to-morrow?'}



 "'Certainly,' I answered.



 "'Then, good-bye, Mr. Jabez Wilson, and let me congratulate you

 once more on the \textcolor{green}{important} position which you have been \textcolor{green}{fortunate}

 enough to \textcolor{BurntOrange}{gain.'} He bowed me out of the room and I went home with

 my assistant, hardly knowing what to say or do, I was so \textcolor{green}{pleased}

 at my own \textcolor{BurntOrange}{good} \textcolor{BurntOrange}{fortune.}



 "Well, I \textcolor{blue}{thought} over the matter all day, and by evening I was in

 low \textcolor{green}{spirits} again; for I had quite \textcolor{green}{persuaded} myself that the

 whole affair must be some great \textcolor{BurntOrange}{hoax} or \textcolor{red}{fraud,} though what its

 object might be I could not imagine. It seemed altogether past

 belief that anyone could make such a will, or that they would \textcolor{BurntOrange}{pay}

 such a sum for doing anything so simple as copying out the

 'Encyclopaedia Britannica.' Vincent Spaulding did what he could to

 \textcolor{BurntOrange}{cheer} me up, but by bedtime I had \textcolor{green}{reasoned} myself out of the

 whole thing. However, in the morning I determined to have a look

 at it anyhow, so I bought a penny bottle of ink, and with a

 quill-pen, and seven sheets of foolscap paper, I \textcolor{blue}{started} off for

 \textcolor{green}{Pope's} \textcolor{BurntOrange}{Court.}



 "Well, to my \textcolor{BurntOrange}{surprise} and \textcolor{BurntOrange}{delight,} everything was as right as

 possible. The table was set out \textcolor{blue}{ready} for me, and Mr. Duncan Ross

 was there to see that I got \textcolor{green}{fairly} to work. He \textcolor{blue}{started} me off

 upon the \textcolor{blue}{letter} A, and then he left me; but he would drop in from

 \textcolor{blue}{time} to \textcolor{blue}{time} to see that all was right with me. At two o'clock he

 bade me good-day, \textcolor{BurntOrange}{complimented} me upon the amount that I had

 written, and locked the door of the office after me.



 "This went on day after day, Mr. Holmes, and on Saturday the

 manager came in and planked down four golden \textcolor{green}{sovereigns} for my

 week's work. It was the same next week, and the same the week

 after. Every morning I was there at ten, and every afternoon I

 left at two. By \textcolor{green}{degrees} Mr. Duncan Ross took to coming in only

 once of a morning, and then, after a \textcolor{blue}{time,} he did not come in at

 all. Still, of course, I never \textcolor{BurntOrange}{dared} to \textcolor{BurntOrange}{leave} the room for an

 instant, for I was not sure when he might come, and the billet

 was such a \textcolor{BurntOrange}{good} one, and suited me so well, that I would not \textcolor{BurntOrange}{risk}

 the \textcolor{red}{loss} of it.



 "Eight weeks passed away like this, and I had written about

 \textcolor{green}{Abbots} and Archery and Armour and \textcolor{green}{Architecture} and Attica, and

 hoped with \textcolor{green}{diligence} that I might get on to the B's before very

 \textcolor{blue}{long.} It cost me something in foolscap, and I had \textcolor{BurntOrange}{pretty} nearly

 \textcolor{green}{filled} a shelf with my writings. And then \textcolor{blue}{suddenly} the whole

 business came to an end."



 "To an end?"



 "Yes, \textcolor{green}{sir.} And no later than this morning. I went to my work as

 \textcolor{green}{usual} at ten o'clock, but the door was shut and locked, with a

 little square of cardboard hammered on to the middle of the

 panel with a tack. Here it is, and you can read for yourself."



 He held up a piece of \textcolor{BurntOrange}{white} cardboard about the size of a sheet

 of note-paper. It read in this fashion:



 THE RED-HEADED \textcolor{green}{LEAGUE}



 IS



 DISSOLVED.



 October 9, 1890.



 Sherlock Holmes and I surveyed this curt \textcolor{blue}{announcement} and the

 rueful face behind it, until the comical side of the affair so

 \textcolor{green}{completely} overtopped every other consideration that we both

 burst out into a roar of \textcolor{BurntOrange}{laughter.}



 "I cannot see that there is anything very funny," \textcolor{red}{cried} our

 client, \textcolor{green}{flushing} up to the roots of his flaming head. "If you can

 do nothing better than \textcolor{BurntOrange}{laugh} at me, I can go elsewhere."



 "No, no," \textcolor{red}{cried} Holmes, \textcolor{red}{shoving} him back into the chair from

 which he had half risen. "I really wouldn't miss your \textcolor{red}{case} for

 the world. It is most refreshingly unusual. But there is, if you

 will \textcolor{red}{excuse} my saying so, something just a little funny about it.

 \textcolor{BurntOrange}{Pray} what steps did you take when you \textcolor{green}{found} the card upon the

 door?"



 "I was \textcolor{blue}{staggered,} \textcolor{green}{sir.} I did not know what to do. Then I called

 at the offices round, but none of them seemed to know anything

 about it. \textcolor{BurntOrange}{Finally,} I went to the landlord, who is an \textcolor{green}{accountant}

 living on the ground-floor, and I asked him if he could tell me

 what had become of the Red-headed \textcolor{green}{League.} He said that he had

 never heard of any such body. Then I asked him who Mr. Duncan

 Ross was. He answered that the name was new to him.



 "'Well,' said I, 'the \textcolor{green}{gentleman} at No. 4.'



 "'What, the red-headed man?'



 "'Yes.'



 "'Oh,' said he, 'his name was William Morris. He was a solicitor

 and was using my room as a temporary \textcolor{green}{convenience} until his new

 premises were \textcolor{blue}{ready.} He moved out yesterday.'



 "'Where could I find him?'



 "'Oh, at his new offices. He did tell me the address. Yes, 17

 \textcolor{green}{King} Edward Street, near St. Paul's.'



 "I \textcolor{blue}{started} off, Mr. Holmes, but when I got to that address it was

 a manufactory of artificial knee-caps, and no one in it had ever

 heard of either Mr. William Morris or Mr. Duncan Ross."



 "And what did you do then?" asked Holmes.



 "I went home to Saxe-Coburg Square, and I took the \textcolor{green}{advice} of my

 assistant. But he could not help me in any way. He could only say

 that if I \textcolor{BurntOrange}{waited} I should hear by post. But that was not quite

 \textcolor{BurntOrange}{good} enough, Mr. Holmes. I did not wish to \textcolor{BurntOrange}{lose} such a place

 without a \textcolor{red}{struggle,} so, as I had heard that you were \textcolor{BurntOrange}{good} enough

 to give \textcolor{green}{advice} to poor folk who were in need of it, I came right

 away to you."



 "And you did very wisely," said Holmes. "Your \textcolor{red}{case} is an

 exceedingly \textcolor{BurntOrange}{remarkable} one, and I shall be \textcolor{BurntOrange}{happy} to look into it.

 From what you have told me I think that it is possible that

 graver issues hang from it than might at first sight appear."



 \textcolor{red}{"Grave} enough!" said Mr. Jabez Wilson. "Why, I have \textcolor{BurntOrange}{lost} four

 \textcolor{red}{pound} a week."



 "As far as you are personally \textcolor{red}{concerned,"} remarked Holmes, "I do

 not see that you have any \textcolor{red}{grievance} against this \textcolor{green}{extraordinary}

 \textcolor{green}{league.} On the \textcolor{red}{contrary,} you are, as I understand, richer by some

 30 \textcolor{red}{pounds,} to say nothing of the minute \textcolor{green}{knowledge} which you have

 \textcolor{BurntOrange}{gained} on every \textcolor{red}{subject} which comes under the \textcolor{blue}{letter} A. You have

 \textcolor{BurntOrange}{lost} nothing by them."



 "No, \textcolor{green}{sir.} But I want to find out about them, and who they are,

 and what their object was in playing this prank--if it was a

 prank--upon me. It was a \textcolor{BurntOrange}{pretty} expensive \textcolor{red}{joke} for them, for it

 cost them two and thirty \textcolor{red}{pounds."}



 "We shall endeavour to clear up these points for you. And, first,

 one or two \textcolor{green}{questions,} Mr. Wilson. This assistant of yours who

 first called your \textcolor{green}{attention} to the advertisement--how \textcolor{blue}{long} had he

 been with you?"



 "About a month then."



 "How did he come?"



 "In answer to an advertisement."



 "Was he the only \textcolor{blue}{applicant?"}



 "No, I had a dozen."



 "Why did you \textcolor{green}{pick} him?"



 "Because he was \textcolor{green}{handy} and would come \textcolor{red}{cheap."}



 "At half-wages, in \textcolor{green}{fact."}



 "Yes."



 "What is he like, this Vincent Spaulding?"



 \textcolor{red}{"Small,} stout-built, very quick in his ways, no hair on his face,

 though he's not short of thirty. Has a \textcolor{BurntOrange}{white} \textcolor{blue}{splash} of \textcolor{red}{acid} upon

 his forehead."



 Holmes sat up in his chair in \textcolor{green}{considerable} \textcolor{BurntOrange}{excitement.} "I \textcolor{blue}{thought}

 as much," said he. "Have you ever observed that his ears are

 pierced for earrings?"



 "Yes, \textcolor{green}{sir.} He told me that a gipsy had done it for him when he

 was a lad."



 "Hum!" said Holmes, sinking back in deep \textcolor{blue}{thought.} "He is still

 with you?"



 "Oh, yes, \textcolor{green}{sir;} I have only just left him."



 "And has your business been attended to in your \textcolor{red}{absence?"}



 "Nothing to \textcolor{red}{complain} of, \textcolor{green}{sir.} There's never very much to do of a

 morning."



 "That will do, Mr. Wilson. I shall be \textcolor{BurntOrange}{happy} to give you an

 opinion upon the \textcolor{red}{subject} in the course of a day or two. To-day is

 Saturday, and I \textcolor{BurntOrange}{hope} that by Monday we may come to a conclusion."



 "Well, Watson," said Holmes when our \textcolor{BurntOrange}{visitor} had left us, "what

 do you make of it all?"



 "I make nothing of it," I answered frankly. "It is a most

 \textcolor{BurntOrange}{mysterious} business."



 "As a \textcolor{BurntOrange}{rule,"} said Holmes, "the more \textcolor{BurntOrange}{bizarre} a thing is the less

 \textcolor{BurntOrange}{mysterious} it proves to be. It is your \textcolor{BurntOrange}{commonplace,} featureless

 \textcolor{red}{crimes} which are really puzzling, just as a \textcolor{BurntOrange}{commonplace} face is

 the most \textcolor{red}{difficult} to identify. But I must be prompt over this

 matter."



 "What are you going to do, then?" I asked.



 "To smoke," he answered. "It is quite a three pipe \textcolor{red}{problem,} and I

 \textcolor{red}{beg} that you \textcolor{blue}{won't} speak to me for fifty minutes." He \textcolor{green}{curled}

 himself up in his chair, with his thin knees drawn up to his

 hawk-like \textcolor{red}{nose,} and there he sat with his eyes closed and his

 \textcolor{red}{black} clay pipe thrusting out like the bill of some strange bird.

 I had come to the conclusion that he had dropped asleep, and

 indeed was nodding myself, when he \textcolor{blue}{suddenly} sprang out of his

 chair with the gesture of a man who has made up his mind and put

 his pipe down upon the mantelpiece.



 "Sarasate plays at the St. James's Hall this afternoon," he

 remarked. "What do you think, Watson? Could your \textcolor{BurntOrange}{patients} spare

 you for a few hours?"



 "I have nothing to do to-day. My \textcolor{green}{practice} is never very

 absorbing."



 "Then put on your hat and come. I am going through the City

 first, and we can have some lunch on the way. I observe that

 there is a \textcolor{BurntOrange}{good} \textcolor{BurntOrange}{deal} of German \textcolor{BurntOrange}{music} on the programme, which is

 rather more to my taste than Italian or French. It is

 introspective, and I want to introspect. Come along!"



 We travelled by the Underground as far as Aldersgate; and a short

 walk took us to Saxe-Coburg Square, the scene of the singular

 story which we had listened to in the morning. It was a poky,

 little, shabby-genteel place, where four lines of dingy

 two-storied brick houses looked out into a \textcolor{red}{small} railed-in

 enclosure, where a lawn of weedy grass and a few \textcolor{red}{clumps} of \textcolor{red}{faded}

 laurel-bushes made a hard \textcolor{red}{fight} against a smoke-laden and

 uncongenial atmosphere. Three gilt balls and a brown \textcolor{blue}{board} with

 "JABEZ WILSON" in \textcolor{BurntOrange}{white} \textcolor{blue}{letters,} upon a corner house, announced

 the place where our red-headed client carried on his business.

 Sherlock Holmes stopped in front of it with his head on one side

 and looked it all over, with his eyes shining brightly between

 puckered lids. Then he walked slowly up the street, and then down

 again to the corner, still looking keenly at the houses. \textcolor{BurntOrange}{Finally}

 he returned to the pawnbroker's, and, having thumped vigorously

 upon the \textcolor{green}{pavement} with his stick two or three \textcolor{blue}{times,} he went up

 to the door and knocked. It was instantly opened by a

 bright-looking, clean-shaven \textcolor{BurntOrange}{young} \textcolor{green}{fellow,} who asked him to step

 in.



 "Thank you," said Holmes, "I only wished to ask you how you would

 go from here to the Strand."



 "Third right, fourth left," answered the assistant promptly,

 closing the door.



 "Smart \textcolor{green}{fellow,} that," observed Holmes as we walked away. "He is,

 in my \textcolor{blue}{judgment,} the fourth smartest man in London, and for \textcolor{BurntOrange}{daring}

 I am not sure that he has not a claim to be third. I have known

 something of him before."



 "Evidently," said I, "Mr. Wilson's assistant \textcolor{green}{counts} for a \textcolor{BurntOrange}{good}

 \textcolor{BurntOrange}{deal} in this \textcolor{blue}{mystery} of the Red-headed \textcolor{green}{League.} I am sure that you

 inquired your way merely in order that you might see him."



 "Not him."



 "What then?"



 "The knees of his trousers."



 "And what did you see?"



 "What I \textcolor{BurntOrange}{expected} to see."



 "Why did you beat the \textcolor{green}{pavement?"}



 "My \textcolor{green}{dear} \textcolor{green}{doctor,} this is a \textcolor{blue}{time} for observation, not for \textcolor{green}{talk.} We

 are spies in an \textcolor{red}{enemy's} country. We know something of Saxe-Coburg

 Square. Let us now \textcolor{blue}{explore} the parts which \textcolor{red}{lie} behind it."



 The road in which we \textcolor{green}{found} ourselves as we turned round the

 corner from the retired Saxe-Coburg Square \textcolor{BurntOrange}{presented} as great a

 contrast to it as the front of a picture does to the back. It was

 one of the \textcolor{green}{main} arteries which conveyed the traffic of the City

 to the north and west. The roadway was blocked with the \textcolor{green}{immense}

 stream of \textcolor{green}{commerce} \textcolor{green}{flowing} in a double tide inward and \textcolor{green}{outward,}

 while the footpaths were \textcolor{red}{black} with the \textcolor{blue}{hurrying} \textcolor{red}{swarm} of

 \textcolor{red}{pedestrians.} It was \textcolor{red}{difficult} to realise as we looked at the line

 of fine shops and \textcolor{green}{stately} business premises that they really

 abutted on the other side upon the \textcolor{red}{faded} and \textcolor{red}{stagnant} square

 which we had just \textcolor{red}{quitted.}



 "Let me see," said Holmes, standing at the corner and glancing

 along the line, "I should like just to remember the order of the

 houses here. It is a \textcolor{green}{hobby} of mine to have an exact \textcolor{green}{knowledge} of

 London. There is Mortimer's, the tobacconist, the little

 newspaper shop, the Coburg branch of the City and Suburban \textcolor{green}{Bank,}

 the Vegetarian Restaurant, and McFarlane's carriage-building

 depot. That carries us right on to the other block. And now,

 \textcolor{green}{Doctor,} we've done our work, so it's \textcolor{blue}{time} we had some play. A

 sandwich and a cup of coffee, and then off to violin-land, where

 all is \textcolor{green}{sweetness} and delicacy and \textcolor{green}{harmony,} and there are no

 red-headed clients to vex us with their conundrums."



 My \textcolor{green}{friend} was an enthusiastic musician, being himself not only a

 very capable \textcolor{green}{performer} but a \textcolor{green}{composer} of no ordinary \textcolor{green}{merit.} All

 the afternoon he sat in the \textcolor{red}{stalls} wrapped in the most \textcolor{BurntOrange}{perfect}

 \textcolor{BurntOrange}{happiness,} gently waving his \textcolor{blue}{long,} thin fingers in \textcolor{blue}{time} to the

 \textcolor{BurntOrange}{music,} while his gently \textcolor{BurntOrange}{smiling} face and his \textcolor{red}{languid,} dreamy eyes

 were as unlike those of Holmes the sleuth-hound, Holmes the

 relentless, keen-witted, ready-handed \textcolor{red}{criminal} agent, as it was

 possible to conceive. In his singular character the dual nature

 alternately asserted itself, and his extreme exactness and

 astuteness represented, as I have often \textcolor{blue}{thought,} the reaction

 against the poetic and contemplative mood which occasionally

 predominated in him. The swing of his nature took him from

 extreme languor to \textcolor{red}{devouring} energy; and, as I knew well, he was

 never so truly \textcolor{red}{formidable} as when, for days on end, he had been

 \textcolor{red}{lounging} in his armchair amid his \textcolor{blue}{improvisations} and his

 black-letter \textcolor{blue}{editions.} Then it was that the \textcolor{BurntOrange}{lust} of the \textcolor{red}{chase}

 would \textcolor{blue}{suddenly} come upon him, and that his \textcolor{BurntOrange}{brilliant} \textcolor{green}{reasoning}

 power would rise to the \textcolor{green}{level} of \textcolor{green}{intuition,} until those who were

 unacquainted with his methods would look askance at him as on a

 man whose \textcolor{green}{knowledge} was not that of other \textcolor{red}{mortals.} When I saw him

 that afternoon so enwrapped in the \textcolor{BurntOrange}{music} at St. James's Hall I

 felt that an \textcolor{red}{evil} \textcolor{blue}{time} might be coming upon those whom he had set

 himself to hunt down.



 "You want to go home, no \textcolor{BurntOrange}{doubt,} \textcolor{green}{Doctor,"} he remarked as we

 emerged.



 "Yes, it would be as well."



 "And I have some business to do which will take some hours. This

 business at Coburg Square is serious."



 "Why serious?"



 "A \textcolor{green}{considerable} \textcolor{red}{crime} is in \textcolor{green}{contemplation.} I have every \textcolor{green}{reason} to

 believe that we shall be in \textcolor{blue}{time} to stop it. But to-day being

 Saturday rather complicates matters. I shall want your help

 to-night."



 "At what \textcolor{blue}{time?"}



 "Ten will be early enough."



 "I shall be at Baker Street at ten."



 "Very well. And, I say, \textcolor{green}{Doctor,} there may be some little \textcolor{red}{danger,}

 so kindly put your army \textcolor{red}{revolver} in your pocket." He waved his

 hand, turned on his \textcolor{red}{heel,} and \textcolor{red}{disappeared} in an instant among the

 crowd.



 I \textcolor{green}{trust} that I am not more dense than my neighbours, but I was

 always \textcolor{red}{oppressed} with a \textcolor{green}{sense} of my own \textcolor{red}{stupidity} in my dealings

 with Sherlock Holmes. Here I had heard what he had heard, I had

 seen what he had seen, and yet from his \textcolor{green}{words} it was \textcolor{green}{evident} that

 he saw clearly not only what had \textcolor{blue}{happened} but what was about to

 \textcolor{blue}{happen,} while to me the whole business was still \textcolor{red}{confused} and

 \textcolor{red}{grotesque.} As I drove home to my house in Kensington I \textcolor{blue}{thought}

 over it all, from the \textcolor{green}{extraordinary} story of the red-headed

 copier of the "Encyclopaedia" down to the \textcolor{green}{visit} to Saxe-Coburg

 Square, and the \textcolor{BurntOrange}{ominous} \textcolor{green}{words} with which he had parted from me.

 What was this nocturnal \textcolor{BurntOrange}{expedition,} and why should I go armed?

 Where were we going, and what were we to do? I had the hint from

 Holmes that this smooth-faced pawnbroker's assistant was a

 \textcolor{red}{formidable} man--a man who might play a deep game. I tried to

 puzzle it out, but gave it up in \textcolor{red}{despair} and set the matter aside

 until night should bring an explanation.



 It was a quarter-past nine when I \textcolor{blue}{started} from home and made my

 way across the Park, and so through Oxford Street to Baker

 Street. Two hansoms were standing at the door, and as I entered

 the passage I heard the sound of voices from above. On entering

 his room I \textcolor{green}{found} Holmes in \textcolor{green}{animated} conversation with two men,

 one of whom I recognised as Peter Jones, the \textcolor{green}{official} \textcolor{BurntOrange}{police}

 agent, while the other was a \textcolor{blue}{long,} thin, sad-faced man, with a

 very shiny hat and oppressively \textcolor{green}{respectable} frock-coat.



 "Ha! Our party is complete," said Holmes, buttoning up his

 pea-jacket and taking his heavy hunting crop from the \textcolor{red}{rack.}

 "Watson, I think you know Mr. Jones, of Scotland Yard? Let me

 introduce you to Mr. Merryweather, who is to be our \textcolor{green}{companion} in

 to-night's \textcolor{BurntOrange}{adventure."}



 "We're hunting in couples again, \textcolor{green}{Doctor,} you see," said Jones in

 his consequential way. "Our \textcolor{green}{friend} here is a \textcolor{BurntOrange}{wonderful} man for

 \textcolor{blue}{starting} a \textcolor{red}{chase.} All he wants is an old dog to help him to do

 the running down."



 "I \textcolor{BurntOrange}{hope} a \textcolor{BurntOrange}{wild} goose may not \textcolor{green}{prove} to be the end of our \textcolor{red}{chase,"}

 observed Mr. Merryweather gloomily.



 "You may place \textcolor{green}{considerable} \textcolor{BurntOrange}{confidence} in Mr. Holmes, \textcolor{green}{sir,"} said

 the \textcolor{BurntOrange}{police} agent loftily. "He has his own little methods, which

 are, if he \textcolor{blue}{won't} mind my saying so, just a little too \textcolor{green}{theoretical}

 and fantastic, but he has the makings of a detective in him. It

 is not too much to say that once or twice, as in that business of

 the Sholto \textcolor{BurntOrange}{murder} and the Agra \textcolor{BurntOrange}{treasure,} he has been more nearly

 correct than the \textcolor{green}{official} \textcolor{red}{force."}



 "Oh, if you say so, Mr. Jones, it is all right," said the

 \textcolor{red}{stranger} with \textcolor{green}{deference.} "Still, I \textcolor{BurntOrange}{confess} that I miss my rubber.

 It is the first Saturday night for seven-and-twenty years that I

 have not had my rubber."



 "I think you will find," said Sherlock Holmes, "that you will

 play for a higher stake to-night than you have ever done yet, and

 that the play will be more \textcolor{BurntOrange}{exciting.} For you, Mr. Merryweather,

 the stake will be some 30,000 \textcolor{red}{pounds;} and for you, Jones, it will

 be the man upon whom you wish to lay your hands."



 \textcolor{red}{"John} Clay, the \textcolor{red}{murderer,} \textcolor{BurntOrange}{thief,} smasher, and forger. He's a

 \textcolor{BurntOrange}{young} man, Mr. Merryweather, but he is at the head of his

 \textcolor{green}{profession,} and I would rather have my bracelets on him than on

 any \textcolor{red}{criminal} in London. He's a \textcolor{BurntOrange}{remarkable} man, is \textcolor{BurntOrange}{young} \textcolor{red}{John}

 Clay. His \textcolor{green}{grandfather} was a royal \textcolor{green}{duke,} and he himself has been

 to Eton and Oxford. His brain is as \textcolor{BurntOrange}{cunning} as his fingers, and

 though we meet signs of him at every turn, we never know where to

 find the man himself. \textcolor{red}{He'll} \textcolor{red}{crack} a crib in Scotland one week,

 and be raising \textcolor{BurntOrange}{money} to \textcolor{green}{build} an orphanage in Cornwall the next.

 I've been on his \textcolor{blue}{track} for years and have never set eyes on him

 yet."



 "I \textcolor{BurntOrange}{hope} that I may have the pleasure of introducing you to-night.

 I've had one or two little turns also with Mr. \textcolor{red}{John} Clay, and I

 \textcolor{green}{agree} with you that he is at the head of his \textcolor{green}{profession.} It is

 past ten, however, and quite \textcolor{blue}{time} that we \textcolor{blue}{started.} If you two

 will take the first hansom, Watson and I will follow in the

 second."



 Sherlock Holmes was not very \textcolor{green}{communicative} during the \textcolor{blue}{long} drive

 and lay back in the \textcolor{green}{cab} humming the tunes which he had heard in

 the afternoon. We rattled through an \textcolor{BurntOrange}{endless} \textcolor{BurntOrange}{labyrinth} of gas-lit

 streets until we emerged into Farrington Street.



 "We are close there now," my \textcolor{green}{friend} remarked. "This \textcolor{green}{fellow}

 Merryweather is a \textcolor{green}{bank} \textcolor{green}{director,} and personally \textcolor{BurntOrange}{interested} in the

 matter. I \textcolor{blue}{thought} it as well to have Jones with us also. He is

 not a \textcolor{red}{bad} \textcolor{green}{fellow,} though an \textcolor{green}{absolute} imbecile in his \textcolor{green}{profession.}

 He has one positive \textcolor{green}{virtue.} He is as brave as a \textcolor{green}{bulldog} and as

 \textcolor{green}{tenacious} as a lobster if he gets his \textcolor{red}{claws} upon anyone. Here we

 are, and they are \textcolor{BurntOrange}{waiting} for us."



 We had reached the same crowded thoroughfare in which we had

 \textcolor{green}{found} ourselves in the morning. Our \textcolor{green}{cabs} were dismissed, and,

 following the \textcolor{green}{guidance} of Mr. Merryweather, we passed down a

 narrow passage and through a side door, which he opened for us.

 Within there was a \textcolor{red}{small} corridor, which ended in a very massive

 \textcolor{green}{iron} \textcolor{green}{gate.} This also was opened, and \textcolor{green}{led} down a flight of winding

 \textcolor{red}{stone} steps, which \textcolor{red}{terminated} at another \textcolor{red}{formidable} \textcolor{green}{gate.} Mr.

 Merryweather stopped to light a lantern, and then conducted us

 down a \textcolor{red}{dark,} earth-smelling passage, and so, after opening a

 third door, into a huge vault or cellar, which was piled all

 round with crates and massive boxes.



 "You are not very vulnerable from above," Holmes remarked as he

 held up the lantern and gazed about him.



 "Nor from below," said Mr. Merryweather, \textcolor{red}{striking} his stick upon

 the flags which lined the floor. "Why, \textcolor{green}{dear} me, it sounds quite

 \textcolor{red}{hollow!"} he remarked, looking up in \textcolor{BurntOrange}{surprise.}



 "I must really ask you to be a little more \textcolor{BurntOrange}{quiet!"} said Holmes

 severely. "You have already imperilled the whole \textcolor{BurntOrange}{success} of our

 \textcolor{BurntOrange}{expedition.} Might I \textcolor{red}{beg} that you would have the \textcolor{BurntOrange}{goodness} to sit

 down upon one of those boxes, and not to interfere?"



 The solemn Mr. Merryweather perched himself upon a crate, with a

 very \textcolor{red}{injured} expression upon his face, while Holmes \textcolor{red}{fell} upon his

 knees upon the floor and, with the lantern and a magnifying lens,

 began to examine minutely the \textcolor{red}{cracks} between the \textcolor{red}{stones.} A few

 seconds sufficed to satisfy him, for he sprang to his feet again

 and put his glass in his pocket.



 "We have at least an hour before us," he remarked, "for they can

 hardly take any steps until the \textcolor{BurntOrange}{good} pawnbroker is safely in bed.

 Then they will not \textcolor{BurntOrange}{lose} a minute, for the sooner they do their

 work the longer \textcolor{blue}{time} they will have for their \textcolor{BurntOrange}{escape.} We are at

 \textcolor{BurntOrange}{present,} Doctor--as no \textcolor{BurntOrange}{doubt} you have divined--in the cellar of

 the City branch of one of the \textcolor{green}{principal} London \textcolor{green}{banks.} Mr.

 Merryweather is the \textcolor{green}{chairman} of \textcolor{green}{directors,} and he will \textcolor{green}{explain} to

 you that there are \textcolor{green}{reasons} why the more \textcolor{BurntOrange}{daring} \textcolor{red}{criminals} of

 London should take a \textcolor{green}{considerable} \textcolor{green}{interest} in this cellar at

 \textcolor{BurntOrange}{present."}



 "It is our French \textcolor{green}{gold,"} whispered the \textcolor{green}{director.} "We have had

 several \textcolor{red}{warnings} that an \textcolor{blue}{attempt} might be made upon it."



 "Your French \textcolor{green}{gold?"}



 "Yes. We had occasion some months ago to \textcolor{green}{strengthen} our resources

 and borrowed for that purpose 30,000 napoleons from the \textcolor{green}{Bank} of

 France. It has become known that we have never had occasion to

 unpack the \textcolor{BurntOrange}{money,} and that it is still \textcolor{red}{lying} in our cellar. The

 crate upon which I sit contains 2,000 napoleons packed between

 layers of \textcolor{green}{lead} foil. Our \textcolor{green}{reserve} of bullion is much larger at

 \textcolor{BurntOrange}{present} than is usually kept in a single branch office, and the

 \textcolor{green}{directors} have had misgivings upon the \textcolor{red}{subject."}



 "Which were very well justified," observed Holmes. "And now it is

 \textcolor{blue}{time} that we arranged our little \textcolor{blue}{plans.} I \textcolor{BurntOrange}{expect} that within an

 hour matters will come to a head. In the meantime Mr.

 Merryweather, we must put the screen over that \textcolor{red}{dark} lantern."



 "And sit in the \textcolor{red}{dark?"}



 "I am \textcolor{red}{afraid} so. I had brought a pack of cards in my pocket, and

 I \textcolor{blue}{thought} that, as we were a partie carrée, you might have your

 rubber after all. But I see that the \textcolor{red}{enemy's} \textcolor{blue}{preparations} have

 gone so far that we cannot \textcolor{BurntOrange}{risk} the \textcolor{green}{presence} of a light. And,

 first of all, we must choose our positions. These are \textcolor{BurntOrange}{daring} men,

 and though we shall take them at a disadvantage, they may do us

 some \textcolor{red}{harm} unless we are \textcolor{green}{careful.} I shall stand behind this crate,

 and do you \textcolor{red}{conceal} yourselves behind those. Then, when I flash a

 light upon them, close in swiftly. If they \textcolor{red}{fire,} Watson, have no

 compunction about \textcolor{red}{shooting} them down."



 I placed my \textcolor{red}{revolver,} cocked, upon the \textcolor{BurntOrange}{top} of the wooden \textcolor{red}{case}

 behind which I \textcolor{red}{crouched.} Holmes \textcolor{BurntOrange}{shot} the slide across the front

 of his lantern and left us in pitch darkness--such an \textcolor{green}{absolute}

 \textcolor{red}{darkness} as I have never before \textcolor{green}{experienced.} The \textcolor{red}{smell} of \textcolor{red}{hot}

 metal remained to \textcolor{green}{assure} us that the light was still there, \textcolor{blue}{ready}

 to flash out at a moment's notice. To me, with my \textcolor{green}{nerves} worked

 up to a pitch of \textcolor{blue}{expectancy,} there was something \textcolor{red}{depressing} and

 \textcolor{red}{subduing} in the \textcolor{blue}{sudden} \textcolor{red}{gloom,} and in the \textcolor{red}{cold} \textcolor{red}{dank} air of the

 vault.



 "They have but one retreat," whispered Holmes. "That is back

 through the house into Saxe-Coburg Square. I \textcolor{BurntOrange}{hope} that you have

 done what I asked you, Jones?"



 "I have an \textcolor{green}{inspector} and two \textcolor{green}{officers} \textcolor{BurntOrange}{waiting} at the front door."



 "Then we have stopped all the holes. And now we must be silent

 and \textcolor{BurntOrange}{wait."}



 What a \textcolor{blue}{time} it seemed! From comparing notes afterwards it was but

 an hour and a quarter, yet it appeared to me that the night must

 have almost gone and the \textcolor{BurntOrange}{dawn} be \textcolor{blue}{breaking} above us. My limbs

 were \textcolor{red}{weary} and \textcolor{red}{stiff,} for I \textcolor{red}{feared} to \textcolor{red}{change} my position; yet my

 \textcolor{green}{nerves} were worked up to the highest pitch of \textcolor{red}{tension,} and my

 \textcolor{red}{hearing} was so acute that I could not only hear the gentle

 breathing of my \textcolor{green}{companions,} but I could distinguish the deeper,

 heavier in-breath of the bulky Jones from the thin, sighing note

 of the \textcolor{green}{bank} \textcolor{green}{director.} From my position I could look over the \textcolor{red}{case}

 in the direction of the floor. \textcolor{blue}{Suddenly} my eyes caught the glint

 of a light.



 At first it was but a \textcolor{red}{lurid} spark upon the \textcolor{red}{stone} \textcolor{green}{pavement.} Then

 it lengthened out until it became a yellow line, and then,

 without any \textcolor{BurntOrange}{warning} or sound, a \textcolor{red}{gash} seemed to open and a hand

 appeared, a \textcolor{BurntOrange}{white,} almost womanly hand, which felt about in the

 centre of the little area of light. For a minute or more the

 hand, with its writhing fingers, protruded out of the floor. Then

 it was withdrawn as \textcolor{blue}{suddenly} as it appeared, and all was \textcolor{red}{dark}

 again \textcolor{green}{save} the single \textcolor{red}{lurid} spark which \textcolor{green}{marked} a chink between

 the \textcolor{red}{stones.}



 Its disappearance, however, was but momentary. With a \textcolor{red}{rending,}

 tearing sound, one of the broad, \textcolor{BurntOrange}{white} \textcolor{red}{stones} turned over upon

 its side and left a square, \textcolor{red}{gaping} hole, through which streamed

 the light of a lantern. Over the edge there peeped a clean-cut,

 boyish face, which looked keenly about it, and then, with a hand

 on either side of the aperture, drew itself shoulder-high and

 waist-high, until one knee \textcolor{green}{rested} upon the edge. In another

 instant he stood at the side of the hole and was hauling after

 him a \textcolor{green}{companion,} \textcolor{green}{lithe} and \textcolor{red}{small} like himself, with a pale face

 and a \textcolor{BurntOrange}{shock} of very red hair.



 "It's all clear," he whispered. "Have you the \textcolor{green}{chisel} and the

 bags? Great Scott! \textcolor{green}{Jump,} Archie, \textcolor{green}{jump,} and \textcolor{red}{I'll} swing for it!"



 Sherlock Holmes had sprung out and \textcolor{red}{seized} the \textcolor{BurntOrange}{intruder} by the

 collar. The other dived down the hole, and I heard the sound of

 \textcolor{red}{rending} cloth as Jones clutched at his skirts. The light flashed

 upon the barrel of a \textcolor{red}{revolver,} but Holmes' hunting crop came

 down on the man's wrist, and the \textcolor{red}{pistol} clinked upon the \textcolor{red}{stone}

 floor.



 "It's no use, \textcolor{red}{John} Clay," said Holmes blandly. "You have no

 \textcolor{blue}{chance} at all."



 "So I see," the other answered with the utmost \textcolor{green}{coolness.} "I \textcolor{BurntOrange}{fancy}

 that my pal is all right, though I see you have got his

 coat-tails."



 "There are three men \textcolor{BurntOrange}{waiting} for him at the door," said Holmes.



 "Oh, indeed! You seem to have done the thing very \textcolor{green}{completely.} I

 must \textcolor{BurntOrange}{compliment} you."



 "And I you," Holmes answered. "Your red-headed idea was very new

 and \textcolor{green}{effective."}



 "You'll see your pal again presently," said Jones. "He's quicker

 at climbing down holes than I am. Just hold out while I fix the

 derbies."



 "I \textcolor{red}{beg} that you will not touch me with your \textcolor{red}{filthy} hands,"

 remarked our \textcolor{red}{prisoner} as the handcuffs clattered upon his wrists.

 "You may not be aware that I have royal blood in my veins. Have

 the \textcolor{BurntOrange}{goodness,} also, when you address me always to say \textcolor{green}{'sir'} and

 'please.'"



 "All right," said Jones with a stare and a snigger. "Well, would

 you please, \textcolor{green}{sir,} \textcolor{green}{march} upstairs, where we can get a \textcolor{green}{cab} to carry

 your Highness to the police-station?"



 "That is better," said \textcolor{red}{John} Clay serenely. He made a sweeping bow

 to the three of us and walked quietly off in the \textcolor{green}{custody} of the

 detective.



 "Really, Mr. Holmes," said Mr. Merryweather as we followed them

 from the cellar, "I do not know how the \textcolor{green}{bank} can thank you or

 \textcolor{BurntOrange}{repay} you. There is no \textcolor{BurntOrange}{doubt} that you have \textcolor{green}{detected} and \textcolor{red}{defeated}

 in the most complete manner one of the most determined \textcolor{blue}{attempts}

 at \textcolor{green}{bank} \textcolor{red}{robbery} that have ever come within my experience."



 "I have had one or two little \textcolor{BurntOrange}{scores} of my own to settle with Mr.

 \textcolor{red}{John} Clay," said Holmes. "I have been at some \textcolor{red}{small} expense over

 this matter, which I shall \textcolor{BurntOrange}{expect} the \textcolor{green}{bank} to refund, but beyond

 that I am amply repaid by having had an experience which is in

 many ways \textcolor{BurntOrange}{unique,} and by \textcolor{red}{hearing} the very \textcolor{BurntOrange}{remarkable} narrative of

 the Red-headed \textcolor{green}{League."}





 "You see, Watson," he \textcolor{green}{explained} in the early hours of the morning

 as we sat over a glass of \textcolor{red}{whisky} and soda in Baker Street, "it

 was perfectly \textcolor{green}{obvious} from the first that the only possible

 object of this rather fantastic business of the advertisement of

 the \textcolor{green}{League,} and the copying of the 'Encyclopaedia,' must be to get

 this not over-bright pawnbroker out of the way for a number of

 hours every day. It was a curious way of \textcolor{green}{managing} it, but,

 really, it would be \textcolor{red}{difficult} to \textcolor{green}{suggest} a better. The method was

 no \textcolor{BurntOrange}{doubt} \textcolor{green}{suggested} to Clay's \textcolor{green}{ingenious} mind by the colour of his

 accomplice's hair. The 4 \textcolor{red}{pounds} a week was a \textcolor{red}{lure} which must draw

 him, and what was it to them, who were playing for thousands?

 They put in the advertisement, one \textcolor{red}{rogue} has the temporary

 office, the other \textcolor{red}{rogue} incites the man to apply for it, and

 together they \textcolor{green}{manage} to secure his \textcolor{red}{absence} every morning in the

 week. From the \textcolor{blue}{time} that I heard of the assistant having come for

 half wages, it was \textcolor{green}{obvious} to me that he had some strong \textcolor{green}{motive}

 for securing the situation."



 "But how could you \textcolor{blue}{guess} what the \textcolor{green}{motive} was?"



 "Had there been women in the house, I should have \textcolor{red}{suspected} a

 mere \textcolor{red}{vulgar} \textcolor{BurntOrange}{intrigue.} That, however, was out of the \textcolor{green}{question.} The

 man's business was a \textcolor{red}{small} one, and there was nothing in his

 house which could \textcolor{green}{account} for such elaborate \textcolor{blue}{preparations,} and

 such an \textcolor{red}{expenditure} as they were at. It must, then, be something

 out of the house. What could it be? I \textcolor{blue}{thought} of the assistant's

 \textcolor{green}{fondness} for photography, and his \textcolor{BurntOrange}{trick} of \textcolor{blue}{vanishing} into the

 cellar. The cellar! There was the end of this tangled \textcolor{blue}{clue.} Then

 I made \textcolor{BurntOrange}{inquiries} as to this \textcolor{BurntOrange}{mysterious} assistant and \textcolor{green}{found} that I

 had to \textcolor{BurntOrange}{deal} with one of the coolest and most \textcolor{BurntOrange}{daring} \textcolor{red}{criminals} in

 London. He was doing something in the cellar--something which

 took many hours a day for months on end. What could it be, once

 more? I could think of nothing \textcolor{green}{save} that he was running a tunnel

 to some other \textcolor{green}{building.}



 "So far I had got when we went to \textcolor{green}{visit} the scene of \textcolor{green}{action.} I

 \textcolor{blue}{surprised} you by \textcolor{red}{beating} upon the \textcolor{green}{pavement} with my stick. I was

 ascertaining whether the cellar stretched out in front or behind.

 It was not in front. Then I rang the bell, and, as I hoped, the

 assistant answered it. We have had some \textcolor{red}{skirmishes,} but we had

 never set eyes upon each other before. I hardly looked at his

 face. His knees were what I wished to see. You must yourself have

 remarked how \textcolor{red}{worn,} wrinkled, and \textcolor{red}{stained} they were. They \textcolor{red}{spoke} of

 those hours of burrowing. The only remaining point was what they

 were burrowing for. I walked round the corner, saw the City and

 Suburban \textcolor{green}{Bank} abutted on our \textcolor{green}{friend's} premises, and felt that I

 had solved my \textcolor{red}{problem.} When you drove home after the concert I

 called upon Scotland Yard and upon the \textcolor{green}{chairman} of the \textcolor{green}{bank}

 \textcolor{green}{directors,} with the \textcolor{blue}{result} that you have seen."



 "And how could you tell that they would make their \textcolor{blue}{attempt}

 to-night?" I asked.



 "Well, when they closed their \textcolor{green}{League} offices that was a sign that

 they cared no longer about Mr. Jabez Wilson's presence--in other

 \textcolor{green}{words,} that they had completed their tunnel. But it was \textcolor{green}{essential}

 that they should use it soon, as it might be discovered, or the

 bullion might be \textcolor{red}{removed.} Saturday would suit them better than

 any other day, as it would give them two days for their \textcolor{BurntOrange}{escape.}

 For all these \textcolor{green}{reasons} I \textcolor{BurntOrange}{expected} them to come to-night."



 "You \textcolor{green}{reasoned} it out beautifully," I \textcolor{blue}{exclaimed} in unfeigned

 \textcolor{green}{admiration.} "It is so \textcolor{blue}{long} a chain, and yet every link rings

 \textcolor{green}{true."}



 "It \textcolor{green}{saved} me from ennui," he answered, \textcolor{red}{yawning.} "Alas! I already

 feel it closing in upon me. My life is \textcolor{red}{spent} in one \textcolor{blue}{long} \textcolor{green}{effort}

 to \textcolor{BurntOrange}{escape} from the \textcolor{BurntOrange}{commonplaces} of \textcolor{green}{existence.} These little

 \textcolor{red}{problems} help me to do so."



 "And you are a \textcolor{green}{benefactor} of the race," said I.



 He shrugged his \textcolor{green}{shoulders.} "Well, perhaps, after all, it is of

 some little use," he remarked. "'L'homme c'est rien--l'oeuvre

 c'est tout,' as Gustave Flaubert wrote to George Sand."







 \textcolor{BurntOrange}{ADVENTURE} III. A \textcolor{red}{CASE} OF IDENTITY



 "My \textcolor{green}{dear} \textcolor{green}{fellow,"} said Sherlock Holmes as we sat on either side

 of the \textcolor{red}{fire} in his \textcolor{green}{lodgings} at Baker Street, "life is infinitely

 \textcolor{red}{stranger} than anything which the mind of man could invent. We

 would not \textcolor{BurntOrange}{dare} to conceive the things which are really mere

 \textcolor{BurntOrange}{commonplaces} of \textcolor{green}{existence.} If we could fly out of that window

 hand in hand, hover over this great city, gently \textcolor{red}{remove} the

 roofs, and peep in at the queer things which are going on, the

 strange \textcolor{blue}{coincidences,} the \textcolor{BurntOrange}{plannings,} the cross-purposes, the

 \textcolor{BurntOrange}{wonderful} chains of events, working through generations, and

 \textcolor{green}{leading} to the most outré \textcolor{blue}{results,} it would make all fiction with

 its conventionalities and \textcolor{BurntOrange}{foreseen} conclusions most \textcolor{red}{stale} and

 \textcolor{red}{unprofitable."}



 "And yet I am not \textcolor{BurntOrange}{convinced} of it," I answered. "The \textcolor{red}{cases} which

 come to light in the papers are, as a \textcolor{BurntOrange}{rule,} bald enough, and

 \textcolor{red}{vulgar} enough. We have in our \textcolor{BurntOrange}{police} reports realism pushed to

 its extreme limits, and yet the \textcolor{blue}{result} is, it must be \textcolor{BurntOrange}{confessed,}

 neither fascinating nor \textcolor{green}{artistic."}



 "A certain selection and \textcolor{BurntOrange}{discretion} must be used in producing a

 realistic effect," remarked Holmes. "This is wanting in the

 \textcolor{BurntOrange}{police} report, where more \textcolor{red}{stress} is laid, perhaps, upon the

 platitudes of the magistrate than upon the details, which to an

 observer contain the \textcolor{green}{vital} essence of the whole matter. \textcolor{BurntOrange}{Depend}

 upon it, there is nothing so \textcolor{red}{unnatural} as the \textcolor{BurntOrange}{commonplace."}



 I \textcolor{BurntOrange}{smiled} and shook my head. "I can quite understand your thinking

 so," I said. "Of course, in your position of \textcolor{red}{unofficial} \textcolor{green}{adviser}

 and \textcolor{green}{helper} to everybody who is absolutely puzzled, throughout

 three continents, you are brought in \textcolor{green}{contact} with all that is

 strange and \textcolor{BurntOrange}{bizarre.} But here"--I picked up the morning paper

 from the ground--"let us put it to a practical test. Here is the

 first heading upon which I come. 'A husband's \textcolor{red}{cruelty} to his

 wife.' There is half a column of print, but I know without

 \textcolor{green}{reading} it that it is all perfectly \textcolor{green}{familiar} to me. There is, of

 course, the other woman, the drink, the push, the blow, the

 \textcolor{BurntOrange}{bruise,} the \textcolor{BurntOrange}{sympathetic} sister or landlady. The crudest of

 \textcolor{green}{writers} could invent nothing more \textcolor{red}{crude."}



 "Indeed, your example is an \textcolor{red}{unfortunate} one for your \textcolor{red}{argument,"}

 said Holmes, taking the paper and glancing his eye down it. "This

 is the Dundas separation \textcolor{red}{case,} and, as it happens, I was engaged

 in clearing up some \textcolor{red}{small} points in connection with it. The

 husband was a teetotaler, there was no other woman, and the

 conduct \textcolor{red}{complained} of was that he had drifted into the habit of

 winding up every meal by taking out his false teeth and hurling

 them at his wife, which, you will allow, is not an \textcolor{green}{action} likely

 to occur to the imagination of the average story-teller. Take a

 pinch of snuff, \textcolor{green}{Doctor,} and acknowledge that I have \textcolor{BurntOrange}{scored} over

 you in your example."



 He held out his snuffbox of old \textcolor{green}{gold,} with a great amethyst in

 the centre of the lid. Its splendour was in such contrast to his

 homely ways and simple life that I could not help commenting upon

 it.



 "Ah," said he, "I forgot that I had not seen you for some weeks.

 It is a little souvenir from the \textcolor{green}{King} of Bohemia in return for my

 \textcolor{green}{assistance} in the \textcolor{red}{case} of the Irene Adler papers."



 "And the ring?" I asked, glancing at a \textcolor{BurntOrange}{remarkable} \textcolor{BurntOrange}{brilliant} which

 \textcolor{BurntOrange}{sparkled} upon his finger.



 "It was from the reigning family of Holland, though the matter in

 which I \textcolor{BurntOrange}{served} them was of such delicacy that I cannot \textcolor{green}{confide} it

 even to you, who have been \textcolor{BurntOrange}{good} enough to \textcolor{green}{chronicle} one or two of

 my little \textcolor{red}{problems."}



 "And have you any on hand just now?" I asked with \textcolor{green}{interest.}



 "Some ten or twelve, but none which \textcolor{BurntOrange}{present} any \textcolor{green}{feature} of

 \textcolor{green}{interest.} They are \textcolor{green}{important,} you understand, without being

 \textcolor{green}{interesting.} Indeed, I have \textcolor{green}{found} that it is usually in

 \textcolor{red}{unimportant} matters that there is a field for the observation,

 and for the quick analysis of cause and effect which gives the

 \textcolor{green}{charm} to an \textcolor{blue}{investigation.} The larger \textcolor{red}{crimes} are \textcolor{green}{apt} to be the

 simpler, for the bigger the \textcolor{red}{crime} the more \textcolor{green}{obvious,} as a \textcolor{BurntOrange}{rule,} is

 the \textcolor{green}{motive.} In these \textcolor{red}{cases,} \textcolor{green}{save} for one rather intricate matter

 which has been referred to me from Marseilles, there is nothing

 which \textcolor{BurntOrange}{presents} any \textcolor{green}{features} of \textcolor{green}{interest.} It is possible, however,

 that I may have something better before very many minutes are

 over, for this is one of my clients, or I am much \textcolor{red}{mistaken."}



 He had risen from his chair and was standing between the parted

 \textcolor{red}{blinds} gazing down into the \textcolor{red}{dull} neutral-tinted London street.

 Looking over his \textcolor{green}{shoulder,} I saw that on the \textcolor{green}{pavement} opposite

 there stood a large woman with a heavy fur boa round her neck,

 and a large \textcolor{green}{curling} red feather in a broad-brimmed hat which was

 tilted in a coquettish Duchess of Devonshire fashion over her

 ear. From under this great panoply she peeped up in a \textcolor{BurntOrange}{nervous,}

 hesitating fashion at our windows, while her body oscillated

 \textcolor{red}{backward} and \textcolor{green}{forward,} and her fingers fidgeted with her glove

 buttons. \textcolor{blue}{Suddenly,} with a \textcolor{red}{plunge,} as of the swimmer who leaves

 the \textcolor{green}{bank,} she \textcolor{blue}{hurried} across the road, and we heard the sharp

 clang of the bell.



 "I have seen those \textcolor{red}{symptoms} before," said Holmes, throwing his

 \textcolor{red}{cigarette} into the \textcolor{red}{fire.} "Oscillation upon the \textcolor{green}{pavement} always

 means an affaire de coeur. She would like \textcolor{green}{advice,} but is not sure

 that the matter is not too delicate for \textcolor{green}{communication.} And yet

 even here we may \textcolor{red}{discriminate.} When a woman has been seriously

 \textcolor{red}{wronged} by a man she no longer oscillates, and the \textcolor{green}{usual} \textcolor{red}{symptom}

 is a \textcolor{red}{broken} bell wire. Here we may take it that there is a \textcolor{green}{love}

 matter, but that the \textcolor{green}{maiden} is not so much \textcolor{red}{angry} as \textcolor{red}{perplexed,} or

 \textcolor{red}{grieved.} But here she comes in person to resolve our \textcolor{BurntOrange}{doubts."}



 As he \textcolor{red}{spoke} there was a tap at the door, and the \textcolor{red}{boy} in buttons

 entered to announce Miss Mary Sutherland, while the lady herself

 \textcolor{BurntOrange}{loomed} behind his \textcolor{red}{small} \textcolor{red}{black} figure like a full-sailed

 merchant-man behind a tiny \textcolor{green}{pilot} boat. Sherlock Holmes welcomed

 her with the easy \textcolor{green}{courtesy} for which he was \textcolor{BurntOrange}{remarkable,} and,

 having closed the door and bowed her into an armchair, he looked

 her over in the minute and yet abstracted fashion which was

 peculiar to him.



 "Do you not find," he said, "that with your short sight it is a

 little trying to do so much typewriting?"



 "I did at first," she answered, "but now I know where the \textcolor{blue}{letters}

 are without looking." Then, \textcolor{blue}{suddenly} realising the \textcolor{green}{full} purport

 of his \textcolor{green}{words,} she gave a \textcolor{BurntOrange}{violent} \textcolor{blue}{start} and looked up, with \textcolor{red}{fear}

 and \textcolor{BurntOrange}{astonishment} upon her broad, good-humoured face. "You've

 heard about me, Mr. Holmes," she \textcolor{red}{cried,} "else how could you know

 all that?"



 "Never mind," said Holmes, \textcolor{BurntOrange}{laughing;} "it is my business to know

 things. Perhaps I have trained myself to see what others

 overlook. If not, why should you come to \textcolor{green}{consult} me?"



 "I came to you, \textcolor{green}{sir,} because I heard of you from Mrs. Etherege,

 whose husband you \textcolor{green}{found} so easy when the \textcolor{BurntOrange}{police} and everyone had

 given him up for dead. Oh, Mr. Holmes, I wish you would do as

 much for me. I'm not rich, but still I have a hundred a year in

 my own right, besides the little that I make by the \textcolor{green}{machine,} and

 I would give it all to know what has become of Mr. Hosmer \textcolor{BurntOrange}{Angel."}



 "Why did you come away to \textcolor{green}{consult} me in such a \textcolor{blue}{hurry?"} asked

 Sherlock Holmes, with his finger-tips together and his eyes to

 the ceiling.



 Again a \textcolor{BurntOrange}{startled} look came over the somewhat \textcolor{red}{vacuous} face of Miss

 Mary Sutherland. "Yes, I did \textcolor{BurntOrange}{bang} out of the house," she said,

 "for it made me \textcolor{red}{angry} to see the easy way in which Mr.

 Windibank--that is, my father--took it all. He would not go to

 the \textcolor{BurntOrange}{police,} and he would not go to you, and so at last, as he

 would do nothing and kept on saying that there was no \textcolor{red}{harm} done,

 it made me \textcolor{red}{mad,} and I just on with my things and came right away

 to you."



 "Your \textcolor{green}{father,"} said Holmes, "your stepfather, surely, since the

 name is different."



 "Yes, my stepfather. I call him \textcolor{green}{father,} though it sounds funny,

 too, for he is only five years and two months older than myself."



 "And your \textcolor{BurntOrange}{mother} is \textcolor{BurntOrange}{alive?"}



 "Oh, yes, \textcolor{BurntOrange}{mother} is \textcolor{BurntOrange}{alive} and well. I wasn't best \textcolor{green}{pleased,} Mr.

 Holmes, when she married again so soon after \textcolor{green}{father's} \textcolor{BurntOrange}{death,} and

 a man who was nearly fifteen years \textcolor{BurntOrange}{younger} than herself. \textcolor{green}{Father}

 was a plumber in the Tottenham \textcolor{BurntOrange}{Court} Road, and he left a tidy

 business behind him, which \textcolor{BurntOrange}{mother} carried on with Mr. \textcolor{green}{Hardy,} the

 \textcolor{green}{foreman;} but when Mr. Windibank came he made her sell the

 business, for he was very \textcolor{green}{superior,} being a traveller in wines.

 They got 4700 \textcolor{red}{pounds} for the \textcolor{green}{goodwill} and \textcolor{green}{interest,} which wasn't

 near as much as \textcolor{green}{father} could have got if he had been \textcolor{BurntOrange}{alive."}



 I had \textcolor{BurntOrange}{expected} to see Sherlock Holmes \textcolor{BurntOrange}{impatient} under this

 rambling and \textcolor{red}{inconsequential} narrative, but, on the \textcolor{red}{contrary,} he

 had listened with the greatest concentration of \textcolor{green}{attention.}



 "Your own little \textcolor{BurntOrange}{income,"} he asked, "does it come out of the

 business?"



 "Oh, no, \textcolor{green}{sir.} It is quite separate and was left me by my uncle

 Ned in Auckland. It is in New Zealand stock, \textcolor{BurntOrange}{paying} 4 1/2 per

 cent. Two thousand five hundred \textcolor{red}{pounds} was the amount, but I can

 only touch the \textcolor{green}{interest."}



 "You \textcolor{green}{interest} me extremely," said Holmes. "And since you draw so

 large a sum as a hundred a year, with what you \textcolor{green}{earn} into the

 \textcolor{green}{bargain,} you no \textcolor{BurntOrange}{doubt} travel a little and indulge yourself in

 every way. I believe that a single lady can get on very nicely

 upon an \textcolor{BurntOrange}{income} of about 60 \textcolor{red}{pounds."}



 "I could do with much less than that, Mr. Holmes, but you

 understand that as \textcolor{blue}{long} as I live at home I don't wish to be a

 burden to them, and so they have the use of the \textcolor{BurntOrange}{money} just while

 I am staying with them. Of course, that is only just for the

 \textcolor{blue}{time.} Mr. Windibank draws my \textcolor{green}{interest} every quarter and \textcolor{BurntOrange}{pays} it

 over to \textcolor{BurntOrange}{mother,} and I find that I can do \textcolor{BurntOrange}{pretty} well with what I

 \textcolor{green}{earn} at typewriting. It brings me twopence a sheet, and I can

 often do from fifteen to twenty sheets in a day."



 "You have made your position very clear to me," said Holmes.

 "This is my \textcolor{green}{friend,} Dr. Watson, before whom you can speak as

 \textcolor{green}{freely} as before myself. Kindly tell us now all about your

 connection with Mr. Hosmer \textcolor{BurntOrange}{Angel."}



 A \textcolor{green}{flush} stole over Miss Sutherland's face, and she picked

 nervously at the fringe of her jacket. "I met him first at the

 gasfitters' ball," she said. "They used to send \textcolor{green}{father} tickets

 when he was \textcolor{BurntOrange}{alive,} and then afterwards they remembered us, and

 sent them to \textcolor{BurntOrange}{mother.} Mr. Windibank did not wish us to go. He

 never did wish us to go anywhere. He would get quite \textcolor{red}{mad} if I

 wanted so much as to \textcolor{green}{join} a Sunday-school \textcolor{BurntOrange}{treat.} But this \textcolor{blue}{time} I

 was set on going, and I would go; for what right had he to

 \textcolor{red}{prevent?} He said the folk were not fit for us to know, when all

 \textcolor{green}{father's} \textcolor{green}{friends} were to be there. And he said that I had nothing

 fit to \textcolor{BurntOrange}{wear,} when I had my purple \textcolor{green}{plush} that I had never so much

 as taken out of the drawer. At last, when nothing else would do,

 he went off to France upon the business of the firm, but we went,

 \textcolor{BurntOrange}{mother} and I, with Mr. \textcolor{green}{Hardy,} who used to be our \textcolor{green}{foreman,} and it

 was there I met Mr. Hosmer \textcolor{BurntOrange}{Angel."}



 "I suppose," said Holmes, "that when Mr. Windibank came back from

 France he was very annoyed at your having gone to the ball."



 "Oh, well, he was very \textcolor{BurntOrange}{good} about it. He \textcolor{BurntOrange}{laughed,} I remember, and

 shrugged his \textcolor{green}{shoulders,} and said there was no use \textcolor{red}{denying}

 anything to a woman, for she would have her way."



 "I see. Then at the gasfitters' ball you met, as I understand, a

 \textcolor{green}{gentleman} called Mr. Hosmer \textcolor{BurntOrange}{Angel."}



 "Yes, \textcolor{green}{sir.} I met him that night, and he called next day to ask if

 we had got home all \textcolor{green}{safe,} and after that we met him--that is to

 say, Mr. Holmes, I met him twice for walks, but after that \textcolor{green}{father}

 came back again, and Mr. Hosmer \textcolor{BurntOrange}{Angel} could not come to the house

 any more."



 "No?"



 "Well, you know \textcolor{green}{father} didn't like anything of the sort. He

 wouldn't have any \textcolor{BurntOrange}{visitors} if he could help it, and he used to

 say that a woman should be \textcolor{BurntOrange}{happy} in her own family circle. But

 then, as I used to say to \textcolor{BurntOrange}{mother,} a woman wants her own circle to

 begin with, and I had not got mine yet."



 "But how about Mr. Hosmer \textcolor{BurntOrange}{Angel?} Did he make no \textcolor{blue}{attempt} to see

 you?"



 "Well, \textcolor{green}{father} was going off to France again in a week, and Hosmer

 wrote and said that it would be safer and better not to see each

 other until he had gone. We could write in the meantime, and he

 used to write every day. I took the \textcolor{blue}{letters} in in the morning, so

 there was no need for \textcolor{green}{father} to know."



 "Were you engaged to the \textcolor{green}{gentleman} at this \textcolor{blue}{time?"}



 "Oh, yes, Mr. Holmes. We were engaged after the first walk that

 we took. Hosmer--Mr. Angel--was a \textcolor{green}{cashier} in an office in

 Leadenhall Street--and--"



 "What office?"



 "That's the \textcolor{red}{worst} of it, Mr. Holmes, I don't know."



 "Where did he live, then?"



 "He slept on the premises."



 "And you don't know his address?"



 "No--except that it was Leadenhall Street."



 "Where did you address your \textcolor{blue}{letters,} then?"



 "To the Leadenhall Street Post Office, to be left till called

 for. He said that if they were sent to the office he would be

 chaffed by all the other clerks about having \textcolor{blue}{letters} from a lady,

 so I \textcolor{green}{offered} to typewrite them, like he did his, but he wouldn't

 have that, for he said that when I wrote them they seemed to come

 from me, but when they were typewritten he always felt that the

 \textcolor{green}{machine} had come between us. That will just \textcolor{green}{show} you how fond he

 was of me, Mr. Holmes, and the little things that he would think

 of."



 "It was most suggestive," said Holmes. "It has \textcolor{blue}{long} been an \textcolor{green}{axiom}

 of mine that the little things are infinitely the most \textcolor{green}{important.}

 Can you remember any other little things about Mr. Hosmer \textcolor{BurntOrange}{Angel?"}



 "He was a very shy man, Mr. Holmes. He would rather walk with me

 in the evening than in the daylight, for he said that he hated to

 be conspicuous. Very retiring and gentlemanly he was. Even his

 voice was gentle. He'd had the quinsy and \textcolor{red}{swollen} glands when he

 was \textcolor{BurntOrange}{young,} he told me, and it had left him with a weak throat,

 and a hesitating, whispering fashion of \textcolor{green}{speech.} He was always

 well dressed, very neat and plain, but his eyes were weak, just

 as mine are, and he wore tinted glasses against the \textcolor{red}{glare."}



 "Well, and what \textcolor{blue}{happened} when Mr. Windibank, your stepfather,

 returned to France?"



 "Mr. Hosmer \textcolor{BurntOrange}{Angel} came to the house again and proposed that we

 should \textcolor{BurntOrange}{marry} before \textcolor{green}{father} came back. He was in \textcolor{BurntOrange}{dreadful} \textcolor{green}{earnest}

 and made me \textcolor{green}{swear,} with my hands on the \textcolor{BurntOrange}{Testament,} that whatever

 \textcolor{blue}{happened} I would always be \textcolor{green}{true} to him. \textcolor{BurntOrange}{Mother} said he was quite

 right to make me \textcolor{green}{swear,} and that it was a sign of his \textcolor{BurntOrange}{passion.}

 \textcolor{BurntOrange}{Mother} was all in his favour from the first and was even fonder

 of him than I was. Then, when they \textcolor{green}{talked} of \textcolor{BurntOrange}{marrying} within the

 week, I began to ask about \textcolor{green}{father;} but they both said never to

 mind about \textcolor{green}{father,} but just to tell him afterwards, and \textcolor{BurntOrange}{mother}

 said she would make it all right with him. I didn't quite like

 that, Mr. Holmes. It seemed funny that I should ask his \textcolor{BurntOrange}{leave,} as

 he was only a few years older than me; but I didn't want to do

 anything on the \textcolor{red}{sly,} so I wrote to \textcolor{green}{father} at Bordeaux, where the

 company has its French offices, but the \textcolor{blue}{letter} came back to me on

 the very morning of the wedding."



 "It missed him, then?"



 "Yes, \textcolor{green}{sir;} for he had \textcolor{blue}{started} to England just before it \textcolor{blue}{arrived."}



 "Ha! that was \textcolor{red}{unfortunate.} Your wedding was arranged, then, for

 the Friday. Was it to be in \textcolor{BurntOrange}{church?"}



 "Yes, \textcolor{green}{sir,} but very quietly. It was to be at St. Saviour's, near

 \textcolor{green}{King's} \textcolor{red}{Cross,} and we were to have \textcolor{green}{breakfast} afterwards at the St.

 Pancras Hotel. Hosmer came for us in a hansom, but as there were

 two of us he put us both into it and stepped himself into a

 four-wheeler, which \textcolor{blue}{happened} to be the only other \textcolor{green}{cab} in the

 street. We got to the \textcolor{BurntOrange}{church} first, and when the four-wheeler

 drove up we \textcolor{BurntOrange}{waited} for him to step out, but he never did, and

 when the cabman got down from the box and looked there was no one

 there! The cabman said that he could not imagine what had become

 of him, for he had seen him get in with his own eyes. That was

 last Friday, Mr. Holmes, and I have never seen or heard anything

 since then to throw any light upon what became of him."



 "It seems to me that you have been very shamefully \textcolor{BurntOrange}{treated,"} said

 Holmes.



 "Oh, no, \textcolor{green}{sir!} He was too \textcolor{BurntOrange}{good} and \textcolor{green}{kind} to \textcolor{BurntOrange}{leave} me so. Why, all

 the morning he was saying to me that, whatever \textcolor{blue}{happened,} I was to

 be \textcolor{green}{true;} and that even if something quite \textcolor{blue}{unforeseen} occurred to

 separate us, I was always to remember that I was \textcolor{green}{pledged} to him,

 and that he would claim his \textcolor{green}{pledge} sooner or later. It seemed

 strange \textcolor{green}{talk} for a wedding-morning, but what has \textcolor{blue}{happened} since

 gives a meaning to it."



 "Most certainly it does. Your own opinion is, then, that some

 \textcolor{blue}{unforeseen} \textcolor{BurntOrange}{catastrophe} has occurred to him?"



 "Yes, \textcolor{green}{sir.} I believe that he foresaw some \textcolor{red}{danger,} or else he

 would not have \textcolor{green}{talked} so. And then I think that what he foresaw

 \textcolor{blue}{happened."}



 "But you have no \textcolor{green}{notion} as to what it could have been?"



 "None."



 "One more \textcolor{green}{question.} How did your \textcolor{BurntOrange}{mother} take the matter?"



 "She was \textcolor{red}{angry,} and said that I was never to speak of the matter

 again."



 "And your \textcolor{green}{father?} Did you tell him?"



 "Yes; and he seemed to think, with me, that something had

 \textcolor{blue}{happened,} and that I should hear of Hosmer again. As he said,

 what \textcolor{green}{interest} could anyone have in bringing me to the doors of

 the \textcolor{BurntOrange}{church,} and then \textcolor{BurntOrange}{leaving} me? Now, if he had borrowed my

 \textcolor{BurntOrange}{money,} or if he had married me and got my \textcolor{BurntOrange}{money} settled on him,

 there might be some \textcolor{green}{reason,} but Hosmer was very independent about

 \textcolor{BurntOrange}{money} and never would look at a shilling of mine. And yet, what

 could have \textcolor{blue}{happened?} And why could he not write? Oh, it drives me

 half-mad to think of it, and I can't sleep a wink at night." She

 \textcolor{green}{pulled} a little handkerchief out of her \textcolor{red}{muff} and began to \textcolor{red}{sob}

 \textcolor{red}{heavily} into it.



 "I shall glance into the \textcolor{red}{case} for you," said Holmes, rising, "and

 I have no \textcolor{BurntOrange}{doubt} that we shall reach some definite \textcolor{blue}{result.} Let the

 \textcolor{BurntOrange}{weight} of the matter \textcolor{green}{rest} upon me now, and do not let your mind

 dwell upon it further. Above all, try to let Mr. Hosmer \textcolor{BurntOrange}{Angel}

 \textcolor{blue}{vanish} from your memory, as he has done from your life."



 "Then you don't think \textcolor{red}{I'll} see him again?"



 "I \textcolor{red}{fear} not."



 "Then what has \textcolor{blue}{happened} to him?"



 "You will \textcolor{BurntOrange}{leave} that \textcolor{green}{question} in my hands. I should like an

 \textcolor{green}{accurate} description of him and any \textcolor{blue}{letters} of his which you can

 spare."



 "I advertised for him in last Saturday's \textcolor{green}{Chronicle,"} said she.

 "Here is the \textcolor{BurntOrange}{slip} and here are four \textcolor{blue}{letters} from him."



 "Thank you. And your address?"



 "No. 31 Lyon Place, Camberwell."



 "Mr. \textcolor{BurntOrange}{Angel's} address you never had, I understand. Where is your

 \textcolor{green}{father's} place of business?"



 "He travels for Westhouse & Marbank, the great claret importers

 of Fenchurch Street."



 "Thank you. You have made your \textcolor{green}{statement} very clearly. You will

 \textcolor{BurntOrange}{leave} the papers here, and remember the \textcolor{green}{advice} which I have given

 you. Let the whole \textcolor{blue}{incident} be a \textcolor{green}{sealed} book, and do not allow it

 to affect your life."



 "You are very \textcolor{green}{kind,} Mr. Holmes, but I cannot do that. I shall be

 \textcolor{green}{true} to Hosmer. He shall find me \textcolor{blue}{ready} when he comes back."



 For all the preposterous hat and the \textcolor{red}{vacuous} face, there was

 something \textcolor{green}{noble} in the simple \textcolor{BurntOrange}{faith} of our \textcolor{BurntOrange}{visitor} which

 compelled our \textcolor{BurntOrange}{respect.} She laid her little bundle of papers upon

 the table and went her way, with a \textcolor{green}{promise} to come again whenever

 she might be summoned.



 Sherlock Holmes sat silent for a few minutes with his fingertips

 still pressed together, his legs stretched out in front of him,

 and his gaze directed upward to the ceiling. Then he took down

 from the \textcolor{red}{rack} the old and oily clay pipe, which was to him as a

 \textcolor{BurntOrange}{counsellor,} and, having lit it, he leaned back in his chair, with

 the thick \textcolor{red}{blue} cloud-wreaths spinning up from him, and a look of

 \textcolor{green}{infinite} languor in his face.



 "Quite an \textcolor{green}{interesting} \textcolor{green}{study,} that \textcolor{green}{maiden,"} he observed. "I \textcolor{green}{found}

 her more \textcolor{green}{interesting} than her little \textcolor{red}{problem,} which, by the way,

 is rather a trite one. You will find parallel \textcolor{red}{cases,} if you

 \textcolor{green}{consult} my index, in Andover in '77, and there was something of

 the sort at The Hague last year. Old as is the idea, however,

 there were one or two details which were new to me. But the

 \textcolor{green}{maiden} herself was most instructive."



 "You appeared to read a \textcolor{BurntOrange}{good} \textcolor{BurntOrange}{deal} upon her which was quite

 invisible to me," I remarked.



 "Not invisible but unnoticed, Watson. You did not know where to

 look, and so you missed all that was \textcolor{green}{important.} I can never bring

 you to realise the \textcolor{BurntOrange}{importance} of sleeves, the suggestiveness of

 thumb-nails, or the great issues that may hang from a boot-lace.

 Now, what did you gather from that woman's appearance? Describe

 it."



 "Well, she had a slate-coloured, broad-brimmed straw hat, with a

 feather of a brickish red. Her jacket was \textcolor{red}{black,} with \textcolor{red}{black} beads

 sewn upon it, and a fringe of little \textcolor{red}{black} jet ornaments. Her

 dress was brown, rather darker than coffee colour, with a little

 purple \textcolor{green}{plush} at the neck and sleeves. Her gloves were greyish and

 were \textcolor{red}{worn} through at the right forefinger. Her boots I didn't

 observe. She had \textcolor{red}{small} round, hanging \textcolor{green}{gold} earrings, and a

 \textcolor{green}{general} air of being \textcolor{green}{fairly} well-to-do in a \textcolor{red}{vulgar,} comfortable,

 \textcolor{green}{easy-going} way."



 Sherlock Holmes clapped his hands softly together and \textcolor{BurntOrange}{chuckled.}



 "'Pon my \textcolor{green}{word,} Watson, you are coming along \textcolor{BurntOrange}{wonderfully.} You have

 really done very well indeed. It is \textcolor{green}{true} that you have missed

 everything of \textcolor{BurntOrange}{importance,} but you have \textcolor{red}{hit} upon the method, and

 you have a quick eye for colour. Never \textcolor{green}{trust} to \textcolor{green}{general}

 \textcolor{green}{impressions,} my \textcolor{red}{boy,} but concentrate yourself upon details. My

 first glance is always at a woman's sleeve. In a man it is

 perhaps better first to take the knee of the trouser. As you

 observe, this woman had \textcolor{green}{plush} upon her sleeves, which is a most

 useful material for \textcolor{green}{showing} traces. The double line a little

 above the wrist, where the typewritist presses against the table,

 was beautifully defined. The sewing-machine, of the hand type,

 leaves a similar mark, but only on the left arm, and on the side

 of it farthest from the thumb, instead of being right across the

 broadest part, as this was. I then glanced at her face, and,

 observing the dint of a pince-nez at either side of her \textcolor{red}{nose,} I

 ventured a remark upon short sight and typewriting, which seemed

 to \textcolor{BurntOrange}{surprise} her."



 "It \textcolor{blue}{surprised} me."



 "But, surely, it was \textcolor{green}{obvious.} I was then much \textcolor{blue}{surprised} and

 \textcolor{BurntOrange}{interested} on glancing down to observe that, though the boots

 which she was \textcolor{BurntOrange}{wearing} were not unlike each other, they were

 really odd ones; the one having a slightly decorated toe-cap, and

 the other a plain one. One was buttoned only in the two lower

 buttons out of five, and the other at the first, third, and

 fifth. Now, when you see that a \textcolor{BurntOrange}{young} lady, otherwise \textcolor{green}{neatly}

 dressed, has come away from home with odd boots, half-buttoned,

 it is no great deduction to say that she came away in a \textcolor{blue}{hurry."}



 "And what else?" I asked, keenly \textcolor{BurntOrange}{interested,} as I always was, by

 my \textcolor{green}{friend's} \textcolor{green}{incisive} \textcolor{green}{reasoning.}



 "I noted, in passing, that she had written a note before \textcolor{BurntOrange}{leaving}

 home but after being \textcolor{green}{fully} dressed. You observed that her right

 glove was \textcolor{red}{torn} at the forefinger, but you did not apparently see

 that both glove and finger were \textcolor{red}{stained} with violet ink. She had

 written in a \textcolor{blue}{hurry} and dipped her pen too deep. It must have been

 this morning, or the mark would not remain clear upon the finger.

 All this is \textcolor{green}{amusing,} though rather elementary, but I must go back

 to business, Watson. Would you mind \textcolor{green}{reading} me the advertised

 description of Mr. Hosmer \textcolor{BurntOrange}{Angel?"}



 I held the little printed \textcolor{BurntOrange}{slip} to the light.



 "Missing," it said, "on the morning of the fourteenth, a \textcolor{green}{gentleman}

 named Hosmer \textcolor{BurntOrange}{Angel.} About five ft. seven in. in height;

 \textcolor{green}{strongly} built, sallow complexion, \textcolor{red}{black} hair, a little bald in

 the centre, bushy, \textcolor{red}{black} side-whiskers and moustache; tinted

 glasses, slight \textcolor{red}{infirmity} of \textcolor{green}{speech.} Was dressed, when last seen,

 in \textcolor{red}{black} frock-coat faced with \textcolor{green}{silk,} \textcolor{red}{black} waistcoat, \textcolor{green}{gold} Albert

 chain, and grey Harris tweed trousers, with brown gaiters over

 elastic-sided boots. Known to have been \textcolor{green}{employed} in an office in

 Leadenhall Street. Anybody bringing--"



 "That will do," said Holmes. "As to the \textcolor{blue}{letters,"} he continued,

 glancing over them, "they are very \textcolor{BurntOrange}{commonplace.} Absolutely no

 \textcolor{blue}{clue} in them to Mr. \textcolor{BurntOrange}{Angel,} \textcolor{green}{save} that he \textcolor{BurntOrange}{quotes} Balzac once. There

 is one \textcolor{BurntOrange}{remarkable} point, however, which will no \textcolor{BurntOrange}{doubt} \textcolor{red}{strike}

 you."



 "They are typewritten," I remarked.



 "Not only that, but the \textcolor{green}{signature} is typewritten. Look at the

 neat little 'Hosmer \textcolor{BurntOrange}{Angel'} at the \textcolor{red}{bottom.} There is a date, you

 see, but no superscription except Leadenhall Street, which is

 rather \textcolor{red}{vague.} The point about the \textcolor{green}{signature} is very suggestive--in

 \textcolor{green}{fact,} we may call it conclusive."



 "Of what?"



 "My \textcolor{green}{dear} \textcolor{green}{fellow,} is it possible you do not see how \textcolor{green}{strongly} it

 \textcolor{red}{bears} upon the \textcolor{red}{case?"}



 "I cannot say that I do unless it were that he wished to be able

 to \textcolor{red}{deny} his \textcolor{green}{signature} if an \textcolor{green}{action} for \textcolor{red}{breach} of \textcolor{green}{promise} were

 \textcolor{green}{instituted."}



 "No, that was not the point. However, I shall write two \textcolor{blue}{letters,}

 which should settle the matter. One is to a firm in the City, the

 other is to the \textcolor{BurntOrange}{young} lady's stepfather, Mr. Windibank, asking

 him whether he could meet us here at six o'clock \textcolor{blue}{tomorrow}

 evening. It is just as well that we should do business with the

 male \textcolor{green}{relatives.} And now, \textcolor{green}{Doctor,} we can do nothing until the

 answers to those \textcolor{blue}{letters} come, so we may put our little \textcolor{red}{problem}

 upon the shelf for the \textcolor{blue}{interim."}



 I had had so many \textcolor{green}{reasons} to believe in my \textcolor{green}{friend's} subtle powers

 of \textcolor{green}{reasoning} and \textcolor{green}{extraordinary} energy in \textcolor{green}{action} that I felt that

 he must have some \textcolor{green}{solid} \textcolor{green}{grounds} for the \textcolor{green}{assured} and easy

 demeanour with which he \textcolor{BurntOrange}{treated} the singular \textcolor{blue}{mystery} which he had

 been called upon to fathom. Once only had I known him to fail, in

 the \textcolor{red}{case} of the \textcolor{green}{King} of Bohemia and of the Irene Adler

 photograph; but when I looked back to the \textcolor{red}{weird} business of the

 Sign of Four, and the \textcolor{green}{extraordinary} circumstances connected with

 the \textcolor{green}{Study} in Scarlet, I felt that it would be a strange tangle

 indeed which he could not unravel.



 I left him then, still puffing at his \textcolor{red}{black} clay pipe, with the

 \textcolor{red}{conviction} that when I came again on the next evening I would

 find that he held in his hands all the \textcolor{blue}{clues} which would \textcolor{green}{lead} up

 to the identity of the \textcolor{red}{disappearing} \textcolor{BurntOrange}{bridegroom} of Miss Mary

 Sutherland.



 A \textcolor{green}{professional} \textcolor{red}{case} of great gravity was engaging my own

 \textcolor{green}{attention} at the \textcolor{blue}{time,} and the whole of next day I was busy at

 the bedside of the \textcolor{red}{sufferer.} It was not until close upon six

 o'clock that I \textcolor{green}{found} myself free and was able to spring into a

 hansom and drive to Baker Street, half \textcolor{red}{afraid} that I might be too

 \textcolor{red}{late} to \textcolor{green}{assist} at the dénouement of the little \textcolor{blue}{mystery.} I \textcolor{green}{found}

 Sherlock Holmes alone, however, half asleep, with his \textcolor{blue}{long,} thin

 form \textcolor{green}{curled} up in the recesses of his armchair. A \textcolor{red}{formidable}

 \textcolor{green}{array} of bottles and test-tubes, with the \textcolor{red}{pungent} \textcolor{green}{cleanly} \textcolor{red}{smell}

 of hydrochloric \textcolor{red}{acid,} told me that he had \textcolor{red}{spent} his day in the

 chemical work which was so \textcolor{green}{dear} to him.



 "Well, have you solved it?" I asked as I entered.



 "Yes. It was the bisulphate of baryta."



 "No, no, the \textcolor{blue}{mystery!"} I \textcolor{red}{cried.}



 "Oh, that! I \textcolor{blue}{thought} of the salt that I have been working upon.

 There was never any \textcolor{blue}{mystery} in the matter, though, as I said

 yesterday, some of the details are of \textcolor{green}{interest.} The only \textcolor{red}{drawback}

 is that there is no \textcolor{green}{law,} I \textcolor{red}{fear,} that can touch the \textcolor{BurntOrange}{scoundrel."}



 "Who was he, then, and what was his object in \textcolor{red}{deserting} Miss

 Sutherland?"



 The \textcolor{green}{question} was hardly out of my \textcolor{blue}{mouth,} and Holmes had not yet

 opened his lips to reply, when we heard a heavy footfall in the

 passage and a tap at the door.



 "This is the girl's stepfather, Mr. James Windibank," said

 Holmes. "He has written to me to say that he would be here at

 six. Come in!"



 The man who entered was a \textcolor{green}{sturdy,} middle-sized \textcolor{green}{fellow,} some

 thirty years of age, clean-shaven, and sallow-skinned, with a

 \textcolor{red}{bland,} insinuating manner, and a pair of \textcolor{BurntOrange}{wonderfully} sharp and

 penetrating grey eyes. He \textcolor{BurntOrange}{shot} a \textcolor{green}{questioning} glance at each of

 us, placed his shiny top-hat upon the sideboard, and with a

 slight bow sidled down into the nearest chair.



 "Good-evening, Mr. James Windibank," said Holmes. "I think that

 this typewritten \textcolor{blue}{letter} is from you, in which you made an

 appointment with me for six o'clock?"



 "Yes, \textcolor{green}{sir.} I am \textcolor{red}{afraid} that I am a little \textcolor{red}{late,} but I am not

 quite my own \textcolor{green}{master,} you know. I am sorry that Miss Sutherland

 has troubled you about this little matter, for I think it is far

 better not to wash linen of the sort in \textcolor{BurntOrange}{public.} It was quite

 against my wishes that she came, but she is a very \textcolor{green}{excitable,}

 impulsive girl, as you may have noticed, and she is not easily

 controlled when she has made up her mind on a point. Of course, I

 did not mind you so much, as you are not connected with the

 \textcolor{green}{official} \textcolor{BurntOrange}{police,} but it is not \textcolor{BurntOrange}{pleasant} to have a family

 \textcolor{red}{misfortune} like this \textcolor{red}{noised} abroad. Besides, it is a \textcolor{red}{useless}

 expense, for how could you possibly find this Hosmer \textcolor{BurntOrange}{Angel?"}



 "On the \textcolor{red}{contrary,"} said Holmes quietly; "I have every \textcolor{green}{reason} to

 believe that I will \textcolor{BurntOrange}{succeed} in discovering Mr. Hosmer \textcolor{BurntOrange}{Angel."}



 Mr. Windibank gave a \textcolor{BurntOrange}{violent} \textcolor{blue}{start} and dropped his gloves. "I am

 \textcolor{BurntOrange}{delighted} to hear it," he said.



 "It is a curious thing," remarked Holmes, "that a typewriter has

 really quite as much \textcolor{green}{individuality} as a man's handwriting. Unless

 they are quite new, no two of them write exactly alike. Some

 \textcolor{blue}{letters} get more \textcolor{red}{worn} than others, and some \textcolor{BurntOrange}{wear} only on one

 side. Now, you remark in this note of yours, Mr. Windibank, that

 in every \textcolor{red}{case} there is some little \textcolor{red}{slurring} over of the 'e,' and

 a slight \textcolor{red}{defect} in the tail of the 'r.' There are fourteen other

 characteristics, but those are the more \textcolor{green}{obvious."}



 "We do all our \textcolor{BurntOrange}{correspondence} with this \textcolor{green}{machine} at the office,

 and no \textcolor{BurntOrange}{doubt} it is a little \textcolor{red}{worn,"} our \textcolor{BurntOrange}{visitor} answered, glancing

 keenly at Holmes with his bright little eyes.



 "And now I will \textcolor{green}{show} you what is really a very \textcolor{green}{interesting} \textcolor{green}{study,}

 Mr. Windibank," Holmes continued. "I think of writing another

 little monograph some of these days on the typewriter and its

 relation to \textcolor{red}{crime.} It is a \textcolor{red}{subject} to which I have devoted some

 little \textcolor{green}{attention.} I have here four \textcolor{blue}{letters} which purport to come

 from the missing man. They are all typewritten. In each \textcolor{red}{case,} not

 only are the 'e's' \textcolor{red}{slurred} and the 'r's' tailless, but you will

 observe, if you care to use my magnifying lens, that the fourteen

 other characteristics to which I have alluded are there as well."



 Mr. Windibank sprang out of his chair and picked up his hat. "I

 cannot \textcolor{red}{waste} \textcolor{blue}{time} over this sort of fantastic \textcolor{green}{talk,} Mr. Holmes,"

 he said. "If you can \textcolor{blue}{catch} the man, \textcolor{blue}{catch} him, and let me know

 when you have done it."



 "Certainly," said Holmes, stepping over and turning the key in

 the door. "I let you know, then, that I have caught him!"



 "What! where?" \textcolor{BurntOrange}{shouted} Mr. Windibank, turning \textcolor{BurntOrange}{white} to his lips

 and glancing about him like a \textcolor{red}{rat} in a trap.



 "Oh, it \textcolor{blue}{won't} do--really it \textcolor{blue}{won't,"} said Holmes suavely. "There

 is no possible getting out of it, Mr. Windibank. It is quite too

 transparent, and it was a very \textcolor{red}{bad} \textcolor{BurntOrange}{compliment} when you said that

 it was \textcolor{red}{impossible} for me to solve so simple a \textcolor{green}{question.} That's

 right! Sit down and let us \textcolor{green}{talk} it over."



 Our \textcolor{BurntOrange}{visitor} \textcolor{red}{collapsed} into a chair, with a \textcolor{red}{ghastly} face and a

 \textcolor{BurntOrange}{glitter} of moisture on his brow. "It--it's not \textcolor{red}{actionable,"} he

 stammered.



 "I am very much \textcolor{red}{afraid} that it is not. But between ourselves,

 Windibank, it was as \textcolor{red}{cruel} and \textcolor{red}{selfish} and \textcolor{red}{heartless} a \textcolor{BurntOrange}{trick} in a

 \textcolor{red}{petty} way as ever came before me. Now, let me just run over the

 course of events, and you will \textcolor{red}{contradict} me if I go \textcolor{red}{wrong."}



 The man sat huddled up in his chair, with his head \textcolor{red}{sunk} upon his

 breast, like one who is utterly crushed. Holmes stuck his feet up

 on the corner of the mantelpiece and, leaning back with his hands

 in his pockets, began \textcolor{green}{talking,} rather to himself, as it seemed,

 than to us.



 "The man married a woman very much older than himself for her

 \textcolor{BurntOrange}{money,"} said he, "and he \textcolor{BurntOrange}{enjoyed} the use of the \textcolor{BurntOrange}{money} of the

 \textcolor{green}{daughter} as \textcolor{blue}{long} as she lived with them. It was a \textcolor{green}{considerable}

 sum, for people in their position, and the \textcolor{red}{loss} of it would have

 made a serious difference. It was \textcolor{green}{worth} an \textcolor{green}{effort} to \textcolor{green}{preserve} it.

 The \textcolor{green}{daughter} was of a \textcolor{BurntOrange}{good,} \textcolor{green}{amiable} disposition, but affectionate

 and warm-hearted in her ways, so that it was \textcolor{green}{evident} that with

 her \textcolor{green}{fair} \textcolor{green}{personal} \textcolor{green}{advantages,} and her little \textcolor{BurntOrange}{income,} she would

 not be allowed to remain single \textcolor{blue}{long.} Now her \textcolor{BurntOrange}{marriage} would

 mean, of course, the \textcolor{red}{loss} of a hundred a year, so what does her

 stepfather do to \textcolor{red}{prevent} it? He takes the \textcolor{green}{obvious} course of

 keeping her at home and \textcolor{red}{forbidding} her to \textcolor{blue}{seek} the company of

 people of her own age. But soon he \textcolor{green}{found} that that would not

 answer forever. She became restive, insisted upon her rights, and

 \textcolor{BurntOrange}{finally} announced her positive intention of going to a certain

 ball. What does her \textcolor{green}{clever} stepfather do then? He conceives an

 idea more \textcolor{green}{creditable} to his head than to his heart. With the

 connivance and \textcolor{green}{assistance} of his wife he disguised himself,

 \textcolor{green}{covered} those keen eyes with tinted glasses, masked the face with

 a moustache and a pair of bushy whiskers, \textcolor{red}{sunk} that clear voice

 into an insinuating whisper, and doubly secure on \textcolor{green}{account} of the

 girl's short sight, he appears as Mr. Hosmer \textcolor{BurntOrange}{Angel,} and keeps off

 other \textcolor{BurntOrange}{lovers} by making \textcolor{green}{love} himself."



 "It was only a \textcolor{red}{joke} at first," \textcolor{red}{groaned} our \textcolor{BurntOrange}{visitor.} "We never

 \textcolor{blue}{thought} that she would have been so carried away."



 "Very likely not. However that may be, the \textcolor{BurntOrange}{young} lady was very

 decidedly carried away, and, having quite made up her mind that

 her stepfather was in France, the \textcolor{red}{suspicion} of \textcolor{BurntOrange}{treachery} never

 for an instant entered her mind. She was flattered by the

 \textcolor{green}{gentleman's} \textcolor{green}{attentions,} and the effect was \textcolor{green}{increased} by the

 loudly expressed \textcolor{green}{admiration} of her \textcolor{BurntOrange}{mother.} Then Mr. \textcolor{BurntOrange}{Angel} began

 to call, for it was \textcolor{green}{obvious} that the matter should be pushed as

 far as it would go if a \textcolor{green}{real} effect were to be produced. There

 were meetings, and an engagement, which would \textcolor{BurntOrange}{finally} secure the

 girl's \textcolor{green}{affections} from turning towards anyone else. But the

 \textcolor{red}{deception} could not be kept up forever. These \textcolor{red}{pretended} \textcolor{BurntOrange}{journeys}

 to France were rather cumbrous. The thing to do was clearly to

 bring the business to an end in such a dramatic manner that it

 would \textcolor{BurntOrange}{leave} a permanent \textcolor{green}{impression} upon the \textcolor{BurntOrange}{young} lady's mind and

 \textcolor{red}{prevent} her from looking upon any other suitor for some \textcolor{blue}{time} to

 come. Hence those \textcolor{BurntOrange}{vows} of \textcolor{green}{fidelity} exacted upon a \textcolor{BurntOrange}{Testament,} and

 hence also the allusions to a \textcolor{blue}{possibility} of something \textcolor{blue}{happening}

 on the very morning of the wedding. James Windibank wished Miss

 Sutherland to be so \textcolor{red}{bound} to Hosmer \textcolor{BurntOrange}{Angel,} and so \textcolor{BurntOrange}{uncertain} as to

 his \textcolor{BurntOrange}{fate,} that for ten years to come, at any rate, she would not

 listen to another man. As far as the \textcolor{BurntOrange}{church} door he brought her,

 and then, as he could go no farther, he conveniently \textcolor{BurntOrange}{vanished}

 away by the old \textcolor{BurntOrange}{trick} of stepping in at one door of a

 four-wheeler and out at the other. I think that was the chain of

 events, Mr. Windibank!"



 Our \textcolor{BurntOrange}{visitor} had recovered something of his \textcolor{green}{assurance} while Holmes

 had been \textcolor{green}{talking,} and he rose from his chair now with a \textcolor{red}{cold}

 \textcolor{red}{sneer} upon his pale face.



 "It may be so, or it may not, Mr. Holmes," said he, "but if you

 are so very sharp you ought to be sharp enough to know that it is

 you who are \textcolor{blue}{breaking} the \textcolor{green}{law} now, and not me. I have done nothing

 \textcolor{red}{actionable} from the first, but as \textcolor{blue}{long} as you keep that door

 locked you lay yourself open to an \textcolor{green}{action} for \textcolor{red}{assault} and \textcolor{red}{illegal}

 \textcolor{red}{constraint."}



 "The \textcolor{green}{law} cannot, as you say, touch you," said Holmes, unlocking

 and throwing open the door, "yet there never was a man who

 \textcolor{BurntOrange}{deserved} \textcolor{red}{punishment} more. If the \textcolor{BurntOrange}{young} lady has a \textcolor{green}{brother} or a

 \textcolor{green}{friend,} he ought to lay a \textcolor{red}{whip} across your \textcolor{green}{shoulders.} By Jove!"

 he continued, \textcolor{green}{flushing} up at the sight of the bitter \textcolor{red}{sneer} upon

 the man's face, "it is not part of my duties to my client, but

 here's a hunting crop \textcolor{green}{handy,} and I think I shall just \textcolor{BurntOrange}{treat}

 myself to--" He took two \textcolor{green}{swift} steps to the \textcolor{red}{whip,} but before he

 could grasp it there was a \textcolor{BurntOrange}{wild} clatter of steps upon the stairs,

 the heavy hall door \textcolor{BurntOrange}{banged,} and from the window we could see Mr.

 James Windibank running at the \textcolor{BurntOrange}{top} of his speed down the road.



 "There's a cold-blooded \textcolor{BurntOrange}{scoundrel!"} said Holmes, \textcolor{BurntOrange}{laughing,} as he

 threw himself down into his chair once more. "That \textcolor{green}{fellow} will

 rise from \textcolor{red}{crime} to \textcolor{red}{crime} until he does something very \textcolor{red}{bad,} and

 ends on a \textcolor{red}{gallows.} The \textcolor{red}{case} has, in some \textcolor{BurntOrange}{respects,} been not

 entirely devoid of \textcolor{green}{interest."}



 "I cannot now entirely see all the steps of your \textcolor{green}{reasoning,"} I

 remarked.



 "Well, of course it was \textcolor{green}{obvious} from the first that this Mr.

 Hosmer \textcolor{BurntOrange}{Angel} must have some strong object for his curious

 conduct, and it was \textcolor{green}{equally} clear that the only man who really

 profited by the \textcolor{blue}{incident,} as far as we could see, was the

 stepfather. Then the \textcolor{green}{fact} that the two men were never together,

 but that the one always appeared when the other was away, was

 suggestive. So were the tinted \textcolor{BurntOrange}{spectacles} and the curious voice,

 which both hinted at a disguise, as did the bushy whiskers. My

 \textcolor{red}{suspicions} were all confirmed by his peculiar \textcolor{green}{action} in

 typewriting his \textcolor{green}{signature,} which, of course, inferred that his

 handwriting was so \textcolor{green}{familiar} to her that she would recognise even

 the \textcolor{red}{smallest} sample of it. You see all these \textcolor{red}{isolated} \textcolor{green}{facts,}

 together with many minor ones, all pointed in the same

 direction."



 "And how did you verify them?"



 "Having once spotted my man, it was easy to get \textcolor{green}{corroboration.} I

 knew the firm for which this man worked. Having taken the printed

 description. I eliminated everything from it which could be the

 \textcolor{blue}{result} of a disguise--the whiskers, the glasses, the voice, and I

 sent it to the firm, with a request that they would \textcolor{green}{inform} me

 whether it answered to the description of any of their

 travellers. I had already noticed the \textcolor{green}{peculiarities} of the

 typewriter, and I wrote to the man himself at his business

 address asking him if he would come here. As I \textcolor{BurntOrange}{expected,} his

 reply was typewritten and revealed the same trivial but

 characteristic \textcolor{red}{defects.} The same post brought me a \textcolor{blue}{letter} from

 Westhouse & Marbank, of Fenchurch Street, to say that the

 description tallied in every \textcolor{BurntOrange}{respect} with that of their \textcolor{green}{employé,}

 James Windibank. Voilà tout!"



 "And Miss Sutherland?"



 "If I tell her she will not believe me. You may remember the old

 Persian saying, 'There is \textcolor{red}{danger} for him who taketh the tiger

 cub, and \textcolor{red}{danger} also for whoso snatches a \textcolor{red}{delusion} from a woman.'

 There is as much \textcolor{green}{sense} in Hafiz as in Horace, and as much

 \textcolor{green}{knowledge} of the world."







 \textcolor{BurntOrange}{ADVENTURE} IV. THE BOSCOMBE VALLEY \textcolor{blue}{MYSTERY}



 We were seated at \textcolor{green}{breakfast} one morning, my wife and I, when the

 maid brought in a telegram. It was from Sherlock Holmes and ran

 in this way:



 "Have you a couple of days to spare? Have just been wired for from

 the west of England in connection with Boscombe Valley \textcolor{red}{tragedy.}

 Shall be \textcolor{BurntOrange}{glad} if you will come with me. Air and scenery \textcolor{BurntOrange}{perfect.}

 \textcolor{BurntOrange}{Leave} Paddington by the 11:15."



 "What do you say, \textcolor{green}{dear?"} said my wife, looking across at me.

 "Will you go?"



 "I really don't know what to say. I have a \textcolor{green}{fairly} \textcolor{blue}{long} list at

 \textcolor{BurntOrange}{present."}



 "Oh, Anstruther would do your work for you. You have been looking

 a little pale lately. I think that the \textcolor{red}{change} would do you \textcolor{BurntOrange}{good,}

 and you are always so \textcolor{BurntOrange}{interested} in Mr. Sherlock Holmes' \textcolor{red}{cases."}



 "I should be \textcolor{red}{ungrateful} if I were not, seeing what I \textcolor{BurntOrange}{gained}

 through one of them," I answered. "But if I am to go, I must pack

 at once, for I have only half an hour."



 My experience of camp life in Afghanistan had at least had the

 effect of making me a prompt and \textcolor{blue}{ready} traveller. My wants were

 few and simple, so that in less than the \textcolor{blue}{time} stated I was in a

 \textcolor{green}{cab} with my valise, rattling away to Paddington Station. Sherlock

 Holmes was pacing up and down the platform, his tall, \textcolor{red}{gaunt}

 figure made even gaunter and taller by his \textcolor{blue}{long} grey

 travelling-cloak and close-fitting cloth \textcolor{BurntOrange}{cap.}



 "It is really very \textcolor{BurntOrange}{good} of you to come, Watson," said he. "It

 makes a \textcolor{green}{considerable} difference to me, having someone with me on

 whom I can thoroughly rely. Local \textcolor{green}{aid} is always either \textcolor{red}{worthless}

 or else \textcolor{red}{biassed.} If you will keep the two corner seats I shall

 get the tickets."



 We had the carriage to ourselves \textcolor{green}{save} for an \textcolor{green}{immense} \textcolor{red}{litter} of

 papers which Holmes had brought with him. Among these he rummaged

 and read, with intervals of note-taking and of meditation, until

 we were past \textcolor{green}{Reading.} Then he \textcolor{blue}{suddenly} rolled them all into a

 \textcolor{green}{gigantic} ball and tossed them up onto the \textcolor{red}{rack.}



 "Have you heard anything of the \textcolor{red}{case?"} he asked.



 "Not a \textcolor{green}{word.} I have not seen a paper for some days."



 "The London press has not had very \textcolor{green}{full} \textcolor{green}{accounts.} I have just

 been looking through all the recent papers in order to \textcolor{green}{master} the

 particulars. It seems, from what I gather, to be one of those

 simple \textcolor{red}{cases} which are so extremely \textcolor{red}{difficult."}



 "That sounds a little paradoxical."



 "But it is profoundly \textcolor{green}{true.} Singularity is almost \textcolor{green}{invariably} a

 \textcolor{blue}{clue.} The more featureless and \textcolor{BurntOrange}{commonplace} a \textcolor{red}{crime} is, the more

 \textcolor{red}{difficult} it is to bring it home. In this \textcolor{red}{case,} however, they

 have \textcolor{green}{established} a very serious \textcolor{red}{case} against the son of the

 \textcolor{BurntOrange}{murdered} man."



 "It is a \textcolor{BurntOrange}{murder,} then?"



 "Well, it is \textcolor{blue}{conjectured} to be so. I shall take nothing for

 \textcolor{BurntOrange}{granted} until I have the \textcolor{BurntOrange}{opportunity} of looking personally into

 it. I will \textcolor{green}{explain} the state of things to you, as far as I have

 been able to understand it, in a very few \textcolor{green}{words.}



 "Boscombe Valley is a country district not very far from Ross, in

 Herefordshire. The largest \textcolor{green}{landed} proprietor in that part is a

 Mr. \textcolor{red}{John} Turner, who made his \textcolor{BurntOrange}{money} in Australia and returned

 some years ago to the old country. One of the \textcolor{blue}{farms} which he

 held, that of Hatherley, was let to Mr. Charles McCarthy, who was

 also an ex-Australian. The men had known each other in the

 colonies, so that it was not \textcolor{red}{unnatural} that when they came to

 settle down they should do so as near each other as possible.

 Turner was apparently the richer man, so McCarthy became his

 \textcolor{green}{tenant} but still remained, it seems, upon terms of \textcolor{BurntOrange}{perfect}

 \textcolor{green}{equality,} as they were frequently together. McCarthy had one son,

 a lad of eighteen, and Turner had an only \textcolor{green}{daughter} of the same

 age, but neither of them had wives living. They appear to have

 \textcolor{red}{avoided} the society of the neighbouring English families and to

 have \textcolor{green}{led} retired lives, though both the McCarthys were fond of

 sport and were frequently seen at the race-meetings of the

 neighbourhood. McCarthy kept two servants--a man and a girl.

 Turner had a \textcolor{green}{considerable} \textcolor{green}{household,} some half-dozen at the

 least. That is as much as I have been able to gather about the

 families. Now for the \textcolor{green}{facts.}



 "On June 3rd, that is, on Monday last, McCarthy left his house at

 Hatherley about three in the afternoon and walked down to the

 Boscombe \textcolor{green}{Pool,} which is a \textcolor{red}{small} lake formed by the spreading out

 of the stream which runs down the Boscombe Valley. He had been

 out with his serving-man in the morning at Ross, and he had told

 the man that he must \textcolor{blue}{hurry,} as he had an appointment of

 \textcolor{BurntOrange}{importance} to keep at three. From that appointment he never came

 back \textcolor{BurntOrange}{alive.}



 "From Hatherley Farm-house to the Boscombe \textcolor{green}{Pool} is a quarter of a

 mile, and two people saw him as he passed over this \textcolor{green}{ground.} One

 was an old woman, whose name is not mentioned, and the other was

 William Crowder, a game-keeper in the \textcolor{green}{employ} of Mr. Turner. Both

 these \textcolor{green}{witnesses} depose that Mr. McCarthy was walking alone. The

 game-keeper adds that within a few minutes of his seeing Mr.

 McCarthy pass he had seen his son, Mr. James McCarthy, going the

 same way with a \textcolor{red}{gun} under his arm. To the best of his belief, the

 \textcolor{green}{father} was actually in sight at the \textcolor{blue}{time,} and the son was

 following him. He \textcolor{blue}{thought} no more of the matter until he heard in

 the evening of the \textcolor{red}{tragedy} that had occurred.



 "The two McCarthys were seen after the \textcolor{blue}{time} when William Crowder,

 the game-keeper, \textcolor{BurntOrange}{lost} sight of them. The Boscombe \textcolor{green}{Pool} is thickly

 wooded round, with just a fringe of grass and of reeds round the

 edge. A girl of fourteen, \textcolor{BurntOrange}{Patience} Moran, who is the \textcolor{green}{daughter} of

 the lodge-keeper of the Boscombe Valley estate, was in one of the

 woods \textcolor{green}{picking} flowers. She states that while she was there she

 saw, at the border of the wood and close by the lake, Mr.

 McCarthy and his son, and that they appeared to be having a

 \textcolor{BurntOrange}{violent} \textcolor{red}{quarrel.} She heard Mr. McCarthy the \textcolor{green}{elder} using very

 strong language to his son, and she saw the latter raise up his

 hand as if to \textcolor{red}{strike} his \textcolor{green}{father.} She was so \textcolor{BurntOrange}{frightened} by their

 \textcolor{red}{violence} that she ran away and told her \textcolor{BurntOrange}{mother} when she reached

 home that she had left the two McCarthys \textcolor{red}{quarrelling} near

 Boscombe \textcolor{green}{Pool,} and that she was \textcolor{red}{afraid} that they were going to

 \textcolor{red}{fight.} She had hardly said the \textcolor{green}{words} when \textcolor{BurntOrange}{young} Mr. McCarthy came

 running up to the lodge to say that he had \textcolor{green}{found} his \textcolor{green}{father} dead

 in the wood, and to ask for the help of the lodge-keeper. He was

 much \textcolor{BurntOrange}{excited,} without either his \textcolor{red}{gun} or his hat, and his right

 hand and sleeve were observed to be \textcolor{red}{stained} with fresh blood. On

 following him they \textcolor{green}{found} the dead body stretched out upon the

 grass beside the \textcolor{green}{pool.} The head had been beaten in by repeated

 blows of some heavy and blunt weapon. The \textcolor{red}{injuries} were such as

 might very well have been \textcolor{red}{inflicted} by the butt-end of his son's

 \textcolor{red}{gun,} which was \textcolor{green}{found} \textcolor{red}{lying} on the grass within a few paces of the

 body. Under these circumstances the \textcolor{BurntOrange}{young} man was instantly

 \textcolor{red}{arrested,} and a \textcolor{red}{verdict} of 'wilful \textcolor{BurntOrange}{murder'} having been returned

 at the inquest on Tuesday, he was on Wednesday brought before the

 magistrates at Ross, who have referred the \textcolor{red}{case} to the next

 Assizes. Those are the \textcolor{green}{main} \textcolor{green}{facts} of the \textcolor{red}{case} as they came out

 before the \textcolor{red}{coroner} and the police-court."



 "I could hardly imagine a more \textcolor{red}{damning} \textcolor{red}{case,"} I remarked. "If

 ever circumstantial evidence pointed to a \textcolor{red}{criminal} it does so

 here."



 "Circumstantial evidence is a very tricky thing," answered Holmes

 thoughtfully. "It may seem to point very straight to one thing,

 but if you shift your own point of view a little, you may find it

 pointing in an \textcolor{green}{equally} uncompromising manner to something

 entirely different. It must be \textcolor{BurntOrange}{confessed,} however, that the \textcolor{red}{case}

 looks exceedingly \textcolor{red}{grave} against the \textcolor{BurntOrange}{young} man, and it is very

 possible that he is indeed the \textcolor{red}{culprit.} There are several people

 in the neighbourhood, however, and among them Miss Turner, the

 \textcolor{green}{daughter} of the neighbouring landowner, who believe in his

 \textcolor{green}{innocence,} and who have \textcolor{green}{retained} Lestrade, whom you may recollect

 in connection with the \textcolor{green}{Study} in Scarlet, to work out the \textcolor{red}{case} in

 his \textcolor{green}{interest.} Lestrade, being rather puzzled, has referred the

 \textcolor{red}{case} to me, and hence it is that two middle-aged \textcolor{green}{gentlemen} are

 flying westward at fifty miles an hour instead of quietly

 digesting their \textcolor{green}{breakfasts} at home."



 "I am \textcolor{red}{afraid,"} said I, "that the \textcolor{green}{facts} are so \textcolor{green}{obvious} that you

 will find little \textcolor{green}{credit} to be \textcolor{BurntOrange}{gained} out of this \textcolor{red}{case."}



 "There is nothing more \textcolor{red}{deceptive} than an \textcolor{green}{obvious} \textcolor{green}{fact,"} he

 answered, \textcolor{BurntOrange}{laughing.} "Besides, we may \textcolor{blue}{chance} to \textcolor{red}{hit} upon some

 other \textcolor{green}{obvious} \textcolor{green}{facts} which may have been by no means \textcolor{green}{obvious} to

 Mr. Lestrade. You know me too well to think that I am \textcolor{red}{boasting}

 when I say that I shall either confirm or destroy his \textcolor{BurntOrange}{theory} by

 means which he is quite incapable of \textcolor{green}{employing,} or even of

 understanding. To take the first example to hand, I very clearly

 \textcolor{green}{perceive} that in your bedroom the window is upon the right-hand

 side, and yet I \textcolor{green}{question} whether Mr. Lestrade would have noted

 even so self-evident a thing as that."



 "How on earth--"



 "My \textcolor{green}{dear} \textcolor{green}{fellow,} I know you well. I know the \textcolor{red}{military} neatness

 which characterises you. You shave every morning, and in this

 season you shave by the sunlight; but since your shaving is less

 and less complete as we get farther back on the left side, until

 it becomes positively slovenly as we get round the angle of the

 jaw, it is surely very clear that that side is less \textcolor{BurntOrange}{illuminated}

 than the other. I could not imagine a man of your habits looking

 at himself in an equal light and being \textcolor{green}{satisfied} with such a

 \textcolor{blue}{result.} I only \textcolor{BurntOrange}{quote} this as a trivial example of observation and

 inference. Therein \textcolor{red}{lies} my métier, and it is just possible that

 it may be of some service in the \textcolor{blue}{investigation} which \textcolor{red}{lies} before

 us. There are one or two minor points which were brought out in

 the inquest, and which are \textcolor{green}{worth} considering."



 "What are they?"



 "It appears that his \textcolor{red}{arrest} did not take place at once, but after

 the return to Hatherley \textcolor{blue}{Farm.} On the \textcolor{green}{inspector} of constabulary

 \textcolor{green}{informing} him that he was a \textcolor{red}{prisoner,} he remarked that he was not

 \textcolor{blue}{surprised} to hear it, and that it was no more than his \textcolor{red}{deserts.}

 This observation of his had the natural effect of \textcolor{red}{removing} any

 traces of \textcolor{BurntOrange}{doubt} which might have remained in the minds of the

 \textcolor{red}{coroner's} \textcolor{green}{jury."}



 "It was a \textcolor{BurntOrange}{confession,"} I ejaculated.



 "No, for it was followed by a protestation of \textcolor{green}{innocence."}



 "Coming on the \textcolor{BurntOrange}{top} of such a \textcolor{red}{damning} \textcolor{green}{series} of events, it was at

 least a most \textcolor{BurntOrange}{suspicious} remark."



 "On the \textcolor{red}{contrary,"} said Holmes, "it is the brightest \textcolor{red}{rift} which I

 can at \textcolor{BurntOrange}{present} see in the clouds. However \textcolor{green}{innocent} he might be,

 he could not be such an \textcolor{green}{absolute} imbecile as not to see that the

 circumstances were very \textcolor{red}{black} against him. Had he appeared

 \textcolor{blue}{surprised} at his own \textcolor{red}{arrest,} or feigned \textcolor{red}{indignation} at it, I

 should have looked upon it as highly \textcolor{BurntOrange}{suspicious,} because such

 \textcolor{BurntOrange}{surprise} or \textcolor{red}{anger} would not be natural under the circumstances,

 and yet might appear to be the best \textcolor{green}{policy} to a \textcolor{red}{scheming} man. His

 \textcolor{green}{frank} \textcolor{green}{acceptance} of the situation marks him as either an \textcolor{green}{innocent}

 man, or else as a man of \textcolor{green}{considerable} self-restraint and

 \textcolor{green}{firmness.} As to his remark about his \textcolor{red}{deserts,} it was also not

 \textcolor{red}{unnatural} if you consider that he stood beside the dead body of

 his \textcolor{green}{father,} and that there is no \textcolor{BurntOrange}{doubt} that he had that very day

 so far \textcolor{red}{forgotten} his filial duty as to bandy \textcolor{green}{words} with him, and

 even, \textcolor{green}{according} to the little girl whose evidence is so

 \textcolor{green}{important,} to raise his hand as if to \textcolor{red}{strike} him. The

 self-reproach and contrition which are displayed in his remark

 appear to me to be the signs of a \textcolor{green}{healthy} mind rather than of a

 \textcolor{red}{guilty} one."



 I shook my head. "Many men have been hanged on far slighter

 evidence," I remarked.



 "So they have. And many men have been wrongfully hanged."



 "What is the \textcolor{BurntOrange}{young} man's own \textcolor{green}{account} of the matter?"



 "It is, I am \textcolor{red}{afraid,} not very \textcolor{green}{encouraging} to his \textcolor{green}{supporters,}

 though there are one or two points in it which are suggestive.

 You will find it here, and may read it for yourself."



 He picked out from his bundle a \textcolor{red}{copy} of the local Herefordshire

 paper, and having turned down the sheet he pointed out the

 paragraph in which the \textcolor{red}{unfortunate} \textcolor{BurntOrange}{young} man had given his own

 \textcolor{green}{statement} of what had occurred. I settled myself down in the

 corner of the carriage and read it very \textcolor{green}{carefully.} It ran in this

 way:



 "Mr. James McCarthy, the only son of the deceased, was then called

 and gave evidence as follows: 'I had been away from home for

 three days at Bristol, and had only just returned upon the

 morning of last Monday, the 3rd. My \textcolor{green}{father} was \textcolor{red}{absent} from home at

 the \textcolor{blue}{time} of my \textcolor{blue}{arrival,} and I was \textcolor{green}{informed} by the maid that he

 had driven over to Ross with \textcolor{red}{John} Cobb, the groom. \textcolor{blue}{Shortly} after

 my return I heard the wheels of his trap in the yard, and,

 looking out of my window, I saw him get out and walk rapidly out

 of the yard, though I was not aware in which direction he was

 going. I then took my \textcolor{red}{gun} and strolled out in the direction of

 the Boscombe \textcolor{green}{Pool,} with the intention of \textcolor{green}{visiting} the rabbit

 warren which is upon the other side. On my way I saw William

 Crowder, the game-keeper, as he had stated in his evidence; but

 he is \textcolor{red}{mistaken} in thinking that I was following my \textcolor{green}{father.} I had

 no idea that he was in front of me. When about a hundred yards

 from the \textcolor{green}{pool} I heard a \textcolor{red}{cry} of "Cooee!" which was a \textcolor{green}{usual} signal

 between my \textcolor{green}{father} and myself. I then \textcolor{blue}{hurried} \textcolor{green}{forward,} and \textcolor{green}{found}

 him standing by the \textcolor{green}{pool.} He appeared to be much \textcolor{blue}{surprised} at

 seeing me and asked me rather roughly what I was doing there. A

 conversation ensued which \textcolor{green}{led} to high \textcolor{green}{words} and almost to blows,

 for my \textcolor{green}{father} was a man of a very \textcolor{BurntOrange}{violent} temper. Seeing that his

 \textcolor{BurntOrange}{passion} was becoming ungovernable, I left him and returned

 towards Hatherley \textcolor{blue}{Farm.} I had not gone more than 150 yards,

 however, when I heard a \textcolor{red}{hideous} \textcolor{BurntOrange}{outcry} behind me, which caused me

 to run back again. I \textcolor{green}{found} my \textcolor{green}{father} \textcolor{red}{expiring} upon the \textcolor{green}{ground,}

 with his head \textcolor{red}{terribly} \textcolor{red}{injured.} I dropped my \textcolor{red}{gun} and held him in

 my arms, but he almost instantly \textcolor{red}{expired.} I knelt beside him for

 some minutes, and then made my way to Mr. Turner's lodge-keeper,

 his house being the nearest, to ask for \textcolor{green}{assistance.} I saw no one

 near my \textcolor{green}{father} when I returned, and I have no idea how he came by

 his \textcolor{red}{injuries.} He was not a popular man, being somewhat \textcolor{red}{cold} and

 \textcolor{red}{forbidding} in his manners, but he had, as far as I know, no

 active \textcolor{red}{enemies.} I know nothing further of the matter.'



 "The \textcolor{red}{Coroner:} Did your \textcolor{green}{father} make any \textcolor{green}{statement} to you before

 he \textcolor{red}{died?}



 \textcolor{green}{"Witness:} He \textcolor{red}{mumbled} a few \textcolor{green}{words,} but I could only \textcolor{blue}{catch} some

 allusion to a \textcolor{red}{rat.}



 "The \textcolor{red}{Coroner:} What did you understand by that?



 \textcolor{green}{"Witness:} It conveyed no meaning to me. I \textcolor{blue}{thought} that he was

 \textcolor{red}{delirious.}



 "The \textcolor{red}{Coroner:} What was the point upon which you and your \textcolor{green}{father}

 had this final \textcolor{red}{quarrel?}



 \textcolor{green}{"Witness:} I should \textcolor{green}{prefer} not to answer.



 "The \textcolor{red}{Coroner:} I am \textcolor{red}{afraid} that I must press it.



 \textcolor{green}{"Witness:} It is really \textcolor{red}{impossible} for me to tell you. I can

 \textcolor{green}{assure} you that it has nothing to do with the sad \textcolor{red}{tragedy} which

 followed.



 "The \textcolor{red}{Coroner:} That is for the \textcolor{BurntOrange}{court} to decide. I need not point

 out to you that your \textcolor{red}{refusal} to answer will \textcolor{red}{prejudice} your \textcolor{red}{case}

 considerably in any future \textcolor{blue}{proceedings} which may arise.



 \textcolor{green}{"Witness:} I must still \textcolor{red}{refuse.}



 "The \textcolor{red}{Coroner:} I understand that the \textcolor{red}{cry} of 'Cooee' was a common

 signal between you and your \textcolor{green}{father?}



 \textcolor{green}{"Witness:} It was.



 "The \textcolor{red}{Coroner:} How was it, then, that he uttered it before he saw

 you, and before he even knew that you had returned from Bristol?



 \textcolor{green}{"Witness} (with \textcolor{green}{considerable} \textcolor{red}{confusion):} I do not know.



 "A Juryman: Did you see nothing which \textcolor{BurntOrange}{aroused} your \textcolor{red}{suspicions}

 when you returned on \textcolor{red}{hearing} the \textcolor{red}{cry} and \textcolor{green}{found} your \textcolor{green}{father}

 fatally \textcolor{red}{injured?}



 \textcolor{green}{"Witness:} Nothing definite.



 "The \textcolor{red}{Coroner:} What do you mean?



 \textcolor{green}{"Witness:} I was so \textcolor{red}{disturbed} and \textcolor{BurntOrange}{excited} as I rushed out into

 the open, that I could think of nothing except of my \textcolor{green}{father.} Yet

 I have a \textcolor{red}{vague} \textcolor{green}{impression} that as I ran \textcolor{green}{forward} something lay

 upon the \textcolor{green}{ground} to the left of me. It seemed to me to be

 something grey in colour, a coat of some sort, or a plaid perhaps.

 When I rose from my \textcolor{green}{father} I looked round for it, but it was

 gone.



 "'Do you mean that it \textcolor{red}{disappeared} before you went for help?'



 "'Yes, it was gone.'



 "'You cannot say what it was?'



 "'No, I had a feeling something was there.'



 "'How far from the body?'



 "'A dozen yards or so.'



 "'And how far from the edge of the wood?'



 "'About the same.'



 "'Then if it was \textcolor{red}{removed} it was while you were within a dozen

 yards of it?'



 "'Yes, but with my back towards it.'



 "This concluded the \textcolor{BurntOrange}{examination} of the \textcolor{green}{witness."}



 "I see," said I as I glanced down the column, "that the \textcolor{red}{coroner}

 in his concluding remarks was rather severe upon \textcolor{BurntOrange}{young} McCarthy.

 He calls \textcolor{green}{attention,} and with \textcolor{green}{reason,} to the discrepancy about his

 \textcolor{green}{father} having signalled to him before seeing him, also to his

 \textcolor{red}{refusal} to give details of his conversation with his \textcolor{green}{father,} and

 his singular \textcolor{green}{account} of his \textcolor{green}{father's} \textcolor{red}{dying} \textcolor{green}{words.} They are all,

 as he remarks, very much against the son."



 Holmes \textcolor{BurntOrange}{laughed} softly to himself and stretched himself out upon

 the \textcolor{green}{cushioned} seat. "Both you and the \textcolor{red}{coroner} have been at some

 \textcolor{red}{pains,"} said he, "to single out the very strongest points in the

 \textcolor{BurntOrange}{young} man's favour. Don't you see that you alternately give him

 \textcolor{green}{credit} for having too much imagination and too little? Too

 little, if he could not invent a cause of \textcolor{red}{quarrel} which would

 give him the \textcolor{BurntOrange}{sympathy} of the \textcolor{green}{jury;} too much, if he evolved from

 his own inner \textcolor{green}{consciousness} anything so outré as a \textcolor{red}{dying}

 reference to a \textcolor{red}{rat,} and the \textcolor{blue}{incident} of the \textcolor{blue}{vanishing} cloth. No,

 \textcolor{green}{sir,} I shall approach this \textcolor{red}{case} from the point of view that what

 this \textcolor{BurntOrange}{young} man says is \textcolor{green}{true,} and we shall see whither that

 \textcolor{blue}{hypothesis} will \textcolor{green}{lead} us. And now here is my pocket Petrarch, and

 not another \textcolor{green}{word} shall I say of this \textcolor{red}{case} until we are on the

 scene of \textcolor{green}{action.} We lunch at Swindon, and I see that we shall be

 there in twenty minutes."



 It was nearly four o'clock when we at last, after passing through

 the \textcolor{green}{beautiful} Stroud Valley, and over the broad gleaming Severn,

 \textcolor{green}{found} ourselves at the \textcolor{BurntOrange}{pretty} little country-town of Ross. A

 lean, ferret-like man, furtive and sly-looking, was \textcolor{BurntOrange}{waiting} for

 us upon the platform. In \textcolor{red}{spite} of the light brown dustcoat and

 leather-leggings which he wore in \textcolor{green}{deference} to his rustic

 surroundings, I had no \textcolor{red}{difficulty} in recognising Lestrade, of

 Scotland Yard. With him we drove to the Hereford Arms where a

 room had already been engaged for us.



 "I have ordered a carriage," said Lestrade as we sat over a cup

 of tea. "I knew your \textcolor{green}{energetic} nature, and that you would not be

 \textcolor{BurntOrange}{happy} until you had been on the scene of the \textcolor{red}{crime."}



 "It was very nice and complimentary of you," Holmes answered. "It

 is entirely a \textcolor{green}{question} of barometric \textcolor{red}{pressure."}



 Lestrade looked \textcolor{BurntOrange}{startled.} "I do not quite follow," he said.



 "How is the glass? Twenty-nine, I see. No wind, and not a cloud

 in the \textcolor{green}{sky.} I have a caseful of \textcolor{red}{cigarettes} here which need

 smoking, and the sofa is very much \textcolor{green}{superior} to the \textcolor{green}{usual} country

 hotel \textcolor{red}{abomination.} I do not think that it is probable that I

 shall use the carriage to-night."



 Lestrade \textcolor{BurntOrange}{laughed} indulgently. "You have, no \textcolor{BurntOrange}{doubt,} already formed

 your conclusions from the newspapers," he said. "The \textcolor{red}{case} is as

 plain as a pikestaff, and the more one goes into it the plainer

 it becomes. Still, of course, one can't \textcolor{red}{refuse} a lady, and such a

 very positive one, too. She has heard of you, and would have your

 opinion, though I repeatedly told her that there was nothing

 which you could do which I had not already done. Why, \textcolor{BurntOrange}{bless} my

 soul! here is her carriage at the door."



 He had hardly spoken before there rushed into the room one of the

 most \textcolor{BurntOrange}{lovely} \textcolor{BurntOrange}{young} women that I have ever seen in my life. Her

 violet eyes shining, her lips parted, a pink \textcolor{green}{flush} upon her

 cheeks, all \textcolor{blue}{thought} of her natural \textcolor{green}{reserve} \textcolor{BurntOrange}{lost} in her

 \textcolor{red}{overpowering} \textcolor{BurntOrange}{excitement} and concern.



 "Oh, Mr. Sherlock Holmes!" she \textcolor{red}{cried,} glancing from one to the

 other of us, and \textcolor{BurntOrange}{finally,} with a woman's quick \textcolor{green}{intuition,}

 fastening upon my \textcolor{green}{companion,} "I am so \textcolor{BurntOrange}{glad} that you have come. I

 have driven down to tell you so. I know that James didn't do it.

 I know it, and I want you to \textcolor{blue}{start} upon your work knowing it,

 too. Never let yourself \textcolor{BurntOrange}{doubt} upon that point. We have known each

 other since we were little \textcolor{BurntOrange}{children,} and I know his \textcolor{red}{faults} as no

 one else does; but he is too tender-hearted to \textcolor{red}{hurt} a fly. Such a

 charge is \textcolor{red}{absurd} to anyone who really knows him."



 "I \textcolor{BurntOrange}{hope} we may clear him, Miss Turner," said Sherlock Holmes.

 "You may rely upon my doing all that I can."



 "But you have read the evidence. You have formed some conclusion?

 Do you not see some loophole, some \textcolor{red}{flaw?} Do you not yourself

 think that he is \textcolor{green}{innocent?"}



 "I think that it is very probable."



 "There, now!" she \textcolor{red}{cried,} throwing back her head and looking

 defiantly at Lestrade. "You hear! He gives me \textcolor{BurntOrange}{hopes."}



 Lestrade shrugged his \textcolor{green}{shoulders.} "I am \textcolor{red}{afraid} that my colleague

 has been a little quick in forming his conclusions," he said.



 "But he is right. Oh! I know that he is right. James never did

 it. And about his \textcolor{red}{quarrel} with his \textcolor{green}{father,} I am sure that the

 \textcolor{green}{reason} why he would not speak about it to the \textcolor{red}{coroner} was because

 I was \textcolor{red}{concerned} in it."



 "In what way?" asked Holmes.



 "It is no \textcolor{blue}{time} for me to \textcolor{red}{hide} anything. James and his \textcolor{green}{father} had

 many \textcolor{red}{disagreements} about me. Mr. McCarthy was very \textcolor{BurntOrange}{anxious} that

 there should be a \textcolor{BurntOrange}{marriage} between us. James and I have always

 \textcolor{green}{loved} each other as \textcolor{green}{brother} and sister; but of course he is \textcolor{BurntOrange}{young}

 and has seen very little of life yet, and--and--well, he

 naturally did not wish to do anything like that yet. So there

 were \textcolor{red}{quarrels,} and this, I am sure, was one of them."



 "And your \textcolor{green}{father?"} asked Holmes. "Was he in favour of such a

 union?"



 "No, he was \textcolor{red}{averse} to it also. No one but Mr. McCarthy was in

 favour of it." A quick \textcolor{red}{blush} passed over her fresh \textcolor{BurntOrange}{young} face as

 Holmes \textcolor{BurntOrange}{shot} one of his keen, \textcolor{green}{questioning} glances at her.



 "Thank you for this \textcolor{green}{information,"} said he. "May I see your \textcolor{green}{father}

 if I call \textcolor{blue}{to-morrow?"}



 "I am \textcolor{red}{afraid} the \textcolor{green}{doctor} \textcolor{blue}{won't} allow it."



 "The \textcolor{green}{doctor?"}



 "Yes, have you not heard? Poor \textcolor{green}{father} has never been strong for

 years back, but this has \textcolor{red}{broken} him down \textcolor{green}{completely.} He has taken

 to his bed, and Dr. Willows says that he is a \textcolor{BurntOrange}{wreck} and that his

 \textcolor{BurntOrange}{nervous} \textcolor{green}{system} is \textcolor{BurntOrange}{shattered.} Mr. McCarthy was the only man \textcolor{BurntOrange}{alive}

 who had known dad in the old days in Victoria."



 "Ha! In Victoria! That is \textcolor{green}{important."}



 "Yes, at the mines."



 "Quite so; at the gold-mines, where, as I understand, Mr. Turner

 made his \textcolor{BurntOrange}{money."}



 "Yes, certainly."



 "Thank you, Miss Turner. You have been of material \textcolor{green}{assistance} to

 me."



 "You will tell me if you have any news \textcolor{blue}{to-morrow.} No \textcolor{BurntOrange}{doubt} you

 will go to the \textcolor{red}{prison} to see James. Oh, if you do, Mr. Holmes, do

 tell him that I know him to be \textcolor{green}{innocent."}



 "I will, Miss Turner."



 "I must go home now, for dad is very \textcolor{red}{ill,} and he misses me so if

 I \textcolor{BurntOrange}{leave} him. Good-bye, and \textcolor{BurntOrange}{God} help you in your \textcolor{blue}{undertaking."} She

 \textcolor{blue}{hurried} from the room as impulsively as she had entered, and we

 heard the wheels of her carriage rattle off down the street.



 "I am \textcolor{red}{ashamed} of you, Holmes," said Lestrade with \textcolor{green}{dignity} after a

 few minutes' silence. "Why should you raise up \textcolor{BurntOrange}{hopes} which you

 are \textcolor{red}{bound} to \textcolor{red}{disappoint?} I am not over-tender of heart, but I

 call it \textcolor{red}{cruel."}



 "I think that I see my way to clearing James McCarthy," said

 Holmes. "Have you an order to see him in \textcolor{red}{prison?"}



 "Yes, but only for you and me."



 "Then I shall reconsider my resolution about going out. We have

 still \textcolor{blue}{time} to take a train to Hereford and see him to-night?"



 "Ample."



 "Then let us do so. Watson, I \textcolor{red}{fear} that you will find it very

 slow, but I shall only be away a couple of hours."



 I walked down to the station with them, and then wandered through

 the streets of the little town, \textcolor{BurntOrange}{finally} returning to the hotel,

 where I lay upon the sofa and tried to \textcolor{green}{interest} myself in a

 yellow-backed novel. The puny plot of the story was so thin,

 however, when compared to the deep \textcolor{blue}{mystery} through which we were

 \textcolor{red}{groping,} and I \textcolor{green}{found} my \textcolor{green}{attention} wander so continually from the

 \textcolor{green}{action} to the \textcolor{green}{fact,} that I at last flung it across the room and

 gave myself up entirely to a consideration of the events of the

 day. Supposing that this \textcolor{red}{unhappy} \textcolor{BurntOrange}{young} man's story were

 absolutely \textcolor{green}{true,} then what \textcolor{red}{hellish} thing, what absolutely

 \textcolor{blue}{unforeseen} and \textcolor{green}{extraordinary} \textcolor{red}{calamity} could have occurred between

 the \textcolor{blue}{time} when he parted from his \textcolor{green}{father,} and the moment when,

 drawn back by his \textcolor{BurntOrange}{screams,} he rushed into the glade? It was

 something \textcolor{red}{terrible} and \textcolor{red}{deadly.} What could it be? Might not the

 nature of the \textcolor{red}{injuries} reveal something to my \textcolor{BurntOrange}{medical} instincts?

 I rang the bell and called for the weekly \textcolor{green}{county} paper, which

 contained a verbatim \textcolor{green}{account} of the inquest. In the surgeon's

 deposition it was stated that the posterior third of the left

 \textcolor{green}{parietal} bone and the left half of the occipital bone had been

 \textcolor{BurntOrange}{shattered} by a heavy blow from a blunt weapon. I \textcolor{green}{marked} the spot

 upon my own head. Clearly such a blow must have been struck from

 behind. That was to some extent in favour of the accused, as when

 seen \textcolor{red}{quarrelling} he was face to face with his \textcolor{green}{father.} Still, it

 did not go for very much, for the older man might have turned his

 back before the blow \textcolor{red}{fell.} Still, it might be \textcolor{green}{worth} while to call

 Holmes' \textcolor{green}{attention} to it. Then there was the peculiar \textcolor{red}{dying}

 reference to a \textcolor{red}{rat.} What could that mean? It could not be

 \textcolor{red}{delirium.} A man \textcolor{red}{dying} from a \textcolor{blue}{sudden} blow does not commonly become

 \textcolor{red}{delirious.} No, it was more likely to be an \textcolor{blue}{attempt} to \textcolor{green}{explain} how

 he met his \textcolor{BurntOrange}{fate.} But what could it indicate? I cudgelled my

 brains to find some possible explanation. And then the \textcolor{blue}{incident}

 of the grey cloth seen by \textcolor{BurntOrange}{young} McCarthy. If that were \textcolor{green}{true} the

 \textcolor{red}{murderer} must have dropped some part of his dress, presumably his

 overcoat, in his flight, and must have had the hardihood to

 return and to carry it away at the instant when the son was

 kneeling with his back turned not a dozen paces off. What a

 tissue of \textcolor{blue}{mysteries} and improbabilities the whole thing was! I

 did not wonder at Lestrade's opinion, and yet I had so much \textcolor{BurntOrange}{faith}

 in Sherlock Holmes' insight that I could not \textcolor{BurntOrange}{lose} \textcolor{BurntOrange}{hope} as \textcolor{blue}{long}

 as every fresh \textcolor{green}{fact} seemed to \textcolor{green}{strengthen} his \textcolor{red}{conviction} of \textcolor{BurntOrange}{young}

 McCarthy's \textcolor{green}{innocence.}



 It was \textcolor{red}{late} before Sherlock Holmes returned. He came back alone,

 for Lestrade was staying in \textcolor{green}{lodgings} in the town.



 "The glass still keeps very high," he remarked as he sat down.

 "It is of \textcolor{BurntOrange}{importance} that it should not rain before we are able

 to go over the \textcolor{green}{ground.} On the other hand, a man should be at his

 very best and keenest for such nice work as that, and I did not

 wish to do it when fagged by a \textcolor{blue}{long} \textcolor{BurntOrange}{journey.} I have seen \textcolor{BurntOrange}{young}

 McCarthy."



 "And what did you \textcolor{green}{learn} from him?"



 "Nothing."



 "Could he throw no light?"



 "None at all. I was inclined to think at one \textcolor{blue}{time} that he knew

 who had done it and was screening him or her, but I am \textcolor{BurntOrange}{convinced}

 now that he is as puzzled as everyone else. He is not a very

 quick-witted \textcolor{BurntOrange}{youth,} though comely to look at and, I should think,

 sound at heart."



 "I cannot \textcolor{green}{admire} his taste," I remarked, "if it is indeed a \textcolor{green}{fact}

 that he was \textcolor{red}{averse} to a \textcolor{BurntOrange}{marriage} with so \textcolor{green}{charming} a \textcolor{BurntOrange}{young} lady as

 this Miss Turner."



 "Ah, thereby hangs a rather \textcolor{red}{painful} \textcolor{green}{tale.} This \textcolor{green}{fellow} is madly,

 insanely, in \textcolor{green}{love} with her, but some two years ago, when he was

 only a lad, and before he really knew her, for she had been away

 five years at a boarding-school, what does the \textcolor{red}{idiot} do but get

 into the clutches of a barmaid in Bristol and \textcolor{BurntOrange}{marry} her at a

 \textcolor{green}{registry} office? No one knows a \textcolor{green}{word} of the matter, but you can

 imagine how \textcolor{red}{maddening} it must be to him to be upbraided for not

 doing what he would give his very eyes to do, but what he knows

 to be absolutely \textcolor{red}{impossible.} It was sheer \textcolor{red}{frenzy} of this sort

 which made him throw his hands up into the air when his \textcolor{green}{father,}

 at their last interview, was goading him on to propose to Miss

 Turner. On the other hand, he had no means of supporting himself,

 and his \textcolor{green}{father,} who was by all \textcolor{green}{accounts} a very hard man, would

 have thrown him over utterly had he known the \textcolor{green}{truth.} It was with

 his barmaid wife that he had \textcolor{red}{spent} the last three days in

 Bristol, and his \textcolor{green}{father} did not know where he was. Mark that

 point. It is of \textcolor{BurntOrange}{importance.} \textcolor{BurntOrange}{Good} has come out of \textcolor{red}{evil,} however,

 for the barmaid, finding from the papers that he is in serious

 trouble and likely to be hanged, has thrown him over utterly and

 has written to him to say that she has a husband already in the

 Bermuda Dockyard, so that there is really no tie between them. I

 think that that bit of news has \textcolor{BurntOrange}{consoled} \textcolor{BurntOrange}{young} McCarthy for all

 that he has \textcolor{red}{suffered."}



 "But if he is \textcolor{green}{innocent,} who has done it?"



 "Ah! who? I would call your \textcolor{green}{attention} very particularly to two

 points. One is that the \textcolor{BurntOrange}{murdered} man had an appointment with

 someone at the \textcolor{green}{pool,} and that the someone could not have been his

 son, for his son was away, and he did not know when he would

 return. The second is that the \textcolor{BurntOrange}{murdered} man was heard to \textcolor{red}{cry}

 'Cooee!' before he knew that his son had returned. Those are the

 \textcolor{green}{crucial} points upon which the \textcolor{red}{case} depends. And now let us \textcolor{green}{talk}

 about George Meredith, if you please, and we shall \textcolor{BurntOrange}{leave} all

 minor matters until \textcolor{blue}{to-morrow."}



 There was no rain, as Holmes had foretold, and the morning \textcolor{red}{broke}

 bright and cloudless. At nine o'clock Lestrade called for us with

 the carriage, and we set off for Hatherley \textcolor{blue}{Farm} and the Boscombe

 \textcolor{green}{Pool.}



 "There is serious news this morning," Lestrade observed. "It is

 said that Mr. Turner, of the Hall, is so \textcolor{red}{ill} that his life is

 \textcolor{red}{despaired} of."



 "An elderly man, I presume?" said Holmes.



 "About sixty; but his constitution has been \textcolor{BurntOrange}{shattered} by his life

 abroad, and he has been in failing health for some \textcolor{blue}{time.} This

 business has had a very \textcolor{red}{bad} effect upon him. He was an old \textcolor{green}{friend}

 of McCarthy's, and, I may add, a great \textcolor{green}{benefactor} to him, for I

 have \textcolor{green}{learned} that he gave him Hatherley \textcolor{blue}{Farm} rent free."



 "Indeed! That is \textcolor{green}{interesting,"} said Holmes.



 "Oh, yes! In a hundred other ways he has helped him. Everybody

 about here speaks of his \textcolor{green}{kindness} to him."



 "Really! Does it not \textcolor{red}{strike} you as a little singular that this

 McCarthy, who appears to have had little of his own, and to have

 been under such obligations to Turner, should still \textcolor{green}{talk} of

 \textcolor{BurntOrange}{marrying} his son to Turner's \textcolor{green}{daughter,} who is, presumably,

 heiress to the estate, and that in such a very cocksure manner,

 as if it were merely a \textcolor{red}{case} of a proposal and all else would

 follow? It is the more strange, since we know that Turner himself

 was \textcolor{red}{averse} to the idea. The \textcolor{green}{daughter} told us as much. Do you not

 deduce something from that?"



 "We have got to the deductions and the inferences," said

 Lestrade, winking at me. "I find it hard enough to \textcolor{BurntOrange}{tackle} \textcolor{green}{facts,}

 Holmes, without flying away after \textcolor{BurntOrange}{theories} and \textcolor{BurntOrange}{fancies."}



 "You are right," said Holmes demurely; "you do find it very hard

 to \textcolor{BurntOrange}{tackle} the \textcolor{green}{facts."}



 "Anyhow, I have grasped one \textcolor{green}{fact} which you seem to find it

 \textcolor{red}{difficult} to get hold of," replied Lestrade with some warmth.



 "And that is--"



 "That McCarthy senior met his \textcolor{BurntOrange}{death} from McCarthy junior and that

 all \textcolor{BurntOrange}{theories} to the \textcolor{red}{contrary} are the merest moonshine."



 "Well, moonshine is a brighter thing than fog," said Holmes,

 \textcolor{BurntOrange}{laughing.} "But I am very much \textcolor{red}{mistaken} if this is not Hatherley

 \textcolor{blue}{Farm} upon the left."



 "Yes, that is it." It was a \textcolor{green}{widespread,} comfortable-looking

 \textcolor{green}{building,} two-storied, slate-roofed, with great yellow blotches

 of lichen upon the grey walls. The drawn \textcolor{red}{blinds} and the smokeless

 chimneys, however, gave it a \textcolor{red}{stricken} look, as though the \textcolor{BurntOrange}{weight}

 of this \textcolor{BurntOrange}{horror} still lay heavy upon it. We called at the door,

 when the maid, at Holmes' request, \textcolor{green}{showed} us the boots which her

 \textcolor{green}{master} wore at the \textcolor{blue}{time} of his \textcolor{BurntOrange}{death,} and also a pair of the

 son's, though not the pair which he had then had. Having \textcolor{green}{measured}

 these very \textcolor{green}{carefully} from seven or eight different points, Holmes

 desired to be \textcolor{green}{led} to the court-yard, from which we all followed

 the winding \textcolor{blue}{track} which \textcolor{green}{led} to Boscombe \textcolor{green}{Pool.}



 Sherlock Holmes was transformed when he was \textcolor{red}{hot} upon such a scent

 as this. Men who had only known the \textcolor{BurntOrange}{quiet} \textcolor{green}{thinker} and logician of

 Baker Street would have failed to recognise him. His face \textcolor{green}{flushed}

 and \textcolor{red}{darkened.} His brows were drawn into two hard \textcolor{red}{black} lines,

 while his eyes shone out from beneath them with a steely \textcolor{BurntOrange}{glitter.}

 His face was bent downward, his \textcolor{green}{shoulders} bowed, his lips

 \textcolor{red}{compressed,} and the veins stood out like whipcord in his \textcolor{blue}{long,}

 sinewy neck. His nostrils seemed to dilate with a \textcolor{green}{purely} animal

 \textcolor{BurntOrange}{lust} for the \textcolor{red}{chase,} and his mind was so absolutely concentrated

 upon the matter before him that a \textcolor{green}{question} or remark \textcolor{red}{fell}

 unheeded upon his ears, or, at the most, only provoked a quick,

 \textcolor{BurntOrange}{impatient} \textcolor{red}{snarl} in reply. Swiftly and silently he made his way

 along the \textcolor{blue}{track} which ran through the \textcolor{green}{meadows,} and so by way of

 the woods to the Boscombe \textcolor{green}{Pool.} It was damp, marshy \textcolor{green}{ground,} as is

 all that district, and there were marks of many feet, both upon

 the path and amid the short grass which \textcolor{red}{bounded} it on either

 side. Sometimes Holmes would \textcolor{blue}{hurry} on, sometimes stop dead, and

 once he made quite a little detour into the \textcolor{green}{meadow.} Lestrade and

 I walked behind him, the detective indifferent and \textcolor{red}{contemptuous,}

 while I \textcolor{BurntOrange}{watched} my \textcolor{green}{friend} with the \textcolor{green}{interest} which sprang from the

 \textcolor{red}{conviction} that every one of his \textcolor{green}{actions} was directed towards a

 definite end.



 The Boscombe \textcolor{green}{Pool,} which is a little reed-girt sheet of water

 some fifty yards across, is situated at the boundary between the

 Hatherley \textcolor{blue}{Farm} and the private park of the wealthy Mr. Turner.

 Above the woods which lined it upon the farther side we could see

 the red, jutting \textcolor{green}{pinnacles} which \textcolor{green}{marked} the site of the rich

 landowner's dwelling. On the Hatherley side of the \textcolor{green}{pool} the woods

 \textcolor{BurntOrange}{grew} very thick, and there was a narrow \textcolor{red}{belt} of sodden grass

 twenty paces across between the edge of the \textcolor{BurntOrange}{trees} and the reeds

 which lined the lake. Lestrade \textcolor{green}{showed} us the exact spot at which

 the body had been \textcolor{green}{found,} and, indeed, so moist was the \textcolor{green}{ground,}

 that I could plainly see the traces which had been left by the

 \textcolor{red}{fall} of the \textcolor{red}{stricken} man. To Holmes, as I could see by his \textcolor{BurntOrange}{eager}

 face and peering eyes, very many other things were to be read

 upon the trampled grass. He ran round, like a dog who is \textcolor{green}{picking}

 up a scent, and then turned upon my \textcolor{green}{companion.}



 "What did you go into the \textcolor{green}{pool} for?" he asked.



 "I fished about with a rake. I \textcolor{blue}{thought} there might be some weapon

 or other trace. But how on earth--"



 "Oh, tut, tut! I have no \textcolor{blue}{time!} That left foot of yours with its

 inward twist is all over the place. A mole could trace it, and

 there it vanishes among the reeds. Oh, how simple it would all

 have been had I been here before they came like a herd of buffalo

 and wallowed all over it. Here is where the party with the

 lodge-keeper came, and they have \textcolor{green}{covered} all \textcolor{blue}{tracks} for six or

 eight feet round the body. But here are three separate \textcolor{blue}{tracks} of

 the same feet." He drew out a lens and lay down upon his

 \textcolor{green}{waterproof} to have a better view, \textcolor{green}{talking} all the \textcolor{blue}{time} rather to

 himself than to us. "These are \textcolor{BurntOrange}{young} McCarthy's feet. Twice he

 was walking, and once he ran swiftly, so that the soles are

 deeply \textcolor{green}{marked} and the \textcolor{red}{heels} hardly visible. That \textcolor{red}{bears} out his

 story. He ran when he saw his \textcolor{green}{father} on the \textcolor{green}{ground.} Then here are

 the \textcolor{green}{father's} feet as he paced up and down. What is this, then? It

 is the butt-end of the \textcolor{red}{gun} as the son stood listening. And this?

 Ha, ha! What have we here? Tiptoes! tiptoes! Square, too, quite

 unusual boots! They come, they go, they come again--of course

 that was for the cloak. Now where did they come from?" He ran up

 and down, sometimes \textcolor{BurntOrange}{losing,} sometimes finding the \textcolor{blue}{track} until we

 were well within the edge of the wood and under the shadow of a

 great beech, the largest \textcolor{BurntOrange}{tree} in the neighbourhood. Holmes traced

 his way to the farther side of this and lay down once more upon

 his face with a little \textcolor{red}{cry} of satisfaction. For a \textcolor{blue}{long} \textcolor{blue}{time} he

 remained there, turning over the leaves and dried sticks,

 gathering up what seemed to me to be \textcolor{red}{dust} into an envelope and

 examining with his lens not only the \textcolor{green}{ground} but even the \textcolor{red}{bark} of

 the \textcolor{BurntOrange}{tree} as far as he could reach. A jagged \textcolor{red}{stone} was \textcolor{red}{lying} among

 the moss, and this also he \textcolor{green}{carefully} examined and \textcolor{green}{retained.} Then

 he followed a pathway through the wood until he came to the

 highroad, where all traces were \textcolor{BurntOrange}{lost.}



 "It has been a \textcolor{red}{case} of \textcolor{green}{considerable} \textcolor{green}{interest,"} he remarked,

 returning to his natural manner. "I \textcolor{BurntOrange}{fancy} that this grey house on

 the right must be the lodge. I think that I will go in and have a

 \textcolor{green}{word} with Moran, and perhaps write a little note. Having done

 that, we may drive back to our luncheon. You may walk to the \textcolor{green}{cab,}

 and I shall be with you presently."



 It was about ten minutes before we regained our \textcolor{green}{cab} and drove

 back into Ross, Holmes still carrying with him the \textcolor{red}{stone} which he

 had picked up in the wood.



 "This may \textcolor{green}{interest} you, Lestrade," he remarked, holding it out.

 "The \textcolor{BurntOrange}{murder} was done with it."



 "I see no marks."



 "There are none."



 "How do you know, then?"



 "The grass was \textcolor{BurntOrange}{growing} under it. It had only lain there a few

 days. There was no sign of a place whence it had been taken. It

 corresponds with the \textcolor{red}{injuries.} There is no sign of any other

 weapon."



 "And the \textcolor{red}{murderer?"}



 "Is a tall man, left-handed, \textcolor{red}{limps} with the right leg, \textcolor{BurntOrange}{wears}

 thick-soled shooting-boots and a grey cloak, smokes Indian

 cigars, uses a cigar-holder, and carries a blunt pen-knife in his

 pocket. There are several other indications, but these may be

 enough to \textcolor{green}{aid} us in our search."



 Lestrade \textcolor{BurntOrange}{laughed.} "I am \textcolor{red}{afraid} that I am still a sceptic," he

 said. \textcolor{BurntOrange}{"Theories} are all very well, but we have to \textcolor{BurntOrange}{deal} with a

 hard-headed British \textcolor{green}{jury."}



 "Nous verrons," answered Holmes calmly. "You work your own

 method, and I shall work mine. I shall be busy this afternoon,

 and shall probably return to London by the evening train."



 "And \textcolor{BurntOrange}{leave} your \textcolor{red}{case} \textcolor{red}{unfinished?"}



 "No, finished."



 "But the \textcolor{blue}{mystery?"}



 "It is solved."



 "Who was the \textcolor{red}{criminal,} then?"



 "The \textcolor{green}{gentleman} I describe."



 "But who is he?"



 "Surely it would not be \textcolor{red}{difficult} to find out. This is not such a

 populous neighbourhood."



 Lestrade shrugged his \textcolor{green}{shoulders.} "I am a practical man," he said,

 "and I really cannot undertake to go about the country looking

 for a left-handed \textcolor{green}{gentleman} with a game leg. I should become the

 laughing-stock of Scotland Yard."



 "All right," said Holmes quietly. "I have given you the \textcolor{blue}{chance.}

 Here are your \textcolor{green}{lodgings.} Good-bye. I shall drop you a line before

 I \textcolor{BurntOrange}{leave."}



 Having left Lestrade at his rooms, we drove to our hotel, where

 we \textcolor{green}{found} lunch upon the table. Holmes was silent and \textcolor{red}{buried} in

 \textcolor{blue}{thought} with a \textcolor{red}{pained} expression upon his face, as one who finds

 himself in a perplexing position.



 "Look here, Watson," he said when the cloth was cleared "just sit

 down in this chair and let me preach to you for a little. I don't

 know quite what to do, and I should value your \textcolor{green}{advice.} Light a

 cigar and let me expound."



 \textcolor{BurntOrange}{"Pray} do so."



 "Well, now, in considering this \textcolor{red}{case} there are two points about

 \textcolor{BurntOrange}{young} McCarthy's narrative which struck us both instantly,

 although they impressed me in his favour and you against him. One

 was the \textcolor{green}{fact} that his \textcolor{green}{father} should, \textcolor{green}{according} to his \textcolor{green}{account,}

 \textcolor{red}{cry} 'Cooee!' before seeing him. The other was his singular \textcolor{red}{dying}

 reference to a \textcolor{red}{rat.} He \textcolor{red}{mumbled} several \textcolor{green}{words,} you understand, but

 that was all that caught the son's ear. Now from this double

 point our research must commence, and we will begin it by

 presuming that what the lad says is absolutely \textcolor{green}{true."}



 "What of this 'Cooee!' then?"



 "Well, obviously it could not have been meant for the son. The

 son, as far as he knew, was in Bristol. It was mere \textcolor{blue}{chance} that

 he was within earshot. The 'Cooee!' was meant to attract the

 \textcolor{green}{attention} of whoever it was that he had the appointment with. But

 'Cooee' is a distinctly Australian \textcolor{red}{cry,} and one which is used

 between Australians. There is a strong \textcolor{green}{presumption} that the

 person whom McCarthy \textcolor{BurntOrange}{expected} to meet him at Boscombe \textcolor{green}{Pool} was

 someone who had been in Australia."



 "What of the \textcolor{red}{rat,} then?"



 Sherlock Holmes took a folded paper from his pocket and flattened

 it out on the table. "This is a map of the Colony of Victoria,"

 he said. "I wired to Bristol for it last night." He put his hand

 over part of the map. "What do you read?"



 "ARAT," I read.



 "And now?" He raised his hand.



 "BALLARAT."



 "Quite so. That was the \textcolor{green}{word} the man uttered, and of which his

 son only caught the last two syllables. He was trying to utter

 the name of his \textcolor{red}{murderer.} So and so, of Ballarat."



 "It is \textcolor{BurntOrange}{wonderful!"} I \textcolor{blue}{exclaimed.}



 "It is \textcolor{green}{obvious.} And now, you see, I had narrowed the field down

 considerably. The \textcolor{red}{possession} of a grey garment was a third point

 which, \textcolor{BurntOrange}{granting} the son's \textcolor{green}{statement} to be correct, was a

 \textcolor{green}{certainty.} We have come now out of mere \textcolor{red}{vagueness} to the definite

 conception of an Australian from Ballarat with a grey cloak."



 "Certainly."



 "And one who was at home in the district, for the \textcolor{green}{pool} can only

 be approached by the \textcolor{blue}{farm} or by the estate, where \textcolor{red}{strangers} could

 hardly wander."



 "Quite so."



 "Then comes our \textcolor{BurntOrange}{expedition} of to-day. By an \textcolor{BurntOrange}{examination} of the

 \textcolor{green}{ground} I \textcolor{BurntOrange}{gained} the \textcolor{red}{trifling} details which I gave to that

 imbecile Lestrade, as to the personality of the \textcolor{red}{criminal."}



 "But how did you \textcolor{BurntOrange}{gain} them?"



 "You know my method. It is \textcolor{green}{founded} upon the observation of

 \textcolor{red}{trifles."}



 "His height I know that you might roughly judge from the length

 of his stride. His boots, too, might be told from their traces."



 "Yes, they were peculiar boots."



 "But his lameness?"



 "The \textcolor{green}{impression} of his right foot was always less distinct than

 his left. He put less \textcolor{BurntOrange}{weight} upon it. Why? Because he limped--he

 was lame."



 "But his left-handedness."



 "You were yourself struck by the nature of the \textcolor{red}{injury} as recorded

 by the surgeon at the inquest. The blow was struck from

 \textcolor{BurntOrange}{immediately} behind, and yet was upon the left side. Now, how can

 that be unless it were by a left-handed man? He had stood behind

 that \textcolor{BurntOrange}{tree} during the interview between the \textcolor{green}{father} and son. He had

 even smoked there. I \textcolor{green}{found} the \textcolor{red}{ash} of a cigar, which my \textcolor{green}{special}

 \textcolor{green}{knowledge} of \textcolor{red}{tobacco} \textcolor{red}{ashes} enables me to pronounce as an Indian

 cigar. I have, as you know, devoted some \textcolor{green}{attention} to this, and

 written a little monograph on the \textcolor{red}{ashes} of 140 different

 varieties of pipe, cigar, and \textcolor{red}{cigarette} \textcolor{red}{tobacco.} Having \textcolor{green}{found} the

 \textcolor{red}{ash,} I then looked round and discovered the stump among the moss

 where he had tossed it. It was an Indian cigar, of the variety

 which are rolled in Rotterdam."



 "And the cigar-holder?"



 "I could see that the end had not been in his \textcolor{blue}{mouth.} Therefore he

 used a holder. The tip had been cut off, not bitten off, but the

 cut was not a \textcolor{green}{clean} one, so I deduced a blunt pen-knife."



 "Holmes," I said, "you have drawn a net round this man from which

 he cannot \textcolor{BurntOrange}{escape,} and you have \textcolor{green}{saved} an \textcolor{green}{innocent} human life as

 truly as if you had cut the cord which was hanging him. I see the

 direction in which all this points. The \textcolor{red}{culprit} is--"



 "Mr. \textcolor{red}{John} Turner," \textcolor{red}{cried} the hotel waiter, opening the door of

 our sitting-room, and \textcolor{green}{ushering} in a \textcolor{BurntOrange}{visitor.}



 The man who entered was a strange and impressive figure. His

 slow, \textcolor{red}{limping} step and bowed \textcolor{green}{shoulders} gave the appearance of

 decrepitude, and yet his hard, deep-lined, craggy \textcolor{green}{features,} and

 his enormous limbs \textcolor{green}{showed} that he was \textcolor{BurntOrange}{possessed} of unusual

 \textcolor{green}{strength} of body and of character. His tangled beard, grizzled

 hair, and \textcolor{BurntOrange}{outstanding,} drooping eyebrows combined to give an air

 of \textcolor{green}{dignity} and power to his appearance, but his face was of an

 ashen \textcolor{BurntOrange}{white,} while his lips and the corners of his nostrils were

 tinged with a shade of \textcolor{red}{blue.} It was clear to me at a glance that

 he was in the grip of some \textcolor{red}{deadly} and \textcolor{red}{chronic} \textcolor{red}{disease.}



 \textcolor{BurntOrange}{"Pray} sit down on the sofa," said Holmes gently. "You had my

 note?"



 "Yes, the lodge-keeper brought it up. You said that you wished to

 see me here to \textcolor{red}{avoid} \textcolor{red}{scandal."}



 "I \textcolor{blue}{thought} people would \textcolor{green}{talk} if I went to the Hall."



 "And why did you wish to see me?" He looked across at my

 \textcolor{green}{companion} with \textcolor{red}{despair} in his \textcolor{red}{weary} eyes, as though his \textcolor{green}{question}

 was already answered.



 "Yes," said Holmes, answering the look rather than the \textcolor{green}{words.} "It

 is so. I know all about McCarthy."



 The old man sank his face in his hands. \textcolor{BurntOrange}{"God} help me!" he \textcolor{red}{cried.}

 "But I would not have let the \textcolor{BurntOrange}{young} man come to \textcolor{red}{harm.} I give you

 my \textcolor{green}{word} that I would have spoken out if it went against him at

 the Assizes."



 "I am \textcolor{BurntOrange}{glad} to hear you say so," said Holmes gravely.



 "I would have spoken now had it not been for my \textcolor{green}{dear} girl. It

 would \textcolor{blue}{break} her heart--it will \textcolor{blue}{break} her heart when she hears

 that I am \textcolor{red}{arrested."}



 "It may not come to that," said Holmes.



 "What?"



 "I am no \textcolor{green}{official} agent. I understand that it was your \textcolor{green}{daughter}

 who required my \textcolor{green}{presence} here, and I am acting in her \textcolor{green}{interests.}

 \textcolor{BurntOrange}{Young} McCarthy must be got off, however."



 "I am a \textcolor{red}{dying} man," said old Turner. "I have had diabetes for

 years. My \textcolor{green}{doctor} says it is a \textcolor{green}{question} whether I shall live a

 month. Yet I would rather \textcolor{red}{die} under my own roof than in a \textcolor{red}{gaol."}



 Holmes rose and sat down at the table with his pen in his hand

 and a bundle of paper before him. "Just tell us the \textcolor{green}{truth,"} he

 said. "I shall jot down the \textcolor{green}{facts.} You will sign it, and Watson

 here can \textcolor{green}{witness} it. Then I could produce your \textcolor{BurntOrange}{confession} at the

 last \textcolor{red}{extremity} to \textcolor{green}{save} \textcolor{BurntOrange}{young} McCarthy. I \textcolor{green}{promise} you that I shall

 not use it unless it is absolutely needed."



 "It's as well," said the old man; "it's a \textcolor{green}{question} whether I

 shall live to the Assizes, so it matters little to me, but I

 should wish to spare Alice the \textcolor{BurntOrange}{shock.} And now I will make the

 thing clear to you; it has been a \textcolor{blue}{long} \textcolor{blue}{time} in the acting, but

 will not take me \textcolor{blue}{long} to tell.



 "You didn't know this dead man, McCarthy. He was a \textcolor{BurntOrange}{devil}

 incarnate. I tell you that. \textcolor{BurntOrange}{God} keep you out of the clutches of

 such a man as he. His grip has been upon me these twenty years,

 and he has \textcolor{BurntOrange}{blasted} my life. \textcolor{red}{I'll} tell you first how I came to be

 in his power.



 "It was in the early '60's at the diggings. I was a \textcolor{BurntOrange}{young} chap

 then, hot-blooded and \textcolor{red}{reckless,} \textcolor{blue}{ready} to turn my hand at

 anything; I got among \textcolor{red}{bad} \textcolor{green}{companions,} took to drink, had no \textcolor{BurntOrange}{luck}

 with my claim, took to the bush, and in a \textcolor{green}{word} became what you

 would call over here a highway \textcolor{red}{robber.} There were six of us, and

 we had a \textcolor{BurntOrange}{wild,} free life of it, sticking up a station from \textcolor{blue}{time}

 to \textcolor{blue}{time,} or stopping the wagons on the road to the diggings.

 \textcolor{red}{Black} Jack of Ballarat was the name I went under, and our party

 is still remembered in the colony as the Ballarat \textcolor{red}{Gang.}



 "One day a \textcolor{green}{gold} convoy came down from Ballarat to Melbourne, and

 we lay in \textcolor{BurntOrange}{wait} for it and \textcolor{red}{attacked} it. There were six troopers

 and six of us, so it was a close thing, but we emptied four of

 their saddles at the first volley. Three of our \textcolor{red}{boys} were \textcolor{red}{killed,}

 however, before we got the swag. I put my \textcolor{red}{pistol} to the head of

 the wagon-driver, who was this very man McCarthy. I wish to the

 \textcolor{BurntOrange}{Lord} that I had \textcolor{BurntOrange}{shot} him then, but I spared him, though I saw his

 \textcolor{red}{wicked} little eyes fixed on my face, as though to remember every

 \textcolor{green}{feature.} We got away with the \textcolor{green}{gold,} became wealthy men, and made

 our way over to England without being \textcolor{red}{suspected.} There I parted

 from my old pals and determined to settle down to a \textcolor{BurntOrange}{quiet} and

 \textcolor{green}{respectable} life. I bought this estate, which \textcolor{blue}{chanced} to be in

 the market, and I set myself to do a little \textcolor{BurntOrange}{good} with my \textcolor{BurntOrange}{money,}

 to make up for the way in which I had \textcolor{green}{earned} it. I married, too,

 and though my wife \textcolor{red}{died} \textcolor{BurntOrange}{young} she left me my \textcolor{green}{dear} little Alice.

 Even when she was just a \textcolor{green}{baby} her wee hand seemed to \textcolor{green}{lead} me down

 the right path as nothing else had ever done. In a \textcolor{green}{word,} I turned

 over a new leaf and did my best to make up for the past. All was

 going well when McCarthy laid his grip upon me.



 "I had gone up to town about an investment, and I met him in

 \textcolor{green}{Regent} Street with hardly a coat to his back or a boot to his

 foot.



 "'Here we are, Jack,' says he, touching me on the arm; 'we'll be

 as \textcolor{BurntOrange}{good} as a family to you. There's two of us, me and my son, and

 you can have the keeping of us. If you don't--it's a fine,

 law-abiding country is England, and there's always a \textcolor{BurntOrange}{policeman}

 within \textcolor{BurntOrange}{hail.'}



 "Well, down they came to the west country, there was no shaking

 them off, and there they have lived rent free on my best \textcolor{green}{land}

 ever since. There was no \textcolor{green}{rest} for me, no \textcolor{BurntOrange}{peace,} no forgetfulness;

 turn where I would, there was his \textcolor{BurntOrange}{cunning,} \textcolor{BurntOrange}{grinning} face at my

 \textcolor{red}{elbow.} It \textcolor{BurntOrange}{grew} \textcolor{red}{worse} as Alice \textcolor{BurntOrange}{grew} up, for he soon saw I was more

 \textcolor{red}{afraid} of her knowing my past than of the \textcolor{BurntOrange}{police.} Whatever he

 wanted he must have, and whatever it was I gave him without

 \textcolor{green}{question,} \textcolor{green}{land,} \textcolor{BurntOrange}{money,} houses, until at last he asked a thing

 which I could not give. He asked for Alice.



 "His son, you see, had grown up, and so had my girl, and as I was

 known to be in weak health, it seemed a fine \textcolor{red}{stroke} to him that

 his lad should step into the whole property. But there I was

 firm. I would not have his \textcolor{red}{cursed} stock mixed with mine; not that

 I had any \textcolor{red}{dislike} to the lad, but his blood was in him, and that

 was enough. I stood firm. McCarthy \textcolor{BurntOrange}{threatened.} I braved him to do

 his \textcolor{red}{worst.} We were to meet at the \textcolor{green}{pool} midway between our houses

 to \textcolor{green}{talk} it over.



 "When I went down there I \textcolor{green}{found} him \textcolor{green}{talking} with his son, so I

 smoked a cigar and \textcolor{BurntOrange}{waited} behind a \textcolor{BurntOrange}{tree} until he should be alone.

 But as I listened to his \textcolor{green}{talk} all that was \textcolor{red}{black} and bitter in

 me seemed to come uppermost. He was urging his son to \textcolor{BurntOrange}{marry} my

 \textcolor{green}{daughter} with as little regard for what she might think as if she

 were a \textcolor{red}{slut} from off the streets. It drove me \textcolor{red}{mad} to think that I

 and all that I held most \textcolor{green}{dear} should be in the power of such a

 man as this. Could I not snap the bond? I was already a \textcolor{red}{dying} and

 a \textcolor{red}{desperate} man. Though clear of mind and \textcolor{green}{fairly} strong of limb,

 I knew that my own \textcolor{BurntOrange}{fate} was \textcolor{green}{sealed.} But my memory and my girl!

 Both could be \textcolor{green}{saved} if I could but silence that \textcolor{red}{foul} tongue. I

 did it, Mr. Holmes. I would do it again. Deeply as I have \textcolor{red}{sinned,}

 I have \textcolor{green}{led} a life of \textcolor{red}{martyrdom} to \textcolor{BurntOrange}{atone} for it. But that my girl

 should be entangled in the same meshes which held me was more

 than I could \textcolor{red}{suffer.} I struck him down with no more compunction

 than if he had been some \textcolor{red}{foul} and \textcolor{red}{venomous} \textcolor{red}{beast.} His \textcolor{red}{cry} brought

 back his son; but I had \textcolor{BurntOrange}{gained} the \textcolor{green}{cover} of the wood, though I

 was \textcolor{red}{forced} to go back to fetch the cloak which I had dropped in

 my flight. That is the \textcolor{green}{true} story, \textcolor{green}{gentlemen,} of all that

 occurred."



 "Well, it is not for me to judge you," said Holmes as the old man

 signed the \textcolor{green}{statement} which had been drawn out. "I \textcolor{BurntOrange}{pray} that we

 may never be \textcolor{BurntOrange}{exposed} to such a \textcolor{red}{temptation."}



 "I \textcolor{BurntOrange}{pray} not, \textcolor{green}{sir.} And what do you \textcolor{green}{intend} to do?"



 "In view of your health, nothing. You are yourself aware that you

 will soon have to answer for your \textcolor{green}{deed} at a higher \textcolor{BurntOrange}{court} than the

 Assizes. I will keep your \textcolor{BurntOrange}{confession,} and if McCarthy is

 \textcolor{red}{condemned} I shall be \textcolor{red}{forced} to use it. If not, it shall never be

 seen by \textcolor{red}{mortal} eye; and your \textcolor{green}{secret,} whether you be \textcolor{BurntOrange}{alive} or

 dead, shall be \textcolor{green}{safe} with us."



 "Farewell, then," said the old man solemnly. "Your own deathbeds,

 when they come, will be the easier for the \textcolor{blue}{thought} of the \textcolor{BurntOrange}{peace}

 which you have given to mine." Tottering and shaking in all his

 \textcolor{red}{giant} frame, he \textcolor{red}{stumbled} slowly from the room.



 \textcolor{BurntOrange}{"God} help us!" said Holmes after a \textcolor{blue}{long} silence. "Why does \textcolor{BurntOrange}{fate}

 play such \textcolor{BurntOrange}{tricks} with poor, \textcolor{red}{helpless} \textcolor{BurntOrange}{worms?} I never hear of such

 a \textcolor{red}{case} as this that I do not think of Baxter's \textcolor{green}{words,} and say,

 'There, but for the \textcolor{green}{grace} of \textcolor{BurntOrange}{God,} goes Sherlock Holmes.'"



 James McCarthy was acquitted at the Assizes on the \textcolor{green}{strength} of a

 number of \textcolor{red}{objections} which had been drawn out by Holmes and

 \textcolor{blue}{submitted} to the \textcolor{BurntOrange}{defending} \textcolor{green}{counsel.} Old Turner lived for seven

 months after our interview, but he is now dead; and there is

 every \textcolor{green}{prospect} that the son and \textcolor{green}{daughter} may come to live \textcolor{green}{happily}

 together in \textcolor{red}{ignorance} of the \textcolor{red}{black} cloud which \textcolor{green}{rests} upon their

 past.







 \textcolor{BurntOrange}{ADVENTURE} V. THE FIVE ORANGE PIPS



 When I glance over my notes and records of the Sherlock Holmes

 \textcolor{red}{cases} between the years '82 and '90, I am faced by so many which

 \textcolor{BurntOrange}{present} strange and \textcolor{green}{interesting} \textcolor{green}{features} that it is no easy

 matter to know which to choose and which to \textcolor{BurntOrange}{leave.} Some, however,

 have already \textcolor{BurntOrange}{gained} publicity through the papers, and others have

 not \textcolor{green}{offered} a field for those peculiar qualities which my \textcolor{green}{friend}

 \textcolor{BurntOrange}{possessed} in so high a \textcolor{green}{degree,} and which it is the object of

 these papers to \textcolor{green}{illustrate.} Some, too, have baffled his

 analytical skill, and would be, as narratives, beginnings without

 an ending, while others have been but partially cleared up, and

 have their explanations \textcolor{green}{founded} rather upon \textcolor{blue}{conjecture} and

 \textcolor{green}{surmise} than on that \textcolor{green}{absolute} \textcolor{green}{logical} \textcolor{green}{proof} which was so \textcolor{green}{dear} to

 him. There is, however, one of these last which was so \textcolor{BurntOrange}{remarkable}

 in its details and so \textcolor{BurntOrange}{startling} in its \textcolor{blue}{results} that I am tempted

 to give some \textcolor{green}{account} of it in \textcolor{red}{spite} of the \textcolor{green}{fact} that there are

 points in connection with it which never have been, and probably

 never will be, entirely cleared up.



 The year '87 furnished us with a \textcolor{blue}{long} \textcolor{green}{series} of \textcolor{red}{cases} of greater

 or less \textcolor{green}{interest,} of which I \textcolor{green}{retain} the records. Among my

 headings under this one twelve months I find an \textcolor{green}{account} of the

 \textcolor{BurntOrange}{adventure} of the Paradol Chamber, of the Amateur Mendicant

 Society, who held a \textcolor{green}{luxurious} club in the lower vault of a

 furniture warehouse, of the \textcolor{green}{facts} connected with the \textcolor{red}{loss} of the

 British barque "Sophy Anderson", of the singular \textcolor{BurntOrange}{adventures} of the

 Grice Patersons in the island of Uffa, and \textcolor{BurntOrange}{finally} of the

 Camberwell \textcolor{red}{poisoning} \textcolor{red}{case.} In the latter, as may be remembered,

 Sherlock Holmes was able, by winding up the dead man's \textcolor{BurntOrange}{watch,} to

 \textcolor{green}{prove} that it had been \textcolor{red}{wound} up two hours before, and that

 therefore the deceased had gone to bed within that time--a

 deduction which was of the greatest \textcolor{BurntOrange}{importance} in clearing up the

 \textcolor{red}{case.} All these I may sketch out at some future date, but none of

 them \textcolor{BurntOrange}{present} such singular \textcolor{green}{features} as the strange train of

 circumstances which I have now taken up my pen to describe.



 It was in the latter days of September, and the equinoctial gales

 had set in with exceptional \textcolor{red}{violence.} All day the wind had

 \textcolor{BurntOrange}{screamed} and the rain had beaten against the windows, so that

 even here in the heart of great, hand-made London we were \textcolor{red}{forced}

 to raise our minds for the instant from the \textcolor{green}{routine} of life and

 to recognise the \textcolor{green}{presence} of those great elemental \textcolor{red}{forces} which

 \textcolor{BurntOrange}{shriek} at mankind through the bars of his civilisation, like

 \textcolor{red}{untamed} \textcolor{red}{beasts} in a \textcolor{red}{cage.} As evening drew in, the \textcolor{red}{storm} \textcolor{BurntOrange}{grew}

 higher and louder, and the wind \textcolor{red}{cried} and sobbed like a \textcolor{BurntOrange}{child} in

 the chimney. Sherlock Holmes sat moodily at one side of the

 fireplace cross-indexing his records of \textcolor{red}{crime,} while I at the

 other was deep in one of Clark Russell's fine sea-stories until

 the \textcolor{BurntOrange}{howl} of the gale from without seemed to blend with the text,

 and the \textcolor{blue}{splash} of the rain to lengthen out into the \textcolor{blue}{long} swash of

 the \textcolor{green}{sea} waves. My wife was on a \textcolor{green}{visit} to her \textcolor{BurntOrange}{mother's,} and for a

 few days I was a dweller once more in my old quarters at Baker

 Street.



 "Why," said I, glancing up at my \textcolor{green}{companion,} "that was surely the

 bell. Who could come to-night? Some \textcolor{green}{friend} of yours, perhaps?"



 "Except yourself I have none," he answered. "I do not \textcolor{green}{encourage}

 \textcolor{BurntOrange}{visitors."}



 "A client, then?"



 "If so, it is a serious \textcolor{red}{case.} Nothing less would bring a man out

 on such a day and at such an hour. But I take it that it is more

 likely to be some crony of the landlady's."



 Sherlock Holmes was \textcolor{red}{wrong} in his \textcolor{blue}{conjecture,} however, for there

 came a step in the passage and a tapping at the door. He

 stretched out his \textcolor{blue}{long} arm to turn the lamp away from himself and

 towards the vacant chair upon which a \textcolor{BurntOrange}{newcomer} must sit.



 "Come in!" said he.



 The man who entered was \textcolor{BurntOrange}{young,} some two-and-twenty at the

 outside, well-groomed and trimly clad, with something of

 \textcolor{green}{refinement} and delicacy in his bearing. The streaming umbrella

 which he held in his hand, and his \textcolor{blue}{long} shining \textcolor{green}{waterproof} told

 of the \textcolor{red}{fierce} weather through which he had come. He looked about

 him anxiously in the \textcolor{red}{glare} of the lamp, and I could see that his

 face was pale and his eyes heavy, like those of a man who is

 \textcolor{BurntOrange}{weighed} down with some great \textcolor{BurntOrange}{anxiety.}



 "I owe you an \textcolor{green}{apology,"} he said, raising his golden pince-nez to

 his eyes. "I \textcolor{green}{trust} that I am not intruding. I \textcolor{red}{fear} that I have

 brought some traces of the \textcolor{red}{storm} and rain into your snug

 chamber."



 "Give me your coat and umbrella," said Holmes. "They may \textcolor{green}{rest}

 here on the hook and will be dry presently. You have come up from

 the south-west, I see."



 "Yes, from Horsham."



 "That clay and chalk mixture which I see upon your toe \textcolor{BurntOrange}{caps} is

 quite distinctive."



 "I have come for \textcolor{green}{advice."}



 "That is easily got."



 "And help."



 "That is not always so easy."



 "I have heard of you, Mr. Holmes. I heard from \textcolor{green}{Major} Prendergast

 how you \textcolor{green}{saved} him in the Tankerville Club \textcolor{red}{scandal."}



 "Ah, of course. He was wrongfully accused of \textcolor{red}{cheating} at cards."



 "He said that you could solve anything."



 "He said too much."



 "That you are never beaten."



 "I have been beaten four times--three \textcolor{blue}{times} by men, and once by a

 woman."



 "But what is that compared with the number of your \textcolor{BurntOrange}{successes?"}



 "It is \textcolor{green}{true} that I have been generally \textcolor{BurntOrange}{successful."}



 "Then you may be so with me."



 "I \textcolor{red}{beg} that you will draw your chair up to the \textcolor{red}{fire} and favour me

 with some details as to your \textcolor{red}{case."}



 "It is no ordinary one."



 "None of those which come to me are. I am the last \textcolor{BurntOrange}{court} of

 \textcolor{blue}{appeal."}



 "And yet I \textcolor{green}{question,} \textcolor{green}{sir,} whether, in all your experience, you

 have ever listened to a more \textcolor{BurntOrange}{mysterious} and \textcolor{BurntOrange}{inexplicable} chain of

 events than those which have \textcolor{blue}{happened} in my own family."



 "You \textcolor{green}{fill} me with \textcolor{green}{interest,"} said Holmes. \textcolor{BurntOrange}{"Pray} give us the

 \textcolor{green}{essential} \textcolor{green}{facts} from the commencement, and I can afterwards

 \textcolor{green}{question} you as to those details which seem to me to be most

 \textcolor{green}{important."}



 The \textcolor{BurntOrange}{young} man \textcolor{green}{pulled} his chair up and pushed his wet feet out

 towards the \textcolor{red}{blaze.}



 "My name," said he, "is \textcolor{red}{John} Openshaw, but my own affairs have,

 as far as I can understand, little to do with this \textcolor{red}{awful}

 business. It is a hereditary matter; so in order to give you an

 idea of the \textcolor{green}{facts,} I must go back to the commencement of the

 affair.



 "You must know that my \textcolor{green}{grandfather} had two sons--my uncle Elias

 and my \textcolor{green}{father} Joseph. My \textcolor{green}{father} had a \textcolor{red}{small} factory at Coventry,

 which he enlarged at the \textcolor{blue}{time} of the invention of bicycling. He

 was a patentee of the Openshaw \textcolor{green}{unbreakable} tire, and his business

 met with such \textcolor{BurntOrange}{success} that he was able to sell it and to retire

 upon a handsome \textcolor{green}{competence.}



 "My uncle Elias emigrated to America when he was a \textcolor{BurntOrange}{young} man and

 became a planter in Florida, where he was reported to have done

 very well. At the \textcolor{blue}{time} of the \textcolor{red}{war} he fought in Jackson's army,

 and afterwards under \textcolor{red}{Hood,} where he rose to be a \textcolor{green}{colonel.} When

 Lee laid down his arms my uncle returned to his plantation, where

 he remained for three or four years. About 1869 or 1870 he came

 back to Europe and took a \textcolor{red}{small} estate in Sussex, near Horsham.

 He had made a very \textcolor{green}{considerable} \textcolor{BurntOrange}{fortune} in the States, and his

 \textcolor{green}{reason} for \textcolor{BurntOrange}{leaving} them was his \textcolor{red}{aversion} to the \textcolor{red}{negroes,} and his

 \textcolor{red}{dislike} of the Republican \textcolor{green}{policy} in \textcolor{green}{extending} the franchise to

 them. He was a singular man, \textcolor{red}{fierce} and quick-tempered, very

 foul-mouthed when he was \textcolor{red}{angry,} and of a most retiring

 disposition. During all the years that he lived at Horsham, I

 \textcolor{BurntOrange}{doubt} if ever he set foot in the town. He had a \textcolor{green}{garden} and two or

 three fields round his house, and there he would take his

 exercise, though very often for weeks on end he would never \textcolor{BurntOrange}{leave}

 his room. He drank a great \textcolor{BurntOrange}{deal} of \textcolor{red}{brandy} and smoked very

 \textcolor{red}{heavily,} but he would see no society and did not want any

 \textcolor{green}{friends,} not even his own \textcolor{green}{brother.}



 "He didn't mind me; in \textcolor{green}{fact,} he took a \textcolor{BurntOrange}{fancy} to me, for at the

 \textcolor{blue}{time} when he saw me first I was a youngster of twelve or so. This

 would be in the year 1878, after he had been eight or nine years

 in England. He \textcolor{red}{begged} my \textcolor{green}{father} to let me live with him and he

 was very \textcolor{green}{kind} to me in his way. When he was sober he used to be

 fond of playing backgammon and draughts with me, and he would

 make me his representative both with the \textcolor{BurntOrange}{servants} and with the

 tradespeople, so that by the \textcolor{blue}{time} that I was sixteen I was quite

 \textcolor{green}{master} of the house. I kept all the keys and could go where I

 liked and do what I liked, so \textcolor{blue}{long} as I did not disturb him in

 his privacy. There was one singular exception, however, for he

 had a single room, a lumber-room up among the attics, which was

 \textcolor{green}{invariably} locked, and which he would never permit either me or

 anyone else to enter. With a \textcolor{red}{boy's} \textcolor{BurntOrange}{curiosity} I have peeped

 through the keyhole, but I was never able to see more than such a

 collection of old trunks and bundles as would be \textcolor{BurntOrange}{expected} in such

 a room.



 "One day--it was in \textcolor{green}{March,} 1883--a \textcolor{blue}{letter} with a \textcolor{red}{foreign} stamp

 lay upon the table in front of the \textcolor{green}{colonel's} plate. It was not a

 common thing for him to receive \textcolor{blue}{letters,} for his bills were all

 paid in \textcolor{blue}{ready} \textcolor{BurntOrange}{money,} and he had no \textcolor{green}{friends} of any sort. 'From

 India!' said he as he took it up, 'Pondicherry postmark! What can

 this be?' Opening it hurriedly, out there jumped five little

 dried orange pips, which \textcolor{red}{pattered} down upon his plate. I began to

 \textcolor{BurntOrange}{laugh} at this, but the \textcolor{BurntOrange}{laugh} was struck from my lips at the sight

 of his face. His lip had \textcolor{red}{fallen,} his eyes were protruding, his

 skin the colour of putty, and he \textcolor{red}{glared} at the envelope which he

 still held in his trembling hand, 'K. K. K.!' he \textcolor{BurntOrange}{shrieked,} and

 then, 'My \textcolor{BurntOrange}{God,} my \textcolor{BurntOrange}{God,} my \textcolor{red}{sins} have overtaken me!'



 "'What is it, uncle?' I \textcolor{red}{cried.}



 \textcolor{BurntOrange}{"'Death,'} said he, and rising from the table he retired to his

 room, \textcolor{BurntOrange}{leaving} me palpitating with \textcolor{BurntOrange}{horror.} I took up the envelope

 and saw scrawled in red ink upon the inner \textcolor{red}{flap,} just above the

 gum, the \textcolor{blue}{letter} K three \textcolor{blue}{times} repeated. There was nothing else

 \textcolor{green}{save} the five dried pips. What could be the \textcolor{green}{reason} of his

 \textcolor{red}{overpowering} \textcolor{red}{terror?} I left the breakfast-table, and as I

 ascended the stair I met him coming down with an old \textcolor{red}{rusty} key,

 which must have belonged to the attic, in one hand, and a \textcolor{red}{small}

 brass box, like a cashbox, in the other.



 "'They may do what they like, but \textcolor{red}{I'll} checkmate them still,'

 said he with an \textcolor{green}{oath.} 'Tell Mary that I shall want a \textcolor{red}{fire} in my

 room to-day, and send down to Fordham, the Horsham \textcolor{red}{lawyer.'}



 "I did as he ordered, and when the \textcolor{red}{lawyer} \textcolor{blue}{arrived} I was asked to

 step up to the room. The \textcolor{red}{fire} was burning brightly, and in the

 \textcolor{red}{grate} there was a mass of \textcolor{red}{black,} fluffy \textcolor{red}{ashes,} as of burned

 paper, while the brass box stood open and empty beside it. As I

 glanced at the box I noticed, with a \textcolor{blue}{start,} that upon the lid was

 printed the treble K which I had read in the morning upon the

 envelope.



 "'I wish you, \textcolor{red}{John,'} said my uncle, 'to \textcolor{green}{witness} my will. I \textcolor{BurntOrange}{leave}

 my estate, with all its \textcolor{green}{advantages} and all its disadvantages, to

 my \textcolor{green}{brother,} your \textcolor{green}{father,} whence it will, no \textcolor{BurntOrange}{doubt,} descend to

 you. If you can \textcolor{BurntOrange}{enjoy} it in \textcolor{BurntOrange}{peace,} well and \textcolor{BurntOrange}{good!} If you find you

 cannot, take my \textcolor{green}{advice,} my \textcolor{red}{boy,} and \textcolor{BurntOrange}{leave} it to your deadliest

 \textcolor{red}{enemy.} I am sorry to give you such a two-edged thing, but I can't

 say what turn things are going to take. Kindly sign the paper

 where Mr. Fordham \textcolor{green}{shows} you.'



 "I signed the paper as directed, and the \textcolor{red}{lawyer} took it away with

 him. The singular \textcolor{blue}{incident} made, as you may think, the deepest

 \textcolor{green}{impression} upon me, and I pondered over it and turned it every

 way in my mind without being able to make anything of it. Yet I

 could not shake off the \textcolor{red}{vague} feeling of \textcolor{BurntOrange}{dread} which it left

 behind, though the sensation \textcolor{BurntOrange}{grew} less keen as the weeks passed

 and nothing \textcolor{blue}{happened} to disturb the \textcolor{green}{usual} \textcolor{green}{routine} of our lives. I

 could see a \textcolor{red}{change} in my uncle, however. He drank more than ever,

 and he was less inclined for any sort of society. Most of his

 \textcolor{blue}{time} he would spend in his room, with the door locked upon the

 inside, but sometimes he would emerge in a sort of \textcolor{red}{drunken} \textcolor{red}{frenzy}

 and would burst out of the house and tear about the \textcolor{green}{garden} with a

 \textcolor{red}{revolver} in his hand, \textcolor{BurntOrange}{screaming} out that he was \textcolor{red}{afraid} of no man,

 and that he was not to be cooped up, like a sheep in a pen, by

 man or \textcolor{BurntOrange}{devil.} When these \textcolor{red}{hot} fits were over, however, he would

 rush tumultuously in at the door and lock and bar it behind him,

 like a man who can \textcolor{red}{brazen} it out no longer against the \textcolor{red}{terror}

 which \textcolor{red}{lies} at the roots of his soul. At such \textcolor{blue}{times} I have seen

 his face, even on a \textcolor{red}{cold} day, glisten with moisture, as though it

 were new raised from a basin.



 "Well, to come to an end of the matter, Mr. Holmes, and not to

 \textcolor{red}{abuse} your \textcolor{BurntOrange}{patience,} there came a night when he made one of those

 \textcolor{red}{drunken} \textcolor{blue}{sallies} from which he never came back. We \textcolor{green}{found} him, when

 we went to search for him, face downward in a little

 green-scummed \textcolor{green}{pool,} which lay at the foot of the \textcolor{green}{garden.} There

 was no sign of any \textcolor{red}{violence,} and the water was but two feet deep,

 so that the \textcolor{green}{jury,} having regard to his known eccentricity,

 brought in a \textcolor{red}{verdict} of \textcolor{red}{'suicide.'} But I, who knew how he \textcolor{red}{winced}

 from the very \textcolor{blue}{thought} of \textcolor{BurntOrange}{death,} had much ado to \textcolor{green}{persuade} myself

 that he had gone out of his way to meet it. The matter passed,

 however, and my \textcolor{green}{father} entered into \textcolor{red}{possession} of the estate, and

 of some 14,000 \textcolor{red}{pounds,} which lay to his \textcolor{green}{credit} at the \textcolor{green}{bank."}



 "One moment," Holmes interposed, "your \textcolor{green}{statement} is, I \textcolor{BurntOrange}{foresee,}

 one of the most \textcolor{BurntOrange}{remarkable} to which I have ever listened. Let me

 have the date of the reception by your uncle of the \textcolor{blue}{letter,} and

 the date of his supposed \textcolor{red}{suicide."}



 "The \textcolor{blue}{letter} \textcolor{blue}{arrived} on \textcolor{green}{March} 10, 1883. His \textcolor{BurntOrange}{death} was seven weeks

 later, upon the night of May 2nd."



 "Thank you. \textcolor{BurntOrange}{Pray} proceed."



 "When my \textcolor{green}{father} took over the Horsham property, he, at my

 request, made a \textcolor{green}{careful} \textcolor{BurntOrange}{examination} of the attic, which had been

 always locked up. We \textcolor{green}{found} the brass box there, although its

 \textcolor{green}{contents} had been \textcolor{red}{destroyed.} On the inside of the \textcolor{green}{cover} was a

 paper \textcolor{green}{label,} with the initials of K. K. K. repeated upon it, and

 \textcolor{blue}{'Letters,} memoranda, receipts, and a register' written beneath.

 These, we presume, indicated the nature of the papers which had

 been \textcolor{red}{destroyed} by \textcolor{green}{Colonel} Openshaw. For the \textcolor{green}{rest,} there was

 nothing of much \textcolor{BurntOrange}{importance} in the attic \textcolor{green}{save} a great many

 scattered papers and note-books bearing upon my uncle's life in

 America. Some of them were of the \textcolor{red}{war} \textcolor{blue}{time} and \textcolor{green}{showed} that he had

 done his duty well and had borne the repute of a brave \textcolor{BurntOrange}{soldier.}

 Others were of a date during the \textcolor{BurntOrange}{reconstruction} of the Southern

 states, and were mostly \textcolor{red}{concerned} with \textcolor{red}{politics,} for he had

 evidently taken a strong part in \textcolor{red}{opposing} the carpet-bag

 politicians who had been sent down from the North.



 "Well, it was the beginning of '84 when my \textcolor{green}{father} came to live at

 Horsham, and all went as well as possible with us until the

 January of '85. On the fourth day after the new year I heard my

 \textcolor{green}{father} give a sharp \textcolor{red}{cry} of \textcolor{BurntOrange}{surprise} as we sat together at the

 breakfast-table. There he was, sitting with a newly opened

 envelope in one hand and five dried orange pips in the

 outstretched palm of the other one. He had always \textcolor{BurntOrange}{laughed} at what

 he called my cock-and-bull story about the \textcolor{green}{colonel,} but he looked

 very \textcolor{red}{scared} and puzzled now that the same thing had come upon

 himself.



 "'Why, what on earth does this mean, \textcolor{red}{John?'} he stammered.



 "My heart had turned to \textcolor{green}{lead.} 'It is K. K. K.,' said I.



 "He looked inside the envelope. 'So it is,' he \textcolor{red}{cried.} 'Here are

 the very \textcolor{blue}{letters.} But what is this written above them?'



 "'Put the papers on the \textcolor{BurntOrange}{sundial,'} I read, peeping over his

 \textcolor{green}{shoulder.}



 "'What papers? What \textcolor{BurntOrange}{sundial?'} he asked.



 "'The \textcolor{BurntOrange}{sundial} in the \textcolor{green}{garden.} There is no other,' said I; 'but the

 papers must be those that are \textcolor{red}{destroyed.'}



 "'Pooh!' said he, gripping hard at his \textcolor{green}{courage.} 'We are in a

 civilised \textcolor{green}{land} here, and we can't have tomfoolery of this \textcolor{green}{kind.}

 Where does the thing come from?'



 "'From Dundee,' I answered, glancing at the postmark.



 "'Some preposterous practical \textcolor{red}{joke,'} said he. 'What have I to do

 with \textcolor{BurntOrange}{sundials} and papers? I shall take no notice of such

 \textcolor{red}{nonsense.'}



 "'I should certainly speak to the \textcolor{BurntOrange}{police,'} I said.



 "'And be \textcolor{BurntOrange}{laughed} at for my \textcolor{red}{pains.} Nothing of the sort.'



 "'Then let me do so?'



 "'No, I \textcolor{red}{forbid} you. I \textcolor{blue}{won't} have a \textcolor{red}{fuss} made about such

 \textcolor{red}{nonsense.'}



 "It was in vain to \textcolor{red}{argue} with him, for he was a very \textcolor{red}{obstinate}

 man. I went about, however, with a heart which was \textcolor{green}{full} of

 \textcolor{BurntOrange}{forebodings.}



 "On the third day after the coming of the \textcolor{blue}{letter} my \textcolor{green}{father} went

 from home to \textcolor{green}{visit} an old \textcolor{green}{friend} of his, \textcolor{green}{Major} Freebody, who is

 in command of one of the \textcolor{green}{forts} upon Portsdown Hill. I was \textcolor{BurntOrange}{glad}

 that he should go, for it seemed to me that he was farther from

 \textcolor{red}{danger} when he was away from home. In that, however, I was in

 \textcolor{red}{error.} Upon the second day of his \textcolor{red}{absence} I received a telegram

 from the \textcolor{green}{major,} imploring me to come at once. My \textcolor{green}{father} had

 \textcolor{red}{fallen} over one of the deep chalk-pits which abound in the

 neighbourhood, and was \textcolor{red}{lying} \textcolor{BurntOrange}{senseless,} with a \textcolor{BurntOrange}{shattered} skull. I

 \textcolor{blue}{hurried} to him, but he passed away without having ever recovered

 his \textcolor{green}{consciousness.} He had, as it appears, been returning from

 Fareham in the twilight, and as the country was \textcolor{BurntOrange}{unknown} to him,

 and the chalk-pit unfenced, the \textcolor{green}{jury} had no \textcolor{red}{hesitation} in

 bringing in a \textcolor{red}{verdict} of \textcolor{BurntOrange}{'death} from \textcolor{BurntOrange}{accidental} causes.'

 \textcolor{green}{Carefully} as I examined every \textcolor{green}{fact} connected with his \textcolor{BurntOrange}{death,} I

 was \textcolor{red}{unable} to find anything which could \textcolor{green}{suggest} the idea of

 \textcolor{BurntOrange}{murder.} There were no signs of \textcolor{red}{violence,} no footmarks, no

 \textcolor{red}{robbery,} no record of \textcolor{red}{strangers} having been seen upon the roads.

 And yet I need not tell you that my mind was far from at \textcolor{green}{ease,}

 and that I was well-nigh certain that some \textcolor{red}{foul} plot had been

 woven round him.



 "In this \textcolor{red}{sinister} way I came into my \textcolor{BurntOrange}{inheritance.} You will ask me

 why I did not \textcolor{red}{dispose} of it? I answer, because I was well

 \textcolor{BurntOrange}{convinced} that our troubles were in some way \textcolor{BurntOrange}{dependent} upon an

 \textcolor{blue}{incident} in my uncle's life, and that the \textcolor{red}{danger} would be as

 pressing in one house as in another.



 "It was in January, '85, that my poor \textcolor{green}{father} met his end, and two

 years and eight months have elapsed since then. During that \textcolor{blue}{time}

 I have lived \textcolor{green}{happily} at Horsham, and I had begun to \textcolor{BurntOrange}{hope} that

 this \textcolor{red}{curse} had passed away from the family, and that it had ended

 with the last generation. I had begun to take \textcolor{BurntOrange}{comfort} too soon,

 however; yesterday morning the blow \textcolor{red}{fell} in the very \textcolor{green}{shape} in

 which it had come upon my \textcolor{green}{father."}



 The \textcolor{BurntOrange}{young} man took from his waistcoat a crumpled envelope, and

 turning to the table he shook out upon it five little dried

 orange pips.



 "This is the envelope," he continued. "The postmark is

 London--eastern division. Within are the very \textcolor{green}{words} which were

 upon my \textcolor{green}{father's} last message: 'K. K. K.'; and then 'Put the

 papers on the \textcolor{BurntOrange}{sundial.'"}



 "What have you done?" asked Holmes.



 "Nothing."



 "Nothing?"



 "To tell the truth"--he sank his face into his thin, \textcolor{BurntOrange}{white}

 hands--"I have felt \textcolor{red}{helpless.} I have felt like one of those poor

 rabbits when the \textcolor{red}{snake} is writhing towards it. I seem to be in

 the grasp of some resistless, inexorable \textcolor{red}{evil,} which no \textcolor{BurntOrange}{foresight}

 and no \textcolor{green}{precautions} can \textcolor{BurntOrange}{guard} against."



 "Tut! tut!" \textcolor{red}{cried} Sherlock Holmes. "You must act, man, or you are

 \textcolor{BurntOrange}{lost.} Nothing but energy can \textcolor{green}{save} you. This is no \textcolor{blue}{time} for

 \textcolor{red}{despair."}



 "I have seen the \textcolor{BurntOrange}{police."}



 "Ah!"



 "But they listened to my story with a \textcolor{BurntOrange}{smile.} I am \textcolor{BurntOrange}{convinced} that

 the \textcolor{green}{inspector} has formed the opinion that the \textcolor{blue}{letters} are all

 practical \textcolor{red}{jokes,} and that the \textcolor{BurntOrange}{deaths} of my relations were really

 \textcolor{BurntOrange}{accidents,} as the \textcolor{green}{jury} stated, and were not to be connected with

 the \textcolor{red}{warnings."}



 Holmes shook his clenched hands in the air. "Incredible

 imbecility!" he \textcolor{red}{cried.}



 "They have, however, allowed me a \textcolor{BurntOrange}{policeman,} who may remain in

 the house with me."



 "Has he come with you to-night?"



 "No. His orders were to stay in the house."



 Again Holmes \textcolor{BurntOrange}{raved} in the air.



 "Why did you come to me," he \textcolor{red}{cried,} "and, above all, why did you

 not come at once?"



 "I did not know. It was only to-day that I \textcolor{red}{spoke} to \textcolor{green}{Major}

 Prendergast about my troubles and was \textcolor{green}{advised} by him to come to

 you."



 "It is really two days since you had the \textcolor{blue}{letter.} We should have

 acted before this. You have no further evidence, I suppose, than

 that which you have placed before us--no suggestive detail which

 might help us?"



 "There is one thing," said \textcolor{red}{John} Openshaw. He rummaged in his coat

 pocket, and, drawing out a piece of discoloured, blue-tinted

 paper, he laid it out upon the table. "I have some remembrance,"

 said he, "that on the day when my uncle burned the papers I

 observed that the \textcolor{red}{small,} unburned \textcolor{red}{margins} which lay amid the

 \textcolor{red}{ashes} were of this particular colour. I \textcolor{green}{found} this single sheet

 upon the floor of his room, and I am inclined to think that it

 may be one of the papers which has, perhaps, fluttered out from

 among the others, and in that way has \textcolor{BurntOrange}{escaped} \textcolor{red}{destruction.} Beyond

 the mention of pips, I do not see that it helps us much. I think

 myself that it is a page from some private \textcolor{green}{diary.} The writing is

 undoubtedly my uncle's."



 Holmes moved the lamp, and we both bent over the sheet of paper,

 which \textcolor{green}{showed} by its ragged edge that it had indeed been \textcolor{red}{torn} from

 a book. It was headed, \textcolor{green}{"March,} 1869," and beneath were the

 following enigmatical notices:



 "4th. Hudson came. Same old platform.



 "7th. Set the pips on McCauley, Paramore, and

 \textcolor{red}{John} Swain, of St. Augustine.



 "9th. McCauley cleared.



 "10th. \textcolor{red}{John} Swain cleared.



 "12th. \textcolor{green}{Visited} Paramore. All well."



 "Thank you!" said Holmes, folding up the paper and returning it

 to our \textcolor{BurntOrange}{visitor.} "And now you must on no \textcolor{green}{account} \textcolor{BurntOrange}{lose} another

 instant. We cannot spare \textcolor{blue}{time} even to discuss what you have told

 me. You must get home instantly and act."



 "What shall I do?"



 "There is but one thing to do. It must be done at once. You must

 put this piece of paper which you have \textcolor{green}{shown} us into the brass

 box which you have described. You must also put in a note to say

 that all the other papers were burned by your uncle, and that

 this is the only one which \textcolor{BurntOrange}{remains.} You must assert that in such

 \textcolor{green}{words} as will carry \textcolor{red}{conviction} with them. Having done this, you

 must at once put the box out upon the \textcolor{BurntOrange}{sundial,} as directed. Do

 you understand?"



 "Entirely."



 "Do not think of \textcolor{BurntOrange}{revenge,} or anything of the sort, at \textcolor{BurntOrange}{present.} I

 think that we may \textcolor{BurntOrange}{gain} that by means of the \textcolor{green}{law;} but we have our

 web to weave, while theirs is already woven. The first

 consideration is to \textcolor{red}{remove} the pressing \textcolor{red}{danger} which threatens

 you. The second is to clear up the \textcolor{blue}{mystery} and to \textcolor{red}{punish} the

 \textcolor{red}{guilty} parties."



 "I thank you," said the \textcolor{BurntOrange}{young} man, rising and \textcolor{green}{pulling} on his

 overcoat. "You have given me fresh life and \textcolor{BurntOrange}{hope.} I shall

 certainly do as you \textcolor{green}{advise."}



 "Do not \textcolor{BurntOrange}{lose} an instant. And, above all, take care of yourself in

 the meanwhile, for I do not think that there can be a \textcolor{BurntOrange}{doubt} that

 you are \textcolor{BurntOrange}{threatened} by a very \textcolor{green}{real} and \textcolor{BurntOrange}{imminent} \textcolor{red}{danger.} How do you

 go back?"



 "By train from Waterloo."



 "It is not yet nine. The streets will be crowded, so I \textcolor{green}{trust} that

 you may be in safety. And yet you cannot \textcolor{BurntOrange}{guard} yourself too

 closely."



 "I am armed."



 "That is well. \textcolor{blue}{To-morrow} I shall set to work upon your \textcolor{red}{case."}



 "I shall see you at Horsham, then?"



 "No, your \textcolor{green}{secret} \textcolor{red}{lies} in London. It is there that I shall \textcolor{blue}{seek}

 it."



 "Then I shall call upon you in a day, or in two days, with news

 as to the box and the papers. I shall take your \textcolor{green}{advice} in every

 particular." He shook hands with us and took his \textcolor{BurntOrange}{leave.} Outside

 the wind still \textcolor{BurntOrange}{screamed} and the rain \textcolor{blue}{splashed} and \textcolor{red}{pattered}

 against the windows. This strange, \textcolor{BurntOrange}{wild} story seemed to have come

 to us from amid the \textcolor{red}{mad} elements--blown in upon us like a sheet

 of sea-weed in a gale--and now to have been reabsorbed by them

 once more.



 Sherlock Holmes sat for some \textcolor{blue}{time} in silence, with his head \textcolor{red}{sunk}

 \textcolor{green}{forward} and his eyes bent upon the red \textcolor{BurntOrange}{glow} of the \textcolor{red}{fire.} Then he

 lit his pipe, and leaning back in his chair he \textcolor{BurntOrange}{watched} the \textcolor{red}{blue}

 smoke-rings as they \textcolor{red}{chased} each other up to the ceiling.



 "I think, Watson," he remarked at last, "that of all our \textcolor{red}{cases} we

 have had none more fantastic than this."



 \textcolor{green}{"Save,} perhaps, the Sign of Four."



 "Well, yes. \textcolor{green}{Save,} perhaps, that. And yet this \textcolor{red}{John} Openshaw seems

 to me to be walking amid even greater \textcolor{BurntOrange}{perils} than did the

 Sholtos."



 "But have you," I asked, "formed any definite conception as to

 what these \textcolor{BurntOrange}{perils} are?"



 "There can be no \textcolor{green}{question} as to their nature," he answered.



 "Then what are they? Who is this K. K. K., and why does he pursue

 this \textcolor{red}{unhappy} family?"



 Sherlock Holmes closed his eyes and placed his \textcolor{red}{elbows} upon the

 arms of his chair, with his finger-tips together. "The ideal

 reasoner," he remarked, "would, when he had once been \textcolor{green}{shown} a

 single \textcolor{green}{fact} in all its bearings, deduce from it not only all the

 chain of events which \textcolor{green}{led} up to it but also all the \textcolor{blue}{results} which

 would follow from it. As Cuvier could correctly describe a whole

 animal by the \textcolor{green}{contemplation} of a single bone, so the observer who

 has thoroughly understood one link in a \textcolor{green}{series} of \textcolor{blue}{incidents}

 should be able to accurately state all the other ones, both

 before and after. We have not yet grasped the \textcolor{blue}{results} which the

 \textcolor{green}{reason} alone can attain to. \textcolor{red}{Problems} may be solved in the \textcolor{green}{study}

 which have baffled all those who have sought a \textcolor{green}{solution} by the

 \textcolor{green}{aid} of their senses. To carry the \textcolor{BurntOrange}{art,} however, to its highest

 pitch, it is necessary that the reasoner should be able to

 utilise all the \textcolor{green}{facts} which have come to his \textcolor{green}{knowledge;} and this

 in itself implies, as you will \textcolor{green}{readily} see, a \textcolor{red}{possession} of all

 \textcolor{green}{knowledge,} which, even in these days of free education and

 encyclopaedias, is a somewhat rare \textcolor{green}{accomplishment.} It is not so

 \textcolor{red}{impossible,} however, that a man should \textcolor{red}{possess} all \textcolor{green}{knowledge}

 which is likely to be useful to him in his work, and this I have

 endeavoured in my \textcolor{red}{case} to do. If I remember \textcolor{green}{rightly,} you on one

 occasion, in the early days of our \textcolor{green}{friendship,} defined my limits

 in a very \textcolor{green}{precise} fashion."



 "Yes," I answered, \textcolor{BurntOrange}{laughing.} "It was a singular document.

 Philosophy, astronomy, and \textcolor{red}{politics} were \textcolor{green}{marked} at zero, I

 remember. Botany \textcolor{blue}{variable,} geology profound as regards the

 mud-stains from any region within fifty miles of town, chemistry

 eccentric, anatomy unsystematic, \textcolor{green}{sensational} literature and \textcolor{red}{crime}

 records \textcolor{BurntOrange}{unique,} violin-player, boxer, swordsman, \textcolor{red}{lawyer,} and

 self-poisoner by \textcolor{red}{cocaine} and \textcolor{red}{tobacco.} Those, I think, were the

 \textcolor{green}{main} points of my analysis."



 Holmes \textcolor{BurntOrange}{grinned} at the last item. "Well," he said, "I say now, as

 I said then, that a man should keep his little brain-attic

 stocked with all the furniture that he is likely to use, and the

 \textcolor{green}{rest} he can put away in the lumber-room of his \textcolor{green}{library,} where he

 can get it if he wants it. Now, for such a \textcolor{red}{case} as the one which

 has been \textcolor{blue}{submitted} to us to-night, we need certainly to muster

 all our resources. Kindly hand me down the \textcolor{blue}{letter} K of the

 'American Encyclopaedia' which stands upon the shelf beside you.

 Thank you. Now let us consider the situation and see what may be

 deduced from it. In the first place, we may \textcolor{blue}{start} with a strong

 \textcolor{green}{presumption} that \textcolor{green}{Colonel} Openshaw had some very strong \textcolor{green}{reason} for

 \textcolor{BurntOrange}{leaving} America. Men at his \textcolor{blue}{time} of life do not \textcolor{red}{change} all their

 habits and \textcolor{green}{exchange} \textcolor{green}{willingly} the \textcolor{green}{charming} climate of Florida for

 the \textcolor{red}{lonely} life of an English provincial town. His extreme \textcolor{green}{love}

 of solitude in England suggests the idea that he was in \textcolor{red}{fear} of

 someone or something, so we may assume as a working \textcolor{blue}{hypothesis}

 that it was \textcolor{red}{fear} of someone or something which drove him from

 America. As to what it was he \textcolor{red}{feared,} we can only deduce that by

 considering the \textcolor{red}{formidable} \textcolor{blue}{letters} which were received by himself

 and his successors. Did you remark the postmarks of those

 \textcolor{blue}{letters?"}



 "The first was from Pondicherry, the second from Dundee, and the

 third from London."



 "From East London. What do you deduce from that?"



 "They are all seaports. That the \textcolor{green}{writer} was on \textcolor{blue}{board} of a \textcolor{blue}{ship."}



 \textcolor{green}{"Excellent.} We have already a \textcolor{blue}{clue.} There can be no \textcolor{BurntOrange}{doubt} that

 the probability--the strong probability--is that the \textcolor{green}{writer} was

 on \textcolor{blue}{board} of a \textcolor{blue}{ship.} And now let us consider another point. In the

 \textcolor{red}{case} of Pondicherry, seven weeks elapsed between the \textcolor{red}{threat} and

 its fulfilment, in Dundee it was only some three or four days.

 Does that \textcolor{green}{suggest} anything?"



 "A greater distance to travel."



 "But the \textcolor{blue}{letter} had also a greater distance to come."



 "Then I do not see the point."



 "There is at least a \textcolor{green}{presumption} that the vessel in which the man

 or men are is a sailing-ship. It looks as if they always send

 their singular \textcolor{BurntOrange}{warning} or token before them when \textcolor{blue}{starting} upon

 their mission. You see how quickly the \textcolor{green}{deed} followed the sign

 when it came from Dundee. If they had come from Pondicherry in a

 steamer they would have \textcolor{blue}{arrived} almost as soon as their \textcolor{blue}{letter.}

 But, as a matter of \textcolor{green}{fact,} seven weeks elapsed. I think that those

 seven weeks represented the difference between the mail-boat which

 brought the \textcolor{blue}{letter} and the sailing vessel which brought the

 \textcolor{green}{writer."}



 "It is possible."



 "More than that. It is probable. And now you see the \textcolor{red}{deadly}

 \textcolor{BurntOrange}{urgency} of this new \textcolor{red}{case,} and why I urged \textcolor{BurntOrange}{young} Openshaw to

 \textcolor{BurntOrange}{caution.} The blow has always \textcolor{red}{fallen} at the end of the \textcolor{blue}{time} which

 it would take the senders to travel the distance. But this one

 comes from London, and therefore we cannot \textcolor{green}{count} upon \textcolor{red}{delay."}



 \textcolor{BurntOrange}{"Good} \textcolor{BurntOrange}{God!"} I \textcolor{red}{cried.} "What can it mean, this relentless

 \textcolor{red}{persecution?"}



 "The papers which Openshaw carried are obviously of \textcolor{green}{vital}

 \textcolor{BurntOrange}{importance} to the person or persons in the sailing-ship. I think

 that it is quite clear that there must be more than one of them.

 A single man could not have carried out two \textcolor{BurntOrange}{deaths} in such a way

 as to \textcolor{red}{deceive} a \textcolor{red}{coroner's} \textcolor{green}{jury.} There must have been several in

 it, and they must have been men of resource and \textcolor{green}{determination.}

 Their papers they mean to have, be the holder of them who it may.

 In this way you see K. K. K. ceases to be the initials of an

 individual and becomes the \textcolor{green}{badge} of a society."



 "But of what society?"



 "Have you never--" said Sherlock Holmes, bending \textcolor{green}{forward} and

 sinking his voice--"have you never heard of the Ku Klux Klan?"



 "I never have."



 Holmes turned over the leaves of the book upon his knee. "Here it

 is," said he presently:



 "'Ku Klux Klan. A name derived from the fanciful resemblance to

 the sound produced by cocking a \textcolor{red}{rifle.} This \textcolor{red}{terrible} \textcolor{green}{secret}

 society was formed by some ex-Confederate \textcolor{BurntOrange}{soldiers} in the

 Southern states after the \textcolor{green}{Civil} \textcolor{red}{War,} and it rapidly formed local

 branches in different parts of the country, notably in Tennessee,

 Louisiana, the Carolinas, Georgia, and Florida. Its power was

 used for political purposes, principally for the terrorising of

 the \textcolor{red}{negro} voters and the \textcolor{BurntOrange}{murdering} and driving from the country

 of those who were \textcolor{red}{opposed} to its views. Its \textcolor{red}{outrages} were usually

 \textcolor{green}{preceded} by a \textcolor{BurntOrange}{warning} sent to the \textcolor{green}{marked} man in some fantastic

 but generally recognised shape--a sprig of oak-leaves in some

 parts, melon seeds or orange pips in others. On receiving this

 the \textcolor{red}{victim} might either openly abjure his former ways, or might

 fly from the country. If he braved the matter out, \textcolor{BurntOrange}{death} would

 unfailingly come upon him, and usually in some strange and

 \textcolor{blue}{unforeseen} manner. So \textcolor{BurntOrange}{perfect} was the organisation of the

 society, and so systematic its methods, that there is hardly a

 \textcolor{red}{case} upon record where any man \textcolor{BurntOrange}{succeeded} in braving it with

 impunity, or in which any of its \textcolor{red}{outrages} were traced home to the

 \textcolor{red}{perpetrators.} For some years the organisation flourished in \textcolor{red}{spite}

 of the \textcolor{green}{efforts} of the \textcolor{green}{United} States \textcolor{red}{government} and of the better

 classes of the \textcolor{green}{community} in the South. Eventually, in the year

 1869, the movement rather \textcolor{blue}{suddenly} \textcolor{red}{collapsed,} although there have

 been sporadic outbreaks of the same sort since that date.'



 "You will observe," said Holmes, laying down the volume, "that

 the \textcolor{blue}{sudden} \textcolor{blue}{breaking} up of the society was coincident with the

 disappearance of Openshaw from America with their papers. It may

 well have been cause and effect. It is no wonder that he and his

 family have some of the more \textcolor{red}{implacable} \textcolor{green}{spirits} upon their \textcolor{blue}{track.}

 You can understand that this register and \textcolor{green}{diary} may \textcolor{red}{implicate}

 some of the first men in the South, and that there may be many

 who will not sleep easy at night until it is recovered."



 "Then the page we have seen--"



 "Is such as we might \textcolor{BurntOrange}{expect.} It ran, if I remember right, 'sent

 the pips to A, B, and C'--that is, sent the society's \textcolor{BurntOrange}{warning} to

 them. Then there are successive entries that A and B cleared, or

 left the country, and \textcolor{BurntOrange}{finally} that C was \textcolor{green}{visited,} with, I \textcolor{red}{fear,} a

 \textcolor{red}{sinister} \textcolor{blue}{result} for C. Well, I think, \textcolor{green}{Doctor,} that we may let

 some light into this \textcolor{red}{dark} place, and I believe that the only

 \textcolor{blue}{chance} \textcolor{BurntOrange}{young} Openshaw has in the meantime is to do what I have

 told him. There is nothing more to be said or to be done

 to-night, so hand me over my violin and let us try to \textcolor{red}{forget} for

 half an hour the \textcolor{red}{miserable} weather and the still more \textcolor{red}{miserable}

 ways of our fellow-men."





 It had cleared in the morning, and the \textcolor{BurntOrange}{sun} was shining with a

 \textcolor{red}{subdued} \textcolor{green}{brightness} through the dim veil which hangs over the

 great city. Sherlock Holmes was already at \textcolor{green}{breakfast} when I came

 down.



 "You will \textcolor{red}{excuse} me for not \textcolor{BurntOrange}{waiting} for you," said he; "I have, I

 \textcolor{BurntOrange}{foresee,} a very busy day before me in looking into this \textcolor{red}{case} of

 \textcolor{BurntOrange}{young} Openshaw's."



 "What steps will you take?" I asked.



 "It will very much \textcolor{BurntOrange}{depend} upon the \textcolor{blue}{results} of my first \textcolor{BurntOrange}{inquiries.}

 I may have to go down to Horsham, after all."



 "You will not go there first?"



 "No, I shall commence with the City. Just ring the bell and the

 maid will bring up your coffee."



 As I \textcolor{BurntOrange}{waited,} I lifted the unopened newspaper from the table and

 glanced my eye over it. It \textcolor{green}{rested} upon a heading which sent a

 chill to my heart.



 "Holmes," I \textcolor{red}{cried,} "you are too \textcolor{red}{late."}



 "Ah!" said he, laying down his cup, "I \textcolor{red}{feared} as much. How was it

 done?" He \textcolor{red}{spoke} calmly, but I could see that he was deeply moved.



 "My eye caught the name of Openshaw, and the heading \textcolor{red}{'Tragedy}

 Near Waterloo Bridge.' Here is the \textcolor{green}{account:}



 "Between nine and ten last night Police-Constable Cook, of the H

 Division, on duty near Waterloo Bridge, heard a \textcolor{red}{cry} for help and

 a \textcolor{blue}{splash} in the water. The night, however, was extremely \textcolor{red}{dark} and

 \textcolor{red}{stormy,} so that, in \textcolor{red}{spite} of the help of several passers-by, it

 was quite \textcolor{red}{impossible} to effect a \textcolor{BurntOrange}{rescue.} The \textcolor{BurntOrange}{alarm,} however, was

 given, and, by the \textcolor{green}{aid} of the water-police, the body was

 eventually recovered. It \textcolor{green}{proved} to be that of a \textcolor{BurntOrange}{young} \textcolor{green}{gentleman}

 whose name, as it appears from an envelope which was \textcolor{green}{found} in his

 pocket, was \textcolor{red}{John} Openshaw, and whose residence is near Horsham.

 It is \textcolor{blue}{conjectured} that he may have been \textcolor{blue}{hurrying} down to \textcolor{blue}{catch}

 the last train from Waterloo Station, and that in his \textcolor{blue}{haste} and

 the extreme \textcolor{red}{darkness} he missed his path and walked over the edge

 of one of the \textcolor{red}{small} landing-places for river steamboats. The body

 exhibited no traces of \textcolor{red}{violence,} and there can be no \textcolor{BurntOrange}{doubt} that

 the deceased had been the \textcolor{red}{victim} of an \textcolor{red}{unfortunate} \textcolor{BurntOrange}{accident,}

 which should have the effect of calling the \textcolor{green}{attention} of the

 \textcolor{green}{authorities} to the condition of the riverside landing-stages."



 We sat in silence for some minutes, Holmes more \textcolor{red}{depressed} and

 shaken than I had ever seen him.



 "That \textcolor{red}{hurts} my \textcolor{green}{pride,} Watson," he said at last. "It is a \textcolor{red}{petty}

 feeling, no \textcolor{BurntOrange}{doubt,} but it \textcolor{red}{hurts} my \textcolor{green}{pride.} It becomes a \textcolor{green}{personal}

 matter with me now, and, if \textcolor{BurntOrange}{God} sends me health, I shall set my

 hand upon this \textcolor{red}{gang.} That he should come to me for help, and that

 I should send him away to his \textcolor{BurntOrange}{death--!"} He sprang from his chair

 and paced about the room in \textcolor{BurntOrange}{uncontrollable} \textcolor{red}{agitation,} with a

 \textcolor{green}{flush} upon his sallow cheeks and a \textcolor{BurntOrange}{nervous} clasping and

 unclasping of his \textcolor{blue}{long} thin hands.



 "They must be \textcolor{BurntOrange}{cunning} \textcolor{BurntOrange}{devils,"} he \textcolor{blue}{exclaimed} at last. "How could

 they have decoyed him down there? The Embankment is not on the

 direct line to the station. The bridge, no \textcolor{BurntOrange}{doubt,} was too

 crowded, even on such a night, for their purpose. Well, Watson,

 we shall see who will win in the \textcolor{blue}{long} run. I am going out now!"



 "To the \textcolor{BurntOrange}{police?"}



 "No; I shall be my own \textcolor{BurntOrange}{police.} When I have spun the web they may

 take the flies, but not before."



 All day I was engaged in my \textcolor{green}{professional} work, and it was \textcolor{red}{late} in

 the evening before I returned to Baker Street. Sherlock Holmes

 had not come back yet. It was nearly ten o'clock before he

 entered, looking pale and \textcolor{red}{worn.} He walked up to the sideboard,

 and tearing a piece from the \textcolor{red}{loaf} he \textcolor{red}{devoured} it voraciously,

 washing it down with a \textcolor{blue}{long} draught of water.



 "You are \textcolor{BurntOrange}{hungry,"} I remarked.



 "Starving. It had \textcolor{BurntOrange}{escaped} my memory. I have had nothing since

 \textcolor{green}{breakfast."}



 "Nothing?"



 "Not a \textcolor{red}{bite.} I had no \textcolor{blue}{time} to think of it."



 "And how have you \textcolor{BurntOrange}{succeeded?"}



 "Well."



 "You have a \textcolor{blue}{clue?"}



 "I have them in the \textcolor{red}{hollow} of my hand. \textcolor{BurntOrange}{Young} Openshaw shall not

 \textcolor{blue}{long} remain unavenged. Why, Watson, let us put their own \textcolor{red}{devilish}

 trade-mark upon them. It is well \textcolor{blue}{thought} of!"



 "What do you mean?"



 He took an orange from the cupboard, and tearing it to pieces he

 squeezed out the pips upon the table. Of these he took five and

 thrust them into an envelope. On the inside of the \textcolor{red}{flap} he wrote

 "S. H. for J. O." Then he \textcolor{green}{sealed} it and addressed it to \textcolor{green}{"Captain}

 James Calhoun, Barque \textcolor{red}{'Lone} \textcolor{BurntOrange}{Star,'} Savannah, Georgia."



 "That will \textcolor{blue}{await} him when he enters port," said he, \textcolor{BurntOrange}{chuckling.}

 "It may give him a sleepless night. He will find it as sure a

 \textcolor{blue}{precursor} of his \textcolor{BurntOrange}{fate} as Openshaw did before him."



 "And who is this \textcolor{green}{Captain} Calhoun?"



 "The \textcolor{green}{leader} of the \textcolor{red}{gang.} I shall have the others, but he first."



 "How did you trace it, then?"



 He took a large sheet of paper from his pocket, all \textcolor{green}{covered} with

 dates and names.



 "I have \textcolor{red}{spent} the whole day," said he, "over Lloyd's registers

 and files of the old papers, following the future \textcolor{BurntOrange}{career} of every

 vessel which touched at Pondicherry in January and February in

 '83. There were thirty-six \textcolor{blue}{ships} of \textcolor{green}{fair} tonnage which were

 reported there during those months. Of these, one, the \textcolor{red}{'Lone} \textcolor{BurntOrange}{Star,'}

 instantly attracted my \textcolor{green}{attention,} since, although it was reported

 as having cleared from London, the name is that which is given to

 one of the states of the Union."



 "Texas, I think."



 "I was not and am not sure which; but I knew that the \textcolor{blue}{ship} must

 have an American origin."



 "What then?"



 "I searched the Dundee records, and when I \textcolor{green}{found} that the barque

 \textcolor{red}{'Lone} \textcolor{BurntOrange}{Star'} was there in January, '85, my \textcolor{red}{suspicion} became a

 \textcolor{green}{certainty.} I then inquired as to the vessels which lay at \textcolor{BurntOrange}{present}

 in the port of London."



 "Yes?"



 "The \textcolor{red}{'Lone} \textcolor{BurntOrange}{Star'} had \textcolor{blue}{arrived} here last week. I went down to the

 Albert Dock and \textcolor{green}{found} that she had been taken down the river by

 the early tide this morning, homeward \textcolor{red}{bound} to Savannah. I wired

 to Gravesend and \textcolor{green}{learned} that she had passed some \textcolor{blue}{time} ago, and

 as the wind is easterly I have no \textcolor{BurntOrange}{doubt} that she is now past the

 Goodwins and not very far from the Isle of Wight."



 "What will you do, then?"



 "Oh, I have my hand upon him. He and the two \textcolor{green}{mates,} are as I

 \textcolor{green}{learn,} the only native-born Americans in the \textcolor{blue}{ship.} The others are

 Finns and Germans. I know, also, that they were all three away

 from the \textcolor{blue}{ship} last night. I had it from the stevedore who has

 been loading their cargo. By the \textcolor{blue}{time} that their sailing-ship

 reaches Savannah the mail-boat will have carried this \textcolor{blue}{letter,} and

 the \textcolor{blue}{cable} will have \textcolor{green}{informed} the \textcolor{BurntOrange}{police} of Savannah that these

 three \textcolor{green}{gentlemen} are \textcolor{red}{badly} wanted here upon a charge of \textcolor{BurntOrange}{murder."}



 There is ever a \textcolor{red}{flaw,} however, in the best laid of human \textcolor{blue}{plans,}

 and the \textcolor{red}{murderers} of \textcolor{red}{John} Openshaw were never to receive the

 orange pips which would \textcolor{green}{show} them that another, as \textcolor{BurntOrange}{cunning} and as

 resolute as themselves, was upon their \textcolor{blue}{track.} Very \textcolor{blue}{long} and very

 severe were the equinoctial gales that year. We \textcolor{BurntOrange}{waited} \textcolor{blue}{long} for

 news of the \textcolor{red}{"Lone} \textcolor{BurntOrange}{Star"} of Savannah, but none ever reached us. We

 did at last hear that somewhere far out in the Atlantic a

 \textcolor{BurntOrange}{shattered} stern-post of a boat was seen swinging in the trough

 of a wave, with the \textcolor{blue}{letters} "L. S." carved upon it, and that is

 all which we shall ever know of the \textcolor{BurntOrange}{fate} of the \textcolor{red}{"Lone} \textcolor{BurntOrange}{Star."}







 \textcolor{BurntOrange}{ADVENTURE} VI. THE MAN WITH THE TWISTED LIP



 Isa Whitney, \textcolor{green}{brother} of the \textcolor{red}{late} Elias Whitney, D.D., \textcolor{green}{Principal}

 of the \textcolor{green}{Theological} College of St. George's, was much addicted to

 \textcolor{red}{opium.} The habit \textcolor{BurntOrange}{grew} upon him, as I understand, from some

 \textcolor{red}{foolish} freak when he was at college; for having read De

 Quincey's description of his dreams and sensations, he had

 drenched his \textcolor{red}{tobacco} with laudanum in an \textcolor{blue}{attempt} to produce the

 same effects. He \textcolor{green}{found,} as so many more have done, that the

 \textcolor{green}{practice} is easier to attain than to get rid of, and for many

 years he continued to be a \textcolor{red}{slave} to the drug, an object of

 mingled \textcolor{BurntOrange}{horror} and \textcolor{red}{pity} to his \textcolor{green}{friends} and \textcolor{green}{relatives.} I can see

 him now, with yellow, pasty face, drooping lids, and pin-point

 pupils, all huddled in a chair, the \textcolor{BurntOrange}{wreck} and \textcolor{red}{ruin} of a \textcolor{green}{noble}

 man.



 One night--it was in June, '89--there came a ring to my bell,

 about the hour when a man gives his first \textcolor{red}{yawn} and glances at the

 \textcolor{blue}{clock.} I sat up in my chair, and my wife laid her needle-work

 down in her lap and made a little face of \textcolor{red}{disappointment.}



 "A \textcolor{BurntOrange}{patient!"} said she. "You'll have to go out."



 I \textcolor{red}{groaned,} for I was newly come back from a \textcolor{red}{weary} day.



 We heard the door open, a few \textcolor{blue}{hurried} \textcolor{green}{words,} and then quick steps

 upon the linoleum. Our own door flew open, and a lady, clad in

 some dark-coloured stuff, with a \textcolor{red}{black} veil, entered the room.



 "You will \textcolor{red}{excuse} my calling so \textcolor{red}{late,"} she began, and then,

 \textcolor{blue}{suddenly} \textcolor{BurntOrange}{losing} her self-control, she ran \textcolor{green}{forward,} threw her arms

 about my wife's neck, and sobbed upon her \textcolor{green}{shoulder.} "Oh, I'm in

 such trouble!" she \textcolor{red}{cried;} "I do so want a little help."



 "Why," said my wife, \textcolor{green}{pulling} up her veil, "it is Kate Whitney.

 How you \textcolor{BurntOrange}{startled} me, Kate! I had not an idea who you were when

 you came in."



 "I didn't know what to do, so I came straight to you." That was

 always the way. Folk who were in \textcolor{red}{grief} came to my wife like birds

 to a \textcolor{green}{light-house.}



 "It was very \textcolor{BurntOrange}{sweet} of you to come. Now, you must have some wine

 and water, and sit here comfortably and tell us all about it. Or

 should you rather that I sent James off to bed?"



 "Oh, no, no! I want the \textcolor{green}{doctor's} \textcolor{green}{advice} and help, too. It's about

 Isa. He has not been home for two days. I am so \textcolor{BurntOrange}{frightened} about

 him!"



 It was not the first \textcolor{blue}{time} that she had spoken to us of her

 husband's trouble, to me as a \textcolor{green}{doctor,} to my wife as an old \textcolor{green}{friend}

 and \textcolor{green}{school} \textcolor{green}{companion.} We \textcolor{green}{soothed} and \textcolor{BurntOrange}{comforted} her by such \textcolor{green}{words}

 as we could find. Did she know where her husband was? Was it

 possible that we could bring him back to her?



 It seems that it was. She had the surest \textcolor{green}{information} that of \textcolor{red}{late}

 he had, when the fit was on him, made use of an \textcolor{red}{opium} den in the

 farthest east of the City. \textcolor{red}{Hitherto} his orgies had always been

 \textcolor{red}{confined} to one day, and he had come back, \textcolor{red}{twitching} and

 \textcolor{BurntOrange}{shattered,} in the evening. But now the spell had been upon him

 eight-and-forty hours, and he lay there, \textcolor{green}{doubtless} among the

 dregs of the docks, breathing in the \textcolor{red}{poison} or sleeping off the

 effects. There he was to be \textcolor{green}{found,} she was sure of it, at the Bar

 of \textcolor{green}{Gold,} in Upper Swandam Lane. But what was she to do? How could

 she, a \textcolor{BurntOrange}{young} and \textcolor{red}{timid} woman, make her way into such a place and

 pluck her husband out from among the ruffians who \textcolor{BurntOrange}{surrounded} him?



 There was the \textcolor{red}{case,} and of course there was but one way out of

 it. Might I not \textcolor{green}{escort} her to this place? And then, as a second

 \textcolor{blue}{thought,} why should she come at all? I was Isa Whitney's \textcolor{BurntOrange}{medical}

 \textcolor{green}{adviser,} and as such I had \textcolor{BurntOrange}{influence} over him. I could \textcolor{green}{manage} it

 better if I were alone. I \textcolor{green}{promised} her on my \textcolor{green}{word} that I would

 send him home in a \textcolor{green}{cab} within two hours if he were indeed at the

 address which she had given me. And so in ten minutes I had left

 my armchair and \textcolor{BurntOrange}{cheery} sitting-room behind me, and was speeding

 eastward in a hansom on a strange \textcolor{BurntOrange}{errand,} as it seemed to me at

 the \textcolor{blue}{time,} though the future only could \textcolor{green}{show} how strange it was to

 be.



 But there was no great \textcolor{red}{difficulty} in the first stage of my

 \textcolor{BurntOrange}{adventure.} Upper Swandam Lane is a vile alley \textcolor{red}{lurking} behind the

 high wharves which line the north side of the river to the east

 of London Bridge. Between a slop-shop and a gin-shop, approached

 by a steep flight of steps \textcolor{green}{leading} down to a \textcolor{red}{black} \textcolor{red}{gap} like the

 \textcolor{blue}{mouth} of a cave, I \textcolor{green}{found} the den of which I was in search.

 Ordering my \textcolor{green}{cab} to \textcolor{BurntOrange}{wait,} I passed down the steps, \textcolor{red}{worn} \textcolor{red}{hollow} in

 the centre by the ceaseless tread of \textcolor{red}{drunken} feet; and by the

 light of a flickering oil-lamp above the door I \textcolor{green}{found} the latch

 and made my way into a \textcolor{blue}{long,} low room, thick and heavy with the

 brown \textcolor{red}{opium} smoke, and terraced with wooden \textcolor{green}{berths,} like the

 forecastle of an emigrant \textcolor{blue}{ship.}



 Through the \textcolor{red}{gloom} one could dimly \textcolor{blue}{catch} a glimpse of bodies \textcolor{red}{lying}

 in strange fantastic \textcolor{red}{poses,} bowed \textcolor{green}{shoulders,} bent knees, heads

 thrown back, and chins pointing upward, with here and there a

 \textcolor{red}{dark,} lack-lustre eye turned upon the \textcolor{BurntOrange}{newcomer.} Out of the \textcolor{red}{black}

 shadows there \textcolor{BurntOrange}{glimmered} little red circles of light, now bright,

 now faint, as the burning \textcolor{red}{poison} waxed or \textcolor{red}{waned} in the bowls of

 the metal pipes. The most lay silent, but some \textcolor{red}{muttered} to

 themselves, and others \textcolor{green}{talked} together in a strange, low,

 monotonous voice, their conversation coming in \textcolor{BurntOrange}{gushes,} and then

 \textcolor{blue}{suddenly} tailing off into silence, each \textcolor{red}{mumbling} out his own

 \textcolor{blue}{thoughts} and \textcolor{BurntOrange}{paying} little heed to the \textcolor{green}{words} of his neighbour. At

 the farther end was a \textcolor{red}{small} brazier of burning charcoal, beside

 which on a three-legged wooden stool there sat a tall, thin old

 man, with his jaw \textcolor{green}{resting} upon his two fists, and his \textcolor{red}{elbows} upon

 his knees, \textcolor{BurntOrange}{staring} into the \textcolor{red}{fire.}



 As I entered, a sallow Malay \textcolor{green}{attendant} had \textcolor{blue}{hurried} up with a pipe

 for me and a \textcolor{green}{supply} of the drug, beckoning me to an empty \textcolor{green}{berth.}



 "Thank you. I have not come to stay," said I. "There is a \textcolor{green}{friend}

 of mine here, Mr. Isa Whitney, and I wish to speak with him."



 There was a movement and an exclamation from my right, and

 peering through the \textcolor{red}{gloom,} I saw Whitney, pale, \textcolor{red}{haggard,} and

 unkempt, \textcolor{BurntOrange}{staring} out at me.



 "My \textcolor{BurntOrange}{God!} It's Watson," said he. He was in a pitiable state of

 reaction, with every \textcolor{green}{nerve} in a twitter. "I say, Watson, what

 o'clock is it?"



 "Nearly eleven."



 "Of what day?"



 "Of Friday, June 19th."



 \textcolor{BurntOrange}{"Good} heavens! I \textcolor{blue}{thought} it was Wednesday. It is Wednesday. What

 d'you want to \textcolor{BurntOrange}{frighten} a chap for?" He sank his face onto his

 arms and began to \textcolor{red}{sob} in a high treble key.



 "I tell you that it is Friday, man. Your wife has been \textcolor{BurntOrange}{waiting}

 this two days for you. You should be \textcolor{red}{ashamed} of yourself!"



 "So I am. But you've got mixed, Watson, for I have only been here

 a few hours, three pipes, four pipes--I \textcolor{red}{forget} how many. But \textcolor{red}{I'll}

 go home with you. I wouldn't \textcolor{BurntOrange}{frighten} Kate--poor little Kate.

 Give me your hand! Have you a \textcolor{green}{cab?"}



 "Yes, I have one \textcolor{BurntOrange}{waiting."}



 "Then I shall go in it. But I must owe something. Find what I

 owe, Watson. I am all off colour. I can do nothing for myself."



 I walked down the narrow passage between the double \textcolor{red}{row} of

 sleepers, holding my breath to keep out the vile, stupefying

 \textcolor{red}{fumes} of the drug, and looking about for the manager. As I passed

 the tall man who sat by the brazier I felt a \textcolor{blue}{sudden} pluck at my

 skirt, and a low voice whispered, "Walk past me, and then look

 back at me." The \textcolor{green}{words} \textcolor{red}{fell} quite distinctly upon my ear. I

 glanced down. They could only have come from the old man at my

 side, and yet he sat now as \textcolor{green}{absorbed} as ever, very thin, very

 wrinkled, bent with age, an \textcolor{red}{opium} pipe dangling down from between

 his knees, as though it had dropped in sheer lassitude from his

 fingers. I took two steps \textcolor{green}{forward} and looked back. It took all my

 self-control to \textcolor{red}{prevent} me from \textcolor{blue}{breaking} out into a \textcolor{red}{cry} of

 \textcolor{BurntOrange}{astonishment.} He had turned his back so that none could see him

 but I. His form had \textcolor{green}{filled} out, his wrinkles were gone, the \textcolor{red}{dull}

 eyes had regained their \textcolor{red}{fire,} and there, sitting by the \textcolor{red}{fire} and

 \textcolor{BurntOrange}{grinning} at my \textcolor{BurntOrange}{surprise,} was none other than Sherlock Holmes. He

 made a slight \textcolor{blue}{motion} to me to approach him, and instantly, as he

 turned his face half round to the company once more, subsided

 into a doddering, loose-lipped senility.



 "Holmes!" I whispered, "what on earth are you doing in this den?"



 "As low as you can," he answered; "I have \textcolor{green}{excellent} ears. If you

 would have the great \textcolor{green}{kindness} to get rid of that sottish \textcolor{green}{friend}

 of yours I should be exceedingly \textcolor{BurntOrange}{glad} to have a little \textcolor{green}{talk} with

 you."



 "I have a \textcolor{green}{cab} outside."



 "Then \textcolor{BurntOrange}{pray} send him home in it. You may safely \textcolor{green}{trust} him, for he

 appears to be too \textcolor{red}{limp} to get into any \textcolor{red}{mischief.} I should

 \textcolor{green}{recommend} you also to send a note by the cabman to your wife to

 say that you have thrown in your lot with me. If you will \textcolor{BurntOrange}{wait}

 outside, I shall be with you in five minutes."



 It was \textcolor{red}{difficult} to \textcolor{red}{refuse} any of Sherlock Holmes' requests, for

 they were always so exceedingly definite, and put \textcolor{green}{forward} with

 such a \textcolor{BurntOrange}{quiet} air of \textcolor{BurntOrange}{mastery.} I felt, however, that when Whitney

 was once \textcolor{red}{confined} in the \textcolor{green}{cab} my mission was practically

 \textcolor{green}{accomplished;} and for the \textcolor{green}{rest,} I could not wish anything better

 than to be \textcolor{green}{associated} with my \textcolor{green}{friend} in one of those singular

 \textcolor{BurntOrange}{adventures} which were the normal condition of his \textcolor{green}{existence.} In a

 few minutes I had written my note, paid Whitney's bill, \textcolor{green}{led} him

 out to the \textcolor{green}{cab,} and seen him driven through the \textcolor{red}{darkness.} In a

 very short \textcolor{blue}{time} a \textcolor{red}{decrepit} figure had emerged from the \textcolor{red}{opium} den,

 and I was walking down the street with Sherlock Holmes. For two

 streets he shuffled along with a bent back and an \textcolor{BurntOrange}{uncertain} foot.

 Then, glancing quickly round, he straightened himself out and

 burst into a hearty fit of \textcolor{BurntOrange}{laughter.}



 "I suppose, Watson," said he, "that you imagine that I have added

 opium-smoking to \textcolor{red}{cocaine} \textcolor{red}{injections,} and all the other little

 \textcolor{red}{weaknesses} on which you have favoured me with your \textcolor{BurntOrange}{medical}

 views."



 "I was certainly \textcolor{blue}{surprised} to find you there."



 "But not more so than I to find you."



 "I came to find a \textcolor{green}{friend."}



 "And I to find an \textcolor{red}{enemy."}



 "An \textcolor{red}{enemy?"}



 "Yes; one of my natural \textcolor{red}{enemies,} or, shall I say, my natural

 \textcolor{red}{prey.} Briefly, Watson, I am in the midst of a very \textcolor{BurntOrange}{remarkable}

 \textcolor{BurntOrange}{inquiry,} and I have hoped to find a \textcolor{blue}{clue} in the \textcolor{red}{incoherent}

 ramblings of these sots, as I have done before now. Had I been

 recognised in that den my life would not have been \textcolor{green}{worth} an

 hour's purchase; for I have used it before now for my own

 purposes, and the rascally Lascar who runs it has sworn to have

 \textcolor{red}{vengeance} upon me. There is a trap-door at the back of that

 \textcolor{green}{building,} near the corner of Paul's Wharf, which could tell some

 strange \textcolor{green}{tales} of what has passed through it upon the moonless

 nights."



 "What! You do not mean bodies?"



 \textcolor{green}{"Ay,} bodies, Watson. We should be rich men if we had 1000 \textcolor{red}{pounds}

 for every poor \textcolor{BurntOrange}{devil} who has been done to \textcolor{BurntOrange}{death} in that den. It

 is the vilest murder-trap on the whole riverside, and I \textcolor{red}{fear} that

 Neville St. Clair has entered it never to \textcolor{BurntOrange}{leave} it more. But our

 trap should be here." He put his two forefingers between his

 teeth and whistled shrilly--a signal which was answered by a

 similar whistle from the distance, followed \textcolor{blue}{shortly} by the rattle

 of wheels and the clink of \textcolor{green}{horses'} hoofs.



 "Now, Watson," said Holmes, as a tall dog-cart dashed up through

 the \textcolor{red}{gloom,} throwing out two golden tunnels of yellow light from

 its side lanterns. "You'll come with me, \textcolor{blue}{won't} you?"



 "If I can be of use."



 "Oh, a \textcolor{green}{trusty} \textcolor{green}{comrade} is always of use; and a chronicler still

 more so. My room at The Cedars is a double-bedded one."



 "The Cedars?"



 "Yes; that is Mr. St. Clair's house. I am staying there while I

 conduct the \textcolor{BurntOrange}{inquiry."}



 "Where is it, then?"



 "Near Lee, in Kent. We have a seven-mile drive before us."



 "But I am all in the \textcolor{red}{dark."}



 "Of course you are. You'll know all about it presently. \textcolor{green}{Jump} up

 here. All right, \textcolor{red}{John;} we shall not need you. Here's half a

 crown. Look out for me \textcolor{blue}{to-morrow,} about eleven. Give her her

 head. So \textcolor{blue}{long,} then!"



 He flicked the \textcolor{green}{horse} with his \textcolor{red}{whip,} and we dashed away through

 the \textcolor{BurntOrange}{endless} succession of sombre and \textcolor{red}{deserted} streets, which

 widened gradually, until we were flying across a broad

 balustraded bridge, with the \textcolor{red}{murky} river \textcolor{green}{flowing} sluggishly

 beneath us. Beyond lay another \textcolor{red}{dull} \textcolor{BurntOrange}{wilderness} of bricks and

 \textcolor{green}{mortar,} its silence \textcolor{red}{broken} only by the heavy, regular footfall of

 the \textcolor{BurntOrange}{policeman,} or the songs and \textcolor{BurntOrange}{shouts} of some \textcolor{red}{belated} party of

 revellers. A \textcolor{red}{dull} wrack was drifting slowly across the \textcolor{green}{sky,} and a

 \textcolor{BurntOrange}{star} or two \textcolor{BurntOrange}{twinkled} dimly here and there through the \textcolor{red}{rifts} of

 the clouds. Holmes drove in silence, with his head \textcolor{red}{sunk} upon his

 breast, and the air of a man who is \textcolor{BurntOrange}{lost} in \textcolor{blue}{thought,} while I sat

 beside him, curious to \textcolor{green}{learn} what this new \textcolor{BurntOrange}{quest} might be which

 seemed to \textcolor{red}{tax} his powers so \textcolor{red}{sorely,} and yet \textcolor{red}{afraid} to \textcolor{blue}{break} in

 upon the current of his \textcolor{blue}{thoughts.} We had driven several miles,

 and were beginning to get to the fringe of the \textcolor{red}{belt} of suburban

 villas, when he shook himself, shrugged his \textcolor{green}{shoulders,} and lit up

 his pipe with the air of a man who has \textcolor{green}{satisfied} himself that he

 is acting for the best.



 "You have a grand \textcolor{BurntOrange}{gift} of silence, Watson," said he. "It makes

 you quite invaluable as a \textcolor{green}{companion.} 'Pon my \textcolor{green}{word,} it is a great

 thing for me to have someone to \textcolor{green}{talk} to, for my own \textcolor{blue}{thoughts} are

 not over-pleasant. I was wondering what I should say to this \textcolor{green}{dear}

 little woman to-night when she meets me at the door."



 "You \textcolor{red}{forget} that I know nothing about it."



 "I shall just have \textcolor{blue}{time} to tell you the \textcolor{green}{facts} of the \textcolor{red}{case} before

 we get to Lee. It seems absurdly simple, and yet, somehow I can

 get nothing to go upon. There's plenty of thread, no \textcolor{BurntOrange}{doubt,} but I

 can't get the end of it into my hand. Now, \textcolor{red}{I'll} state the \textcolor{red}{case}

 clearly and concisely to you, Watson, and maybe you can see a

 spark where all is \textcolor{red}{dark} to me."



 "Proceed, then."



 "Some years ago--to be definite, in May, 1884--there came to Lee

 a \textcolor{green}{gentleman,} Neville St. Clair by name, who appeared to have

 plenty of \textcolor{BurntOrange}{money.} He took a large villa, laid out the \textcolor{green}{grounds} very

 nicely, and lived generally in \textcolor{BurntOrange}{good} style. By \textcolor{green}{degrees} he made

 \textcolor{green}{friends} in the neighbourhood, and in 1887 he married the \textcolor{green}{daughter}

 of a local brewer, by whom he now has two \textcolor{BurntOrange}{children.} He had no

 \textcolor{green}{occupation,} but was \textcolor{BurntOrange}{interested} in several companies and went into

 town as a \textcolor{BurntOrange}{rule} in the morning, returning by the 5:14 from \textcolor{red}{Cannon}

 Street every night. Mr. St. Clair is now thirty-seven years of

 age, is a man of \textcolor{green}{temperate} habits, a \textcolor{BurntOrange}{good} husband, a very

 affectionate \textcolor{green}{father,} and a man who is popular with all who know

 him. I may add that his whole \textcolor{red}{debts} at the \textcolor{BurntOrange}{present} moment, as far

 as we have been able to ascertain, amount to 88 \textcolor{red}{pounds} 10s., while

 he has 220 \textcolor{red}{pounds} standing to his \textcolor{green}{credit} in the Capital and

 \textcolor{green}{Counties} \textcolor{green}{Bank.} There is no \textcolor{green}{reason,} therefore, to think that \textcolor{BurntOrange}{money}

 troubles have been \textcolor{BurntOrange}{weighing} upon his mind.



 "Last Monday Mr. Neville St. Clair went into town rather earlier

 than \textcolor{green}{usual,} remarking before he \textcolor{blue}{started} that he had two \textcolor{green}{important}

 \textcolor{green}{commissions} to perform, and that he would bring his little \textcolor{red}{boy}

 home a box of bricks. Now, by the merest \textcolor{blue}{chance,} his wife

 received a telegram upon this same Monday, very \textcolor{blue}{shortly} after his

 \textcolor{red}{departure,} to the effect that a \textcolor{red}{small} parcel of \textcolor{green}{considerable}

 value which she had been \textcolor{BurntOrange}{expecting} was \textcolor{BurntOrange}{waiting} for her at the

 offices of the Aberdeen Shipping Company. Now, if you are well up

 in your London, you will know that the office of the company is

 in Fresno Street, which branches out of Upper Swandam Lane, where

 you \textcolor{green}{found} me to-night. Mrs. St. Clair had her lunch, \textcolor{blue}{started} for

 the City, did some \textcolor{BurntOrange}{shopping,} proceeded to the company's office,

 got her packet, and \textcolor{green}{found} herself at exactly 4:35 walking through

 Swandam Lane on her way back to the station. Have you followed me

 so far?"



 "It is very clear."



 "If you remember, Monday was an exceedingly \textcolor{red}{hot} day, and Mrs. St.

 Clair walked slowly, glancing about in the \textcolor{BurntOrange}{hope} of seeing a \textcolor{green}{cab,}

 as she did not like the neighbourhood in which she \textcolor{green}{found} herself.

 While she was walking in this way down Swandam Lane, she \textcolor{blue}{suddenly}

 heard an \textcolor{BurntOrange}{ejaculation} or \textcolor{red}{cry,} and was struck \textcolor{red}{cold} to see her

 husband looking down at her and, as it seemed to her, beckoning

 to her from a second-floor window. The window was open, and she

 distinctly saw his face, which she describes as being \textcolor{red}{terribly}

 agitated. He waved his hands frantically to her, and then

 \textcolor{BurntOrange}{vanished} from the window so \textcolor{blue}{suddenly} that it seemed to her that

 he had been plucked back by some irresistible \textcolor{red}{force} from behind.

 One singular point which struck her quick feminine eye was that

 although he wore some \textcolor{red}{dark} coat, such as he had \textcolor{blue}{started} to town

 in, he had on neither collar nor necktie.



 \textcolor{BurntOrange}{"Convinced} that something was amiss with him, she rushed down the

 steps--for the house was none other than the \textcolor{red}{opium} den in which

 you \textcolor{green}{found} me to-night--and running through the front room she

 \textcolor{blue}{attempted} to ascend the stairs which \textcolor{green}{led} to the first floor. At

 the foot of the stairs, however, she met this Lascar \textcolor{BurntOrange}{scoundrel} of

 whom I have spoken, who thrust her back and, \textcolor{green}{aided} by a Dane, who

 acts as assistant there, pushed her out into the street. \textcolor{green}{Filled}

 with the most \textcolor{red}{maddening} \textcolor{BurntOrange}{doubts} and \textcolor{red}{fears,} she rushed down the

 lane and, by rare good-fortune, met in Fresno Street a number of

 \textcolor{green}{constables} with an \textcolor{green}{inspector,} all on their way to their beat. The

 \textcolor{green}{inspector} and two men accompanied her back, and in \textcolor{red}{spite} of the

 continued \textcolor{red}{resistance} of the proprietor, they made their way to

 the room in which Mr. St. Clair had last been seen. There was no

 sign of him there. In \textcolor{green}{fact,} in the whole of that floor there was

 no one to be \textcolor{green}{found} \textcolor{green}{save} a \textcolor{red}{crippled} \textcolor{red}{wretch} of \textcolor{red}{hideous} aspect, who,

 it seems, made his home there. Both he and the Lascar stoutly

 swore that no one else had been in the front room during the

 afternoon. So determined was their \textcolor{red}{denial} that the \textcolor{green}{inspector} was

 \textcolor{blue}{staggered,} and had almost come to believe that Mrs. St. Clair had

 been deluded when, with a \textcolor{red}{cry,} she sprang at a \textcolor{red}{small} \textcolor{BurntOrange}{deal} box

 which lay upon the table and tore the lid from it. Out there \textcolor{red}{fell}

 a \textcolor{green}{cascade} of children's bricks. It was the toy which he had

 \textcolor{green}{promised} to bring home.



 "This \textcolor{green}{discovery,} and the \textcolor{green}{evident} \textcolor{red}{confusion} which the \textcolor{red}{cripple}

 \textcolor{green}{showed,} made the \textcolor{green}{inspector} realise that the matter was serious.

 The rooms were \textcolor{green}{carefully} examined, and \textcolor{blue}{results} all pointed to an

 \textcolor{red}{abominable} \textcolor{red}{crime.} The front room was plainly furnished as a

 sitting-room and \textcolor{green}{led} into a \textcolor{red}{small} bedroom, which looked out upon

 the back of one of the wharves. Between the wharf and the bedroom

 window is a narrow \textcolor{red}{strip,} which is dry at low tide but is \textcolor{green}{covered}

 at high tide with at least four and a half feet of water. The

 bedroom window was a broad one and opened from below. On

 \textcolor{BurntOrange}{examination} traces of blood were to be seen upon the windowsill,

 and several scattered drops were visible upon the wooden floor of

 the bedroom. Thrust away behind a curtain in the front room were

 all the clothes of Mr. Neville St. Clair, with the exception of

 his coat. His boots, his socks, his hat, and his watch--all were

 there. There were no signs of \textcolor{red}{violence} upon any of these

 garments, and there were no other traces of Mr. Neville St.

 Clair. Out of the window he must apparently have gone for no

 other exit could be discovered, and the \textcolor{BurntOrange}{ominous} bloodstains upon

 the sill gave little \textcolor{green}{promise} that he could \textcolor{green}{save} himself by

 \textcolor{BurntOrange}{swimming,} for the tide was at its very highest at the moment of

 the \textcolor{red}{tragedy.}



 "And now as to the \textcolor{red}{villains} who seemed to be \textcolor{BurntOrange}{immediately}

 \textcolor{red}{implicated} in the matter. The Lascar was known to be a man of the

 vilest antecedents, but as, by Mrs. St. Clair's story, he was

 known to have been at the foot of the stair within a very few

 seconds of her husband's appearance at the window, he could

 hardly have been more than an accessory to the \textcolor{red}{crime.} His defence

 was one of \textcolor{green}{absolute} \textcolor{red}{ignorance,} and he protested that he had no

 \textcolor{green}{knowledge} as to the doings of Hugh Boone, his lodger, and that he

 could not \textcolor{green}{account} in any way for the \textcolor{green}{presence} of the missing

 \textcolor{green}{gentleman's} clothes.



 "So much for the Lascar manager. Now for the \textcolor{red}{sinister} \textcolor{red}{cripple} who

 lives upon the second floor of the \textcolor{red}{opium} den, and who was

 certainly the last human being whose eyes \textcolor{green}{rested} upon Neville St.

 Clair. His name is Hugh Boone, and his \textcolor{red}{hideous} face is one which

 is \textcolor{green}{familiar} to every man who goes much to the City. He is a

 \textcolor{green}{professional} \textcolor{red}{beggar,} though in order to \textcolor{red}{avoid} the \textcolor{BurntOrange}{police}

 regulations he \textcolor{red}{pretends} to a \textcolor{red}{small} \textcolor{green}{trade} in wax vestas. Some

 little distance down Threadneedle Street, upon the left-hand

 side, there is, as you may have remarked, a \textcolor{red}{small} angle in the

 wall. Here it is that this \textcolor{red}{creature} takes his \textcolor{blue}{daily} seat,

 cross-legged with his tiny stock of matches on his lap, and as he

 is a piteous \textcolor{BurntOrange}{spectacle} a \textcolor{red}{small} rain of \textcolor{green}{charity} descends into the

 \textcolor{red}{greasy} leather \textcolor{BurntOrange}{cap} which \textcolor{red}{lies} upon the \textcolor{green}{pavement} beside him. I

 have \textcolor{BurntOrange}{watched} the \textcolor{green}{fellow} more than once before ever I \textcolor{blue}{thought} of

 making his \textcolor{green}{professional} acquaintance, and I have been \textcolor{blue}{surprised}

 at the \textcolor{BurntOrange}{harvest} which he has reaped in a short \textcolor{blue}{time.} His

 appearance, you see, is so \textcolor{BurntOrange}{remarkable} that no one can pass him

 without observing him. A \textcolor{BurntOrange}{shock} of orange hair, a pale face

 disfigured by a \textcolor{red}{horrible} \textcolor{red}{scar,} which, by its contraction, has

 turned up the outer edge of his upper lip, a \textcolor{green}{bulldog} chin, and a

 pair of very penetrating \textcolor{red}{dark} eyes, which \textcolor{BurntOrange}{present} a singular

 contrast to the colour of his hair, all mark him out from amid

 the common crowd of mendicants and so, too, does his \textcolor{green}{wit,} for he

 is ever \textcolor{blue}{ready} with a reply to any piece of \textcolor{red}{chaff} which may be

 thrown at him by the passers-by. This is the man whom we now

 \textcolor{green}{learn} to have been the lodger at the \textcolor{red}{opium} den, and to have been

 the last man to see the \textcolor{green}{gentleman} of whom we are in \textcolor{BurntOrange}{quest."}



 "But a \textcolor{red}{cripple!"} said I. "What could he have done single-handed

 against a man in the \textcolor{green}{prime} of life?"



 "He is a \textcolor{red}{cripple} in the \textcolor{green}{sense} that he walks with a \textcolor{red}{limp;} but in

 other \textcolor{BurntOrange}{respects} he appears to be a \textcolor{BurntOrange}{powerful} and well-nurtured man.

 Surely your \textcolor{BurntOrange}{medical} experience would tell you, Watson, that

 \textcolor{red}{weakness} in one limb is often \textcolor{BurntOrange}{compensated} for by exceptional

 \textcolor{green}{strength} in the others."



 \textcolor{BurntOrange}{"Pray} \textcolor{BurntOrange}{continue} your narrative."



 "Mrs. St. Clair had fainted at the sight of the blood upon the

 window, and she was \textcolor{green}{escorted} home in a \textcolor{green}{cab} by the \textcolor{BurntOrange}{police,} as her

 \textcolor{green}{presence} could be of no help to them in their \textcolor{blue}{investigations.}

 \textcolor{green}{Inspector} Barton, who had charge of the \textcolor{red}{case,} made a very \textcolor{green}{careful}

 \textcolor{BurntOrange}{examination} of the premises, but without finding anything which

 threw any light upon the matter. One \textcolor{red}{mistake} had been made in not

 \textcolor{red}{arresting} Boone instantly, as he was allowed some few minutes

 during which he might have \textcolor{green}{communicated} with his \textcolor{green}{friend} the

 Lascar, but this \textcolor{red}{fault} was soon remedied, and he was \textcolor{red}{seized} and

 searched, without anything being \textcolor{green}{found} which could incriminate

 him. There were, it is \textcolor{green}{true,} some blood-stains upon his right

 shirt-sleeve, but he pointed to his ring-finger, which had been

 cut near the nail, and \textcolor{green}{explained} that the \textcolor{red}{bleeding} came from

 there, adding that he had been to the window not \textcolor{blue}{long} before, and

 that the \textcolor{red}{stains} which had been observed there came \textcolor{green}{doubtless} from

 the same source. He \textcolor{red}{denied} strenuously having ever seen Mr.

 Neville St. Clair and swore that the \textcolor{green}{presence} of the clothes in

 his room was as much a \textcolor{blue}{mystery} to him as to the \textcolor{BurntOrange}{police.} As to

 Mrs. St. Clair's assertion that she had actually seen her husband

 at the window, he declared that she must have been either \textcolor{red}{mad} or

 dreaming. He was \textcolor{red}{removed,} loudly protesting, to the

 police-station, while the \textcolor{green}{inspector} remained upon the premises in

 the \textcolor{BurntOrange}{hope} that the ebbing tide might \textcolor{green}{afford} some fresh \textcolor{blue}{clue.}



 "And it did, though they hardly \textcolor{green}{found} upon the mud-bank what they

 had \textcolor{red}{feared} to find. It was Neville St. Clair's coat, and not

 Neville St. Clair, which lay uncovered as the tide receded. And

 what do you think they \textcolor{green}{found} in the pockets?"



 "I cannot imagine."



 "No, I don't think you would \textcolor{blue}{guess.} Every pocket stuffed with

 pennies and half-pennies--421 pennies and 270 half-pennies. It

 was no wonder that it had not been swept away by the tide. But a

 human body is a different matter. There is a \textcolor{red}{fierce} eddy between

 the wharf and the house. It seemed likely enough that the

 \textcolor{BurntOrange}{weighted} coat had remained when the \textcolor{red}{stripped} body had been \textcolor{red}{sucked}

 away into the river."



 "But I understand that all the other clothes were \textcolor{green}{found} in the

 room. Would the body be dressed in a coat alone?"



 "No, \textcolor{green}{sir,} but the \textcolor{green}{facts} might be met speciously enough. Suppose

 that this man Boone had thrust Neville St. Clair through the

 window, there is no human eye which could have seen the \textcolor{green}{deed.}

 What would he do then? It would of course instantly \textcolor{red}{strike} him

 that he must get rid of the tell-tale garments. He would \textcolor{red}{seize}

 the coat, then, and be in the act of throwing it out, when it

 would occur to him that it would \textcolor{BurntOrange}{swim} and not sink. He has little

 \textcolor{blue}{time,} for he has heard the scuffle downstairs when the wife tried

 to \textcolor{red}{force} her way up, and perhaps he has already heard from his

 Lascar \textcolor{green}{confederate} that the \textcolor{BurntOrange}{police} are \textcolor{blue}{hurrying} up the street.

 There is not an instant to be \textcolor{BurntOrange}{lost.} He rushes to some \textcolor{green}{secret}

 hoard, where he has accumulated the fruits of his beggary, and he

 stuffs all the coins upon which he can lay his hands into the

 pockets to make sure of the coat's sinking. He throws it out, and

 would have done the same with the other garments had not he heard

 the rush of steps below, and only just had \textcolor{blue}{time} to close the

 window when the \textcolor{BurntOrange}{police} appeared."



 "It certainly sounds feasible."



 "Well, we will take it as a working \textcolor{blue}{hypothesis} for want of a

 better. Boone, as I have told you, was \textcolor{red}{arrested} and taken to the

 station, but it could not be \textcolor{green}{shown} that there had ever before

 been anything against him. He had for years been known as a

 \textcolor{green}{professional} \textcolor{red}{beggar,} but his life appeared to have been a very

 \textcolor{BurntOrange}{quiet} and \textcolor{green}{innocent} one. There the matter stands at \textcolor{BurntOrange}{present,} and

 the \textcolor{green}{questions} which have to be solved--what Neville St. Clair was

 doing in the \textcolor{red}{opium} den, what \textcolor{blue}{happened} to him when there, where is

 he now, and what Hugh Boone had to do with his disappearance--are

 all as far from a \textcolor{green}{solution} as ever. I \textcolor{BurntOrange}{confess} that I cannot

 recall any \textcolor{red}{case} within my experience which looked at the first

 glance so simple and yet which \textcolor{BurntOrange}{presented} such \textcolor{red}{difficulties."}



 While Sherlock Holmes had been detailing this singular \textcolor{green}{series} of

 events, we had been whirling through the outskirts of the great

 town until the last straggling houses had been left behind, and

 we rattled along with a country hedge upon either side of us.

 Just as he finished, however, we drove through two scattered

 villages, where a few lights still \textcolor{BurntOrange}{glimmered} in the windows.



 "We are on the outskirts of Lee," said my \textcolor{green}{companion.} "We have

 touched on three English \textcolor{green}{counties} in our short drive, \textcolor{blue}{starting} in

 Middlesex, passing over an angle of Surrey, and ending in Kent.

 See that light among the \textcolor{BurntOrange}{trees?} That is The Cedars, and beside

 that lamp sits a woman whose \textcolor{BurntOrange}{anxious} ears have already, I have

 little \textcolor{BurntOrange}{doubt,} caught the clink of our \textcolor{green}{horse's} feet."



 "But why are you not conducting the \textcolor{red}{case} from Baker Street?" I

 asked.



 "Because there are many \textcolor{BurntOrange}{inquiries} which must be made out here.

 Mrs. St. Clair has most kindly put two rooms at my \textcolor{red}{disposal,} and

 you may \textcolor{green}{rest} \textcolor{green}{assured} that she will have nothing but a welcome for

 my \textcolor{green}{friend} and colleague. I \textcolor{red}{hate} to meet her, Watson, when I have

 no news of her husband. Here we are. Whoa, there, whoa!"



 We had \textcolor{green}{pulled} up in front of a large villa which stood within its

 own \textcolor{green}{grounds.} A stable-boy had run out to the \textcolor{green}{horse's} head, and

 springing down, I followed Holmes up the \textcolor{red}{small,} winding

 gravel-drive which \textcolor{green}{led} to the house. As we approached, the door

 flew open, and a little blonde woman stood in the opening, clad

 in some sort of light mousseline de soie, with a touch of fluffy

 pink chiffon at her neck and wrists. She stood with her figure

 outlined against the \textcolor{red}{flood} of light, one hand upon the door, one

 half-raised in her \textcolor{BurntOrange}{eagerness,} her body slightly bent, her head

 and face protruded, with \textcolor{BurntOrange}{eager} eyes and parted lips, a standing

 \textcolor{green}{question.}



 "Well?" she \textcolor{red}{cried,} "well?" And then, seeing that there were two

 of us, she gave a \textcolor{red}{cry} of \textcolor{BurntOrange}{hope} which sank into a \textcolor{red}{groan} as she saw

 that my \textcolor{green}{companion} shook his head and shrugged his \textcolor{green}{shoulders.}



 "No \textcolor{BurntOrange}{good} news?"



 "None."



 "No \textcolor{red}{bad?"}



 "No."



 "Thank \textcolor{BurntOrange}{God} for that. But come in. You must be \textcolor{red}{weary,} for you have

 had a \textcolor{blue}{long} day."



 "This is my \textcolor{green}{friend,} Dr. Watson. He has been of most \textcolor{green}{vital} use to

 me in several of my \textcolor{red}{cases,} and a \textcolor{BurntOrange}{lucky} \textcolor{blue}{chance} has made it

 possible for me to bring him out and \textcolor{green}{associate} him with this

 \textcolor{blue}{investigation."}



 "I am \textcolor{BurntOrange}{delighted} to see you," said she, pressing my hand warmly.

 "You will, I am sure, \textcolor{green}{forgive} anything that may be wanting in our

 arrangements, when you consider the blow which has come so

 \textcolor{blue}{suddenly} upon us."



 "My \textcolor{green}{dear} madam," said I, "I am an old campaigner, and if I were

 not I can very well see that no \textcolor{green}{apology} is needed. If I can be of

 any \textcolor{green}{assistance,} either to you or to my \textcolor{green}{friend} here, I shall be

 indeed \textcolor{BurntOrange}{happy."}



 "Now, Mr. Sherlock Holmes," said the lady as we entered a

 well-lit dining-room, upon the table of which a \textcolor{red}{cold} supper had

 been laid out, "I should very much like to ask you one or two

 plain \textcolor{green}{questions,} to which I \textcolor{red}{beg} that you will give a plain

 answer."



 "Certainly, madam."



 "Do not trouble about my \textcolor{BurntOrange}{feelings.} I am not \textcolor{red}{hysterical,} nor given

 to \textcolor{BurntOrange}{fainting.} I simply wish to hear your \textcolor{green}{real,} \textcolor{green}{real} opinion."



 "Upon what point?"



 "In your heart of hearts, do you think that Neville is \textcolor{BurntOrange}{alive?"}



 Sherlock Holmes seemed to be \textcolor{red}{embarrassed} by the \textcolor{green}{question.}

 "Frankly, now!" she repeated, standing upon the rug and looking

 keenly down at him as he leaned back in a basket-chair.



 "Frankly, then, madam, I do not."



 "You think that he is dead?"



 "I do."



 \textcolor{BurntOrange}{"Murdered?"}



 "I don't say that. Perhaps."



 "And on what day did he meet his \textcolor{BurntOrange}{death?"}



 "On Monday."



 "Then perhaps, Mr. Holmes, you will be \textcolor{BurntOrange}{good} enough to \textcolor{green}{explain} how

 it is that I have received a \textcolor{blue}{letter} from him to-day."



 Sherlock Holmes sprang out of his chair as if he had been

 galvanised.



 "What!" he roared.



 "Yes, to-day." She stood \textcolor{BurntOrange}{smiling,} holding up a little \textcolor{BurntOrange}{slip} of

 paper in the air.



 "May I see it?"



 "Certainly."



 He snatched it from her in his \textcolor{BurntOrange}{eagerness,} and smoothing it out

 upon the table he drew over the lamp and examined it intently. I

 had left my chair and was gazing at it over his \textcolor{green}{shoulder.} The

 envelope was a very coarse one and was stamped with the Gravesend

 postmark and with the date of that very day, or rather of the day

 before, for it was considerably after midnight.



 "Coarse writing," murmured Holmes. "Surely this is not your

 husband's writing, madam."



 "No, but the enclosure is."



 "I \textcolor{green}{perceive} also that whoever addressed the envelope had to go

 and inquire as to the address."



 "How can you tell that?"



 "The name, you see, is in perfectly \textcolor{red}{black} ink, which has dried

 itself. The \textcolor{green}{rest} is of the greyish colour, which \textcolor{green}{shows} that

 blotting-paper has been used. If it had been written straight

 off, and then \textcolor{red}{blotted,} none would be of a deep \textcolor{red}{black} shade. This

 man has written the name, and there has then been a pause before

 he wrote the address, which can only mean that he was not

 \textcolor{green}{familiar} with it. It is, of course, a \textcolor{red}{trifle,} but there is

 nothing so \textcolor{green}{important} as \textcolor{red}{trifles.} Let us now see the \textcolor{blue}{letter.} Ha!

 there has been an enclosure here!"



 "Yes, there was a ring. His signet-ring."



 "And you are sure that this is your husband's hand?"



 "One of his hands."



 "One?"



 "His hand when he wrote hurriedly. It is very unlike his \textcolor{green}{usual}

 writing, and yet I know it well."



 "'Dearest do not be \textcolor{BurntOrange}{frightened.} All will come well. There is a

 huge \textcolor{red}{error} which it may take some little \textcolor{blue}{time} to \textcolor{green}{rectify.}

 \textcolor{BurntOrange}{Wait} in patience.--NEVILLE.' Written in pencil upon the fly-leaf

 of a book, octavo size, no water-mark. Hum! Posted to-day in

 Gravesend by a man with a \textcolor{red}{dirty} thumb. Ha! And the \textcolor{red}{flap} has been

 gummed, if I am not very much in \textcolor{red}{error,} by a person who had been

 chewing \textcolor{red}{tobacco.} And you have no \textcolor{BurntOrange}{doubt} that it is your husband's

 hand, madam?"



 "None. Neville wrote those \textcolor{green}{words."}



 "And they were posted to-day at Gravesend. Well, Mrs. St. Clair,

 the clouds lighten, though I should not venture to say that the

 \textcolor{red}{danger} is over."



 "But he must be \textcolor{BurntOrange}{alive,} Mr. Holmes."



 "Unless this is a \textcolor{green}{clever} \textcolor{red}{forgery} to put us on the \textcolor{red}{wrong} scent.

 The ring, after all, proves nothing. It may have been taken from

 him."



 "No, no; it is, it is his very own writing!"



 "Very well. It may, however, have been written on Monday and only

 posted to-day."



 "That is possible."



 "If so, much may have \textcolor{blue}{happened} between."



 "Oh, you must not \textcolor{red}{discourage} me, Mr. Holmes. I know that all is

 well with him. There is so keen a \textcolor{BurntOrange}{sympathy} between us that I

 should know if \textcolor{red}{evil} came upon him. On the very day that I saw him

 last he cut himself in the bedroom, and yet I in the dining-room

 rushed upstairs instantly with the utmost \textcolor{green}{certainty} that

 something had \textcolor{blue}{happened.} Do you think that I would respond to such

 a \textcolor{red}{trifle} and yet be \textcolor{red}{ignorant} of his \textcolor{BurntOrange}{death?"}



 "I have seen too much not to know that the \textcolor{green}{impression} of a woman

 may be more \textcolor{green}{valuable} than the conclusion of an analytical

 reasoner. And in this \textcolor{blue}{letter} you certainly have a very strong

 piece of evidence to \textcolor{green}{corroborate} your view. But if your husband

 is \textcolor{BurntOrange}{alive} and able to write \textcolor{blue}{letters,} why should he remain away

 from you?"



 "I cannot imagine. It is \textcolor{red}{unthinkable."}



 "And on Monday he made no remarks before \textcolor{BurntOrange}{leaving} you?"



 "No."



 "And you were \textcolor{blue}{surprised} to see him in Swandam Lane?"



 "Very much so."



 "Was the window open?"



 "Yes."



 "Then he might have called to you?"



 "He might."



 "He only, as I understand, gave an inarticulate \textcolor{red}{cry?"}



 "Yes."



 "A call for help, you \textcolor{blue}{thought?"}



 "Yes. He waved his hands."



 "But it might have been a \textcolor{red}{cry} of \textcolor{BurntOrange}{surprise.} \textcolor{BurntOrange}{Astonishment} at the

 \textcolor{BurntOrange}{unexpected} sight of you might cause him to throw up his hands?"



 "It is possible."



 "And you \textcolor{blue}{thought} he was \textcolor{green}{pulled} back?"



 "He \textcolor{red}{disappeared} so \textcolor{blue}{suddenly."}



 "He might have leaped back. You did not see anyone else in the

 room?"



 "No, but this \textcolor{red}{horrible} man \textcolor{BurntOrange}{confessed} to having been there, and

 the Lascar was at the foot of the stairs."



 "Quite so. Your husband, as far as you could see, had his

 ordinary clothes on?"



 "But without his collar or tie. I distinctly saw his bare

 throat."



 "Had he ever spoken of Swandam Lane?"



 "Never."



 "Had he ever \textcolor{green}{showed} any signs of having taken \textcolor{red}{opium?"}



 "Never."



 "Thank you, Mrs. St. Clair. Those are the \textcolor{green}{principal} points about

 which I wished to be absolutely clear. We shall now have a little

 supper and then retire, for we may have a very busy day

 \textcolor{blue}{to-morrow."}



 A large and comfortable double-bedded room had been placed at our

 \textcolor{red}{disposal,} and I was quickly between the sheets, for I was \textcolor{red}{weary}

 after my night of \textcolor{BurntOrange}{adventure.} Sherlock Holmes was a man, however,

 who, when he had an unsolved \textcolor{red}{problem} upon his mind, would go for

 days, and even for a week, without \textcolor{green}{rest,} turning it over,

 rearranging his \textcolor{green}{facts,} looking at it from every point of view

 until he had either fathomed it or \textcolor{BurntOrange}{convinced} himself that his

 data were \textcolor{red}{insufficient.} It was soon \textcolor{green}{evident} to me that he was now

 \textcolor{BurntOrange}{preparing} for an all-night sitting. He took off his coat and

 waistcoat, put on a large \textcolor{red}{blue} dressing-gown, and then wandered

 about the room collecting \textcolor{green}{pillows} from his bed and \textcolor{green}{cushions} from

 the sofa and armchairs. With these he \textcolor{green}{constructed} a sort of

 Eastern \textcolor{green}{divan,} upon which he perched himself cross-legged, with

 an ounce of shag \textcolor{red}{tobacco} and a box of matches laid out in front

 of him. In the dim light of the lamp I saw him sitting there, an

 old briar pipe between his lips, his eyes fixed vacantly upon the

 corner of the ceiling, the \textcolor{red}{blue} smoke \textcolor{green}{curling} up from him,

 silent, motionless, with the light shining upon his strong-set

 aquiline \textcolor{green}{features.} So he sat as I dropped off to sleep, and so he

 sat when a \textcolor{blue}{sudden} \textcolor{BurntOrange}{ejaculation} caused me to wake up, and I \textcolor{green}{found}

 the summer \textcolor{BurntOrange}{sun} shining into the apartment. The pipe was still

 between his lips, the smoke still \textcolor{green}{curled} upward, and the room was

 \textcolor{green}{full} of a dense \textcolor{red}{tobacco} \textcolor{red}{haze,} but nothing remained of the heap of

 shag which I had seen upon the previous night.



 "Awake, Watson?" he asked.



 "Yes."



 "Game for a morning drive?"



 "Certainly."



 "Then dress. No one is stirring yet, but I know where the

 stable-boy sleeps, and we shall soon have the trap out." He

 \textcolor{BurntOrange}{chuckled} to himself as he \textcolor{red}{spoke,} his eyes \textcolor{BurntOrange}{twinkled,} and he seemed

 a different man to the sombre \textcolor{green}{thinker} of the previous night.



 As I dressed I glanced at my \textcolor{BurntOrange}{watch.} It was no wonder that no one

 was stirring. It was twenty-five minutes past four. I had hardly

 finished when Holmes returned with the news that the \textcolor{red}{boy} was

 putting in the \textcolor{green}{horse.}



 "I want to test a little \textcolor{BurntOrange}{theory} of mine," said he, \textcolor{green}{pulling} on his

 boots. "I think, Watson, that you are now standing in the

 \textcolor{green}{presence} of one of the most \textcolor{green}{absolute} \textcolor{red}{fools} in Europe. I \textcolor{BurntOrange}{deserve}

 to be \textcolor{red}{kicked} from here to Charing \textcolor{red}{Cross.} But I think I have the

 key of the affair now."



 "And where is it?" I asked, \textcolor{BurntOrange}{smiling.}



 "In the bathroom," he answered. "Oh, yes, I am not \textcolor{green}{joking,"} he

 continued, seeing my look of incredulity. "I have just been

 there, and I have taken it out, and I have got it in this

 Gladstone bag. Come on, my \textcolor{red}{boy,} and we shall see whether it will

 not fit the lock."



 We made our way downstairs as quietly as possible, and out into

 the bright morning \textcolor{green}{sunshine.} In the road stood our \textcolor{green}{horse} and

 trap, with the half-clad stable-boy \textcolor{BurntOrange}{waiting} at the head. We both

 sprang in, and away we dashed down the London Road. A few country

 carts were stirring, bearing in vegetables to the metropolis, but

 the lines of villas on either side were as silent and \textcolor{red}{lifeless} as

 some city in a dream.



 "It has been in some points a singular \textcolor{red}{case,"} said Holmes,

 flicking the \textcolor{green}{horse} on into a gallop. "I \textcolor{BurntOrange}{confess} that I have been

 as \textcolor{red}{blind} as a mole, but it is better to \textcolor{green}{learn} \textcolor{green}{wisdom} \textcolor{red}{late} than

 never to \textcolor{green}{learn} it at all."



 In town the earliest risers were just beginning to look sleepily

 from their windows as we drove through the streets of the Surrey

 side. Passing down the Waterloo Bridge Road we \textcolor{red}{crossed} over the

 river, and dashing up Wellington Street wheeled sharply to the

 right and \textcolor{green}{found} ourselves in Bow Street. Sherlock Holmes was well

 known to the \textcolor{red}{force,} and the two \textcolor{green}{constables} at the door \textcolor{green}{saluted}

 him. One of them held the \textcolor{green}{horse's} head while the other \textcolor{green}{led} us in.



 "Who is on duty?" asked Holmes.



 \textcolor{green}{"Inspector} Bradstreet, \textcolor{green}{sir."}



 "Ah, Bradstreet, how are you?" A tall, stout \textcolor{green}{official} had come

 down the stone-flagged passage, in a peaked \textcolor{BurntOrange}{cap} and frogged

 jacket. "I wish to have a \textcolor{BurntOrange}{quiet} \textcolor{green}{word} with you, Bradstreet."

 "Certainly, Mr. Holmes. Step into my room here." It was a \textcolor{red}{small,}

 office-like room, with a huge ledger upon the table, and a

 telephone projecting from the wall. The \textcolor{green}{inspector} sat down at his

 desk.



 "What can I do for you, Mr. Holmes?"



 "I called about that beggarman, Boone--the one who was charged

 with being \textcolor{red}{concerned} in the disappearance of Mr. Neville St.

 Clair, of Lee."



 "Yes. He was brought up and \textcolor{red}{remanded} for further \textcolor{BurntOrange}{inquiries."}



 "So I heard. You have him here?"



 "In the cells."



 "Is he \textcolor{BurntOrange}{quiet?"}



 "Oh, he gives no trouble. But he is a \textcolor{red}{dirty} \textcolor{BurntOrange}{scoundrel."}



 \textcolor{red}{"Dirty?"}



 "Yes, it is all we can do to make him wash his hands, and his

 face is as \textcolor{red}{black} as a tinker's. Well, when once his \textcolor{red}{case} has been

 settled, he will have a regular \textcolor{red}{prison} \textcolor{green}{bath;} and I think, if you

 saw him, you would \textcolor{green}{agree} with me that he needed it."



 "I should like to see him very much."



 "Would you? That is easily done. Come this way. You can \textcolor{BurntOrange}{leave}

 your bag."



 "No, I think that \textcolor{red}{I'll} take it."



 "Very \textcolor{BurntOrange}{good.} Come this way, if you please." He \textcolor{green}{led} us down a

 passage, opened a barred door, passed down a winding stair, and

 brought us to a whitewashed corridor with a line of doors on each

 side.



 "The third on the right is his," said the \textcolor{green}{inspector.} "Here it

 is!" He quietly \textcolor{BurntOrange}{shot} back a panel in the upper part of the door

 and glanced through.



 "He is asleep," said he. "You can see him very well."



 We both put our eyes to the \textcolor{red}{grating.} The \textcolor{red}{prisoner} lay with his

 face towards us, in a very deep sleep, breathing slowly and

 \textcolor{red}{heavily.} He was a middle-sized man, coarsely clad as became his

 calling, with a coloured shirt protruding through the rent in his

 tattered coat. He was, as the \textcolor{green}{inspector} had said, extremely

 \textcolor{red}{dirty,} but the \textcolor{red}{grime} which \textcolor{green}{covered} his face could not \textcolor{red}{conceal} its

 repulsive \textcolor{red}{ugliness.} A broad wheal from an old \textcolor{red}{scar} ran right

 across it from eye to chin, and by its contraction had turned up

 one side of the upper lip, so that three teeth were \textcolor{BurntOrange}{exposed} in a

 perpetual \textcolor{red}{snarl.} A \textcolor{BurntOrange}{shock} of very bright red hair \textcolor{BurntOrange}{grew} low over

 his eyes and forehead.



 "He's a \textcolor{green}{beauty,} isn't he?" said the \textcolor{green}{inspector.}



 "He certainly needs a wash," remarked Holmes. "I had an idea that

 he might, and I took the \textcolor{BurntOrange}{liberty} of bringing the tools with me."

 He opened the Gladstone bag as he \textcolor{red}{spoke,} and took out, to my

 \textcolor{BurntOrange}{astonishment,} a very large bath-sponge.



 "He! he! You are a funny one," \textcolor{BurntOrange}{chuckled} the \textcolor{green}{inspector.}



 "Now, if you will have the great \textcolor{BurntOrange}{goodness} to open that door very

 quietly, we will soon make him cut a much more \textcolor{green}{respectable}

 figure."



 "Well, I don't know why not," said the \textcolor{green}{inspector.} "He doesn't

 look a \textcolor{green}{credit} to the Bow Street cells, does he?" He \textcolor{BurntOrange}{slipped} his

 key into the lock, and we all very quietly entered the cell. The

 sleeper half turned, and then settled down once more into a deep

 slumber. Holmes stooped to the water-jug, moistened his \textcolor{red}{sponge,}

 and then rubbed it twice vigorously across and down the

 \textcolor{red}{prisoner's} face.



 "Let me introduce you," he \textcolor{BurntOrange}{shouted,} "to Mr. Neville St. Clair, of

 Lee, in the \textcolor{green}{county} of Kent."



 Never in my life have I seen such a sight. The man's face peeled

 off under the \textcolor{red}{sponge} like the \textcolor{red}{bark} from a \textcolor{BurntOrange}{tree.} Gone was the

 coarse brown tint! Gone, too, was the \textcolor{red}{horrid} \textcolor{red}{scar} which had

 seamed it across, and the twisted lip which had given the

 repulsive \textcolor{red}{sneer} to the face! A \textcolor{red}{twitch} brought away the tangled

 red hair, and there, sitting up in his bed, was a pale,

 sad-faced, refined-looking man, black-haired and smooth-skinned,

 rubbing his eyes and \textcolor{BurntOrange}{staring} about him with sleepy \textcolor{BurntOrange}{bewilderment.}

 Then \textcolor{blue}{suddenly} realising the exposure, he \textcolor{red}{broke} into a \textcolor{BurntOrange}{scream} and

 threw himself down with his face to the \textcolor{green}{pillow.}



 "Great heavens!" \textcolor{red}{cried} the \textcolor{green}{inspector,} "it is, indeed, the missing

 man. I know him from the photograph."



 The \textcolor{red}{prisoner} turned with the \textcolor{red}{reckless} air of a man who \textcolor{red}{abandons}

 himself to his destiny. "Be it so," said he. "And \textcolor{BurntOrange}{pray} what am I

 charged with?"



 "With making away with Mr. Neville St.-- Oh, come, you can't be

 charged with that unless they make a \textcolor{red}{case} of \textcolor{blue}{attempted} \textcolor{red}{suicide} of

 it," said the \textcolor{green}{inspector} with a \textcolor{BurntOrange}{grin.} "Well, I have been

 twenty-seven years in the \textcolor{red}{force,} but this really takes the cake."



 "If I am Mr. Neville St. Clair, then it is \textcolor{green}{obvious} that no \textcolor{red}{crime}

 has been committed, and that, therefore, I am illegally

 \textcolor{red}{detained."}



 "No \textcolor{red}{crime,} but a very great \textcolor{red}{error} has been committed," said

 Holmes. "You would have done better to have \textcolor{green}{trusted} your wife."



 "It was not the wife; it was the \textcolor{BurntOrange}{children,"} \textcolor{red}{groaned} the \textcolor{red}{prisoner.}

 \textcolor{BurntOrange}{"God} help me, I would not have them \textcolor{red}{ashamed} of their \textcolor{green}{father.} My

 \textcolor{BurntOrange}{God!} What an exposure! What can I do?"



 Sherlock Holmes sat down beside him on the \textcolor{red}{couch} and patted him

 kindly on the \textcolor{green}{shoulder.}



 "If you \textcolor{BurntOrange}{leave} it to a \textcolor{BurntOrange}{court} of \textcolor{green}{law} to clear the matter up," said

 he, "of course you can hardly \textcolor{red}{avoid} publicity. On the other hand,

 if you \textcolor{BurntOrange}{convince} the \textcolor{BurntOrange}{police} \textcolor{green}{authorities} that there is no possible

 \textcolor{red}{case} against you, I do not know that there is any \textcolor{green}{reason} that the

 details should find their way into the papers. \textcolor{green}{Inspector}

 Bradstreet would, I am sure, make notes upon anything which you

 might tell us and \textcolor{blue}{submit} it to the \textcolor{green}{proper} \textcolor{green}{authorities.} The \textcolor{red}{case}

 would then never go into \textcolor{BurntOrange}{court} at all."



 \textcolor{BurntOrange}{"God} \textcolor{BurntOrange}{bless} you!" \textcolor{red}{cried} the \textcolor{red}{prisoner} passionately. "I would have

 \textcolor{green}{endured} \textcolor{red}{imprisonment,} \textcolor{green}{ay,} even \textcolor{BurntOrange}{execution,} rather than have left

 my \textcolor{red}{miserable} \textcolor{green}{secret} as a family \textcolor{red}{blot} to my \textcolor{BurntOrange}{children.}



 "You are the first who have ever heard my story. My \textcolor{green}{father} was a

 schoolmaster in Chesterfield, where I received an \textcolor{green}{excellent}

 education. I travelled in my \textcolor{BurntOrange}{youth,} took to the stage, and

 \textcolor{BurntOrange}{finally} became a \textcolor{green}{reporter} on an evening paper in London. One day

 my editor wished to have a \textcolor{green}{series} of articles upon \textcolor{red}{begging} in the

 metropolis, and I \textcolor{BurntOrange}{volunteered} to \textcolor{green}{supply} them. There was the point

 from which all my \textcolor{BurntOrange}{adventures} \textcolor{blue}{started.} It was only by trying

 \textcolor{red}{begging} as an amateur that I could get the \textcolor{green}{facts} upon which to

 \textcolor{green}{base} my articles. When an actor I had, of course, \textcolor{green}{learned} all the

 \textcolor{green}{secrets} of making up, and had been \textcolor{green}{famous} in the green-room for

 my skill. I took \textcolor{green}{advantage} now of my \textcolor{green}{attainments.} I painted my

 face, and to make myself as pitiable as possible I made a \textcolor{BurntOrange}{good}

 \textcolor{red}{scar} and fixed one side of my lip in a twist by the \textcolor{green}{aid} of a

 \textcolor{red}{small} \textcolor{BurntOrange}{slip} of flesh-coloured plaster. Then with a red head of

 hair, and an appropriate dress, I took my station in the business

 part of the city, \textcolor{red}{ostensibly} as a match-seller but really as a

 \textcolor{red}{beggar.} For seven hours I \textcolor{green}{plied} my \textcolor{green}{trade,} and when I returned

 home in the evening I \textcolor{green}{found} to my \textcolor{BurntOrange}{surprise} that I had received no

 less than 26s. 4d.



 "I wrote my articles and \textcolor{blue}{thought} little more of the matter until,

 some \textcolor{blue}{time} later, I backed a bill for a \textcolor{green}{friend} and had a writ

 \textcolor{BurntOrange}{served} upon me for 25 \textcolor{red}{pounds.} I was at my \textcolor{green}{wit's} end where to get

 the \textcolor{BurntOrange}{money,} but a \textcolor{blue}{sudden} idea came to me. I \textcolor{red}{begged} a fortnight's

 \textcolor{green}{grace} from the creditor, asked for a \textcolor{BurntOrange}{holiday} from my employers,

 and \textcolor{red}{spent} the \textcolor{blue}{time} in \textcolor{red}{begging} in the City under my disguise. In

 ten days I had the \textcolor{BurntOrange}{money} and had paid the \textcolor{red}{debt.}



 "Well, you can imagine how hard it was to settle down to \textcolor{red}{arduous}

 work at 2 \textcolor{red}{pounds} a week when I knew that I could \textcolor{green}{earn} as much in

 a day by smearing my face with a little paint, laying my \textcolor{BurntOrange}{cap} on

 the \textcolor{green}{ground,} and sitting still. It was a \textcolor{blue}{long} \textcolor{red}{fight} between my

 \textcolor{green}{pride} and the \textcolor{BurntOrange}{money,} but the dollars won at last, and I threw up

 reporting and sat day after day in the corner which I had first

 \textcolor{green}{chosen,} \textcolor{BurntOrange}{inspiring} \textcolor{red}{pity} by my \textcolor{red}{ghastly} face and \textcolor{green}{filling} my pockets

 with coppers. Only one man knew my \textcolor{green}{secret.} He was the keeper of a

 low den in which I used to lodge in Swandam Lane, where I could

 every morning emerge as a squalid \textcolor{red}{beggar} and in the evenings

 transform myself into a well-dressed man about town. This \textcolor{green}{fellow,}

 a Lascar, was well paid by me for his rooms, so that I knew that

 my \textcolor{green}{secret} was \textcolor{green}{safe} in his \textcolor{red}{possession.}



 "Well, very soon I \textcolor{green}{found} that I was \textcolor{green}{saving} \textcolor{green}{considerable} sums of

 \textcolor{BurntOrange}{money.} I do not mean that any \textcolor{red}{beggar} in the streets of London

 could \textcolor{green}{earn} 700 \textcolor{red}{pounds} a year--which is less than my average

 takings--but I had exceptional \textcolor{green}{advantages} in my power of making

 up, and also in a facility of repartee, which \textcolor{BurntOrange}{improved} by

 \textcolor{green}{practice} and made me quite a recognised character in the City.

 All day a stream of pennies, varied by silver, poured in upon me,

 and it was a very \textcolor{red}{bad} day in which I failed to take 2 \textcolor{red}{pounds.}



 "As I \textcolor{BurntOrange}{grew} richer I \textcolor{BurntOrange}{grew} more ambitious, took a house in the

 country, and eventually married, without anyone having a

 \textcolor{red}{suspicion} as to my \textcolor{green}{real} \textcolor{green}{occupation.} My \textcolor{green}{dear} wife knew that I had

 business in the City. She little knew what.



 "Last Monday I had finished for the day and was dressing in my

 room above the \textcolor{red}{opium} den when I looked out of my window and saw,

 to my \textcolor{BurntOrange}{horror} and \textcolor{BurntOrange}{astonishment,} that my wife was standing in the

 street, with her eyes fixed \textcolor{green}{full} upon me. I gave a \textcolor{red}{cry} of

 \textcolor{BurntOrange}{surprise,} threw up my arms to \textcolor{green}{cover} my face, and, rushing to my

 confidant, the Lascar, entreated him to \textcolor{red}{prevent} anyone from

 coming up to me. I heard her voice downstairs, but I knew that

 she could not ascend. Swiftly I threw off my clothes, \textcolor{green}{pulled} on

 those of a \textcolor{red}{beggar,} and put on my pigments and wig. Even a wife's

 eyes could not pierce so complete a disguise. But then it

 occurred to me that there might be a search in the room, and that

 the clothes might \textcolor{BurntOrange}{betray} me. I threw open the window, reopening

 by my \textcolor{red}{violence} a \textcolor{red}{small} cut which I had \textcolor{red}{inflicted} upon myself in

 the bedroom that morning. Then I \textcolor{red}{seized} my coat, which was

 \textcolor{BurntOrange}{weighted} by the coppers which I had just transferred to it from

 the leather bag in which I carried my takings. I hurled it out of

 the window, and it \textcolor{red}{disappeared} into the Thames. The other clothes

 would have followed, but at that moment there was a rush of

 \textcolor{green}{constables} up the stair, and a few minutes after I \textcolor{green}{found,} rather,

 I \textcolor{BurntOrange}{confess,} to my \textcolor{green}{relief,} that instead of being identified as Mr.

 Neville St. Clair, I was \textcolor{red}{arrested} as his \textcolor{red}{murderer.}



 "I do not know that there is anything else for me to \textcolor{green}{explain.} I

 was determined to \textcolor{green}{preserve} my disguise as \textcolor{blue}{long} as possible, and

 hence my preference for a \textcolor{red}{dirty} face. Knowing that my wife would

 be \textcolor{red}{terribly} \textcolor{BurntOrange}{anxious,} I \textcolor{BurntOrange}{slipped} off my ring and \textcolor{green}{confided} it to the

 Lascar at a moment when no \textcolor{green}{constable} was \textcolor{BurntOrange}{watching} me, together

 with a \textcolor{blue}{hurried} scrawl, telling her that she had no cause to

 \textcolor{red}{fear."}



 "That note only reached her yesterday," said Holmes.



 \textcolor{BurntOrange}{"Good} \textcolor{BurntOrange}{God!} What a week she must have \textcolor{red}{spent!"}



 "The \textcolor{BurntOrange}{police} have \textcolor{BurntOrange}{watched} this Lascar," said \textcolor{green}{Inspector} Bradstreet,

 "and I can quite understand that he might find it \textcolor{red}{difficult} to

 post a \textcolor{blue}{letter} unobserved. Probably he handed it to some sailor

 \textcolor{green}{customer} of his, who forgot all about it for some days."



 "That was it," said Holmes, nodding approvingly; "I have no \textcolor{BurntOrange}{doubt}

 of it. But have you never been \textcolor{red}{prosecuted} for \textcolor{red}{begging?"}



 "Many \textcolor{blue}{times;} but what was a fine to me?"



 "It must stop here, however," said Bradstreet. "If the \textcolor{BurntOrange}{police} are

 to \textcolor{green}{hush} this thing up, there must be no more of Hugh Boone."



 "I have sworn it by the most solemn \textcolor{green}{oaths} which a man can take."



 "In that \textcolor{red}{case} I think that it is probable that no further steps

 may be taken. But if you are \textcolor{green}{found} again, then all must come out.

 I am sure, Mr. Holmes, that we are very much indebted to you for

 having cleared the matter up. I wish I knew how you reach your

 \textcolor{blue}{results."}



 "I reached this one," said my \textcolor{green}{friend,} "by sitting upon five

 \textcolor{green}{pillows} and consuming an ounce of shag. I think, Watson, that if

 we drive to Baker Street we shall just be in \textcolor{blue}{time} for \textcolor{green}{breakfast."}







 VII. THE \textcolor{BurntOrange}{ADVENTURE} OF THE \textcolor{red}{BLUE} CARBUNCLE



 I had called upon my \textcolor{green}{friend} Sherlock Holmes upon the second

 morning after Christmas, with the intention of wishing him the

 \textcolor{BurntOrange}{compliments} of the season. He was \textcolor{red}{lounging} upon the sofa in a

 purple dressing-gown, a pipe-rack within his reach upon the

 right, and a pile of crumpled morning papers, evidently newly

 \textcolor{green}{studied,} near at hand. Beside the \textcolor{red}{couch} was a wooden chair, and

 on the angle of the back hung a very seedy and \textcolor{red}{disreputable}

 hard-felt hat, much the \textcolor{red}{worse} for \textcolor{BurntOrange}{wear,} and \textcolor{red}{cracked} in several

 places. A lens and a forceps \textcolor{red}{lying} upon the seat of the chair

 \textcolor{green}{suggested} that the hat had been suspended in this manner for the

 purpose of \textcolor{BurntOrange}{examination.}



 "You are engaged," said I; "perhaps I \textcolor{BurntOrange}{interrupt} you."



 "Not at all. I am \textcolor{BurntOrange}{glad} to have a \textcolor{green}{friend} with whom I can discuss

 my \textcolor{blue}{results.} The matter is a perfectly trivial one"--he jerked his

 thumb in the direction of the old hat--"but there are points in

 connection with it which are not entirely devoid of \textcolor{green}{interest} and

 even of \textcolor{green}{instruction."}



 I seated myself in his armchair and warmed my hands before his

 crackling \textcolor{red}{fire,} for a sharp frost had set in, and the windows

 were thick with the ice \textcolor{green}{crystals.} "I suppose," I remarked, "that,

 homely as it looks, this thing has some \textcolor{red}{deadly} story linked on to

 it--that it is the \textcolor{blue}{clue} which will \textcolor{green}{guide} you in the \textcolor{green}{solution} of

 some \textcolor{blue}{mystery} and the \textcolor{red}{punishment} of some \textcolor{red}{crime."}



 "No, no. No \textcolor{red}{crime,"} said Sherlock Holmes, \textcolor{BurntOrange}{laughing.} "Only one of

 those \textcolor{green}{whimsical} little \textcolor{blue}{incidents} which will \textcolor{blue}{happen} when you have

 four million human beings all jostling each other within the

 space of a few square miles. Amid the \textcolor{green}{action} and reaction of so

 dense a \textcolor{red}{swarm} of \textcolor{green}{humanity,} every possible combination of events

 may be \textcolor{BurntOrange}{expected} to take place, and many a little \textcolor{red}{problem} will be

 \textcolor{BurntOrange}{presented} which may be \textcolor{red}{striking} and \textcolor{BurntOrange}{bizarre} without being

 \textcolor{red}{criminal.} We have already had experience of such."



 "So much so," I remarked, "that of the last six \textcolor{red}{cases} which I

 have added to my notes, three have been entirely free of any

 \textcolor{green}{legal} \textcolor{red}{crime."}



 "Precisely. You allude to my \textcolor{blue}{attempt} to recover the Irene Adler

 papers, to the singular \textcolor{red}{case} of Miss Mary Sutherland, and to the

 \textcolor{BurntOrange}{adventure} of the man with the twisted lip. Well, I have no \textcolor{BurntOrange}{doubt}

 that this \textcolor{red}{small} matter will \textcolor{red}{fall} into the same \textcolor{green}{innocent} category.

 You know Peterson, the commissionaire?"



 "Yes."



 "It is to him that this \textcolor{BurntOrange}{trophy} belongs."



 "It is his hat."



 "No, no, he \textcolor{green}{found} it. Its owner is \textcolor{BurntOrange}{unknown.} I \textcolor{red}{beg} that you will

 look upon it not as a \textcolor{red}{battered} billycock but as an \textcolor{green}{intellectual}

 \textcolor{red}{problem.} And, first, as to how it came here. It \textcolor{blue}{arrived} upon

 Christmas morning, in company with a \textcolor{BurntOrange}{good} \textcolor{red}{fat} goose, which is, I

 have no \textcolor{BurntOrange}{doubt,} roasting at this moment in front of Peterson's

 \textcolor{red}{fire.} The \textcolor{green}{facts} are these: about four o'clock on Christmas

 morning, Peterson, who, as you know, is a very \textcolor{BurntOrange}{honest} \textcolor{green}{fellow,} was

 returning from some \textcolor{red}{small} jollification and was making his way

 homeward down Tottenham \textcolor{BurntOrange}{Court} Road. In front of him he saw, in

 the gaslight, a tallish man, walking with a slight \textcolor{blue}{stagger,} and

 carrying a \textcolor{BurntOrange}{white} goose slung over his \textcolor{green}{shoulder.} As he reached the

 corner of Goodge Street, a \textcolor{red}{row} \textcolor{red}{broke} out between this \textcolor{red}{stranger}

 and a little knot of roughs. One of the latter knocked off the

 man's hat, on which he raised his stick to \textcolor{BurntOrange}{defend} himself and,

 swinging it over his head, \textcolor{red}{smashed} the shop window behind him.

 Peterson had rushed \textcolor{green}{forward} to \textcolor{green}{protect} the \textcolor{red}{stranger} from his

 \textcolor{red}{assailants;} but the man, \textcolor{BurntOrange}{shocked} at having \textcolor{red}{broken} the window, and

 seeing an official-looking person in uniform rushing towards him,

 dropped his goose, took to his \textcolor{red}{heels,} and \textcolor{BurntOrange}{vanished} amid the

 \textcolor{BurntOrange}{labyrinth} of \textcolor{red}{small} streets which \textcolor{red}{lie} at the back of Tottenham

 \textcolor{BurntOrange}{Court} Road. The roughs had also \textcolor{red}{fled} at the appearance of

 Peterson, so that he was left in \textcolor{red}{possession} of the field of

 \textcolor{red}{battle,} and also of the \textcolor{red}{spoils} of \textcolor{BurntOrange}{victory} in the \textcolor{green}{shape} of this

 \textcolor{red}{battered} hat and a most unimpeachable Christmas goose."



 "Which surely he restored to their owner?"



 "My \textcolor{green}{dear} \textcolor{green}{fellow,} there \textcolor{red}{lies} the \textcolor{red}{problem.} It is \textcolor{green}{true} that 'For

 Mrs. Henry Baker' was printed upon a \textcolor{red}{small} card which was tied to

 the bird's left leg, and it is also \textcolor{green}{true} that the initials 'H.

 B.' are \textcolor{green}{legible} upon the lining of this hat, but as there are

 some thousands of Bakers, and some hundreds of Henry Bakers in

 this city of ours, it is not easy to restore \textcolor{BurntOrange}{lost} property to any

 one of them."



 "What, then, did Peterson do?"



 "He brought round both hat and goose to me on Christmas morning,

 knowing that even the \textcolor{red}{smallest} \textcolor{red}{problems} are of \textcolor{green}{interest} to me.

 The goose we \textcolor{green}{retained} until this morning, when there were signs

 that, in \textcolor{red}{spite} of the slight frost, it would be well that it

 should be \textcolor{green}{eaten} without unnecessary \textcolor{red}{delay.} Its finder has carried

 it off, therefore, to fulfil the \textcolor{BurntOrange}{ultimate} destiny of a goose,

 while I \textcolor{BurntOrange}{continue} to \textcolor{green}{retain} the hat of the \textcolor{BurntOrange}{unknown} \textcolor{green}{gentleman} who

 \textcolor{BurntOrange}{lost} his Christmas \textcolor{green}{dinner."}



 "Did he not advertise?"



 "No."



 "Then, what \textcolor{blue}{clue} could you have as to his identity?"



 "Only as much as we can deduce."



 "From his hat?"



 "Precisely."



 "But you are \textcolor{green}{joking.} What can you gather from this old \textcolor{red}{battered}

 felt?"



 "Here is my lens. You know my methods. What can you gather

 yourself as to the \textcolor{green}{individuality} of the man who has \textcolor{red}{worn} this

 article?"



 I took the tattered object in my hands and turned it over rather

 ruefully. It was a very ordinary \textcolor{red}{black} hat of the \textcolor{green}{usual} round

 \textcolor{green}{shape,} hard and much the \textcolor{red}{worse} for \textcolor{BurntOrange}{wear.} The lining had been of

 red \textcolor{green}{silk,} but was a \textcolor{BurntOrange}{good} \textcolor{BurntOrange}{deal} discoloured. There was no maker's

 name; but, as Holmes had remarked, the initials "H. B." were

 scrawled upon one side. It was pierced in the brim for a

 hat-securer, but the elastic was missing. For the \textcolor{green}{rest,} it was

 \textcolor{red}{cracked,} exceedingly dusty, and spotted in several places,

 although there seemed to have been some \textcolor{blue}{attempt} to \textcolor{red}{hide} the

 discoloured \textcolor{red}{patches} by smearing them with ink.



 "I can see nothing," said I, handing it back to my \textcolor{green}{friend.}



 "On the \textcolor{red}{contrary,} Watson, you can see everything. You fail,

 however, to \textcolor{green}{reason} from what you see. You are too \textcolor{red}{timid} in

 drawing your inferences."



 "Then, \textcolor{BurntOrange}{pray} tell me what it is that you can infer from this hat?"



 He picked it up and gazed at it in the peculiar introspective

 fashion which was characteristic of him. "It is perhaps less

 suggestive than it might have been," he remarked, "and yet there

 are a few inferences which are very distinct, and a few others

 which represent at least a strong \textcolor{green}{balance} of \textcolor{blue}{probability.} That

 the man was highly \textcolor{green}{intellectual} is of course \textcolor{green}{obvious} upon the

 face of it, and also that he was \textcolor{green}{fairly} well-to-do within the

 last three years, although he has now \textcolor{red}{fallen} upon \textcolor{red}{evil} days. He

 had \textcolor{BurntOrange}{foresight,} but has less now than formerly, pointing to a

 \textcolor{BurntOrange}{moral} retrogression, which, when taken with the \textcolor{red}{decline} of his

 \textcolor{BurntOrange}{fortunes,} seems to indicate some \textcolor{red}{evil} \textcolor{BurntOrange}{influence,} probably drink,

 at work upon him. This may \textcolor{green}{account} also for the \textcolor{green}{obvious} \textcolor{green}{fact} that

 his wife has ceased to \textcolor{green}{love} him."



 "My \textcolor{green}{dear} Holmes!"



 "He has, however, \textcolor{green}{retained} some \textcolor{green}{degree} of self-respect," he

 continued, \textcolor{red}{disregarding} my remonstrance. "He is a man who \textcolor{green}{leads} a

 sedentary life, goes out little, is out of training entirely, is

 middle-aged, has grizzled hair which he has had cut within the

 last few days, and which he anoints with lime-cream. These are

 the more \textcolor{green}{patent} \textcolor{green}{facts} which are to be deduced from his hat. Also,

 by the way, that it is extremely improbable that he has gas laid

 on in his house."



 "You are certainly \textcolor{green}{joking,} Holmes."



 "Not in the least. Is it possible that even now, when I give you

 these \textcolor{blue}{results,} you are \textcolor{red}{unable} to see how they are attained?"



 "I have no \textcolor{BurntOrange}{doubt} that I am very \textcolor{red}{stupid,} but I must \textcolor{BurntOrange}{confess} that I

 am \textcolor{red}{unable} to follow you. For example, how did you deduce that

 this man was \textcolor{green}{intellectual?"}



 For answer Holmes clapped the hat upon his head. It came right

 over the forehead and settled upon the bridge of his \textcolor{red}{nose.} "It is

 a \textcolor{green}{question} of cubic capacity," said he; "a man with so large a

 brain must have something in it."



 "The \textcolor{red}{decline} of his \textcolor{BurntOrange}{fortunes,} then?"



 "This hat is three years old. These flat brims \textcolor{green}{curled} at the edge

 came in then. It is a hat of the very best quality. Look at the

 band of ribbed \textcolor{green}{silk} and the \textcolor{green}{excellent} lining. If this man could

 \textcolor{green}{afford} to buy so expensive a hat three years ago, and has had no

 hat since, then he has \textcolor{green}{assuredly} gone down in the world."



 "Well, that is clear enough, certainly. But how about the

 \textcolor{BurntOrange}{foresight} and the \textcolor{BurntOrange}{moral} retrogression?"



 Sherlock Holmes \textcolor{BurntOrange}{laughed.} "Here is the \textcolor{BurntOrange}{foresight,"} said he putting

 his finger upon the little disc and loop of the hat-securer.

 "They are never sold upon hats. If this man ordered one, it is a

 sign of a certain amount of \textcolor{BurntOrange}{foresight,} since he went out of his

 way to take this \textcolor{green}{precaution} against the wind. But since we see

 that he has \textcolor{red}{broken} the elastic and has not troubled to replace

 it, it is \textcolor{green}{obvious} that he has less \textcolor{BurntOrange}{foresight} now than formerly,

 which is a distinct \textcolor{green}{proof} of a weakening nature. On the other

 hand, he has endeavoured to \textcolor{red}{conceal} some of these \textcolor{red}{stains} upon the

 felt by daubing them with ink, which is a sign that he has not

 entirely \textcolor{BurntOrange}{lost} his self-respect."



 "Your \textcolor{green}{reasoning} is certainly plausible."



 "The further points, that he is middle-aged, that his hair is

 grizzled, that it has been recently cut, and that he uses

 lime-cream, are all to be gathered from a close \textcolor{BurntOrange}{examination} of the

 lower part of the lining. The lens discloses a large number of

 hair-ends, \textcolor{green}{clean} cut by the scissors of the barber. They all

 appear to be adhesive, and there is a distinct odour of

 lime-cream. This \textcolor{red}{dust,} you will observe, is not the gritty, grey

 \textcolor{red}{dust} of the street but the fluffy brown \textcolor{red}{dust} of the house,

 \textcolor{green}{showing} that it has been hung up indoors most of the \textcolor{blue}{time,} while

 the marks of moisture upon the inside are \textcolor{green}{proof} positive that the

 wearer perspired very \textcolor{green}{freely,} and could therefore, hardly be in

 the best of training."



 "But his wife--you said that she had ceased to \textcolor{green}{love} him."



 "This hat has not been brushed for weeks. When I see you, my \textcolor{green}{dear}

 Watson, with a week's accumulation of \textcolor{red}{dust} upon your hat, and

 when your wife allows you to go out in such a state, I shall \textcolor{red}{fear}

 that you also have been \textcolor{red}{unfortunate} enough to \textcolor{BurntOrange}{lose} your wife's

 \textcolor{green}{affection."}



 "But he might be a bachelor."



 \textcolor{red}{"Nay,} he was bringing home the goose as a peace-offering to his

 wife. Remember the card upon the bird's leg."



 "You have an answer to everything. But how on earth do you deduce

 that the gas is not laid on in his house?"



 "One tallow \textcolor{red}{stain,} or even two, might come by \textcolor{blue}{chance;} but when I

 see no less than five, I think that there can be little \textcolor{BurntOrange}{doubt}

 that the individual must be brought into frequent \textcolor{green}{contact} with

 burning tallow--walks upstairs at night probably with his hat in

 one hand and a \textcolor{red}{guttering} candle in the other. Anyhow, he never

 got tallow-stains from a gas-jet. Are you \textcolor{green}{satisfied?"}



 "Well, it is very \textcolor{green}{ingenious,"} said I, \textcolor{BurntOrange}{laughing;} "but since, as

 you said just now, there has been no \textcolor{red}{crime} committed, and no \textcolor{red}{harm}

 done \textcolor{green}{save} the \textcolor{red}{loss} of a goose, all this seems to be rather a

 \textcolor{red}{waste} of energy."



 Sherlock Holmes had opened his \textcolor{blue}{mouth} to reply, when the door flew

 open, and Peterson, the commissionaire, rushed into the apartment

 with \textcolor{green}{flushed} cheeks and the face of a man who is dazed with

 \textcolor{BurntOrange}{astonishment.}



 "The goose, Mr. Holmes! The goose, \textcolor{green}{sir!"} he gasped.



 "Eh? What of it, then? Has it returned to life and \textcolor{red}{flapped} off

 through the kitchen window?" Holmes twisted himself round upon

 the sofa to get a fairer view of the man's \textcolor{BurntOrange}{excited} face.



 "See here, \textcolor{green}{sir!} See what my wife \textcolor{green}{found} in its crop!" He held out

 his hand and displayed upon the centre of the palm a brilliantly

 scintillating \textcolor{red}{blue} \textcolor{red}{stone,} rather \textcolor{red}{smaller} than a bean in size, but

 of such \textcolor{BurntOrange}{purity} and \textcolor{BurntOrange}{radiance} that it \textcolor{BurntOrange}{twinkled} like an \textcolor{BurntOrange}{electric}

 point in the \textcolor{red}{dark} \textcolor{red}{hollow} of his hand.



 Sherlock Holmes sat up with a whistle. "By Jove, Peterson!" said

 he, "this is \textcolor{BurntOrange}{treasure} trove indeed. I suppose you know what you

 have got?"



 "A \textcolor{green}{diamond,} \textcolor{green}{sir?} A \textcolor{BurntOrange}{precious} \textcolor{red}{stone.} It cuts into glass as though

 it were putty."



 "It's more than a \textcolor{BurntOrange}{precious} \textcolor{red}{stone.} It is the \textcolor{BurntOrange}{precious} \textcolor{red}{stone."}



 "Not the \textcolor{green}{Countess} of Morcar's \textcolor{red}{blue} carbuncle!" I ejaculated.



 "Precisely so. I ought to know its size and \textcolor{green}{shape,} seeing that I

 have read the advertisement about it in The \textcolor{blue}{Times} every day

 lately. It is absolutely \textcolor{BurntOrange}{unique,} and its value can only be

 \textcolor{blue}{conjectured,} but the \textcolor{BurntOrange}{reward} \textcolor{green}{offered} of 1000 \textcolor{red}{pounds} is certainly

 not within a twentieth part of the market price."



 "A thousand \textcolor{red}{pounds!} Great \textcolor{BurntOrange}{Lord} of \textcolor{green}{mercy!"} The commissionaire

 plumped down into a chair and \textcolor{BurntOrange}{stared} from one to the other of us.



 "That is the \textcolor{BurntOrange}{reward,} and I have \textcolor{green}{reason} to know that there are

 \textcolor{green}{sentimental} considerations in the background which would induce

 the \textcolor{green}{Countess} to part with half her \textcolor{BurntOrange}{fortune} if she could but

 recover the \textcolor{green}{gem."}



 "It was \textcolor{BurntOrange}{lost,} if I remember aright, at the Hotel \textcolor{green}{Cosmopolitan,"} I

 remarked.



 "Precisely so, on December 22nd, just five days ago. \textcolor{red}{John} Horner,

 a plumber, was accused of having abstracted it from the lady's

 jewel-case. The evidence against him was so strong that the \textcolor{red}{case}

 has been referred to the Assizes. I have some \textcolor{green}{account} of the

 matter here, I believe." He rummaged amid his newspapers,

 glancing over the dates, until at last he smoothed one out,

 doubled it over, and read the following paragraph:



 "Hotel \textcolor{green}{Cosmopolitan} Jewel \textcolor{red}{Robbery.} \textcolor{red}{John} Horner, 26, plumber, was

 brought up upon the charge of having upon the 22nd inst.,

 abstracted from the jewel-case of the \textcolor{green}{Countess} of Morcar the

 \textcolor{green}{valuable} \textcolor{green}{gem} known as the \textcolor{red}{blue} carbuncle. James Ryder,

 upper-attendant at the hotel, gave his evidence to the effect

 that he had \textcolor{green}{shown} Horner up to the dressing-room of the \textcolor{green}{Countess}

 of Morcar upon the day of the \textcolor{red}{robbery} in order that he might

 solder the second bar of the \textcolor{red}{grate,} which was loose. He had

 remained with Horner some little \textcolor{blue}{time,} but had \textcolor{BurntOrange}{finally} been

 called away. On returning, he \textcolor{green}{found} that Horner had \textcolor{red}{disappeared,}

 that the bureau had been \textcolor{red}{forced} open, and that the \textcolor{red}{small} morocco

 \textcolor{red}{casket} in which, as it afterwards transpired, the \textcolor{green}{Countess} was

 accustomed to keep her jewel, was \textcolor{red}{lying} empty upon the

 dressing-table. Ryder instantly gave the \textcolor{BurntOrange}{alarm,} and Horner was

 \textcolor{red}{arrested} the same evening; but the \textcolor{red}{stone} could not be \textcolor{green}{found}

 either upon his person or in his rooms. Catherine Cusack, maid to

 the \textcolor{green}{Countess,} deposed to having heard Ryder's \textcolor{red}{cry} of \textcolor{BurntOrange}{dismay} on

 discovering the \textcolor{red}{robbery,} and to having rushed into the room,

 where she \textcolor{green}{found} matters as described by the last \textcolor{green}{witness.}

 \textcolor{green}{Inspector} Bradstreet, B division, gave evidence as to the \textcolor{red}{arrest}

 of Horner, who \textcolor{red}{struggled} frantically, and protested his \textcolor{green}{innocence}

 in the strongest terms. Evidence of a previous \textcolor{red}{conviction} for

 \textcolor{red}{robbery} having been given against the \textcolor{red}{prisoner,} the magistrate

 \textcolor{red}{refused} to \textcolor{BurntOrange}{deal} summarily with the offence, but referred it to

 the Assizes. Horner, who had \textcolor{green}{shown} signs of \textcolor{BurntOrange}{intense} emotion

 during the \textcolor{blue}{proceedings,} fainted away at the conclusion and was

 carried out of \textcolor{BurntOrange}{court."}



 "Hum! So much for the police-court," said Holmes thoughtfully,

 tossing aside the paper. "The \textcolor{green}{question} for us now to solve is the

 sequence of events \textcolor{green}{leading} from a \textcolor{red}{rifled} jewel-case at one end to

 the crop of a goose in Tottenham \textcolor{BurntOrange}{Court} Road at the other. You

 see, Watson, our little deductions have \textcolor{blue}{suddenly} assumed a much

 more \textcolor{green}{important} and less \textcolor{green}{innocent} aspect. Here is the \textcolor{red}{stone;} the

 \textcolor{red}{stone} came from the goose, and the goose came from Mr. Henry

 Baker, the \textcolor{green}{gentleman} with the \textcolor{red}{bad} hat and all the other

 characteristics with which I have \textcolor{red}{bored} you. So now we must set

 ourselves very seriously to finding this \textcolor{green}{gentleman} and

 ascertaining what part he has played in this little \textcolor{blue}{mystery.} To

 do this, we must try the simplest means first, and these \textcolor{red}{lie}

 undoubtedly in an advertisement in all the evening papers. If

 this fail, I shall have recourse to other methods."



 "What will you say?"



 "Give me a pencil and that \textcolor{BurntOrange}{slip} of paper. Now, then: \textcolor{green}{'Found} at

 the corner of Goodge Street, a goose and a \textcolor{red}{black} felt hat. Mr.

 Henry Baker can have the same by applying at 6:30 this evening at

 221B, Baker Street.' That is clear and concise."



 "Very. But will he see it?"



 "Well, he is sure to keep an eye on the papers, since, to a poor

 man, the \textcolor{red}{loss} was a heavy one. He was clearly so \textcolor{red}{scared} by his

 mischance in \textcolor{blue}{breaking} the window and by the approach of Peterson

 that he \textcolor{blue}{thought} of nothing but flight, but since then he must

 have \textcolor{red}{bitterly} \textcolor{red}{regretted} the impulse which caused him to drop his

 bird. Then, again, the introduction of his name will cause him to

 see it, for everyone who knows him will direct his \textcolor{green}{attention} to

 it. Here you are, Peterson, run down to the advertising agency

 and have this put in the evening papers."



 "In which, \textcolor{green}{sir?"}



 "Oh, in the Globe, \textcolor{BurntOrange}{Star,} Pall Mall, St. James's, Evening News,

 Standard, Echo, and any others that occur to you."



 "Very well, \textcolor{green}{sir.} And this \textcolor{red}{stone?"}



 "Ah, yes, I shall keep the \textcolor{red}{stone.} Thank you. And, I say,

 Peterson, just buy a goose on your way back and \textcolor{BurntOrange}{leave} it here

 with me, for we must have one to give to this \textcolor{green}{gentleman} in place

 of the one which your family is now \textcolor{red}{devouring."}



 When the commissionaire had gone, Holmes took up the \textcolor{red}{stone} and

 held it against the light. "It's a bonny thing," said he. "Just

 see how it glints and \textcolor{BurntOrange}{sparkles.} Of course it is a nucleus and

 \textcolor{green}{focus} of \textcolor{red}{crime.} Every \textcolor{BurntOrange}{good} \textcolor{red}{stone} is. They are the \textcolor{BurntOrange}{devil's} \textcolor{red}{pet}

 \textcolor{BurntOrange}{baits.} In the larger and older jewels every facet may stand for a

 \textcolor{red}{bloody} \textcolor{green}{deed.} This \textcolor{red}{stone} is not yet twenty years old. It was \textcolor{green}{found}

 in the \textcolor{green}{banks} of the Amoy River in southern China and is \textcolor{BurntOrange}{remarkable}

 in having every characteristic of the carbuncle, \textcolor{green}{save} that it is

 \textcolor{red}{blue} in shade instead of ruby red. In \textcolor{red}{spite} of its \textcolor{BurntOrange}{youth,} it has

 already a \textcolor{red}{sinister} history. There have been two \textcolor{BurntOrange}{murders,} a

 vitriol-throwing, a \textcolor{red}{suicide,} and several \textcolor{red}{robberies} brought about

 for the sake of this forty-grain \textcolor{BurntOrange}{weight} of crystallised charcoal.

 Who would think that so \textcolor{BurntOrange}{pretty} a toy would be a purveyor to the

 \textcolor{red}{gallows} and the \textcolor{red}{prison?} \textcolor{red}{I'll} lock it up in my strong box now and

 drop a line to the \textcolor{green}{Countess} to say that we have it."



 "Do you think that this man Horner is \textcolor{green}{innocent?"}



 "I cannot tell."



 "Well, then, do you imagine that this other one, Henry Baker, had

 anything to do with the matter?"



 "It is, I think, much more likely that Henry Baker is an

 absolutely \textcolor{green}{innocent} man, who had no idea that the bird which he

 was carrying was of considerably more value than if it were made

 of \textcolor{green}{solid} \textcolor{green}{gold.} That, however, I shall determine by a very simple

 test if we have an answer to our advertisement."



 "And you can do nothing until then?"



 "Nothing."



 "In that \textcolor{red}{case} I shall \textcolor{BurntOrange}{continue} my \textcolor{green}{professional} round. But I shall

 come back in the evening at the hour you have mentioned, for I

 should like to see the \textcolor{green}{solution} of so tangled a business."



 "Very \textcolor{BurntOrange}{glad} to see you. I dine at seven. There is a woodcock, I

 believe. By the way, in view of recent occurrences, perhaps I

 ought to ask Mrs. Hudson to examine its crop."



 I had been \textcolor{red}{delayed} at a \textcolor{red}{case,} and it was a little after half-past

 six when I \textcolor{green}{found} myself in Baker Street once more. As I

 approached the house I saw a tall man in a \textcolor{red}{Scotch} bonnet with a

 coat which was buttoned up to his chin \textcolor{BurntOrange}{waiting} outside in the

 bright semicircle which was thrown from the fanlight. Just as I

 \textcolor{blue}{arrived} the door was opened, and we were \textcolor{green}{shown} up together to

 Holmes' room.



 "Mr. Henry Baker, I believe," said he, rising from his armchair

 and greeting his \textcolor{BurntOrange}{visitor} with the easy air of geniality which he

 could so \textcolor{green}{readily} assume. \textcolor{BurntOrange}{"Pray} take this chair by the \textcolor{red}{fire,} Mr.

 Baker. It is a \textcolor{red}{cold} night, and I observe that your circulation is

 more \textcolor{green}{adapted} for summer than for winter. Ah, Watson, you have

 just come at the right \textcolor{blue}{time.} Is that your hat, Mr. Baker?"



 "Yes, \textcolor{green}{sir,} that is undoubtedly my hat."



 He was a large man with rounded \textcolor{green}{shoulders,} a massive head, and a

 broad, \textcolor{green}{intelligent} face, \textcolor{red}{sloping} down to a pointed beard of

 grizzled brown. A touch of red in \textcolor{red}{nose} and cheeks, with a slight

 \textcolor{BurntOrange}{tremor} of his \textcolor{green}{extended} hand, recalled Holmes' \textcolor{green}{surmise} as to his

 habits. His \textcolor{red}{rusty} \textcolor{red}{black} frock-coat was buttoned right up in

 front, with the collar turned up, and his lank wrists protruded

 from his sleeves without a sign of cuff or shirt. He \textcolor{red}{spoke} in a

 slow \textcolor{green}{staccato} fashion, choosing his \textcolor{green}{words} with care, and gave the

 \textcolor{green}{impression} generally of a man of \textcolor{green}{learning} and \textcolor{blue}{letters} who had had

 ill-usage at the hands of \textcolor{BurntOrange}{fortune.}



 "We have \textcolor{green}{retained} these things for some days," said Holmes,

 "because we \textcolor{BurntOrange}{expected} to see an advertisement from you giving your

 address. I am at a \textcolor{red}{loss} to know now why you did not advertise."



 Our \textcolor{BurntOrange}{visitor} gave a rather shamefaced \textcolor{BurntOrange}{laugh.} "Shillings have not

 been so \textcolor{green}{plentiful} with me as they once were," he remarked. "I had

 no \textcolor{BurntOrange}{doubt} that the \textcolor{red}{gang} of roughs who \textcolor{red}{assaulted} me had carried off

 both my hat and the bird. I did not care to spend more \textcolor{BurntOrange}{money} in a

 \textcolor{red}{hopeless} \textcolor{blue}{attempt} at recovering them."



 "Very naturally. By the way, about the bird, we were compelled to

 \textcolor{green}{eat} it."



 "To \textcolor{green}{eat} it!" Our \textcolor{BurntOrange}{visitor} half rose from his chair in his

 \textcolor{BurntOrange}{excitement.}



 "Yes, it would have been of no use to anyone had we not done so.

 But I presume that this other goose upon the sideboard, which is

 about the same \textcolor{BurntOrange}{weight} and perfectly fresh, will answer your

 purpose \textcolor{green}{equally} well?"



 "Oh, certainly, certainly," answered Mr. Baker with a sigh of

 \textcolor{green}{relief.}



 "Of course, we still have the feathers, legs, crop, and so on of

 your own bird, so if you wish--"



 The man burst into a hearty \textcolor{BurntOrange}{laugh.} "They might be useful to me as

 relics of my \textcolor{BurntOrange}{adventure,"} said he, "but beyond that I can hardly

 see what use the disjecta membra of my \textcolor{red}{late} acquaintance are

 going to be to me. No, \textcolor{green}{sir,} I think that, with your \textcolor{green}{permission,} I

 will \textcolor{red}{confine} my \textcolor{green}{attentions} to the \textcolor{green}{excellent} bird which I \textcolor{green}{perceive}

 upon the sideboard."



 Sherlock Holmes glanced sharply across at me with a slight shrug

 of his \textcolor{green}{shoulders.}



 "There is your hat, then, and there your bird," said he. "By the

 way, would it \textcolor{red}{bore} you to tell me where you got the other one

 from? I am somewhat of a fowl fancier, and I have seldom seen a

 better grown goose."



 "Certainly, \textcolor{green}{sir,"} said Baker, who had risen and tucked his newly

 \textcolor{BurntOrange}{gained} property under his arm. "There are a few of us who

 frequent the Alpha Inn, near the Museum--we are to be \textcolor{green}{found} in

 the Museum itself during the day, you understand. This year our

 \textcolor{BurntOrange}{good} host, Windigate by name, \textcolor{green}{instituted} a goose club, by which,

 on consideration of some few pence every week, we were each to

 receive a bird at Christmas. My pence were duly paid, and the

 \textcolor{green}{rest} is \textcolor{green}{familiar} to you. I am much indebted to you, \textcolor{green}{sir,} for a

 \textcolor{red}{Scotch} bonnet is fitted neither to my years nor my gravity." With

 a comical pomposity of manner he bowed solemnly to both of us and

 strode off upon his way.



 "So much for Mr. Henry Baker," said Holmes when he had closed the

 door behind him. "It is quite certain that he knows nothing

 whatever about the matter. Are you \textcolor{BurntOrange}{hungry,} Watson?"



 "Not particularly."



 "Then I \textcolor{green}{suggest} that we turn our \textcolor{green}{dinner} into a supper and follow

 up this \textcolor{blue}{clue} while it is still \textcolor{red}{hot."}



 "By all means."



 It was a bitter night, so we drew on our ulsters and wrapped

 cravats about our throats. Outside, the \textcolor{BurntOrange}{stars} were shining \textcolor{red}{coldly}

 in a cloudless \textcolor{green}{sky,} and the breath of the passers-by blew out

 into smoke like so many \textcolor{red}{pistol} \textcolor{BurntOrange}{shots.} Our footfalls rang out

 crisply and loudly as we swung through the \textcolor{green}{doctors'} quarter,

 Wimpole Street, Harley Street, and so through Wigmore Street into

 Oxford Street. In a quarter of an hour we were in Bloomsbury at

 the Alpha Inn, which is a \textcolor{red}{small} public-house at the corner of one

 of the streets which runs down into Holborn. Holmes pushed open

 the door of the private bar and ordered two glasses of \textcolor{green}{beer} from

 the ruddy-faced, white-aproned landlord.



 "Your \textcolor{green}{beer} should be \textcolor{green}{excellent} if it is as \textcolor{BurntOrange}{good} as your geese,"

 said he.



 "My geese!" The man seemed \textcolor{blue}{surprised.}



 "Yes. I was speaking only half an hour ago to Mr. Henry Baker,

 who was a member of your goose club."



 "Ah! yes, I see. But you see, \textcolor{green}{sir,} them's not our geese."



 "Indeed! Whose, then?"



 "Well, I got the two dozen from a salesman in Covent \textcolor{green}{Garden."}



 "Indeed? I know some of them. Which was it?"



 "Breckinridge is his name."



 "Ah! I don't know him. Well, here's your \textcolor{BurntOrange}{good} health landlord,

 and \textcolor{green}{prosperity} to your house. Good-night."



 "Now for Mr. Breckinridge," he continued, buttoning up his coat

 as we came out into the frosty air. "Remember, Watson that though

 we have so homely a thing as a goose at one end of this chain, we

 have at the other a man who will certainly get seven years' \textcolor{red}{penal}

 \textcolor{red}{servitude} unless we can \textcolor{green}{establish} his \textcolor{green}{innocence.} It is possible

 that our \textcolor{BurntOrange}{inquiry} may but confirm his \textcolor{red}{guilt;} but, in any \textcolor{red}{case,} we

 have a line of \textcolor{blue}{investigation} which has been missed by the \textcolor{BurntOrange}{police,}

 and which a singular \textcolor{blue}{chance} has placed in our hands. Let us

 follow it out to the bitter end. Faces to the south, then, and

 quick \textcolor{green}{march!"}



 We passed across Holborn, down Endell Street, and so through a

 zigzag of \textcolor{red}{slums} to Covent \textcolor{green}{Garden} Market. One of the largest

 \textcolor{red}{stalls} \textcolor{red}{bore} the name of Breckinridge upon it, and the proprietor

 a horsey-looking man, with a sharp face and trim side-whiskers was

 helping a \textcolor{red}{boy} to put up the shutters.



 "Good-evening. It's a \textcolor{red}{cold} night," said Holmes.



 The salesman nodded and \textcolor{BurntOrange}{shot} a \textcolor{green}{questioning} glance at my

 \textcolor{green}{companion.}



 "Sold out of geese, I see," continued Holmes, pointing at the

 bare slabs of marble.



 "Let you have five hundred \textcolor{blue}{to-morrow} morning."



 "That's no \textcolor{BurntOrange}{good."}



 "Well, there are some on the \textcolor{red}{stall} with the gas-flare."



 "Ah, but I was \textcolor{green}{recommended} to you."



 "Who by?"



 "The landlord of the Alpha."



 "Oh, yes; I sent him a couple of dozen."



 "Fine birds they were, too. Now where did you get them from?"



 To my \textcolor{BurntOrange}{surprise} the \textcolor{green}{question} provoked a burst of \textcolor{red}{anger} from the

 salesman.



 "Now, then, mister," said he, with his head cocked and his arms

 akimbo, "what are you driving at? Let's have it straight, now."



 "It is straight enough. I should like to know who sold you the

 geese which you \textcolor{green}{supplied} to the Alpha."



 "Well then, I shan't tell you. So now!"



 "Oh, it is a matter of no \textcolor{BurntOrange}{importance;} but I don't know why you

 should be so warm over such a \textcolor{red}{trifle."}



 "Warm! You'd be as warm, maybe, if you were as pestered as I am.

 When I \textcolor{BurntOrange}{pay} \textcolor{BurntOrange}{good} \textcolor{BurntOrange}{money} for a \textcolor{BurntOrange}{good} article there should be an end

 of the business; but it's 'Where are the geese?' and 'Who did you

 sell the geese to?' and 'What will you take for the geese?' One

 would think they were the only geese in the world, to hear the

 \textcolor{red}{fuss} that is made over them."



 "Well, I have no connection with any other people who have been

 making \textcolor{BurntOrange}{inquiries,"} said Holmes carelessly. "If you \textcolor{blue}{won't} tell us

 the bet is off, that is all. But I'm always \textcolor{blue}{ready} to back my

 opinion on a matter of fowls, and I have a fiver on it that the

 bird I ate is country bred."



 "Well, then, you've \textcolor{BurntOrange}{lost} your fiver, for it's town bred," snapped

 the salesman.



 "It's nothing of the \textcolor{green}{kind."}



 "I say it is."



 "I don't believe it."



 "D'you think you know more about fowls than I, who have handled

 them ever since I was a nipper? I tell you, all those birds that

 went to the Alpha were town bred."



 "You'll never \textcolor{green}{persuade} me to believe that."



 "Will you bet, then?"



 "It's merely taking your \textcolor{BurntOrange}{money,} for I know that I am right. But

 \textcolor{red}{I'll} have a \textcolor{green}{sovereign} on with you, just to \textcolor{BurntOrange}{teach} you not to be

 \textcolor{red}{obstinate."}



 The salesman \textcolor{BurntOrange}{chuckled} grimly. "Bring me the books, Bill," said

 he.



 The \textcolor{red}{small} \textcolor{red}{boy} brought round a \textcolor{red}{small} thin volume and a great

 greasy-backed one, laying them out together beneath the hanging

 lamp.



 "Now then, Mr. Cocksure," said the salesman, "I \textcolor{blue}{thought} that I

 was out of geese, but before I finish you'll find that there is

 still one left in my shop. You see this little book?"



 "Well?"



 "That's the list of the folk from whom I buy. D'you see? Well,

 then, here on this page are the country folk, and the numbers

 after their names are where their \textcolor{green}{accounts} are in the big ledger.

 Now, then! You see this other page in red ink? Well, that is a

 list of my town suppliers. Now, look at that third name. Just

 read it out to me."



 "Mrs. Oakshott, 117, Brixton Road--249," read Holmes.



 "Quite so. Now turn that up in the ledger."



 Holmes turned to the page indicated. "Here you are, 'Mrs.

 Oakshott, 117, Brixton Road, egg and poultry supplier.'"



 "Now, then, what's the last entry?"



 "'December 22nd. Twenty-four geese at 7s. 6d.'"



 "Quite so. There you are. And underneath?"



 "'Sold to Mr. Windigate of the Alpha, at 12s.'"



 "What have you to say now?"



 Sherlock Holmes looked deeply \textcolor{red}{chagrined.} He drew a \textcolor{green}{sovereign} from

 his pocket and threw it down upon the slab, turning away with the

 air of a man whose \textcolor{red}{disgust} is too deep for \textcolor{green}{words.} A few yards off

 he stopped under a lamp-post and \textcolor{BurntOrange}{laughed} in the hearty, noiseless

 fashion which was peculiar to him.



 "When you see a man with whiskers of that cut and the 'Pink 'un'

 protruding out of his pocket, you can always draw him by a bet,"

 said he. "I daresay that if I had put 100 \textcolor{red}{pounds} down in front of

 him, that man would not have given me such complete \textcolor{green}{information}

 as was drawn from him by the idea that he was doing me on a

 wager. Well, Watson, we are, I \textcolor{BurntOrange}{fancy,} nearing the end of our

 \textcolor{BurntOrange}{quest,} and the only point which \textcolor{BurntOrange}{remains} to be determined is

 whether we should go on to this Mrs. Oakshott to-night, or

 whether we should \textcolor{green}{reserve} it for \textcolor{blue}{to-morrow.} It is clear from what

 that \textcolor{red}{surly} \textcolor{green}{fellow} said that there are others besides ourselves

 who are \textcolor{BurntOrange}{anxious} about the matter, and I should--"



 His remarks were \textcolor{blue}{suddenly} cut short by a loud hubbub which \textcolor{red}{broke}

 out from the \textcolor{red}{stall} which we had just left. Turning round we saw a

 little rat-faced \textcolor{green}{fellow} standing in the centre of the circle of

 yellow light which was thrown by the swinging lamp, while

 Breckinridge, the salesman, framed in the door of his \textcolor{red}{stall,} was

 shaking his fists fiercely at the \textcolor{red}{cringing} figure.



 "I've had enough of you and your geese," he \textcolor{BurntOrange}{shouted.} "I wish you

 were all at the \textcolor{BurntOrange}{devil} together. If you come pestering me any more

 with your \textcolor{BurntOrange}{silly} \textcolor{green}{talk} \textcolor{red}{I'll} set the dog at you. You bring Mrs.

 Oakshott here and \textcolor{red}{I'll} answer her, but what have you to do with

 it? Did I buy the geese off you?"



 "No; but one of them was mine all the same," \textcolor{red}{whined} the little

 man.



 "Well, then, ask Mrs. Oakshott for it."



 "She told me to ask you."



 "Well, you can ask the \textcolor{green}{King} of Proosia, for all I care. I've had

 enough of it. Get out of this!" He rushed fiercely \textcolor{green}{forward,} and

 the \textcolor{green}{inquirer} flitted away into the \textcolor{red}{darkness.}



 "Ha! this may \textcolor{green}{save} us a \textcolor{green}{visit} to Brixton Road," whispered Holmes.

 "Come with me, and we will see what is to be made of this

 \textcolor{green}{fellow."} Striding through the scattered knots of people who

 \textcolor{red}{lounged} round the flaring \textcolor{red}{stalls,} my \textcolor{green}{companion} speedily overtook

 the little man and touched him upon the \textcolor{green}{shoulder.} He sprang

 round, and I could see in the gas-light that every vestige of

 colour had been driven from his face.



 "Who are you, then? What do you want?" he asked in a quavering

 voice.



 "You will \textcolor{red}{excuse} me," said Holmes blandly, "but I could not help

 overhearing the \textcolor{green}{questions} which you put to the salesman just now.

 I think that I could be of \textcolor{green}{assistance} to you."



 "You? Who are you? How could you know anything of the matter?"



 "My name is Sherlock Holmes. It is my business to know what other

 people don't know."



 "But you can know nothing of this?"



 \textcolor{red}{"Excuse} me, I know everything of it. You are endeavouring to

 trace some geese which were sold by Mrs. Oakshott, of Brixton

 Road, to a salesman named Breckinridge, by him in turn to Mr.

 Windigate, of the Alpha, and by him to his club, of which Mr.

 Henry Baker is a member."



 "Oh, \textcolor{green}{sir,} you are the very man whom I have \textcolor{blue}{longed} to meet," \textcolor{red}{cried}

 the little \textcolor{green}{fellow} with outstretched hands and \textcolor{red}{quivering} fingers.

 "I can hardly \textcolor{green}{explain} to you how \textcolor{BurntOrange}{interested} I am in this matter."



 Sherlock Holmes \textcolor{BurntOrange}{hailed} a four-wheeler which was passing. "In that

 \textcolor{red}{case} we had better discuss it in a \textcolor{green}{cosy} room rather than in this

 wind-swept market-place," said he. "But \textcolor{BurntOrange}{pray} tell me, before we

 go farther, who it is that I have the pleasure of \textcolor{green}{assisting."}



 The man hesitated for an instant. "My name is \textcolor{red}{John} Robinson," he

 answered with a sidelong glance.



 "No, no; the \textcolor{green}{real} name," said Holmes sweetly. "It is always

 awkward doing business with an alias."



 A \textcolor{green}{flush} sprang to the \textcolor{BurntOrange}{white} cheeks of the \textcolor{red}{stranger.} "Well then,"

 said he, "my \textcolor{green}{real} name is James Ryder."



 "Precisely so. Head \textcolor{green}{attendant} at the Hotel \textcolor{green}{Cosmopolitan.} \textcolor{BurntOrange}{Pray}

 step into the \textcolor{green}{cab,} and I shall soon be able to tell you

 everything which you would wish to know."



 The little man stood glancing from one to the other of us with

 half-frightened, half-hopeful eyes, as one who is not sure

 whether he is on the \textcolor{BurntOrange}{verge} of a \textcolor{green}{windfall} or of a \textcolor{BurntOrange}{catastrophe.}

 Then he stepped into the \textcolor{green}{cab,} and in half an hour we were back in

 the sitting-room at Baker Street. Nothing had been said during

 our drive, but the high, thin breathing of our new \textcolor{green}{companion,} and

 the claspings and unclaspings of his hands, \textcolor{red}{spoke} of the \textcolor{BurntOrange}{nervous}

 \textcolor{red}{tension} within him.



 "Here we are!" said Holmes cheerily as we filed into the room.

 "The \textcolor{red}{fire} looks very seasonable in this weather. You look \textcolor{red}{cold,}

 Mr. Ryder. \textcolor{BurntOrange}{Pray} take the basket-chair. I will just put on my

 slippers before we settle this little matter of yours. Now, then!

 You want to know what became of those geese?"



 "Yes, \textcolor{green}{sir."}



 "Or rather, I \textcolor{BurntOrange}{fancy,} of that goose. It was one bird, I imagine in

 which you were interested--white, with a \textcolor{red}{black} bar across the

 tail."



 Ryder \textcolor{red}{quivered} with emotion. "Oh, \textcolor{green}{sir,"} he \textcolor{red}{cried,} "can you tell

 me where it went to?"



 "It came here."



 "Here?"



 "Yes, and a most \textcolor{BurntOrange}{remarkable} bird it \textcolor{green}{proved.} I don't wonder that

 you should take an \textcolor{green}{interest} in it. It laid an egg after it was

 dead--the bonniest, brightest little \textcolor{red}{blue} egg that ever was seen.

 I have it here in my museum."



 Our \textcolor{BurntOrange}{visitor} \textcolor{blue}{staggered} to his feet and clutched the mantelpiece

 with his right hand. Holmes unlocked his strong-box and held up

 the \textcolor{red}{blue} carbuncle, which shone out like a \textcolor{BurntOrange}{star,} with a \textcolor{red}{cold,}

 \textcolor{BurntOrange}{brilliant,} many-pointed \textcolor{BurntOrange}{radiance.} Ryder stood \textcolor{red}{glaring} with a

 drawn face, \textcolor{BurntOrange}{uncertain} whether to claim or to disown it.



 "The game's up, Ryder," said Holmes quietly. "Hold up, man, or

 you'll be into the \textcolor{red}{fire!} Give him an arm back into his chair,

 Watson. He's not got blood enough to go in for \textcolor{red}{felony} with

 impunity. Give him a dash of \textcolor{red}{brandy.} So! Now he looks a little

 more human. What a shrimp it is, to be sure!"



 For a moment he had \textcolor{blue}{staggered} and nearly \textcolor{red}{fallen,} but the \textcolor{red}{brandy}

 brought a tinge of colour into his cheeks, and he sat \textcolor{BurntOrange}{staring}

 with \textcolor{BurntOrange}{frightened} eyes at his \textcolor{red}{accuser.}



 "I have almost every link in my hands, and all the \textcolor{green}{proofs} which I

 could possibly need, so there is little which you need tell me.

 Still, that little may as well be cleared up to make the \textcolor{red}{case}

 complete. You had heard, Ryder, of this \textcolor{red}{blue} \textcolor{red}{stone} of the

 \textcolor{green}{Countess} of Morcar's?"



 "It was Catherine Cusack who told me of it," said he in a

 crackling voice.



 "I see--her ladyship's waiting-maid. Well, the \textcolor{red}{temptation} of

 \textcolor{blue}{sudden} \textcolor{green}{wealth} so easily \textcolor{green}{acquired} was too much for you, as it has

 been for better men before you; but you were not very scrupulous

 in the means you used. It seems to me, Ryder, that there is the

 making of a very \textcolor{BurntOrange}{pretty} \textcolor{red}{villain} in you. You knew that this man

 Horner, the plumber, had been \textcolor{red}{concerned} in some such matter

 before, and that \textcolor{red}{suspicion} would \textcolor{green}{rest} the more \textcolor{green}{readily} upon him.

 What did you do, then? You made some \textcolor{red}{small} \textcolor{green}{job} in my lady's

 room--you and your \textcolor{green}{confederate} Cusack--and you \textcolor{green}{managed} that he

 should be the man sent for. Then, when he had left, you \textcolor{red}{rifled}

 the jewel-case, raised the \textcolor{BurntOrange}{alarm,} and had this \textcolor{red}{unfortunate} man

 \textcolor{red}{arrested.} You then--"



 Ryder threw himself down \textcolor{blue}{suddenly} upon the rug and clutched at my

 \textcolor{green}{companion's} knees. "For \textcolor{BurntOrange}{God's} sake, have \textcolor{green}{mercy!"} he \textcolor{BurntOrange}{shrieked.}

 "Think of my \textcolor{green}{father!} Of my \textcolor{BurntOrange}{mother!} It would \textcolor{blue}{break} their hearts. I

 never went \textcolor{red}{wrong} before! I never will again. I \textcolor{green}{swear} it. \textcolor{red}{I'll}

 \textcolor{green}{swear} it on a Bible. Oh, don't bring it into \textcolor{BurntOrange}{court!} For Christ's

 sake, don't!"



 "Get back into your chair!" said Holmes sternly. "It is very well

 to \textcolor{red}{cringe} and \textcolor{red}{crawl} now, but you \textcolor{blue}{thought} little enough of this

 poor Horner in the dock for a \textcolor{red}{crime} of which he knew nothing."



 "I will fly, Mr. Holmes. I will \textcolor{BurntOrange}{leave} the country, \textcolor{green}{sir.} Then the

 charge against him will \textcolor{blue}{break} down."



 "Hum! We will \textcolor{green}{talk} about that. And now let us hear a \textcolor{green}{true} \textcolor{green}{account}

 of the next act. How came the \textcolor{red}{stone} into the goose, and how came

 the goose into the open market? Tell us the \textcolor{green}{truth,} for there \textcolor{red}{lies}

 your only \textcolor{BurntOrange}{hope} of safety."



 Ryder passed his tongue over his parched lips. "I will tell you

 it just as it \textcolor{blue}{happened,} \textcolor{green}{sir,"} said he. "When Horner had been

 \textcolor{red}{arrested,} it seemed to me that it would be best for me to get

 away with the \textcolor{red}{stone} at once, for I did not know at what moment

 the \textcolor{BurntOrange}{police} might not take it into their heads to search me and my

 room. There was no place about the hotel where it would be \textcolor{green}{safe.}

 I went out, as if on some \textcolor{green}{commission,} and I made for my sister's

 house. She had married a man named Oakshott, and lived in Brixton

 Road, where she fattened fowls for the market. All the way there

 every man I met seemed to me to be a \textcolor{BurntOrange}{policeman} or a detective;

 and, for all that it was a \textcolor{red}{cold} night, the \textcolor{red}{sweat} was pouring down

 my face before I came to the Brixton Road. My sister asked me

 what was the matter, and why I was so pale; but I told her that I

 had been \textcolor{red}{upset} by the jewel \textcolor{red}{robbery} at the hotel. Then I went

 into the back yard and smoked a pipe and wondered what it would

 be best to do.



 "I had a \textcolor{green}{friend} once called Maudsley, who went to the \textcolor{red}{bad,} and

 has just been \textcolor{BurntOrange}{serving} his \textcolor{blue}{time} in Pentonville. One day he had met

 me, and \textcolor{red}{fell} into \textcolor{green}{talk} about the ways of \textcolor{BurntOrange}{thieves,} and how they

 could get rid of what they stole. I knew that he would be \textcolor{green}{true} to

 me, for I knew one or two things about him; so I made up my mind

 to go right on to Kilburn, where he lived, and take him into my

 \textcolor{BurntOrange}{confidence.} He would \textcolor{green}{show} me how to turn the \textcolor{red}{stone} into \textcolor{BurntOrange}{money.}

 But how to get to him in safety? I \textcolor{blue}{thought} of the \textcolor{red}{agonies} I had

 gone through in coming from the hotel. I might at any moment be

 \textcolor{red}{seized} and searched, and there would be the \textcolor{red}{stone} in my waistcoat

 pocket. I was leaning against the wall at the \textcolor{blue}{time} and looking at

 the geese which were waddling about round my feet, and \textcolor{blue}{suddenly}

 an idea came into my head which \textcolor{green}{showed} me how I could beat the

 best detective that ever lived.



 "My sister had told me some weeks before that I might have the

 \textcolor{green}{pick} of her geese for a Christmas \textcolor{BurntOrange}{present,} and I knew that she

 was always as \textcolor{BurntOrange}{good} as her \textcolor{green}{word.} I would take my goose now, and in

 it I would carry my \textcolor{red}{stone} to Kilburn. There was a little \textcolor{red}{shed} in

 the yard, and behind this I drove one of the birds--a fine big

 one, \textcolor{BurntOrange}{white,} with a barred tail. I caught it, and \textcolor{BurntOrange}{prying} its bill

 open, I thrust the \textcolor{red}{stone} down its throat as far as my finger

 could reach. The bird gave a \textcolor{BurntOrange}{gulp,} and I felt the \textcolor{red}{stone} pass

 along its gullet and down into its crop. But the \textcolor{red}{creature} \textcolor{red}{flapped}

 and \textcolor{red}{struggled,} and out came my sister to know what was the

 matter. As I turned to speak to her the \textcolor{red}{brute} \textcolor{red}{broke} loose and

 fluttered off among the others.



 "'Whatever were you doing with that bird, Jem?' says she.



 "'Well,' said I, 'you said you'd give me one for Christmas, and I

 was feeling which was the fattest.'



 "'Oh,' says she, 'we've set yours aside for you--Jem's bird, we

 call it. It's the big \textcolor{BurntOrange}{white} one over yonder. There's twenty-six

 of them, which makes one for you, and one for us, and two dozen

 for the market.'



 "'Thank you, Maggie,' says I; 'but if it is all the same to you,

 I'd rather have that one I was handling just now.'



 "'The other is a \textcolor{BurntOrange}{good} three \textcolor{red}{pound} heavier,' said she, 'and we

 fattened it expressly for you.'



 "'Never mind. \textcolor{red}{I'll} have the other, and \textcolor{red}{I'll} take it now,' said I.



 "'Oh, just as you like,' said she, a little huffed. 'Which is it

 you want, then?'



 "'That \textcolor{BurntOrange}{white} one with the barred tail, right in the middle of the

 flock.'



 "'Oh, very well. \textcolor{red}{Kill} it and take it with you.'



 "Well, I did what she said, Mr. Holmes, and I carried the bird

 all the way to Kilburn. I told my pal what I had done, for he was

 a man that it was easy to tell a thing like that to. He \textcolor{BurntOrange}{laughed}

 until he choked, and we got a knife and opened the goose. My

 heart turned to water, for there was no sign of the \textcolor{red}{stone,} and I

 knew that some \textcolor{red}{terrible} \textcolor{red}{mistake} had occurred. I left the bird,

 rushed back to my sister's, and \textcolor{blue}{hurried} into the back yard. There

 was not a bird to be seen there.



 "'Where are they all, Maggie?' I \textcolor{red}{cried.}



 "'Gone to the dealer's, Jem.'



 "'Which dealer's?'



 "'Breckinridge, of Covent \textcolor{green}{Garden.'}



 "'But was there another with a barred tail?' I asked, 'the same

 as the one I chose?'



 "'Yes, Jem; there were two barred-tailed ones, and I could never

 tell them apart.'



 "Well, then, of course I saw it all, and I ran off as hard as my

 feet would carry me to this man Breckinridge; but he had sold the

 lot at once, and not one \textcolor{green}{word} would he tell me as to where they

 had gone. You heard him yourselves to-night. Well, he has always

 answered me like that. My sister thinks that I am going \textcolor{red}{mad.}

 Sometimes I think that I am myself. And now--and now I am myself

 a branded \textcolor{BurntOrange}{thief,} without ever having touched the \textcolor{green}{wealth} for which

 I sold my character. \textcolor{BurntOrange}{God} help me! \textcolor{BurntOrange}{God} help me!" He burst into

 convulsive \textcolor{red}{sobbing,} with his face \textcolor{red}{buried} in his hands.



 There was a \textcolor{blue}{long} silence, \textcolor{red}{broken} only by his heavy breathing and

 by the \textcolor{green}{measured} tapping of Sherlock Holmes' finger-tips upon the

 edge of the table. Then my \textcolor{green}{friend} rose and threw open the door.



 "Get out!" said he.



 "What, \textcolor{green}{sir!} Oh, Heaven \textcolor{BurntOrange}{bless} you!"



 "No more \textcolor{green}{words.} Get out!"



 And no more \textcolor{green}{words} were needed. There was a rush, a clatter upon

 the stairs, the \textcolor{BurntOrange}{bang} of a door, and the \textcolor{BurntOrange}{crisp} rattle of running

 footfalls from the street.



 "After all, Watson," said Holmes, reaching up his hand for his

 clay pipe, "I am not \textcolor{green}{retained} by the \textcolor{BurntOrange}{police} to \textcolor{green}{supply} their

 \textcolor{red}{deficiencies.} If Horner were in \textcolor{red}{danger} it would be another thing;

 but this \textcolor{green}{fellow} will not appear against him, and the \textcolor{red}{case} must

 \textcolor{red}{collapse.} I suppose that I am \textcolor{green}{commuting} a \textcolor{red}{felony,} but it is just

 possible that I am \textcolor{green}{saving} a soul. This \textcolor{green}{fellow} will not go \textcolor{red}{wrong}

 again; he is too \textcolor{red}{terribly} \textcolor{BurntOrange}{frightened.} Send him to \textcolor{red}{gaol} now, and

 you make him a gaol-bird for life. Besides, it is the season of

 forgiveness. \textcolor{blue}{Chance} has put in our way a most singular and

 \textcolor{green}{whimsical} \textcolor{red}{problem,} and its \textcolor{green}{solution} is its own \textcolor{BurntOrange}{reward.} If you

 will have the \textcolor{BurntOrange}{goodness} to touch the bell, \textcolor{green}{Doctor,} we will begin

 another \textcolor{blue}{investigation,} in which, also a bird will be the chief

 \textcolor{green}{feature."}







 VIII. THE \textcolor{BurntOrange}{ADVENTURE} OF THE SPECKLED BAND



 On glancing over my notes of the seventy odd \textcolor{red}{cases} in which I

 have during the last eight years \textcolor{green}{studied} the methods of my \textcolor{green}{friend}

 Sherlock Holmes, I find many \textcolor{red}{tragic,} some comic, a large number

 merely strange, but none \textcolor{BurntOrange}{commonplace;} for, working as he did

 rather for the \textcolor{green}{love} of his \textcolor{BurntOrange}{art} than for the acquirement of

 \textcolor{green}{wealth,} he \textcolor{red}{refused} to \textcolor{green}{associate} himself with any \textcolor{blue}{investigation}

 which did not tend towards the unusual, and even the fantastic.

 Of all these varied \textcolor{red}{cases,} however, I cannot recall any which

 \textcolor{BurntOrange}{presented} more singular \textcolor{green}{features} than that which was \textcolor{green}{associated}

 with the well-known Surrey family of the Roylotts of Stoke Moran.

 The events in \textcolor{green}{question} occurred in the early days of my

 \textcolor{green}{association} with Holmes, when we were \textcolor{BurntOrange}{sharing} rooms as bachelors

 in Baker Street. It is possible that I might have placed them

 upon record before, but a \textcolor{green}{promise} of \textcolor{BurntOrange}{secrecy} was made at the

 \textcolor{blue}{time,} from which I have only been freed during the last month by

 the \textcolor{red}{untimely} \textcolor{BurntOrange}{death} of the lady to whom the \textcolor{green}{pledge} was given. It

 is perhaps as well that the \textcolor{green}{facts} should now come to light, for I

 have \textcolor{green}{reasons} to know that there are \textcolor{green}{widespread} rumours as to the

 \textcolor{BurntOrange}{death} of Dr. Grimesby Roylott which tend to make the matter even

 more \textcolor{red}{terrible} than the \textcolor{green}{truth.}



 It was early in April in the year '83 that I woke one morning to

 find Sherlock Holmes standing, \textcolor{green}{fully} dressed, by the side of my

 bed. He was a \textcolor{red}{late} riser, as a \textcolor{BurntOrange}{rule,} and as the \textcolor{blue}{clock} on the

 mantelpiece \textcolor{green}{showed} me that it was only a quarter-past seven, I

 blinked up at him in some \textcolor{BurntOrange}{surprise,} and perhaps just a little

 \textcolor{red}{resentment,} for I was myself regular in my habits.



 "Very sorry to knock you up, Watson," said he, "but it's the

 common lot this morning. Mrs. Hudson has been knocked up, she

 \textcolor{red}{retorted} upon me, and I on you."



 "What is it, then--a \textcolor{red}{fire?"}



 "No; a client. It seems that a \textcolor{BurntOrange}{young} lady has \textcolor{blue}{arrived} in a

 \textcolor{green}{considerable} state of \textcolor{BurntOrange}{excitement,} who insists upon seeing me. She

 is \textcolor{BurntOrange}{waiting} now in the sitting-room. Now, when \textcolor{BurntOrange}{young} ladies wander

 about the metropolis at this hour of the morning, and knock

 sleepy people up out of their beds, I presume that it is

 something very pressing which they have to \textcolor{green}{communicate.} Should it

 \textcolor{green}{prove} to be an \textcolor{green}{interesting} \textcolor{red}{case,} you would, I am sure, wish to

 follow it from the outset. I \textcolor{blue}{thought,} at any rate, that I should

 call you and give you the \textcolor{blue}{chance."}



 "My \textcolor{green}{dear} \textcolor{green}{fellow,} I would not miss it for anything."



 I had no keener pleasure than in following Holmes in his

 \textcolor{green}{professional} \textcolor{blue}{investigations,} and in \textcolor{green}{admiring} the \textcolor{blue}{rapid}

 deductions, as \textcolor{green}{swift} as \textcolor{green}{intuitions,} and yet always \textcolor{green}{founded} on a

 \textcolor{green}{logical} basis with which he unravelled the \textcolor{red}{problems} which were

 \textcolor{blue}{submitted} to him. I rapidly threw on my clothes and was \textcolor{blue}{ready} in

 a few minutes to accompany my \textcolor{green}{friend} down to the sitting-room. A

 lady dressed in \textcolor{red}{black} and \textcolor{red}{heavily} veiled, who had been sitting in

 the window, rose as we entered.



 "Good-morning, madam," said Holmes cheerily. "My name is Sherlock

 Holmes. This is my \textcolor{BurntOrange}{intimate} \textcolor{green}{friend} and \textcolor{green}{associate,} Dr. Watson,

 before whom you can speak as \textcolor{green}{freely} as before myself. Ha! I am

 \textcolor{BurntOrange}{glad} to see that Mrs. Hudson has had the \textcolor{BurntOrange}{good} \textcolor{green}{sense} to light the

 \textcolor{red}{fire.} \textcolor{BurntOrange}{Pray} draw up to it, and I shall order you a cup of \textcolor{red}{hot}

 coffee, for I observe that you are \textcolor{BurntOrange}{shivering."}



 "It is not \textcolor{red}{cold} which makes me \textcolor{BurntOrange}{shiver,"} said the woman in a low

 voice, \textcolor{red}{changing} her seat as requested.



 "What, then?"



 "It is \textcolor{red}{fear,} Mr. Holmes. It is \textcolor{red}{terror."} She raised her veil as

 she \textcolor{red}{spoke,} and we could see that she was indeed in a pitiable

 state of \textcolor{red}{agitation,} her face all drawn and grey, with restless

 \textcolor{BurntOrange}{frightened} eyes, like those of some hunted animal. Her \textcolor{green}{features}

 and figure were those of a woman of thirty, but her hair was \textcolor{BurntOrange}{shot}

 with \textcolor{blue}{premature} grey, and her expression was \textcolor{red}{weary} and \textcolor{red}{haggard.}

 Sherlock Holmes ran her over with one of his quick,

 all-comprehensive glances.



 "You must not \textcolor{red}{fear,"} said he soothingly, bending \textcolor{green}{forward} and

 patting her \textcolor{BurntOrange}{forearm.} "We shall soon set matters right, I have no

 \textcolor{BurntOrange}{doubt.} You have come in by train this morning, I see."



 "You know me, then?"



 "No, but I observe the second half of a return ticket in the palm

 of your left glove. You must have \textcolor{blue}{started} early, and yet you had

 a \textcolor{BurntOrange}{good} drive in a dog-cart, along heavy roads, before you reached

 the station."



 The lady gave a \textcolor{BurntOrange}{violent} \textcolor{blue}{start} and \textcolor{BurntOrange}{stared} in \textcolor{BurntOrange}{bewilderment} at my

 \textcolor{green}{companion.}



 "There is no \textcolor{blue}{mystery,} my \textcolor{green}{dear} madam," said he, \textcolor{BurntOrange}{smiling.} "The left

 arm of your jacket is spattered with \textcolor{red}{mud} in no less than seven

 places. The marks are perfectly fresh. There is no vehicle \textcolor{green}{save} a

 dog-cart which throws up \textcolor{red}{mud} in that way, and then only when you

 sit on the left-hand side of the driver."



 "Whatever your \textcolor{green}{reasons} may be, you are perfectly correct," said

 she. "I \textcolor{blue}{started} from home before six, reached Leatherhead at

 twenty past, and came in by the first train to Waterloo. \textcolor{green}{Sir,} I

 can stand this strain no longer; I shall go \textcolor{red}{mad} if it \textcolor{BurntOrange}{continues.}

 I have no one to turn to--none, \textcolor{green}{save} only one, who cares for me,

 and he, poor \textcolor{green}{fellow,} can be of little \textcolor{green}{aid.} I have heard of you,

 Mr. Holmes; I have heard of you from Mrs. Farintosh, whom you

 helped in the hour of her \textcolor{red}{sore} need. It was from her that I had

 your address. Oh, \textcolor{green}{sir,} do you not think that you could help me,

 too, and at least throw a little light through the dense \textcolor{red}{darkness}

 which \textcolor{BurntOrange}{surrounds} me? At \textcolor{BurntOrange}{present} it is out of my power to \textcolor{BurntOrange}{reward}

 you for your services, but in a month or six weeks I shall be

 married, with the control of my own \textcolor{BurntOrange}{income,} and then at least you

 shall not find me \textcolor{red}{ungrateful."}



 Holmes turned to his desk and, unlocking it, drew out a \textcolor{red}{small}

 case-book, which he \textcolor{green}{consulted.}



 "Farintosh," said he. "Ah yes, I recall the \textcolor{red}{case;} it was

 \textcolor{red}{concerned} with an opal tiara. I think it was before your \textcolor{blue}{time,}

 Watson. I can only say, madam, that I shall be \textcolor{BurntOrange}{happy} to devote

 the same care to your \textcolor{red}{case} as I did to that of your \textcolor{green}{friend.} As to

 \textcolor{BurntOrange}{reward,} my \textcolor{green}{profession} is its own \textcolor{BurntOrange}{reward;} but you are at \textcolor{BurntOrange}{liberty}

 to defray whatever expenses I may be put to, at the \textcolor{blue}{time} which

 suits you best. And now I \textcolor{red}{beg} that you will lay before us

 everything that may help us in forming an opinion upon the

 matter."



 "Alas!" replied our \textcolor{BurntOrange}{visitor,} "the very \textcolor{BurntOrange}{horror} of my situation

 \textcolor{red}{lies} in the \textcolor{green}{fact} that my \textcolor{red}{fears} are so \textcolor{red}{vague,} and my \textcolor{red}{suspicions}

 \textcolor{BurntOrange}{depend} so entirely upon \textcolor{red}{small} points, which might seem trivial to

 another, that even he to whom of all others I have a right to

 look for help and \textcolor{green}{advice} looks upon all that I tell him about it

 as the \textcolor{BurntOrange}{fancies} of a \textcolor{BurntOrange}{nervous} woman. He does not say so, but I can

 read it from his \textcolor{green}{soothing} answers and averted eyes. But I have

 heard, Mr. Holmes, that you can see deeply into the manifold

 \textcolor{red}{wickedness} of the human heart. You may \textcolor{green}{advise} me how to walk amid

 the \textcolor{red}{dangers} which encompass me."



 "I am all \textcolor{green}{attention,} madam."



 "My name is Helen Stoner, and I am living with my stepfather, who

 is the last survivor of one of the oldest Saxon families in

 England, the Roylotts of Stoke Moran, on the western border of

 Surrey."



 Holmes nodded his head. "The name is \textcolor{green}{familiar} to me," said he.



 "The family was at one \textcolor{blue}{time} among the richest in England, and the

 estates \textcolor{green}{extended} over the borders into Berkshire in the north,

 and Hampshire in the west. In the last century, however, four

 successive heirs were of a dissolute and \textcolor{red}{wasteful} disposition,

 and the family \textcolor{red}{ruin} was eventually completed by a \textcolor{BurntOrange}{gambler} in the

 days of the Regency. Nothing was left \textcolor{green}{save} a few acres of \textcolor{green}{ground,}

 and the two-hundred-year-old house, which is itself crushed under

 a heavy \textcolor{red}{mortgage.} The last squire dragged out his \textcolor{green}{existence}

 there, living the \textcolor{red}{horrible} life of an \textcolor{green}{aristocratic} \textcolor{red}{pauper;} but

 his only son, my stepfather, seeing that he must \textcolor{green}{adapt} himself to

 the new conditions, obtained an \textcolor{BurntOrange}{advance} from a \textcolor{green}{relative,} which

 \textcolor{green}{enabled} him to take a \textcolor{BurntOrange}{medical} \textcolor{green}{degree} and went out to Calcutta,

 where, by his \textcolor{green}{professional} skill and his \textcolor{red}{force} of character, he

 \textcolor{green}{established} a large \textcolor{green}{practice.} In a fit of \textcolor{red}{anger,} however, caused

 by some \textcolor{red}{robberies} which had been perpetrated in the house, he

 beat his native \textcolor{green}{butler} to \textcolor{BurntOrange}{death} and narrowly \textcolor{BurntOrange}{escaped} a capital

 \textcolor{BurntOrange}{sentence.} As it was, he \textcolor{red}{suffered} a \textcolor{blue}{long} term of \textcolor{red}{imprisonment} and

 afterwards returned to England a morose and \textcolor{red}{disappointed} man.



 "When Dr. Roylott was in India he married my \textcolor{BurntOrange}{mother,} Mrs. Stoner,

 the \textcolor{BurntOrange}{young} \textcolor{red}{widow} of Major-General Stoner, of the Bengal \textcolor{red}{Artillery.}

 My sister Julia and I were \textcolor{green}{twins,} and we were only two years old

 at the \textcolor{blue}{time} of my \textcolor{BurntOrange}{mother's} re-marriage. She had a \textcolor{green}{considerable}

 sum of money--not less than 1000 \textcolor{red}{pounds} a year--and this she

 bequeathed to Dr. Roylott entirely while we resided with him,

 with a provision that a certain annual sum should be allowed to

 each of us in the event of our \textcolor{BurntOrange}{marriage.} \textcolor{blue}{Shortly} after our return

 to England my \textcolor{BurntOrange}{mother} died--she was \textcolor{red}{killed} eight years ago in a

 railway \textcolor{BurntOrange}{accident} near Crewe. Dr. Roylott then \textcolor{red}{abandoned} his

 \textcolor{blue}{attempts} to \textcolor{green}{establish} himself in \textcolor{green}{practice} in London and took us

 to live with him in the old \textcolor{green}{ancestral} house at Stoke Moran. The

 \textcolor{BurntOrange}{money} which my \textcolor{BurntOrange}{mother} had left was enough for all our wants, and

 there seemed to be no \textcolor{red}{obstacle} to our \textcolor{BurntOrange}{happiness.}



 "But a \textcolor{red}{terrible} \textcolor{red}{change} came over our stepfather about this \textcolor{blue}{time.}

 Instead of making \textcolor{green}{friends} and \textcolor{green}{exchanging} \textcolor{green}{visits} with our

 neighbours, who had at first been \textcolor{green}{overjoyed} to see a Roylott of

 Stoke Moran back in the old family seat, he shut himself up in

 his house and seldom came out \textcolor{green}{save} to indulge in \textcolor{red}{ferocious}

 \textcolor{red}{quarrels} with whoever might \textcolor{red}{cross} his path. \textcolor{red}{Violence} of temper

 approaching to \textcolor{red}{mania} has been hereditary in the men of the

 family, and in my stepfather's \textcolor{red}{case} it had, I believe, been

 intensified by his \textcolor{blue}{long} residence in the tropics. A \textcolor{green}{series} of

 \textcolor{red}{disgraceful} \textcolor{red}{brawls} took place, two of which ended in the

 police-court, until at last he became the \textcolor{red}{terror} of the village,

 and the folks would fly at his approach, for he is a man of

 \textcolor{green}{immense} \textcolor{green}{strength,} and absolutely \textcolor{BurntOrange}{uncontrollable} in his \textcolor{red}{anger.}



 "Last week he hurled the local blacksmith over a parapet into a

 stream, and it was only by \textcolor{BurntOrange}{paying} over all the \textcolor{BurntOrange}{money} which I

 could gather together that I was able to avert another \textcolor{BurntOrange}{public}

 exposure. He had no \textcolor{green}{friends} at all \textcolor{green}{save} the wandering gipsies,

 and he would give these vagabonds \textcolor{BurntOrange}{leave} to encamp upon the few

 acres of bramble-covered \textcolor{green}{land} which represent the family estate,

 and would accept in return the \textcolor{green}{hospitality} of their tents,

 wandering away with them sometimes for weeks on end. He has a

 \textcolor{BurntOrange}{passion} also for Indian animals, which are sent over to him by a

 correspondent, and he has at this moment a cheetah and a \textcolor{red}{baboon,}

 which wander \textcolor{green}{freely} over his \textcolor{green}{grounds} and are \textcolor{red}{feared} by the

 \textcolor{green}{villagers} almost as much as their \textcolor{green}{master.}



 "You can imagine from what I say that my poor sister Julia and I

 had no great pleasure in our lives. No \textcolor{BurntOrange}{servant} would stay with

 us, and for a \textcolor{blue}{long} \textcolor{blue}{time} we did all the work of the house. She was

 but thirty at the \textcolor{blue}{time} of her \textcolor{BurntOrange}{death,} and yet her hair had already

 begun to whiten, even as mine has."



 "Your sister is dead, then?"



 "She \textcolor{red}{died} just two years ago, and it is of her \textcolor{BurntOrange}{death} that I wish

 to speak to you. You can understand that, living the life which I

 have described, we were little likely to see anyone of our own

 age and position. We had, however, an \textcolor{green}{aunt,} my \textcolor{BurntOrange}{mother's} \textcolor{green}{maiden}

 sister, Miss Honoria Westphail, who lives near Harrow, and we

 were occasionally allowed to \textcolor{BurntOrange}{pay} short \textcolor{green}{visits} at this lady's

 house. Julia went there at Christmas two years ago, and met there

 a half-pay \textcolor{green}{major} of \textcolor{green}{marines,} to whom she became engaged. My

 stepfather \textcolor{green}{learned} of the engagement when my sister returned and

 \textcolor{green}{offered} no \textcolor{red}{objection} to the \textcolor{BurntOrange}{marriage;} but within a fortnight of

 the day which had been fixed for the wedding, the \textcolor{red}{terrible} event

 occurred which has deprived me of my only \textcolor{green}{companion."}



 Sherlock Holmes had been leaning back in his chair with his eyes

 closed and his head \textcolor{red}{sunk} in a \textcolor{green}{cushion,} but he half opened his

 lids now and glanced across at his \textcolor{BurntOrange}{visitor.}



 \textcolor{BurntOrange}{"Pray} be \textcolor{green}{precise} as to details," said he.



 "It is easy for me to be so, for every event of that \textcolor{BurntOrange}{dreadful}

 \textcolor{blue}{time} is \textcolor{red}{seared} into my memory. The manor-house is, as I have

 already said, very old, and only one wing is now inhabited. The

 bedrooms in this wing are on the \textcolor{green}{ground} floor, the sitting-rooms

 being in the central block of the \textcolor{green}{buildings.} Of these bedrooms

 the first is Dr. Roylott's, the second my sister's, and the third

 my own. There is no \textcolor{green}{communication} between them, but they all open

 out into the same corridor. Do I make myself plain?"



 "Perfectly so."



 "The windows of the three rooms open out upon the lawn. That

 \textcolor{red}{fatal} night Dr. Roylott had gone to his room early, though we

 knew that he had not retired to \textcolor{green}{rest,} for my sister was troubled

 by the \textcolor{red}{smell} of the strong Indian cigars which it was his custom

 to smoke. She left her room, therefore, and came into mine, where

 she sat for some \textcolor{blue}{time,} chatting about her approaching wedding. At

 eleven o'clock she rose to \textcolor{BurntOrange}{leave} me, but she paused at the door

 and looked back.



 "'Tell me, Helen,' said she, 'have you ever heard anyone whistle

 in the dead of the night?'



 "'Never,' said I.



 "'I suppose that you could not possibly whistle, yourself, in

 your sleep?'



 "'Certainly not. But why?'



 "'Because during the last few nights I have always, about three

 in the morning, heard a low, clear whistle. I am a light sleeper,

 and it has awakened me. I cannot tell where it came from--perhaps

 from the next room, perhaps from the lawn. I \textcolor{blue}{thought} that I would

 just ask you whether you had heard it.'



 "'No, I have not. It must be those \textcolor{red}{wretched} gipsies in the

 plantation.'



 "'Very likely. And yet if it were on the lawn, I wonder that you

 did not hear it also.'



 "'Ah, but I sleep more \textcolor{red}{heavily} than you.'



 "'Well, it is of no great consequence, at any rate.' She \textcolor{BurntOrange}{smiled}

 back at me, closed my door, and a few moments later I heard her

 key turn in the lock."



 "Indeed," said Holmes. "Was it your custom always to lock

 yourselves in at night?"



 "Always."



 "And why?"



 "I think that I mentioned to you that the \textcolor{green}{doctor} kept a cheetah

 and a \textcolor{red}{baboon.} We had no feeling of security unless our doors were

 locked."



 "Quite so. \textcolor{BurntOrange}{Pray} proceed with your \textcolor{green}{statement."}



 "I could not sleep that night. A \textcolor{red}{vague} feeling of impending

 \textcolor{red}{misfortune} impressed me. My sister and I, you will recollect,

 were \textcolor{green}{twins,} and you know how subtle are the links which bind two

 souls which are so closely \textcolor{green}{allied.} It was a \textcolor{BurntOrange}{wild} night. The wind

 was \textcolor{BurntOrange}{howling} outside, and the rain was \textcolor{red}{beating} and \textcolor{blue}{splashing}

 against the windows. \textcolor{blue}{Suddenly,} amid all the hubbub of the gale,

 there burst forth the \textcolor{BurntOrange}{wild} \textcolor{BurntOrange}{scream} of a terrified woman. I knew

 that it was my sister's voice. I sprang from my bed, wrapped a

 shawl round me, and rushed into the corridor. As I opened my door

 I seemed to hear a low whistle, such as my sister described, and

 a few moments later a clanging sound, as if a mass of metal had

 \textcolor{red}{fallen.} As I ran down the passage, my sister's door was unlocked,

 and revolved slowly upon its hinges. I \textcolor{BurntOrange}{stared} at it

 horror-stricken, not knowing what was about to issue from it. By

 the light of the corridor-lamp I saw my sister appear at the

 opening, her face blanched with \textcolor{red}{terror,} her hands \textcolor{red}{groping} for

 help, her whole figure swaying to and fro like that of a

 drunkard. I ran to her and threw my arms round her, but at that

 moment her knees seemed to give way and she \textcolor{red}{fell} to the \textcolor{green}{ground.}

 She writhed as one who is in \textcolor{red}{terrible} \textcolor{red}{pain,} and her limbs were

 \textcolor{BurntOrange}{dreadfully} convulsed. At first I \textcolor{blue}{thought} that she had not

 recognised me, but as I bent over her she \textcolor{blue}{suddenly} \textcolor{BurntOrange}{shrieked} out

 in a voice which I shall never \textcolor{red}{forget,} 'Oh, my \textcolor{BurntOrange}{God!} Helen! It was

 the band! The speckled band!' There was something else which she

 would \textcolor{BurntOrange}{fain} have said, and she stabbed with her finger into the

 air in the direction of the \textcolor{green}{doctor's} room, but a fresh convulsion

 \textcolor{red}{seized} her and choked her \textcolor{green}{words.} I rushed out, calling loudly for

 my stepfather, and I met him hastening from his room in his

 dressing-gown. When he reached my sister's side she was

 \textcolor{red}{unconscious,} and though he poured \textcolor{red}{brandy} down her throat and sent

 for \textcolor{BurntOrange}{medical} \textcolor{green}{aid} from the village, all \textcolor{green}{efforts} were in vain, for

 she slowly sank and \textcolor{red}{died} without having recovered her

 \textcolor{green}{consciousness.} Such was the \textcolor{BurntOrange}{dreadful} end of my beloved sister."



 "One moment," said Holmes, "are you sure about this whistle and

 metallic sound? Could you \textcolor{green}{swear} to it?"



 "That was what the \textcolor{green}{county} \textcolor{red}{coroner} asked me at the \textcolor{BurntOrange}{inquiry.} It is

 my strong \textcolor{green}{impression} that I heard it, and yet, among the \textcolor{BurntOrange}{crash} of

 the gale and the creaking of an old house, I may possibly have

 been \textcolor{red}{deceived."}



 "Was your sister dressed?"



 "No, she was in her night-dress. In her right hand was \textcolor{green}{found} the

 charred stump of a match, and in her left a match-box."



 \textcolor{green}{"Showing} that she had struck a light and looked about her when

 the \textcolor{BurntOrange}{alarm} took place. That is \textcolor{green}{important.} And what conclusions did

 the \textcolor{red}{coroner} come to?"



 "He \textcolor{green}{investigated} the \textcolor{red}{case} with great care, for Dr. Roylott's

 conduct had \textcolor{blue}{long} been notorious in the \textcolor{green}{county,} but he was \textcolor{red}{unable}

 to find any satisfactory cause of \textcolor{BurntOrange}{death.} My evidence \textcolor{green}{showed} that

 the door had been fastened upon the inner side, and the windows

 were blocked by old-fashioned shutters with broad \textcolor{green}{iron} bars,

 which were secured every night. The walls were \textcolor{green}{carefully} sounded,

 and were \textcolor{green}{shown} to be quite \textcolor{green}{solid} all round, and the flooring was

 also thoroughly examined, with the same \textcolor{blue}{result.} The chimney is

 wide, but is barred up by four large staples. It is certain,

 therefore, that my sister was quite alone when she met her end.

 Besides, there were no marks of any \textcolor{red}{violence} upon her."



 "How about \textcolor{red}{poison?"}



 "The \textcolor{green}{doctors} examined her for it, but without \textcolor{BurntOrange}{success."}



 "What do you think that this \textcolor{red}{unfortunate} lady \textcolor{red}{died} of, then?"



 "It is my belief that she \textcolor{red}{died} of pure \textcolor{red}{fear} and \textcolor{BurntOrange}{nervous} \textcolor{BurntOrange}{shock,}

 though what it was that \textcolor{BurntOrange}{frightened} her I cannot imagine."



 "Were there gipsies in the plantation at the \textcolor{blue}{time?"}



 "Yes, there are nearly always some there."



 "Ah, and what did you gather from this allusion to a band--a

 speckled band?"



 "Sometimes I have \textcolor{blue}{thought} that it was merely the \textcolor{BurntOrange}{wild} \textcolor{green}{talk} of

 \textcolor{red}{delirium,} sometimes that it may have referred to some band of

 people, perhaps to these very gipsies in the plantation. I do not

 know whether the spotted handkerchiefs which so many of them \textcolor{BurntOrange}{wear}

 over their heads might have \textcolor{green}{suggested} the strange adjective which

 she used."



 Holmes shook his head like a man who is far from being \textcolor{green}{satisfied.}



 "These are very deep waters," said he; \textcolor{BurntOrange}{"pray} go on with your

 narrative."



 "Two years have passed since then, and my life has been until

 lately lonelier than ever. A month ago, however, a \textcolor{green}{dear} \textcolor{green}{friend,}

 whom I have known for many years, has done me the honour to ask

 my hand in \textcolor{BurntOrange}{marriage.} His name is Armitage--Percy Armitage--the

 second son of Mr. Armitage, of Crane Water, near \textcolor{green}{Reading.} My

 stepfather has \textcolor{green}{offered} no \textcolor{red}{opposition} to the match, and we are to

 be married in the course of the spring. Two days ago some repairs

 were \textcolor{blue}{started} in the west wing of the \textcolor{green}{building,} and my bedroom

 wall has been pierced, so that I have had to move into the

 chamber in which my sister \textcolor{red}{died,} and to sleep in the very bed in

 which she slept. Imagine, then, my \textcolor{BurntOrange}{thrill} of \textcolor{red}{terror} when last

 night, as I lay awake, thinking over her \textcolor{red}{terrible} \textcolor{BurntOrange}{fate,} I

 \textcolor{blue}{suddenly} heard in the silence of the night the low whistle which

 had been the herald of her own \textcolor{BurntOrange}{death.} I sprang up and lit the

 lamp, but nothing was to be seen in the room. I was too shaken to

 go to bed again, however, so I dressed, and as soon as it was

 daylight I \textcolor{BurntOrange}{slipped} down, got a dog-cart at the Crown Inn, which

 is opposite, and drove to Leatherhead, from whence I have come on

 this morning with the one object of seeing you and asking your

 \textcolor{green}{advice."}



 "You have done wisely," said my \textcolor{green}{friend.} "But have you told me

 all?"



 "Yes, all."



 "Miss Roylott, you have not. You are screening your stepfather."



 "Why, what do you mean?"



 For answer Holmes pushed back the frill of \textcolor{red}{black} \textcolor{BurntOrange}{lace} which

 fringed the hand that lay upon our \textcolor{BurntOrange}{visitor's} knee. Five little

 \textcolor{red}{livid} spots, the marks of four fingers and a thumb, were printed

 upon the \textcolor{BurntOrange}{white} wrist.



 "You have been \textcolor{red}{cruelly} used," said Holmes.



 The lady coloured deeply and \textcolor{green}{covered} over her \textcolor{red}{injured} wrist. "He

 is a hard man," she said, "and perhaps he hardly knows his own

 \textcolor{green}{strength."}



 There was a \textcolor{blue}{long} silence, during which Holmes leaned his chin

 upon his hands and \textcolor{BurntOrange}{stared} into the crackling \textcolor{red}{fire.}



 "This is a very deep business," he said at last. "There are a

 thousand details which I should desire to know before I decide

 upon our course of \textcolor{green}{action.} Yet we have not a moment to \textcolor{BurntOrange}{lose.} If

 we were to come to Stoke Moran to-day, would it be possible for

 us to see over these rooms without the \textcolor{green}{knowledge} of your

 stepfather?"



 "As it happens, he \textcolor{red}{spoke} of coming into town to-day upon some

 most \textcolor{green}{important} business. It is probable that he will be away all

 day, and that there would be nothing to disturb you. We have a

 housekeeper now, but she is old and \textcolor{red}{foolish,} and I could easily

 get her out of the way."



 \textcolor{green}{"Excellent.} You are not \textcolor{red}{averse} to this \textcolor{blue}{trip,} Watson?"



 "By no means."



 "Then we shall both come. What are you going to do yourself?"



 "I have one or two things which I would wish to do now that I am

 in town. But I shall return by the twelve o'clock train, so as to

 be there in \textcolor{blue}{time} for your coming."



 "And you may \textcolor{BurntOrange}{expect} us early in the afternoon. I have myself some

 \textcolor{red}{small} business matters to attend to. Will you not \textcolor{BurntOrange}{wait} and

 \textcolor{green}{breakfast?"}



 "No, I must go. My heart is lightened already since I have

 \textcolor{green}{confided} my trouble to you. I shall look \textcolor{green}{forward} to seeing you

 again this afternoon." She dropped her thick \textcolor{red}{black} veil over her

 face and \textcolor{BurntOrange}{glided} from the room.



 "And what do you think of it all, Watson?" asked Sherlock Holmes,

 leaning back in his chair.



 "It seems to me to be a most \textcolor{red}{dark} and \textcolor{red}{sinister} business."



 \textcolor{red}{"Dark} enough and \textcolor{red}{sinister} enough."



 "Yet if the lady is correct in saying that the flooring and walls

 are sound, and that the door, window, and chimney are \textcolor{red}{impassable,}

 then her sister must have been undoubtedly alone when she met her

 \textcolor{BurntOrange}{mysterious} end."



 "What becomes, then, of these nocturnal whistles, and what of the

 very peculiar \textcolor{green}{words} of the \textcolor{red}{dying} woman?"



 "I cannot think."



 "When you combine the ideas of whistles at night, the \textcolor{green}{presence} of

 a band of gipsies who are on \textcolor{BurntOrange}{intimate} terms with this old \textcolor{green}{doctor,}

 the \textcolor{green}{fact} that we have every \textcolor{green}{reason} to believe that the \textcolor{green}{doctor} has

 an \textcolor{green}{interest} in \textcolor{red}{preventing} his stepdaughter's \textcolor{BurntOrange}{marriage,} the \textcolor{red}{dying}

 allusion to a band, and, \textcolor{BurntOrange}{finally,} the \textcolor{green}{fact} that Miss Helen Stoner

 heard a metallic clang, which might have been caused by one of

 those metal bars that secured the shutters \textcolor{red}{falling} back into its

 place, I think that there is \textcolor{BurntOrange}{good} \textcolor{green}{ground} to think that the

 \textcolor{blue}{mystery} may be cleared along those lines."



 "But what, then, did the gipsies do?"



 "I cannot imagine."



 "I see many \textcolor{red}{objections} to any such \textcolor{BurntOrange}{theory."}



 "And so do I. It is precisely for that \textcolor{green}{reason} that we are going

 to Stoke Moran this day. I want to see whether the \textcolor{red}{objections} are

 \textcolor{red}{fatal,} or if they may be \textcolor{green}{explained} away. But what in the name of

 the \textcolor{BurntOrange}{devil!"}



 The \textcolor{BurntOrange}{ejaculation} had been drawn from my \textcolor{green}{companion} by the \textcolor{green}{fact} that

 our door had been \textcolor{blue}{suddenly} dashed open, and that a huge man had

 framed himself in the aperture. His costume was a peculiar

 mixture of the \textcolor{green}{professional} and of the agricultural, having a

 \textcolor{red}{black} top-hat, a \textcolor{blue}{long} frock-coat, and a pair of high gaiters,

 with a hunting-crop swinging in his hand. So tall was he that his

 hat actually brushed the \textcolor{red}{cross} bar of the doorway, and his

 breadth seemed to span it across from side to side. A large face,

 \textcolor{red}{seared} with a thousand wrinkles, burned yellow with the \textcolor{BurntOrange}{sun,} and

 \textcolor{green}{marked} with every \textcolor{red}{evil} \textcolor{BurntOrange}{passion,} was turned from one to the other

 of us, while his deep-set, bile-shot eyes, and his high, thin,

 fleshless \textcolor{red}{nose,} gave him somewhat the resemblance to a \textcolor{red}{fierce} old

 bird of \textcolor{red}{prey.}



 "Which of you is Holmes?" asked this \textcolor{BurntOrange}{apparition.}



 "My name, \textcolor{green}{sir;} but you have the \textcolor{green}{advantage} of me," said my

 \textcolor{green}{companion} quietly.



 "I am Dr. Grimesby Roylott, of Stoke Moran."



 "Indeed, \textcolor{green}{Doctor,"} said Holmes blandly. \textcolor{BurntOrange}{"Pray} take a seat."



 "I will do nothing of the \textcolor{green}{kind.} My stepdaughter has been here. I

 have traced her. What has she been saying to you?"



 "It is a little \textcolor{red}{cold} for the \textcolor{blue}{time} of the year," said Holmes.



 "What has she been saying to you?" \textcolor{BurntOrange}{screamed} the old man

 \textcolor{red}{furiously.}



 "But I have heard that the crocuses \textcolor{green}{promise} well," continued my

 \textcolor{green}{companion} imperturbably.



 "Ha! You put me off, do you?" said our new \textcolor{BurntOrange}{visitor,} taking a step

 \textcolor{green}{forward} and shaking his hunting-crop. "I know you, you \textcolor{BurntOrange}{scoundrel!}

 I have heard of you before. You are Holmes, the meddler."



 My \textcolor{green}{friend} \textcolor{BurntOrange}{smiled.}



 "Holmes, the busybody!"



 His \textcolor{BurntOrange}{smile} broadened.



 "Holmes, the Scotland Yard Jack-in-office!"



 Holmes \textcolor{BurntOrange}{chuckled} \textcolor{green}{heartily.} "Your conversation is most

 \textcolor{green}{entertaining,"} said he. "When you go out close the door, for

 there is a decided draught."



 "I will go when I have said my say. Don't you \textcolor{BurntOrange}{dare} to \textcolor{red}{meddle} with

 my affairs. I know that Miss Stoner has been here. I traced her!

 I am a \textcolor{red}{dangerous} man to \textcolor{red}{fall} \textcolor{red}{foul} of! See here." He stepped

 swiftly \textcolor{green}{forward,} \textcolor{red}{seized} the poker, and bent it into a curve with

 his huge brown hands.



 "See that you keep yourself out of my grip," he \textcolor{red}{snarled,} and

 hurling the twisted poker into the fireplace he strode out of the

 room.



 "He seems a very \textcolor{green}{amiable} person," said Holmes, \textcolor{BurntOrange}{laughing.} "I am

 not quite so bulky, but if he had remained I might have \textcolor{green}{shown} him

 that my grip was not much more \textcolor{red}{feeble} than his own." As he \textcolor{red}{spoke}

 he picked up the steel poker and, with a \textcolor{blue}{sudden} \textcolor{green}{effort,}

 straightened it out again.



 \textcolor{BurntOrange}{"Fancy} his having the insolence to \textcolor{red}{confound} me with the \textcolor{green}{official}

 detective \textcolor{red}{force!} This \textcolor{blue}{incident} gives \textcolor{BurntOrange}{zest} to our \textcolor{blue}{investigation,}

 however, and I only \textcolor{green}{trust} that our little \textcolor{green}{friend} will not \textcolor{red}{suffer}

 from her imprudence in allowing this \textcolor{red}{brute} to trace her. And now,

 Watson, we shall order \textcolor{green}{breakfast,} and afterwards I shall walk

 down to \textcolor{green}{Doctors'} Commons, where I \textcolor{BurntOrange}{hope} to get some data which may

 help us in this matter."





 It was nearly one o'clock when Sherlock Holmes returned from his

 excursion. He held in his hand a sheet of \textcolor{red}{blue} paper, scrawled

 over with notes and figures.



 "I have seen the will of the deceased wife," said he. "To

 determine its exact meaning I have been \textcolor{BurntOrange}{obliged} to work out the

 \textcolor{BurntOrange}{present} prices of the investments with which it is \textcolor{red}{concerned.} The

 total \textcolor{BurntOrange}{income,} which at the \textcolor{blue}{time} of the wife's \textcolor{BurntOrange}{death} was little

 short of 1100 \textcolor{red}{pounds,} is now, through the \textcolor{red}{fall} in agricultural

 prices, not more than 750 \textcolor{red}{pounds.} Each \textcolor{green}{daughter} can claim an

 \textcolor{BurntOrange}{income} of 250 \textcolor{red}{pounds,} in \textcolor{red}{case} of \textcolor{BurntOrange}{marriage.} It is \textcolor{green}{evident,}

 therefore, that if both girls had married, this \textcolor{green}{beauty} would have

 had a mere pittance, while even one of them would \textcolor{red}{cripple} him to

 a very serious extent. My morning's work has not been \textcolor{red}{wasted,}

 since it has \textcolor{green}{proved} that he has the very strongest motives for

 standing in the way of anything of the sort. And now, Watson,

 this is too serious for dawdling, especially as the old man is

 aware that we are \textcolor{green}{interesting} ourselves in his affairs; so if you

 are \textcolor{blue}{ready,} we shall call a \textcolor{green}{cab} and drive to Waterloo. I should be

 very much \textcolor{BurntOrange}{obliged} if you would \textcolor{BurntOrange}{slip} your \textcolor{red}{revolver} into your

 pocket. An Eley's No. 2 is an \textcolor{green}{excellent} \textcolor{red}{argument} with \textcolor{green}{gentlemen}

 who can twist steel pokers into knots. That and a tooth-brush

 are, I think, all that we need."



 At Waterloo we were \textcolor{green}{fortunate} in \textcolor{blue}{catching} a train for

 Leatherhead, where we \textcolor{BurntOrange}{hired} a trap at the station inn and drove

 for four or five miles through the \textcolor{BurntOrange}{lovely} Surrey lanes. It was a

 \textcolor{BurntOrange}{perfect} day, with a bright \textcolor{BurntOrange}{sun} and a few fleecy clouds in the

 heavens. The \textcolor{BurntOrange}{trees} and wayside hedges were just throwing out

 their first \textcolor{green}{green} \textcolor{red}{shoots,} and the air was \textcolor{green}{full} of the \textcolor{BurntOrange}{pleasant}

 \textcolor{red}{smell} of the moist earth. To me at least there was a strange

 contrast between the \textcolor{BurntOrange}{sweet} \textcolor{green}{promise} of the spring and this

 \textcolor{red}{sinister} \textcolor{BurntOrange}{quest} upon which we were engaged. My \textcolor{green}{companion} sat in

 the front of the trap, his arms folded, his hat \textcolor{green}{pulled} down over

 his eyes, and his chin \textcolor{red}{sunk} upon his breast, \textcolor{red}{buried} in the

 deepest \textcolor{blue}{thought.} \textcolor{blue}{Suddenly,} however, he \textcolor{blue}{started,} tapped me on the

 \textcolor{green}{shoulder,} and pointed over the \textcolor{green}{meadows.}



 "Look there!" said he.



 A \textcolor{red}{heavily} timbered park stretched up in a gentle slope,

 thickening into a grove at the highest point. From amid the

 branches there jutted out the grey gables and high roof-tree of a

 very old mansion.



 "Stoke Moran?" said he.



 "Yes, \textcolor{green}{sir,} that be the house of Dr. Grimesby Roylott," remarked

 the driver.



 "There is some \textcolor{green}{building} going on there," said Holmes; "that is

 where we are going."



 "There's the village," said the driver, pointing to a cluster of

 roofs some distance to the left; "but if you want to get to the

 house, you'll find it shorter to get over this stile, and so by

 the foot-path over the fields. There it is, where the lady is

 walking."



 "And the lady, I \textcolor{BurntOrange}{fancy,} is Miss Stoner," observed Holmes, shading

 his eyes. "Yes, I think we had better do as you \textcolor{green}{suggest."}



 We got off, paid our fare, and the trap rattled back on its way

 to Leatherhead.



 "I \textcolor{blue}{thought} it as well," said Holmes as we climbed the stile,

 "that this \textcolor{green}{fellow} should think we had come here as architects, or

 on some definite business. It may stop his \textcolor{red}{gossip.}

 Good-afternoon, Miss Stoner. You see that we have been as \textcolor{BurntOrange}{good} as

 our \textcolor{green}{word."}



 Our client of the morning had \textcolor{blue}{hurried} \textcolor{green}{forward} to meet us with a

 face which \textcolor{red}{spoke} her \textcolor{green}{joy.} "I have been \textcolor{BurntOrange}{waiting} so eagerly for

 you," she \textcolor{red}{cried,} shaking hands with us warmly. "All has turned

 out splendidly. Dr. Roylott has gone to town, and it is unlikely

 that he will be back before evening."



 "We have had the pleasure of making the \textcolor{green}{doctor's} acquaintance,"

 said Holmes, and in a few \textcolor{green}{words} he sketched out what had

 occurred. Miss Stoner turned \textcolor{BurntOrange}{white} to the lips as she listened.



 \textcolor{BurntOrange}{"Good} heavens!" she \textcolor{red}{cried,} "he has followed me, then."



 "So it appears."



 "He is so \textcolor{BurntOrange}{cunning} that I never know when I am \textcolor{green}{safe} from him. What

 will he say when he returns?"



 "He must \textcolor{BurntOrange}{guard} himself, for he may find that there is someone

 more \textcolor{BurntOrange}{cunning} than himself upon his \textcolor{blue}{track.} You must lock yourself

 up from him to-night. If he is \textcolor{BurntOrange}{violent,} we shall take you away to

 your \textcolor{green}{aunt's} at Harrow. Now, we must make the best use of our

 \textcolor{blue}{time,} so kindly take us at once to the rooms which we are to

 examine."



 The \textcolor{green}{building} was of grey, lichen-blotched \textcolor{red}{stone,} with a high

 central portion and two curving wings, like the \textcolor{red}{claws} of a crab,

 thrown out on each side. In one of these wings the windows were

 \textcolor{red}{broken} and blocked with wooden \textcolor{blue}{boards,} while the roof was partly

 caved in, a picture of \textcolor{red}{ruin.} The central portion was in little

 better repair, but the right-hand block was comparatively modern,

 and the \textcolor{red}{blinds} in the windows, with the \textcolor{red}{blue} smoke \textcolor{green}{curling} up

 from the chimneys, \textcolor{green}{showed} that this was where the family resided.

 Some \textcolor{red}{scaffolding} had been erected against the end wall, and the

 stone-work had been \textcolor{red}{broken} into, but there were no signs of any

 workmen at the moment of our \textcolor{green}{visit.} Holmes walked slowly up and

 down the ill-trimmed lawn and examined with deep \textcolor{green}{attention} the

 outsides of the windows.



 "This, I take it, belongs to the room in which you used to sleep,

 the centre one to your sister's, and the one next to the \textcolor{green}{main}

 \textcolor{green}{building} to Dr. Roylott's chamber?"



 "Exactly so. But I am now sleeping in the middle one."



 "Pending the alterations, as I understand. By the way, there does

 not seem to be any very pressing need for repairs at that end

 wall."



 "There were none. I believe that it was an \textcolor{red}{excuse} to move me from

 my room."



 "Ah! that is suggestive. Now, on the other side of this narrow

 wing runs the corridor from which these three rooms open. There

 are windows in it, of course?"



 "Yes, but very \textcolor{red}{small} ones. Too narrow for anyone to pass

 through."



 "As you both locked your doors at night, your rooms were

 unapproachable from that side. Now, would you have the \textcolor{green}{kindness}

 to go into your room and bar your shutters?"



 Miss Stoner did so, and Holmes, after a \textcolor{green}{careful} \textcolor{BurntOrange}{examination}

 through the open window, endeavoured in every way to \textcolor{red}{force} the

 shutter open, but without \textcolor{BurntOrange}{success.} There was no slit through

 which a knife could be passed to raise the bar. Then with his

 lens he tested the hinges, but they were of \textcolor{green}{solid} \textcolor{green}{iron,} built

 firmly into the massive masonry. "Hum!" said he, scratching his

 chin in some \textcolor{red}{perplexity,} "my \textcolor{BurntOrange}{theory} certainly \textcolor{BurntOrange}{presents} some

 \textcolor{red}{difficulties.} No one could pass these shutters if they were

 bolted. Well, we shall see if the inside throws any light upon

 the matter."



 A \textcolor{red}{small} side door \textcolor{green}{led} into the whitewashed corridor from which

 the three bedrooms opened. Holmes \textcolor{red}{refused} to examine the third

 chamber, so we passed at once to the second, that in which Miss

 Stoner was now sleeping, and in which her sister had met with her

 \textcolor{BurntOrange}{fate.} It was a homely little room, with a low ceiling and a

 \textcolor{red}{gaping} fireplace, after the fashion of old country-houses. A

 brown chest of drawers stood in one corner, a narrow

 white-counterpaned bed in another, and a dressing-table on the

 left-hand side of the window. These articles, with two \textcolor{red}{small}

 wicker-work chairs, made up all the furniture in the room \textcolor{green}{save}

 for a square of Wilton carpet in the centre. The \textcolor{blue}{boards} round and

 the panelling of the walls were of brown, worm-eaten \textcolor{green}{oak,} so old

 and discoloured that it may have dated from the original \textcolor{green}{building}

 of the house. Holmes drew one of the chairs into a corner and sat

 silent, while his eyes travelled round and round and up and down,

 taking in every detail of the apartment.



 "Where does that bell \textcolor{green}{communicate} with?" he asked at last

 pointing to a thick bell-rope which hung down beside the bed, the

 tassel actually \textcolor{red}{lying} upon the \textcolor{green}{pillow.}



 "It goes to the housekeeper's room."



 "It looks newer than the other things?"



 "Yes, it was only put there a couple of years ago."



 "Your sister asked for it, I suppose?"



 "No, I never heard of her using it. We used always to get what we

 wanted for ourselves."



 "Indeed, it seemed unnecessary to put so nice a bell-pull there.

 You will \textcolor{red}{excuse} me for a few minutes while I satisfy myself as to

 this floor." He threw himself down upon his face with his lens in

 his hand and \textcolor{red}{crawled} swiftly \textcolor{red}{backward} and \textcolor{green}{forward,} examining

 minutely the \textcolor{red}{cracks} between the \textcolor{blue}{boards.} Then he did the same with

 the wood-work with which the chamber was panelled. \textcolor{BurntOrange}{Finally} he

 walked over to the bed and \textcolor{red}{spent} some \textcolor{blue}{time} in \textcolor{BurntOrange}{staring} at it and

 in running his eye up and down the wall. \textcolor{BurntOrange}{Finally} he took the

 bell-rope in his hand and gave it a brisk tug.



 "Why, it's a \textcolor{red}{dummy,"} said he.



 \textcolor{blue}{"Won't} it ring?"



 "No, it is not even attached to a wire. This is very \textcolor{green}{interesting.}

 You can see now that it is fastened to a hook just above where

 the little opening for the ventilator is."



 "How very \textcolor{red}{absurd!} I never noticed that before."



 "Very strange!" \textcolor{red}{muttered} Holmes, \textcolor{green}{pulling} at the rope. "There are

 one or two very singular points about this room. For example,

 what a \textcolor{red}{fool} a builder must be to open a ventilator into another

 room, when, with the same trouble, he might have \textcolor{green}{communicated}

 with the outside air!"



 "That is also quite modern," said the lady.



 "Done about the same \textcolor{blue}{time} as the bell-rope?" remarked Holmes.



 "Yes, there were several little \textcolor{red}{changes} carried out about that

 \textcolor{blue}{time."}



 "They seem to have been of a most \textcolor{green}{interesting} character--dummy

 bell-ropes, and ventilators which do not ventilate. With your

 \textcolor{green}{permission,} Miss Stoner, we shall now carry our researches into

 the inner apartment."



 Dr. Grimesby Roylott's chamber was larger than that of his

 step-daughter, but was as plainly furnished. A camp-bed, a \textcolor{red}{small}

 wooden shelf \textcolor{green}{full} of books, mostly of a technical character, an

 armchair beside the bed, a plain wooden chair against the wall, a

 round table, and a large \textcolor{green}{iron} \textcolor{green}{safe} were the \textcolor{green}{principal} things

 which met the eye. Holmes walked slowly round and examined each

 and all of them with the keenest \textcolor{green}{interest.}



 "What's in here?" he asked, tapping the \textcolor{green}{safe.}



 "My stepfather's business papers."



 "Oh! you have seen inside, then?"



 "Only once, some years ago. I remember that it was \textcolor{green}{full} of

 papers."



 "There isn't a cat in it, for example?"



 "No. What a strange idea!"



 "Well, look at this!" He took up a \textcolor{red}{small} saucer of milk which

 stood on the \textcolor{BurntOrange}{top} of it.



 "No; we don't keep a cat. But there is a cheetah and a \textcolor{red}{baboon."}



 "Ah, yes, of course! Well, a cheetah is just a big cat, and yet a

 saucer of milk does not go very far in satisfying its wants, I

 daresay. There is one point which I should wish to determine." He

 squatted down in front of the wooden chair and examined the seat

 of it with the greatest \textcolor{green}{attention.}



 "Thank you. That is quite settled," said he, rising and putting

 his lens in his pocket. "Hullo! Here is something \textcolor{green}{interesting!"}



 The object which had caught his eye was a \textcolor{red}{small} dog \textcolor{red}{lash} hung on

 one corner of the bed. The \textcolor{red}{lash,} however, was \textcolor{green}{curled} upon itself

 and tied so as to make a loop of whipcord.



 "What do you make of that, Watson?"



 "It's a common enough \textcolor{red}{lash.} But I don't know why it should be

 tied."



 "That is not quite so common, is it? Ah, me! it's a \textcolor{red}{wicked} world,

 and when a \textcolor{green}{clever} man turns his brains to \textcolor{red}{crime} it is the \textcolor{red}{worst}

 of all. I think that I have seen enough now, Miss Stoner, and

 with your \textcolor{green}{permission} we shall walk out upon the lawn."



 I had never seen my \textcolor{green}{friend's} face so \textcolor{BurntOrange}{grim} or his brow so \textcolor{red}{dark} as

 it was when we turned from the scene of this \textcolor{blue}{investigation.} We

 had walked several \textcolor{blue}{times} up and down the lawn, neither Miss

 Stoner nor myself liking to \textcolor{blue}{break} in upon his \textcolor{blue}{thoughts} before he

 roused himself from his \textcolor{green}{reverie.}



 "It is very \textcolor{green}{essential,} Miss Stoner," said he, "that you should

 absolutely follow my \textcolor{green}{advice} in every \textcolor{BurntOrange}{respect."}



 "I shall most certainly do so."



 "The matter is too serious for any \textcolor{red}{hesitation.} Your life may

 \textcolor{BurntOrange}{depend} upon your \textcolor{green}{compliance."}



 "I \textcolor{green}{assure} you that I am in your hands."



 "In the first place, both my \textcolor{green}{friend} and I must spend the night in

 your room."



 Both Miss Stoner and I gazed at him in \textcolor{BurntOrange}{astonishment.}



 "Yes, it must be so. Let me \textcolor{green}{explain.} I believe that that is the

 village inn over there?"



 "Yes, that is the Crown."



 "Very \textcolor{BurntOrange}{good.} Your windows would be visible from there?"



 "Certainly."



 "You must \textcolor{red}{confine} yourself to your room, on pretence of a

 \textcolor{red}{headache,} when your stepfather comes back. Then when you hear him

 retire for the night, you must open the shutters of your window,

 \textcolor{red}{undo} the hasp, put your lamp there as a signal to us, and then

 \textcolor{red}{withdraw} quietly with everything which you are likely to want

 into the room which you used to \textcolor{green}{occupy.} I have no \textcolor{BurntOrange}{doubt} that, in

 \textcolor{red}{spite} of the repairs, you could \textcolor{green}{manage} there for one night."



 "Oh, yes, easily."



 "The \textcolor{green}{rest} you will \textcolor{BurntOrange}{leave} in our hands."



 "But what will you do?"



 "We shall spend the night in your room, and we shall \textcolor{green}{investigate}

 the cause of this \textcolor{red}{noise} which has \textcolor{red}{disturbed} you."



 "I believe, Mr. Holmes, that you have already made up your mind,"

 said Miss Stoner, laying her hand upon my \textcolor{green}{companion's} sleeve.



 "Perhaps I have."



 "Then, for \textcolor{red}{pity's} sake, tell me what was the cause of my sister's

 \textcolor{BurntOrange}{death."}



 "I should \textcolor{green}{prefer} to have clearer \textcolor{green}{proofs} before I speak."



 "You can at least tell me whether my own \textcolor{blue}{thought} is correct, and

 if she \textcolor{red}{died} from some \textcolor{blue}{sudden} \textcolor{BurntOrange}{fright."}



 "No, I do not think so. I think that there was probably some more

 tangible cause. And now, Miss Stoner, we must \textcolor{BurntOrange}{leave} you for if

 Dr. Roylott returned and saw us our \textcolor{BurntOrange}{journey} would be in vain.

 Good-bye, and be brave, for if you will do what I have told you,

 you may \textcolor{green}{rest} \textcolor{green}{assured} that we shall soon drive away the \textcolor{red}{dangers}

 that \textcolor{BurntOrange}{threaten} you."



 Sherlock Holmes and I had no \textcolor{red}{difficulty} in engaging a bedroom and

 sitting-room at the Crown Inn. They were on the upper floor, and

 from our window we could command a view of the avenue \textcolor{green}{gate,} and

 of the inhabited wing of Stoke Moran Manor House. At dusk we saw

 Dr. Grimesby Roylott drive past, his huge form \textcolor{BurntOrange}{looming} up beside

 the little figure of the lad who drove him. The \textcolor{red}{boy} had some

 slight \textcolor{red}{difficulty} in \textcolor{red}{undoing} the heavy \textcolor{green}{iron} \textcolor{green}{gates,} and we heard

 the \textcolor{red}{hoarse} roar of the \textcolor{green}{doctor's} voice and saw the \textcolor{red}{fury} with which

 he shook his clinched fists at him. The trap drove on, and a few

 minutes later we saw a \textcolor{blue}{sudden} light spring up among the \textcolor{BurntOrange}{trees} as

 the lamp was lit in one of the sitting-rooms.



 "Do you know, Watson," said Holmes as we sat together in the

 gathering \textcolor{red}{darkness,} "I have really some scruples as to taking you

 to-night. There is a distinct element of \textcolor{red}{danger."}



 "Can I be of \textcolor{green}{assistance?"}



 "Your \textcolor{green}{presence} might be invaluable."



 "Then I shall certainly come."



 "It is very \textcolor{green}{kind} of you."



 "You speak of \textcolor{red}{danger.} You have evidently seen more in these rooms

 than was visible to me."



 "No, but I \textcolor{BurntOrange}{fancy} that I may have deduced a little more. I imagine

 that you saw all that I did."



 "I saw nothing \textcolor{BurntOrange}{remarkable} \textcolor{green}{save} the bell-rope, and what purpose

 that could answer I \textcolor{BurntOrange}{confess} is more than I can imagine."



 "You saw the ventilator, too?"



 "Yes, but I do not think that it is such a very unusual thing to

 have a \textcolor{red}{small} opening between two rooms. It was so \textcolor{red}{small} that a

 \textcolor{red}{rat} could hardly pass through."



 "I knew that we should find a ventilator before ever we came to

 Stoke Moran."



 "My \textcolor{green}{dear} Holmes!"



 "Oh, yes, I did. You remember in her \textcolor{green}{statement} she said that her

 sister could \textcolor{red}{smell} Dr. Roylott's cigar. Now, of course that

 \textcolor{green}{suggested} at once that there must be a \textcolor{green}{communication} between the

 two rooms. It could only be a \textcolor{red}{small} one, or it would have been

 remarked upon at the \textcolor{red}{coroner's} \textcolor{BurntOrange}{inquiry.} I deduced a ventilator."



 "But what \textcolor{red}{harm} can there be in that?"



 "Well, there is at least a curious \textcolor{blue}{coincidence} of dates. A

 ventilator is made, a cord is hung, and a lady who sleeps in the

 bed dies. Does not that \textcolor{red}{strike} you?"



 "I cannot as yet see any connection."



 "Did you observe anything very peculiar about that bed?"



 "No."



 "It was clamped to the floor. Did you ever see a bed fastened

 like that before?"



 "I cannot say that I have."



 "The lady could not move her bed. It must always be in the same

 \textcolor{green}{relative} position to the ventilator and to the rope--or so we may

 call it, since it was clearly never meant for a bell-pull."



 "Holmes," I \textcolor{red}{cried,} "I seem to see dimly what you are hinting at.

 We are only just in \textcolor{blue}{time} to \textcolor{red}{prevent} some subtle and \textcolor{red}{horrible}

 \textcolor{red}{crime."}



 "Subtle enough and \textcolor{red}{horrible} enough. When a \textcolor{green}{doctor} does go \textcolor{red}{wrong}

 he is the first of \textcolor{red}{criminals.} He has \textcolor{green}{nerve} and he has \textcolor{green}{knowledge.}

 Palmer and Pritchard were among the heads of their \textcolor{green}{profession.}

 This man \textcolor{red}{strikes} even deeper, but I think, Watson, that we shall

 be able to \textcolor{red}{strike} deeper still. But we shall have \textcolor{BurntOrange}{horrors} enough

 before the night is over; for \textcolor{BurntOrange}{goodness'} sake let us have a \textcolor{BurntOrange}{quiet}

 pipe and turn our minds for a few hours to something more

 \textcolor{BurntOrange}{cheerful."}





 About nine o'clock the light among the \textcolor{BurntOrange}{trees} was \textcolor{red}{extinguished,}

 and all was \textcolor{red}{dark} in the direction of the Manor House. Two hours

 passed slowly away, and then, \textcolor{blue}{suddenly,} just at the \textcolor{red}{stroke} of

 eleven, a single bright light shone out right in front of us.



 "That is our signal," said Holmes, springing to his feet; "it

 comes from the middle window."



 As we passed out he \textcolor{green}{exchanged} a few \textcolor{green}{words} with the landlord,

 \textcolor{green}{explaining} that we were going on a \textcolor{red}{late} \textcolor{green}{visit} to an acquaintance,

 and that it was possible that we might spend the night there. A

 moment later we were out on the \textcolor{red}{dark} road, a chill wind blowing

 in our faces, and one yellow light \textcolor{BurntOrange}{twinkling} in front of us

 through the \textcolor{red}{gloom} to \textcolor{green}{guide} us on our sombre \textcolor{BurntOrange}{errand.}



 There was little \textcolor{red}{difficulty} in entering the \textcolor{green}{grounds,} for

 unrepaired \textcolor{red}{breaches} gaped in the old park wall. Making our way

 among the \textcolor{BurntOrange}{trees,} we reached the lawn, \textcolor{red}{crossed} it, and were about

 to enter through the window when out from a \textcolor{red}{clump} of \textcolor{green}{laurel}

 bushes there \textcolor{red}{darted} what seemed to be a \textcolor{red}{hideous} and distorted

 \textcolor{BurntOrange}{child,} who threw itself upon the grass with writhing limbs and

 then ran swiftly across the lawn into the \textcolor{red}{darkness.}



 "My \textcolor{BurntOrange}{God!"} I whispered; "did you see it?"



 Holmes was for the moment as \textcolor{BurntOrange}{startled} as I. His hand closed like

 a \textcolor{red}{vice} upon my wrist in his \textcolor{red}{agitation.} Then he \textcolor{red}{broke} into a low

 \textcolor{BurntOrange}{laugh} and put his lips to my ear.



 "It is a nice \textcolor{green}{household,"} he murmured. "That is the \textcolor{red}{baboon."}



 I had \textcolor{red}{forgotten} the strange \textcolor{red}{pets} which the \textcolor{green}{doctor} affected. There

 was a cheetah, too; perhaps we might find it upon our \textcolor{green}{shoulders}

 at any moment. I \textcolor{BurntOrange}{confess} that I felt easier in my mind when,

 after following Holmes' example and \textcolor{BurntOrange}{slipping} off my shoes, I

 \textcolor{green}{found} myself inside the bedroom. My \textcolor{green}{companion} noiselessly closed

 the shutters, moved the lamp onto the table, and cast his eyes

 round the room. All was as we had seen it in the daytime. Then

 \textcolor{red}{creeping} up to me and making a \textcolor{red}{trumpet} of his hand, he whispered

 into my ear again so gently that it was all that I could do to

 distinguish the \textcolor{green}{words:}



 "The least sound would be \textcolor{red}{fatal} to our \textcolor{blue}{plans."}



 I nodded to \textcolor{green}{show} that I had heard.



 "We must sit without light. He would see it through the

 ventilator."



 I nodded again.



 "Do not go asleep; your very life may \textcolor{BurntOrange}{depend} upon it. Have your

 \textcolor{red}{pistol} \textcolor{blue}{ready} in \textcolor{red}{case} we should need it. I will sit on the side of

 the bed, and you in that chair."



 I took out my \textcolor{red}{revolver} and laid it on the corner of the table.



 Holmes had brought up a \textcolor{blue}{long} thin \textcolor{red}{cane,} and this he placed upon

 the bed beside him. By it he laid the box of matches and the

 stump of a candle. Then he turned down the lamp, and we were left

 in \textcolor{red}{darkness.}



 How shall I ever \textcolor{red}{forget} that \textcolor{BurntOrange}{dreadful} \textcolor{blue}{vigil?} I could not hear a

 sound, not even the drawing of a breath, and yet I knew that my

 \textcolor{green}{companion} sat open-eyed, within a few feet of me, in the same

 state of \textcolor{BurntOrange}{nervous} \textcolor{red}{tension} in which I was myself. The shutters cut

 off the least ray of light, and we \textcolor{BurntOrange}{waited} in \textcolor{green}{absolute} \textcolor{red}{darkness.}



 From outside came the \textcolor{blue}{occasional} \textcolor{red}{cry} of a night-bird, and once at

 our very window a \textcolor{blue}{long} drawn catlike \textcolor{red}{whine,} which told us that

 the cheetah was indeed at \textcolor{BurntOrange}{liberty.} Far away we could hear the

 deep tones of the \textcolor{green}{parish} \textcolor{blue}{clock,} which boomed out every quarter of

 an hour. How \textcolor{blue}{long} they seemed, those quarters! Twelve struck, and

 one and two and three, and still we sat \textcolor{BurntOrange}{waiting} silently for

 whatever might \textcolor{red}{befall.}



 \textcolor{blue}{Suddenly} there was the momentary gleam of a light up in the

 direction of the ventilator, which \textcolor{BurntOrange}{vanished} \textcolor{BurntOrange}{immediately,} but was

 \textcolor{BurntOrange}{succeeded} by a strong \textcolor{red}{smell} of burning oil and heated metal.

 Someone in the next room had lit a dark-lantern. I heard a gentle

 sound of movement, and then all was silent once more, though the

 \textcolor{red}{smell} \textcolor{BurntOrange}{grew} stronger. For half an hour I sat with straining ears.

 Then \textcolor{blue}{suddenly} another sound became audible--a very gentle,

 \textcolor{green}{soothing} sound, like that of a \textcolor{red}{small} jet of steam \textcolor{BurntOrange}{escaping}

 continually from a kettle. The instant that we heard it, Holmes

 sprang from the bed, struck a match, and \textcolor{red}{lashed} \textcolor{red}{furiously} with

 his \textcolor{red}{cane} at the bell-pull.



 "You see it, Watson?" he \textcolor{BurntOrange}{yelled.} "You see it?"



 But I saw nothing. At the moment when Holmes struck the light I

 heard a low, clear whistle, but the \textcolor{blue}{sudden} \textcolor{red}{glare} flashing into my

 \textcolor{red}{weary} eyes made it \textcolor{red}{impossible} for me to tell what it was at which

 my \textcolor{green}{friend} \textcolor{red}{lashed} so savagely. I could, however, see that his face

 was \textcolor{red}{deadly} pale and \textcolor{green}{filled} with \textcolor{BurntOrange}{horror} and \textcolor{red}{loathing.} He had

 ceased to \textcolor{red}{strike} and was gazing up at the ventilator when

 \textcolor{blue}{suddenly} there \textcolor{red}{broke} from the silence of the night the most

 \textcolor{red}{horrible} \textcolor{red}{cry} to which I have ever listened. It swelled up louder

 and louder, a \textcolor{red}{hoarse} \textcolor{BurntOrange}{yell} of \textcolor{red}{pain} and \textcolor{red}{fear} and \textcolor{red}{anger} all mingled

 in the one \textcolor{BurntOrange}{dreadful} \textcolor{BurntOrange}{shriek.} They say that away down in the

 village, and even in the distant parsonage, that \textcolor{red}{cry} raised the

 sleepers from their beds. It struck \textcolor{red}{cold} to our hearts, and I

 stood gazing at Holmes, and he at me, until the last echoes of it

 had \textcolor{red}{died} away into the silence from which it rose.



 "What can it mean?" I gasped.



 "It means that it is all over," Holmes answered. "And perhaps,

 after all, it is for the best. Take your \textcolor{red}{pistol,} and we will

 enter Dr. Roylott's room."



 With a \textcolor{red}{grave} face he lit the lamp and \textcolor{green}{led} the way down the

 corridor. Twice he struck at the chamber door without any reply

 from within. Then he turned the handle and entered, I at his

 \textcolor{red}{heels,} with the cocked \textcolor{red}{pistol} in my hand.



 It was a singular sight which met our eyes. On the table stood a

 dark-lantern with the shutter half open, throwing a \textcolor{BurntOrange}{brilliant}

 \textcolor{green}{beam} of light upon the \textcolor{green}{iron} \textcolor{green}{safe,} the door of which was ajar.

 Beside this table, on the wooden chair, sat Dr. Grimesby Roylott

 clad in a \textcolor{blue}{long} grey dressing-gown, his bare ankles protruding

 beneath, and his feet thrust into red heelless Turkish slippers.

 Across his lap lay the short stock with the \textcolor{blue}{long} \textcolor{red}{lash} which we

 had noticed during the day. His chin was cocked upward and his

 eyes were fixed in a \textcolor{BurntOrange}{dreadful,} \textcolor{red}{rigid} stare at the corner of the

 ceiling. Round his brow he had a peculiar yellow band, with

 brownish speckles, which seemed to be \textcolor{red}{bound} tightly round his

 head. As we entered he made neither sound nor \textcolor{blue}{motion.}



 "The band! the speckled band!" whispered Holmes.



 I took a step \textcolor{green}{forward.} In an instant his strange headgear began

 to move, and there \textcolor{red}{reared} itself from among his hair the squat

 diamond-shaped head and puffed neck of a \textcolor{red}{loathsome} \textcolor{red}{serpent.}



 "It is a \textcolor{red}{swamp} \textcolor{red}{adder!"} \textcolor{red}{cried} Holmes; "the deadliest \textcolor{red}{snake} in

 India. He has \textcolor{red}{died} within ten seconds of being bitten. \textcolor{red}{Violence}

 does, in \textcolor{green}{truth,} recoil upon the \textcolor{BurntOrange}{violent,} and the schemer \textcolor{red}{falls}

 into the pit which he digs for another. Let us thrust this

 \textcolor{red}{creature} back into its den, and we can then \textcolor{red}{remove} Miss Stoner to

 some place of \textcolor{green}{shelter} and let the \textcolor{green}{county} \textcolor{BurntOrange}{police} know what has

 \textcolor{blue}{happened."}



 As he \textcolor{red}{spoke} he drew the dog-whip swiftly from the dead man's lap,

 and throwing the \textcolor{red}{noose} round the reptile's neck he drew it from

 its \textcolor{red}{horrid} perch and, carrying it at arm's length, threw it into

 the \textcolor{green}{iron} \textcolor{green}{safe,} which he closed upon it.



 Such are the \textcolor{green}{true} \textcolor{green}{facts} of the \textcolor{BurntOrange}{death} of Dr. Grimesby Roylott, of

 Stoke Moran. It is not necessary that I should \textcolor{red}{prolong} a

 narrative which has already run to too great a length by telling

 how we \textcolor{red}{broke} the sad news to the terrified girl, how we conveyed

 her by the morning train to the care of her \textcolor{BurntOrange}{good} \textcolor{green}{aunt} at Harrow,

 of how the slow process of \textcolor{green}{official} \textcolor{BurntOrange}{inquiry} came to the

 conclusion that the \textcolor{green}{doctor} met his \textcolor{BurntOrange}{fate} while indiscreetly

 playing with a \textcolor{red}{dangerous} \textcolor{red}{pet.} The little which I had yet to \textcolor{green}{learn}

 of the \textcolor{red}{case} was told me by Sherlock Holmes as we travelled back

 next day.



 "I had," said he, "come to an entirely \textcolor{red}{erroneous} conclusion which

 \textcolor{green}{shows,} my \textcolor{green}{dear} Watson, how \textcolor{red}{dangerous} it always is to \textcolor{green}{reason} from

 \textcolor{red}{insufficient} data. The \textcolor{green}{presence} of the gipsies, and the use of

 the \textcolor{green}{word} 'band,' which was used by the poor girl, no \textcolor{BurntOrange}{doubt,} to

 \textcolor{green}{explain} the appearance which she had caught a \textcolor{blue}{hurried} glimpse of

 by the light of her match, were sufficient to put me upon an

 entirely \textcolor{red}{wrong} scent. I can only claim the \textcolor{green}{merit} that I instantly

 reconsidered my position when, however, it became clear to me

 that whatever \textcolor{red}{danger} \textcolor{BurntOrange}{threatened} an \textcolor{green}{occupant} of the room could not

 come either from the window or the door. My \textcolor{green}{attention} was

 speedily drawn, as I have already remarked to you, to this

 ventilator, and to the bell-rope which hung down to the bed. The

 \textcolor{green}{discovery} that this was a \textcolor{red}{dummy,} and that the bed was clamped to

 the floor, instantly gave rise to the \textcolor{red}{suspicion} that the rope was

 there as a bridge for something passing through the hole and

 coming to the bed. The idea of a \textcolor{red}{snake} instantly occurred to me,

 and when I coupled it with my \textcolor{green}{knowledge} that the \textcolor{green}{doctor} was

 furnished with a \textcolor{green}{supply} of \textcolor{red}{creatures} from India, I felt that I

 was probably on the right \textcolor{blue}{track.} The idea of using a form of

 \textcolor{red}{poison} which could not possibly be discovered by any chemical

 test was just such a one as would occur to a \textcolor{green}{clever} and \textcolor{red}{ruthless}

 man who had had an Eastern training. The rapidity with which such

 a \textcolor{red}{poison} would take effect would also, from his point of view, be

 an \textcolor{green}{advantage.} It would be a sharp-eyed \textcolor{red}{coroner,} indeed, who could

 distinguish the two little \textcolor{red}{dark} punctures which would \textcolor{green}{show} where

 the \textcolor{red}{poison} \textcolor{red}{fangs} had done their work. Then I \textcolor{blue}{thought} of the

 whistle. Of course he must recall the \textcolor{red}{snake} before the morning

 light revealed it to the \textcolor{red}{victim.} He had trained it, probably by

 the use of the milk which we saw, to return to him when summoned.

 He would put it through this ventilator at the hour that he

 \textcolor{blue}{thought} best, with the \textcolor{green}{certainty} that it would \textcolor{red}{crawl} down the

 rope and \textcolor{green}{land} on the bed. It might or might not \textcolor{red}{bite} the

 \textcolor{green}{occupant,} perhaps she might \textcolor{BurntOrange}{escape} every night for a week, but

 sooner or later she must \textcolor{red}{fall} a \textcolor{red}{victim.}



 "I had come to these conclusions before ever I had entered his

 room. An inspection of his chair \textcolor{green}{showed} me that he had been in

 the habit of standing on it, which of course would be necessary

 in order that he should reach the ventilator. The sight of the

 \textcolor{green}{safe,} the saucer of milk, and the loop of whipcord were enough to

 \textcolor{BurntOrange}{finally} \textcolor{red}{dispel} any \textcolor{BurntOrange}{doubts} which may have remained. The metallic

 clang heard by Miss Stoner was obviously caused by her stepfather

 hastily closing the door of his \textcolor{green}{safe} upon its \textcolor{red}{terrible} \textcolor{green}{occupant.}

 Having once made up my mind, you know the steps which I took in

 order to put the matter to the \textcolor{green}{proof.} I heard the \textcolor{red}{creature} \textcolor{red}{hiss}

 as I have no \textcolor{BurntOrange}{doubt} that you did also, and I instantly lit the

 light and \textcolor{red}{attacked} it."



 "With the \textcolor{blue}{result} of driving it through the ventilator."



 "And also with the \textcolor{blue}{result} of causing it to turn upon its \textcolor{green}{master}

 at the other side. Some of the blows of my \textcolor{red}{cane} came home and

 roused its snakish temper, so that it flew upon the first person

 it saw. In this way I am no \textcolor{BurntOrange}{doubt} indirectly \textcolor{green}{responsible} for Dr.

 Grimesby Roylott's \textcolor{BurntOrange}{death,} and I cannot say that it is likely to

 \textcolor{BurntOrange}{weigh} very \textcolor{red}{heavily} upon my \textcolor{green}{conscience."}







 IX. THE \textcolor{BurntOrange}{ADVENTURE} OF THE ENGINEER'S THUMB



 Of all the \textcolor{red}{problems} which have been \textcolor{blue}{submitted} to my \textcolor{green}{friend,} Mr.

 Sherlock Holmes, for \textcolor{green}{solution} during the years of our intimacy,

 there were only two which I was the means of introducing to his

 notice--that of Mr. Hatherley's thumb, and that of \textcolor{green}{Colonel}

 Warburton's \textcolor{red}{madness.} Of these the latter may have \textcolor{green}{afforded} a

 finer field for an acute and original observer, but the other was

 so strange in its inception and so dramatic in its details that

 it may be the more \textcolor{green}{worthy} of being placed upon record, even if it

 gave my \textcolor{green}{friend} fewer openings for those deductive methods of

 \textcolor{green}{reasoning} by which he \textcolor{green}{achieved} such \textcolor{BurntOrange}{remarkable} \textcolor{blue}{results.} The story

 has, I believe, been told more than once in the newspapers, but,

 like all such narratives, its effect is much less \textcolor{red}{striking} when

 set forth en bloc in a single half-column of print than when the

 \textcolor{green}{facts} slowly evolve before your own eyes, and the \textcolor{blue}{mystery} clears

 gradually away as each new \textcolor{green}{discovery} furnishes a step which \textcolor{green}{leads}

 on to the complete \textcolor{green}{truth.} At the \textcolor{blue}{time} the circumstances made a

 deep \textcolor{green}{impression} upon me, and the \textcolor{red}{lapse} of two years has hardly

 \textcolor{BurntOrange}{served} to weaken the effect.



 It was in the summer of '89, not \textcolor{blue}{long} after my \textcolor{BurntOrange}{marriage,} that the

 events occurred which I am now about to summarise. I had returned

 to \textcolor{green}{civil} \textcolor{green}{practice} and had \textcolor{BurntOrange}{finally} \textcolor{red}{abandoned} Holmes in his Baker

 Street rooms, although I continually \textcolor{green}{visited} him and occasionally

 even \textcolor{green}{persuaded} him to forgo his Bohemian habits so far as to come

 and \textcolor{green}{visit} us. My \textcolor{green}{practice} had steadily \textcolor{green}{increased,} and as I

 \textcolor{blue}{happened} to live at no very great distance from Paddington

 Station, I got a few \textcolor{BurntOrange}{patients} from among the \textcolor{green}{officials.} One of

 these, whom I had cured of a \textcolor{red}{painful} and \textcolor{blue}{lingering} \textcolor{red}{disease,} was

 never \textcolor{red}{weary} of advertising my \textcolor{green}{virtues} and of endeavouring to send

 me on every \textcolor{red}{sufferer} over whom he might have any \textcolor{BurntOrange}{influence.}



 One morning, at a little before seven o'clock, I was awakened by

 the maid tapping at the door to announce that two men had come

 from Paddington and were \textcolor{BurntOrange}{waiting} in the consulting-room. I

 dressed hurriedly, for I knew by experience that railway \textcolor{red}{cases}

 were seldom trivial, and hastened downstairs. As I descended, my

 old \textcolor{green}{ally,} the \textcolor{BurntOrange}{guard,} came out of the room and closed the door

 tightly behind him.



 "I've got him here," he whispered, jerking his thumb over his

 \textcolor{green}{shoulder;} "he's all right."



 "What is it, then?" I asked, for his manner \textcolor{green}{suggested} that it was

 some strange \textcolor{red}{creature} which he had \textcolor{red}{caged} up in my room.



 "It's a new \textcolor{BurntOrange}{patient,"} he whispered. "I \textcolor{blue}{thought} I'd bring him

 round myself; then he couldn't \textcolor{BurntOrange}{slip} away. There he is, all \textcolor{green}{safe}

 and sound. I must go now, \textcolor{green}{Doctor;} I have my dooties, just the

 same as you." And off he went, this \textcolor{green}{trusty} tout, without even

 giving me \textcolor{blue}{time} to thank him.



 I entered my consulting-room and \textcolor{green}{found} a \textcolor{green}{gentleman} seated by the

 table. He was quietly dressed in a suit of heather tweed with a

 soft cloth \textcolor{BurntOrange}{cap} which he had laid down upon my books. Round one of

 his hands he had a handkerchief wrapped, which was mottled all

 over with bloodstains. He was \textcolor{BurntOrange}{young,} not more than

 five-and-twenty, I should say, with a strong, \textcolor{green}{masculine} face; but

 he was exceedingly pale and gave me the \textcolor{green}{impression} of a man who

 was \textcolor{red}{suffering} from some strong \textcolor{red}{agitation,} which it took all his

 \textcolor{green}{strength} of mind to control.



 "I am sorry to knock you up so early, \textcolor{green}{Doctor,"} said he, "but I

 have had a very serious \textcolor{BurntOrange}{accident} during the night. I came in by

 train this morning, and on inquiring at Paddington as to where I

 might find a \textcolor{green}{doctor,} a \textcolor{green}{worthy} \textcolor{green}{fellow} very kindly \textcolor{green}{escorted} me

 here. I gave the maid a card, but I see that she has left it upon

 the side-table."



 I took it up and glanced at it. "Mr. \textcolor{green}{Victor} Hatherley, hydraulic

 engineer, 16A, Victoria Street (3rd floor)." That was the name,

 style, and abode of my morning \textcolor{BurntOrange}{visitor.} "I \textcolor{red}{regret} that I have

 kept you \textcolor{BurntOrange}{waiting,"} said I, sitting down in my library-chair. "You

 are fresh from a night \textcolor{BurntOrange}{journey,} I understand, which is in itself

 a monotonous \textcolor{green}{occupation."}



 "Oh, my night could not be called monotonous," said he, and

 \textcolor{BurntOrange}{laughed.} He \textcolor{BurntOrange}{laughed} very \textcolor{green}{heartily,} with a high, ringing note,

 leaning back in his chair and shaking his sides. All my \textcolor{BurntOrange}{medical}

 instincts rose up against that \textcolor{BurntOrange}{laugh.}



 "Stop it!" I \textcolor{red}{cried;} \textcolor{green}{"pull} yourself together!" and I poured out

 some water from a caraffe.



 It was \textcolor{red}{useless,} however. He was off in one of those \textcolor{red}{hysterical}

 \textcolor{BurntOrange}{outbursts} which come upon a strong nature when some great \textcolor{red}{crisis}

 is over and gone. Presently he came to himself once more, very

 \textcolor{red}{weary} and pale-looking.



 "I have been making a \textcolor{red}{fool} of myself," he gasped.



 "Not at all. Drink this." I dashed some \textcolor{red}{brandy} into the water,

 and the colour began to come back to his \textcolor{green}{bloodless} cheeks.



 "That's better!" said he. "And now, \textcolor{green}{Doctor,} perhaps you would

 kindly attend to my thumb, or rather to the place where my thumb

 used to be."



 He unwound the handkerchief and held out his hand. It gave even

 my hardened \textcolor{green}{nerves} a \textcolor{red}{shudder} to look at it. There were four

 protruding fingers and a \textcolor{red}{horrid} red, spongy surface where the

 thumb should have been. It had been hacked or \textcolor{red}{torn} right out from

 the roots.



 \textcolor{BurntOrange}{"Good} heavens!" I \textcolor{red}{cried,} "this is a \textcolor{red}{terrible} \textcolor{red}{injury.} It must have

 bled considerably."



 "Yes, it did. I fainted when it was done, and I think that I must

 have been \textcolor{BurntOrange}{senseless} for a \textcolor{blue}{long} \textcolor{blue}{time.} When I came to I \textcolor{green}{found} that

 it was still \textcolor{red}{bleeding,} so I tied one end of my handkerchief very

 tightly round the wrist and braced it up with a twig."



 \textcolor{green}{"Excellent!} You should have been a surgeon."



 "It is a \textcolor{green}{question} of hydraulics, you see, and came within my own

 province."



 "This has been done," said I, examining the \textcolor{red}{wound,} "by a very

 heavy and sharp instrument."



 "A thing like a cleaver," said he.



 "An \textcolor{BurntOrange}{accident,} I presume?"



 "By no means."



 "What! a \textcolor{BurntOrange}{murderous} \textcolor{red}{attack?"}



 "Very \textcolor{BurntOrange}{murderous} indeed."



 "You horrify me."



 I \textcolor{red}{sponged} the \textcolor{red}{wound,} \textcolor{green}{cleaned} it, dressed it, and \textcolor{BurntOrange}{finally} \textcolor{green}{covered}

 it over with cotton wadding and carbolised bandages. He lay back

 without \textcolor{red}{wincing,} though he bit his lip from \textcolor{blue}{time} to \textcolor{blue}{time.}



 "How is that?" I asked when I had finished.



 "Capital! Between your \textcolor{red}{brandy} and your bandage, I feel a new man.

 I was very weak, but I have had a \textcolor{BurntOrange}{good} \textcolor{BurntOrange}{deal} to go through."



 "Perhaps you had better not speak of the matter. It is evidently

 trying to your \textcolor{green}{nerves."}



 "Oh, no, not now. I shall have to tell my \textcolor{green}{tale} to the \textcolor{BurntOrange}{police;}

 but, between ourselves, if it were not for the \textcolor{green}{convincing}

 evidence of this \textcolor{red}{wound} of mine, I should be \textcolor{blue}{surprised} if they

 believed my \textcolor{green}{statement,} for it is a very \textcolor{green}{extraordinary} one, and I

 have not much in the way of \textcolor{green}{proof} with which to back it up; and,

 even if they believe me, the \textcolor{blue}{clues} which I can give them are so

 \textcolor{red}{vague} that it is a \textcolor{green}{question} whether \textcolor{green}{justice} will be done."



 "Ha!" \textcolor{red}{cried} I, "if it is anything in the nature of a \textcolor{red}{problem}

 which you desire to see solved, I should \textcolor{green}{strongly} \textcolor{green}{recommend} you

 to come to my \textcolor{green}{friend,} Mr. Sherlock Holmes, before you go to the

 \textcolor{green}{official} \textcolor{BurntOrange}{police."}



 "Oh, I have heard of that \textcolor{green}{fellow,"} answered my \textcolor{BurntOrange}{visitor,} "and I

 should be very \textcolor{BurntOrange}{glad} if he would take the matter up, though of

 course I must use the \textcolor{green}{official} \textcolor{BurntOrange}{police} as well. Would you give me

 an introduction to him?"



 \textcolor{red}{"I'll} do better. \textcolor{red}{I'll} take you round to him myself."



 "I should be immensely \textcolor{BurntOrange}{obliged} to you."



 "We'll call a \textcolor{green}{cab} and go together. We shall just be in \textcolor{blue}{time} to

 have a little \textcolor{green}{breakfast} with him. Do you feel equal to it?"



 "Yes; I shall not feel easy until I have told my story."



 "Then my \textcolor{BurntOrange}{servant} will call a \textcolor{green}{cab,} and I shall be with you in an

 instant." I rushed upstairs, \textcolor{green}{explained} the matter \textcolor{blue}{shortly} to my

 wife, and in five minutes was inside a hansom, driving with my

 new acquaintance to Baker Street.



 Sherlock Holmes was, as I \textcolor{BurntOrange}{expected,} \textcolor{red}{lounging} about his

 sitting-room in his dressing-gown, \textcolor{green}{reading} the \textcolor{red}{agony} column of The

 \textcolor{blue}{Times} and smoking his before-breakfast pipe, which was composed

 of all the plugs and dottles left from his smokes of the day

 before, all \textcolor{green}{carefully} dried and collected on the corner of the

 mantelpiece. He received us in his quietly \textcolor{green}{genial} fashion,

 ordered fresh rashers and eggs, and \textcolor{green}{joined} us in a hearty meal.

 When it was concluded he settled our new acquaintance upon the

 sofa, placed a \textcolor{green}{pillow} beneath his head, and laid a glass of

 \textcolor{red}{brandy} and water within his reach.



 "It is easy to see that your experience has been no common one,

 Mr. Hatherley," said he. \textcolor{BurntOrange}{"Pray,} \textcolor{red}{lie} down there and make yourself

 absolutely at home. Tell us what you can, but stop when you are

 tired and keep up your \textcolor{green}{strength} with a little stimulant."



 "Thank you," said my \textcolor{BurntOrange}{patient,} "but I have felt another man since

 the \textcolor{green}{doctor} bandaged me, and I think that your \textcolor{green}{breakfast} has

 completed the cure. I shall take up as little of your \textcolor{green}{valuable}

 \textcolor{blue}{time} as possible, so I shall \textcolor{blue}{start} at once upon my peculiar

 experiences."



 Holmes sat in his big armchair with the \textcolor{red}{weary,} heavy-lidded

 expression which veiled his keen and \textcolor{BurntOrange}{eager} nature, while I sat

 opposite to him, and we listened in silence to the strange story

 which our \textcolor{BurntOrange}{visitor} detailed to us.



 "You must know," said he, "that I am an \textcolor{red}{orphan} and a bachelor,

 residing alone in \textcolor{green}{lodgings} in London. By \textcolor{green}{profession} I am a

 hydraulic engineer, and I have had \textcolor{green}{considerable} experience of my

 work during the seven years that I was \textcolor{green}{apprenticed} to Venner &

 Matheson, the well-known firm, of Greenwich. Two years ago,

 having \textcolor{BurntOrange}{served} my \textcolor{blue}{time,} and having also come into a \textcolor{green}{fair} sum of

 \textcolor{BurntOrange}{money} through my poor \textcolor{green}{father's} \textcolor{BurntOrange}{death,} I determined to \textcolor{blue}{start} in

 business for myself and took \textcolor{green}{professional} chambers in Victoria

 Street.



 "I suppose that everyone finds his first independent \textcolor{blue}{start} in

 business a \textcolor{red}{dreary} experience. To me it has been exceptionally so.

 During two years I have had three consultations and one \textcolor{red}{small}

 \textcolor{green}{job,} and that is absolutely all that my \textcolor{green}{profession} has brought

 me. My \textcolor{red}{gross} takings amount to 27 \textcolor{red}{pounds} 10s. Every day, from

 nine in the morning until four in the afternoon, I \textcolor{BurntOrange}{waited} in my

 little den, until at last my heart began to sink, and I came to

 believe that I should never have any \textcolor{green}{practice} at all.



 "Yesterday, however, just as I was thinking of \textcolor{BurntOrange}{leaving} the

 office, my clerk entered to say there was a \textcolor{green}{gentleman} \textcolor{BurntOrange}{waiting} who

 wished to see me upon business. He brought up a card, too, with

 the name of \textcolor{green}{'Colonel} Lysander \textcolor{BurntOrange}{Stark'} engraved upon it. Close at

 his \textcolor{red}{heels} came the \textcolor{green}{colonel} himself, a man rather over the middle

 size, but of an \textcolor{BurntOrange}{exceeding} thinness. I do not think that I have

 ever seen so thin a man. His whole face \textcolor{BurntOrange}{sharpened} away into \textcolor{red}{nose}

 and chin, and the skin of his cheeks was drawn quite tense over

 his \textcolor{BurntOrange}{outstanding} bones. Yet this emaciation seemed to be his

 natural habit, and due to no \textcolor{red}{disease,} for his eye was bright, his

 step brisk, and his bearing \textcolor{green}{assured.} He was plainly but \textcolor{green}{neatly}

 dressed, and his age, I should judge, would be nearer forty than

 thirty.



 "'Mr. Hatherley?' said he, with something of a German accent.

 'You have been \textcolor{green}{recommended} to me, Mr. Hatherley, as being a man

 who is not only \textcolor{green}{proficient} in his \textcolor{green}{profession} but is also \textcolor{BurntOrange}{discreet}

 and capable of \textcolor{green}{preserving} a \textcolor{green}{secret.'}



 "I bowed, feeling as flattered as any \textcolor{BurntOrange}{young} man would at such an

 address. 'May I ask who it was who gave me so \textcolor{BurntOrange}{good} a character?'



 "'Well, perhaps it is better that I should not tell you that just

 at this moment. I have it from the same source that you are both

 an \textcolor{red}{orphan} and a bachelor and are residing alone in London.'



 "'That is quite correct,' I answered; 'but you will \textcolor{red}{excuse} me if

 I say that I cannot see how all this \textcolor{red}{bears} upon my \textcolor{green}{professional}

 qualifications. I understand that it was on a \textcolor{green}{professional} matter

 that you wished to speak to me?'



 "'Undoubtedly so. But you will find that all I say is really to

 the point. I have a \textcolor{green}{professional} \textcolor{green}{commission} for you, but \textcolor{green}{absolute}

 \textcolor{BurntOrange}{secrecy} is quite essential--absolute \textcolor{BurntOrange}{secrecy,} you understand, and

 of course we may \textcolor{BurntOrange}{expect} that more from a man who is alone than

 from one who lives in the bosom of his family.'



 "'If I \textcolor{green}{promise} to keep a \textcolor{green}{secret,'} said I, 'you may absolutely

 \textcolor{BurntOrange}{depend} upon my doing so.'



 "He looked very hard at me as I \textcolor{red}{spoke,} and it seemed to me that I

 had never seen so \textcolor{BurntOrange}{suspicious} and \textcolor{green}{questioning} an eye.



 "'Do you \textcolor{green}{promise,} then?' said he at last.



 "'Yes, I \textcolor{green}{promise.'}



 \textcolor{green}{"'Absolute} and complete silence before, during, and after? No

 reference to the matter at all, either in \textcolor{green}{word} or writing?'



 "'I have already given you my \textcolor{green}{word.'}



 "'Very \textcolor{BurntOrange}{good.'} He \textcolor{blue}{suddenly} sprang up, and \textcolor{red}{darting} like \textcolor{BurntOrange}{lightning}

 across the room he flung open the door. The passage outside was

 empty.



 "'That's all right,' said he, coming back. 'I know that clerks are

 sometimes curious as to their \textcolor{green}{master's} affairs. Now we can \textcolor{green}{talk}

 in safety.' He drew up his chair very close to mine and began to

 stare at me again with the same \textcolor{green}{questioning} and \textcolor{green}{thoughtful} look.



 "A feeling of \textcolor{red}{repulsion,} and of something \textcolor{green}{akin} to \textcolor{red}{fear} had begun

 to rise within me at the strange antics of this fleshless man.

 Even my \textcolor{BurntOrange}{dread} of \textcolor{BurntOrange}{losing} a client could not \textcolor{red}{restrain} me from

 \textcolor{green}{showing} my \textcolor{red}{impatience.}



 "'I \textcolor{red}{beg} that you will state your business, \textcolor{green}{sir,'} said I; 'my \textcolor{blue}{time}

 is of value.' Heaven \textcolor{green}{forgive} me for that last \textcolor{BurntOrange}{sentence,} but the

 \textcolor{green}{words} came to my lips.



 "'How would fifty guineas for a night's work suit you?' he asked.



 "'Most admirably.'



 "'I say a night's work, but an hour's would be nearer the mark. I

 simply want your opinion about a hydraulic stamping \textcolor{green}{machine} which

 has got out of \textcolor{green}{gear.} If you \textcolor{green}{show} us what is \textcolor{red}{wrong} we shall soon

 set it right ourselves. What do you think of such a \textcolor{green}{commission} as

 that?'



 "'The work appears to be light and the \textcolor{BurntOrange}{pay} munificent.'



 "'Precisely so. We shall want you to come to-night by the last

 train.'



 "'Where to?'



 "'To Eyford, in Berkshire. It is a little place near the borders

 of Oxfordshire, and within seven miles of \textcolor{green}{Reading.} There is a

 train from Paddington which would bring you there at about

 11:15.'



 "'Very \textcolor{BurntOrange}{good.'}



 "'I shall come down in a carriage to meet you.'



 "'There is a drive, then?'



 "'Yes, our little place is quite out in the country. It is a \textcolor{BurntOrange}{good}

 seven miles from Eyford Station.'



 "'Then we can hardly get there before midnight. I suppose there

 would be no \textcolor{blue}{chance} of a train back. I should be compelled to stop

 the night.'



 "'Yes, we could easily give you a shake-down.'



 "'That is very awkward. Could I not come at some more \textcolor{green}{convenient}

 hour?'



 "'We have judged it best that you should come \textcolor{red}{late.} It is to

 recompense you for any inconvenience that we are \textcolor{BurntOrange}{paying} to you, a

 \textcolor{BurntOrange}{young} and \textcolor{BurntOrange}{unknown} man, a \textcolor{red}{fee} which would buy an opinion from the

 very heads of your \textcolor{green}{profession.} Still, of course, if you would

 like to draw out of the business, there is plenty of \textcolor{blue}{time} to do

 so.'



 "I \textcolor{blue}{thought} of the fifty guineas, and of how very useful they

 would be to me. 'Not at all,' said I, 'I shall be very \textcolor{BurntOrange}{happy} to

 accommodate myself to your wishes. I should like, however, to

 understand a little more clearly what it is that you wish me to

 do.'



 "'Quite so. It is very natural that the \textcolor{green}{pledge} of \textcolor{BurntOrange}{secrecy} which

 we have exacted from you should have \textcolor{BurntOrange}{aroused} your \textcolor{BurntOrange}{curiosity.} I

 have no wish to commit you to anything without your having it all

 laid before you. I suppose that we are absolutely \textcolor{green}{safe} from

 eavesdroppers?'



 "'Entirely.'



 "'Then the matter stands thus. You are probably aware that

 fuller's-earth is a \textcolor{green}{valuable} product, and that it is only \textcolor{green}{found}

 in one or two places in England?'



 "'I have heard so.'



 "'Some little \textcolor{blue}{time} ago I bought a \textcolor{red}{small} place--a very \textcolor{red}{small}

 place--within ten miles of \textcolor{green}{Reading.} I was \textcolor{green}{fortunate} enough to

 discover that there was a deposit of fuller's-earth in one of my

 fields. On examining it, however, I \textcolor{green}{found} that this deposit was a

 comparatively \textcolor{red}{small} one, and that it formed a link between two

 very much larger ones upon the right and left--both of them,

 however, in the \textcolor{green}{grounds} of my neighbours. These \textcolor{BurntOrange}{good} people were

 absolutely \textcolor{red}{ignorant} that their \textcolor{green}{land} contained that which was

 quite as \textcolor{green}{valuable} as a gold-mine. Naturally, it was to my

 \textcolor{green}{interest} to buy their \textcolor{green}{land} before they discovered its \textcolor{green}{true} value,

 but unfortunately I had no capital by which I could do this. I

 took a few of my \textcolor{green}{friends} into the \textcolor{green}{secret,} however, and they

 \textcolor{green}{suggested} that we should quietly and secretly work our own little

 deposit and that in this way we should \textcolor{green}{earn} the \textcolor{BurntOrange}{money} which would

 \textcolor{green}{enable} us to buy the neighbouring fields. This we have now been

 doing for some \textcolor{blue}{time,} and in order to help us in our \textcolor{BurntOrange}{operations} we

 erected a hydraulic press. This press, as I have already

 \textcolor{green}{explained,} has got out of order, and we wish your \textcolor{green}{advice} upon the

 \textcolor{red}{subject.} We \textcolor{BurntOrange}{guard} our \textcolor{green}{secret} very jealously, however, and if it

 once became known that we had hydraulic engineers coming to our

 little house, it would soon rouse \textcolor{BurntOrange}{inquiry,} and then, if the \textcolor{green}{facts}

 came out, it would be good-bye to any \textcolor{blue}{chance} of getting these

 fields and carrying out our \textcolor{blue}{plans.} That is why I have made you

 \textcolor{green}{promise} me that you will not tell a human being that you are

 going to Eyford to-night. I \textcolor{BurntOrange}{hope} that I make it all plain?'



 "'I quite follow you,' said I. 'The only point which I could not

 quite understand was what use you could make of a hydraulic press

 in excavating fuller's-earth, which, as I understand, is dug out

 like gravel from a pit.'



 "'Ah!' said he carelessly, 'we have our own process. We \textcolor{red}{compress}

 the earth into bricks, so as to \textcolor{red}{remove} them without revealing

 what they are. But that is a mere detail. I have taken you \textcolor{green}{fully}

 into my \textcolor{BurntOrange}{confidence} now, Mr. Hatherley, and I have \textcolor{green}{shown} you how I

 \textcolor{green}{trust} you.' He rose as he \textcolor{red}{spoke.} 'I shall \textcolor{BurntOrange}{expect} you, then, at

 Eyford at 11:15.'



 "'I shall certainly be there.'



 "'And not a \textcolor{green}{word} to a soul.' He looked at me with a last \textcolor{blue}{long,}

 \textcolor{green}{questioning} gaze, and then, pressing my hand in a \textcolor{red}{cold,} \textcolor{red}{dank}

 grasp, he \textcolor{blue}{hurried} from the room.



 "Well, when I came to think it all over in \textcolor{green}{cool} blood I was very

 much astonished, as you may both think, at this \textcolor{blue}{sudden} \textcolor{green}{commission}

 which had been intrusted to me. On the one hand, of course, I was

 \textcolor{BurntOrange}{glad,} for the \textcolor{red}{fee} was at least tenfold what I should have asked

 had I set a price upon my own services, and it was possible that

 this order might \textcolor{green}{lead} to other ones. On the other hand, the face

 and manner of my \textcolor{green}{patron} had made an \textcolor{red}{unpleasant} \textcolor{green}{impression} upon

 me, and I could not think that his explanation of the

 fuller's-earth was sufficient to \textcolor{green}{explain} the \textcolor{red}{necessity} for my

 coming at midnight, and his extreme \textcolor{BurntOrange}{anxiety} lest I should tell

 anyone of my \textcolor{BurntOrange}{errand.} However, I threw all \textcolor{red}{fears} to the winds, ate

 a hearty supper, drove to Paddington, and \textcolor{blue}{started} off, having

 obeyed to the \textcolor{blue}{letter} the \textcolor{red}{injunction} as to holding my tongue.



 "At \textcolor{green}{Reading} I had to \textcolor{red}{change} not only my carriage but my station.

 However, I was in \textcolor{blue}{time} for the last train to Eyford, and I

 reached the little dim-lit station after eleven o'clock. I was the

 only \textcolor{blue}{passenger} who got out there, and there was no one upon the

 platform \textcolor{green}{save} a single sleepy porter with a lantern. As I passed

 out through the \textcolor{green}{wicket} \textcolor{green}{gate,} however, I \textcolor{green}{found} my acquaintance of

 the morning \textcolor{BurntOrange}{waiting} in the shadow upon the other side. Without a

 \textcolor{green}{word} he grasped my arm and \textcolor{blue}{hurried} me into a carriage, the door

 of which was standing open. He drew up the windows on either

 side, tapped on the wood-work, and away we went as fast as the

 \textcolor{green}{horse} could go."



 "One \textcolor{green}{horse?"} interjected Holmes.



 "Yes, only one."



 "Did you observe the colour?"



 "Yes, I saw it by the side-lights when I was stepping into the

 carriage. It was a chestnut."



 "Tired-looking or fresh?"



 "Oh, fresh and glossy."



 "Thank you. I am sorry to have \textcolor{BurntOrange}{interrupted} you. \textcolor{BurntOrange}{Pray} \textcolor{BurntOrange}{continue}

 your most \textcolor{green}{interesting} \textcolor{green}{statement."}



 "Away we went then, and we drove for at least an hour. \textcolor{green}{Colonel}

 Lysander \textcolor{BurntOrange}{Stark} had said that it was only seven miles, but I

 should think, from the rate that we seemed to go, and from the

 \textcolor{blue}{time} that we took, that it must have been nearer twelve. He sat

 at my side in silence all the \textcolor{blue}{time,} and I was aware, more than

 once when I glanced in his direction, that he was looking at me

 with great intensity. The country roads seem to be not very \textcolor{BurntOrange}{good}

 in that part of the world, for we \textcolor{red}{lurched} and \textcolor{blue}{jolted} \textcolor{red}{terribly.} I

 tried to look out of the windows to see something of where we

 were, but they were made of frosted glass, and I could make out

 nothing \textcolor{green}{save} the \textcolor{blue}{occasional} bright \textcolor{red}{blur} of a passing light. Now

 and then I \textcolor{red}{hazarded} some remark to \textcolor{blue}{break} the monotony of the

 \textcolor{BurntOrange}{journey,} but the \textcolor{green}{colonel} answered only in monosyllables, and the

 conversation soon flagged. At last, however, the bumping of the

 road was \textcolor{green}{exchanged} for the \textcolor{BurntOrange}{crisp} \textcolor{green}{smoothness} of a gravel-drive,

 and the carriage came to a stand. \textcolor{green}{Colonel} Lysander \textcolor{BurntOrange}{Stark} sprang

 out, and, as I followed after him, \textcolor{green}{pulled} me swiftly into a porch

 which gaped in front of us. We stepped, as it were, right out of

 the carriage and into the hall, so that I failed to \textcolor{blue}{catch} the

 most fleeting glance of the front of the house. The instant that

 I had \textcolor{red}{crossed} the threshold the door \textcolor{BurntOrange}{slammed} \textcolor{red}{heavily} behind us,

 and I heard faintly the rattle of the wheels as the carriage

 drove away.



 "It was pitch \textcolor{red}{dark} inside the house, and the \textcolor{green}{colonel} \textcolor{red}{fumbled}

 about looking for matches and \textcolor{red}{muttering} under his breath.

 \textcolor{blue}{Suddenly} a door opened at the other end of the passage, and a

 \textcolor{blue}{long,} golden bar of light \textcolor{BurntOrange}{shot} out in our direction. It \textcolor{BurntOrange}{grew}

 broader, and a woman appeared with a lamp in her hand, which she

 held above her head, pushing her face \textcolor{green}{forward} and peering at us.

 I could see that she was \textcolor{BurntOrange}{pretty,} and from the \textcolor{green}{gloss} with which

 the light shone upon her \textcolor{red}{dark} dress I knew that it was a rich

 material. She \textcolor{red}{spoke} a few \textcolor{green}{words} in a \textcolor{red}{foreign} tongue in a tone as

 though asking a \textcolor{green}{question,} and when my \textcolor{green}{companion} answered in a

 \textcolor{red}{gruff} monosyllable she gave such a \textcolor{blue}{start} that the lamp nearly

 \textcolor{red}{fell} from her hand. \textcolor{green}{Colonel} \textcolor{BurntOrange}{Stark} went up to her, whispered

 something in her ear, and then, pushing her back into the room

 from whence she had come, he walked towards me again with the

 lamp in his hand.



 "'Perhaps you will have the \textcolor{green}{kindness} to \textcolor{BurntOrange}{wait} in this room for a

 few minutes,' said he, throwing open another door. It was a

 \textcolor{BurntOrange}{quiet,} little, plainly furnished room, with a round table in the

 centre, on which several German books were scattered. \textcolor{green}{Colonel}

 \textcolor{BurntOrange}{Stark} laid down the lamp on the \textcolor{BurntOrange}{top} of a harmonium beside the

 door. 'I shall not keep you \textcolor{BurntOrange}{waiting} an instant,' said he, and

 \textcolor{BurntOrange}{vanished} into the \textcolor{red}{darkness.}



 "I glanced at the books upon the table, and in \textcolor{red}{spite} of my

 \textcolor{red}{ignorance} of German I could see that two of them were treatises

 on science, the others being volumes of poetry. Then I walked

 across to the window, hoping that I might \textcolor{blue}{catch} some glimpse of

 the country-side, but an \textcolor{green}{oak} shutter, \textcolor{red}{heavily} barred, was folded

 across it. It was a \textcolor{BurntOrange}{wonderfully} silent house. There was an old

 \textcolor{blue}{clock} ticking loudly somewhere in the passage, but otherwise

 everything was \textcolor{red}{deadly} still. A \textcolor{red}{vague} feeling of \textcolor{BurntOrange}{uneasiness} began

 to \textcolor{red}{steal} over me. Who were these German people, and what were

 they doing living in this strange, out-of-the-way place? And

 where was the place? I was ten miles or so from Eyford, that was

 all I knew, but whether north, south, east, or west I had no

 idea. For that matter, \textcolor{green}{Reading,} and possibly other large towns,

 were within that radius, so the place might not be so secluded,

 after all. Yet it was quite certain, from the \textcolor{green}{absolute} \textcolor{BurntOrange}{stillness,}

 that we were in the country. I paced up and down the room,

 humming a tune under my breath to keep up my \textcolor{green}{spirits} and feeling

 that I was thoroughly \textcolor{green}{earning} my fifty-guinea \textcolor{red}{fee.}



 \textcolor{blue}{"Suddenly,} without any \textcolor{blue}{preliminary} sound in the midst of the

 utter \textcolor{BurntOrange}{stillness,} the door of my room swung slowly open. The woman

 was standing in the aperture, the \textcolor{red}{darkness} of the hall behind

 her, the yellow light from my lamp \textcolor{red}{beating} upon her \textcolor{BurntOrange}{eager} and

 \textcolor{green}{beautiful} face. I could see at a glance that she was \textcolor{red}{sick} with

 \textcolor{red}{fear,} and the sight sent a chill to my own heart. She held up one

 shaking finger to \textcolor{BurntOrange}{warn} me to be silent, and she \textcolor{BurntOrange}{shot} a few

 whispered \textcolor{green}{words} of \textcolor{red}{broken} English at me, her eyes glancing back,

 like those of a \textcolor{BurntOrange}{frightened} \textcolor{green}{horse,} into the \textcolor{red}{gloom} behind her.



 "'I would go,' said she, trying hard, as it seemed to me, to

 speak calmly; 'I would go. I should not stay here. There is no

 \textcolor{BurntOrange}{good} for you to do.'



 "'But, madam,' said I, 'I have not yet done what I came for. I

 cannot possibly \textcolor{BurntOrange}{leave} until I have seen the \textcolor{green}{machine.'}



 "'It is not \textcolor{green}{worth} your while to \textcolor{BurntOrange}{wait,'} she went on. 'You can pass

 through the door; no one hinders.' And then, seeing that I \textcolor{BurntOrange}{smiled}

 and shook my head, she \textcolor{blue}{suddenly} threw aside her \textcolor{red}{constraint} and

 made a step \textcolor{green}{forward,} with her hands wrung together. 'For the \textcolor{green}{love}

 of Heaven!' she whispered, 'get away from here before it is too

 \textcolor{red}{late!'}



 "But I am somewhat headstrong by nature, and the more \textcolor{blue}{ready} to

 engage in an affair when there is some \textcolor{red}{obstacle} in the way. I

 \textcolor{blue}{thought} of my fifty-guinea \textcolor{red}{fee,} of my wearisome \textcolor{BurntOrange}{journey,} and of

 the \textcolor{red}{unpleasant} night which seemed to be before me. Was it all to

 go for nothing? Why should I \textcolor{red}{slink} away without having carried

 out my \textcolor{green}{commission,} and without the \textcolor{red}{payment} which was my due? This

 woman might, for all I knew, be a monomaniac. With a stout

 bearing, therefore, though her manner had shaken me more than I

 cared to \textcolor{BurntOrange}{confess,} I still shook my head and declared my intention

 of remaining where I was. She was about to renew her entreaties

 when a door \textcolor{BurntOrange}{slammed} overhead, and the sound of several footsteps

 was heard upon the stairs. She listened for an instant, threw up

 her hands with a \textcolor{red}{despairing} gesture, and \textcolor{BurntOrange}{vanished} as \textcolor{blue}{suddenly} and

 as noiselessly as she had come.



 "The \textcolor{BurntOrange}{newcomers} were \textcolor{green}{Colonel} Lysander \textcolor{BurntOrange}{Stark} and a short thick man

 with a chinchilla beard \textcolor{BurntOrange}{growing} out of the creases of his double

 chin, who was introduced to me as Mr. Ferguson.



 "'This is my secretary and manager,' said the \textcolor{green}{colonel.} 'By the

 way, I was under the \textcolor{green}{impression} that I left this door shut just

 now. I \textcolor{red}{fear} that you have felt the draught.'



 "'On the \textcolor{red}{contrary,'} said I, 'I opened the door myself because I

 felt the room to be a little close.'



 "He \textcolor{BurntOrange}{shot} one of his \textcolor{BurntOrange}{suspicious} looks at me. 'Perhaps we had

 better proceed to business, then,' said he. 'Mr. Ferguson and I

 will take you up to see the \textcolor{green}{machine.'}



 "'I had better put my hat on, I suppose.'



 "'Oh, no, it is in the house.'



 "'What, you dig fuller's-earth in the house?'



 "'No, no. This is only where we \textcolor{red}{compress} it. But never mind that.

 All we wish you to do is to examine the \textcolor{green}{machine} and to let us

 know what is \textcolor{red}{wrong} with it.'



 "We went upstairs together, the \textcolor{green}{colonel} first with the lamp, the

 \textcolor{red}{fat} manager and I behind him. It was a \textcolor{BurntOrange}{labyrinth} of an old house,

 with corridors, passages, narrow winding staircases, and little

 low doors, the thresholds of which were \textcolor{red}{hollowed} out by the

 generations who had \textcolor{red}{crossed} them. There were no carpets and no

 signs of any furniture above the \textcolor{green}{ground} floor, while the plaster

 was peeling off the walls, and the damp was \textcolor{blue}{breaking} through in

 \textcolor{green}{green,} \textcolor{red}{unhealthy} blotches. I tried to put on as unconcerned an

 air as possible, but I had not \textcolor{red}{forgotten} the \textcolor{red}{warnings} of the

 lady, even though I \textcolor{red}{disregarded} them, and I kept a keen eye upon

 my two \textcolor{green}{companions.} Ferguson appeared to be a morose and silent

 man, but I could see from the little that he said that he was at

 least a fellow-countryman.



 \textcolor{green}{"Colonel} Lysander \textcolor{BurntOrange}{Stark} stopped at last before a low door, which

 he unlocked. Within was a \textcolor{red}{small,} square room, in which the three

 of us could hardly get at one \textcolor{blue}{time.} Ferguson remained outside,

 and the \textcolor{green}{colonel} ushered me in.



 "'We are now,' said he, 'actually within the hydraulic press, and

 it would be a particularly \textcolor{red}{unpleasant} thing for us if anyone were

 to turn it on. The ceiling of this \textcolor{red}{small} chamber is really the

 end of the descending piston, and it comes down with the \textcolor{red}{force} of

 many tons upon this metal floor. There are \textcolor{red}{small} lateral columns

 of water outside which receive the \textcolor{red}{force,} and which transmit and

 multiply it in the manner which is \textcolor{green}{familiar} to you. The \textcolor{green}{machine}

 goes \textcolor{green}{readily} enough, but there is some \textcolor{red}{stiffness} in the working

 of it, and it has \textcolor{BurntOrange}{lost} a little of its \textcolor{red}{force.} Perhaps you will

 have the \textcolor{BurntOrange}{goodness} to look it over and to \textcolor{green}{show} us how we can set

 it right.'



 "I took the lamp from him, and I examined the \textcolor{green}{machine} very

 thoroughly. It was indeed a \textcolor{green}{gigantic} one, and capable of

 exercising enormous \textcolor{red}{pressure.} When I passed outside, however, and

 pressed down the levers which controlled it, I knew at once by

 the whishing sound that there was a slight \textcolor{red}{leakage,} which allowed

 a \textcolor{red}{regurgitation} of water through one of the side cylinders. An

 \textcolor{BurntOrange}{examination} \textcolor{green}{showed} that one of the india-rubber bands which was

 round the head of a driving-rod had \textcolor{red}{shrunk} so as not quite to

 \textcolor{green}{fill} the socket along which it worked. This was clearly the cause

 of the \textcolor{red}{loss} of power, and I pointed it out to my \textcolor{green}{companions,} who

 followed my remarks very \textcolor{green}{carefully} and asked several practical

 \textcolor{green}{questions} as to how they should proceed to set it right. When I

 had made it clear to them, I returned to the \textcolor{green}{main} chamber of the

 \textcolor{green}{machine} and took a \textcolor{BurntOrange}{good} look at it to satisfy my own \textcolor{BurntOrange}{curiosity.}

 It was \textcolor{green}{obvious} at a glance that the story of the fuller's-earth

 was the merest \textcolor{BurntOrange}{fabrication,} for it would be \textcolor{red}{absurd} to suppose

 that so \textcolor{BurntOrange}{powerful} an engine could be designed for so \textcolor{red}{inadequate} a

 purpose. The walls were of wood, but the floor consisted of a

 large \textcolor{green}{iron} trough, and when I came to examine it I could see a

 crust of metallic deposit all over it. I had stooped and was

 scraping at this to see exactly what it was when I heard a

 \textcolor{red}{muttered} exclamation in German and saw the cadaverous face of the

 \textcolor{green}{colonel} looking down at me.



 "'What are you doing there?' he asked.



 "I felt \textcolor{red}{angry} at having been tricked by so elaborate a story as

 that which he had told me. 'I was \textcolor{green}{admiring} your fuller's-earth,'

 said I; 'I think that I should be better able to \textcolor{green}{advise} you as to

 your \textcolor{green}{machine} if I knew what the exact purpose was for which it

 was used.'



 "The instant that I uttered the \textcolor{green}{words} I \textcolor{red}{regretted} the rashness of

 my \textcolor{green}{speech.} His face set hard, and a baleful light sprang up in

 his grey eyes.



 "'Very well,' said he, 'you shall know all about the \textcolor{green}{machine.'} He

 took a step \textcolor{red}{backward,} \textcolor{BurntOrange}{slammed} the little door, and turned the key

 in the lock. I rushed towards it and \textcolor{green}{pulled} at the handle, but it

 was quite secure, and did not give in the least to my \textcolor{red}{kicks} and

 \textcolor{red}{shoves.} 'Hullo!' I \textcolor{BurntOrange}{yelled.} 'Hullo! \textcolor{green}{Colonel!} Let me out!'



 "And then \textcolor{blue}{suddenly} in the silence I heard a sound which sent my

 heart into my \textcolor{blue}{mouth.} It was the clank of the levers and the swish

 of the \textcolor{red}{leaking} cylinder. He had set the engine at work. The lamp

 still stood upon the floor where I had placed it when examining

 the trough. By its light I saw that the \textcolor{red}{black} ceiling was coming

 down upon me, slowly, jerkily, but, as none knew better than

 myself, with a \textcolor{red}{force} which must within a minute grind me to a

 shapeless pulp. I threw myself, \textcolor{BurntOrange}{screaming,} against the door, and

 dragged with my nails at the lock. I implored the \textcolor{green}{colonel} to let

 me out, but the remorseless clanking of the levers \textcolor{red}{drowned} my

 \textcolor{red}{cries.} The ceiling was only a foot or two above my head, and with

 my hand upraised I could feel its hard, rough surface. Then it

 flashed through my mind that the \textcolor{red}{pain} of my \textcolor{BurntOrange}{death} would \textcolor{BurntOrange}{depend}

 very much upon the position in which I met it. If I lay on my

 face the \textcolor{BurntOrange}{weight} would come upon my \textcolor{BurntOrange}{spine,} and I \textcolor{red}{shuddered} to

 think of that \textcolor{BurntOrange}{dreadful} snap. Easier the other way, perhaps; and

 yet, had I the \textcolor{green}{nerve} to \textcolor{red}{lie} and look up at that \textcolor{red}{deadly} \textcolor{red}{black}

 shadow \textcolor{red}{wavering} down upon me? Already I was \textcolor{red}{unable} to stand

 erect, when my eye caught something which brought a \textcolor{BurntOrange}{gush} of \textcolor{BurntOrange}{hope}

 back to my heart.



 "I have said that though the floor and ceiling were of \textcolor{green}{iron,} the

 walls were of wood. As I gave a last \textcolor{blue}{hurried} glance around, I saw

 a thin line of yellow light between two of the \textcolor{blue}{boards,} which

 broadened and broadened as a \textcolor{red}{small} panel was pushed \textcolor{red}{backward.} For

 an instant I could hardly believe that here was indeed a door

 which \textcolor{green}{led} away from \textcolor{BurntOrange}{death.} The next instant I threw myself

 through, and lay half-fainting upon the other side. The panel had

 closed again behind me, but the \textcolor{BurntOrange}{crash} of the lamp, and a few

 moments afterwards the clang of the two slabs of metal, told me

 how narrow had been my \textcolor{BurntOrange}{escape.}



 "I was recalled to myself by a \textcolor{BurntOrange}{frantic} plucking at my wrist, and

 I \textcolor{green}{found} myself \textcolor{red}{lying} upon the \textcolor{red}{stone} floor of a narrow corridor,

 while a woman bent over me and tugged at me with her left hand,

 while she held a candle in her right. It was the same \textcolor{BurntOrange}{good} \textcolor{green}{friend}

 whose \textcolor{BurntOrange}{warning} I had so foolishly \textcolor{red}{rejected.}



 "'Come! come!' she \textcolor{red}{cried} breathlessly. 'They will be here in a

 moment. They will see that you are not there. Oh, do not \textcolor{red}{waste}

 the so-precious \textcolor{blue}{time,} but come!'



 "This \textcolor{blue}{time,} at least, I did not \textcolor{red}{scorn} her \textcolor{green}{advice.} I \textcolor{blue}{staggered} to

 my feet and ran with her along the corridor and down a winding

 stair. The latter \textcolor{green}{led} to another broad passage, and just as we

 reached it we heard the sound of running feet and the \textcolor{BurntOrange}{shouting} of

 two voices, one answering the other from the floor on which we

 were and from the one beneath. My \textcolor{green}{guide} stopped and looked about

 her like one who is at her \textcolor{green}{wit's} end. Then she threw open a door

 which \textcolor{green}{led} into a bedroom, through the window of which the moon

 was shining brightly.



 "'It is your only \textcolor{blue}{chance,'} said she. 'It is high, but it may be

 that you can \textcolor{green}{jump} it.'



 "As she \textcolor{red}{spoke} a light sprang into view at the further end of the

 passage, and I saw the lean figure of \textcolor{green}{Colonel} Lysander \textcolor{BurntOrange}{Stark}

 rushing \textcolor{green}{forward} with a lantern in one hand and a weapon like a

 \textcolor{red}{butcher's} cleaver in the other. I rushed across the bedroom,

 flung open the window, and looked out. How \textcolor{BurntOrange}{quiet} and \textcolor{BurntOrange}{sweet} and

 \textcolor{green}{wholesome} the \textcolor{green}{garden} looked in the moonlight, and it could not be

 more than thirty feet down. I clambered out upon the sill, but I

 hesitated to \textcolor{green}{jump} until I should have heard what passed between

 my saviour and the ruffian who pursued me. If she were ill-used,

 then at any \textcolor{BurntOrange}{risks} I was determined to go back to her \textcolor{green}{assistance.}

 The \textcolor{blue}{thought} had hardly flashed through my mind before he was at

 the door, pushing his way past her; but she threw her arms round

 him and tried to hold him back.



 "'Fritz! Fritz!' she \textcolor{red}{cried} in English, 'remember your \textcolor{green}{promise}

 after the last \textcolor{blue}{time.} You said it should not be again. He will be

 silent! Oh, he will be silent!'



 "'You are \textcolor{red}{mad,} Elise!' he \textcolor{BurntOrange}{shouted,} \textcolor{red}{struggling} to \textcolor{blue}{break} away from

 her. 'You will be the \textcolor{red}{ruin} of us. He has seen too much. Let me

 pass, I say!' He dashed her to one side, and, rushing to the

 window, cut at me with his heavy weapon. I had let myself go, and

 was hanging by the hands to the sill, when his blow \textcolor{red}{fell.} I was

 conscious of a \textcolor{red}{dull} \textcolor{red}{pain,} my grip loosened, and I \textcolor{red}{fell} into the

 \textcolor{green}{garden} below.



 "I was shaken but not \textcolor{red}{hurt} by the \textcolor{red}{fall;} so I picked myself up and

 rushed off among the bushes as hard as I could run, for I

 understood that I was far from being out of \textcolor{red}{danger} yet. \textcolor{blue}{Suddenly,}

 however, as I ran, a \textcolor{red}{deadly} \textcolor{red}{dizziness} and \textcolor{red}{sickness} came over me.

 I glanced down at my hand, which was \textcolor{red}{throbbing} \textcolor{red}{painfully,} and

 then, for the first \textcolor{blue}{time,} saw that my thumb had been cut off and

 that the blood was pouring from my \textcolor{red}{wound.} I endeavoured to tie my

 handkerchief round it, but there came a \textcolor{blue}{sudden} buzzing in my

 ears, and next moment I \textcolor{red}{fell} in a dead faint among the

 rose-bushes.



 "How \textcolor{blue}{long} I remained \textcolor{red}{unconscious} I cannot tell. It must have been

 a very \textcolor{blue}{long} \textcolor{blue}{time,} for the moon had \textcolor{red}{sunk,} and a bright morning was

 \textcolor{blue}{breaking} when I came to myself. My clothes were all sodden with

 dew, and my coat-sleeve was drenched with blood from my \textcolor{red}{wounded}

 thumb. The smarting of it recalled in an instant all the

 particulars of my night's \textcolor{BurntOrange}{adventure,} and I sprang to my feet with

 the feeling that I might hardly yet be \textcolor{green}{safe} from my pursuers. But

 to my \textcolor{BurntOrange}{astonishment,} when I came to look round me, neither house

 nor \textcolor{green}{garden} were to be seen. I had been \textcolor{red}{lying} in an angle of the

 hedge close by the highroad, and just a little lower down was a

 \textcolor{blue}{long} \textcolor{green}{building,} which \textcolor{green}{proved,} upon my approaching it, to be the

 very station at which I had \textcolor{blue}{arrived} upon the previous night. Were

 it not for the \textcolor{red}{ugly} \textcolor{red}{wound} upon my hand, all that had passed

 during those \textcolor{BurntOrange}{dreadful} hours might have been an \textcolor{red}{evil} dream.



 "Half dazed, I went into the station and asked about the morning

 train. There would be one to \textcolor{green}{Reading} in less than an hour. The

 same porter was on duty, I \textcolor{green}{found,} as had been there when I

 \textcolor{blue}{arrived.} I inquired of him whether he had ever heard of \textcolor{green}{Colonel}

 Lysander \textcolor{BurntOrange}{Stark.} The name was strange to him. Had he observed a

 carriage the night before \textcolor{BurntOrange}{waiting} for me? No, he had not. Was

 there a police-station anywhere near? There was one about three

 miles off.



 "It was too far for me to go, weak and \textcolor{red}{ill} as I was. I determined

 to \textcolor{BurntOrange}{wait} until I got back to town before telling my story to the

 \textcolor{BurntOrange}{police.} It was a little past six when I \textcolor{blue}{arrived,} so I went first

 to have my \textcolor{red}{wound} dressed, and then the \textcolor{green}{doctor} was \textcolor{green}{kind} enough to

 bring me along here. I put the \textcolor{red}{case} into your hands and shall do

 exactly what you \textcolor{green}{advise."}



 We both sat in silence for some little \textcolor{blue}{time} after listening to

 this \textcolor{green}{extraordinary} narrative. Then Sherlock Holmes \textcolor{green}{pulled} down

 from the shelf one of the \textcolor{red}{ponderous} \textcolor{BurntOrange}{commonplace} books in which he

 placed his \textcolor{red}{cuttings.}



 "Here is an advertisement which will \textcolor{green}{interest} you," said he. "It

 appeared in all the papers about a year ago. Listen to this:

 \textcolor{BurntOrange}{'Lost,} on the 9th inst., Mr. Jeremiah Hayling, aged

 twenty-six, a hydraulic engineer. Left his \textcolor{green}{lodgings} at ten

 o'clock at night, and has not been heard of since. Was

 dressed in,' etc., etc. Ha! That represents the last \textcolor{blue}{time} that

 the \textcolor{green}{colonel} needed to have his \textcolor{green}{machine} overhauled, I \textcolor{BurntOrange}{fancy."}



 \textcolor{BurntOrange}{"Good} heavens!" \textcolor{red}{cried} my \textcolor{BurntOrange}{patient.} "Then that explains what the

 girl said."



 "Undoubtedly. It is quite clear that the \textcolor{green}{colonel} was a \textcolor{green}{cool} and

 \textcolor{red}{desperate} man, who was absolutely determined that nothing should

 stand in the way of his little game, like those out-and-out

 \textcolor{red}{pirates} who will \textcolor{BurntOrange}{leave} no survivor from a \textcolor{red}{captured} \textcolor{blue}{ship.} Well,

 every moment now is \textcolor{BurntOrange}{precious,} so if you feel equal to it we shall

 go down to Scotland Yard at once as a \textcolor{blue}{preliminary} to \textcolor{blue}{starting} for

 Eyford."



 Some three hours or so afterwards we were all in the train

 together, \textcolor{red}{bound} from \textcolor{green}{Reading} to the little Berkshire village.

 There were Sherlock Holmes, the hydraulic engineer, \textcolor{green}{Inspector}

 Bradstreet, of Scotland Yard, a plain-clothes man, and myself.

 Bradstreet had spread an \textcolor{red}{ordnance} map of the \textcolor{green}{county} out upon the

 seat and was busy with his \textcolor{green}{compasses} drawing a circle with Eyford

 for its centre.



 "There you are," said he. "That circle is drawn at a radius of

 ten miles from the village. The place we want must be somewhere

 near that line. You said ten miles, I think, \textcolor{green}{sir."}



 "It was an hour's \textcolor{BurntOrange}{good} drive."



 "And you think that they brought you back all that way when you

 were \textcolor{red}{unconscious?"}



 "They must have done so. I have a \textcolor{red}{confused} memory, too, of having

 been lifted and conveyed somewhere."



 "What I cannot understand," said I, "is why they should have

 spared you when they \textcolor{green}{found} you \textcolor{red}{lying} \textcolor{BurntOrange}{fainting} in the \textcolor{green}{garden.}

 Perhaps the \textcolor{red}{villain} was softened by the woman's entreaties."



 "I hardly think that likely. I never saw a more inexorable face

 in my life."



 "Oh, we shall soon clear up all that," said Bradstreet. "Well, I

 have drawn my circle, and I only wish I knew at what point upon

 it the folk that we are in search of are to be \textcolor{green}{found."}



 "I think I could lay my finger on it," said Holmes quietly.



 "Really, now!" \textcolor{red}{cried} the \textcolor{green}{inspector,} "you have formed your

 opinion! Come, now, we shall see who agrees with you. I say it is

 south, for the country is more \textcolor{red}{deserted} there."



 "And I say east," said my \textcolor{BurntOrange}{patient.}



 "I am for west," remarked the plain-clothes man. "There are

 several \textcolor{BurntOrange}{quiet} little villages up there."



 "And I am for north," said I, "because there are no hills there,

 and our \textcolor{green}{friend} says that he did not notice the carriage go up

 any."



 "Come," \textcolor{red}{cried} the \textcolor{green}{inspector,} \textcolor{BurntOrange}{laughing;} "it's a very \textcolor{BurntOrange}{pretty}

 diversity of opinion. We have boxed the \textcolor{green}{compass} among us. Who do

 you give your casting \textcolor{BurntOrange}{vote} to?"



 "You are all \textcolor{red}{wrong."}



 "But we can't all be."



 "Oh, yes, you can. This is my point." He placed his finger in the

 centre of the circle. "This is where we shall find them."



 "But the twelve-mile drive?" gasped Hatherley.



 "Six out and six back. Nothing simpler. You say yourself that the

 \textcolor{green}{horse} was fresh and glossy when you got in. How could it be that

 if it had gone twelve miles over heavy roads?"



 "Indeed, it is a likely \textcolor{red}{ruse} enough," observed Bradstreet

 thoughtfully. "Of course there can be no \textcolor{BurntOrange}{doubt} as to the nature

 of this \textcolor{red}{gang."}



 "None at all," said Holmes. "They are coiners on a large scale,

 and have used the \textcolor{green}{machine} to form the amalgam which has taken the

 place of silver."



 "We have known for some \textcolor{blue}{time} that a \textcolor{green}{clever} \textcolor{red}{gang} was at work,"

 said the \textcolor{green}{inspector.} "They have been turning out half-crowns by

 the thousand. We even traced them as far as \textcolor{green}{Reading,} but could

 get no farther, for they had \textcolor{green}{covered} their traces in a way that

 \textcolor{green}{showed} that they were very old hands. But now, thanks to this

 \textcolor{BurntOrange}{lucky} \textcolor{blue}{chance,} I think that we have got them right enough."



 But the \textcolor{green}{inspector} was \textcolor{red}{mistaken,} for those \textcolor{red}{criminals} were not

 destined to \textcolor{red}{fall} into the hands of \textcolor{green}{justice.} As we rolled into

 Eyford Station we saw a \textcolor{green}{gigantic} column of smoke which streamed

 up from behind a \textcolor{red}{small} \textcolor{red}{clump} of \textcolor{BurntOrange}{trees} in the neighbourhood and

 hung like an \textcolor{green}{immense} ostrich feather over the landscape.



 "A house on \textcolor{red}{fire?"} asked Bradstreet as the train steamed off

 again on its way.



 "Yes, \textcolor{green}{sir!"} said the station-master.



 "When did it \textcolor{blue}{break} out?"



 "I hear that it was during the night, \textcolor{green}{sir,} but it has got \textcolor{red}{worse,}

 and the whole place is in a \textcolor{red}{blaze."}



 "Whose house is it?"



 "Dr. Becher's."



 "Tell me," \textcolor{red}{broke} in the engineer, "is Dr. Becher a German, very

 thin, with a \textcolor{blue}{long,} sharp \textcolor{red}{nose?"}



 The station-master \textcolor{BurntOrange}{laughed} \textcolor{green}{heartily.} "No, \textcolor{green}{sir,} Dr. Becher is an

 Englishman, and there isn't a man in the \textcolor{green}{parish} who has a

 better-lined waistcoat. But he has a \textcolor{green}{gentleman} staying with him,

 a \textcolor{BurntOrange}{patient,} as I understand, who is a \textcolor{red}{foreigner,} and he looks as

 if a little \textcolor{BurntOrange}{good} Berkshire beef would do him no \textcolor{red}{harm."}



 The station-master had not finished his \textcolor{green}{speech} before we were all

 hastening in the direction of the \textcolor{red}{fire.} The road topped a low

 hill, and there was a great \textcolor{green}{widespread} whitewashed \textcolor{green}{building} in

 front of us, spouting \textcolor{red}{fire} at every chink and window, while in

 the \textcolor{green}{garden} in front three fire-engines were \textcolor{red}{vainly} \textcolor{blue}{striving} to

 keep the flames under.



 "That's it!" \textcolor{red}{cried} Hatherley, in \textcolor{BurntOrange}{intense} \textcolor{BurntOrange}{excitement.} "There is

 the gravel-drive, and there are the rose-bushes where I lay. That

 second window is the one that I jumped from."



 "Well, at least," said Holmes, "you have had your \textcolor{BurntOrange}{revenge} upon

 them. There can be no \textcolor{green}{question} that it was your oil-lamp which,

 when it was crushed in the press, set \textcolor{red}{fire} to the wooden walls,

 though no \textcolor{BurntOrange}{doubt} they were too \textcolor{BurntOrange}{excited} in the \textcolor{red}{chase} after you to

 observe it at the \textcolor{blue}{time.} Now keep your eyes open in this crowd for

 your \textcolor{green}{friends} of last night, though I very much \textcolor{red}{fear} that they are

 a \textcolor{BurntOrange}{good} hundred miles off by now."



 And Holmes' \textcolor{red}{fears} came to be realised, for from that day to this

 no \textcolor{green}{word} has ever been heard either of the \textcolor{green}{beautiful} woman, the

 \textcolor{red}{sinister} German, or the morose Englishman. Early that morning a

 peasant had met a cart containing several people and some very

 bulky boxes driving rapidly in the direction of \textcolor{green}{Reading,} but

 there all traces of the \textcolor{BurntOrange}{fugitives} \textcolor{red}{disappeared,} and even Holmes'

 ingenuity failed ever to discover the least \textcolor{blue}{clue} as to their

 whereabouts.



 The \textcolor{green}{firemen} had been much perturbed at the strange arrangements

 which they had \textcolor{green}{found} within, and still more so by discovering a

 newly \textcolor{red}{severed} human thumb upon a window-sill of the second floor.

 About \textcolor{BurntOrange}{sunset,} however, their \textcolor{green}{efforts} were at last \textcolor{BurntOrange}{successful,} and

 they \textcolor{red}{subdued} the flames, but not before the roof had \textcolor{red}{fallen} in,

 and the whole place been reduced to such \textcolor{green}{absolute} \textcolor{red}{ruin} that, \textcolor{green}{save}

 some twisted cylinders and \textcolor{green}{iron} piping, not a trace remained of

 the machinery which had cost our \textcolor{red}{unfortunate} acquaintance so

 dearly. Large masses of nickel and of tin were discovered \textcolor{BurntOrange}{stored}

 in an \textcolor{red}{out-house,} but no coins were to be \textcolor{green}{found,} which may have

 \textcolor{green}{explained} the \textcolor{green}{presence} of those bulky boxes which have been

 already referred to.



 How our hydraulic engineer had been conveyed from the \textcolor{green}{garden} to

 the spot where he recovered his senses might have remained

 forever a \textcolor{blue}{mystery} were it not for the soft mould, which told us a

 very plain \textcolor{green}{tale.} He had evidently been carried down by two

 persons, one of whom had \textcolor{green}{remarkably} \textcolor{red}{small} feet and the other

 unusually large ones. On the whole, it was most probable that the

 silent Englishman, being less \textcolor{green}{bold} or less \textcolor{BurntOrange}{murderous} than his

 \textcolor{green}{companion,} had \textcolor{green}{assisted} the woman to \textcolor{red}{bear} the \textcolor{red}{unconscious} man out

 of the way of \textcolor{red}{danger.}



 "Well," said our engineer ruefully as we took our seats to return

 once more to London, "it has been a \textcolor{BurntOrange}{pretty} business for me! I

 have \textcolor{BurntOrange}{lost} my thumb and I have \textcolor{BurntOrange}{lost} a fifty-guinea \textcolor{red}{fee,} and what

 have I \textcolor{BurntOrange}{gained?"}



 "Experience," said Holmes, \textcolor{BurntOrange}{laughing.} "Indirectly it may be of

 value, you know; you have only to put it into \textcolor{green}{words} to \textcolor{BurntOrange}{gain} the

 reputation of being \textcolor{green}{excellent} company for the remainder of your

 \textcolor{green}{existence."}







 X. THE \textcolor{BurntOrange}{ADVENTURE} OF THE \textcolor{green}{NOBLE} BACHELOR



 The \textcolor{BurntOrange}{Lord} St. Simon \textcolor{BurntOrange}{marriage,} and its curious \textcolor{red}{termination,} have

 \textcolor{blue}{long} ceased to be a \textcolor{red}{subject} of \textcolor{green}{interest} in those \textcolor{BurntOrange}{exalted} circles

 in which the \textcolor{red}{unfortunate} \textcolor{BurntOrange}{bridegroom} moves. Fresh \textcolor{red}{scandals} have

 eclipsed it, and their more piquant details have drawn the

 \textcolor{red}{gossips} away from this four-year-old drama. As I have \textcolor{green}{reason} to

 believe, however, that the \textcolor{green}{full} \textcolor{green}{facts} have never been revealed to

 the \textcolor{green}{general} \textcolor{BurntOrange}{public,} and as my \textcolor{green}{friend} Sherlock Holmes had a

 \textcolor{green}{considerable} \textcolor{BurntOrange}{share} in clearing the matter up, I feel that no

 memoir of him would be complete without some little sketch of

 this \textcolor{BurntOrange}{remarkable} episode.



 It was a few weeks before my own \textcolor{BurntOrange}{marriage,} during the days when I

 was still \textcolor{BurntOrange}{sharing} rooms with Holmes in Baker Street, that he came

 home from an afternoon stroll to find a \textcolor{blue}{letter} on the table

 \textcolor{BurntOrange}{waiting} for him. I had remained indoors all day, for the weather

 had taken a \textcolor{blue}{sudden} turn to rain, with high autumnal winds, and

 the Jezail bullet which I had brought back in one of my limbs as

 a relic of my Afghan campaign throbbed with \textcolor{red}{dull} \textcolor{green}{persistence.}

 With my body in one easy-chair and my legs upon another, I had

 \textcolor{BurntOrange}{surrounded} myself with a cloud of newspapers until at last,

 saturated with the news of the day, I tossed them all aside and

 lay \textcolor{red}{listless,} \textcolor{BurntOrange}{watching} the huge crest and monogram upon the

 envelope upon the table and wondering lazily who my \textcolor{green}{friend's}

 \textcolor{green}{noble} correspondent could be.



 "Here is a very \textcolor{green}{fashionable} epistle," I remarked as he entered.

 "Your morning \textcolor{blue}{letters,} if I remember right, were from a

 fish-monger and a tide-waiter."



 "Yes, my \textcolor{BurntOrange}{correspondence} has certainly the \textcolor{green}{charm} of variety," he

 answered, \textcolor{BurntOrange}{smiling,} "and the humbler are usually the more

 \textcolor{green}{interesting.} This looks like one of those \textcolor{red}{unwelcome} social

 \textcolor{red}{summonses} which call upon a man either to be \textcolor{red}{bored} or to \textcolor{red}{lie."}



 He \textcolor{red}{broke} the \textcolor{green}{seal} and glanced over the \textcolor{green}{contents.}



 "Oh, come, it may \textcolor{green}{prove} to be something of \textcolor{green}{interest,} after all."



 "Not social, then?"



 "No, distinctly \textcolor{green}{professional."}



 "And from a \textcolor{green}{noble} client?"



 "One of the highest in England."



 "My \textcolor{green}{dear} \textcolor{green}{fellow,} I congratulate you."



 "I \textcolor{green}{assure} you, Watson, without affectation, that the \textcolor{green}{status} of my

 client is a matter of less moment to me than the \textcolor{green}{interest} of his

 \textcolor{red}{case.} It is just possible, however, that that also may not be

 wanting in this new \textcolor{blue}{investigation.} You have been \textcolor{green}{reading} the

 papers diligently of \textcolor{red}{late,} have you not?"



 "It looks like it," said I ruefully, pointing to a huge bundle in

 the corner. "I have had nothing else to do."



 "It is \textcolor{green}{fortunate,} for you will perhaps be able to post me up. I

 read nothing except the \textcolor{red}{criminal} news and the \textcolor{red}{agony} column. The

 latter is always instructive. But if you have followed recent

 events so closely you must have read about \textcolor{BurntOrange}{Lord} St. Simon and his

 wedding?"



 "Oh, yes, with the deepest \textcolor{green}{interest."}



 "That is well. The \textcolor{blue}{letter} which I hold in my hand is from \textcolor{BurntOrange}{Lord}

 St. Simon. I will read it to you, and in return you must turn

 over these papers and let me have whatever \textcolor{red}{bears} upon the matter.

 This is what he says:



 "'MY \textcolor{green}{DEAR} MR. SHERLOCK HOLMES:--Lord \textcolor{red}{Backwater} tells me that I

 may place implicit \textcolor{green}{reliance} upon your \textcolor{blue}{judgment} and \textcolor{BurntOrange}{discretion.} I

 have determined, therefore, to call upon you and to \textcolor{green}{consult} you

 in reference to the very \textcolor{red}{painful} event which has occurred in

 connection with my wedding. Mr. Lestrade, of Scotland Yard, is

 acting already in the matter, but he assures me that he sees no

 \textcolor{red}{objection} to your \textcolor{green}{co-operation,} and that he even thinks that

 it might be of some \textcolor{green}{assistance.} I will call at four o'clock in

 the afternoon, and, should you have any other engagement at that

 \textcolor{blue}{time,} I \textcolor{BurntOrange}{hope} that you will postpone it, as this matter is of

 \textcolor{green}{paramount} \textcolor{BurntOrange}{importance.} Yours faithfully, ST. SIMON.'



 "It is dated from Grosvenor Mansions, written with a quill pen,

 and the \textcolor{green}{noble} \textcolor{BurntOrange}{lord} has had the \textcolor{red}{misfortune} to get a smear of ink

 upon the outer side of his right little finger," remarked Holmes

 as he folded up the epistle.



 "He says four o'clock. It is three now. He will be here in an

 hour."



 "Then I have just \textcolor{blue}{time,} with your \textcolor{green}{assistance,} to get clear upon

 the \textcolor{red}{subject.} Turn over those papers and arrange the extracts in

 their order of \textcolor{blue}{time,} while I take a glance as to who our client

 is." He picked a red-covered volume from a line of books of

 reference beside the mantelpiece. "Here he is," said he, sitting

 down and flattening it out upon his knee. \textcolor{BurntOrange}{"'Lord} Robert Walsingham

 de Vere St. Simon, second son of the \textcolor{green}{Duke} of Balmoral.' Hum! 'Arms:

 Azure, three caltrops in chief over a fess sable. Born in 1846.'

 He's forty-one years of age, which is mature for \textcolor{BurntOrange}{marriage.} Was

 Under-Secretary for the colonies in a \textcolor{red}{late} administration. The

 \textcolor{green}{Duke,} his \textcolor{green}{father,} was at one \textcolor{blue}{time} Secretary for \textcolor{red}{Foreign} Affairs.

 They inherit Plantagenet blood by direct \textcolor{red}{descent,} and Tudor on

 the distaff side. Ha! Well, there is nothing very instructive in

 all this. I think that I must turn to you Watson, for something

 more \textcolor{green}{solid."}



 "I have very little \textcolor{red}{difficulty} in finding what I want," said I,

 "for the \textcolor{green}{facts} are quite recent, and the matter struck me as

 \textcolor{BurntOrange}{remarkable.} I \textcolor{red}{feared} to refer them to you, however, as I knew

 that you had an \textcolor{BurntOrange}{inquiry} on hand and that you \textcolor{red}{disliked} the

 \textcolor{red}{intrusion} of other matters."



 "Oh, you mean the little \textcolor{red}{problem} of the Grosvenor Square

 furniture van. That is quite cleared up now--though, indeed, it

 was \textcolor{green}{obvious} from the first. \textcolor{BurntOrange}{Pray} give me the \textcolor{blue}{results} of your

 newspaper selections."



 "Here is the first notice which I can find. It is in the \textcolor{green}{personal}

 column of the Morning Post, and dates, as you see, some weeks

 back: 'A \textcolor{BurntOrange}{marriage} has been arranged,' it says, 'and will, if

 rumour is correct, very \textcolor{blue}{shortly} take place, between \textcolor{BurntOrange}{Lord} Robert

 St. Simon, second son of the \textcolor{green}{Duke} of Balmoral, and Miss Hatty

 Doran, the only \textcolor{green}{daughter} of Aloysius Doran. Esq., of San

 Francisco, Cal., U.S.A.' That is all."



 "Terse and to the point," remarked Holmes, stretching his \textcolor{blue}{long,}

 thin legs towards the \textcolor{red}{fire.}



 "There was a paragraph amplifying this in one of the society

 papers of the same week. Ah, here it is: 'There will soon be a

 call for protection in the \textcolor{BurntOrange}{marriage} market, for the \textcolor{BurntOrange}{present}

 free-trade principle appears to tell \textcolor{red}{heavily} against our home

 product. One by one the \textcolor{green}{management} of the \textcolor{green}{noble} houses of Great

 Britain is passing into the hands of our \textcolor{green}{fair} cousins from across

 the Atlantic. An \textcolor{green}{important} addition has been made during the last

 week to the list of the prizes which have been borne away by

 these \textcolor{green}{charming} \textcolor{red}{invaders.} \textcolor{BurntOrange}{Lord} St. Simon, who has \textcolor{green}{shown} himself

 for over twenty years \textcolor{green}{proof} against the little \textcolor{BurntOrange}{god's} arrows, has

 now definitely announced his approaching \textcolor{BurntOrange}{marriage} with Miss Hatty

 Doran, the fascinating \textcolor{green}{daughter} of a California millionaire. Miss

 Doran, whose \textcolor{green}{graceful} figure and \textcolor{red}{striking} face attracted much

 \textcolor{green}{attention} at the Westbury House festivities, is an only \textcolor{BurntOrange}{child,}

 and it is currently reported that her dowry will run to

 considerably over the six figures, with \textcolor{blue}{expectancies} for the

 future. As it is an open \textcolor{green}{secret} that the \textcolor{green}{Duke} of Balmoral has

 been compelled to sell his pictures within the last few years,

 and as \textcolor{BurntOrange}{Lord} St. Simon has no property of his own \textcolor{green}{save} the \textcolor{red}{small}

 estate of Birchmoor, it is \textcolor{green}{obvious} that the Californian heiress

 is not the only gainer by an \textcolor{green}{alliance} which will \textcolor{green}{enable} her to

 make the easy and common transition from a Republican lady to a

 British peeress.'"



 "Anything else?" asked Holmes, \textcolor{red}{yawning.}



 "Oh, yes; plenty. Then there is another note in the Morning Post

 to say that the \textcolor{BurntOrange}{marriage} would be an absolutely \textcolor{BurntOrange}{quiet} one, that it

 would be at St. George's, Hanover Square, that only half a dozen

 \textcolor{BurntOrange}{intimate} \textcolor{green}{friends} would be \textcolor{BurntOrange}{invited,} and that the party would

 return to the furnished house at Lancaster \textcolor{green}{Gate} which has been

 taken by Mr. Aloysius Doran. Two days later--that is, on

 Wednesday last--there is a curt \textcolor{blue}{announcement} that the wedding had

 taken place, and that the \textcolor{BurntOrange}{honeymoon} would be passed at \textcolor{BurntOrange}{Lord}

 \textcolor{red}{Backwater's} place, near Petersfield. Those are all the notices

 which appeared before the disappearance of the \textcolor{BurntOrange}{bride."}



 "Before the what?" asked Holmes with a \textcolor{blue}{start.}



 "The \textcolor{blue}{vanishing} of the lady."



 "When did she \textcolor{blue}{vanish,} then?"



 "At the wedding \textcolor{green}{breakfast."}



 "Indeed. This is more \textcolor{green}{interesting} than it \textcolor{green}{promised} to be; quite

 dramatic, in \textcolor{green}{fact."}



 "Yes; it struck me as being a little out of the common."



 "They often \textcolor{blue}{vanish} before the \textcolor{BurntOrange}{ceremony,} and occasionally during

 the \textcolor{BurntOrange}{honeymoon;} but I cannot call to mind anything quite so prompt

 as this. \textcolor{BurntOrange}{Pray} let me have the details."



 "I \textcolor{BurntOrange}{warn} you that they are very incomplete."



 "Perhaps we may make them less so."



 "Such as they are, they are set forth in a single article of a

 morning paper of yesterday, which I will read to you. It is

 headed, 'Singular Occurrence at a \textcolor{green}{Fashionable} Wedding':



 "'The family of \textcolor{BurntOrange}{Lord} Robert St. Simon has been thrown into the

 greatest \textcolor{red}{consternation} by the strange and \textcolor{red}{painful} episodes which

 have taken place in connection with his wedding. The \textcolor{BurntOrange}{ceremony,} as

 \textcolor{blue}{shortly} announced in the papers of yesterday, occurred on the

 previous morning; but it is only now that it has been possible to

 confirm the strange rumours which have been so persistently

 floating about. In \textcolor{red}{spite} of the \textcolor{blue}{attempts} of the \textcolor{green}{friends} to \textcolor{green}{hush}

 the matter up, so much \textcolor{BurntOrange}{public} \textcolor{green}{attention} has now been drawn to it

 that no \textcolor{BurntOrange}{good} purpose can be \textcolor{BurntOrange}{served} by affecting to \textcolor{red}{disregard} what

 is a common \textcolor{red}{subject} for conversation.



 "'The \textcolor{BurntOrange}{ceremony,} which was performed at St. George's, Hanover

 Square, was a very \textcolor{BurntOrange}{quiet} one, no one being \textcolor{BurntOrange}{present} \textcolor{green}{save} the

 \textcolor{green}{father} of the \textcolor{BurntOrange}{bride,} Mr. Aloysius Doran, the Duchess of Balmoral,

 \textcolor{BurntOrange}{Lord} \textcolor{red}{Backwater,} \textcolor{BurntOrange}{Lord} Eustace and Lady Clara St. Simon (the

 \textcolor{BurntOrange}{younger} \textcolor{green}{brother} and sister of the \textcolor{BurntOrange}{bridegroom),} and Lady Alicia

 Whittington. The whole party proceeded afterwards to the house of

 Mr. Aloysius Doran, at Lancaster \textcolor{green}{Gate,} where \textcolor{green}{breakfast} had been

 \textcolor{BurntOrange}{prepared.} It appears that some little trouble was caused by a

 woman, whose name has not been ascertained, who endeavoured to

 \textcolor{red}{force} her way into the house after the \textcolor{BurntOrange}{bridal} party, \textcolor{red}{alleging}

 that she had some claim upon \textcolor{BurntOrange}{Lord} St. Simon. It was only after a

 \textcolor{red}{painful} and \textcolor{red}{prolonged} scene that she was \textcolor{red}{ejected} by the \textcolor{green}{butler}

 and the footman. The \textcolor{BurntOrange}{bride,} who had fortunately entered the house

 before this \textcolor{red}{unpleasant} interruption, had sat down to \textcolor{green}{breakfast}

 with the \textcolor{green}{rest,} when she \textcolor{red}{complained} of a \textcolor{blue}{sudden} indisposition and

 retired to her room. Her \textcolor{red}{prolonged} \textcolor{red}{absence} having caused some

 comment, her \textcolor{green}{father} followed her, but \textcolor{green}{learned} from her maid that

 she had only come up to her chamber for an instant, caught up an

 ulster and bonnet, and \textcolor{blue}{hurried} down to the passage. One of the

 footmen declared that he had seen a lady \textcolor{BurntOrange}{leave} the house thus

 apparelled, but had \textcolor{red}{refused} to \textcolor{green}{credit} that it was his \textcolor{red}{mistress,}

 believing her to be with the company. On ascertaining that his

 \textcolor{green}{daughter} had \textcolor{red}{disappeared,} Mr. Aloysius Doran, in conjunction with

 the \textcolor{BurntOrange}{bridegroom,} instantly put themselves in \textcolor{green}{communication} with

 the \textcolor{BurntOrange}{police,} and very \textcolor{green}{energetic} \textcolor{BurntOrange}{inquiries} are being made, which

 will probably \textcolor{blue}{result} in a \textcolor{green}{speedy} clearing up of this very

 singular business. Up to a \textcolor{red}{late} hour last night, however, nothing

 had transpired as to the whereabouts of the missing lady. There

 are rumours of \textcolor{red}{foul} play in the matter, and it is said that the

 \textcolor{BurntOrange}{police} have caused the \textcolor{red}{arrest} of the woman who had caused the

 original \textcolor{BurntOrange}{disturbance,} in the belief that, from \textcolor{red}{jealousy} or some

 other \textcolor{green}{motive,} she may have been \textcolor{red}{concerned} in the strange

 disappearance of the \textcolor{BurntOrange}{bride.'"}



 "And is that all?"



 "Only one little item in another of the morning papers, but it is

 a suggestive one."



 "And it is--"



 "That Miss Flora Millar, the lady who had caused the \textcolor{BurntOrange}{disturbance,}

 has actually been \textcolor{red}{arrested.} It appears that she was formerly a

 danseuse at the \textcolor{green}{Allegro,} and that she has known the \textcolor{BurntOrange}{bridegroom}

 for some years. There are no further particulars, and the whole

 \textcolor{red}{case} is in your hands now--so far as it has been set forth in the

 \textcolor{BurntOrange}{public} press."



 "And an exceedingly \textcolor{green}{interesting} \textcolor{red}{case} it appears to be. I would

 not have missed it for worlds. But there is a ring at the bell,

 Watson, and as the \textcolor{blue}{clock} makes it a few minutes after four, I

 have no \textcolor{BurntOrange}{doubt} that this will \textcolor{green}{prove} to be our \textcolor{green}{noble} client. Do not

 dream of going, Watson, for I very much \textcolor{green}{prefer} having a \textcolor{green}{witness,}

 if only as a check to my own memory."



 \textcolor{BurntOrange}{"Lord} Robert St. Simon," announced our page-boy, throwing open

 the door. A \textcolor{green}{gentleman} entered, with a \textcolor{BurntOrange}{pleasant,} \textcolor{green}{cultured} face,

 high-nosed and pale, with something perhaps of petulance about

 the \textcolor{blue}{mouth,} and with the \textcolor{BurntOrange}{steady,} well-opened eye of a man whose

 \textcolor{BurntOrange}{pleasant} lot it had ever been to command and to be obeyed. His

 manner was brisk, and yet his \textcolor{green}{general} appearance gave an undue

 \textcolor{green}{impression} of age, for he had a slight \textcolor{green}{forward} stoop and a little

 bend of the knees as he walked. His hair, too, as he swept off

 his very curly-brimmed hat, was grizzled round the edges and thin

 upon the \textcolor{BurntOrange}{top.} As to his dress, it was \textcolor{green}{careful} to the \textcolor{BurntOrange}{verge} of

 foppishness, with high collar, \textcolor{red}{black} frock-coat, \textcolor{BurntOrange}{white} waistcoat,

 yellow gloves, patent-leather shoes, and light-coloured gaiters.

 He \textcolor{green}{advanced} slowly into the room, turning his head from left to

 right, and swinging in his right hand the cord which held his

 golden eyeglasses.



 "Good-day, \textcolor{BurntOrange}{Lord} St. Simon," said Holmes, rising and bowing. \textcolor{BurntOrange}{"Pray}

 take the basket-chair. This is my \textcolor{green}{friend} and colleague, Dr.

 Watson. Draw up a little to the \textcolor{red}{fire,} and we will \textcolor{green}{talk} this

 matter over."



 "A most \textcolor{red}{painful} matter to me, as you can most \textcolor{green}{readily} imagine,

 Mr. Holmes. I have been cut to the quick. I understand that you

 have already \textcolor{green}{managed} several delicate \textcolor{red}{cases} of this sort, \textcolor{green}{sir,}

 though I presume that they were hardly from the same class of

 society."



 "No, I am descending."



 "I \textcolor{red}{beg} \textcolor{green}{pardon."}



 "My last client of the sort was a \textcolor{green}{king."}



 "Oh, really! I had no idea. And which \textcolor{green}{king?"}



 "The \textcolor{green}{King} of Scandinavia."



 "What! Had he \textcolor{BurntOrange}{lost} his wife?"



 "You can understand," said Holmes suavely, "that I \textcolor{green}{extend} to the

 affairs of my other clients the same \textcolor{BurntOrange}{secrecy} which I \textcolor{green}{promise} to

 you in yours."



 "Of course! Very right! very right! I'm sure I \textcolor{red}{beg} \textcolor{green}{pardon.} As to

 my own \textcolor{red}{case,} I am \textcolor{blue}{ready} to give you any \textcolor{green}{information} which may

 \textcolor{green}{assist} you in forming an opinion."



 "Thank you. I have already \textcolor{green}{learned} all that is in the \textcolor{BurntOrange}{public}

 prints, nothing more. I presume that I may take it as correct--this

 article, for example, as to the disappearance of the \textcolor{BurntOrange}{bride."}



 \textcolor{BurntOrange}{Lord} St. Simon glanced over it. "Yes, it is correct, as far as it

 goes."



 "But it needs a great \textcolor{BurntOrange}{deal} of supplementing before anyone could

 \textcolor{green}{offer} an opinion. I think that I may \textcolor{blue}{arrive} at my \textcolor{green}{facts} most

 directly by \textcolor{green}{questioning} you."



 \textcolor{BurntOrange}{"Pray} do so."



 "When did you first meet Miss Hatty Doran?"



 "In San Francisco, a year ago."



 "You were travelling in the States?"



 "Yes."



 "Did you become engaged then?"



 "No."



 "But you were on a \textcolor{BurntOrange}{friendly} \textcolor{green}{footing?"}



 "I was \textcolor{green}{amused} by her society, and she could see that I was

 \textcolor{green}{amused."}



 "Her \textcolor{green}{father} is very rich?"



 "He is said to be the richest man on the \textcolor{green}{Pacific} slope."



 "And how did he make his \textcolor{BurntOrange}{money?"}



 "In mining. He had nothing a few years ago. Then he struck \textcolor{green}{gold,}

 invested it, and came up by leaps and \textcolor{red}{bounds."}



 "Now, what is your own \textcolor{green}{impression} as to the \textcolor{BurntOrange}{young} lady's--your

 wife's character?"



 The \textcolor{green}{nobleman} swung his glasses a little faster and \textcolor{BurntOrange}{stared} down

 into the \textcolor{red}{fire.} "You see, Mr. Holmes," said he, "my wife was

 twenty before her \textcolor{green}{father} became a rich man. During that \textcolor{blue}{time} she

 ran free in a mining camp and wandered through woods or

 \textcolor{blue}{mountains,} so that her education has come from Nature rather than

 from the schoolmaster. She is what we call in England a tomboy,

 with a strong nature, \textcolor{BurntOrange}{wild} and free, unfettered by any sort of

 traditions. She is impetuous--volcanic, I was about to say. She

 is \textcolor{green}{swift} in making up her mind and \textcolor{BurntOrange}{fearless} in carrying out her

 resolutions. On the other hand, I would not have given her the

 name which I have the honour to bear"--he gave a little \textcolor{green}{stately}

 cough--"had not I \textcolor{blue}{thought} her to be at \textcolor{red}{bottom} a \textcolor{green}{noble} woman. I

 believe that she is capable of \textcolor{BurntOrange}{heroic} self-sacrifice and that

 anything dishonourable would be repugnant to her."



 "Have you her photograph?"



 "I brought this with me." He opened a locket and \textcolor{green}{showed} us the

 \textcolor{green}{full} face of a very \textcolor{BurntOrange}{lovely} woman. It was not a photograph but an

 ivory miniature, and the artist had brought out the \textcolor{green}{full} effect

 of the \textcolor{green}{lustrous} \textcolor{red}{black} hair, the large \textcolor{red}{dark} eyes, and the

 \textcolor{green}{exquisite} \textcolor{blue}{mouth.} Holmes gazed \textcolor{blue}{long} and \textcolor{green}{earnestly} at it. Then he

 closed the locket and handed it back to \textcolor{BurntOrange}{Lord} St. Simon.



 "The \textcolor{BurntOrange}{young} lady came to London, then, and you renewed your

 acquaintance?"



 "Yes, her \textcolor{green}{father} brought her over for this last London season. I

 met her several \textcolor{blue}{times,} became engaged to her, and have now

 married her."



 "She brought, I understand, a \textcolor{green}{considerable} dowry?"



 "A \textcolor{green}{fair} dowry. Not more than is \textcolor{green}{usual} in my family."



 "And this, of course, \textcolor{BurntOrange}{remains} to you, since the \textcolor{BurntOrange}{marriage} is a

 fait accompli?"



 "I really have made no \textcolor{BurntOrange}{inquiries} on the \textcolor{red}{subject."}



 "Very naturally not. Did you see Miss Doran on the day before the

 wedding?"



 "Yes."



 "Was she in \textcolor{BurntOrange}{good} \textcolor{green}{spirits?"}



 "Never better. She kept \textcolor{green}{talking} of what we should do in our

 future lives."



 "Indeed! That is very \textcolor{green}{interesting.} And on the morning of the

 wedding?"



 "She was as bright as possible--at least until after the

 \textcolor{BurntOrange}{ceremony."}



 "And did you observe any \textcolor{red}{change} in her then?"



 "Well, to tell the \textcolor{green}{truth,} I saw then the first signs that I had

 ever seen that her temper was just a little sharp. The \textcolor{blue}{incident}

 however, was too trivial to relate and can have no possible

 bearing upon the \textcolor{red}{case."}



 \textcolor{BurntOrange}{"Pray} let us have it, for all that."



 "Oh, it is \textcolor{red}{childish.} She dropped her \textcolor{green}{bouquet} as we went towards

 the vestry. She was passing the front pew at the \textcolor{blue}{time,} and it

 \textcolor{red}{fell} over into the pew. There was a moment's \textcolor{red}{delay,} but the

 \textcolor{green}{gentleman} in the pew handed it up to her again, and it did not

 appear to be the \textcolor{red}{worse} for the \textcolor{red}{fall.} Yet when I \textcolor{red}{spoke} to her of

 the matter, she answered me abruptly; and in the carriage, on our

 way home, she seemed absurdly agitated over this \textcolor{red}{trifling} cause."



 "Indeed! You say that there was a \textcolor{green}{gentleman} in the pew. Some of

 the \textcolor{green}{general} \textcolor{BurntOrange}{public} were \textcolor{BurntOrange}{present,} then?"



 "Oh, yes. It is \textcolor{red}{impossible} to exclude them when the \textcolor{BurntOrange}{church} is

 open."



 "This \textcolor{green}{gentleman} was not one of your wife's \textcolor{green}{friends?"}



 "No, no; I call him a \textcolor{green}{gentleman} by \textcolor{green}{courtesy,} but he was quite a

 common-looking person. I hardly noticed his appearance. But

 really I think that we are wandering rather far from the point."



 "Lady St. Simon, then, returned from the wedding in a less

 \textcolor{BurntOrange}{cheerful} frame of mind than she had gone to it. What did she do

 on re-entering her \textcolor{green}{father's} house?"



 "I saw her in conversation with her maid."



 "And who is her maid?"



 "Alice is her name. She is an American and came from California

 with her."



 "A \textcolor{green}{confidential} \textcolor{BurntOrange}{servant?"}



 "A little too much so. It seemed to me that her \textcolor{red}{mistress} allowed

 her to take great \textcolor{BurntOrange}{liberties.} Still, of course, in America they

 look upon these things in a different way."



 "How \textcolor{blue}{long} did she speak to this Alice?"



 "Oh, a few minutes. I had something else to think of."



 "You did not overhear what they said?"



 "Lady St. Simon said something about 'jumping a claim.' She was

 accustomed to use slang of the \textcolor{green}{kind.} I have no idea what she

 meant."



 "American slang is very expressive sometimes. And what did your

 wife do when she finished speaking to her maid?"



 "She walked into the breakfast-room."



 "On your arm?"



 "No, alone. She was very independent in little matters like that.

 Then, after we had sat down for ten minutes or so, she rose

 hurriedly, \textcolor{red}{muttered} some \textcolor{green}{words} of \textcolor{green}{apology,} and left the room. She

 never came back."



 "But this maid, Alice, as I understand, deposes that she went to

 her room, \textcolor{green}{covered} her \textcolor{BurntOrange}{bride's} dress with a \textcolor{blue}{long} ulster, put on a

 bonnet, and went out."



 "Quite so. And she was afterwards seen walking into Hyde Park in

 company with Flora Millar, a woman who is now in \textcolor{green}{custody,} and who

 had already made a \textcolor{BurntOrange}{disturbance} at Mr. Doran's house that

 morning."



 "Ah, yes. I should like a few particulars as to this \textcolor{BurntOrange}{young} lady,

 and your relations to her."



 \textcolor{BurntOrange}{Lord} St. Simon shrugged his \textcolor{green}{shoulders} and raised his eyebrows.

 "We have been on a \textcolor{BurntOrange}{friendly} \textcolor{green}{footing} for some years--I may say on

 a very \textcolor{BurntOrange}{friendly} \textcolor{green}{footing.} She used to be at the \textcolor{green}{Allegro.} I have

 not \textcolor{BurntOrange}{treated} her ungenerously, and she had no just cause of

 \textcolor{red}{complaint} against me, but you know what women are, Mr. Holmes.

 Flora was a \textcolor{green}{dear} little thing, but exceedingly hot-headed and

 devotedly attached to me. She wrote me \textcolor{BurntOrange}{dreadful} \textcolor{blue}{letters} when she

 heard that I was about to be married, and, to tell the \textcolor{green}{truth,} the

 \textcolor{green}{reason} why I had the \textcolor{BurntOrange}{marriage} celebrated so quietly was that I

 \textcolor{red}{feared} lest there might be a \textcolor{red}{scandal} in the \textcolor{BurntOrange}{church.} She came to

 Mr. Doran's door just after we returned, and she endeavoured to

 push her way in, uttering very abusive expressions towards my

 wife, and even \textcolor{BurntOrange}{threatening} her, but I had \textcolor{BurntOrange}{foreseen} the

 \textcolor{blue}{possibility} of something of the sort, and I had two \textcolor{BurntOrange}{police}

 \textcolor{green}{fellows} there in private clothes, who soon pushed her out again.

 She was \textcolor{BurntOrange}{quiet} when she saw that there was no \textcolor{BurntOrange}{good} in making a

 \textcolor{red}{row."}



 "Did your wife hear all this?"



 "No, thank \textcolor{BurntOrange}{goodness,} she did not."



 "And she was seen walking with this very woman afterwards?"



 "Yes. That is what Mr. Lestrade, of Scotland Yard, looks upon as

 so serious. It is \textcolor{blue}{thought} that Flora decoyed my wife out and laid

 some \textcolor{red}{terrible} trap for her."



 "Well, it is a possible supposition."



 "You think so, too?"



 "I did not say a probable one. But you do not yourself look upon

 this as likely?"



 "I do not think Flora would \textcolor{red}{hurt} a fly."



 "Still, \textcolor{red}{jealousy} is a strange transformer of characters. \textcolor{BurntOrange}{Pray}

 what is your own \textcolor{BurntOrange}{theory} as to what took place?"



 "Well, really, I came to \textcolor{blue}{seek} a \textcolor{BurntOrange}{theory,} not to propound one. I

 have given you all the \textcolor{green}{facts.} Since you ask me, however, I may

 say that it has occurred to me as possible that the \textcolor{BurntOrange}{excitement} of

 this affair, the \textcolor{green}{consciousness} that she had made so \textcolor{green}{immense} a

 social stride, had the effect of causing some little \textcolor{BurntOrange}{nervous}

 \textcolor{BurntOrange}{disturbance} in my wife."



 "In short, that she had become \textcolor{blue}{suddenly} deranged?"



 "Well, really, when I consider that she has turned her back--I

 will not say upon me, but upon so much that many have \textcolor{BurntOrange}{aspired} to

 without success--I can hardly \textcolor{green}{explain} it in any other fashion."



 "Well, certainly that is also a conceivable \textcolor{blue}{hypothesis,"} said

 Holmes, \textcolor{BurntOrange}{smiling.} "And now, \textcolor{BurntOrange}{Lord} St. Simon, I think that I have

 nearly all my data. May I ask whether you were seated at the

 breakfast-table so that you could see out of the window?"



 "We could see the other side of the road and the Park."



 "Quite so. Then I do not think that I need to \textcolor{red}{detain} you longer.

 I shall \textcolor{green}{communicate} with you."



 "Should you be \textcolor{green}{fortunate} enough to solve this \textcolor{red}{problem,"} said our

 client, rising.



 "I have solved it."



 "Eh? What was that?"



 "I say that I have solved it."



 "Where, then, is my wife?"



 "That is a detail which I shall speedily \textcolor{green}{supply."}



 \textcolor{BurntOrange}{Lord} St. Simon shook his head. "I am \textcolor{red}{afraid} that it will take

 wiser heads than yours or mine," he remarked, and bowing in a

 \textcolor{green}{stately,} old-fashioned manner he \textcolor{BurntOrange}{departed.}



 "It is very \textcolor{BurntOrange}{good} of \textcolor{BurntOrange}{Lord} St. Simon to honour my head by putting

 it on a \textcolor{green}{level} with his own," said Sherlock Holmes, \textcolor{BurntOrange}{laughing.} "I

 think that I shall have a \textcolor{red}{whisky} and soda and a cigar after all

 this cross-questioning. I had formed my conclusions as to the

 \textcolor{red}{case} before our client came into the room."



 "My \textcolor{green}{dear} Holmes!"



 "I have notes of several similar \textcolor{red}{cases,} though none, as I

 remarked before, which were quite as prompt. My whole \textcolor{BurntOrange}{examination}

 \textcolor{BurntOrange}{served} to turn my \textcolor{blue}{conjecture} into a \textcolor{green}{certainty.} Circumstantial

 evidence is occasionally very \textcolor{green}{convincing,} as when you find a

 trout in the milk, to \textcolor{BurntOrange}{quote} Thoreau's example."



 "But I have heard all that you have heard."



 "Without, however, the \textcolor{green}{knowledge} of pre-existing \textcolor{red}{cases} which

 serves me so well. There was a parallel instance in Aberdeen some

 years back, and something on very much the same lines at Munich

 the year after the Franco-Prussian \textcolor{red}{War.} It is one of these

 cases--but, hullo, here is Lestrade! Good-afternoon, Lestrade!

 You will find an \textcolor{green}{extra} tumbler upon the sideboard, and there are

 cigars in the box."



 The \textcolor{green}{official} detective was attired in a pea-jacket and cravat,

 which gave him a decidedly nautical appearance, and he carried a

 \textcolor{red}{black} canvas bag in his hand. With a short greeting he seated

 himself and lit the cigar which had been \textcolor{green}{offered} to him.



 "What's up, then?" asked Holmes with a \textcolor{BurntOrange}{twinkle} in his eye. "You

 look dissatisfied."



 "And I feel dissatisfied. It is this infernal St. Simon \textcolor{BurntOrange}{marriage}

 \textcolor{red}{case.} I can make neither head nor tail of the business."



 "Really! You \textcolor{BurntOrange}{surprise} me."



 "Who ever heard of such a mixed affair? Every \textcolor{blue}{clue} seems to \textcolor{BurntOrange}{slip}

 through my fingers. I have been at work upon it all day."



 "And very wet it seems to have made you," said Holmes laying his

 hand upon the arm of the pea-jacket.



 "Yes, I have been dragging the Serpentine."



 "In heaven's name, what for?"



 "In search of the body of Lady St. Simon."



 Sherlock Holmes leaned back in his chair and \textcolor{BurntOrange}{laughed} \textcolor{green}{heartily.}



 "Have you dragged the basin of Trafalgar Square fountain?" he

 asked.



 "Why? What do you mean?"



 "Because you have just as \textcolor{BurntOrange}{good} a \textcolor{blue}{chance} of finding this lady in

 the one as in the other."



 Lestrade \textcolor{BurntOrange}{shot} an \textcolor{red}{angry} glance at my \textcolor{green}{companion.} "I suppose you

 know all about it," he \textcolor{red}{snarled.}



 "Well, I have only just heard the \textcolor{green}{facts,} but my mind is made up."



 "Oh, indeed! Then you think that the Serpentine plays no part in

 the matter?"



 "I think it very unlikely."



 "Then perhaps you will kindly \textcolor{green}{explain} how it is that we \textcolor{green}{found}

 this in it?" He opened his bag as he \textcolor{red}{spoke,} and \textcolor{red}{tumbled} onto the

 floor a wedding-dress of watered \textcolor{green}{silk,} a pair of \textcolor{BurntOrange}{white} \textcolor{green}{satin}

 shoes and a \textcolor{BurntOrange}{bride's} wreath and veil, all discoloured and \textcolor{red}{soaked}

 in water. "There," said he, putting a new wedding-ring upon the

 \textcolor{BurntOrange}{top} of the pile. "There is a little nut for you to \textcolor{red}{crack,} \textcolor{green}{Master}

 Holmes."



 "Oh, indeed!" said my \textcolor{green}{friend,} blowing \textcolor{red}{blue} rings into the air.

 "You dragged them from the Serpentine?"



 "No. They were \textcolor{green}{found} floating near the \textcolor{red}{margin} by a park-keeper.

 They have been identified as her clothes, and it seemed to me

 that if the clothes were there the body would not be far off."



 "By the same \textcolor{BurntOrange}{brilliant} \textcolor{green}{reasoning,} every man's body is to be \textcolor{green}{found}

 in the neighbourhood of his wardrobe. And \textcolor{BurntOrange}{pray} what did you \textcolor{BurntOrange}{hope}

 to \textcolor{blue}{arrive} at through this?"



 "At some evidence \textcolor{red}{implicating} Flora Millar in the disappearance."



 "I am \textcolor{red}{afraid} that you will find it \textcolor{red}{difficult."}



 "Are you, indeed, now?" \textcolor{red}{cried} Lestrade with some \textcolor{red}{bitterness.} "I

 am \textcolor{red}{afraid,} Holmes, that you are not very practical with your

 deductions and your inferences. You have made two \textcolor{red}{blunders} in as

 many minutes. This dress does \textcolor{red}{implicate} Miss Flora Millar."



 "And how?"



 "In the dress is a pocket. In the pocket is a card-case. In the

 card-case is a note. And here is the very note." He \textcolor{BurntOrange}{slapped} it

 down upon the table in front of him. "Listen to this: 'You will

 see me when all is \textcolor{blue}{ready.} Come at once. F.H.M.' Now my \textcolor{BurntOrange}{theory} all

 along has been that Lady St. Simon was decoyed away by Flora

 Millar, and that she, with \textcolor{green}{confederates,} no \textcolor{BurntOrange}{doubt,} was

 \textcolor{green}{responsible} for her disappearance. Here, signed with her

 initials, is the very note which was no \textcolor{BurntOrange}{doubt} quietly \textcolor{BurntOrange}{slipped}

 into her hand at the door and which \textcolor{red}{lured} her within their

 reach."



 "Very \textcolor{BurntOrange}{good,} Lestrade," said Holmes, \textcolor{BurntOrange}{laughing.} "You really are

 very fine indeed. Let me see it." He took up the paper in a

 \textcolor{red}{listless} way, but his \textcolor{green}{attention} instantly became riveted, and he

 gave a little \textcolor{red}{cry} of satisfaction. "This is indeed \textcolor{green}{important,"}

 said he.



 "Ha! you find it so?"



 "Extremely so. I congratulate you warmly."



 Lestrade rose in his \textcolor{BurntOrange}{triumph} and bent his head to look. "Why," he

 \textcolor{BurntOrange}{shrieked,} "you're looking at the \textcolor{red}{wrong} side!"



 "On the \textcolor{red}{contrary,} this is the right side."



 "The right side? You're \textcolor{red}{mad!} Here is the note written in pencil

 over here."



 "And over here is what appears to be the fragment of a hotel

 bill, which \textcolor{green}{interests} me deeply."



 "There's nothing in it. I looked at it before," said Lestrade.

 "'Oct. 4th, rooms 8s., \textcolor{green}{breakfast} 2s. 6d., cocktail 1s., lunch 2s.

 6d., glass sherry, 8d.' I see nothing in that."



 "Very likely not. It is most \textcolor{green}{important,} all the same. As to the

 note, it is \textcolor{green}{important} also, or at least the initials are, so I

 congratulate you again."



 "I've \textcolor{red}{wasted} \textcolor{blue}{time} enough," said Lestrade, rising. "I believe in

 hard work and not in sitting by the \textcolor{red}{fire} spinning fine \textcolor{BurntOrange}{theories.}

 Good-day, Mr. Holmes, and we shall see which gets to the \textcolor{red}{bottom}

 of the matter first." He gathered up the garments, thrust them

 into the bag, and made for the door.



 "Just one hint to you, Lestrade," drawled Holmes before his rival

 \textcolor{BurntOrange}{vanished;} "I will tell you the \textcolor{green}{true} \textcolor{green}{solution} of the matter. Lady

 St. Simon is a myth. There is not, and there never has been, any

 such person."



 Lestrade looked \textcolor{red}{sadly} at my \textcolor{green}{companion.} Then he turned to me,

 tapped his forehead three \textcolor{blue}{times,} shook his head solemnly, and

 \textcolor{blue}{hurried} away.



 He had hardly shut the door behind him when Holmes rose to put on

 his overcoat. "There is something in what the \textcolor{green}{fellow} says about

 outdoor work," he remarked, "so I think, Watson, that I must

 \textcolor{BurntOrange}{leave} you to your papers for a little."



 It was after five o'clock when Sherlock Holmes left me, but I had

 no \textcolor{blue}{time} to be \textcolor{red}{lonely,} for within an hour there \textcolor{blue}{arrived} a

 confectioner's man with a very large flat box. This he unpacked

 with the help of a \textcolor{BurntOrange}{youth} whom he had brought with him, and

 presently, to my very great \textcolor{BurntOrange}{astonishment,} a quite epicurean

 little \textcolor{red}{cold} supper began to be laid out upon our \textcolor{BurntOrange}{humble}

 lodging-house mahogany. There were a couple of brace of \textcolor{red}{cold}

 woodcock, a pheasant, a pâté de foie gras pie with a group of

 \textcolor{red}{ancient} and cobwebby bottles. Having laid out all these \textcolor{green}{luxuries,}

 my two \textcolor{BurntOrange}{visitors} \textcolor{BurntOrange}{vanished} away, like the \textcolor{green}{genii} of the Arabian

 Nights, with no explanation \textcolor{green}{save} that the things had been paid

 for and were ordered to this address.



 Just before nine o'clock Sherlock Holmes stepped briskly into the

 room. His \textcolor{green}{features} were gravely set, but there was a light in his

 eye which made me think that he had not been \textcolor{red}{disappointed} in his

 conclusions.



 "They have laid the supper, then," he said, rubbing his hands.



 "You seem to \textcolor{BurntOrange}{expect} company. They have laid for five."



 "Yes, I \textcolor{BurntOrange}{fancy} we may have some company dropping in," said he. "I

 am \textcolor{blue}{surprised} that \textcolor{BurntOrange}{Lord} St. Simon has not already \textcolor{blue}{arrived.} Ha! I

 \textcolor{BurntOrange}{fancy} that I hear his step now upon the stairs."



 It was indeed our \textcolor{BurntOrange}{visitor} of the afternoon who came bustling in,

 dangling his glasses more vigorously than ever, and with a very

 perturbed expression upon his \textcolor{green}{aristocratic} \textcolor{green}{features.}



 "My \textcolor{green}{messenger} reached you, then?" asked Holmes.



 "Yes, and I \textcolor{BurntOrange}{confess} that the \textcolor{green}{contents} \textcolor{BurntOrange}{startled} me beyond \textcolor{green}{measure.}

 Have you \textcolor{BurntOrange}{good} \textcolor{green}{authority} for what you say?"



 "The best possible."



 \textcolor{BurntOrange}{Lord} St. Simon sank into a chair and passed his hand over his

 forehead.



 "What will the \textcolor{green}{Duke} say," he murmured, "when he hears that one of

 the family has been \textcolor{red}{subjected} to such \textcolor{red}{humiliation?"}



 "It is the purest \textcolor{BurntOrange}{accident.} I cannot allow that there is any

 \textcolor{red}{humiliation."}



 "Ah, you look on these things from another standpoint."



 "I fail to see that anyone is to \textcolor{red}{blame.} I can hardly see how the

 lady could have acted otherwise, though her \textcolor{blue}{abrupt} method of

 doing it was undoubtedly to be \textcolor{red}{regretted.} Having no \textcolor{BurntOrange}{mother,} she

 had no one to \textcolor{green}{advise} her at such a \textcolor{red}{crisis."}



 "It was a slight, \textcolor{green}{sir,} a \textcolor{BurntOrange}{public} slight," said \textcolor{BurntOrange}{Lord} St. Simon,

 tapping his fingers upon the table.



 "You must make allowance for this poor girl, placed in so

 \textcolor{blue}{unprecedented} a position."



 "I will make no allowance. I am very \textcolor{red}{angry} indeed, and I have

 been shamefully used."



 "I think that I heard a ring," said Holmes. "Yes, there are steps

 on the \textcolor{green}{landing.} If I cannot \textcolor{green}{persuade} you to take a \textcolor{green}{lenient} view

 of the matter, \textcolor{BurntOrange}{Lord} St. Simon, I have brought an \textcolor{green}{advocate} here

 who may be more \textcolor{BurntOrange}{successful."} He opened the door and ushered in a

 lady and \textcolor{green}{gentleman.} \textcolor{BurntOrange}{"Lord} St. Simon," said he "allow me to

 introduce you to Mr. and Mrs. Francis Hay Moulton. The lady, I

 think, you have already met."



 At the sight of these \textcolor{BurntOrange}{newcomers} our client had sprung from his

 seat and stood very erect, with his eyes cast down and his hand

 thrust into the breast of his frock-coat, a picture of \textcolor{red}{offended}

 \textcolor{green}{dignity.} The lady had taken a quick step \textcolor{green}{forward} and had held out

 her hand to him, but he still \textcolor{red}{refused} to raise his eyes. It was

 as well for his resolution, perhaps, for her pleading face was

 one which it was hard to \textcolor{red}{resist.}



 "You're \textcolor{red}{angry,} Robert," said she. "Well, I \textcolor{blue}{guess} you have every

 cause to be."



 \textcolor{BurntOrange}{"Pray} make no \textcolor{green}{apology} to me," said \textcolor{BurntOrange}{Lord} St. Simon \textcolor{red}{bitterly.}



 "Oh, yes, I know that I have \textcolor{BurntOrange}{treated} you \textcolor{green}{real} \textcolor{red}{bad} and that I

 should have spoken to you before I went; but I was \textcolor{green}{kind} of

 rattled, and from the \textcolor{blue}{time} when I saw \textcolor{green}{Frank} here again I just

 didn't know what I was doing or saying. I only wonder I didn't

 \textcolor{red}{fall} down and do a faint right there before the altar."



 "Perhaps, Mrs. Moulton, you would like my \textcolor{green}{friend} and me to \textcolor{BurntOrange}{leave}

 the room while you \textcolor{green}{explain} this matter?"



 "If I may give an opinion," remarked the strange \textcolor{green}{gentleman,}

 "we've had just a little too much \textcolor{BurntOrange}{secrecy} over this business

 already. For my part, I should like all Europe and America to

 hear the rights of it." He was a \textcolor{red}{small,} wiry, sunburnt man,

 clean-shaven, with a sharp face and alert manner.



 "Then \textcolor{red}{I'll} tell our story right away," said the lady. \textcolor{green}{"Frank} here

 and I met in '84, in McQuire's camp, near the Rockies, where pa

 was working a claim. We were engaged to each other, \textcolor{green}{Frank} and I;

 but then one day \textcolor{green}{father} struck a rich pocket and made a pile,

 while poor \textcolor{green}{Frank} here had a claim that petered out and came to

 nothing. The richer pa \textcolor{BurntOrange}{grew} the poorer was \textcolor{green}{Frank;} so at last pa

 wouldn't hear of our engagement lasting any longer, and he took

 me away to 'Frisco. \textcolor{green}{Frank} wouldn't throw up his hand, though; so

 he followed me there, and he saw me without pa knowing anything

 about it. It would only have made him \textcolor{red}{mad} to know, so we just

 fixed it all up for ourselves. \textcolor{green}{Frank} said that he would go and

 make his pile, too, and never come back to claim me until he had

 as much as pa. So then I \textcolor{green}{promised} to \textcolor{BurntOrange}{wait} for him to the end of

 \textcolor{blue}{time} and \textcolor{green}{pledged} myself not to \textcolor{BurntOrange}{marry} anyone else while he lived.

 'Why shouldn't we be married right away, then,' said he, 'and

 then I will feel sure of you; and I \textcolor{blue}{won't} claim to be your

 husband until I come back?' Well, we \textcolor{green}{talked} it over, and he had

 fixed it all up so nicely, with a clergyman all \textcolor{blue}{ready} in \textcolor{BurntOrange}{waiting,}

 that we just did it right there; and then \textcolor{green}{Frank} went off to \textcolor{blue}{seek}

 his \textcolor{BurntOrange}{fortune,} and I went back to pa.



 "The next I heard of \textcolor{green}{Frank} was that he was in Montana, and then

 he went \textcolor{green}{prospecting} in Arizona, and then I heard of him from New

 Mexico. After that came a \textcolor{blue}{long} newspaper story about how a

 miners' camp had been \textcolor{red}{attacked} by \textcolor{red}{Apache} Indians, and there was

 my \textcolor{green}{Frank's} name among the \textcolor{red}{killed.} I fainted dead away, and I was

 very \textcolor{red}{sick} for months after. Pa \textcolor{blue}{thought} I had a \textcolor{red}{decline} and took

 me to half the \textcolor{green}{doctors} in 'Frisco. Not a \textcolor{green}{word} of news came for a

 year and more, so that I never \textcolor{BurntOrange}{doubted} that \textcolor{green}{Frank} was really

 dead. Then \textcolor{BurntOrange}{Lord} St. Simon came to 'Frisco, and we came to London,

 and a \textcolor{BurntOrange}{marriage} was arranged, and pa was very \textcolor{green}{pleased,} but I felt

 all the \textcolor{blue}{time} that no man on this earth would ever take the place

 in my heart that had been given to my poor \textcolor{green}{Frank.}



 "Still, if I had married \textcolor{BurntOrange}{Lord} St. Simon, of course I'd have done

 my duty by him. We can't command our \textcolor{green}{love,} but we can our

 \textcolor{green}{actions.} I went to the altar with him with the intention to make

 him just as \textcolor{BurntOrange}{good} a wife as it was in me to be. But you may

 imagine what I felt when, just as I came to the altar \textcolor{BurntOrange}{rails,} I

 glanced back and saw \textcolor{green}{Frank} standing and looking at me out of the

 first pew. I \textcolor{blue}{thought} it was his \textcolor{red}{ghost} at first; but when I looked

 again there he was still, with a \textcolor{green}{kind} of \textcolor{green}{question} in his eyes, as

 if to ask me whether I were \textcolor{BurntOrange}{glad} or sorry to see him. I wonder I

 didn't drop. I know that everything was turning round, and the

 \textcolor{green}{words} of the clergyman were just like the \textcolor{BurntOrange}{buzz} of a \textcolor{red}{bee} in my

 ear. I didn't know what to do. Should I stop the service and make

 a scene in the \textcolor{BurntOrange}{church?} I glanced at him again, and he seemed to

 know what I was thinking, for he raised his finger to his lips to

 tell me to be still. Then I saw him scribble on a piece of paper,

 and I knew that he was writing me a note. As I passed his pew on

 the way out I dropped my \textcolor{green}{bouquet} over to him, and he \textcolor{BurntOrange}{slipped} the

 note into my hand when he returned me the flowers. It was only a

 line asking me to \textcolor{green}{join} him when he made the sign to me to do so.

 Of course I never \textcolor{BurntOrange}{doubted} for a moment that my first duty was now

 to him, and I determined to do just whatever he might direct.



 "When I got back I told my maid, who had known him in California,

 and had always been his \textcolor{green}{friend.} I ordered her to say nothing, but

 to get a few things packed and my ulster \textcolor{blue}{ready.} I know I ought to

 have spoken to \textcolor{BurntOrange}{Lord} St. Simon, but it was \textcolor{BurntOrange}{dreadful} hard before

 his \textcolor{BurntOrange}{mother} and all those great people. I just made up my mind to

 run away and \textcolor{green}{explain} afterwards. I hadn't been at the table ten

 minutes before I saw \textcolor{green}{Frank} out of the window at the other side of

 the road. He beckoned to me and then began walking into the Park.

 I \textcolor{BurntOrange}{slipped} out, put on my things, and followed him. Some woman

 came \textcolor{green}{talking} something or other about \textcolor{BurntOrange}{Lord} St. Simon to

 me--seemed to me from the little I heard as if he had a little

 \textcolor{green}{secret} of his own before \textcolor{BurntOrange}{marriage} also--but I \textcolor{green}{managed} to get away

 from her and soon overtook \textcolor{green}{Frank.} We got into a \textcolor{green}{cab} together, and

 away we drove to some \textcolor{green}{lodgings} he had taken in Gordon Square, and

 that was my \textcolor{green}{true} wedding after all those years of \textcolor{BurntOrange}{waiting.} \textcolor{green}{Frank}

 had been a \textcolor{red}{prisoner} among the \textcolor{red}{Apaches,} had \textcolor{BurntOrange}{escaped,} came on to

 'Frisco, \textcolor{green}{found} that I had given him up for dead and had gone to

 England, followed me there, and had come upon me at last on the

 very morning of my second wedding."



 "I saw it in a paper," \textcolor{green}{explained} the American. "It gave the name

 and the \textcolor{BurntOrange}{church} but not where the lady lived."



 "Then we had a \textcolor{green}{talk} as to what we should do, and \textcolor{green}{Frank} was all

 for \textcolor{green}{openness,} but I was so \textcolor{red}{ashamed} of it all that I felt as if I

 should like to \textcolor{blue}{vanish} away and never see any of them again--just

 sending a line to pa, perhaps, to \textcolor{green}{show} him that I was \textcolor{BurntOrange}{alive.} It

 was \textcolor{red}{awful} to me to think of all those \textcolor{BurntOrange}{lords} and ladies sitting

 round that breakfast-table and \textcolor{BurntOrange}{waiting} for me to come back. So

 \textcolor{green}{Frank} took my wedding-clothes and things and made a bundle of

 them, so that I should not be traced, and dropped them away

 somewhere where no one could find them. It is likely that we

 should have gone on to Paris \textcolor{blue}{to-morrow,} only that this \textcolor{BurntOrange}{good}

 \textcolor{green}{gentleman,} Mr. Holmes, came round to us this evening, though how

 he \textcolor{green}{found} us is more than I can think, and he \textcolor{green}{showed} us very

 clearly and kindly that I was \textcolor{red}{wrong} and that \textcolor{green}{Frank} was right, and

 that we should be putting ourselves in the \textcolor{red}{wrong} if we were so

 \textcolor{green}{secret.} Then he \textcolor{green}{offered} to give us a \textcolor{blue}{chance} of \textcolor{green}{talking} to \textcolor{BurntOrange}{Lord}

 St. Simon alone, and so we came right away round to his rooms at

 once. Now, Robert, you have heard it all, and I am very sorry if

 I have given you \textcolor{red}{pain,} and I \textcolor{BurntOrange}{hope} that you do not think very

 meanly of me."



 \textcolor{BurntOrange}{Lord} St. Simon had by no means relaxed his \textcolor{red}{rigid} attitude, but

 had listened with a \textcolor{red}{frowning} brow and a \textcolor{red}{compressed} lip to this

 \textcolor{blue}{long} narrative.



 \textcolor{red}{"Excuse} me," he said, "but it is not my custom to discuss my most

 \textcolor{BurntOrange}{intimate} \textcolor{green}{personal} affairs in this \textcolor{BurntOrange}{public} manner."



 "Then you \textcolor{blue}{won't} \textcolor{green}{forgive} me? You \textcolor{blue}{won't} shake hands before I go?"



 "Oh, certainly, if it would give you any pleasure." He put out

 his hand and \textcolor{red}{coldly} grasped that which she \textcolor{green}{extended} to him.



 "I had hoped," \textcolor{green}{suggested} Holmes, "that you would have \textcolor{green}{joined} us

 in a \textcolor{BurntOrange}{friendly} supper."



 "I think that there you ask a little too much," responded his

 \textcolor{green}{Lordship.} "I may be \textcolor{red}{forced} to acquiesce in these recent

 developments, but I can hardly be \textcolor{BurntOrange}{expected} to make \textcolor{green}{merry} over

 them. I think that with your \textcolor{green}{permission} I will now wish you all a

 very good-night." He \textcolor{green}{included} us all in a sweeping bow and

 \textcolor{red}{stalked} out of the room.



 "Then I \textcolor{green}{trust} that you at least will honour me with your

 company," said Sherlock Holmes. "It is always a \textcolor{green}{joy} to meet an

 American, Mr. Moulton, for I am one of those who believe that the

 \textcolor{red}{folly} of a monarch and the blundering of a minister in far-gone

 years will not \textcolor{red}{prevent} our \textcolor{BurntOrange}{children} from being some day \textcolor{green}{citizens}

 of the same world-wide country under a flag which shall be a

 quartering of the Union Jack with the \textcolor{BurntOrange}{Stars} and \textcolor{red}{Stripes."}



 "The \textcolor{red}{case} has been an \textcolor{green}{interesting} one," remarked Holmes when our

 \textcolor{BurntOrange}{visitors} had left us, "because it serves to \textcolor{green}{show} very clearly how

 simple the explanation may be of an affair which at first sight

 seems to be almost \textcolor{BurntOrange}{inexplicable.} Nothing could be more natural

 than the sequence of events as narrated by this lady, and nothing

 \textcolor{red}{stranger} than the \textcolor{blue}{result} when viewed, for instance, by Mr.

 Lestrade of Scotland Yard."



 "You were not yourself at \textcolor{red}{fault} at all, then?"



 "From the first, two \textcolor{green}{facts} were very \textcolor{green}{obvious} to me, the one that

 the lady had been quite willing to undergo the wedding \textcolor{BurntOrange}{ceremony,}

 the other that she had \textcolor{BurntOrange}{repented} of it within a few minutes of

 returning home. Obviously something had occurred during the

 morning, then, to cause her to \textcolor{red}{change} her mind. What could that

 something be? She could not have spoken to anyone when she was

 out, for she had been in the company of the \textcolor{BurntOrange}{bridegroom.} Had she

 seen someone, then? If she had, it must be someone from America

 because she had \textcolor{red}{spent} so short a \textcolor{blue}{time} in this country that she

 could hardly have allowed anyone to \textcolor{green}{acquire} so deep an \textcolor{BurntOrange}{influence}

 over her that the mere sight of him would induce her to \textcolor{red}{change}

 her \textcolor{blue}{plans} so \textcolor{green}{completely.} You see we have already \textcolor{blue}{arrived,} by a

 process of \textcolor{red}{exclusion,} at the idea that she might have seen an

 American. Then who could this American be, and why should he

 \textcolor{red}{possess} so much \textcolor{BurntOrange}{influence} over her? It might be a \textcolor{BurntOrange}{lover;} it might

 be a husband. Her \textcolor{BurntOrange}{young} womanhood had, I knew, been \textcolor{red}{spent} in

 rough scenes and under strange conditions. So far I had got

 before I ever heard \textcolor{BurntOrange}{Lord} St. Simon's narrative. When he told us

 of a man in a pew, of the \textcolor{red}{change} in the \textcolor{BurntOrange}{bride's} manner, of so

 transparent a device for obtaining a note as the dropping of a

 \textcolor{green}{bouquet,} of her resort to her \textcolor{green}{confidential} maid, and of her very

 significant allusion to claim-jumping--which in miners' parlance

 means taking \textcolor{red}{possession} of that which another person has a prior

 claim to--the whole situation became absolutely clear. She had

 gone off with a man, and the man was either a \textcolor{BurntOrange}{lover} or was a

 previous husband--the \textcolor{blue}{chances} being in favour of the latter."



 "And how in the world did you find them?"



 "It might have been \textcolor{red}{difficult,} but \textcolor{green}{friend} Lestrade held

 \textcolor{green}{information} in his hands the value of which he did not himself

 know. The initials were, of course, of the highest \textcolor{BurntOrange}{importance,}

 but more \textcolor{green}{valuable} still was it to know that within a week he had

 settled his bill at one of the most select London hotels."



 "How did you deduce the select?"



 "By the select prices. Eight shillings for a bed and eightpence

 for a glass of sherry pointed to one of the most expensive

 hotels. There are not many in London which charge at that rate.

 In the second one which I \textcolor{green}{visited} in Northumberland Avenue, I

 \textcolor{green}{learned} by an inspection of the book that Francis H. Moulton, an

 American \textcolor{green}{gentleman,} had left only the day before, and on looking

 over the entries against him, I came upon the very items which I

 had seen in the duplicate bill. His \textcolor{blue}{letters} were to be \textcolor{green}{forwarded}

 to 226 Gordon Square; so thither I travelled, and being \textcolor{green}{fortunate}

 enough to find the \textcolor{green}{loving} couple at home, I ventured to give them

 some paternal \textcolor{green}{advice} and to point out to them that it would be

 better in every way that they should make their position a little

 clearer both to the \textcolor{green}{general} \textcolor{BurntOrange}{public} and to \textcolor{BurntOrange}{Lord} St. Simon in

 particular. I \textcolor{BurntOrange}{invited} them to meet him here, and, as you see, I

 made him keep the appointment."



 "But with no very \textcolor{BurntOrange}{good} \textcolor{blue}{result,"} I remarked. "His conduct was

 certainly not very \textcolor{green}{gracious."}



 "Ah, Watson," said Holmes, \textcolor{BurntOrange}{smiling,} "perhaps you would not be

 very \textcolor{green}{gracious} either, if, after all the trouble of wooing and

 wedding, you \textcolor{green}{found} yourself deprived in an instant of wife and of

 \textcolor{BurntOrange}{fortune.} I think that we may judge \textcolor{BurntOrange}{Lord} St. Simon very mercifully

 and thank our \textcolor{BurntOrange}{stars} that we are never likely to find ourselves in

 the same position. Draw your chair up and hand me my violin, for

 the only \textcolor{red}{problem} we have still to solve is how to while away

 these \textcolor{red}{bleak} autumnal evenings."







 XI. THE \textcolor{BurntOrange}{ADVENTURE} OF THE BERYL CORONET



 "Holmes," said I as I stood one morning in our bow-window looking

 down the street, "here is a \textcolor{red}{madman} coming along. It seems rather

 sad that his \textcolor{green}{relatives} should allow him to come out alone."



 My \textcolor{green}{friend} rose lazily from his armchair and stood with his hands

 in the pockets of his dressing-gown, looking over my \textcolor{green}{shoulder.} It

 was a bright, \textcolor{BurntOrange}{crisp} February morning, and the snow of the day

 before still lay deep upon the \textcolor{green}{ground,} shimmering brightly in the

 wintry \textcolor{BurntOrange}{sun.} Down the centre of Baker Street it had been ploughed

 into a brown crumbly band by the traffic, but at either side and

 on the heaped-up edges of the foot-paths it still lay as \textcolor{BurntOrange}{white} as

 when it \textcolor{red}{fell.} The grey \textcolor{green}{pavement} had been \textcolor{green}{cleaned} and scraped, but

 was still dangerously slippery, so that there were fewer

 \textcolor{blue}{passengers} than \textcolor{green}{usual.} Indeed, from the direction of the

 \textcolor{green}{Metropolitan} Station no one was coming \textcolor{green}{save} the single \textcolor{green}{gentleman}

 whose eccentric conduct had drawn my \textcolor{green}{attention.}



 He was a man of about fifty, tall, portly, and imposing, with a

 massive, \textcolor{green}{strongly} \textcolor{green}{marked} face and a commanding figure. He was

 dressed in a sombre yet rich style, in \textcolor{red}{black} frock-coat, shining

 hat, neat brown gaiters, and well-cut pearl-grey trousers. Yet

 his \textcolor{green}{actions} were in \textcolor{red}{absurd} contrast to the \textcolor{green}{dignity} of his dress

 and \textcolor{green}{features,} for he was running hard, with \textcolor{blue}{occasional} little

 springs, such as a \textcolor{red}{weary} man gives who is little accustomed to

 set any \textcolor{red}{tax} upon his legs. As he ran he jerked his hands up and

 down, waggled his head, and writhed his face into the most

 \textcolor{green}{extraordinary} contortions.



 "What on earth can be the matter with him?" I asked. "He is

 looking up at the numbers of the houses."



 "I believe that he is coming here," said Holmes, rubbing his

 hands.



 "Here?"



 "Yes; I rather think he is coming to \textcolor{green}{consult} me professionally. I

 think that I recognise the \textcolor{red}{symptoms.} Ha! did I not tell you?" As

 he \textcolor{red}{spoke,} the man, puffing and blowing, rushed at our door and

 \textcolor{green}{pulled} at our bell until the whole house resounded with the

 clanging.



 A few moments later he was in our room, still puffing, still

 gesticulating, but with so fixed a look of \textcolor{red}{grief} and \textcolor{red}{despair} in

 his eyes that our \textcolor{BurntOrange}{smiles} were turned in an instant to \textcolor{BurntOrange}{horror} and

 \textcolor{red}{pity.} For a while he could not get his \textcolor{green}{words} out, but swayed his

 body and plucked at his hair like one who has been driven to the

 extreme limits of his \textcolor{green}{reason.} Then, \textcolor{blue}{suddenly} springing to his

 feet, he beat his head against the wall with such \textcolor{red}{force} that we

 both rushed upon him and tore him away to the centre of the room.

 Sherlock Holmes pushed him down into the easy-chair and, sitting

 beside him, patted his hand and chatted with him in the easy,

 \textcolor{green}{soothing} tones which he knew so well how to \textcolor{green}{employ.}



 "You have come to me to tell your story, have you not?" said he.

 "You are \textcolor{red}{fatigued} with your \textcolor{blue}{haste.} \textcolor{BurntOrange}{Pray} \textcolor{BurntOrange}{wait} until you have

 recovered yourself, and then I shall be most \textcolor{BurntOrange}{happy} to look into

 any little \textcolor{red}{problem} which you may \textcolor{blue}{submit} to me."



 The man sat for a minute or more with a heaving chest, \textcolor{red}{fighting}

 against his emotion. Then he passed his handkerchief over his

 brow, set his lips tight, and turned his face towards us.



 "No \textcolor{BurntOrange}{doubt} you think me \textcolor{red}{mad?"} said he.



 "I see that you have had some great trouble," responded Holmes.



 \textcolor{BurntOrange}{"God} knows I have!--a trouble which is enough to \textcolor{red}{unseat} my

 \textcolor{green}{reason,} so \textcolor{blue}{sudden} and so \textcolor{red}{terrible} is it. \textcolor{BurntOrange}{Public} \textcolor{red}{disgrace} I might

 have faced, although I am a man whose character has never yet

 borne a \textcolor{red}{stain.} Private \textcolor{red}{affliction} also is the lot of every man;

 but the two coming together, and in so \textcolor{red}{frightful} a form, have

 been enough to shake my very soul. Besides, it is not I alone.

 The very \textcolor{green}{noblest} in the \textcolor{green}{land} may \textcolor{red}{suffer} unless some way be \textcolor{green}{found}

 out of this \textcolor{red}{horrible} affair."



 \textcolor{BurntOrange}{"Pray} compose yourself, \textcolor{green}{sir,"} said Holmes, "and let me have a

 clear \textcolor{green}{account} of who you are and what it is that has befallen

 you."



 "My name," answered our \textcolor{BurntOrange}{visitor,} "is probably \textcolor{green}{familiar} to your

 ears. I am Alexander Holder, of the banking firm of Holder &

 Stevenson, of Threadneedle Street."



 The name was indeed well known to us as belonging to the senior

 \textcolor{green}{partner} in the second largest private banking concern in the City

 of London. What could have \textcolor{blue}{happened,} then, to bring one of the

 foremost \textcolor{green}{citizens} of London to this most pitiable pass? We

 \textcolor{BurntOrange}{waited,} all \textcolor{BurntOrange}{curiosity,} until with another \textcolor{green}{effort} he braced

 himself to tell his story.



 "I feel that \textcolor{blue}{time} is of value," said he; "that is why I hastened

 here when the \textcolor{BurntOrange}{police} \textcolor{green}{inspector} \textcolor{green}{suggested} that I should secure

 your \textcolor{green}{co-operation.} I came to Baker Street by the Underground and

 \textcolor{blue}{hurried} from there on foot, for the \textcolor{green}{cabs} go slowly through this

 snow. That is why I was so out of breath, for I am a man who

 takes very little exercise. I feel better now, and I will put the

 \textcolor{green}{facts} before you as \textcolor{blue}{shortly} and yet as clearly as I can.



 "It is, of course, well known to you that in a \textcolor{BurntOrange}{successful} banking

 business as much depends upon our being able to find remunerative

 investments for our funds as upon our \textcolor{green}{increasing} our connection

 and the number of our depositors. One of our most lucrative means

 of laying out \textcolor{BurntOrange}{money} is in the \textcolor{green}{shape} of loans, where the security

 is unimpeachable. We have done a \textcolor{BurntOrange}{good} \textcolor{BurntOrange}{deal} in this direction

 during the last few years, and there are many \textcolor{green}{noble} families to

 whom we have \textcolor{green}{advanced} large sums upon the security of their

 pictures, \textcolor{green}{libraries,} or plate.



 "Yesterday morning I was seated in my office at the \textcolor{green}{bank} when a

 card was brought in to me by one of the clerks. I \textcolor{blue}{started} when I

 saw the name, for it was that of none other than--well, perhaps

 even to you I had better say no more than that it was a name

 which is a \textcolor{green}{household} \textcolor{green}{word} all over the earth--one of the highest,

 \textcolor{green}{noblest,} most \textcolor{BurntOrange}{exalted} names in England. I was \textcolor{red}{overwhelmed} by the

 honour and \textcolor{blue}{attempted,} when he entered, to say so, but he \textcolor{red}{plunged}

 at once into business with the air of a man who wishes to \textcolor{blue}{hurry}

 quickly through a disagreeable \textcolor{green}{task.}



 "'Mr. Holder,' said he, 'I have been \textcolor{green}{informed} that you are in the

 habit of \textcolor{BurntOrange}{advancing} \textcolor{BurntOrange}{money.'}



 "'The firm does so when the security is \textcolor{BurntOrange}{good.'} I answered.



 "'It is absolutely \textcolor{green}{essential} to me,' said he, 'that I should have

 50,000 \textcolor{red}{pounds} at once. I could, of course, borrow so \textcolor{red}{trifling} a

 sum ten \textcolor{blue}{times} over from my \textcolor{green}{friends,} but I much \textcolor{green}{prefer} to make it

 a matter of business and to carry out that business myself. In my

 position you can \textcolor{green}{readily} understand that it is \textcolor{red}{unwise} to place

 one's self under obligations.'



 "'For how \textcolor{blue}{long,} may I ask, do you want this sum?' I asked.



 "'Next Monday I have a large sum due to me, and I shall then most

 certainly \textcolor{BurntOrange}{repay} what you \textcolor{BurntOrange}{advance,} with whatever \textcolor{green}{interest} you

 think it right to charge. But it is very \textcolor{green}{essential} to me that the

 \textcolor{BurntOrange}{money} should be paid at once.'



 "'I should be \textcolor{BurntOrange}{happy} to \textcolor{BurntOrange}{advance} it without further parley from my

 own private purse,' said I, 'were it not that the strain would be

 rather more than it could \textcolor{red}{bear.} If, on the other hand, I am to do

 it in the name of the firm, then in \textcolor{green}{justice} to my \textcolor{green}{partner} I must

 insist that, even in your \textcolor{red}{case,} every businesslike \textcolor{green}{precaution}

 should be taken.'



 "'I should much \textcolor{green}{prefer} to have it so,' said he, raising up a

 square, \textcolor{red}{black} morocco \textcolor{red}{case} which he had laid beside his chair.

 'You have \textcolor{green}{doubtless} heard of the Beryl Coronet?'



 "'One of the most \textcolor{BurntOrange}{precious} \textcolor{BurntOrange}{public} \textcolor{red}{possessions} of the empire,'

 said I.



 "'Precisely.' He opened the \textcolor{red}{case,} and there, imbedded in soft,

 flesh-coloured \textcolor{green}{velvet,} lay the \textcolor{BurntOrange}{magnificent} piece of jewellery

 which he had named. 'There are thirty-nine enormous beryls,' said

 he, 'and the price of the \textcolor{green}{gold} \textcolor{red}{chasing} is \textcolor{red}{incalculable.} The

 lowest estimate would put the \textcolor{green}{worth} of the coronet at double the

 sum which I have asked. I am \textcolor{BurntOrange}{prepared} to \textcolor{BurntOrange}{leave} it with you as my

 security.'



 "I took the \textcolor{BurntOrange}{precious} \textcolor{red}{case} into my hands and looked in some

 \textcolor{red}{perplexity} from it to my \textcolor{green}{illustrious} client.



 "'You \textcolor{BurntOrange}{doubt} its value?' he asked.



 "'Not at all. I only \textcolor{BurntOrange}{doubt--'}



 "'The propriety of my \textcolor{BurntOrange}{leaving} it. You may set your mind at \textcolor{green}{rest}

 about that. I should not dream of doing so were it not absolutely

 certain that I should be able in four days to reclaim it. It is a

 pure matter of form. Is the security sufficient?'



 "'Ample.'



 "'You understand, Mr. Holder, that I am giving you a strong \textcolor{green}{proof}

 of the \textcolor{BurntOrange}{confidence} which I have in you, \textcolor{green}{founded} upon all that I

 have heard of you. I rely upon you not only to be \textcolor{BurntOrange}{discreet} and to

 refrain from all \textcolor{red}{gossip} upon the matter but, above all, to

 \textcolor{green}{preserve} this coronet with every possible \textcolor{green}{precaution} because I

 need not say that a great \textcolor{BurntOrange}{public} \textcolor{red}{scandal} would be caused if any

 \textcolor{red}{harm} were to \textcolor{red}{befall} it. Any \textcolor{red}{injury} to it would be almost as

 serious as its complete \textcolor{red}{loss,} for there are no beryls in the

 world to match these, and it would be \textcolor{red}{impossible} to replace them.

 I \textcolor{BurntOrange}{leave} it with you, however, with every \textcolor{BurntOrange}{confidence,} and I shall

 call for it in person on Monday morning.'



 "Seeing that my client was \textcolor{BurntOrange}{anxious} to \textcolor{BurntOrange}{leave,} I said no more but,

 calling for my \textcolor{green}{cashier,} I ordered him to \textcolor{BurntOrange}{pay} over fifty 1000

 \textcolor{red}{pound} notes. When I was alone once more, however, with the

 \textcolor{BurntOrange}{precious} \textcolor{red}{case} \textcolor{red}{lying} upon the table in front of me, I could not

 but think with some misgivings of the \textcolor{green}{immense} responsibility

 which it entailed upon me. There could be no \textcolor{BurntOrange}{doubt} that, as it

 was a national \textcolor{red}{possession,} a \textcolor{red}{horrible} \textcolor{red}{scandal} would ensue if any

 \textcolor{red}{misfortune} should occur to it. I already \textcolor{red}{regretted} having ever

 consented to take charge of it. However, it was too \textcolor{red}{late} to alter

 the matter now, so I locked it up in my private \textcolor{green}{safe} and turned

 once more to my work.



 "When evening came I felt that it would be an imprudence to \textcolor{BurntOrange}{leave}

 so \textcolor{BurntOrange}{precious} a thing in the office behind me. \textcolor{green}{Bankers'} \textcolor{green}{safes} had

 been \textcolor{red}{forced} before now, and why should not mine be? If so, how

 \textcolor{red}{terrible} would be the position in which I should find myself! I

 determined, therefore, that for the next few days I would always

 carry the \textcolor{red}{case} \textcolor{red}{backward} and \textcolor{green}{forward} with me, so that it might

 never be really out of my reach. With this intention, I called a

 \textcolor{green}{cab} and drove out to my house at Streatham, carrying the jewel

 with me. I did not breathe \textcolor{green}{freely} until I had taken it upstairs

 and locked it in the bureau of my dressing-room.



 "And now a \textcolor{green}{word} as to my \textcolor{green}{household,} Mr. Holmes, for I wish you to

 thoroughly understand the situation. My groom and my page sleep

 out of the house, and may be set aside altogether. I have three

 maid-servants who have been with me a number of years and whose

 \textcolor{green}{absolute} \textcolor{green}{reliability} is quite above \textcolor{red}{suspicion.} Another, Lucy

 Parr, the second waiting-maid, has only been in my service a few

 months. She came with an \textcolor{green}{excellent} character, however, and has

 always given me satisfaction. She is a very \textcolor{BurntOrange}{pretty} girl and has

 attracted \textcolor{green}{admirers} who have occasionally hung about the place.

 That is the only \textcolor{red}{drawback} which we have \textcolor{green}{found} to her, but we

 believe her to be a thoroughly \textcolor{BurntOrange}{good} girl in every way.



 "So much for the \textcolor{BurntOrange}{servants.} My family itself is so \textcolor{red}{small} that it

 will not take me \textcolor{blue}{long} to describe it. I am a \textcolor{red}{widower} and have an

 only son, Arthur. He has been a \textcolor{red}{disappointment} to me, Mr.

 Holmes--a \textcolor{red}{grievous} \textcolor{red}{disappointment.} I have no \textcolor{BurntOrange}{doubt} that I am

 myself to \textcolor{red}{blame.} People tell me that I have \textcolor{red}{spoiled} him. Very

 likely I have. When my \textcolor{green}{dear} wife \textcolor{red}{died} I felt that he was all I

 had to \textcolor{green}{love.} I could not \textcolor{red}{bear} to see the \textcolor{BurntOrange}{smile} \textcolor{red}{fade} even for a

 moment from his face. I have never \textcolor{red}{denied} him a wish. Perhaps it

 would have been better for both of us had I been sterner, but I

 meant it for the best.



 "It was naturally my intention that he should \textcolor{BurntOrange}{succeed} me in my

 business, but he was not of a business turn. He was \textcolor{BurntOrange}{wild,}

 wayward, and, to speak the \textcolor{green}{truth,} I could not \textcolor{green}{trust} him in the

 handling of large sums of \textcolor{BurntOrange}{money.} When he was \textcolor{BurntOrange}{young} he became a

 member of an \textcolor{green}{aristocratic} club, and there, having \textcolor{green}{charming}

 manners, he was soon the \textcolor{BurntOrange}{intimate} of a number of men with \textcolor{blue}{long}

 purses and expensive habits. He \textcolor{green}{learned} to play \textcolor{red}{heavily} at cards

 and to squander \textcolor{BurntOrange}{money} on the turf, until he had again and again

 to come to me and implore me to give him an \textcolor{BurntOrange}{advance} upon his

 allowance, that he might settle his \textcolor{red}{debts} of honour. He tried

 more than once to \textcolor{blue}{break} away from the \textcolor{red}{dangerous} company which he

 was keeping, but each \textcolor{blue}{time} the \textcolor{BurntOrange}{influence} of his \textcolor{green}{friend,} \textcolor{green}{Sir}

 George Burnwell, was enough to draw him back again.



 "And, indeed, I could not wonder that such a man as \textcolor{green}{Sir} George

 Burnwell should \textcolor{BurntOrange}{gain} an \textcolor{BurntOrange}{influence} over him, for he has frequently

 brought him to my house, and I have \textcolor{green}{found} myself that I could

 hardly \textcolor{red}{resist} the \textcolor{green}{fascination} of his manner. He is older than

 Arthur, a man of the world to his finger-tips, one who had been

 everywhere, seen everything, a \textcolor{BurntOrange}{brilliant} talker, and a man of

 great \textcolor{green}{personal} \textcolor{green}{beauty.} Yet when I think of him in \textcolor{red}{cold} blood, far

 away from the glamour of his \textcolor{green}{presence,} I am \textcolor{BurntOrange}{convinced} from his

 cynical \textcolor{green}{speech} and the look which I have caught in his eyes that

 he is one who should be deeply \textcolor{red}{distrusted.} So I think, and so,

 too, thinks my little Mary, who has a woman's quick insight into

 character.



 "And now there is only she to be described. She is my niece; but

 when my \textcolor{green}{brother} \textcolor{red}{died} five years ago and left her alone in the

 world I adopted her, and have looked upon her ever since as my

 \textcolor{green}{daughter.} She is a sunbeam in my house--sweet, \textcolor{green}{loving,} \textcolor{green}{beautiful,}

 a \textcolor{BurntOrange}{wonderful} manager and housekeeper, yet as \textcolor{green}{tender} and \textcolor{BurntOrange}{quiet} and

 gentle as a woman could be. She is my right hand. I do not know

 what I could do without her. In only one matter has she ever gone

 against my wishes. Twice my \textcolor{red}{boy} has asked her to \textcolor{BurntOrange}{marry} him, for

 he \textcolor{green}{loves} her devotedly, but each \textcolor{blue}{time} she has \textcolor{red}{refused} him. I

 think that if anyone could have drawn him into the right path it

 would have been she, and that his \textcolor{BurntOrange}{marriage} might have \textcolor{red}{changed} his

 whole life; but now, alas! it is too late--forever too \textcolor{red}{late!}



 "Now, Mr. Holmes, you know the people who live under my roof, and

 I shall \textcolor{BurntOrange}{continue} with my \textcolor{red}{miserable} story.



 "When we were taking coffee in the drawing-room that night after

 \textcolor{green}{dinner,} I told Arthur and Mary my experience, and of the \textcolor{BurntOrange}{precious}

 \textcolor{BurntOrange}{treasure} which we had under our roof, \textcolor{red}{suppressing} only the name

 of my client. Lucy Parr, who had brought in the coffee, had, I am

 sure, left the room; but I cannot \textcolor{green}{swear} that the door was closed.

 Mary and Arthur were much \textcolor{BurntOrange}{interested} and wished to see the \textcolor{green}{famous}

 coronet, but I \textcolor{blue}{thought} it better not to disturb it.



 "'Where have you put it?' asked Arthur.



 "'In my own bureau.'



 "'Well, I \textcolor{BurntOrange}{hope} to \textcolor{BurntOrange}{goodness} the house \textcolor{blue}{won't} be burgled during the

 night.' said he.



 "'It is locked up,' I answered.



 "'Oh, any old key will fit that bureau. When I was a youngster I

 have opened it myself with the key of the box-room cupboard.'



 "He often had a \textcolor{BurntOrange}{wild} way of \textcolor{green}{talking,} so that I \textcolor{blue}{thought} little of

 what he said. He followed me to my room, however, that night with

 a very \textcolor{red}{grave} face.



 "'Look here, dad,' said he with his eyes cast down, 'can you let

 me have 200 \textcolor{red}{pounds?'}



 "'No, I cannot!' I answered sharply. 'I have been far too

 \textcolor{green}{generous} with you in \textcolor{BurntOrange}{money} matters.'



 "'You have been very \textcolor{green}{kind,'} said he, 'but I must have this \textcolor{BurntOrange}{money,}

 or else I can never \textcolor{green}{show} my face inside the club again.'



 "'And a very \textcolor{BurntOrange}{good} thing, too!' I \textcolor{red}{cried.}



 "'Yes, but you would not have me \textcolor{BurntOrange}{leave} it a dishonoured man,'

 said he. 'I could not \textcolor{red}{bear} the \textcolor{red}{disgrace.} I must raise the \textcolor{BurntOrange}{money}

 in some way, and if you will not let me have it, then I must try

 other means.'



 "I was very \textcolor{red}{angry,} for this was the third \textcolor{red}{demand} during the

 month. 'You shall not have a farthing from me,' I \textcolor{red}{cried,} on which

 he bowed and left the room without another \textcolor{green}{word.}



 "When he was gone I unlocked my bureau, made sure that my

 \textcolor{BurntOrange}{treasure} was \textcolor{green}{safe,} and locked it again. Then I \textcolor{blue}{started} to go

 round the house to see that all was secure--a duty which I

 usually \textcolor{BurntOrange}{leave} to Mary but which I \textcolor{blue}{thought} it well to perform

 myself that night. As I came down the stairs I saw Mary herself

 at the side window of the hall, which she closed and fastened as

 I approached.



 "'Tell me, dad,' said she, looking, I \textcolor{blue}{thought,} a little

 \textcolor{red}{disturbed,} 'did you give Lucy, the maid, \textcolor{BurntOrange}{leave} to go out

 to-night?'



 "'Certainly not.'



 "'She came in just now by the back door. I have no \textcolor{BurntOrange}{doubt} that she

 has only been to the side \textcolor{green}{gate} to see someone, but I think that

 it is hardly \textcolor{green}{safe} and should be stopped.'



 "'You must speak to her in the morning, or I will if you \textcolor{green}{prefer}

 it. Are you sure that everything is fastened?'



 "'Quite sure, dad.'



 "'Then, good-night.' I \textcolor{BurntOrange}{kissed} her and went up to my bedroom

 again, where I was soon asleep.



 "I am endeavouring to tell you everything, Mr. Holmes, which may

 have any bearing upon the \textcolor{red}{case,} but I \textcolor{red}{beg} that you will \textcolor{green}{question}

 me upon any point which I do not make clear."



 "On the \textcolor{red}{contrary,} your \textcolor{green}{statement} is \textcolor{blue}{singularly} lucid."



 "I come to a part of my story now in which I should wish to be

 particularly so. I am not a very heavy sleeper, and the \textcolor{BurntOrange}{anxiety}

 in my mind tended, no \textcolor{BurntOrange}{doubt,} to make me even less so than \textcolor{green}{usual.}

 About two in the morning, then, I was awakened by some sound in

 the house. It had ceased ere I was wide awake, but it had left an

 \textcolor{green}{impression} behind it as though a window had gently closed

 somewhere. I lay listening with all my ears. \textcolor{blue}{Suddenly,} to my

 \textcolor{BurntOrange}{horror,} there was a distinct sound of footsteps moving softly in

 the next room. I \textcolor{BurntOrange}{slipped} out of bed, all palpitating with \textcolor{red}{fear,}

 and peeped round the corner of my dressing-room door.



 "'Arthur!' I \textcolor{BurntOrange}{screamed,} 'you \textcolor{red}{villain!} you \textcolor{BurntOrange}{thief!} How \textcolor{BurntOrange}{dare} you

 touch that coronet?'



 "The gas was half up, as I had left it, and my \textcolor{red}{unhappy} \textcolor{red}{boy,}

 dressed only in his shirt and trousers, was standing beside the

 light, holding the coronet in his hands. He appeared to be

 \textcolor{red}{wrenching} at it, or bending it with all his \textcolor{green}{strength.} At my \textcolor{red}{cry}

 he dropped it from his grasp and turned as pale as \textcolor{BurntOrange}{death.} I

 snatched it up and examined it. One of the \textcolor{green}{gold} corners, with

 three of the beryls in it, was missing.



 "'You blackguard!' I \textcolor{BurntOrange}{shouted,} beside myself with \textcolor{red}{rage.} 'You have

 \textcolor{red}{destroyed} it! You have dishonoured me forever! Where are the

 jewels which you have \textcolor{red}{stolen?'}



 \textcolor{red}{"'Stolen!'} he \textcolor{red}{cried.}



 "'Yes, \textcolor{BurntOrange}{thief!'} I roared, shaking him by the \textcolor{green}{shoulder.}



 "'There are none missing. There cannot be any missing,' said he.



 "'There are three missing. And you know where they are. Must I

 call you a \textcolor{red}{liar} as well as a \textcolor{BurntOrange}{thief?} Did I not see you trying to

 tear off another piece?'



 "'You have called me names enough,' said he, 'I will not stand it

 any longer. I shall not say another \textcolor{green}{word} about this business,

 since you have \textcolor{green}{chosen} to \textcolor{BurntOrange}{insult} me. I will \textcolor{BurntOrange}{leave} your house in

 the morning and make my own way in the world.'



 "'You shall \textcolor{BurntOrange}{leave} it in the hands of the \textcolor{BurntOrange}{police!'} I \textcolor{red}{cried}

 half-mad with \textcolor{red}{grief} and \textcolor{red}{rage.} 'I shall have this matter probed to

 the \textcolor{red}{bottom.'}



 "'You shall \textcolor{green}{learn} nothing from me,' said he with a \textcolor{BurntOrange}{passion} such

 as I should not have \textcolor{blue}{thought} was in his nature. 'If you choose to

 call the \textcolor{BurntOrange}{police,} let the \textcolor{BurntOrange}{police} find what they can.'



 "By this \textcolor{blue}{time} the whole house was astir, for I had raised my

 voice in my \textcolor{red}{anger.} Mary was the first to rush into my room, and,

 at the sight of the coronet and of Arthur's face, she read the

 whole story and, with a \textcolor{BurntOrange}{scream,} \textcolor{red}{fell} down \textcolor{BurntOrange}{senseless} on the

 \textcolor{green}{ground.} I sent the house-maid for the \textcolor{BurntOrange}{police} and put the

 \textcolor{blue}{investigation} into their hands at once. When the \textcolor{green}{inspector} and a

 \textcolor{green}{constable} entered the house, Arthur, who had stood sullenly with

 his arms folded, asked me whether it was my intention to charge

 him with \textcolor{red}{theft.} I answered that it had ceased to be a private

 matter, but had become a \textcolor{BurntOrange}{public} one, since the \textcolor{red}{ruined} coronet was

 national property. I was determined that the \textcolor{green}{law} should have its

 way in everything.



 "'At least,' said he, 'you will not have me \textcolor{red}{arrested} at once. It

 would be to your \textcolor{green}{advantage} as well as mine if I might \textcolor{BurntOrange}{leave} the

 house for five minutes.'



 "'That you may get away, or perhaps that you may \textcolor{red}{conceal} what you

 have \textcolor{red}{stolen,'} said I. And then, realising the \textcolor{BurntOrange}{dreadful} position

 in which I was placed, I implored him to remember that not only

 my honour but that of one who was far greater than I was at

 stake; and that he \textcolor{BurntOrange}{threatened} to raise a \textcolor{red}{scandal} which would

 convulse the \textcolor{green}{nation.} He might avert it all if he would but tell

 me what he had done with the three missing \textcolor{red}{stones.}



 "'You may as well face the matter,' said I; 'you have been caught

 in the act, and no \textcolor{BurntOrange}{confession} could make your \textcolor{red}{guilt} more \textcolor{red}{heinous.}

 If you but make such \textcolor{green}{reparation} as is in your power, by telling

 us where the beryls are, all shall be \textcolor{green}{forgiven} and \textcolor{red}{forgotten.'}



 "'Keep your forgiveness for those who ask for it,' he answered,

 turning away from me with a \textcolor{red}{sneer.} I saw that he was too hardened

 for any \textcolor{green}{words} of mine to \textcolor{BurntOrange}{influence} him. There was but one way for

 it. I called in the \textcolor{green}{inspector} and gave him into \textcolor{green}{custody.} A search

 was made at once not only of his person but of his room and of

 every portion of the house where he could possibly have \textcolor{red}{concealed}

 the \textcolor{green}{gems;} but no trace of them could be \textcolor{green}{found,} nor would the

 \textcolor{red}{wretched} \textcolor{red}{boy} open his \textcolor{blue}{mouth} for all our persuasions and our

 \textcolor{red}{threats.} This morning he was \textcolor{red}{removed} to a cell, and I, after

 going through all the \textcolor{BurntOrange}{police} \textcolor{green}{formalities,} have \textcolor{blue}{hurried} round to

 you to implore you to use your skill in unravelling the matter.

 The \textcolor{BurntOrange}{police} have openly \textcolor{BurntOrange}{confessed} that they can at \textcolor{BurntOrange}{present} make

 nothing of it. You may go to any expense which you think

 necessary. I have already \textcolor{green}{offered} a \textcolor{BurntOrange}{reward} of 1000 \textcolor{red}{pounds.} My

 \textcolor{BurntOrange}{God,} what shall I do! I have \textcolor{BurntOrange}{lost} my honour, my \textcolor{green}{gems,} and my son

 in one night. Oh, what shall I do!"



 He put a hand on either side of his head and \textcolor{green}{rocked} himself to

 and fro, \textcolor{red}{droning} to himself like a \textcolor{BurntOrange}{child} whose \textcolor{red}{grief} has got

 beyond \textcolor{green}{words.}



 Sherlock Holmes sat silent for some few minutes, with his brows

 knitted and his eyes fixed upon the \textcolor{red}{fire.}



 "Do you receive much company?" he asked.



 "None \textcolor{green}{save} my \textcolor{green}{partner} with his family and an \textcolor{blue}{occasional} \textcolor{green}{friend} of

 Arthur's. \textcolor{green}{Sir} George Burnwell has been several \textcolor{blue}{times} lately. No

 one else, I think."



 "Do you go out much in society?"



 "Arthur does. Mary and I stay at home. We neither of us care for

 it."



 "That is unusual in a \textcolor{BurntOrange}{young} girl."



 "She is of a \textcolor{BurntOrange}{quiet} nature. Besides, she is not so very \textcolor{BurntOrange}{young.} She

 is four-and-twenty."



 "This matter, from what you say, seems to have been a \textcolor{BurntOrange}{shock} to

 her also."



 \textcolor{red}{"Terrible!} She is even more affected than I."



 "You have neither of you any \textcolor{BurntOrange}{doubt} as to your son's \textcolor{red}{guilt?"}



 "How can we have when I saw him with my own eyes with the coronet

 in his hands."



 "I hardly consider that a conclusive \textcolor{green}{proof.} Was the remainder of

 the coronet at all \textcolor{red}{injured?"}



 "Yes, it was twisted."



 "Do you not think, then, that he might have been trying to

 straighten it?"



 \textcolor{BurntOrange}{"God} \textcolor{BurntOrange}{bless} you! You are doing what you can for him and for me.

 But it is too heavy a \textcolor{green}{task.} What was he doing there at all? If

 his purpose were \textcolor{green}{innocent,} why did he not say so?"



 "Precisely. And if it were \textcolor{red}{guilty,} why did he not invent a \textcolor{red}{lie?}

 His silence appears to me to cut both ways. There are several

 singular points about the \textcolor{red}{case.} What did the \textcolor{BurntOrange}{police} think of the

 \textcolor{red}{noise} which awoke you from your sleep?"



 "They considered that it might be caused by Arthur's closing his

 bedroom door."



 "A likely story! As if a man bent on \textcolor{red}{felony} would \textcolor{BurntOrange}{slam} his door

 so as to wake a \textcolor{green}{household.} What did they say, then, of the

 disappearance of these \textcolor{green}{gems?"}



 "They are still sounding the planking and probing the furniture

 in the \textcolor{BurntOrange}{hope} of finding them."



 "Have they \textcolor{blue}{thought} of looking outside the house?"



 "Yes, they have \textcolor{green}{shown} \textcolor{green}{extraordinary} energy. The whole \textcolor{green}{garden} has

 already been minutely examined."



 "Now, my \textcolor{green}{dear} \textcolor{green}{sir,"} said Holmes, "is it not \textcolor{green}{obvious} to you now

 that this matter really \textcolor{red}{strikes} very much deeper than either you

 or the \textcolor{BurntOrange}{police} were at first inclined to think? It appeared to you

 to be a simple \textcolor{red}{case;} to me it seems exceedingly complex. Consider

 what is involved by your \textcolor{BurntOrange}{theory.} You suppose that your son came

 down from his bed, went, at great \textcolor{BurntOrange}{risk,} to your dressing-room,

 opened your bureau, took out your coronet, \textcolor{red}{broke} off by \textcolor{green}{main}

 \textcolor{red}{force} a \textcolor{red}{small} portion of it, went off to some other place,

 \textcolor{red}{concealed} three \textcolor{green}{gems} out of the thirty-nine, with such skill that

 nobody can find them, and then returned with the other thirty-six

 into the room in which he \textcolor{BurntOrange}{exposed} himself to the greatest \textcolor{red}{danger}

 of being discovered. I ask you now, is such a \textcolor{BurntOrange}{theory} \textcolor{green}{tenable?"}



 "But what other is there?" \textcolor{red}{cried} the \textcolor{green}{banker} with a gesture of

 \textcolor{red}{despair.} "If his motives were \textcolor{green}{innocent,} why does he not \textcolor{green}{explain}

 them?"



 "It is our \textcolor{green}{task} to find that out," replied Holmes; "so now, if

 you please, Mr. Holder, we will set off for Streatham together,

 and devote an hour to glancing a little more closely into

 details."



 My \textcolor{green}{friend} insisted upon my accompanying them in their \textcolor{BurntOrange}{expedition,}

 which I was \textcolor{BurntOrange}{eager} enough to do, for my \textcolor{BurntOrange}{curiosity} and \textcolor{BurntOrange}{sympathy}

 were deeply stirred by the story to which we had listened. I

 \textcolor{BurntOrange}{confess} that the \textcolor{red}{guilt} of the \textcolor{green}{banker's} son appeared to me to be

 as \textcolor{green}{obvious} as it did to his \textcolor{red}{unhappy} \textcolor{green}{father,} but still I had such

 \textcolor{BurntOrange}{faith} in Holmes' \textcolor{blue}{judgment} that I felt that there must be some

 \textcolor{green}{grounds} for \textcolor{BurntOrange}{hope} as \textcolor{blue}{long} as he was dissatisfied with the accepted

 explanation. He hardly \textcolor{red}{spoke} a \textcolor{green}{word} the whole way out to the

 southern suburb, but sat with his chin upon his breast and his

 hat drawn over his eyes, \textcolor{red}{sunk} in the deepest \textcolor{blue}{thought.} Our client

 appeared to have taken fresh heart at the little glimpse of \textcolor{BurntOrange}{hope}

 which had been \textcolor{BurntOrange}{presented} to him, and he even \textcolor{red}{broke} into a

 desultory chat with me over his business affairs. A short railway

 \textcolor{BurntOrange}{journey} and a shorter walk brought us to Fairbank, the \textcolor{green}{modest}

 residence of the great financier.



 Fairbank was a good-sized square house of \textcolor{BurntOrange}{white} \textcolor{red}{stone,} standing

 back a little from the road. A double carriage-sweep, with a

 snow-clad lawn, stretched down in front to two large \textcolor{green}{iron} \textcolor{green}{gates}

 which closed the entrance. On the right side was a \textcolor{red}{small} wooden

 thicket, which \textcolor{green}{led} into a narrow path between two neat hedges

 stretching from the road to the kitchen door, and forming the

 tradesmen's entrance. On the left ran a lane which \textcolor{green}{led} to the

 \textcolor{green}{stables,} and was not itself within the \textcolor{green}{grounds} at all, being a

 \textcolor{BurntOrange}{public,} though little used, thoroughfare. Holmes left us standing

 at the door and walked slowly all round the house, across the

 front, down the tradesmen's path, and so round by the \textcolor{green}{garden}

 behind into the \textcolor{green}{stable} lane. So \textcolor{blue}{long} was he that Mr. Holder and I

 went into the dining-room and \textcolor{BurntOrange}{waited} by the \textcolor{red}{fire} until he should

 return. We were sitting there in silence when the door opened and

 a \textcolor{BurntOrange}{young} lady came in. She was rather above the middle height,

 \textcolor{green}{slim,} with \textcolor{red}{dark} hair and eyes, which seemed the darker against

 the \textcolor{green}{absolute} pallor of her skin. I do not think that I have ever

 seen such \textcolor{red}{deadly} paleness in a woman's face. Her lips, too, were

 \textcolor{green}{bloodless,} but her eyes were \textcolor{green}{flushed} with \textcolor{red}{crying.} As she swept

 silently into the room she impressed me with a greater \textcolor{green}{sense} of

 \textcolor{red}{grief} than the \textcolor{green}{banker} had done in the morning, and it was the

 more \textcolor{red}{striking} in her as she was evidently a woman of strong

 character, with \textcolor{green}{immense} capacity for self-restraint. \textcolor{red}{Disregarding}

 my \textcolor{green}{presence,} she went straight to her uncle and passed her hand

 over his head with a \textcolor{BurntOrange}{sweet} womanly \textcolor{green}{caress.}



 "You have given orders that Arthur should be \textcolor{BurntOrange}{liberated,} have you

 not, dad?" she asked.



 "No, no, my girl, the matter must be probed to the \textcolor{red}{bottom."}



 "But I am so sure that he is \textcolor{green}{innocent.} You know what woman's

 instincts are. I know that he has done no \textcolor{red}{harm} and that you will

 be sorry for having acted so harshly."



 "Why is he silent, then, if he is \textcolor{green}{innocent?"}



 "Who knows? Perhaps because he was so \textcolor{red}{angry} that you should

 \textcolor{red}{suspect} him."



 "How could I help \textcolor{red}{suspecting} him, when I actually saw him with

 the coronet in his hand?"



 "Oh, but he had only picked it up to look at it. Oh, do, do take

 my \textcolor{green}{word} for it that he is \textcolor{green}{innocent.} Let the matter drop and say

 no more. It is so \textcolor{BurntOrange}{dreadful} to think of our \textcolor{green}{dear} Arthur in

 \textcolor{red}{prison!"}



 "I shall never let it drop until the \textcolor{green}{gems} are found--never, Mary!

 Your \textcolor{green}{affection} for Arthur \textcolor{red}{blinds} you as to the \textcolor{red}{awful} consequences

 to me. Far from \textcolor{green}{hushing} the thing up, I have brought a \textcolor{green}{gentleman}

 down from London to inquire more deeply into it."



 "This \textcolor{green}{gentleman?"} she asked, facing round to me.



 "No, his \textcolor{green}{friend.} He wished us to \textcolor{BurntOrange}{leave} him alone. He is round in

 the \textcolor{green}{stable} lane now."



 "The \textcolor{green}{stable} lane?" She raised her \textcolor{red}{dark} eyebrows. "What can he

 \textcolor{BurntOrange}{hope} to find there? Ah! this, I suppose, is he. I \textcolor{green}{trust,} \textcolor{green}{sir,}

 that you will \textcolor{BurntOrange}{succeed} in \textcolor{green}{proving,} what I feel sure is the \textcolor{green}{truth,}

 that my cousin Arthur is \textcolor{green}{innocent} of this \textcolor{red}{crime."}



 "I \textcolor{green}{fully} \textcolor{BurntOrange}{share} your opinion, and I \textcolor{green}{trust,} with you, that we may

 \textcolor{green}{prove} it," returned Holmes, going back to the mat to knock the

 snow from his shoes. "I believe I have the honour of addressing

 Miss Mary Holder. Might I ask you a \textcolor{green}{question} or two?"



 \textcolor{BurntOrange}{"Pray} do, \textcolor{green}{sir,} if it may help to clear this \textcolor{red}{horrible} affair up."



 "You heard nothing yourself last night?"



 "Nothing, until my uncle here began to speak loudly. I heard

 that, and I came down."



 "You shut up the windows and doors the night before. Did you

 fasten all the windows?"



 "Yes."



 "Were they all fastened this morning?"



 "Yes."



 "You have a maid who has a \textcolor{BurntOrange}{sweetheart?} I think that you remarked

 to your uncle last night that she had been out to see him?"



 "Yes, and she was the girl who \textcolor{BurntOrange}{waited} in the drawing-room, and

 who may have heard uncle's remarks about the coronet."



 "I see. You infer that she may have gone out to tell her

 \textcolor{BurntOrange}{sweetheart,} and that the two may have \textcolor{blue}{planned} the \textcolor{red}{robbery."}



 "But what is the \textcolor{BurntOrange}{good} of all these \textcolor{red}{vague} \textcolor{BurntOrange}{theories,"} \textcolor{red}{cried} the

 \textcolor{green}{banker} impatiently, "when I have told you that I saw Arthur with

 the coronet in his hands?"



 \textcolor{BurntOrange}{"Wait} a little, Mr. Holder. We must come back to that. About this

 girl, Miss Holder. You saw her return by the kitchen door, I

 presume?"



 "Yes; when I went to see if the door was fastened for the night I

 met her \textcolor{BurntOrange}{slipping} in. I saw the man, too, in the \textcolor{red}{gloom."}



 "Do you know him?"



 "Oh, yes! he is the green-grocer who brings our vegetables round.

 His name is Francis \textcolor{BurntOrange}{Prosper."}



 "He stood," said Holmes, "to the left of the door--that is to

 say, farther up the path than is necessary to reach the door?"



 "Yes, he did."



 "And he is a man with a wooden leg?"



 Something like \textcolor{red}{fear} sprang up in the \textcolor{BurntOrange}{young} lady's expressive

 \textcolor{red}{black} eyes. "Why, you are like a \textcolor{blue}{magician,"} said she. "How do you

 know that?" She \textcolor{BurntOrange}{smiled,} but there was no answering \textcolor{BurntOrange}{smile} in

 Holmes' thin, \textcolor{BurntOrange}{eager} face.



 "I should be very \textcolor{BurntOrange}{glad} now to go upstairs," said he. "I shall

 probably wish to go over the outside of the house again. Perhaps

 I had better take a look at the lower windows before I go up."



 He walked swiftly round from one to the other, pausing only at

 the large one which looked from the hall onto the \textcolor{green}{stable} lane.

 This he opened and made a very \textcolor{green}{careful} \textcolor{BurntOrange}{examination} of the sill

 with his \textcolor{BurntOrange}{powerful} magnifying lens. "Now we shall go upstairs,"

 said he at last.



 The \textcolor{green}{banker's} dressing-room was a plainly furnished little

 chamber, with a grey carpet, a large bureau, and a \textcolor{blue}{long} mirror.

 Holmes went to the bureau first and looked hard at the lock.



 "Which key was used to open it?" he asked.



 "That which my son himself indicated--that of the cupboard of the

 lumber-room."



 "Have you it here?"



 "That is it on the dressing-table."



 Sherlock Holmes took it up and opened the bureau.



 "It is a noiseless lock," said he. "It is no wonder that it did

 not wake you. This \textcolor{red}{case,} I presume, contains the coronet. We must

 have a look at it." He opened the \textcolor{red}{case,} and taking out the diadem

 he laid it upon the table. It was a \textcolor{BurntOrange}{magnificent} specimen of the

 jeweller's \textcolor{BurntOrange}{art,} and the thirty-six \textcolor{red}{stones} were the finest that I

 have ever seen. At one side of the coronet was a \textcolor{red}{cracked} edge,

 where a corner holding three \textcolor{green}{gems} had been \textcolor{red}{torn} away.



 "Now, Mr. Holder," said Holmes, "here is the corner which

 corresponds to that which has been so unfortunately \textcolor{BurntOrange}{lost.} Might I

 \textcolor{red}{beg} that you will \textcolor{blue}{break} it off."



 The \textcolor{green}{banker} recoiled in \textcolor{BurntOrange}{horror.} "I should not dream of trying,"

 said he.



 "Then I will." Holmes \textcolor{blue}{suddenly} bent his \textcolor{green}{strength} upon it, but

 without \textcolor{blue}{result.} "I feel it give a little," said he; "but, though

 I am exceptionally strong in the fingers, it would take me all my

 \textcolor{blue}{time} to \textcolor{blue}{break} it. An ordinary man could not do it. Now, what do

 you think would \textcolor{blue}{happen} if I did \textcolor{blue}{break} it, Mr. Holder? There would

 be a \textcolor{red}{noise} like a \textcolor{red}{pistol} \textcolor{BurntOrange}{shot.} Do you tell me that all this

 \textcolor{blue}{happened} within a few yards of your bed and that you heard

 nothing of it?"



 "I do not know what to think. It is all \textcolor{red}{dark} to me."



 "But perhaps it may \textcolor{BurntOrange}{grow} lighter as we go. What do you think,

 Miss Holder?"



 "I \textcolor{BurntOrange}{confess} that I still \textcolor{BurntOrange}{share} my uncle's \textcolor{red}{perplexity."}



 "Your son had no shoes or slippers on when you saw him?"



 "He had nothing on \textcolor{green}{save} only his trousers and shirt."



 "Thank you. We have certainly been favoured with \textcolor{green}{extraordinary}

 \textcolor{BurntOrange}{luck} during this \textcolor{BurntOrange}{inquiry,} and it will be entirely our own \textcolor{red}{fault}

 if we do not \textcolor{BurntOrange}{succeed} in clearing the matter up. With your

 \textcolor{green}{permission,} Mr. Holder, I shall now \textcolor{BurntOrange}{continue} my \textcolor{blue}{investigations}

 outside."



 He went alone, at his own request, for he \textcolor{green}{explained} that any

 unnecessary footmarks might make his \textcolor{green}{task} more \textcolor{red}{difficult.} For an

 hour or more he was at work, returning at last with his feet

 heavy with snow and his \textcolor{green}{features} as inscrutable as ever.



 "I think that I have seen now all that there is to see, Mr.

 Holder," said he; "I can \textcolor{BurntOrange}{serve} you best by returning to my

 rooms."



 "But the \textcolor{green}{gems,} Mr. Holmes. Where are they?"



 "I cannot tell."



 The \textcolor{green}{banker} wrung his hands. "I shall never see them again!" he

 \textcolor{red}{cried.} "And my son? You give me \textcolor{BurntOrange}{hopes?"}



 "My opinion is in no way altered."



 "Then, for \textcolor{BurntOrange}{God's} sake, what was this \textcolor{red}{dark} business which was

 acted in my house last night?"



 "If you can call upon me at my Baker Street rooms \textcolor{blue}{to-morrow}

 morning between nine and ten I shall be \textcolor{BurntOrange}{happy} to do what I can to

 make it clearer. I understand that you give me carte blanche to

 act for you, \textcolor{green}{provided} only that I get back the \textcolor{green}{gems,} and that you

 place no limit on the sum I may draw."



 "I would give my \textcolor{BurntOrange}{fortune} to have them back."



 "Very \textcolor{BurntOrange}{good.} I shall look into the matter between this and then.

 Good-bye; it is just possible that I may have to come over here

 again before evening."



 It was \textcolor{green}{obvious} to me that my \textcolor{green}{companion's} mind was now made up

 about the \textcolor{red}{case,} although what his conclusions were was more than

 I could even dimly imagine. Several \textcolor{blue}{times} during our homeward

 \textcolor{BurntOrange}{journey} I endeavoured to sound him upon the point, but he always

 \textcolor{BurntOrange}{glided} away to some other topic, until at last I gave it over in

 \textcolor{red}{despair.} It was not yet three when we \textcolor{green}{found} ourselves in our

 rooms once more. He \textcolor{blue}{hurried} to his chamber and was down again in

 a few minutes dressed as a common \textcolor{red}{loafer.} With his collar turned

 up, his shiny, seedy coat, his red cravat, and his \textcolor{red}{worn} boots, he

 was a \textcolor{BurntOrange}{perfect} sample of the class.



 "I think that this should do," said he, glancing into the glass

 above the fireplace. "I only wish that you could come with me,

 Watson, but I \textcolor{red}{fear} that it \textcolor{blue}{won't} do. I may be on the trail in

 this matter, or I may be following a will-o'-the-wisp, but I

 shall soon know which it is. I \textcolor{BurntOrange}{hope} that I may be back in a few

 hours." He cut a slice of beef from the joint upon the sideboard,

 sandwiched it between two rounds of bread, and thrusting this

 rude meal into his pocket he \textcolor{blue}{started} off upon his \textcolor{BurntOrange}{expedition.}



 I had just finished my tea when he returned, evidently in

 \textcolor{green}{excellent} \textcolor{green}{spirits,} swinging an old elastic-sided boot in his

 hand. He chucked it down into a corner and helped himself to a

 cup of tea.



 "I only looked in as I passed," said he. "I am going right on."



 "Where to?"



 "Oh, to the other side of the West End. It may be some \textcolor{blue}{time}

 before I get back. Don't \textcolor{BurntOrange}{wait} up for me in \textcolor{red}{case} I should be

 \textcolor{red}{late."}



 "How are you getting on?"



 "Oh, so so. Nothing to \textcolor{red}{complain} of. I have been out to Streatham

 since I saw you last, but I did not call at the house. It is a

 very \textcolor{BurntOrange}{sweet} little \textcolor{red}{problem,} and I would not have missed it for a

 \textcolor{BurntOrange}{good} \textcolor{BurntOrange}{deal.} However, I must not sit \textcolor{red}{gossiping} here, but must get

 these \textcolor{red}{disreputable} clothes off and return to my highly

 \textcolor{green}{respectable} self."



 I could see by his manner that he had stronger \textcolor{green}{reasons} for

 satisfaction than his \textcolor{green}{words} alone would imply. His eyes \textcolor{BurntOrange}{twinkled,}

 and there was even a touch of colour upon his sallow cheeks. He

 hastened upstairs, and a few minutes later I heard the \textcolor{BurntOrange}{slam} of

 the hall door, which told me that he was off once more upon his

 \textcolor{green}{congenial} hunt.



 I \textcolor{BurntOrange}{waited} until midnight, but there was no sign of his return, so

 I retired to my room. It was no uncommon thing for him to be away

 for days and nights on end when he was \textcolor{red}{hot} upon a scent, so that

 his \textcolor{red}{lateness} caused me no \textcolor{BurntOrange}{surprise.} I do not know at what hour he

 came in, but when I came down to \textcolor{green}{breakfast} in the morning there

 he was with a cup of coffee in one hand and the paper in the

 other, as fresh and trim as possible.



 "You will \textcolor{red}{excuse} my beginning without you, Watson," said he, "but

 you remember that our client has rather an early appointment this

 morning."



 "Why, it is after nine now," I answered. "I should not be

 \textcolor{blue}{surprised} if that were he. I \textcolor{blue}{thought} I heard a ring."



 It was, indeed, our \textcolor{green}{friend} the financier. I was \textcolor{BurntOrange}{shocked} by the

 \textcolor{red}{change} which had come over him, for his face which was naturally

 of a broad and massive mould, was now pinched and \textcolor{red}{fallen} in,

 while his hair seemed to me at least a shade whiter. He entered

 with a \textcolor{red}{weariness} and \textcolor{red}{lethargy} which was even more \textcolor{red}{painful} than

 his \textcolor{red}{violence} of the morning before, and he dropped \textcolor{red}{heavily} into

 the armchair which I pushed \textcolor{green}{forward} for him.



 "I do not know what I have done to be so severely tried," said

 he. "Only two days ago I was a \textcolor{BurntOrange}{happy} and \textcolor{green}{prosperous} man, without

 a care in the world. Now I am left to a \textcolor{red}{lonely} and dishonoured

 age. One \textcolor{red}{sorrow} comes close upon the \textcolor{red}{heels} of another. My niece,

 Mary, has \textcolor{red}{deserted} me."



 \textcolor{red}{"Deserted} you?"



 "Yes. Her bed this morning had not been slept in, her room was

 empty, and a note for me lay upon the hall table. I had said to

 her last night, in \textcolor{red}{sorrow} and not in \textcolor{red}{anger,} that if she had

 married my \textcolor{red}{boy} all might have been well with him. Perhaps it was

 \textcolor{red}{thoughtless} of me to say so. It is to that remark that she refers

 in this note:



 "'MY DEAREST UNCLE:--I feel that I have brought trouble upon you,

 and that if I had acted \textcolor{blue}{differently} this \textcolor{red}{terrible} \textcolor{red}{misfortune}

 might never have occurred. I cannot, with this \textcolor{blue}{thought} in my

 mind, ever again be \textcolor{BurntOrange}{happy} under your roof, and I feel that I must

 \textcolor{BurntOrange}{leave} you forever. Do not \textcolor{BurntOrange}{worry} about my future, for that is

 \textcolor{green}{provided} for; and, above all, do not search for me, for it will

 be \textcolor{red}{fruitless} labour and an ill-service to me. In life or in

 \textcolor{BurntOrange}{death,} I am ever your loving,--MARY.'



 "What could she mean by that note, Mr. Holmes? Do you think it

 points to \textcolor{red}{suicide?"}



 "No, no, nothing of the \textcolor{green}{kind.} It is perhaps the best possible

 \textcolor{green}{solution.} I \textcolor{green}{trust,} Mr. Holder, that you are nearing the end of

 your troubles."



 "Ha! You say so! You have heard something, Mr. Holmes; you have

 \textcolor{green}{learned} something! Where are the \textcolor{green}{gems?"}



 "You would not think 1000 \textcolor{red}{pounds} apiece an excessive sum for

 them?"



 "I would \textcolor{BurntOrange}{pay} ten."



 "That would be unnecessary. Three thousand will \textcolor{green}{cover} the matter.

 And there is a little \textcolor{BurntOrange}{reward,} I \textcolor{BurntOrange}{fancy.} Have you your check-book?

 Here is a pen. Better make it out for 4000 \textcolor{red}{pounds."}



 With a dazed face the \textcolor{green}{banker} made out the required check. Holmes

 walked over to his desk, took out a little triangular piece of

 \textcolor{green}{gold} with three \textcolor{green}{gems} in it, and threw it down upon the table.



 With a \textcolor{BurntOrange}{shriek} of \textcolor{green}{joy} our client clutched it up.



 "You have it!" he gasped. "I am \textcolor{green}{saved!} I am \textcolor{green}{saved!"}



 The reaction of \textcolor{green}{joy} was as \textcolor{BurntOrange}{passionate} as his \textcolor{red}{grief} had been, and

 he \textcolor{green}{hugged} his recovered \textcolor{green}{gems} to his bosom.



 "There is one other thing you owe, Mr. Holder," said Sherlock

 Holmes rather sternly.



 "Owe!" He caught up a pen. "Name the sum, and I will \textcolor{BurntOrange}{pay} it."



 "No, the \textcolor{red}{debt} is not to me. You owe a very \textcolor{BurntOrange}{humble} \textcolor{green}{apology} to that

 \textcolor{green}{noble} lad, your son, who has carried himself in this matter as I

 should be \textcolor{BurntOrange}{proud} to see my own son do, should I ever \textcolor{blue}{chance} to

 have one."



 "Then it was not Arthur who took them?"



 "I told you yesterday, and I repeat to-day, that it was not."



 "You are sure of it! Then let us \textcolor{blue}{hurry} to him at once to let him

 know that the \textcolor{green}{truth} is known."



 "He knows it already. When I had cleared it all up I had an

 interview with him, and finding that he would not tell me the

 story, I told it to him, on which he had to \textcolor{BurntOrange}{confess} that I was

 right and to add the very few details which were not yet quite

 clear to me. Your news of this morning, however, may open his

 lips."



 "For heaven's sake, tell me, then, what is this \textcolor{green}{extraordinary}

 \textcolor{blue}{mystery!"}



 "I will do so, and I will \textcolor{green}{show} you the steps by which I reached

 it. And let me say to you, first, that which it is hardest for me

 to say and for you to hear: there has been an understanding

 between \textcolor{green}{Sir} George Burnwell and your niece Mary. They have now

 \textcolor{red}{fled} together."



 "My Mary? \textcolor{red}{Impossible!"}



 "It is unfortunately more than possible; it is certain. Neither

 you nor your son knew the \textcolor{green}{true} character of this man when you

 admitted him into your family circle. He is one of the most

 \textcolor{red}{dangerous} men in England--a \textcolor{red}{ruined} \textcolor{BurntOrange}{gambler,} an absolutely

 \textcolor{red}{desperate} \textcolor{red}{villain,} a man without heart or \textcolor{green}{conscience.} Your niece

 knew nothing of such men. When he breathed his \textcolor{BurntOrange}{vows} to her, as he

 had done to a hundred before her, she flattered herself that she

 alone had touched his heart. The \textcolor{BurntOrange}{devil} knows best what he said,

 but at least she became his tool and was in the habit of seeing

 him nearly every evening."



 "I cannot, and I will not, believe it!" \textcolor{red}{cried} the \textcolor{green}{banker} with an

 ashen face.



 "I will tell you, then, what occurred in your house last night.

 Your niece, when you had, as she \textcolor{blue}{thought,} gone to your room,

 \textcolor{BurntOrange}{slipped} down and \textcolor{green}{talked} to her \textcolor{BurntOrange}{lover} through the window which

 \textcolor{green}{leads} into the \textcolor{green}{stable} lane. His footmarks had pressed right

 through the snow, so \textcolor{blue}{long} had he stood there. She told him of the

 coronet. His \textcolor{red}{wicked} \textcolor{BurntOrange}{lust} for \textcolor{green}{gold} kindled at the news, and he

 bent her to his will. I have no \textcolor{BurntOrange}{doubt} that she \textcolor{green}{loved} you, but

 there are women in whom the \textcolor{green}{love} of a \textcolor{BurntOrange}{lover} extinguishes all

 other \textcolor{green}{loves,} and I think that she must have been one. She had

 hardly listened to his \textcolor{green}{instructions} when she saw you coming

 downstairs, on which she closed the window rapidly and told you

 about one of the \textcolor{BurntOrange}{servants'} escapade with her wooden-legged \textcolor{BurntOrange}{lover,}

 which was all perfectly \textcolor{green}{true.}



 "Your \textcolor{red}{boy,} Arthur, went to bed after his interview with you but

 he slept \textcolor{red}{badly} on \textcolor{green}{account} of his \textcolor{BurntOrange}{uneasiness} about his club \textcolor{red}{debts.}

 In the middle of the night he heard a soft tread pass his door,

 so he rose and, looking out, was \textcolor{blue}{surprised} to see his cousin

 walking very \textcolor{blue}{stealthily} along the passage until she \textcolor{red}{disappeared}

 into your dressing-room. Petrified with \textcolor{BurntOrange}{astonishment,} the lad

 \textcolor{BurntOrange}{slipped} on some clothes and \textcolor{BurntOrange}{waited} there in the \textcolor{red}{dark} to see what

 would come of this strange affair. Presently she emerged from the

 room again, and in the light of the passage-lamp your son saw

 that she carried the \textcolor{BurntOrange}{precious} coronet in her hands. She passed

 down the stairs, and he, \textcolor{BurntOrange}{thrilling} with \textcolor{BurntOrange}{horror,} ran along and

 \textcolor{BurntOrange}{slipped} behind the curtain near your door, whence he could see

 what passed in the hall beneath. He saw her \textcolor{blue}{stealthily} open the

 window, hand out the coronet to someone in the \textcolor{red}{gloom,} and then

 closing it once more \textcolor{blue}{hurry} back to her room, passing quite close

 to where he stood hid behind the curtain.



 "As \textcolor{blue}{long} as she was on the scene he could not take any \textcolor{green}{action}

 without a \textcolor{red}{horrible} exposure of the woman whom he \textcolor{green}{loved.} But the

 instant that she was gone he realised how crushing a \textcolor{red}{misfortune}

 this would be for you, and how all-important it was to set it

 right. He rushed down, just as he was, in his bare feet, opened

 the window, sprang out into the snow, and ran down the lane,

 where he could see a \textcolor{red}{dark} figure in the moonlight. \textcolor{green}{Sir} George

 Burnwell tried to get away, but Arthur caught him, and there was

 a \textcolor{red}{struggle} between them, your lad tugging at one side of the

 coronet, and his \textcolor{BurntOrange}{opponent} at the other. In the scuffle, your son

 struck \textcolor{green}{Sir} George and cut him over the eye. Then something

 \textcolor{blue}{suddenly} snapped, and your son, finding that he had the coronet

 in his hands, rushed back, closed the window, ascended to your

 room, and had just observed that the coronet had been twisted in

 the \textcolor{red}{struggle} and was endeavouring to straighten it when you

 appeared upon the scene."



 "Is it possible?" gasped the \textcolor{green}{banker.}



 "You then roused his \textcolor{red}{anger} by calling him names at a moment when

 he felt that he had \textcolor{BurntOrange}{deserved} your warmest thanks. He could not

 \textcolor{green}{explain} the \textcolor{green}{true} state of affairs without betraying one who

 certainly \textcolor{BurntOrange}{deserved} little enough consideration at his hands. He

 took the more chivalrous view, however, and \textcolor{green}{preserved} her

 \textcolor{green}{secret."}



 "And that was why she \textcolor{BurntOrange}{shrieked} and fainted when she saw the

 coronet," \textcolor{red}{cried} Mr. Holder. "Oh, my \textcolor{BurntOrange}{God!} what a \textcolor{red}{blind} \textcolor{red}{fool} I have

 been! And his asking to be allowed to go out for five minutes!

 The \textcolor{green}{dear} \textcolor{green}{fellow} wanted to see if the missing piece were at the

 scene of the \textcolor{red}{struggle.} How \textcolor{red}{cruelly} I have misjudged him!"



 "When I \textcolor{blue}{arrived} at the house," continued Holmes, "I at once went

 very \textcolor{green}{carefully} round it to observe if there were any traces in

 the snow which might help me. I knew that none had \textcolor{red}{fallen} since

 the evening before, and also that there had been a strong frost

 to \textcolor{green}{preserve} \textcolor{green}{impressions.} I passed along the tradesmen's path, but

 \textcolor{green}{found} it all trampled down and indistinguishable. Just beyond it,

 however, at the far side of the kitchen door, a woman had stood

 and \textcolor{green}{talked} with a man, whose round \textcolor{green}{impressions} on one side \textcolor{green}{showed}

 that he had a wooden leg. I could even tell that they had been

 \textcolor{red}{disturbed,} for the woman had run back swiftly to the door, as was

 \textcolor{green}{shown} by the deep toe and light \textcolor{red}{heel} marks, while Wooden-leg had

 \textcolor{BurntOrange}{waited} a little, and then had gone away. I \textcolor{blue}{thought} at the \textcolor{blue}{time}

 that this might be the maid and her \textcolor{BurntOrange}{sweetheart,} of whom you had

 already spoken to me, and \textcolor{BurntOrange}{inquiry} \textcolor{green}{showed} it was so. I passed

 round the \textcolor{green}{garden} without seeing anything more than random \textcolor{blue}{tracks,}

 which I took to be the \textcolor{BurntOrange}{police;} but when I got into the \textcolor{green}{stable}

 lane a very \textcolor{blue}{long} and complex story was written in the snow in

 front of me.



 "There was a double line of \textcolor{blue}{tracks} of a booted man, and a second

 double line which I saw with \textcolor{BurntOrange}{delight} belonged to a man with naked

 feet. I was at once \textcolor{BurntOrange}{convinced} from what you had told me that the

 latter was your son. The first had walked both ways, but the

 other had run swiftly, and as his tread was \textcolor{green}{marked} in places over

 the \textcolor{red}{depression} of the boot, it was \textcolor{green}{obvious} that he had passed

 after the other. I followed them up and \textcolor{green}{found} they \textcolor{green}{led} to the

 hall window, where Boots had \textcolor{red}{worn} all the snow away while

 \textcolor{BurntOrange}{waiting.} Then I walked to the other end, which was a hundred

 yards or more down the lane. I saw where Boots had faced round,

 where the snow was cut up as though there had been a \textcolor{red}{struggle,}

 and, \textcolor{BurntOrange}{finally,} where a few drops of blood had \textcolor{red}{fallen,} to \textcolor{green}{show} me

 that I was not \textcolor{red}{mistaken.} Boots had then run down the lane, and

 another little \textcolor{red}{smudge} of blood \textcolor{green}{showed} that it was he who had been

 \textcolor{red}{hurt.} When he came to the highroad at the other end, I \textcolor{green}{found} that

 the \textcolor{green}{pavement} had been cleared, so there was an end to that \textcolor{blue}{clue.}



 "On entering the house, however, I examined, as you remember, the

 sill and \textcolor{green}{framework} of the hall window with my lens, and I could

 at once see that someone had passed out. I could distinguish the

 outline of an instep where the wet foot had been placed in coming

 in. I was then beginning to be able to form an opinion as to what

 had occurred. A man had \textcolor{BurntOrange}{waited} outside the window; someone had

 brought the \textcolor{green}{gems;} the \textcolor{green}{deed} had been overseen by your son; he had

 pursued the \textcolor{BurntOrange}{thief;} had \textcolor{red}{struggled} with him; they had each tugged

 at the coronet, their \textcolor{green}{united} \textcolor{green}{strength} causing \textcolor{red}{injuries} which

 neither alone could have effected. He had returned with the

 prize, but had left a fragment in the grasp of his \textcolor{BurntOrange}{opponent.} So

 far I was clear. The \textcolor{green}{question} now was, who was the man and who

 was it brought him the coronet?



 "It is an old \textcolor{green}{maxim} of mine that when you have excluded the

 \textcolor{red}{impossible,} whatever \textcolor{BurntOrange}{remains,} however improbable, must be the

 \textcolor{green}{truth.} Now, I knew that it was not you who had brought it down,

 so there only remained your niece and the maids. But if it were

 the maids, why should your son allow himself to be accused in

 their place? There could be no possible \textcolor{green}{reason.} As he \textcolor{green}{loved} his

 cousin, however, there was an \textcolor{green}{excellent} explanation why he should

 \textcolor{green}{retain} her secret--the more so as the \textcolor{green}{secret} was a \textcolor{red}{disgraceful}

 one. When I remembered that you had seen her at that window, and

 how she had fainted on seeing the coronet again, my \textcolor{blue}{conjecture}

 became a \textcolor{green}{certainty.}



 "And who could it be who was her \textcolor{green}{confederate?} A \textcolor{BurntOrange}{lover} evidently,

 for who else could outweigh the \textcolor{green}{love} and \textcolor{green}{gratitude} which she must

 feel to you? I knew that you went out little, and that your

 circle of \textcolor{green}{friends} was a very \textcolor{red}{limited} one. But among them was \textcolor{green}{Sir}

 George Burnwell. I had heard of him before as being a man of \textcolor{red}{evil}

 reputation among women. It must have been he who wore those boots

 and \textcolor{green}{retained} the missing \textcolor{green}{gems.} Even though he knew that Arthur

 had discovered him, he might still flatter himself that he was

 \textcolor{green}{safe,} for the lad could not say a \textcolor{green}{word} without compromising his

 own family.



 "Well, your own \textcolor{BurntOrange}{good} \textcolor{green}{sense} will \textcolor{green}{suggest} what \textcolor{green}{measures} I took

 next. I went in the \textcolor{green}{shape} of a \textcolor{red}{loafer} to \textcolor{green}{Sir} George's house,

 \textcolor{green}{managed} to \textcolor{green}{pick} up an acquaintance with his valet, \textcolor{green}{learned} that

 his \textcolor{green}{master} had cut his head the night before, and, \textcolor{BurntOrange}{finally,} at

 the expense of six shillings, made all sure by buying a pair of

 his cast-off shoes. With these I journeyed down to Streatham and

 saw that they exactly fitted the \textcolor{blue}{tracks."}



 "I saw an ill-dressed vagabond in the lane yesterday evening,"

 said Mr. Holder.



 "Precisely. It was I. I \textcolor{green}{found} that I had my man, so I came home

 and \textcolor{red}{changed} my clothes. It was a delicate part which I had to

 play then, for I saw that a \textcolor{red}{prosecution} must be \textcolor{red}{avoided} to avert

 \textcolor{red}{scandal,} and I knew that so \textcolor{green}{astute} a \textcolor{red}{villain} would see that our

 hands were tied in the matter. I went and saw him. At first, of

 course, he \textcolor{red}{denied} everything. But when I gave him every

 particular that had occurred, he tried to bluster and took down a

 life-preserver from the wall. I knew my man, however, and I

 clapped a \textcolor{red}{pistol} to his head before he could \textcolor{red}{strike.} Then he

 became a little more reasonable. I told him that we would give

 him a price for the \textcolor{red}{stones} he held--1000 \textcolor{red}{pounds} apiece. That

 brought out the first signs of \textcolor{red}{grief} that he had \textcolor{green}{shown.} 'Why,

 dash it all!' said he, 'I've let them go at six hundred for the

 three!' I soon \textcolor{green}{managed} to get the address of the receiver who had

 them, on \textcolor{green}{promising} him that there would be no \textcolor{red}{prosecution.} Off I

 set to him, and after much chaffering I got our \textcolor{red}{stones} at 1000

 \textcolor{red}{pounds} apiece. Then I looked in upon your son, told him that all

 was right, and eventually got to my bed about two o'clock, after

 what I may call a really hard day's work."



 "A day which has \textcolor{green}{saved} England from a great \textcolor{BurntOrange}{public} \textcolor{red}{scandal,"} said

 the \textcolor{green}{banker,} rising. \textcolor{green}{"Sir,} I cannot find \textcolor{green}{words} to thank you, but

 you shall not find me \textcolor{red}{ungrateful} for what you have done. Your

 skill has indeed \textcolor{BurntOrange}{exceeded} all that I have heard of it. And now I

 must fly to my \textcolor{green}{dear} \textcolor{red}{boy} to apologise to him for the \textcolor{red}{wrong} which I

 have done him. As to what you tell me of poor Mary, it goes to my

 very heart. Not even your skill can \textcolor{green}{inform} me where she is now."



 "I think that we may safely say," returned Holmes, "that she is

 wherever \textcolor{green}{Sir} George Burnwell is. It is \textcolor{green}{equally} certain, too, that

 whatever her \textcolor{red}{sins} are, they will soon receive a more than

 sufficient \textcolor{red}{punishment."}







 XII. THE \textcolor{BurntOrange}{ADVENTURE} OF THE COPPER BEECHES



 "To the man who \textcolor{green}{loves} \textcolor{BurntOrange}{art} for its own sake," remarked Sherlock

 Holmes, tossing aside the advertisement sheet of the \textcolor{blue}{Daily}

 Telegraph, "it is frequently in its least \textcolor{green}{important} and \textcolor{red}{lowliest}

 \textcolor{red}{manifestations} that the keenest pleasure is to be derived. It is

 \textcolor{BurntOrange}{pleasant} to me to observe, Watson, that you have so far grasped

 this \textcolor{green}{truth} that in these little records of our \textcolor{red}{cases} which you

 have been \textcolor{BurntOrange}{good} enough to draw up, and, I am \textcolor{red}{bound} to say,

 occasionally to embellish, you have given \textcolor{green}{prominence} not so much

 to the many causes célèbres and \textcolor{green}{sensational} trials in which I

 have figured but rather to those \textcolor{blue}{incidents} which may have been

 trivial in themselves, but which have given room for those

 \textcolor{green}{faculties} of deduction and of \textcolor{green}{logical} synthesis which I have made

 my \textcolor{green}{special} province."



 "And yet," said I, \textcolor{BurntOrange}{smiling,} "I cannot quite hold myself absolved

 from the charge of sensationalism which has been urged against my

 records."



 "You have \textcolor{red}{erred,} perhaps," he observed, taking up a \textcolor{BurntOrange}{glowing}

 cinder with the tongs and lighting with it the \textcolor{blue}{long} cherry-wood

 pipe which was \textcolor{blue}{wont} to replace his clay when he was in a

 disputatious rather than a meditative mood--"you have \textcolor{red}{erred}

 perhaps in \textcolor{blue}{attempting} to put colour and life into each of your

 \textcolor{green}{statements} instead of \textcolor{red}{confining} yourself to the \textcolor{green}{task} of placing

 upon record that severe \textcolor{green}{reasoning} from cause to effect which is

 really the only \textcolor{green}{notable} \textcolor{green}{feature} about the thing."



 "It seems to me that I have done you \textcolor{green}{full} \textcolor{green}{justice} in the matter,"

 I remarked with some \textcolor{red}{coldness,} for I was repelled by the egotism

 which I had more than once observed to be a strong factor in my

 \textcolor{green}{friend's} singular character.



 "No, it is not \textcolor{red}{selfishness} or \textcolor{red}{conceit,"} said he, answering, as

 was his \textcolor{blue}{wont,} my \textcolor{blue}{thoughts} rather than my \textcolor{green}{words.} "If I claim \textcolor{green}{full}

 \textcolor{green}{justice} for my \textcolor{BurntOrange}{art,} it is because it is an impersonal thing--a

 thing beyond myself. \textcolor{red}{Crime} is common. Logic is rare. Therefore it

 is upon the logic rather than upon the \textcolor{red}{crime} that you should

 dwell. You have \textcolor{red}{degraded} what should have been a course of

 lectures into a \textcolor{green}{series} of \textcolor{green}{tales."}



 It was a \textcolor{red}{cold} morning of the early spring, and we sat after

 \textcolor{green}{breakfast} on either side of a \textcolor{BurntOrange}{cheery} \textcolor{red}{fire} in the old room at

 Baker Street. A thick fog rolled down between the lines of

 dun-coloured houses, and the \textcolor{red}{opposing} windows \textcolor{BurntOrange}{loomed} like \textcolor{red}{dark,}

 shapeless \textcolor{red}{blurs} through the heavy yellow wreaths. Our gas was lit

 and shone on the \textcolor{BurntOrange}{white} cloth and \textcolor{BurntOrange}{glimmer} of china and metal, for

 the table had not been cleared yet. Sherlock Holmes had been

 silent all the morning, dipping continuously into the

 advertisement columns of a succession of papers until at last,

 having apparently given up his search, he had emerged in no very

 \textcolor{BurntOrange}{sweet} temper to lecture me upon my literary \textcolor{red}{shortcomings.}



 "At the same \textcolor{blue}{time,"} he remarked after a pause, during which he

 had sat puffing at his \textcolor{blue}{long} pipe and gazing down into the \textcolor{red}{fire,}

 "you can hardly be open to a charge of sensationalism, for out of

 these \textcolor{red}{cases} which you have been so \textcolor{green}{kind} as to \textcolor{green}{interest} yourself

 in, a \textcolor{green}{fair} proportion do not \textcolor{BurntOrange}{treat} of \textcolor{red}{crime,} in its \textcolor{green}{legal} \textcolor{green}{sense,}

 at all. The \textcolor{red}{small} matter in which I endeavoured to help the \textcolor{green}{King}

 of Bohemia, the singular experience of Miss Mary Sutherland, the

 \textcolor{red}{problem} connected with the man with the twisted lip, and the

 \textcolor{blue}{incident} of the \textcolor{green}{noble} bachelor, were all matters which are

 outside the pale of the \textcolor{green}{law.} But in \textcolor{red}{avoiding} the \textcolor{green}{sensational,} I

 \textcolor{red}{fear} that you may have bordered on the trivial."



 "The end may have been so," I answered, "but the methods I hold

 to have been novel and of \textcolor{green}{interest."}



 "Pshaw, my \textcolor{green}{dear} \textcolor{green}{fellow,} what do the \textcolor{BurntOrange}{public,} the great unobservant

 \textcolor{BurntOrange}{public,} who could hardly tell a weaver by his tooth or a

 compositor by his left thumb, care about the finer shades of

 analysis and deduction! But, indeed, if you are trivial, I cannot

 \textcolor{red}{blame} you, for the days of the great \textcolor{red}{cases} are past. Man, or at

 least \textcolor{red}{criminal} man, has \textcolor{BurntOrange}{lost} all enterprise and \textcolor{BurntOrange}{originality.} As

 to my own little \textcolor{green}{practice,} it seems to be \textcolor{red}{degenerating} into an

 agency for recovering \textcolor{BurntOrange}{lost} \textcolor{green}{lead} pencils and giving \textcolor{green}{advice} to

 \textcolor{BurntOrange}{young} ladies from boarding-schools. I think that I have touched

 \textcolor{red}{bottom} at last, however. This note I had this morning marks my

 zero-point, I \textcolor{BurntOrange}{fancy.} Read it!" He tossed a crumpled \textcolor{blue}{letter} across

 to me.



 It was dated from Montague Place upon the \textcolor{green}{preceding} evening, and

 ran thus:



 \textcolor{green}{"DEAR} MR. HOLMES:--I am very \textcolor{BurntOrange}{anxious} to \textcolor{green}{consult} you as to whether

 I should or should not accept a situation which has been \textcolor{green}{offered}

 to me as \textcolor{green}{governess.} I shall call at half-past ten \textcolor{blue}{to-morrow} if I

 do not inconvenience you. Yours faithfully,

 "VIOLET \textcolor{BurntOrange}{HUNTER."}



 "Do you know the \textcolor{BurntOrange}{young} lady?" I asked.



 "Not I."



 "It is half-past ten now."



 "Yes, and I have no \textcolor{BurntOrange}{doubt} that is her ring."



 "It may turn out to be of more \textcolor{green}{interest} than you think. You

 remember that the affair of the \textcolor{red}{blue} carbuncle, which appeared to

 be a mere \textcolor{BurntOrange}{whim} at first, developed into a serious \textcolor{blue}{investigation.}

 It may be so in this \textcolor{red}{case,} also."



 "Well, let us \textcolor{BurntOrange}{hope} so. But our \textcolor{BurntOrange}{doubts} will very soon be solved,

 for here, unless I am much \textcolor{red}{mistaken,} is the person in \textcolor{green}{question."}



 As he \textcolor{red}{spoke} the door opened and a \textcolor{BurntOrange}{young} lady entered the room.

 She was plainly but \textcolor{green}{neatly} dressed, with a bright, quick face,

 freckled like a plover's egg, and with the brisk manner of a

 woman who has had her own way to make in the world.



 "You will \textcolor{red}{excuse} my troubling you, I am sure," said she, as my

 \textcolor{green}{companion} rose to greet her, "but I have had a very strange

 experience, and as I have no parents or relations of any sort

 from whom I could ask \textcolor{green}{advice,} I \textcolor{blue}{thought} that perhaps you would be

 \textcolor{green}{kind} enough to tell me what I should do."



 \textcolor{BurntOrange}{"Pray} take a seat, Miss \textcolor{BurntOrange}{Hunter.} I shall be \textcolor{BurntOrange}{happy} to do anything

 that I can to \textcolor{BurntOrange}{serve} you."



 I could see that Holmes was favourably impressed by the manner

 and \textcolor{green}{speech} of his new client. He looked her over in his searching

 fashion, and then composed himself, with his lids drooping and

 his finger-tips together, to listen to her story.



 "I have been a \textcolor{green}{governess} for five years," said she, "in the

 family of \textcolor{green}{Colonel} Spence Munro, but two months ago the \textcolor{green}{colonel}

 received an appointment at Halifax, in Nova Scotia, and took his

 \textcolor{BurntOrange}{children} over to America with him, so that I \textcolor{green}{found} myself without

 a situation. I advertised, and I answered advertisements, but

 without \textcolor{BurntOrange}{success.} At last the little \textcolor{BurntOrange}{money} which I had \textcolor{green}{saved} began

 to run short, and I was at my \textcolor{green}{wit's} end as to what I should do.



 "There is a well-known agency for \textcolor{green}{governesses} in the West End

 called Westaway's, and there I used to call about once a week in

 order to see whether anything had turned up which might suit me.

 Westaway was the name of the founder of the business, but it is

 really \textcolor{green}{managed} by Miss Stoper. She sits in her own little office,

 and the ladies who are \textcolor{blue}{seeking} employment \textcolor{BurntOrange}{wait} in an anteroom,

 and are then \textcolor{green}{shown} in one by one, when she consults her ledgers

 and sees whether she has anything which would suit them.



 "Well, when I called last week I was \textcolor{green}{shown} into the little office

 as \textcolor{green}{usual,} but I \textcolor{green}{found} that Miss Stoper was not alone. A

 prodigiously stout man with a very \textcolor{BurntOrange}{smiling} face and a great heavy

 chin which rolled down in fold upon fold over his throat sat at

 her \textcolor{red}{elbow} with a pair of glasses on his \textcolor{red}{nose,} looking very

 \textcolor{green}{earnestly} at the ladies who entered. As I came in he gave quite a

 \textcolor{green}{jump} in his chair and turned quickly to Miss Stoper.



 "'That will do,' said he; 'I could not ask for anything better.

 Capital! capital!' He seemed quite enthusiastic and rubbed his

 hands together in the most \textcolor{green}{genial} fashion. He was such a

 comfortable-looking man that it was quite a pleasure to look at

 him.



 "'You are looking for a situation, miss?' he asked.



 "'Yes, \textcolor{green}{sir.'}



 "'As \textcolor{green}{governess?'}



 "'Yes, \textcolor{green}{sir.'}



 "'And what \textcolor{BurntOrange}{salary} do you ask?'



 "'I had 4 \textcolor{red}{pounds} a month in my last place with \textcolor{green}{Colonel} Spence

 Munro.'



 "'Oh, tut, tut! sweating--rank \textcolor{red}{sweating!'} he \textcolor{red}{cried,} throwing his

 \textcolor{red}{fat} hands out into the air like a man who is in a \textcolor{red}{boiling}

 \textcolor{BurntOrange}{passion.} 'How could anyone \textcolor{green}{offer} so pitiful a sum to a lady with

 such \textcolor{green}{attractions} and \textcolor{green}{accomplishments?'}



 "'My \textcolor{green}{accomplishments,} \textcolor{green}{sir,} may be less than you imagine,' said I.

 'A little French, a little German, \textcolor{BurntOrange}{music,} and drawing--'



 "'Tut, tut!' he \textcolor{red}{cried.} 'This is all quite beside the \textcolor{green}{question.}

 The point is, have you or have you not the bearing and deportment

 of a lady? There it is in a nutshell. If you have not, you are

 not fitted for the \textcolor{red}{rearing} of a \textcolor{BurntOrange}{child} who may some day play a

 \textcolor{green}{considerable} part in the history of the country. But if you have

 why, then, how could any \textcolor{green}{gentleman} ask you to condescend to

 accept anything under the three figures? Your \textcolor{BurntOrange}{salary} with me,

 madam, would commence at 100 \textcolor{red}{pounds} a year.'



 "You may imagine, Mr. Holmes, that to me, \textcolor{red}{destitute} as I was,

 such an \textcolor{green}{offer} seemed almost too \textcolor{BurntOrange}{good} to be \textcolor{green}{true.} The \textcolor{green}{gentleman,}

 however, seeing perhaps the look of incredulity upon my face,

 opened a pocket-book and took out a note.



 "'It is also my custom,' said he, \textcolor{BurntOrange}{smiling} in the most \textcolor{BurntOrange}{pleasant}

 fashion until his eyes were just two little shining slits amid

 the \textcolor{BurntOrange}{white} creases of his face, 'to \textcolor{BurntOrange}{advance} to my \textcolor{BurntOrange}{young} ladies

 half their \textcolor{BurntOrange}{salary} beforehand, so that they may meet any little

 expenses of their \textcolor{BurntOrange}{journey} and their wardrobe.'



 "It seemed to me that I had never met so fascinating and so

 \textcolor{green}{thoughtful} a man. As I was already in \textcolor{red}{debt} to my tradesmen, the

 \textcolor{BurntOrange}{advance} was a great \textcolor{green}{convenience,} and yet there was something

 \textcolor{red}{unnatural} about the whole \textcolor{green}{transaction} which made me wish to know

 a little more before I quite committed myself.



 "'May I ask where you live, \textcolor{green}{sir?'} said I.



 "'Hampshire. \textcolor{green}{Charming} rural place. The Copper Beeches, five miles

 on the far side of Winchester. It is the most \textcolor{BurntOrange}{lovely} country, my

 \textcolor{green}{dear} \textcolor{BurntOrange}{young} lady, and the dearest old country-house.'



 "'And my duties, \textcolor{green}{sir?} I should be \textcolor{BurntOrange}{glad} to know what they would

 be.'



 "'One child--one \textcolor{green}{dear} little romper just six years old. Oh, if

 you could see him \textcolor{red}{killing} cockroaches with a slipper! \textcolor{red}{Smack!}

 \textcolor{red}{smack!} \textcolor{red}{smack!} Three gone before you could wink!' He leaned back

 in his chair and \textcolor{BurntOrange}{laughed} his eyes into his head again.



 "I was a little \textcolor{BurntOrange}{startled} at the nature of the \textcolor{BurntOrange}{child's} \textcolor{green}{amusement,}

 but the \textcolor{green}{father's} \textcolor{BurntOrange}{laughter} made me think that perhaps he was

 \textcolor{green}{joking.}



 "'My sole duties, then,' I asked, 'are to take charge of a single

 \textcolor{BurntOrange}{child?'}



 "'No, no, not the sole, not the sole, my \textcolor{green}{dear} \textcolor{BurntOrange}{young} lady,' he

 \textcolor{red}{cried.} 'Your duty would be, as I am sure your \textcolor{BurntOrange}{good} \textcolor{green}{sense} would

 \textcolor{green}{suggest,} to \textcolor{BurntOrange}{obey} any little commands my wife might give, \textcolor{green}{provided}

 always that they were such commands as a lady might with

 propriety \textcolor{BurntOrange}{obey.} You see no \textcolor{red}{difficulty,} heh?'



 "'I should be \textcolor{BurntOrange}{happy} to make myself useful.'



 "'Quite so. In dress now, for example. We are faddy people, you

 know--faddy but kind-hearted. If you were asked to \textcolor{BurntOrange}{wear} any dress

 which we might give you, you would not object to our little \textcolor{BurntOrange}{whim.}

 Heh?'



 "'No,' said I, considerably astonished at his \textcolor{green}{words.}



 "'Or to sit here, or sit there, that would not be \textcolor{red}{offensive} to

 you?'



 "'Oh, no.'



 "'Or to cut your hair quite short before you come to us?'



 "I could hardly believe my ears. As you may observe, Mr. Holmes,

 my hair is somewhat \textcolor{green}{luxuriant,} and of a rather peculiar tint of

 chestnut. It has been considered \textcolor{green}{artistic.} I could not dream of

 sacrificing it in this \textcolor{red}{offhand} fashion.



 "'I am \textcolor{red}{afraid} that that is quite \textcolor{red}{impossible,'} said I. He had been

 \textcolor{BurntOrange}{watching} me eagerly out of his \textcolor{red}{small} eyes, and I could see a

 shadow pass over his face as I \textcolor{red}{spoke.}



 "'I am \textcolor{red}{afraid} that it is quite \textcolor{green}{essential,'} said he. 'It is a

 little \textcolor{BurntOrange}{fancy} of my wife's, and ladies' \textcolor{BurntOrange}{fancies,} you know, madam,

 ladies' \textcolor{BurntOrange}{fancies} must be \textcolor{green}{consulted.} And so you \textcolor{blue}{won't} cut your

 hair?'



 "'No, \textcolor{green}{sir,} I really could not,' I answered firmly.



 "'Ah, very well; then that quite settles the matter. It is a

 \textcolor{red}{pity,} because in other \textcolor{BurntOrange}{respects} you would really have done very

 nicely. In that \textcolor{red}{case,} Miss Stoper, I had best inspect a few more

 of your \textcolor{BurntOrange}{young} ladies.'



 "The manageress had sat all this while busy with her papers

 without a \textcolor{green}{word} to either of us, but she glanced at me now with so

 much \textcolor{red}{annoyance} upon her face that I could not help \textcolor{red}{suspecting}

 that she had \textcolor{BurntOrange}{lost} a handsome \textcolor{green}{commission} through my \textcolor{red}{refusal.}



 "'Do you desire your name to be kept upon the books?' she asked.



 "'If you please, Miss Stoper.'



 "'Well, really, it seems rather \textcolor{red}{useless,} since you \textcolor{red}{refuse} the

 most \textcolor{green}{excellent} \textcolor{green}{offers} in this fashion,' said she sharply. 'You

 can hardly \textcolor{BurntOrange}{expect} us to exert ourselves to find another such

 opening for you. Good-day to you, Miss \textcolor{BurntOrange}{Hunter.'} She struck a gong

 upon the table, and I was \textcolor{green}{shown} out by the page.



 "Well, Mr. Holmes, when I got back to my \textcolor{green}{lodgings} and \textcolor{green}{found}

 little enough in the cupboard, and two or three bills upon the

 table, I began to ask myself whether I had not done a very

 \textcolor{red}{foolish} thing. After all, if these people had strange fads and

 \textcolor{BurntOrange}{expected} \textcolor{green}{obedience} on the most \textcolor{green}{extraordinary} matters, they were

 at least \textcolor{blue}{ready} to \textcolor{BurntOrange}{pay} for their eccentricity. Very few

 \textcolor{green}{governesses} in England are getting 100 \textcolor{red}{pounds} a year. Besides,

 what use was my hair to me? Many people are \textcolor{BurntOrange}{improved} by \textcolor{BurntOrange}{wearing}

 it short and perhaps I should be among the number. Next day I was

 inclined to think that I had made a \textcolor{red}{mistake,} and by the day after

 I was sure of it. I had almost overcome my \textcolor{green}{pride} so far as to go

 back to the agency and inquire whether the place was still open

 when I received this \textcolor{blue}{letter} from the \textcolor{green}{gentleman} himself. I have it

 here and I will read it to you:



 "'The Copper Beeches, near Winchester.

 \textcolor{green}{"'DEAR} MISS HUNTER:--Miss Stoper has very kindly given me your

 address, and I write from here to ask you whether you have

 reconsidered your decision. My wife is very \textcolor{BurntOrange}{anxious} that you

 should come, for she has been much attracted by my description of

 you. We are willing to give 30 \textcolor{red}{pounds} a quarter, or 120 \textcolor{red}{pounds} a

 year, so as to recompense you for any little inconvenience which

 our fads may cause you. They are not very exacting, after all. My

 wife is fond of a particular shade of \textcolor{BurntOrange}{electric} \textcolor{red}{blue} and would

 like you to \textcolor{BurntOrange}{wear} such a dress indoors in the morning. You need

 not, however, go to the expense of purchasing one, as we have one

 belonging to my \textcolor{green}{dear} \textcolor{green}{daughter} Alice (now in Philadelphia), which

 would, I should think, fit you very well. Then, as to sitting

 here or there, or \textcolor{green}{amusing} yourself in any manner indicated, that

 need cause you no inconvenience. As regards your hair, it is no

 \textcolor{BurntOrange}{doubt} a \textcolor{red}{pity,} especially as I could not help remarking its \textcolor{green}{beauty}

 during our short interview, but I am \textcolor{red}{afraid} that I must remain

 firm upon this point, and I only \textcolor{BurntOrange}{hope} that the \textcolor{green}{increased} \textcolor{BurntOrange}{salary}

 may recompense you for the \textcolor{red}{loss.} Your duties, as far as the \textcolor{BurntOrange}{child}

 is \textcolor{red}{concerned,} are very light. Now do try to come, and I shall

 meet you with the dog-cart at Winchester. Let me know your train.

 Yours faithfully, JEPHRO RUCASTLE.'



 "That is the \textcolor{blue}{letter} which I have just received, Mr. Holmes, and

 my mind is made up that I will accept it. I \textcolor{blue}{thought,} however,

 that before taking the final step I should like to \textcolor{blue}{submit} the

 whole matter to your consideration."



 "Well, Miss \textcolor{BurntOrange}{Hunter,} if your mind is made up, that settles the

 \textcolor{green}{question,"} said Holmes, \textcolor{BurntOrange}{smiling.}



 "But you would not \textcolor{green}{advise} me to \textcolor{red}{refuse?"}



 "I \textcolor{BurntOrange}{confess} that it is not the situation which I should like to

 see a sister of mine apply for."



 "What is the meaning of it all, Mr. Holmes?"



 "Ah, I have no data. I cannot tell. Perhaps you have yourself

 formed some opinion?"



 "Well, there seems to me to be only one possible \textcolor{green}{solution.} Mr.

 Rucastle seemed to be a very \textcolor{green}{kind,} good-natured man. Is it not

 possible that his wife is a \textcolor{red}{lunatic,} that he desires to keep the

 matter \textcolor{BurntOrange}{quiet} for \textcolor{red}{fear} she should be taken to an \textcolor{red}{asylum,} and that

 he humours her \textcolor{BurntOrange}{fancies} in every way in order to \textcolor{red}{prevent} an

 outbreak?"



 "That is a possible solution--in \textcolor{green}{fact,} as matters stand, it is

 the most probable one. But in any \textcolor{red}{case} it does not seem to be a

 nice \textcolor{green}{household} for a \textcolor{BurntOrange}{young} lady."



 "But the \textcolor{BurntOrange}{money,} Mr. Holmes, the \textcolor{BurntOrange}{money!"}



 "Well, yes, of course the \textcolor{BurntOrange}{pay} is good--too \textcolor{BurntOrange}{good.} That is what

 makes me \textcolor{red}{uneasy.} Why should they give you 120 \textcolor{red}{pounds} a year, when

 they could have their \textcolor{green}{pick} for 40 \textcolor{red}{pounds?} There must be some

 strong \textcolor{green}{reason} behind."



 "I \textcolor{blue}{thought} that if I told you the circumstances you would

 understand afterwards if I wanted your help. I should feel so

 much stronger if I felt that you were at the back of me."



 "Oh, you may carry that feeling away with you. I \textcolor{green}{assure} you that

 your little \textcolor{red}{problem} \textcolor{green}{promises} to be the most \textcolor{green}{interesting} which has

 come my way for some months. There is something distinctly novel

 about some of the \textcolor{green}{features.} If you should find yourself in \textcolor{BurntOrange}{doubt}

 or in \textcolor{red}{danger--"}



 \textcolor{red}{"Danger!} What \textcolor{red}{danger} do you \textcolor{BurntOrange}{foresee?"}



 Holmes shook his head gravely. "It would cease to be a \textcolor{red}{danger} if

 we could define it," said he. "But at any \textcolor{blue}{time,} day or night, a

 telegram would bring me down to your help."



 "That is enough." She rose briskly from her chair with the

 \textcolor{BurntOrange}{anxiety} all swept from her face. "I shall go down to Hampshire

 quite easy in my mind now. I shall write to Mr. Rucastle at once,

 sacrifice my poor hair to-night, and \textcolor{blue}{start} for Winchester

 \textcolor{blue}{to-morrow."} With a few \textcolor{green}{grateful} \textcolor{green}{words} to Holmes she bade us both

 good-night and bustled off upon her way.



 "At least," said I as we heard her quick, firm steps descending

 the stairs, "she seems to be a \textcolor{BurntOrange}{young} lady who is very well able

 to take care of herself."



 "And she would need to be," said Holmes gravely. "I am much

 \textcolor{red}{mistaken} if we do not hear from her before many days are past."



 It was not very \textcolor{blue}{long} before my \textcolor{green}{friend's} \textcolor{blue}{prediction} was fulfilled.

 A fortnight went by, during which I frequently \textcolor{green}{found} my \textcolor{blue}{thoughts}

 turning in her direction and wondering what strange side-alley of

 human experience this \textcolor{red}{lonely} woman had strayed into. The unusual

 \textcolor{BurntOrange}{salary,} the curious conditions, the light duties, all pointed to

 something \textcolor{red}{abnormal,} though whether a fad or a plot, or whether

 the man were a \textcolor{green}{philanthropist} or a \textcolor{red}{villain,} it was quite beyond

 my powers to determine. As to Holmes, I observed that he sat

 frequently for half an hour on end, with knitted brows and an

 abstracted air, but he swept the matter away with a wave of his

 hand when I mentioned it. "Data! data! data!" he \textcolor{red}{cried}

 impatiently. "I can't make bricks without clay." And yet he would

 always wind up by \textcolor{red}{muttering} that no sister of his should ever

 have accepted such a situation.



 The telegram which we eventually received came \textcolor{red}{late} one night

 just as I was thinking of turning in and Holmes was settling down

 to one of those all-night chemical researches which he frequently

 indulged in, when I would \textcolor{BurntOrange}{leave} him stooping over a \textcolor{red}{retort} and a

 test-tube at night and find him in the same position when I came

 down to \textcolor{green}{breakfast} in the morning. He opened the yellow envelope,

 and then, glancing at the message, threw it across to me.



 "Just look up the trains in Bradshaw," said he, and turned back

 to his chemical \textcolor{green}{studies.}



 The \textcolor{red}{summons} was a brief and \textcolor{BurntOrange}{urgent} one.



 "Please be at the \textcolor{red}{Black} Swan Hotel at Winchester at midday

 \textcolor{blue}{to-morrow,"} it said. "Do come! I am at my \textcolor{green}{wit's} end. \textcolor{BurntOrange}{HUNTER."}



 "Will you come with me?" asked Holmes, glancing up.



 "I should wish to."



 "Just look it up, then."



 "There is a train at half-past nine," said I, glancing over my

 Bradshaw. "It is due at Winchester at 11:30."



 "That will do very nicely. Then perhaps I had better postpone my

 analysis of the acetones, as we may need to be at our best in the

 morning."



 By eleven o'clock the next day we were well upon our way to the

 old English capital. Holmes had been \textcolor{red}{buried} in the morning papers

 all the way down, but after we had passed the Hampshire border he

 threw them down and began to \textcolor{green}{admire} the scenery. It was an ideal

 spring day, a light \textcolor{red}{blue} \textcolor{green}{sky,} flecked with little fleecy \textcolor{BurntOrange}{white}

 clouds drifting across from west to east. The \textcolor{BurntOrange}{sun} was shining

 very brightly, and yet there was an exhilarating nip in the air,

 which set an edge to a man's energy. All over the countryside,

 away to the rolling hills around Aldershot, the little red and

 grey roofs of the farm-steadings peeped out from amid the light

 \textcolor{green}{green} of the new foliage.



 "Are they not fresh and \textcolor{green}{beautiful?"} I \textcolor{red}{cried} with all the

 \textcolor{BurntOrange}{enthusiasm} of a man fresh from the fogs of Baker Street.



 But Holmes shook his head gravely.



 "Do you know, Watson," said he, "that it is one of the \textcolor{red}{curses} of

 a mind with a turn like mine that I must look at everything with

 reference to my own \textcolor{green}{special} \textcolor{red}{subject.} You look at these scattered

 houses, and you are impressed by their \textcolor{green}{beauty.} I look at them,

 and the only \textcolor{blue}{thought} which comes to me is a feeling of their

 \textcolor{red}{isolation} and of the impunity with which \textcolor{red}{crime} may be committed

 there."



 \textcolor{BurntOrange}{"Good} heavens!" I \textcolor{red}{cried.} "Who would \textcolor{green}{associate} \textcolor{red}{crime} with these

 \textcolor{green}{dear} old homesteads?"



 "They always \textcolor{green}{fill} me with a certain \textcolor{BurntOrange}{horror.} It is my belief,

 Watson, \textcolor{green}{founded} upon my experience, that the lowest and vilest

 alleys in London do not \textcolor{BurntOrange}{present} a more \textcolor{BurntOrange}{dreadful} record of \textcolor{red}{sin}

 than does the \textcolor{BurntOrange}{smiling} and \textcolor{green}{beautiful} countryside."



 "You horrify me!"



 "But the \textcolor{green}{reason} is very \textcolor{green}{obvious.} The \textcolor{red}{pressure} of \textcolor{BurntOrange}{public} opinion

 can do in the town what the \textcolor{green}{law} cannot \textcolor{green}{accomplish.} There is no

 lane so vile that the \textcolor{BurntOrange}{scream} of a \textcolor{BurntOrange}{tortured} \textcolor{BurntOrange}{child,} or the thud of

 a drunkard's blow, does not beget \textcolor{BurntOrange}{sympathy} and \textcolor{red}{indignation} among

 the neighbours, and then the whole machinery of \textcolor{green}{justice} is ever

 so close that a \textcolor{green}{word} of \textcolor{red}{complaint} can set it going, and there is

 but a step between the \textcolor{red}{crime} and the dock. But look at these

 \textcolor{red}{lonely} houses, each in its own fields, \textcolor{green}{filled} for the most part

 with poor \textcolor{red}{ignorant} folk who know little of the \textcolor{green}{law.} Think of the

 \textcolor{green}{deeds} of \textcolor{red}{hellish} \textcolor{red}{cruelty,} the \textcolor{red}{hidden} \textcolor{red}{wickedness} which may go on,

 year in, year out, in such places, and none the wiser. Had this

 lady who \textcolor{blue}{appeals} to us for help gone to live in Winchester, I

 should never have had a \textcolor{red}{fear} for her. It is the five miles of

 country which makes the \textcolor{red}{danger.} Still, it is clear that she is

 not personally \textcolor{BurntOrange}{threatened."}



 "No. If she can come to Winchester to meet us she can get away."



 "Quite so. She has her \textcolor{green}{freedom."}



 "What CAN be the matter, then? Can you \textcolor{green}{suggest} no explanation?"



 "I have devised seven separate explanations, each of which would

 \textcolor{green}{cover} the \textcolor{green}{facts} as far as we know them. But which of these is

 correct can only be determined by the fresh \textcolor{green}{information} which we

 shall no \textcolor{BurntOrange}{doubt} find \textcolor{BurntOrange}{waiting} for us. Well, there is the \textcolor{green}{tower} of

 the \textcolor{green}{cathedral,} and we shall soon \textcolor{green}{learn} all that Miss \textcolor{BurntOrange}{Hunter} has

 to tell."



 The \textcolor{red}{Black} Swan is an inn of repute in the High Street, at no

 distance from the station, and there we \textcolor{green}{found} the \textcolor{BurntOrange}{young} lady

 \textcolor{BurntOrange}{waiting} for us. She had engaged a sitting-room, and our lunch

 \textcolor{blue}{awaited} us upon the table.



 "I am so \textcolor{BurntOrange}{delighted} that you have come," she said \textcolor{green}{earnestly.} "It

 is so very \textcolor{green}{kind} of you both; but indeed I do not know what I

 should do. Your \textcolor{green}{advice} will be altogether invaluable to me."



 \textcolor{BurntOrange}{"Pray} tell us what has \textcolor{blue}{happened} to you."



 "I will do so, and I must be quick, for I have \textcolor{green}{promised} Mr.

 Rucastle to be back before three. I got his \textcolor{BurntOrange}{leave} to come into

 town this morning, though he little knew for what purpose."



 "Let us have everything in its due order." Holmes thrust his \textcolor{blue}{long}

 thin legs out towards the \textcolor{red}{fire} and composed himself to listen.



 "In the first place, I may say that I have met, on the whole,

 with no \textcolor{green}{actual} ill-treatment from Mr. and Mrs. Rucastle. It is

 only \textcolor{green}{fair} to them to say that. But I cannot understand them, and

 I am not easy in my mind about them."



 "What can you not understand?"



 "Their \textcolor{green}{reasons} for their conduct. But you shall have it all just

 as it occurred. When I came down, Mr. Rucastle met me here and

 drove me in his dog-cart to the Copper Beeches. It is, as he

 said, beautifully situated, but it is not \textcolor{green}{beautiful} in itself,

 for it is a large square block of a house, whitewashed, but all

 \textcolor{red}{stained} and streaked with damp and \textcolor{red}{bad} weather. There are \textcolor{green}{grounds}

 round it, woods on three sides, and on the fourth a field which

 slopes down to the Southampton highroad, which curves past about

 a hundred yards from the front door. This \textcolor{green}{ground} in front belongs

 to the house, but the woods all round are part of \textcolor{BurntOrange}{Lord}

 Southerton's \textcolor{green}{preserves.} A \textcolor{red}{clump} of copper beeches \textcolor{BurntOrange}{immediately} in

 front of the hall door has given its name to the place.



 "I was driven over by my employer, who was as \textcolor{green}{amiable} as ever,

 and was introduced by him that evening to his wife and the \textcolor{BurntOrange}{child.}

 There was no \textcolor{green}{truth,} Mr. Holmes, in the \textcolor{blue}{conjecture} which seemed to

 us to be probable in your rooms at Baker Street. Mrs. Rucastle is

 not \textcolor{red}{mad.} I \textcolor{green}{found} her to be a silent, pale-faced woman, much

 \textcolor{BurntOrange}{younger} than her husband, not more than thirty, I should think,

 while he can hardly be less than forty-five. From their

 conversation I have gathered that they have been married about

 seven years, that he was a \textcolor{red}{widower,} and that his only \textcolor{BurntOrange}{child} by

 the first wife was the \textcolor{green}{daughter} who has gone to Philadelphia. Mr.

 Rucastle told me in private that the \textcolor{green}{reason} why she had left them

 was that she had an unreasoning \textcolor{red}{aversion} to her stepmother. As

 the \textcolor{green}{daughter} could not have been less than twenty, I can quite

 imagine that her position must have been \textcolor{red}{uncomfortable} with her

 \textcolor{green}{father's} \textcolor{BurntOrange}{young} wife.



 "Mrs. Rucastle seemed to me to be colourless in mind as well as

 in \textcolor{green}{feature.} She impressed me neither favourably nor the reverse.

 She was a nonentity. It was easy to see that she was passionately

 devoted both to her husband and to her little son. Her light grey

 eyes wandered continually from one to the other, noting every

 little want and forestalling it if possible. He was \textcolor{green}{kind} to her

 also in his \textcolor{red}{bluff,} \textcolor{BurntOrange}{boisterous} fashion, and on the whole they

 seemed to be a \textcolor{BurntOrange}{happy} couple. And yet she had some \textcolor{green}{secret} \textcolor{red}{sorrow,}

 this woman. She would often be \textcolor{BurntOrange}{lost} in deep \textcolor{blue}{thought,} with the

 saddest look upon her face. More than once I have \textcolor{blue}{surprised} her

 in tears. I have \textcolor{blue}{thought} sometimes that it was the disposition of

 her \textcolor{BurntOrange}{child} which \textcolor{BurntOrange}{weighed} upon her mind, for I have never met so

 utterly \textcolor{red}{spoiled} and so ill-natured a little \textcolor{red}{creature.} He is \textcolor{red}{small}

 for his age, with a head which is quite disproportionately large.

 His whole life appears to be \textcolor{red}{spent} in an alternation between

 \textcolor{red}{savage} fits of \textcolor{BurntOrange}{passion} and \textcolor{red}{gloomy} intervals of sulking. Giving

 \textcolor{red}{pain} to any \textcolor{red}{creature} weaker than himself seems to be his one idea

 of \textcolor{green}{amusement,} and he \textcolor{green}{shows} quite \textcolor{BurntOrange}{remarkable} \textcolor{green}{talent} in \textcolor{BurntOrange}{planning}

 the \textcolor{red}{capture} of mice, little birds, and insects. But I would

 rather not \textcolor{green}{talk} about the \textcolor{red}{creature,} Mr. Holmes, and, indeed, he

 has little to do with my story."



 "I am \textcolor{BurntOrange}{glad} of all details," remarked my \textcolor{green}{friend,} "whether they

 seem to you to be \textcolor{green}{relevant} or not."



 "I shall try not to miss anything of \textcolor{BurntOrange}{importance.} The one

 \textcolor{red}{unpleasant} thing about the house, which struck me at once, was

 the appearance and conduct of the \textcolor{BurntOrange}{servants.} There are only two, a

 man and his wife. Toller, for that is his name, is a rough,

 uncouth man, with grizzled hair and whiskers, and a perpetual

 \textcolor{red}{smell} of drink. Twice since I have been with them he has been

 quite drunk, and yet Mr. Rucastle seemed to take no notice of it.

 His wife is a very tall and strong woman with a \textcolor{red}{sour} face, as

 silent as Mrs. Rucastle and much less \textcolor{green}{amiable.} They are a most

 \textcolor{red}{unpleasant} couple, but fortunately I spend most of my \textcolor{blue}{time} in the

 \textcolor{green}{nursery} and my own room, which are next to each other in one

 corner of the \textcolor{green}{building.}



 "For two days after my \textcolor{blue}{arrival} at the Copper Beeches my life was

 very \textcolor{BurntOrange}{quiet;} on the third, Mrs. Rucastle came down just after

 \textcolor{green}{breakfast} and whispered something to her husband.



 "'Oh, yes,' said he, turning to me, 'we are very much \textcolor{BurntOrange}{obliged} to

 you, Miss \textcolor{BurntOrange}{Hunter,} for \textcolor{red}{falling} in with our \textcolor{BurntOrange}{whims} so far as to cut

 your hair. I \textcolor{green}{assure} you that it has not \textcolor{red}{detracted} in the tiniest

 iota from your appearance. We shall now see how the electric-blue

 dress will become you. You will find it laid out upon the bed in

 your room, and if you would be so \textcolor{BurntOrange}{good} as to put it on we should

 both be extremely \textcolor{BurntOrange}{obliged.'}



 "The dress which I \textcolor{green}{found} \textcolor{BurntOrange}{waiting} for me was of a peculiar shade

 of \textcolor{red}{blue.} It was of \textcolor{green}{excellent} material, a sort of beige, but it

 \textcolor{red}{bore} unmistakable signs of having been \textcolor{red}{worn} before. It could not

 have been a better fit if I had been \textcolor{green}{measured} for it. Both Mr.

 and Mrs. Rucastle expressed a \textcolor{BurntOrange}{delight} at the look of it, which

 seemed quite \textcolor{red}{exaggerated} in its vehemence. They were \textcolor{BurntOrange}{waiting} for

 me in the drawing-room, which is a very large room, stretching

 along the entire front of the house, with three \textcolor{blue}{long} windows

 reaching down to the floor. A chair had been placed close to the

 central window, with its back turned towards it. In this I was

 asked to sit, and then Mr. Rucastle, walking up and down on the

 other side of the room, began to tell me a \textcolor{green}{series} of the funniest

 stories that I have ever listened to. You cannot imagine how

 comical he was, and I \textcolor{BurntOrange}{laughed} until I was quite \textcolor{red}{weary.} Mrs.

 Rucastle, however, who has evidently no \textcolor{green}{sense} of humour, never so

 much as \textcolor{BurntOrange}{smiled,} but sat with her hands in her lap, and a sad,

 \textcolor{BurntOrange}{anxious} look upon her face. After an hour or so, Mr. Rucastle

 \textcolor{blue}{suddenly} remarked that it was \textcolor{blue}{time} to commence the duties of the

 day, and that I might \textcolor{red}{change} my dress and go to little Edward in

 the \textcolor{green}{nursery.}



 "Two days later this same performance was gone through under

 exactly similar circumstances. Again I \textcolor{red}{changed} my dress, again I

 sat in the window, and again I \textcolor{BurntOrange}{laughed} very \textcolor{green}{heartily} at the funny

 stories of which my employer had an \textcolor{green}{immense} répertoire, and which

 he told inimitably. Then he handed me a yellow-backed novel, and

 moving my chair a little sideways, that my own shadow might not

 \textcolor{red}{fall} upon the page, he \textcolor{red}{begged} me to read aloud to him. I read for

 about ten minutes, beginning in the heart of a chapter, and then

 \textcolor{blue}{suddenly,} in the middle of a \textcolor{BurntOrange}{sentence,} he ordered me to cease and

 to \textcolor{red}{change} my dress.



 "You can easily imagine, Mr. Holmes, how curious I became as to

 what the meaning of this \textcolor{green}{extraordinary} performance could possibly

 be. They were always very \textcolor{green}{careful,} I observed, to turn my face

 away from the window, so that I became consumed with the desire

 to see what was going on behind my back. At first it seemed to be

 \textcolor{red}{impossible,} but I soon devised a means. My hand-mirror had been

 \textcolor{red}{broken,} so a \textcolor{BurntOrange}{happy} \textcolor{blue}{thought} \textcolor{red}{seized} me, and I \textcolor{red}{concealed} a piece of

 the glass in my handkerchief. On the next occasion, in the midst

 of my \textcolor{BurntOrange}{laughter,} I put my handkerchief up to my eyes, and was able

 with a little \textcolor{green}{management} to see all that there was behind me. I

 \textcolor{BurntOrange}{confess} that I was \textcolor{red}{disappointed.} There was nothing. At least that

 was my first \textcolor{green}{impression.} At the second glance, however, I

 \textcolor{green}{perceived} that there was a man standing in the Southampton Road,

 a \textcolor{red}{small} bearded man in a grey suit, who seemed to be looking in

 my direction. The road is an \textcolor{green}{important} highway, and there are

 usually people there. This man, however, was leaning against the

 railings which bordered our field and was looking \textcolor{green}{earnestly} up. I

 \textcolor{red}{lowered} my handkerchief and glanced at Mrs. Rucastle to find her

 eyes fixed upon me with a most searching gaze. She said nothing,

 but I am \textcolor{BurntOrange}{convinced} that she had divined that I had a mirror in my

 hand and had seen what was behind me. She rose at once.



 "'Jephro,' said she, 'there is an impertinent \textcolor{green}{fellow} upon the

 road there who stares up at Miss \textcolor{BurntOrange}{Hunter.'}



 "'No \textcolor{green}{friend} of yours, Miss \textcolor{BurntOrange}{Hunter?'} he asked.



 "'No, I know no one in these parts.'



 \textcolor{green}{"'Dear} me! How very impertinent! Kindly turn round and \textcolor{blue}{motion} to

 him to go away.'



 "'Surely it would be better to take no notice.'



 "'No, no, we should have him loitering here always. Kindly turn

 round and wave him away like that.'



 "I did as I was told, and at the same instant Mrs. Rucastle drew

 down the \textcolor{red}{blind.} That was a week ago, and from that \textcolor{blue}{time} I have

 not sat again in the window, nor have I \textcolor{red}{worn} the \textcolor{red}{blue} dress, nor

 seen the man in the road."



 \textcolor{BurntOrange}{"Pray} \textcolor{BurntOrange}{continue,"} said Holmes. "Your narrative \textcolor{green}{promises} to be a

 most \textcolor{green}{interesting} one."



 "You will find it rather \textcolor{red}{disconnected,} I \textcolor{red}{fear,} and there may

 \textcolor{green}{prove} to be little relation between the different \textcolor{blue}{incidents} of

 which I speak. On the very first day that I was at the Copper

 Beeches, Mr. Rucastle took me to a \textcolor{red}{small} \textcolor{red}{outhouse} which stands

 near the kitchen door. As we approached it I heard the sharp

 rattling of a chain, and the sound as of a large animal moving

 about.



 "'Look in here!' said Mr. Rucastle, \textcolor{green}{showing} me a slit between two

 planks. 'Is he not a \textcolor{green}{beauty?'}



 "I looked through and was conscious of two \textcolor{BurntOrange}{glowing} eyes, and of a

 \textcolor{red}{vague} figure huddled up in the \textcolor{red}{darkness.}



 "'Don't be \textcolor{BurntOrange}{frightened,'} said my employer, \textcolor{BurntOrange}{laughing} at the \textcolor{blue}{start}

 which I had given. 'It's only Carlo, my mastiff. I call him mine,

 but really old Toller, my groom, is the only man who can do

 anything with him. We feed him once a day, and not too much then,

 so that he is always as keen as mustard. Toller lets him loose

 every night, and \textcolor{BurntOrange}{God} help the trespasser whom he lays his \textcolor{red}{fangs}

 upon. For \textcolor{BurntOrange}{goodness'} sake don't you ever on any pretext set your

 foot over the threshold at night, for it's as much as your life

 is \textcolor{green}{worth.'}



 "The \textcolor{BurntOrange}{warning} was no idle one, for two nights later I \textcolor{blue}{happened} to

 look out of my bedroom window about two o'clock in the morning.

 It was a \textcolor{green}{beautiful} moonlight night, and the lawn in front of the

 house was silvered over and almost as bright as day. I was

 standing, \textcolor{BurntOrange}{rapt} in the \textcolor{BurntOrange}{peaceful} \textcolor{green}{beauty} of the scene, when I was

 aware that something was moving under the shadow of the copper

 beeches. As it emerged into the moonshine I saw what it was. It

 was a \textcolor{red}{giant} dog, as large as a \textcolor{green}{calf,} \textcolor{red}{tawny} tinted, with hanging

 jowl, \textcolor{red}{black} \textcolor{red}{muzzle,} and huge projecting bones. It walked slowly

 across the lawn and \textcolor{BurntOrange}{vanished} into the shadow upon the other side.

 That \textcolor{BurntOrange}{dreadful} \textcolor{green}{sentinel} sent a chill to my heart which I do not

 think that any \textcolor{red}{burglar} could have done.



 "And now I have a very strange experience to tell you. I had, as

 you know, cut off my hair in London, and I had placed it in a

 great coil at the \textcolor{red}{bottom} of my trunk. One evening, after the

 \textcolor{BurntOrange}{child} was in bed, I began to \textcolor{green}{amuse} myself by examining the

 furniture of my room and by rearranging my own little things.

 There was an old chest of drawers in the room, the two upper ones

 empty and open, the lower one locked. I had \textcolor{green}{filled} the first two

 with my linen, and as I had still much to pack away I was

 naturally annoyed at not having the use of the third drawer. It

 struck me that it might have been fastened by a mere \textcolor{red}{oversight,}

 so I took out my bunch of keys and tried to open it. The very

 first key fitted to \textcolor{BurntOrange}{perfection,} and I drew the drawer open. There

 was only one thing in it, but I am sure that you would never

 \textcolor{blue}{guess} what it was. It was my coil of hair.



 "I took it up and examined it. It was of the same peculiar tint,

 and the same thickness. But then the impossibility of the thing

 obtruded itself upon me. How could my hair have been locked in

 the drawer? With trembling hands I undid my trunk, turned out the

 \textcolor{green}{contents,} and drew from the \textcolor{red}{bottom} my own hair. I laid the two

 tresses together, and I \textcolor{green}{assure} you that they were identical. Was

 it not \textcolor{green}{extraordinary?} Puzzle as I would, I could make nothing at

 all of what it meant. I returned the strange hair to the drawer,

 and I said nothing of the matter to the Rucastles as I felt that

 I had put myself in the \textcolor{red}{wrong} by opening a drawer which they had

 locked.



 "I am naturally \textcolor{green}{observant,} as you may have remarked, Mr. Holmes,

 and I soon had a \textcolor{BurntOrange}{pretty} \textcolor{BurntOrange}{good} \textcolor{blue}{plan} of the whole house in my head.

 There was one wing, however, which appeared not to be inhabited

 at all. A door which faced that which \textcolor{green}{led} into the quarters of

 the Tollers opened into this suite, but it was \textcolor{green}{invariably} locked.

 One day, however, as I ascended the stair, I met Mr. Rucastle

 coming out through this door, his keys in his hand, and a look on

 his face which made him a very different person to the round,

 \textcolor{green}{jovial} man to whom I was accustomed. His cheeks were red, his

 brow was all crinkled with \textcolor{red}{anger,} and the veins stood out at his

 temples with \textcolor{BurntOrange}{passion.} He locked the door and \textcolor{blue}{hurried} past me

 without a \textcolor{green}{word} or a look.



 "This \textcolor{BurntOrange}{aroused} my \textcolor{BurntOrange}{curiosity,} so when I went out for a walk in the

 \textcolor{green}{grounds} with my charge, I strolled round to the side from which I

 could see the windows of this part of the house. There were four

 of them in a \textcolor{red}{row,} three of which were simply \textcolor{red}{dirty,} while the

 fourth was shuttered up. They were evidently all \textcolor{red}{deserted.} As I

 strolled up and down, glancing at them occasionally, Mr. Rucastle

 came out to me, looking as \textcolor{green}{merry} and \textcolor{green}{jovial} as ever.



 "'Ah!' said he, 'you must not think me rude if I passed you

 without a \textcolor{green}{word,} my \textcolor{green}{dear} \textcolor{BurntOrange}{young} lady. I was preoccupied with

 business matters.'



 "I \textcolor{green}{assured} him that I was not \textcolor{red}{offended.} 'By the way,' said I,

 'you seem to have quite a suite of spare rooms up there, and one

 of them has the shutters up.'



 "He looked \textcolor{blue}{surprised} and, as it seemed to me, a little \textcolor{BurntOrange}{startled}

 at my remark.



 "'Photography is one of my \textcolor{green}{hobbies,'} said he. 'I have made my

 \textcolor{red}{dark} room up there. But, \textcolor{green}{dear} me! what an \textcolor{green}{observant} \textcolor{BurntOrange}{young} lady we

 have come upon. Who would have believed it? Who would have ever

 believed it?' He \textcolor{red}{spoke} in a jesting tone, but there was no \textcolor{BurntOrange}{jest}

 in his eyes as he looked at me. I read \textcolor{red}{suspicion} there and

 \textcolor{red}{annoyance,} but no \textcolor{BurntOrange}{jest.}



 "Well, Mr. Holmes, from the moment that I understood that there

 was something about that suite of rooms which I was not to know,

 I was all on \textcolor{red}{fire} to go over them. It was not mere \textcolor{BurntOrange}{curiosity,}

 though I have my \textcolor{BurntOrange}{share} of that. It was more a feeling of duty--a

 feeling that some \textcolor{BurntOrange}{good} might come from my penetrating to this

 place. They \textcolor{green}{talk} of woman's instinct; perhaps it was woman's

 instinct which gave me that feeling. At any rate, it was there,

 and I was keenly on the lookout for any \textcolor{blue}{chance} to pass the

 forbidden door.



 "It was only yesterday that the \textcolor{blue}{chance} came. I may tell you that,

 besides Mr. Rucastle, both Toller and his wife find something to

 do in these \textcolor{red}{deserted} rooms, and I once saw him carrying a large

 \textcolor{red}{black} linen bag with him through the door. Recently he has been

 \textcolor{red}{drinking} hard, and yesterday evening he was very drunk; and when

 I came upstairs there was the key in the door. I have no \textcolor{BurntOrange}{doubt} at

 all that he had left it there. Mr. and Mrs. Rucastle were both

 downstairs, and the \textcolor{BurntOrange}{child} was with them, so that I had an

 \textcolor{green}{admirable} \textcolor{BurntOrange}{opportunity.} I turned the key gently in the lock,

 opened the door, and \textcolor{BurntOrange}{slipped} through.



 "There was a little passage in front of me, unpapered and

 uncarpeted, which turned at a right angle at the farther end.

 Round this corner were three doors in a line, the first and third

 of which were open. They each \textcolor{green}{led} into an empty room, dusty and

 cheerless, with two windows in the one and one in the other, so

 thick with \textcolor{red}{dirt} that the evening light \textcolor{BurntOrange}{glimmered} dimly through

 them. The centre door was closed, and across the outside of it

 had been fastened one of the broad bars of an \textcolor{green}{iron} bed, padlocked

 at one end to a ring in the wall, and fastened at the other with

 stout cord. The door itself was locked as well, and the key was

 not there. This \textcolor{red}{barricaded} door corresponded clearly with the

 shuttered window outside, and yet I could see by the \textcolor{BurntOrange}{glimmer} from

 beneath it that the room was not in \textcolor{red}{darkness.} Evidently there was

 a skylight which let in light from above. As I stood in the

 passage gazing at the \textcolor{red}{sinister} door and wondering what \textcolor{green}{secret} it

 might veil, I \textcolor{blue}{suddenly} heard the sound of steps within the room

 and saw a shadow pass \textcolor{red}{backward} and \textcolor{green}{forward} against the little

 slit of dim light which shone out from under the door. A \textcolor{red}{mad,}

 unreasoning \textcolor{red}{terror} rose up in me at the sight, Mr. Holmes. My

 overstrung \textcolor{green}{nerves} failed me \textcolor{blue}{suddenly,} and I turned and ran--ran

 as though some \textcolor{BurntOrange}{dreadful} hand were behind me clutching at the

 skirt of my dress. I rushed down the passage, through the door,

 and straight into the arms of Mr. Rucastle, who was \textcolor{BurntOrange}{waiting}

 outside.



 "'So,' said he, \textcolor{BurntOrange}{smiling,} 'it was you, then. I \textcolor{blue}{thought} that it

 must be when I saw the door open.'



 "'Oh, I am so \textcolor{BurntOrange}{frightened!'} I panted.



 "'My \textcolor{green}{dear} \textcolor{BurntOrange}{young} lady! my \textcolor{green}{dear} \textcolor{BurntOrange}{young} lady!'--you cannot think how

 \textcolor{green}{caressing} and \textcolor{green}{soothing} his manner was--'and what has \textcolor{BurntOrange}{frightened}

 you, my \textcolor{green}{dear} \textcolor{BurntOrange}{young} lady?'



 "But his voice was just a little too \textcolor{green}{coaxing.} He overdid it. I

 was keenly on my \textcolor{BurntOrange}{guard} against him.



 "'I was \textcolor{red}{foolish} enough to go into the empty wing,' I answered.

 'But it is so \textcolor{red}{lonely} and eerie in this dim light that I was

 \textcolor{BurntOrange}{frightened} and ran out again. Oh, it is so \textcolor{BurntOrange}{dreadfully} still in

 there!'



 "'Only that?' said he, looking at me keenly.



 "'Why, what did you think?' I asked.



 "'Why do you think that I lock this door?'



 "'I am sure that I do not know.'



 "'It is to keep people out who have no business there. Do you

 see?' He was still \textcolor{BurntOrange}{smiling} in the most \textcolor{green}{amiable} manner.



 "'I am sure if I had known--'



 "'Well, then, you know now. And if you ever put your foot over

 that threshold again'--here in an instant the \textcolor{BurntOrange}{smile} hardened into

 a \textcolor{BurntOrange}{grin} of \textcolor{red}{rage,} and he \textcolor{red}{glared} down at me with the face of a

 demon--'I'll throw you to the mastiff.'



 "I was so terrified that I do not know what I did. I suppose that

 I must have rushed past him into my room. I remember nothing

 until I \textcolor{green}{found} myself \textcolor{red}{lying} on my bed trembling all over. Then I

 \textcolor{blue}{thought} of you, Mr. Holmes. I could not live there longer without

 some \textcolor{green}{advice.} I was \textcolor{BurntOrange}{frightened} of the house, of the man, of the

 woman, of the \textcolor{BurntOrange}{servants,} even of the \textcolor{BurntOrange}{child.} They were all \textcolor{red}{horrible}

 to me. If I could only bring you down all would be well. Of

 course I might have \textcolor{red}{fled} from the house, but my \textcolor{BurntOrange}{curiosity} was

 almost as strong as my \textcolor{red}{fears.} My mind was soon made up. I would

 send you a wire. I put on my hat and cloak, went down to the

 office, which is about half a mile from the house, and then

 returned, feeling very much easier. A \textcolor{red}{horrible} \textcolor{BurntOrange}{doubt} came into my

 mind as I approached the door lest the dog might be loose, but I

 remembered that Toller had drunk himself into a state of

 insensibility that evening, and I knew that he was the only one

 in the \textcolor{green}{household} who had any \textcolor{BurntOrange}{influence} with the \textcolor{red}{savage} \textcolor{red}{creature,}

 or who would venture to set him free. I \textcolor{BurntOrange}{slipped} in in safety and

 lay awake half the night in my \textcolor{green}{joy} at the \textcolor{blue}{thought} of seeing you.

 I had no \textcolor{red}{difficulty} in getting \textcolor{BurntOrange}{leave} to come into Winchester this

 morning, but I must be back before three o'clock, for Mr. and

 Mrs. Rucastle are going on a \textcolor{green}{visit,} and will be away all the

 evening, so that I must look after the \textcolor{BurntOrange}{child.} Now I have told you

 all my \textcolor{BurntOrange}{adventures,} Mr. Holmes, and I should be very \textcolor{BurntOrange}{glad} if you

 could tell me what it all means, and, above all, what I should

 do."



 Holmes and I had listened spellbound to this \textcolor{green}{extraordinary} story.

 My \textcolor{green}{friend} rose now and paced up and down the room, his hands in

 his pockets, and an expression of the most profound gravity upon

 his face.



 "Is Toller still drunk?" he asked.



 "Yes. I heard his wife tell Mrs. Rucastle that she could do

 nothing with him."



 "That is well. And the Rucastles go out to-night?"



 "Yes."



 "Is there a cellar with a \textcolor{BurntOrange}{good} strong lock?"



 "Yes, the wine-cellar."



 "You seem to me to have acted all through this matter like a very

 brave and sensible girl, Miss \textcolor{BurntOrange}{Hunter.} Do you think that you could

 perform one more \textcolor{BurntOrange}{feat?} I should not ask it of you if I did not

 think you a quite exceptional woman."



 "I will try. What is it?"



 "We shall be at the Copper Beeches by seven o'clock, my \textcolor{green}{friend}

 and I. The Rucastles will be gone by that \textcolor{blue}{time,} and Toller will,

 we \textcolor{BurntOrange}{hope,} be incapable. There only \textcolor{BurntOrange}{remains} Mrs. Toller, who might

 give the \textcolor{BurntOrange}{alarm.} If you could send her into the cellar on some

 \textcolor{BurntOrange}{errand,} and then turn the key upon her, you would \textcolor{green}{facilitate}

 matters immensely."



 "I will do it."



 \textcolor{green}{"Excellent!} We shall then look thoroughly into the affair. Of

 course there is only one feasible explanation. You have been

 brought there to personate someone, and the \textcolor{green}{real} person is

 \textcolor{red}{imprisoned} in this chamber. That is \textcolor{green}{obvious.} As to who this

 \textcolor{red}{prisoner} is, I have no \textcolor{BurntOrange}{doubt} that it is the \textcolor{green}{daughter,} Miss Alice

 Rucastle, if I remember right, who was said to have gone to

 America. You were \textcolor{green}{chosen,} \textcolor{green}{doubtless,} as resembling her in height,

 figure, and the colour of your hair. Hers had been cut off, very

 possibly in some \textcolor{red}{illness} through which she has passed, and so, of

 course, yours had to be sacrificed also. By a curious \textcolor{blue}{chance} you

 came upon her tresses. The man in the road was undoubtedly some

 \textcolor{green}{friend} of hers--possibly her fiancé--and no \textcolor{BurntOrange}{doubt,} as you wore

 the girl's dress and were so like her, he was \textcolor{BurntOrange}{convinced} from your

 \textcolor{BurntOrange}{laughter,} whenever he saw you, and afterwards from your gesture,

 that Miss Rucastle was perfectly \textcolor{BurntOrange}{happy,} and that she no longer

 desired his \textcolor{green}{attentions.} The dog is let loose at night to \textcolor{red}{prevent}

 him from endeavouring to \textcolor{green}{communicate} with her. So much is \textcolor{green}{fairly}

 clear. The most serious point in the \textcolor{red}{case} is the disposition of

 the \textcolor{BurntOrange}{child."}



 "What on earth has that to do with it?" I ejaculated.



 "My \textcolor{green}{dear} Watson, you as a \textcolor{BurntOrange}{medical} man are continually \textcolor{BurntOrange}{gaining}

 light as to the tendencies of a \textcolor{BurntOrange}{child} by the \textcolor{green}{study} of the

 parents. Don't you see that the converse is \textcolor{green}{equally} valid. I have

 frequently \textcolor{BurntOrange}{gained} my first \textcolor{green}{real} insight into the character of

 parents by \textcolor{green}{studying} their \textcolor{BurntOrange}{children.} This \textcolor{BurntOrange}{child's} disposition is

 abnormally \textcolor{red}{cruel,} merely for \textcolor{red}{cruelty's} sake, and whether he

 derives this from his \textcolor{BurntOrange}{smiling} \textcolor{green}{father,} as I should \textcolor{red}{suspect,} or

 from his \textcolor{BurntOrange}{mother,} it bodes \textcolor{red}{evil} for the poor girl who is in their

 power."



 "I am sure that you are right, Mr. Holmes," \textcolor{red}{cried} our client. "A

 thousand things come back to me which make me certain that you

 have \textcolor{red}{hit} it. Oh, let us \textcolor{BurntOrange}{lose} not an instant in bringing help to

 this poor \textcolor{red}{creature."}



 "We must be circumspect, for we are \textcolor{BurntOrange}{dealing} with a very \textcolor{BurntOrange}{cunning}

 man. We can do nothing until seven o'clock. At that hour we shall

 be with you, and it will not be \textcolor{blue}{long} before we solve the

 \textcolor{blue}{mystery."}



 We were as \textcolor{BurntOrange}{good} as our \textcolor{green}{word,} for it was just seven when we

 reached the Copper Beeches, having put up our trap at a wayside

 public-house. The group of \textcolor{BurntOrange}{trees,} with their \textcolor{red}{dark} leaves shining

 like burnished metal in the light of the setting \textcolor{BurntOrange}{sun,} were

 sufficient to mark the house even had Miss \textcolor{BurntOrange}{Hunter} not been

 standing \textcolor{BurntOrange}{smiling} on the door-step.



 "Have you \textcolor{green}{managed} it?" asked Holmes.



 A loud thudding \textcolor{red}{noise} came from somewhere downstairs. "That is

 Mrs. Toller in the cellar," said she. "Her husband \textcolor{red}{lies} snoring

 on the kitchen rug. Here are his keys, which are the duplicates

 of Mr. Rucastle's."



 "You have done well indeed!" \textcolor{red}{cried} Holmes with \textcolor{BurntOrange}{enthusiasm.} "Now

 \textcolor{green}{lead} the way, and we shall soon see the end of this \textcolor{red}{black}

 business."



 We passed up the stair, unlocked the door, followed on down a

 passage, and \textcolor{green}{found} ourselves in front of the \textcolor{red}{barricade} which Miss

 \textcolor{BurntOrange}{Hunter} had described. Holmes cut the cord and \textcolor{red}{removed} the

 transverse bar. Then he tried the various keys in the lock, but

 without \textcolor{BurntOrange}{success.} No sound came from within, and at the silence

 Holmes' face clouded over.



 "I \textcolor{green}{trust} that we are not too \textcolor{red}{late,"} said he. "I think, Miss

 \textcolor{BurntOrange}{Hunter,} that we had better go in without you. Now, Watson, put

 your \textcolor{green}{shoulder} to it, and we shall see whether we cannot make our

 way in."



 It was an old \textcolor{red}{rickety} door and gave at once before our \textcolor{green}{united}

 \textcolor{green}{strength.} Together we rushed into the room. It was empty. There

 was no furniture \textcolor{green}{save} a little pallet bed, a \textcolor{red}{small} table, and a

 basketful of linen. The skylight above was open, and the \textcolor{red}{prisoner}

 gone.



 "There has been some villainy here," said Holmes; "this \textcolor{green}{beauty}

 has \textcolor{blue}{guessed} Miss \textcolor{BurntOrange}{Hunter's} intentions and has carried his \textcolor{red}{victim}

 off."



 "But how?"



 "Through the skylight. We shall soon see how he \textcolor{green}{managed} it." He

 swung himself up onto the roof. "Ah, yes," he \textcolor{red}{cried,} "here's the

 end of a \textcolor{blue}{long} light ladder against the eaves. That is how he did

 it."



 "But it is \textcolor{red}{impossible,"} said Miss \textcolor{BurntOrange}{Hunter;} "the ladder was not

 there when the Rucastles went away."



 "He has come back and done it. I tell you that he is a \textcolor{green}{clever} and

 \textcolor{red}{dangerous} man. I should not be very much \textcolor{blue}{surprised} if this were

 he whose step I hear now upon the stair. I think, Watson, that it

 would be as well for you to have your \textcolor{red}{pistol} \textcolor{blue}{ready."}



 The \textcolor{green}{words} were hardly out of his \textcolor{blue}{mouth} before a man appeared at

 the door of the room, a very \textcolor{red}{fat} and burly man, with a heavy

 stick in his hand. Miss \textcolor{BurntOrange}{Hunter} \textcolor{BurntOrange}{screamed} and \textcolor{red}{shrunk} against the

 wall at the sight of him, but Sherlock Holmes sprang \textcolor{green}{forward} and

 \textcolor{red}{confronted} him.



 "You \textcolor{red}{villain!"} said he, "where's your \textcolor{green}{daughter?"}



 The \textcolor{red}{fat} man cast his eyes round, and then up at the open

 skylight.



 "It is for me to ask you that," he \textcolor{BurntOrange}{shrieked,} "you \textcolor{BurntOrange}{thieves!} Spies

 and \textcolor{BurntOrange}{thieves!} I have caught you, have I? You are in my power. \textcolor{red}{I'll}

 \textcolor{BurntOrange}{serve} you!" He turned and clattered down the stairs as hard as he

 could go.



 "He's gone for the dog!" \textcolor{red}{cried} Miss \textcolor{BurntOrange}{Hunter.}



 "I have my \textcolor{red}{revolver,"} said I.



 "Better close the front door," \textcolor{red}{cried} Holmes, and we all rushed

 down the stairs together. We had hardly reached the hall when we

 heard the baying of a hound, and then a \textcolor{BurntOrange}{scream} of \textcolor{red}{agony,} with a

 \textcolor{red}{horrible} \textcolor{BurntOrange}{worrying} sound which it was \textcolor{BurntOrange}{dreadful} to listen to. An

 elderly man with a red face and shaking limbs came \textcolor{blue}{staggering} out

 at a side door.



 "My \textcolor{BurntOrange}{God!"} he \textcolor{red}{cried.} "Someone has loosed the dog. It's not been

 fed for two days. Quick, quick, or it'll be too \textcolor{red}{late!"}



 Holmes and I rushed out and round the angle of the house, with

 Toller \textcolor{blue}{hurrying} behind us. There was the huge famished \textcolor{red}{brute,} its

 \textcolor{red}{black} \textcolor{red}{muzzle} \textcolor{red}{buried} in Rucastle's throat, while he writhed and

 \textcolor{BurntOrange}{screamed} upon the \textcolor{green}{ground.} Running up, I blew its brains out, and

 it \textcolor{red}{fell} over with its keen \textcolor{BurntOrange}{white} teeth still meeting in the great

 creases of his neck. With much labour we separated them and

 carried him, living but \textcolor{red}{horribly} \textcolor{red}{mangled,} into the house. We laid

 him upon the drawing-room sofa, and having dispatched the sobered

 Toller to \textcolor{red}{bear} the news to his wife, I did what I could to

 relieve his \textcolor{red}{pain.} We were all assembled round him when the door

 opened, and a tall, \textcolor{red}{gaunt} woman entered the room.



 "Mrs. Toller!" \textcolor{red}{cried} Miss \textcolor{BurntOrange}{Hunter.}



 "Yes, miss. Mr. Rucastle let me out when he came back before he

 went up to you. Ah, miss, it is a \textcolor{red}{pity} you didn't let me know

 what you were \textcolor{BurntOrange}{planning,} for I would have told you that your \textcolor{red}{pains}

 were \textcolor{red}{wasted."}



 "Ha!" said Holmes, looking keenly at her. "It is clear that Mrs.

 Toller knows more about this matter than anyone else."



 "Yes, \textcolor{green}{sir,} I do, and I am \textcolor{blue}{ready} enough to tell what I know."



 "Then, \textcolor{BurntOrange}{pray,} sit down, and let us hear it for there are several

 points on which I must \textcolor{BurntOrange}{confess} that I am still in the \textcolor{red}{dark."}



 "I will soon make it clear to you," said she; "and I'd have done

 so before now if I could ha' got out from the cellar. If there's

 police-court business over this, you'll remember that I was the

 one that stood your \textcolor{green}{friend,} and that I was Miss Alice's \textcolor{green}{friend}

 too.



 "She was never \textcolor{BurntOrange}{happy} at home, Miss Alice wasn't, from the \textcolor{blue}{time}

 that her \textcolor{green}{father} married again. She was slighted like and had no

 say in anything, but it never really became \textcolor{red}{bad} for her until

 after she met Mr. Fowler at a \textcolor{green}{friend's} house. As well as I could

 \textcolor{green}{learn,} Miss Alice had rights of her own by will, but she was so

 \textcolor{BurntOrange}{quiet} and \textcolor{BurntOrange}{patient,} she was, that she never said a \textcolor{green}{word} about them

 but just left everything in Mr. Rucastle's hands. He knew he was

 \textcolor{green}{safe} with her; but when there was a \textcolor{blue}{chance} of a husband coming

 \textcolor{green}{forward,} who would ask for all that the \textcolor{green}{law} would give him, then

 her \textcolor{green}{father} \textcolor{blue}{thought} it \textcolor{blue}{time} to put a stop on it. He wanted her to

 sign a paper, so that whether she married or not, he could use

 her \textcolor{BurntOrange}{money.} When she wouldn't do it, he kept on \textcolor{BurntOrange}{worrying} her until

 she got brain-fever, and for six weeks was at \textcolor{BurntOrange}{death's} door. Then

 she got better at last, all \textcolor{red}{worn} to a shadow, and with her

 \textcolor{green}{beautiful} hair cut off; but that didn't make no \textcolor{red}{change} in her

 \textcolor{BurntOrange}{young} man, and he stuck to her as \textcolor{green}{true} as man could be."



 "Ah," said Holmes, "I think that what you have been \textcolor{BurntOrange}{good} enough

 to tell us makes the matter \textcolor{green}{fairly} clear, and that I can deduce

 all that \textcolor{BurntOrange}{remains.} Mr. Rucastle then, I presume, took to this

 \textcolor{green}{system} of \textcolor{red}{imprisonment?"}



 "Yes, \textcolor{green}{sir."}



 "And brought Miss \textcolor{BurntOrange}{Hunter} down from London in order to get rid of

 the disagreeable \textcolor{green}{persistence} of Mr. Fowler."



 "That was it, \textcolor{green}{sir."}



 "But Mr. Fowler being a persevering man, as a \textcolor{BurntOrange}{good} seaman should

 be, \textcolor{red}{blockaded} the house, and having met you \textcolor{BurntOrange}{succeeded} by certain

 \textcolor{red}{arguments,} metallic or otherwise, in \textcolor{green}{convincing} you that your

 \textcolor{green}{interests} were the same as his."



 "Mr. Fowler was a very kind-spoken, free-handed \textcolor{green}{gentleman,"} said

 Mrs. Toller serenely.



 "And in this way he \textcolor{green}{managed} that your \textcolor{BurntOrange}{good} man should have no

 want of drink, and that a ladder should be \textcolor{blue}{ready} at the moment

 when your \textcolor{green}{master} had gone out."



 "You have it, \textcolor{green}{sir,} just as it \textcolor{blue}{happened."}



 "I am sure we owe you an \textcolor{green}{apology,} Mrs. Toller," said Holmes, "for

 you have certainly cleared up everything which puzzled us. And

 here comes the country surgeon and Mrs. Rucastle, so I think,

 Watson, that we had best \textcolor{green}{escort} Miss \textcolor{BurntOrange}{Hunter} back to Winchester,

 as it seems to me that our locus standi now is rather a

 \textcolor{red}{questionable} one."



 And thus was solved the \textcolor{blue}{mystery} of the \textcolor{red}{sinister} house with the

 copper beeches in front of the door. Mr. Rucastle \textcolor{green}{survived,} but

 was always a \textcolor{red}{broken} man, kept \textcolor{BurntOrange}{alive} solely through the care of

 his devoted wife. They still live with their old \textcolor{BurntOrange}{servants,} who

 probably know so much of Rucastle's past life that he finds it

 \textcolor{red}{difficult} to part from them. Mr. Fowler and Miss Rucastle were

 married, by \textcolor{green}{special} license, in Southampton the day after their

 flight, and he is now the holder of a \textcolor{red}{government} appointment in

 the island of Mauritius. As to Miss Violet \textcolor{BurntOrange}{Hunter,} my \textcolor{green}{friend}

 Holmes, rather to my \textcolor{red}{disappointment,} manifested no further

 \textcolor{green}{interest} in her when once she had ceased to be the centre of one

 of his \textcolor{red}{problems,} and she is now the head of a private \textcolor{green}{school} at

 Walsall, where I believe that she has met with \textcolor{green}{considerable} \textcolor{BurntOrange}{success.}



















 End of the Project Gutenberg EBook of The \textcolor{BurntOrange}{Adventures} of Sherlock Holmes, by

 Arthur Conan Doyle



 *** END OF THIS PROJECT GUTENBERG EBOOK THE \textcolor{BurntOrange}{ADVENTURES} OF SHERLOCK HOLMES ***



 ***** This file should be named 1661-8.txt or 1661-8.zip *****

 This and all \textcolor{green}{associated} files of various formats will be \textcolor{green}{found} in:

 http://www.gutenberg.org/1/6/6/1661/



 Produced by an \textcolor{red}{anonymous} Project Gutenberg \textcolor{BurntOrange}{volunteer} and Jose Menendez



 Updated \textcolor{blue}{editions} will replace the previous one--the old \textcolor{blue}{editions}

 will be renamed.



 \textcolor{green}{Creating} the works from \textcolor{BurntOrange}{public} domain print \textcolor{blue}{editions} means that no

 one owns a \textcolor{green}{United} States copyright in these works, so the \textcolor{green}{Foundation}

 (and you!) can \textcolor{red}{copy} and distribute it in the \textcolor{green}{United} States without

 \textcolor{green}{permission} and without \textcolor{BurntOrange}{paying} copyright \textcolor{green}{royalties.} \textcolor{green}{Special} \textcolor{BurntOrange}{rules,}

 set forth in the \textcolor{green}{General} Terms of Use part of this license, apply to

 copying and distributing Project Gutenberg-tm electronic works to

 \textcolor{green}{protect} the PROJECT GUTENBERG-tm concept and trademark. Project

 Gutenberg is a registered trademark, and may not be used if you

 charge for the eBooks, unless you receive specific \textcolor{green}{permission.} If you

 do not charge anything for \textcolor{red}{copies} of this eBook, complying with the

 \textcolor{BurntOrange}{rules} is very easy. You may use this eBook for nearly any purpose

 such as creation of derivative works, reports, performances and

 research. They may be \textcolor{blue}{modified} and printed and given away--you may do

 practically ANYTHING with \textcolor{BurntOrange}{public} domain eBooks. Redistribution is

 \textcolor{red}{subject} to the trademark license, especially commercial

 redistribution.







 *** \textcolor{blue}{START:} \textcolor{green}{FULL} LICENSE ***



 THE \textcolor{green}{FULL} PROJECT GUTENBERG LICENSE

 PLEASE READ THIS BEFORE YOU DISTRIBUTE OR USE THIS WORK



 To \textcolor{green}{protect} the Project Gutenberg-tm mission of promoting the free

 distribution of electronic works, by using or distributing this work

 (or any other work \textcolor{green}{associated} in any way with the phrase "Project

 Gutenberg"), you \textcolor{green}{agree} to comply with all the terms of the \textcolor{green}{Full} Project

 Gutenberg-tm License (available with this file or online at

 http://gutenberg.net/license).





 Section 1. \textcolor{green}{General} Terms of Use and Redistributing Project Gutenberg-tm

 electronic works



 1.A. By \textcolor{green}{reading} or using any part of this Project Gutenberg-tm

 electronic work, you indicate that you have read, understand, \textcolor{green}{agree} to

 and accept all the terms of this license and \textcolor{green}{intellectual} property

 (trademark/copyright) \textcolor{green}{agreement.} If you do not \textcolor{green}{agree} to abide by all

 the terms of this \textcolor{green}{agreement,} you must cease using and return or destroy

 all \textcolor{red}{copies} of Project Gutenberg-tm electronic works in your \textcolor{red}{possession.}

 If you paid a \textcolor{red}{fee} for obtaining a \textcolor{red}{copy} of or access to a Project

 Gutenberg-tm electronic work and you do not \textcolor{green}{agree} to be \textcolor{red}{bound} by the

 terms of this \textcolor{green}{agreement,} you may obtain a refund from the person or

 entity to whom you paid the \textcolor{red}{fee} as set forth in paragraph 1.E.8.



 1.B. "Project Gutenberg" is a registered trademark. It may only be

 used on or \textcolor{green}{associated} in any way with an electronic work by people who

 \textcolor{green}{agree} to be \textcolor{red}{bound} by the terms of this \textcolor{green}{agreement.} There are a few

 things that you can do with most Project Gutenberg-tm electronic works

 even without complying with the \textcolor{green}{full} terms of this \textcolor{green}{agreement.} See

 paragraph 1.C below. There are a lot of things you can do with Project

 Gutenberg-tm electronic works if you follow the terms of this \textcolor{green}{agreement}

 and help \textcolor{green}{preserve} free future access to Project Gutenberg-tm electronic

 works. See paragraph 1.E below.



 1.C. The Project Gutenberg Literary Archive \textcolor{green}{Foundation} ("the \textcolor{green}{Foundation"}

 or PGLAF), owns a compilation copyright in the collection of Project

 Gutenberg-tm electronic works. Nearly all the individual works in the

 collection are in the \textcolor{BurntOrange}{public} domain in the \textcolor{green}{United} States. If an

 individual work is in the \textcolor{BurntOrange}{public} domain in the \textcolor{green}{United} States and you are

 located in the \textcolor{green}{United} States, we do not claim a right to \textcolor{red}{prevent} you from

 copying, distributing, performing, displaying or \textcolor{green}{creating} derivative

 works \textcolor{green}{based} on the work as \textcolor{blue}{long} as all references to Project Gutenberg

 are \textcolor{red}{removed.} Of course, we \textcolor{BurntOrange}{hope} that you will support the Project

 Gutenberg-tm mission of promoting free access to electronic works by

 \textcolor{green}{freely} \textcolor{BurntOrange}{sharing} Project Gutenberg-tm works in \textcolor{green}{compliance} with the terms of

 this \textcolor{green}{agreement} for keeping the Project Gutenberg-tm name \textcolor{green}{associated} with

 the work. You can easily comply with the terms of this \textcolor{green}{agreement} by

 keeping this work in the same format with its attached \textcolor{green}{full} Project

 Gutenberg-tm License when you \textcolor{BurntOrange}{share} it without charge with others.



 1.D. The copyright \textcolor{green}{laws} of the place where you are located also \textcolor{green}{govern}

 what you can do with this work. Copyright \textcolor{green}{laws} in most countries are in

 a \textcolor{green}{constant} state of \textcolor{red}{change.} If you are outside the \textcolor{green}{United} States, check

 the \textcolor{green}{laws} of your country in addition to the terms of this \textcolor{green}{agreement}

 before downloading, copying, displaying, performing, distributing or

 \textcolor{green}{creating} derivative works \textcolor{green}{based} on this work or any other Project

 Gutenberg-tm work. The \textcolor{green}{Foundation} makes no representations concerning

 the copyright \textcolor{green}{status} of any work in any country outside the \textcolor{green}{United}

 States.



 1.E. Unless you have \textcolor{red}{removed} all references to Project Gutenberg:



 1.E.1. The following \textcolor{BurntOrange}{sentence,} with active links to, or other immediate

 access to, the \textcolor{green}{full} Project Gutenberg-tm License must appear \textcolor{green}{prominently}

 whenever any \textcolor{red}{copy} of a Project Gutenberg-tm work (any work on which the

 phrase "Project Gutenberg" appears, or with which the phrase "Project

 Gutenberg" is \textcolor{green}{associated)} is accessed, displayed, performed, viewed,

 \textcolor{red}{copied} or distributed:



 This eBook is for the use of anyone anywhere at no cost and with

 almost no \textcolor{red}{restrictions} whatsoever. You may \textcolor{red}{copy} it, give it away or

 re-use it under the terms of the Project Gutenberg License \textcolor{green}{included}

 with this eBook or online at www.gutenberg.net



 1.E.2. If an individual Project Gutenberg-tm electronic work is derived

 from the \textcolor{BurntOrange}{public} domain (does not contain a notice indicating that it is

 posted with \textcolor{green}{permission} of the copyright holder), the work can be \textcolor{red}{copied}

 and distributed to anyone in the \textcolor{green}{United} States without \textcolor{BurntOrange}{paying} any \textcolor{red}{fees}

 or charges. If you are redistributing or \textcolor{green}{providing} access to a work

 with the phrase "Project Gutenberg" \textcolor{green}{associated} with or appearing on the

 work, you must comply either with the requirements of paragraphs 1.E.1

 through 1.E.7 or obtain \textcolor{green}{permission} for the use of the work and the

 Project Gutenberg-tm trademark as set forth in paragraphs 1.E.8 or

 1.E.9.



 1.E.3. If an individual Project Gutenberg-tm electronic work is posted

 with the \textcolor{green}{permission} of the copyright holder, your use and distribution

 must comply with both paragraphs 1.E.1 through 1.E.7 and any additional

 terms imposed by the copyright holder. Additional terms will be linked

 to the Project Gutenberg-tm License for all works posted with the

 \textcolor{green}{permission} of the copyright holder \textcolor{green}{found} at the beginning of this work.



 1.E.4. Do not unlink or detach or \textcolor{red}{remove} the \textcolor{green}{full} Project Gutenberg-tm

 License terms from this work, or any files containing a part of this

 work or any other work \textcolor{green}{associated} with Project Gutenberg-tm.



 1.E.5. Do not \textcolor{red}{copy,} display, perform, distribute or redistribute this

 electronic work, or any part of this electronic work, without

 \textcolor{green}{prominently} displaying the \textcolor{BurntOrange}{sentence} set forth in paragraph 1.E.1 with

 active links or immediate access to the \textcolor{green}{full} terms of the Project

 Gutenberg-tm License.



 1.E.6. You may \textcolor{green}{convert} to and distribute this work in any binary,

 \textcolor{red}{compressed,} \textcolor{green}{marked} up, nonproprietary or proprietary form, \textcolor{green}{including} any

 \textcolor{green}{word} processing or hypertext form. However, if you \textcolor{green}{provide} access to or

 distribute \textcolor{red}{copies} of a Project Gutenberg-tm work in a format other than

 "Plain Vanilla ASCII" or other format used in the \textcolor{green}{official} version

 posted on the \textcolor{green}{official} Project Gutenberg-tm web site (www.gutenberg.net),

 you must, at no additional cost, \textcolor{red}{fee} or expense to the user, \textcolor{green}{provide} a

 \textcolor{red}{copy,} a means of exporting a \textcolor{red}{copy,} or a means of obtaining a \textcolor{red}{copy} upon

 request, of the work in its original "Plain Vanilla ASCII" or other

 form. Any alternate format must \textcolor{green}{include} the \textcolor{green}{full} Project Gutenberg-tm

 License as specified in paragraph 1.E.1.



 1.E.7. Do not charge a \textcolor{red}{fee} for access to, viewing, displaying,

 performing, copying or distributing any Project Gutenberg-tm works

 unless you comply with paragraph 1.E.8 or 1.E.9.



 1.E.8. You may charge a reasonable \textcolor{red}{fee} for \textcolor{red}{copies} of or \textcolor{green}{providing}

 access to or distributing Project Gutenberg-tm electronic works \textcolor{green}{provided}

 that



 - You \textcolor{BurntOrange}{pay} a \textcolor{green}{royalty} \textcolor{red}{fee} of 20% of the \textcolor{red}{gross} profits you derive from

 the use of Project Gutenberg-tm works calculated using the method

 you already use to calculate your applicable \textcolor{red}{taxes.} The \textcolor{red}{fee} is

 owed to the owner of the Project Gutenberg-tm trademark, but he

 has \textcolor{green}{agreed} to donate \textcolor{green}{royalties} under this paragraph to the

 Project Gutenberg Literary Archive \textcolor{green}{Foundation.} \textcolor{green}{Royalty} \textcolor{red}{payments}

 must be paid within 60 days following each date on which you

 \textcolor{BurntOrange}{prepare} (or are legally required to \textcolor{BurntOrange}{prepare)} your periodic \textcolor{red}{tax}

 returns. \textcolor{green}{Royalty} \textcolor{red}{payments} should be clearly \textcolor{green}{marked} as such and

 sent to the Project Gutenberg Literary Archive \textcolor{green}{Foundation} at the

 address specified in Section 4, \textcolor{green}{"Information} about \textcolor{green}{donations} to

 the Project Gutenberg Literary Archive \textcolor{green}{Foundation."}



 - You \textcolor{green}{provide} a \textcolor{green}{full} refund of any \textcolor{BurntOrange}{money} paid by a user who notifies

 you in writing (or by e-mail) within 30 days of receipt that s/he

 does not \textcolor{green}{agree} to the terms of the \textcolor{green}{full} Project Gutenberg-tm

 License. You must require such a user to return or

 destroy all \textcolor{red}{copies} of the works \textcolor{BurntOrange}{possessed} in a physical medium

 and \textcolor{red}{discontinue} all use of and all access to other \textcolor{red}{copies} of

 Project Gutenberg-tm works.



 - You \textcolor{green}{provide,} in accordance with paragraph 1.F.3, a \textcolor{green}{full} refund of any

 \textcolor{BurntOrange}{money} paid for a work or a replacement \textcolor{red}{copy,} if a \textcolor{red}{defect} in the

 electronic work is discovered and reported to you within 90 days

 of receipt of the work.



 - You comply with all other terms of this \textcolor{green}{agreement} for free

 distribution of Project Gutenberg-tm works.



 1.E.9. If you wish to charge a \textcolor{red}{fee} or distribute a Project Gutenberg-tm

 electronic work or group of works on different terms than are set

 forth in this \textcolor{green}{agreement,} you must obtain \textcolor{green}{permission} in writing from

 both the Project Gutenberg Literary Archive \textcolor{green}{Foundation} and Michael

 Hart, the owner of the Project Gutenberg-tm trademark. \textcolor{green}{Contact} the

 \textcolor{green}{Foundation} as set forth in Section 3 below.



 1.F.



 1.F.1. Project Gutenberg \textcolor{BurntOrange}{volunteers} and employees expend \textcolor{green}{considerable}

 \textcolor{green}{effort} to identify, do copyright research on, transcribe and proofread

 \textcolor{BurntOrange}{public} domain works in \textcolor{green}{creating} the Project Gutenberg-tm

 collection. Despite these \textcolor{green}{efforts,} Project Gutenberg-tm electronic

 works, and the medium on which they may be \textcolor{BurntOrange}{stored,} may contain

 \textcolor{red}{"Defects,"} such as, but not \textcolor{red}{limited} to, incomplete, \textcolor{red}{inaccurate} or

 \textcolor{red}{corrupt} data, transcription \textcolor{red}{errors,} a copyright or other \textcolor{green}{intellectual}

 property \textcolor{red}{infringement,} a \textcolor{red}{defective} or \textcolor{red}{damaged} disk or other medium, a

 computer \textcolor{red}{virus,} or computer codes that \textcolor{red}{damage} or cannot be read by

 your equipment.



 1.F.2. \textcolor{red}{LIMITED} \textcolor{green}{WARRANTY,} DISCLAIMER OF \textcolor{red}{DAMAGES} - Except for the "Right

 of Replacement or Refund" described in paragraph 1.F.3, the Project

 Gutenberg Literary Archive \textcolor{green}{Foundation,} the owner of the Project

 Gutenberg-tm trademark, and any other party distributing a Project

 Gutenberg-tm electronic work under this \textcolor{green}{agreement,} \textcolor{BurntOrange}{disclaim} all

 liability to you for \textcolor{red}{damages,} costs and expenses, \textcolor{green}{including} \textcolor{green}{legal}

 \textcolor{red}{fees.} YOU \textcolor{green}{AGREE} THAT YOU HAVE NO \textcolor{BurntOrange}{REMEDIES} FOR \textcolor{red}{NEGLIGENCE,} STRICT

 LIABILITY, \textcolor{red}{BREACH} OF \textcolor{green}{WARRANTY} OR \textcolor{red}{BREACH} OF CONTRACT EXCEPT THOSE

 \textcolor{green}{PROVIDED} IN PARAGRAPH 1.F.3. YOU \textcolor{green}{AGREE} THAT THE \textcolor{green}{FOUNDATION,} THE

 TRADEMARK OWNER, AND ANY DISTRIBUTOR UNDER THIS \textcolor{green}{AGREEMENT} WILL NOT BE

 LIABLE TO YOU FOR \textcolor{green}{ACTUAL,} DIRECT, INDIRECT, CONSEQUENTIAL, \textcolor{red}{PUNITIVE} OR

 INCIDENTAL \textcolor{red}{DAMAGES} EVEN IF YOU GIVE NOTICE OF THE \textcolor{blue}{POSSIBILITY} OF SUCH

 \textcolor{red}{DAMAGE.}



 1.F.3. \textcolor{red}{LIMITED} RIGHT OF REPLACEMENT OR REFUND - If you discover a

 \textcolor{red}{defect} in this electronic work within 90 days of receiving it, you can

 receive a refund of the \textcolor{BurntOrange}{money} (if any) you paid for it by sending a

 written explanation to the person you received the work from. If you

 received the work on a physical medium, you must return the medium with

 your written explanation. The person or entity that \textcolor{green}{provided} you with

 the \textcolor{red}{defective} work may \textcolor{green}{elect} to \textcolor{green}{provide} a replacement \textcolor{red}{copy} in lieu of a

 refund. If you received the work electronically, the person or entity

 \textcolor{green}{providing} it to you may choose to give you a second \textcolor{BurntOrange}{opportunity} to

 receive the work electronically in lieu of a refund. If the second \textcolor{red}{copy}

 is also \textcolor{red}{defective,} you may \textcolor{red}{demand} a refund in writing without further

 \textcolor{BurntOrange}{opportunities} to fix the \textcolor{red}{problem.}



 1.F.4. Except for the \textcolor{red}{limited} right of replacement or refund set forth

 in paragraph 1.F.3, this work is \textcolor{green}{provided} to you 'AS-IS' WITH NO OTHER

 \textcolor{green}{WARRANTIES} OF ANY \textcolor{green}{KIND,} EXPRESS OR IMPLIED, \textcolor{green}{INCLUDING} BUT NOT \textcolor{red}{LIMITED} TO

 \textcolor{green}{WARRANTIES} OF MERCHANTIBILITY OR FITNESS FOR ANY PURPOSE.



 1.F.5. Some states do not allow disclaimers of certain implied

 \textcolor{green}{warranties} or the \textcolor{red}{exclusion} or limitation of certain types of \textcolor{red}{damages.}

 If any disclaimer or limitation set forth in this \textcolor{green}{agreement} violates the

 \textcolor{green}{law} of the state applicable to this \textcolor{green}{agreement,} the \textcolor{green}{agreement} shall be

 interpreted to make the \textcolor{green}{maximum} disclaimer or limitation permitted by

 the applicable state \textcolor{green}{law.} The \textcolor{red}{invalidity} or unenforceability of any

 provision of this \textcolor{green}{agreement} shall not void the remaining provisions.



 1.F.6. \textcolor{green}{INDEMNITY} - You \textcolor{green}{agree} to \textcolor{red}{indemnify} and hold the \textcolor{green}{Foundation,} the

 trademark owner, any agent or employee of the \textcolor{green}{Foundation,} anyone

 \textcolor{green}{providing} \textcolor{red}{copies} of Project Gutenberg-tm electronic works in accordance

 with this \textcolor{green}{agreement,} and any \textcolor{BurntOrange}{volunteers} \textcolor{green}{associated} with the \textcolor{BurntOrange}{production,}

 \textcolor{green}{promotion} and distribution of Project Gutenberg-tm electronic works,

 harmless from all liability, costs and expenses, \textcolor{green}{including} \textcolor{green}{legal} \textcolor{red}{fees,}

 that arise directly or indirectly from any of the following which you do

 or cause to occur: (a) distribution of this or any Project Gutenberg-tm

 work, (b) alteration, modification, or additions or \textcolor{red}{deletions} to any

 Project Gutenberg-tm work, and (c) any \textcolor{red}{Defect} you cause.





 Section 2. \textcolor{green}{Information} about the Mission of Project Gutenberg-tm



 Project Gutenberg-tm is \textcolor{BurntOrange}{synonymous} with the free distribution of

 electronic works in formats readable by the widest variety of computers

 \textcolor{green}{including} obsolete, old, middle-aged and new computers. It exists

 because of the \textcolor{green}{efforts} of hundreds of \textcolor{BurntOrange}{volunteers} and \textcolor{green}{donations} from

 people in all walks of life.



 \textcolor{BurntOrange}{Volunteers} and financial support to \textcolor{green}{provide} \textcolor{BurntOrange}{volunteers} with the

 \textcolor{green}{assistance} they need are critical to reaching Project Gutenberg-tm's

 goals and ensuring that the Project Gutenberg-tm collection will

 remain \textcolor{green}{freely} available for generations to come. In 2001, the Project

 Gutenberg Literary Archive \textcolor{green}{Foundation} was \textcolor{green}{created} to \textcolor{green}{provide} a secure

 and permanent future for Project Gutenberg-tm and future generations.

 To \textcolor{green}{learn} more about the Project Gutenberg Literary Archive \textcolor{green}{Foundation}

 and how your \textcolor{green}{efforts} and \textcolor{green}{donations} can help, see Sections 3 and 4

 and the \textcolor{green}{Foundation} web page at http://www.pglaf.org.





 Section 3. \textcolor{green}{Information} about the Project Gutenberg Literary Archive

 \textcolor{green}{Foundation}



 The Project Gutenberg Literary Archive \textcolor{green}{Foundation} is a non profit

 501(c)(3) \textcolor{green}{educational} \textcolor{green}{corporation} \textcolor{green}{organized} under the \textcolor{green}{laws} of the

 state of Mississippi and \textcolor{BurntOrange}{granted} \textcolor{red}{tax} exempt \textcolor{green}{status} by the Internal

 Revenue Service. The \textcolor{green}{Foundation's} EIN or federal \textcolor{red}{tax} identification

 number is 64-6221541. Its 501(c)(3) \textcolor{blue}{letter} is posted at

 http://pglaf.org/fundraising. Contributions to the Project Gutenberg

 Literary Archive \textcolor{green}{Foundation} are \textcolor{red}{tax} deductible to the \textcolor{green}{full} extent

 permitted by U.S. federal \textcolor{green}{laws} and your state's \textcolor{green}{laws.}



 The \textcolor{green}{Foundation's} \textcolor{green}{principal} office is located at 4557 Melan Dr. S.

 Fairbanks, AK, 99712., but its \textcolor{BurntOrange}{volunteers} and employees are scattered

 throughout numerous locations. Its business office is located at

 809 North 1500 West, Salt Lake City, UT 84116, (801) 596-1887, email

 business@pglaf.org. Email \textcolor{green}{contact} links and up to date \textcolor{green}{contact}

 \textcolor{green}{information} can be \textcolor{green}{found} at the \textcolor{green}{Foundation's} web site and \textcolor{green}{official}

 page at http://pglaf.org



 For additional \textcolor{green}{contact} \textcolor{green}{information:}

 Dr. Gregory B. Newby

 Chief Executive and \textcolor{green}{Director}

 gbnewby@pglaf.org





 Section 4. \textcolor{green}{Information} about \textcolor{green}{Donations} to the Project Gutenberg

 Literary Archive \textcolor{green}{Foundation}



 Project Gutenberg-tm depends upon and cannot \textcolor{green}{survive} without wide

 spread \textcolor{BurntOrange}{public} support and \textcolor{green}{donations} to carry out its mission of

 \textcolor{green}{increasing} the number of \textcolor{BurntOrange}{public} domain and licensed works that can be

 \textcolor{green}{freely} distributed in \textcolor{green}{machine} readable form \textcolor{green}{accessible} by the widest

 \textcolor{green}{array} of equipment \textcolor{green}{including} outdated equipment. Many \textcolor{red}{small} \textcolor{green}{donations}

 ($1 to $5,000) are particularly \textcolor{green}{important} to maintaining \textcolor{red}{tax} exempt

 \textcolor{green}{status} with the IRS.



 The \textcolor{green}{Foundation} is committed to complying with the \textcolor{green}{laws} \textcolor{green}{regulating}

 \textcolor{green}{charities} and \textcolor{BurntOrange}{charitable} \textcolor{green}{donations} in all 50 states of the \textcolor{green}{United}

 States. \textcolor{green}{Compliance} requirements are not uniform and it takes a

 \textcolor{green}{considerable} \textcolor{green}{effort,} much paperwork and many \textcolor{red}{fees} to meet and keep up

 with these requirements. We do not solicit \textcolor{green}{donations} in locations

 where we have not received written \textcolor{green}{confirmation} of \textcolor{green}{compliance.} To

 SEND \textcolor{green}{DONATIONS} or determine the \textcolor{green}{status} of \textcolor{green}{compliance} for any

 particular state \textcolor{green}{visit} http://pglaf.org



 While we cannot and do not solicit contributions from states where we

 have not met the solicitation requirements, we know of no \textcolor{red}{prohibition}

 against accepting unsolicited \textcolor{green}{donations} from donors in such states who

 approach us with \textcolor{green}{offers} to donate.



 International \textcolor{green}{donations} are gratefully accepted, but we cannot make

 any \textcolor{green}{statements} concerning \textcolor{red}{tax} treatment of \textcolor{green}{donations} received from

 outside the \textcolor{green}{United} States. U.S. \textcolor{green}{laws} alone \textcolor{red}{swamp} our \textcolor{red}{small} staff.



 Please check the Project Gutenberg Web pages for current \textcolor{green}{donation}

 methods and addresses. \textcolor{green}{Donations} are accepted in a number of other

 ways \textcolor{green}{including} \textcolor{green}{including} checks, online \textcolor{red}{payments} and \textcolor{green}{credit} card

 \textcolor{green}{donations.} To donate, please \textcolor{green}{visit:} http://pglaf.org/donate





 Section 5. \textcolor{green}{General} \textcolor{green}{Information} About Project Gutenberg-tm electronic

 works.



 \textcolor{green}{Professor} Michael S. Hart is the originator of the Project Gutenberg-tm

 concept of a \textcolor{green}{library} of electronic works that could be \textcolor{green}{freely} \textcolor{BurntOrange}{shared}

 with anyone. For thirty years, he produced and distributed Project

 Gutenberg-tm eBooks with only a loose \textcolor{blue}{network} of \textcolor{BurntOrange}{volunteer} support.





 Project Gutenberg-tm eBooks are often \textcolor{green}{created} from several printed

 \textcolor{blue}{editions,} all of which are confirmed as \textcolor{BurntOrange}{Public} Domain in the U.S.

 unless a copyright notice is \textcolor{green}{included.} Thus, we do not necessarily

 keep eBooks in \textcolor{green}{compliance} with any particular paper \textcolor{blue}{edition.}





 Most people \textcolor{blue}{start} at our Web site which has the \textcolor{green}{main} PG search facility:



 http://www.gutenberg.net



 This Web site \textcolor{green}{includes} \textcolor{green}{information} about Project Gutenberg-tm,

 \textcolor{green}{including} how to make \textcolor{green}{donations} to the Project Gutenberg Literary

 Archive \textcolor{green}{Foundation,} how to help produce our new eBooks, and how to

 \textcolor{blue}{subscribe} to our email newsletter to hear about new eBooks.



