 ﻿Project Gutenberg’s Alice’s \textcolor{BurntOrange}{Adventures} in Wonderland, by Lewis Carroll



 This eBook is for the use of anyone anywhere at no cost and with

 almost no \textcolor{red}{restrictions} whatsoever. You may \textcolor{red}{copy} it, give it away or

 re-use it under the terms of the Project Gutenberg License \textcolor{green}{included}

 with this eBook or online at www.gutenberg.org





 \textcolor{green}{Title:} Alice’s \textcolor{BurntOrange}{Adventures} in Wonderland



 \textcolor{green}{Author:} Lewis Carroll



 Posting Date: June 25, 2008 [EBook #11]

 Release Date: \textcolor{green}{March,} 1994

 Last Updated: October 6, 2016



 Language: English



 Character set encoding: UTF-8



 *** \textcolor{blue}{START} OF THIS PROJECT GUTENBERG EBOOK ALICE’S \textcolor{BurntOrange}{ADVENTURES} IN WONDERLAND ***





















 ALICE’S \textcolor{BurntOrange}{ADVENTURES} IN WONDERLAND



 Lewis Carroll



 THE MILLENNIUM FULCRUM \textcolor{blue}{EDITION} 3.0









 CHAPTER I. Down the Rabbit-Hole



 Alice was beginning to get very tired of sitting by her sister on the

 \textcolor{green}{bank,} and of having nothing to do: once or twice she had peeped into the

 book her sister was \textcolor{green}{reading,} but it had no pictures or conversations in

 it, ‘and what is the use of a book,’ \textcolor{blue}{thought} Alice ‘without pictures or

 conversations?’



 So she was considering in her own mind (as well as she could, for the

 \textcolor{red}{hot} day made her feel very sleepy and \textcolor{red}{stupid),} whether the pleasure

 of making a daisy-chain would be \textcolor{green}{worth} the trouble of getting up and

 \textcolor{green}{picking} the daisies, when \textcolor{blue}{suddenly} a \textcolor{BurntOrange}{White} Rabbit with pink eyes ran

 close by her.



 There was nothing so VERY \textcolor{BurntOrange}{remarkable} in that; nor did Alice think it so

 VERY much out of the way to hear the Rabbit say to itself, ‘Oh \textcolor{green}{dear!}

 Oh \textcolor{green}{dear!} I shall be \textcolor{red}{late!’} (when she \textcolor{blue}{thought} it over afterwards, it

 occurred to her that she ought to have wondered at this, but at the \textcolor{blue}{time}

 it all seemed quite natural); but when the Rabbit actually TOOK A \textcolor{BurntOrange}{WATCH}

 OUT OF ITS WAISTCOAT-POCKET, and looked at it, and then \textcolor{blue}{hurried} on,

 Alice \textcolor{blue}{started} to her feet, for it flashed across her mind that she had

 never before seen a rabbit with either a waistcoat-pocket, or a \textcolor{BurntOrange}{watch}

 to take out of it, and burning with \textcolor{BurntOrange}{curiosity,} she ran across the field

 after it, and fortunately was just in \textcolor{blue}{time} to see it \textcolor{BurntOrange}{pop} down a large

 rabbit-hole under the hedge.



 In another moment down went Alice after it, never once considering how

 in the world she was to get out again.



 The rabbit-hole went straight on like a tunnel for some way, and then

 dipped \textcolor{blue}{suddenly} down, so \textcolor{blue}{suddenly} that Alice had not a moment to think

 about stopping herself before she \textcolor{green}{found} herself \textcolor{red}{falling} down a very deep

 well.



 Either the well was very deep, or she \textcolor{red}{fell} very slowly, for she had

 plenty of \textcolor{blue}{time} as she went down to look about her and to wonder what was

 going to \textcolor{blue}{happen} next. First, she tried to look down and make out what

 she was coming to, but it was too \textcolor{red}{dark} to see anything; then she

 looked at the sides of the well, and noticed that they were \textcolor{green}{filled} with

 cupboards and book-shelves; here and there she saw maps and pictures

 hung upon pegs. She took down a jar from one of the shelves as

 she passed; it was \textcolor{green}{labelled} ‘ORANGE MARMALADE’, but to her great

 \textcolor{red}{disappointment} it was empty: she did not like to drop the jar for \textcolor{red}{fear}

 of \textcolor{red}{killing} somebody, so \textcolor{green}{managed} to put it into one of the cupboards as

 she \textcolor{red}{fell} past it.



 ‘Well!’ \textcolor{blue}{thought} Alice to herself, ‘after such a \textcolor{red}{fall} as this, I shall

 think nothing of \textcolor{red}{tumbling} down stairs! How brave they’ll all think me at

 home! Why, I wouldn’t say anything about it, even if I \textcolor{red}{fell} off the \textcolor{BurntOrange}{top}

 of the house!’ (Which was very likely \textcolor{green}{true.)}



 Down, down, down. Would the \textcolor{red}{fall} NEVER come to an end! ‘I wonder how

 many miles I’ve \textcolor{red}{fallen} by this \textcolor{blue}{time?’} she said aloud. ‘I must be getting

 somewhere near the centre of the earth. Let me see: that would be four

 thousand miles down, I think--’ (for, you see, Alice had learnt several

 things of this sort in her \textcolor{BurntOrange}{lessons} in the schoolroom, and though this

 was not a VERY \textcolor{BurntOrange}{good} \textcolor{BurntOrange}{opportunity} for \textcolor{green}{showing} off her \textcolor{green}{knowledge,} as there

 was no one to listen to her, still it was \textcolor{BurntOrange}{good} \textcolor{green}{practice} to say it over)

 ‘--yes, that’s about the right distance--but then I wonder what Latitude

 or Longitude I’ve got to?’ (Alice had no idea what Latitude was, or

 Longitude either, but \textcolor{blue}{thought} they were nice grand \textcolor{green}{words} to say.)



 Presently she began again. ‘I wonder if I shall \textcolor{red}{fall} right THROUGH the

 earth! How funny it’ll seem to come out among the people that walk with

 their heads downward! The \textcolor{red}{Antipathies,} I think--’ (she was rather \textcolor{BurntOrange}{glad}

 there WAS no one listening, this \textcolor{blue}{time,} as it didn’t sound at all the

 right \textcolor{green}{word)} ‘--but I shall have to ask them what the name of the country

 is, you know. Please, Ma’am, is this New Zealand or Australia?’ (and

 she tried to curtsey as she spoke--fancy CURTSEYING as you’re \textcolor{red}{falling}

 through the air! Do you think you could \textcolor{green}{manage} it?) ‘And what an

 \textcolor{red}{ignorant} little girl \textcolor{BurntOrange}{she’ll} think me for asking! No, it’ll never do to

 ask: perhaps I shall see it written up somewhere.’



 Down, down, down. There was nothing else to do, so Alice soon began

 \textcolor{green}{talking} again. ‘Dinah’ll miss me very much to-night, I should think!’

 (Dinah was the cat.) ‘I \textcolor{BurntOrange}{hope} they’ll remember her saucer of milk at

 tea-time. Dinah my \textcolor{green}{dear!} I wish you were down here with me! There are no

 mice in the air, I’m \textcolor{red}{afraid,} but you might \textcolor{blue}{catch} a bat, and that’s very

 like a mouse, you know. But do cats \textcolor{green}{eat} bats, I wonder?’ And here Alice

 began to get rather sleepy, and went on saying to herself, in a dreamy

 sort of way, ‘Do cats \textcolor{green}{eat} bats? Do cats \textcolor{green}{eat} bats?’ and sometimes, ‘Do

 bats \textcolor{green}{eat} cats?’ for, you see, as she couldn’t answer either \textcolor{green}{question,}

 it didn’t much matter which way she put it. She felt that she was dozing

 off, and had just begun to dream that she was walking hand in hand with

 Dinah, and saying to her very \textcolor{green}{earnestly,} ‘Now, Dinah, tell me the \textcolor{green}{truth:}

 did you ever \textcolor{green}{eat} a bat?’ when \textcolor{blue}{suddenly,} \textcolor{red}{thump!} \textcolor{red}{thump!} down she came upon

 a heap of sticks and dry leaves, and the \textcolor{red}{fall} was over.



 Alice was not a bit \textcolor{red}{hurt,} and she jumped up on to her feet in a moment:

 she looked up, but it was all \textcolor{red}{dark} overhead; before her was another

 \textcolor{blue}{long} passage, and the \textcolor{BurntOrange}{White} Rabbit was still in sight, \textcolor{blue}{hurrying} down it.

 There was not a moment to be \textcolor{BurntOrange}{lost:} away went Alice like the wind, and

 was just in \textcolor{blue}{time} to hear it say, as it turned a corner, ‘Oh my ears

 and whiskers, how \textcolor{red}{late} it’s getting!’ She was close behind it when she

 turned the corner, but the Rabbit was no longer to be seen: she \textcolor{green}{found}

 herself in a \textcolor{blue}{long,} low hall, which was lit up by a \textcolor{red}{row} of lamps hanging

 from the roof.



 There were doors all round the hall, but they were all locked; and when

 Alice had been all the way down one side and up the other, trying every

 door, she walked \textcolor{red}{sadly} down the middle, wondering how she was ever to

 get out again.



 \textcolor{blue}{Suddenly} she came upon a little three-legged table, all made of \textcolor{green}{solid}

 glass; there was nothing on it except a tiny golden key, and Alice’s

 first \textcolor{blue}{thought} was that it might belong to one of the doors of the hall;

 but, alas! either the locks were too large, or the key was too \textcolor{red}{small,}

 but at any rate it would not open any of them. However, on the second

 \textcolor{blue}{time} round, she came upon a low curtain she had not noticed before, and

 behind it was a little door about fifteen inches high: she tried the

 little golden key in the lock, and to her great \textcolor{BurntOrange}{delight} it fitted!



 Alice opened the door and \textcolor{green}{found} that it \textcolor{green}{led} into a \textcolor{red}{small} passage, not

 much larger than a rat-hole: she knelt down and looked along the passage

 into the \textcolor{BurntOrange}{loveliest} \textcolor{green}{garden} you ever saw. How she \textcolor{blue}{longed} to get out of

 that \textcolor{red}{dark} hall, and wander about among those beds of bright flowers and

 those \textcolor{green}{cool} fountains, but she could not even get her head through the

 doorway; ‘and even if my head would go through,’ \textcolor{blue}{thought} poor Alice, ‘it

 would be of very little use without my \textcolor{green}{shoulders.} Oh, how I wish I could

 shut up like a telescope! I think I could, if I only knew how to begin.’

 For, you see, so many out-of-the-way things had \textcolor{blue}{happened} lately,

 that Alice had begun to think that very few things indeed were really

 \textcolor{red}{impossible.}



 There seemed to be no use in \textcolor{BurntOrange}{waiting} by the little door, so she went

 back to the table, half hoping she might find another key on it, or at

 any rate a book of \textcolor{BurntOrange}{rules} for shutting people up like telescopes: this

 \textcolor{blue}{time} she \textcolor{green}{found} a little bottle on it, [‘which certainly was not here

 before,’ said Alice,) and round the neck of the bottle was a paper

 \textcolor{green}{label,} with the \textcolor{green}{words} ‘DRINK ME’ beautifully printed on it in large

 \textcolor{blue}{letters.}



 It was all very well to say ‘Drink me,’ but the \textcolor{green}{wise} little Alice was

 not going to do THAT in a \textcolor{blue}{hurry.} ‘No, \textcolor{red}{I’ll} look first,’ she said, ‘and

 see whether it’s \textcolor{green}{marked} \textcolor{red}{“poison”} or not’; for she had read several nice

 little histories about \textcolor{BurntOrange}{children} who had got \textcolor{red}{burnt,} and \textcolor{green}{eaten} up by \textcolor{BurntOrange}{wild}

 \textcolor{red}{beasts} and other \textcolor{red}{unpleasant} things, all because they WOULD not remember

 the simple \textcolor{BurntOrange}{rules} their \textcolor{green}{friends} had \textcolor{green}{taught} them: such as, that a red-hot

 poker will burn you if you hold it too \textcolor{blue}{long;} and that if you cut your

 finger VERY deeply with a knife, it usually bleeds; and she had never

 \textcolor{red}{forgotten} that, if you drink much from a bottle \textcolor{green}{marked} \textcolor{red}{‘poison,’} it is

 almost certain to \textcolor{red}{disagree} with you, sooner or later.



 However, this bottle was NOT \textcolor{green}{marked} \textcolor{red}{‘poison,’} so Alice ventured to taste

 it, and finding it very nice, (it had, in \textcolor{green}{fact,} a sort of mixed flavour

 of cherry-tart, custard, pine-apple, roast turkey, toffee, and \textcolor{red}{hot}

 buttered \textcolor{green}{toast,)} she very soon finished it off.



 * * * * * * *



 * * * * * *



 * * * * * * *



 ‘What a curious feeling!’ said Alice; ‘I must be shutting up like a

 telescope.’



 And so it was indeed: she was now only ten inches high, and her face

 \textcolor{BurntOrange}{brightened} up at the \textcolor{blue}{thought} that she was now the right size for going

 through the little door into that \textcolor{BurntOrange}{lovely} \textcolor{green}{garden.} First, however, she

 \textcolor{BurntOrange}{waited} for a few minutes to see if she was going to \textcolor{red}{shrink} any further:

 she felt a little \textcolor{BurntOrange}{nervous} about this; ‘for it might end, you know,’ said

 Alice to herself, ‘in my going out altogether, like a candle. I wonder

 what I should be like then?’ And she tried to \textcolor{BurntOrange}{fancy} what the flame of a

 candle is like after the candle is blown out, for she could not remember

 ever having seen such a thing.



 After a while, finding that nothing more \textcolor{blue}{happened,} she decided on going

 into the \textcolor{green}{garden} at once; but, alas for poor Alice! when she got to the

 door, she \textcolor{green}{found} she had \textcolor{red}{forgotten} the little golden key, and when she

 went back to the table for it, she \textcolor{green}{found} she could not possibly reach

 it: she could see it quite plainly through the glass, and she tried her

 best to climb up one of the legs of the table, but it was too slippery;

 and when she had tired herself out with trying, the poor little thing

 sat down and \textcolor{red}{cried.}



 ‘Come, there’s no use in \textcolor{red}{crying} like that!’ said Alice to herself,

 rather sharply; ‘I \textcolor{green}{advise} you to \textcolor{BurntOrange}{leave} off this minute!’ She generally

 gave herself very \textcolor{BurntOrange}{good} \textcolor{green}{advice,} (though she very seldom followed it),

 and sometimes she \textcolor{red}{scolded} herself so severely as to bring tears into

 her eyes; and once she remembered trying to box her own ears for having

 \textcolor{red}{cheated} herself in a game of croquet she was playing against herself,

 for this curious \textcolor{BurntOrange}{child} was very fond of \textcolor{red}{pretending} to be two people.

 ‘But it’s no use now,’ \textcolor{blue}{thought} poor Alice, ‘to \textcolor{red}{pretend} to be two people!

 Why, there’s hardly enough of me left to make ONE \textcolor{green}{respectable} person!’



 Soon her eye \textcolor{red}{fell} on a little glass box that was \textcolor{red}{lying} under the table:

 she opened it, and \textcolor{green}{found} in it a very \textcolor{red}{small} cake, on which the \textcolor{green}{words}

 \textcolor{green}{‘EAT} ME’ were beautifully \textcolor{green}{marked} in currants. ‘Well, \textcolor{red}{I’ll} \textcolor{green}{eat} it,’ said

 Alice, ‘and if it makes me \textcolor{BurntOrange}{grow} larger, I can reach the key; and if it

 makes me \textcolor{BurntOrange}{grow} \textcolor{red}{smaller,} I can \textcolor{red}{creep} under the door; so either way \textcolor{red}{I’ll}

 get into the \textcolor{green}{garden,} and I don’t care which happens!’



 She ate a little bit, and said anxiously to herself, ‘Which way? Which

 way?’, holding her hand on the \textcolor{BurntOrange}{top} of her head to feel which way it was

 \textcolor{BurntOrange}{growing,} and she was quite \textcolor{blue}{surprised} to find that she remained the same

 size: to be sure, this generally happens when one eats cake, but Alice

 had got so much into the way of \textcolor{BurntOrange}{expecting} nothing but out-of-the-way

 things to \textcolor{blue}{happen,} that it seemed quite \textcolor{red}{dull} and \textcolor{red}{stupid} for life to go on

 in the common way.



 So she set to work, and very soon finished off the cake.



 * * * * * * *



 * * * * * *



 * * * * * * *









 CHAPTER II. The \textcolor{green}{Pool} of Tears



 ‘Curiouser and curiouser!’ \textcolor{red}{cried} Alice (she was so much \textcolor{blue}{surprised,} that

 for the moment she quite forgot how to speak \textcolor{BurntOrange}{good} English); ‘now I’m

 opening out like the largest telescope that ever was! Good-bye, feet!’

 (for when she looked down at her feet, they seemed to be almost out of

 sight, they were getting so far off). ‘Oh, my poor little feet, I wonder

 who will put on your shoes and stockings for you now, \textcolor{green}{dears?} I’m sure

 I shan’t be able! I shall be a great \textcolor{BurntOrange}{deal} too far off to trouble

 myself about you: you must \textcolor{green}{manage} the best way you can;--but I must be

 \textcolor{green}{kind} to them,’ \textcolor{blue}{thought} Alice, ‘or perhaps they \textcolor{blue}{won’t} walk the way I want

 to go! Let me see: \textcolor{red}{I’ll} give them a new pair of boots every Christmas.’



 And she went on \textcolor{BurntOrange}{planning} to herself how she would \textcolor{green}{manage} it. ‘They must

 go by the carrier,’ she \textcolor{blue}{thought;} ‘and how funny it’ll seem, sending

 \textcolor{BurntOrange}{presents} to one’s own feet! And how odd the directions will look!



 ALICE’S RIGHT FOOT, ESQ.

 HEARTHRUG,

 NEAR THE \textcolor{green}{FENDER,}

 (WITH ALICE’S \textcolor{green}{LOVE).}



 Oh \textcolor{green}{dear,} what \textcolor{red}{nonsense} I’m \textcolor{green}{talking!’}



 Just then her head struck against the roof of the hall: in \textcolor{green}{fact} she was

 now more than nine feet high, and she at once took up the little golden

 key and \textcolor{blue}{hurried} off to the \textcolor{green}{garden} door.



 Poor Alice! It was as much as she could do, \textcolor{red}{lying} down on one side, to

 look through into the \textcolor{green}{garden} with one eye; but to get through was more

 \textcolor{red}{hopeless} than ever: she sat down and began to \textcolor{red}{cry} again.



 ‘You ought to be \textcolor{red}{ashamed} of yourself,’ said Alice, ‘a great girl like

 you,’ (she might well say this), ‘to go on \textcolor{red}{crying} in this way! Stop this

 moment, I tell you!’ But she went on all the same, \textcolor{red}{shedding} gallons of

 tears, until there was a large \textcolor{green}{pool} all round her, about four inches

 deep and reaching half down the hall.



 After a \textcolor{blue}{time} she heard a little \textcolor{red}{pattering} of feet in the distance, and

 she hastily dried her eyes to see what was coming. It was the \textcolor{BurntOrange}{White}

 Rabbit returning, splendidly dressed, with a pair of \textcolor{BurntOrange}{white} kid gloves in

 one hand and a large fan in the other: he came trotting along in a great

 \textcolor{blue}{hurry,} \textcolor{red}{muttering} to himself as he came, ‘Oh! the Duchess, the Duchess!

 Oh! \textcolor{blue}{won’t} she be \textcolor{red}{savage} if I’ve kept her \textcolor{BurntOrange}{waiting!’} Alice felt so

 \textcolor{red}{desperate} that she was \textcolor{blue}{ready} to ask help of any one; so, when the Rabbit

 came near her, she began, in a low, \textcolor{red}{timid} voice, ‘If you please, \textcolor{green}{sir--’}

 The Rabbit \textcolor{blue}{started} \textcolor{red}{violently,} dropped the \textcolor{BurntOrange}{white} kid gloves and the fan,

 and skurried away into the \textcolor{red}{darkness} as hard as he could go.



 Alice took up the fan and gloves, and, as the hall was very \textcolor{red}{hot,} she

 kept fanning herself all the \textcolor{blue}{time} she went on \textcolor{green}{talking:} \textcolor{green}{‘Dear,} \textcolor{green}{dear!} How

 queer everything is to-day! And yesterday things went on just as \textcolor{green}{usual.}

 I wonder if I’ve been \textcolor{red}{changed} in the night? Let me think: was I the

 same when I got up this morning? I almost think I can remember feeling a

 little different. But if I’m not the same, the next \textcolor{green}{question} is, Who

 in the world am I? Ah, THAT’S the great puzzle!’ And she began thinking

 over all the \textcolor{BurntOrange}{children} she knew that were of the same age as herself, to

 see if she could have been \textcolor{red}{changed} for any of them.



 ‘I’m sure I’m not Ada,’ she said, ‘for her hair goes in such \textcolor{blue}{long}

 ringlets, and mine doesn’t go in ringlets at all; and I’m sure I can’t

 be Mabel, for I know all sorts of things, and she, oh! she knows such a

 very little! Besides, SHE’S she, and I’m I, and--oh \textcolor{green}{dear,} how puzzling

 it all is! \textcolor{red}{I’ll} try if I know all the things I used to know. Let me

 see: four \textcolor{blue}{times} five is twelve, and four \textcolor{blue}{times} six is thirteen, and

 four \textcolor{blue}{times} seven is--oh \textcolor{green}{dear!} I shall never get to twenty at that rate!

 However, the Multiplication Table doesn’t \textcolor{blue}{signify:} let’s try Geography.

 London is the capital of Paris, and Paris is the capital of Rome, and

 Rome--no, THAT’S all \textcolor{red}{wrong,} I’m certain! I must have been \textcolor{red}{changed} for

 Mabel! \textcolor{red}{I’ll} try and say “How doth the little--“’ and she \textcolor{red}{crossed} her

 hands on her lap as if she were saying \textcolor{BurntOrange}{lessons,} and began to repeat it,

 but her voice sounded \textcolor{red}{hoarse} and strange, and the \textcolor{green}{words} did not come the

 same as they used to do:--



 ‘How doth the little \textcolor{red}{crocodile}

 \textcolor{BurntOrange}{Improve} his shining tail,

 And pour the waters of the Nile

 On every golden scale!



 ‘How cheerfully he seems to \textcolor{BurntOrange}{grin,}

 How \textcolor{green}{neatly} spread his \textcolor{red}{claws,}

 And welcome little fishes in

 With gently \textcolor{BurntOrange}{smiling} jaws!’



 ‘I’m sure those are not the right \textcolor{green}{words,’} said poor Alice, and her eyes

 \textcolor{green}{filled} with tears again as she went on, ‘I must be Mabel after all, and

 I shall have to go and live in that poky little house, and have next to

 no toys to play with, and oh! ever so many \textcolor{BurntOrange}{lessons} to \textcolor{green}{learn!} No, I’ve

 made up my mind about it; if I’m Mabel, \textcolor{red}{I’ll} stay down here! It’ll be no

 use their putting their heads down and saying “Come up again, \textcolor{green}{dear!”} I

 shall only look up and say “Who am I then? Tell me that first, and then,

 if I like being that person, \textcolor{red}{I’ll} come up: if not, \textcolor{red}{I’ll} stay down here

 till I’m somebody else”--but, oh \textcolor{green}{dear!’} \textcolor{red}{cried} Alice, with a \textcolor{blue}{sudden} burst

 of tears, ‘I do wish they WOULD put their heads down! I am so VERY tired

 of being all alone here!’



 As she said this she looked down at her hands, and was \textcolor{blue}{surprised} to see

 that she had put on one of the Rabbit’s little \textcolor{BurntOrange}{white} kid gloves while

 she was \textcolor{green}{talking.} ‘How CAN I have done that?’ she \textcolor{blue}{thought.} ‘I must

 be \textcolor{BurntOrange}{growing} \textcolor{red}{small} again.’ She got up and went to the table to \textcolor{green}{measure}

 herself by it, and \textcolor{green}{found} that, as nearly as she could \textcolor{blue}{guess,} she was now

 about two feet high, and was going on \textcolor{red}{shrinking} rapidly: she soon \textcolor{green}{found}

 out that the cause of this was the fan she was holding, and she dropped

 it hastily, just in \textcolor{blue}{time} to \textcolor{red}{avoid} \textcolor{red}{shrinking} away altogether.



 ‘That WAS a narrow \textcolor{BurntOrange}{escape!’} said Alice, a \textcolor{BurntOrange}{good} \textcolor{BurntOrange}{deal} \textcolor{BurntOrange}{frightened} at the

 \textcolor{blue}{sudden} \textcolor{red}{change,} but very \textcolor{BurntOrange}{glad} to find herself still in \textcolor{green}{existence;} ‘and

 now for the \textcolor{green}{garden!’} and she ran with all speed back to the little door:

 but, alas! the little door was shut again, and the little golden key was

 \textcolor{red}{lying} on the glass table as before, ‘and things are \textcolor{red}{worse} than ever,’

 \textcolor{blue}{thought} the poor \textcolor{BurntOrange}{child,} ‘for I never was so \textcolor{red}{small} as this before, never!

 And I declare it’s too \textcolor{red}{bad,} that it is!’



 As she said these \textcolor{green}{words} her foot \textcolor{BurntOrange}{slipped,} and in another moment, \textcolor{blue}{splash!}

 she was up to her chin in salt water. Her first idea was that she

 had somehow \textcolor{red}{fallen} into the \textcolor{green}{sea,} ‘and in that \textcolor{red}{case} I can go back by

 railway,’ she said to herself. (Alice had been to the seaside once in

 her life, and had come to the \textcolor{green}{general} conclusion, that wherever you go

 to on the English \textcolor{green}{coast} you find a number of bathing \textcolor{green}{machines} in the

 \textcolor{green}{sea,} some \textcolor{BurntOrange}{children} digging in the sand with wooden spades, then a \textcolor{red}{row}

 of lodging houses, and behind them a railway station.) However, she soon

 made out that she was in the \textcolor{green}{pool} of tears which she had wept when she

 was nine feet high.



 ‘I wish I hadn’t \textcolor{red}{cried} so much!’ said Alice, as she swam about, trying

 to find her way out. ‘I shall be \textcolor{red}{punished} for it now, I suppose, by

 being \textcolor{red}{drowned} in my own tears! That WILL be a queer thing, to be sure!

 However, everything is queer to-day.’



 Just then she heard something \textcolor{blue}{splashing} about in the \textcolor{green}{pool} a little way

 off, and she swam nearer to make out what it was: at first she \textcolor{blue}{thought}

 it must be a walrus or hippopotamus, but then she remembered how \textcolor{red}{small}

 she was now, and she soon made out that it was only a mouse that had

 \textcolor{BurntOrange}{slipped} in like herself.



 ‘Would it be of any use, now,’ \textcolor{blue}{thought} Alice, ‘to speak to this mouse?

 Everything is so out-of-the-way down here, that I should think very

 likely it can \textcolor{green}{talk:} at any rate, there’s no \textcolor{red}{harm} in trying.’ So she

 began: ‘O Mouse, do you know the way out of this \textcolor{green}{pool?} I am very tired

 of \textcolor{BurntOrange}{swimming} about here, O Mouse!’ (Alice \textcolor{blue}{thought} this must be the right

 way of speaking to a mouse: she had never done such a thing before, but

 she remembered having seen in her \textcolor{green}{brother’s} Latin \textcolor{green}{Grammar,} ‘A mouse--of

 a mouse--to a mouse--a mouse--O mouse!’) The Mouse looked at her rather

 inquisitively, and seemed to her to wink with one of its little eyes,

 but it said nothing.



 ‘Perhaps it doesn’t understand English,’ \textcolor{blue}{thought} Alice; ‘I daresay it’s

 a French mouse, come over with William the Conqueror.’ (For, with all

 her \textcolor{green}{knowledge} of history, Alice had no very clear \textcolor{green}{notion} how \textcolor{blue}{long} ago

 anything had \textcolor{blue}{happened.)} So she began again: ‘Ou est ma chatte?’ which

 was the first \textcolor{BurntOrange}{sentence} in her French lesson-book. The Mouse gave a

 \textcolor{blue}{sudden} leap out of the water, and seemed to \textcolor{red}{quiver} all over with \textcolor{BurntOrange}{fright.}

 ‘Oh, I \textcolor{red}{beg} your \textcolor{green}{pardon!’} \textcolor{red}{cried} Alice hastily, \textcolor{red}{afraid} that she had \textcolor{red}{hurt}

 the poor animal’s \textcolor{BurntOrange}{feelings.} ‘I quite forgot you didn’t like cats.’



 ‘Not like cats!’ \textcolor{red}{cried} the Mouse, in a \textcolor{BurntOrange}{shrill,} \textcolor{BurntOrange}{passionate} voice. ‘Would

 YOU like cats if you were me?’



 ‘Well, perhaps not,’ said Alice in a \textcolor{green}{soothing} tone: ‘don’t be \textcolor{red}{angry}

 about it. And yet I wish I could \textcolor{green}{show} you our cat Dinah: I think you’d

 take a \textcolor{BurntOrange}{fancy} to cats if you could only see her. She is such a \textcolor{green}{dear} \textcolor{BurntOrange}{quiet}

 thing,’ Alice went on, half to herself, as she swam lazily about in the

 \textcolor{green}{pool,} ‘and she sits \textcolor{green}{purring} so nicely by the \textcolor{red}{fire,} \textcolor{red}{licking} her paws and

 washing her face--and she is such a nice soft thing to nurse--and she’s

 such a capital one for \textcolor{blue}{catching} mice--oh, I \textcolor{red}{beg} your \textcolor{green}{pardon!’} \textcolor{red}{cried}

 Alice again, for this \textcolor{blue}{time} the Mouse was bristling all over, and she

 felt certain it must be really \textcolor{red}{offended.} ‘We \textcolor{blue}{won’t} \textcolor{green}{talk} about her any

 more if you’d rather not.’



 ‘We indeed!’ \textcolor{red}{cried} the Mouse, who was trembling down to the end of his

 tail. ‘As if I would \textcolor{green}{talk} on such a \textcolor{red}{subject!} Our family always HATED

 cats: \textcolor{red}{nasty,} low, \textcolor{red}{vulgar} things! Don’t let me hear the name again!’



 ‘I \textcolor{blue}{won’t} indeed!’ said Alice, in a great \textcolor{blue}{hurry} to \textcolor{red}{change} the \textcolor{red}{subject} of

 conversation. ‘Are you--are you fond--of--of dogs?’ The Mouse did not

 answer, so Alice went on eagerly: ‘There is such a nice little dog near

 our house I should like to \textcolor{green}{show} you! A little bright-eyed terrier, you

 know, with oh, such \textcolor{blue}{long} curly brown hair! And it’ll fetch things when

 you throw them, and it’ll sit up and \textcolor{red}{beg} for its \textcolor{green}{dinner,} and all sorts

 of things--I can’t remember half of them--and it belongs to a farmer,

 you know, and he says it’s so useful, it’s \textcolor{green}{worth} a hundred \textcolor{red}{pounds!} He

 says it \textcolor{red}{kills} all the \textcolor{red}{rats} and--oh \textcolor{green}{dear!’} \textcolor{red}{cried} Alice in a \textcolor{red}{sorrowful}

 tone, ‘I’m \textcolor{red}{afraid} I’ve \textcolor{red}{offended} it again!’ For the Mouse was \textcolor{BurntOrange}{swimming}

 away from her as hard as it could go, and making quite a \textcolor{red}{commotion} in

 the \textcolor{green}{pool} as it went.



 So she called softly after it, ‘Mouse \textcolor{green}{dear!} Do come back again, and we

 \textcolor{blue}{won’t} \textcolor{green}{talk} about cats or dogs either, if you don’t like them!’ When the

 Mouse heard this, it turned round and swam slowly back to her: its

 face was quite pale (with \textcolor{BurntOrange}{passion,} Alice \textcolor{blue}{thought),} and it said in a low

 trembling voice, ‘Let us get to the shore, and then \textcolor{red}{I’ll} tell you my

 history, and you’ll understand why it is I \textcolor{red}{hate} cats and dogs.’



 It was high \textcolor{blue}{time} to go, for the \textcolor{green}{pool} was getting quite crowded with the

 birds and animals that had \textcolor{red}{fallen} into it: there were a Duck and a Dodo,

 a Lory and an Eaglet, and several other curious \textcolor{red}{creatures.} Alice \textcolor{green}{led} the

 way, and the whole party swam to the shore.









 CHAPTER III. A Caucus-Race and a \textcolor{blue}{Long} \textcolor{green}{Tale}



 They were indeed a queer-looking party that assembled on the bank--the

 birds with draggled feathers, the animals with their fur clinging close

 to them, and all dripping wet, \textcolor{red}{cross,} and \textcolor{red}{uncomfortable.}



 The first \textcolor{green}{question} of course was, how to get dry again: they had a

 consultation about this, and after a few minutes it seemed quite natural

 to Alice to find herself \textcolor{green}{talking} familiarly with them, as if she had

 known them all her life. Indeed, she had quite a \textcolor{blue}{long} \textcolor{red}{argument} with the

 Lory, who at last turned sulky, and would only say, ‘I am older than

 you, and must know better’; and this Alice would not allow without

 knowing how old it was, and, as the Lory positively \textcolor{red}{refused} to tell its

 age, there was no more to be said.



 At last the Mouse, who seemed to be a person of \textcolor{green}{authority} among them,

 called out, ‘Sit down, all of you, and listen to me! \textcolor{red}{I’LL} soon make you

 dry enough!’ They all sat down at once, in a large ring, with the Mouse

 in the middle. Alice kept her eyes anxiously fixed on it, for she felt

 sure she would \textcolor{blue}{catch} a \textcolor{red}{bad} \textcolor{red}{cold} if she did not get dry very soon.



 ‘Ahem!’ said the Mouse with an \textcolor{green}{important} air, ‘are you all \textcolor{blue}{ready?} This

 is the driest thing I know. Silence all round, if you please! “William

 the Conqueror, whose cause was favoured by the \textcolor{green}{pope,} was soon \textcolor{blue}{submitted}

 to by the English, who wanted \textcolor{green}{leaders,} and had been of \textcolor{red}{late} much

 accustomed to usurpation and \textcolor{red}{conquest.} Edwin and Morcar, the \textcolor{green}{earls} of

 Mercia and Northumbria--“’



 ‘Ugh!’ said the Lory, with a \textcolor{BurntOrange}{shiver.}



 ‘I \textcolor{red}{beg} your \textcolor{green}{pardon!’} said the Mouse, \textcolor{red}{frowning,} but very politely: ‘Did

 you speak?’



 ‘Not I!’ said the Lory hastily.



 ‘I \textcolor{blue}{thought} you did,’ said the Mouse. ‘--I proceed. “Edwin and Morcar,

 the \textcolor{green}{earls} of Mercia and Northumbria, declared for him: and even Stigand,

 the patriotic archbishop of Canterbury, \textcolor{green}{found} it \textcolor{green}{advisable--“’}



 \textcolor{green}{‘Found} WHAT?’ said the Duck.



 \textcolor{green}{‘Found} IT,’ the Mouse replied rather crossly: ‘of course you know what

 “it” means.’



 ‘I know what “it” means well enough, when I find a thing,’ said the

 Duck: ‘it’s generally a frog or a \textcolor{BurntOrange}{worm.} The \textcolor{green}{question} is, what did the

 archbishop find?’



 The Mouse did not notice this \textcolor{green}{question,} but hurriedly went on, \textcolor{green}{‘“--found}

 it \textcolor{green}{advisable} to go with Edgar Atheling to meet William and \textcolor{green}{offer} him the

 crown. William’s conduct at first was \textcolor{green}{moderate.} But the insolence of his

 Normans--” How are you getting on now, my \textcolor{green}{dear?’} it continued, turning

 to Alice as it \textcolor{red}{spoke.}



 ‘As wet as ever,’ said Alice in a \textcolor{red}{melancholy} tone: ‘it doesn’t seem to

 dry me at all.’



 ‘In that \textcolor{red}{case,’} said the Dodo solemnly, rising to its feet, ‘I move

 that the meeting adjourn, for the immediate adoption of more \textcolor{green}{energetic}

 \textcolor{BurntOrange}{remedies--’}



 ‘Speak English!’ said the Eaglet. ‘I don’t know the meaning of half

 those \textcolor{blue}{long} \textcolor{green}{words,} and, what’s more, I don’t believe you do either!’ And

 the Eaglet bent down its head to \textcolor{red}{hide} a \textcolor{BurntOrange}{smile:} some of the other birds

 tittered audibly.



 ‘What I was going to say,’ said the Dodo in an \textcolor{red}{offended} tone, ‘was, that

 the best thing to get us dry would be a Caucus-race.’



 ‘What IS a Caucus-race?’ said Alice; not that she wanted much to know,

 but the Dodo had paused as if it \textcolor{blue}{thought} that SOMEBODY ought to speak,

 and no one else seemed inclined to say anything.



 ‘Why,’ said the Dodo, ‘the best way to \textcolor{green}{explain} it is to do it.’ (And, as

 you might like to try the thing yourself, some winter day, I will tell

 you how the Dodo \textcolor{green}{managed} it.)



 First it \textcolor{green}{marked} out a race-course, in a sort of circle, [‘the exact

 \textcolor{green}{shape} doesn’t matter,’ it said,) and then all the party were placed

 along the course, here and there. There was no ‘One, two, three, and

 away,’ but they began running when they liked, and left off when they

 liked, so that it was not easy to know when the race was over. However,

 when they had been running half an hour or so, and were quite dry again,

 the Dodo \textcolor{blue}{suddenly} called out ‘The race is over!’ and they all crowded

 round it, panting, and asking, ‘But who has won?’



 This \textcolor{green}{question} the Dodo could not answer without a great \textcolor{BurntOrange}{deal} of \textcolor{blue}{thought,}

 and it sat for a \textcolor{blue}{long} \textcolor{blue}{time} with one finger pressed upon its forehead

 (the position in which you usually see Shakespeare, in the pictures

 of him), while the \textcolor{green}{rest} \textcolor{BurntOrange}{waited} in silence. At last the Dodo said,

 ‘EVERYBODY has won, and all must have prizes.’



 ‘But who is to give the prizes?’ quite a \textcolor{green}{chorus} of voices asked.



 ‘Why, SHE, of course,’ said the Dodo, pointing to Alice with one finger;

 and the whole party at once crowded round her, calling out in a \textcolor{red}{confused}

 way, ‘Prizes! Prizes!’



 Alice had no idea what to do, and in \textcolor{red}{despair} she put her hand in her

 pocket, and \textcolor{green}{pulled} out a box of comfits, (luckily the salt water had

 not got into it), and handed them round as prizes. There was exactly one

 a-piece all round.



 ‘But she must have a prize herself, you know,’ said the Mouse.



 ‘Of course,’ the Dodo replied very gravely. ‘What else have you got in

 your pocket?’ he went on, turning to Alice.



 ‘Only a thimble,’ said Alice \textcolor{red}{sadly.}



 ‘Hand it over here,’ said the Dodo.



 Then they all crowded round her once more, while the Dodo solemnly

 \textcolor{BurntOrange}{presented} the thimble, saying ‘We \textcolor{red}{beg} your \textcolor{green}{acceptance} of this \textcolor{green}{elegant}

 thimble’; and, when it had finished this short \textcolor{green}{speech,} they all \textcolor{BurntOrange}{cheered.}



 Alice \textcolor{blue}{thought} the whole thing very \textcolor{red}{absurd,} but they all looked so \textcolor{red}{grave}

 that she did not \textcolor{BurntOrange}{dare} to \textcolor{BurntOrange}{laugh;} and, as she could not think of anything

 to say, she simply bowed, and took the thimble, looking as solemn as she

 could.



 The next thing was to \textcolor{green}{eat} the comfits: this caused some \textcolor{red}{noise} and

 \textcolor{red}{confusion,} as the large birds \textcolor{red}{complained} that they could not taste

 theirs, and the \textcolor{red}{small} ones choked and had to be patted on the back.

 However, it was over at last, and they sat down again in a ring, and

 \textcolor{red}{begged} the Mouse to tell them something more.



 ‘You \textcolor{green}{promised} to tell me your history, you know,’ said Alice, ‘and why

 it is you hate--C and D,’ she added in a whisper, half \textcolor{red}{afraid} that it

 would be \textcolor{red}{offended} again.



 ‘Mine is a \textcolor{blue}{long} and a sad \textcolor{green}{tale!’} said the Mouse, turning to Alice, and

 sighing.



 ‘It IS a \textcolor{blue}{long} tail, certainly,’ said Alice, looking down with wonder at

 the Mouse’s tail; ‘but why do you call it sad?’ And she kept on puzzling

 about it while the Mouse was speaking, so that her idea of the \textcolor{green}{tale} was

 something like this:--



 \textcolor{red}{‘Fury} said to a

 mouse, That he

 met in the

 house,

 “Let us

 both go to

 \textcolor{green}{law:} I will

 \textcolor{red}{prosecute}

 YOU.--Come,

 \textcolor{red}{I’ll} take no

 \textcolor{red}{denial;} We

 must have a

 trial: For

 really this

 morning I’ve

 nothing

 to do.”

 Said the

 mouse to the

 \textcolor{red}{cur,} “Such

 a trial,

 \textcolor{green}{dear} \textcolor{green}{Sir,}

 With

 no \textcolor{green}{jury}

 or judge,

 would be

 \textcolor{red}{wasting}

 our

 breath.”

 \textcolor{red}{“I’ll} be

 judge, \textcolor{red}{I’ll}

 be \textcolor{green}{jury,”}

 Said

 \textcolor{BurntOrange}{cunning}

 old \textcolor{red}{Fury:}

 \textcolor{red}{“I’ll}

 try the

 whole

 cause,

 and

 \textcolor{red}{condemn}

 you

 to

 \textcolor{BurntOrange}{death.”’}





 ‘You are not attending!’ said the Mouse to Alice severely. ‘What are you

 thinking of?’



 ‘I \textcolor{red}{beg} your \textcolor{green}{pardon,’} said Alice very \textcolor{green}{humbly:} ‘you had got to the fifth

 bend, I think?’



 ‘I had NOT!’ \textcolor{red}{cried} the Mouse, sharply and very angrily.



 ‘A knot!’ said Alice, always \textcolor{blue}{ready} to make herself useful, and looking

 anxiously about her. ‘Oh, do let me help to \textcolor{red}{undo} it!’



 ‘I shall do nothing of the sort,’ said the Mouse, getting up and walking

 away. ‘You \textcolor{BurntOrange}{insult} me by \textcolor{green}{talking} such \textcolor{red}{nonsense!’}



 ‘I didn’t mean it!’ pleaded poor Alice. ‘But you’re so easily \textcolor{red}{offended,}

 you know!’



 The Mouse only \textcolor{red}{growled} in reply.



 ‘Please come back and finish your story!’ Alice called after it; and the

 others all \textcolor{green}{joined} in \textcolor{green}{chorus,} ‘Yes, please do!’ but the Mouse only shook

 its head impatiently, and walked a little quicker.



 ‘What a \textcolor{red}{pity} it wouldn’t stay!’ sighed the Lory, as soon as it was quite

 out of sight; and an old Crab took the \textcolor{BurntOrange}{opportunity} of saying to her

 \textcolor{green}{daughter} ‘Ah, my \textcolor{green}{dear!} Let this be a \textcolor{BurntOrange}{lesson} to you never to \textcolor{BurntOrange}{lose}

 YOUR temper!’ ‘Hold your tongue, Ma!’ said the \textcolor{BurntOrange}{young} Crab, a little

 snappishly. ‘You’re enough to try the \textcolor{BurntOrange}{patience} of an oyster!’



 ‘I wish I had our Dinah here, I know I do!’ said Alice aloud, addressing

 nobody in particular. \textcolor{red}{‘She’d} soon fetch it back!’



 ‘And who is Dinah, if I might venture to ask the \textcolor{green}{question?’} said the

 Lory.



 Alice replied eagerly, for she was always \textcolor{blue}{ready} to \textcolor{green}{talk} about her \textcolor{red}{pet:}

 ‘Dinah’s our cat. And she’s such a capital one for \textcolor{blue}{catching} mice you

 can’t think! And oh, I wish you could see her after the birds! Why,

 \textcolor{BurntOrange}{she’ll} \textcolor{green}{eat} a little bird as soon as look at it!’



 This \textcolor{green}{speech} caused a \textcolor{BurntOrange}{remarkable} sensation among the party. Some of the

 birds \textcolor{blue}{hurried} off at once: one old Magpie began wrapping itself up very

 \textcolor{green}{carefully,} remarking, ‘I really must be getting home; the night-air

 doesn’t suit my throat!’ and a \textcolor{green}{Canary} called out in a trembling voice to

 its \textcolor{BurntOrange}{children,} ‘Come away, my \textcolor{green}{dears!} It’s high \textcolor{blue}{time} you were all in bed!’

 On various pretexts they all moved off, and Alice was soon left alone.



 ‘I wish I hadn’t mentioned Dinah!’ she said to herself in a \textcolor{red}{melancholy}

 tone. ‘Nobody seems to like her, down here, and I’m sure she’s the best

 cat in the world! Oh, my \textcolor{green}{dear} Dinah! I wonder if I shall ever see you

 any more!’ And here poor Alice began to \textcolor{red}{cry} again, for she felt very

 \textcolor{red}{lonely} and low-spirited. In a little while, however, she again heard

 a little \textcolor{red}{pattering} of footsteps in the distance, and she looked up

 eagerly, half hoping that the Mouse had \textcolor{red}{changed} his mind, and was coming

 back to finish his story.









 CHAPTER IV. The Rabbit Sends in a Little Bill



 It was the \textcolor{BurntOrange}{White} Rabbit, trotting slowly back again, and looking

 anxiously about as it went, as if it had \textcolor{BurntOrange}{lost} something; and she heard

 it \textcolor{red}{muttering} to itself ‘The Duchess! The Duchess! Oh my \textcolor{green}{dear} paws! Oh

 my fur and whiskers! \textcolor{BurntOrange}{She’ll} get me executed, as sure as ferrets are

 ferrets! Where CAN I have dropped them, I wonder?’ Alice \textcolor{blue}{guessed} in a

 moment that it was looking for the fan and the pair of \textcolor{BurntOrange}{white} kid gloves,

 and she very good-naturedly began hunting about for them, but they were

 nowhere to be seen--everything seemed to have \textcolor{red}{changed} since her \textcolor{BurntOrange}{swim} in

 the \textcolor{green}{pool,} and the great hall, with the glass table and the little door,

 had \textcolor{BurntOrange}{vanished} \textcolor{green}{completely.}



 Very soon the Rabbit noticed Alice, as she went hunting about, and

 called out to her in an \textcolor{red}{angry} tone, ‘Why, Mary Ann, what ARE you doing

 out here? Run home this moment, and fetch me a pair of gloves and a fan!

 Quick, now!’ And Alice was so much \textcolor{BurntOrange}{frightened} that she ran off at once

 in the direction it pointed to, without trying to \textcolor{green}{explain} the \textcolor{red}{mistake} it

 had made.



 ‘He took me for his housemaid,’ she said to herself as she ran. ‘How

 \textcolor{blue}{surprised} \textcolor{red}{he’ll} be when he finds out who I am! But I’d better take him

 his fan and gloves--that is, if I can find them.’ As she said this, she

 came upon a neat little house, on the door of which was a bright brass

 plate with the name ‘W. RABBIT’ engraved upon it. She went in without

 knocking, and \textcolor{blue}{hurried} upstairs, in great \textcolor{red}{fear} lest she should meet the

 \textcolor{green}{real} Mary Ann, and be turned out of the house before she had \textcolor{green}{found} the

 fan and gloves.



 ‘How queer it seems,’ Alice said to herself, ‘to be going messages for

 a rabbit! I suppose Dinah’ll be sending me on messages next!’ And she

 began \textcolor{BurntOrange}{fancying} the sort of thing that would \textcolor{blue}{happen:} ‘“Miss Alice! Come

 here directly, and get \textcolor{blue}{ready} for your walk!” “Coming in a minute,

 \textcolor{green}{nurse!} But I’ve got to see that the mouse doesn’t get out.” Only I don’t

 think,’ Alice went on, ‘that they’d let Dinah stop in the house if it

 began ordering people about like that!’



 By this \textcolor{blue}{time} she had \textcolor{green}{found} her way into a tidy little room with a table

 in the window, and on it (as she had hoped) a fan and two or three pairs

 of tiny \textcolor{BurntOrange}{white} kid gloves: she took up the fan and a pair of the gloves,

 and was just going to \textcolor{BurntOrange}{leave} the room, when her eye \textcolor{red}{fell} upon a little

 bottle that stood near the looking-glass. There was no \textcolor{green}{label} this \textcolor{blue}{time}

 with the \textcolor{green}{words} ‘DRINK ME,’ but nevertheless she uncorked it and put it

 to her lips. ‘I know SOMETHING \textcolor{green}{interesting} is sure to \textcolor{blue}{happen,’} she said

 to herself, ‘whenever I \textcolor{green}{eat} or drink anything; so \textcolor{red}{I’ll} just see what

 this bottle does. I do \textcolor{BurntOrange}{hope} it’ll make me \textcolor{BurntOrange}{grow} large again, for really

 I’m quite tired of being such a tiny little thing!’



 It did so indeed, and much sooner than she had \textcolor{BurntOrange}{expected:} before she had

 drunk half the bottle, she \textcolor{green}{found} her head pressing against the ceiling,

 and had to stoop to \textcolor{green}{save} her neck from being \textcolor{red}{broken.} She hastily put

 down the bottle, saying to herself ‘That’s quite enough--I \textcolor{BurntOrange}{hope} I shan’t

 \textcolor{BurntOrange}{grow} any more--As it is, I can’t get out at the door--I do wish I hadn’t

 drunk quite so much!’



 Alas! it was too \textcolor{red}{late} to wish that! She went on \textcolor{BurntOrange}{growing,} and \textcolor{BurntOrange}{growing,}

 and very soon had to kneel down on the floor: in another minute there

 was not even room for this, and she tried the effect of \textcolor{red}{lying} down with

 one \textcolor{red}{elbow} against the door, and the other arm \textcolor{green}{curled} round her head.

 Still she went on \textcolor{BurntOrange}{growing,} and, as a last resource, she put one arm out

 of the window, and one foot up the chimney, and said to herself ‘Now I

 can do no more, whatever happens. What WILL become of me?’



 Luckily for Alice, the little magic bottle had now had its \textcolor{green}{full} effect,

 and she \textcolor{BurntOrange}{grew} no larger: still it was very \textcolor{red}{uncomfortable,} and, as there

 seemed to be no sort of \textcolor{blue}{chance} of her ever getting out of the room

 again, no wonder she felt \textcolor{red}{unhappy.}



 ‘It was much pleasanter at home,’ \textcolor{blue}{thought} poor Alice, ‘when one wasn’t

 always \textcolor{BurntOrange}{growing} larger and \textcolor{red}{smaller,} and being ordered about by mice and

 rabbits. I almost wish I hadn’t gone down that rabbit-hole--and yet--and

 yet--it’s rather curious, you know, this sort of life! I do wonder what

 CAN have \textcolor{blue}{happened} to me! When I used to read fairy-tales, I \textcolor{BurntOrange}{fancied} that

 \textcolor{green}{kind} of thing never \textcolor{blue}{happened,} and now here I am in the middle of one!

 There ought to be a book written about me, that there ought! And when I

 \textcolor{BurntOrange}{grow} up, \textcolor{red}{I’ll} write one--but I’m grown up now,’ she added in a \textcolor{red}{sorrowful}

 tone; ‘at least there’s no room to \textcolor{BurntOrange}{grow} up any more HERE.’



 ‘But then,’ \textcolor{blue}{thought} Alice, ‘shall I NEVER get any older than I am

 now? That’ll be a \textcolor{BurntOrange}{comfort,} one way--never to be an old woman--but

 then--always to have \textcolor{BurntOrange}{lessons} to \textcolor{green}{learn!} Oh, I shouldn’t like THAT!’



 ‘Oh, you \textcolor{red}{foolish} Alice!’ she answered herself. ‘How can you \textcolor{green}{learn}

 \textcolor{BurntOrange}{lessons} in here? Why, there’s hardly room for YOU, and no room at all

 for any lesson-books!’



 And so she went on, taking first one side and then the other, and making

 quite a conversation of it altogether; but after a few minutes she heard

 a voice outside, and stopped to listen.



 ‘Mary Ann! Mary Ann!’ said the voice. ‘Fetch me my gloves this moment!’

 Then came a little \textcolor{red}{pattering} of feet on the stairs. Alice knew it was

 the Rabbit coming to look for her, and she trembled till she shook the

 house, quite \textcolor{red}{forgetting} that she was now about a thousand \textcolor{blue}{times} as large

 as the Rabbit, and had no \textcolor{green}{reason} to be \textcolor{red}{afraid} of it.



 Presently the Rabbit came up to the door, and tried to open it; but, as

 the door opened inwards, and Alice’s \textcolor{red}{elbow} was pressed hard against it,

 that \textcolor{blue}{attempt} \textcolor{green}{proved} a \textcolor{red}{failure.} Alice heard it say to itself ‘Then \textcolor{red}{I’ll}

 go round and get in at the window.’



 ‘THAT you \textcolor{blue}{won’t’} \textcolor{blue}{thought} Alice, and, after \textcolor{BurntOrange}{waiting} till she \textcolor{BurntOrange}{fancied}

 she heard the Rabbit just under the window, she \textcolor{blue}{suddenly} spread out her

 hand, and made a snatch in the air. She did not get hold of anything,

 but she heard a little \textcolor{BurntOrange}{shriek} and a \textcolor{red}{fall,} and a \textcolor{BurntOrange}{crash} of \textcolor{red}{broken} glass,

 from which she concluded that it was just possible it had \textcolor{red}{fallen} into a

 cucumber-frame, or something of the sort.



 Next came an \textcolor{red}{angry} voice--the Rabbit’s--‘Pat! Pat! Where are you?’ And

 then a voice she had never heard before, ‘Sure then I’m here! Digging

 for apples, yer honour!’



 ‘Digging for apples, indeed!’ said the Rabbit angrily. ‘Here! Come and

 help me out of THIS!’ (Sounds of more \textcolor{red}{broken} glass.)



 ‘Now tell me, Pat, what’s that in the window?’



 ‘Sure, it’s an arm, yer honour!’ (He pronounced it ‘arrum.’)



 ‘An arm, you goose! Who ever saw one that size? Why, it \textcolor{green}{fills} the whole

 window!’



 ‘Sure, it does, yer honour: but it’s an arm for all that.’



 ‘Well, it’s got no business there, at any rate: go and take it away!’



 There was a \textcolor{blue}{long} silence after this, and Alice could only hear whispers

 now and then; such as, ‘Sure, I don’t like it, yer honour, at all, at

 all!’ ‘Do as I tell you, you \textcolor{red}{coward!’} and at last she spread out her

 hand again, and made another snatch in the air. This \textcolor{blue}{time} there were

 TWO little \textcolor{BurntOrange}{shrieks,} and more sounds of \textcolor{red}{broken} glass. ‘What a number of

 cucumber-frames there must be!’ \textcolor{blue}{thought} Alice. ‘I wonder what they’ll do

 next! As for \textcolor{green}{pulling} me out of the window, I only wish they COULD! I’m

 sure I don’t want to stay in here any longer!’



 She \textcolor{BurntOrange}{waited} for some \textcolor{blue}{time} without \textcolor{red}{hearing} anything more: at last came a

 rumbling of little cartwheels, and the sound of a \textcolor{BurntOrange}{good} many voices

 all \textcolor{green}{talking} together: she made out the \textcolor{green}{words:} ‘Where’s the other

 ladder?--Why, I hadn’t to bring but one; Bill’s got the other--Bill!

 fetch it here, lad!--Here, put ‘em up at this corner--No, tie ‘em

 together first--they don’t reach half high enough yet--Oh! they’ll

 do well enough; don’t be particular--Here, Bill! \textcolor{blue}{catch} hold of this

 rope--Will the roof bear?--Mind that loose slate--Oh, it’s coming

 down! Heads below!’ (a loud crash)--‘Now, who did that?--It was Bill, I

 fancy--Who’s to go down the chimney?--Nay, I shan’t! YOU do it!--That I

 \textcolor{blue}{won’t,} then!--Bill’s to go down--Here, Bill! the \textcolor{green}{master} says you’re to

 go down the chimney!’



 ‘Oh! So Bill’s got to come down the chimney, has he?’ said Alice to

 herself. ‘Shy, they seem to put everything upon Bill! I wouldn’t be in

 Bill’s place for a \textcolor{BurntOrange}{good} \textcolor{BurntOrange}{deal:} this fireplace is narrow, to be sure; but

 I THINK I can \textcolor{red}{kick} a little!’



 She drew her foot as far down the chimney as she could, and \textcolor{BurntOrange}{waited}

 till she heard a little animal (she couldn’t \textcolor{blue}{guess} of what sort it was)

 scratching and scrambling about in the chimney close above her: then,

 saying to herself ‘This is Bill,’ she gave one sharp \textcolor{red}{kick,} and \textcolor{BurntOrange}{waited} to

 see what would \textcolor{blue}{happen} next.



 The first thing she heard was a \textcolor{green}{general} \textcolor{green}{chorus} of ‘There goes Bill!’

 then the Rabbit’s voice along--‘Catch him, you by the hedge!’ then

 silence, and then another \textcolor{red}{confusion} of voices--‘Hold up his head--Brandy

 now--Don’t \textcolor{red}{choke} him--How was it, old \textcolor{green}{fellow?} What \textcolor{blue}{happened} to you? Tell

 us all about it!’



 Last came a little \textcolor{red}{feeble,} squeaking voice, [‘That’s Bill,’ \textcolor{blue}{thought}

 Alice,) ‘Well, I hardly know--No more, thank ye; I’m better now--but I’m

 a \textcolor{BurntOrange}{deal} too flustered to tell you--all I know is, something comes at me

 like a Jack-in-the-box, and up I goes like a sky-rocket!’



 ‘So you did, old \textcolor{green}{fellow!’} said the others.



 ‘We must burn the house down!’ said the Rabbit’s voice; and Alice called

 out as loud as she could, ‘If you do. \textcolor{red}{I’ll} set Dinah at you!’



 There was a dead silence instantly, and Alice \textcolor{blue}{thought} to herself, ‘I

 wonder what they WILL do next! If they had any \textcolor{green}{sense,} they’d take the

 roof off.’ After a minute or two, they began moving about again, and

 Alice heard the Rabbit say, ‘A barrowful will do, to begin with.’



 ‘A barrowful of WHAT?’ \textcolor{blue}{thought} Alice; but she had not \textcolor{blue}{long} to \textcolor{BurntOrange}{doubt,}

 for the next moment a shower of little pebbles came rattling in at the

 window, and some of them \textcolor{red}{hit} her in the face. \textcolor{red}{‘I’ll} put a stop to this,’

 she said to herself, and \textcolor{BurntOrange}{shouted} out, ‘You’d better not do that again!’

 which produced another dead silence.



 Alice noticed with some \textcolor{BurntOrange}{surprise} that the pebbles were all turning into

 little cakes as they lay on the floor, and a bright idea came into her

 head. ‘If I \textcolor{green}{eat} one of these cakes,’ she \textcolor{blue}{thought,} ‘it’s sure to make

 SOME \textcolor{red}{change} in my size; and as it can’t possibly make me larger, it must

 make me \textcolor{red}{smaller,} I suppose.’



 So she swallowed one of the cakes, and was \textcolor{BurntOrange}{delighted} to find that she

 began \textcolor{red}{shrinking} directly. As soon as she was \textcolor{red}{small} enough to get through

 the door, she ran out of the house, and \textcolor{green}{found} quite a crowd of little

 animals and birds \textcolor{BurntOrange}{waiting} outside. The poor little Lizard, Bill, was

 in the middle, being held up by two guinea-pigs, who were giving it

 something out of a bottle. They all made a rush at Alice the moment she

 appeared; but she ran off as hard as she could, and soon \textcolor{green}{found} herself

 \textcolor{green}{safe} in a thick wood.



 ‘The first thing I’ve got to do,’ said Alice to herself, as she wandered

 about in the wood, ‘is to \textcolor{BurntOrange}{grow} to my right size again; and the second

 thing is to find my way into that \textcolor{BurntOrange}{lovely} \textcolor{green}{garden.} I think that will be

 the best \textcolor{blue}{plan.’}



 It sounded an \textcolor{green}{excellent} \textcolor{blue}{plan,} no \textcolor{BurntOrange}{doubt,} and very \textcolor{green}{neatly} and simply

 arranged; the only \textcolor{red}{difficulty} was, that she had not the \textcolor{red}{smallest} idea

 how to set about it; and while she was peering about anxiously among

 the \textcolor{BurntOrange}{trees,} a little sharp \textcolor{red}{bark} just over her head made her look up in a

 great \textcolor{blue}{hurry.}



 An enormous \textcolor{BurntOrange}{puppy} was looking down at her with large round eyes, and

 feebly stretching out one paw, trying to touch her. ‘Poor little thing!’

 said Alice, in a \textcolor{green}{coaxing} tone, and she tried hard to whistle to it; but

 she was \textcolor{red}{terribly} \textcolor{BurntOrange}{frightened} all the \textcolor{blue}{time} at the \textcolor{blue}{thought} that it might be

 \textcolor{BurntOrange}{hungry,} in which \textcolor{red}{case} it would be very likely to \textcolor{green}{eat} her up in \textcolor{red}{spite} of

 all her \textcolor{green}{coaxing.}



 Hardly knowing what she did, she picked up a little bit of stick, and

 held it out to the \textcolor{BurntOrange}{puppy;} whereupon the \textcolor{BurntOrange}{puppy} jumped into the air off

 all its feet at once, with a \textcolor{BurntOrange}{yelp} of \textcolor{BurntOrange}{delight,} and rushed at the stick,

 and made believe to \textcolor{BurntOrange}{worry} it; then Alice dodged behind a great thistle,

 to keep herself from being run over; and the moment she appeared on the

 other side, the \textcolor{BurntOrange}{puppy} made another rush at the stick, and \textcolor{red}{tumbled} head

 over \textcolor{red}{heels} in its \textcolor{blue}{hurry} to get hold of it; then Alice, thinking it was

 very like having a game of play with a cart-horse, and \textcolor{BurntOrange}{expecting} every

 moment to be trampled under its feet, ran round the thistle again; then

 the \textcolor{BurntOrange}{puppy} began a \textcolor{green}{series} of short charges at the stick, running a very

 little way \textcolor{green}{forwards} each \textcolor{blue}{time} and a \textcolor{blue}{long} way back, and barking hoarsely

 all the while, till at last it sat down a \textcolor{BurntOrange}{good} way off, panting, with

 its tongue hanging out of its \textcolor{blue}{mouth,} and its great eyes half shut.



 This seemed to Alice a \textcolor{BurntOrange}{good} \textcolor{BurntOrange}{opportunity} for making her \textcolor{BurntOrange}{escape;} so she

 set off at once, and ran till she was quite tired and out of breath, and

 till the \textcolor{BurntOrange}{puppy’s} \textcolor{red}{bark} sounded quite faint in the distance.



 ‘And yet what a \textcolor{green}{dear} little \textcolor{BurntOrange}{puppy} it was!’ said Alice, as she leant

 against a buttercup to \textcolor{green}{rest} herself, and fanned herself with one of the

 leaves: ‘I should have liked \textcolor{BurntOrange}{teaching} it \textcolor{BurntOrange}{tricks} very much, if--if I’d

 only been the right size to do it! Oh \textcolor{green}{dear!} I’d nearly \textcolor{red}{forgotten} that

 I’ve got to \textcolor{BurntOrange}{grow} up again! Let me see--how IS it to be \textcolor{green}{managed?} I

 suppose I ought to \textcolor{green}{eat} or drink something or other; but the great

 \textcolor{green}{question} is, what?’



 The great \textcolor{green}{question} certainly was, what? Alice looked all round her at

 the flowers and the blades of grass, but she did not see anything that

 looked like the right thing to \textcolor{green}{eat} or drink under the circumstances.

 There was a large mushroom \textcolor{BurntOrange}{growing} near her, about the same height as

 herself; and when she had looked under it, and on both sides of it, and

 behind it, it occurred to her that she might as well look and see what

 was on the \textcolor{BurntOrange}{top} of it.



 She stretched herself up on tiptoe, and peeped over the edge of the

 mushroom, and her eyes \textcolor{BurntOrange}{immediately} met those of a large caterpillar,

 that was sitting on the \textcolor{BurntOrange}{top} with its arms folded, quietly smoking a \textcolor{blue}{long}

 hookah, and taking not the \textcolor{red}{smallest} notice of her or of anything else.









 CHAPTER V. \textcolor{green}{Advice} from a Caterpillar



 The Caterpillar and Alice looked at each other for some \textcolor{blue}{time} in silence:

 at last the Caterpillar took the hookah out of its \textcolor{blue}{mouth,} and addressed

 her in a \textcolor{red}{languid,} sleepy voice.



 ‘Who are YOU?’ said the Caterpillar.



 This was not an \textcolor{green}{encouraging} opening for a conversation. Alice replied,

 rather shyly, ‘I--I hardly know, \textcolor{green}{sir,} just at present--at least I know

 who I WAS when I got up this morning, but I think I must have been

 \textcolor{red}{changed} several \textcolor{blue}{times} since then.’



 ‘What do you mean by that?’ said the Caterpillar sternly. \textcolor{green}{‘Explain}

 yourself!’



 ‘I can’t \textcolor{green}{explain} MYSELF, I’m \textcolor{red}{afraid,} \textcolor{green}{sir’} said Alice, ‘because I’m not

 myself, you see.’



 ‘I don’t see,’ said the Caterpillar.



 ‘I’m \textcolor{red}{afraid} I can’t put it more clearly,’ Alice replied very politely,

 ‘for I can’t understand it myself to begin with; and being so many

 different sizes in a day is very \textcolor{red}{confusing.’}



 ‘It isn’t,’ said the Caterpillar.



 ‘Well, perhaps you haven’t \textcolor{green}{found} it so yet,’ said Alice; ‘but when you

 have to turn into a chrysalis--you will some day, you know--and then

 after that into a butterfly, I should think you’ll feel it a little

 queer, \textcolor{blue}{won’t} you?’



 ‘Not a bit,’ said the Caterpillar.



 ‘Well, perhaps your \textcolor{BurntOrange}{feelings} may be different,’ said Alice; ‘all I know

 is, it would feel very queer to ME.’



 ‘You!’ said the Caterpillar contemptuously. ‘Who are YOU?’



 Which brought them back again to the beginning of the conversation.

 Alice felt a little irritated at the Caterpillar’s making such VERY

 short remarks, and she drew herself up and said, very gravely, ‘I think,

 you ought to tell me who YOU are, first.’



 ‘Why?’ said the Caterpillar.



 Here was another puzzling \textcolor{green}{question;} and as Alice could not think of any

 \textcolor{BurntOrange}{good} \textcolor{green}{reason,} and as the Caterpillar seemed to be in a VERY \textcolor{red}{unpleasant}

 state of mind, she turned away.



 ‘Come back!’ the Caterpillar called after her. ‘I’ve something \textcolor{green}{important}

 to say!’



 This sounded \textcolor{green}{promising,} certainly: Alice turned and came back again.



 ‘Keep your temper,’ said the Caterpillar.



 ‘Is that all?’ said Alice, swallowing down her \textcolor{red}{anger} as well as she

 could.



 ‘No,’ said the Caterpillar.



 Alice \textcolor{blue}{thought} she might as well \textcolor{BurntOrange}{wait,} as she had nothing else to do, and

 perhaps after all it might tell her something \textcolor{green}{worth} \textcolor{red}{hearing.} For some

 minutes it puffed away without speaking, but at last it unfolded its

 arms, took the hookah out of its \textcolor{blue}{mouth} again, and said, ‘So you think

 you’re \textcolor{red}{changed,} do you?’



 ‘I’m \textcolor{red}{afraid} I am, \textcolor{green}{sir,’} said Alice; ‘I can’t remember things as I

 used--and I don’t keep the same size for ten minutes together!’



 ‘Can’t remember WHAT things?’ said the Caterpillar.



 ‘Well, I’ve tried to say “HOW DOTH THE LITTLE BUSY \textcolor{red}{BEE,”} but it all came

 different!’ Alice replied in a very \textcolor{red}{melancholy} voice.



 ‘Repeat, “YOU ARE OLD, \textcolor{green}{FATHER} WILLIAM,”’ said the Caterpillar.



 Alice folded her hands, and began:--



 ‘You are old, \textcolor{green}{Father} William,’ the \textcolor{BurntOrange}{young} man said,

 ‘And your hair has become very \textcolor{BurntOrange}{white;}

 And yet you incessantly stand on your head--

 Do you think, at your age, it is right?’



 ‘In my \textcolor{BurntOrange}{youth,’} \textcolor{green}{Father} William replied to his son,

 ‘I \textcolor{red}{feared} it might \textcolor{red}{injure} the brain;

 But, now that I’m perfectly sure I have none,

 Why, I do it again and again.’



 ‘You are old,’ said the \textcolor{BurntOrange}{youth,} ‘as I mentioned before,

 And have grown most uncommonly \textcolor{red}{fat;}

 Yet you turned a back-somersault in at the door--

 \textcolor{BurntOrange}{Pray,} what is the \textcolor{green}{reason} of that?’



 ‘In my \textcolor{BurntOrange}{youth,’} said the \textcolor{green}{sage,} as he shook his grey locks,

 ‘I kept all my limbs very supple

 By the use of this ointment--one shilling the box--

 Allow me to sell you a couple?’



 ‘You are old,’ said the \textcolor{BurntOrange}{youth,} ‘and your jaws are too weak

 For anything tougher than suet;

 Yet you finished the goose, with the bones and the beak--

 \textcolor{BurntOrange}{Pray} how did you \textcolor{green}{manage} to do it?’



 ‘In my \textcolor{BurntOrange}{youth,’} said his \textcolor{green}{father,} ‘I took to the \textcolor{green}{law,}

 And \textcolor{red}{argued} each \textcolor{red}{case} with my wife;

 And the \textcolor{green}{muscular} \textcolor{green}{strength,} which it gave to my jaw,

 Has lasted the \textcolor{green}{rest} of my life.’



 ‘You are old,’ said the \textcolor{BurntOrange}{youth,} ‘one would hardly suppose

 That your eye was as \textcolor{BurntOrange}{steady} as ever;

 Yet you \textcolor{green}{balanced} an \textcolor{red}{eel} on the end of your \textcolor{red}{nose--}

 What made you so awfully \textcolor{green}{clever?’}



 ‘I have answered three \textcolor{green}{questions,} and that is enough,’

 Said his \textcolor{green}{father;} ‘don’t give yourself airs!

 Do you think I can listen all day to such stuff?

 Be off, or \textcolor{red}{I’ll} \textcolor{red}{kick} you down stairs!’





 ‘That is not said right,’ said the Caterpillar.



 ‘Not QUITE right, I’m \textcolor{red}{afraid,’} said Alice, timidly; ‘some of the \textcolor{green}{words}

 have got altered.’



 ‘It is \textcolor{red}{wrong} from beginning to end,’ said the Caterpillar decidedly, and

 there was silence for some minutes.



 The Caterpillar was the first to speak.



 ‘What size do you want to be?’ it asked.



 ‘Oh, I’m not particular as to size,’ Alice hastily replied; ‘only one

 doesn’t like \textcolor{red}{changing} so often, you know.’



 ‘I DON’T know,’ said the Caterpillar.



 Alice said nothing: she had never been so much \textcolor{red}{contradicted} in her life

 before, and she felt that she was \textcolor{BurntOrange}{losing} her temper.



 ‘Are you \textcolor{green}{content} now?’ said the Caterpillar.



 ‘Well, I should like to be a LITTLE larger, \textcolor{green}{sir,} if you wouldn’t mind,’

 said Alice: ‘three inches is such a \textcolor{red}{wretched} height to be.’



 ‘It is a very \textcolor{BurntOrange}{good} height indeed!’ said the Caterpillar angrily, \textcolor{red}{rearing}

 itself \textcolor{green}{upright} as it \textcolor{red}{spoke} (it was exactly three inches high).



 ‘But I’m not used to it!’ pleaded poor Alice in a piteous tone. And

 she \textcolor{blue}{thought} of herself, ‘I wish the \textcolor{red}{creatures} wouldn’t be so easily

 \textcolor{red}{offended!’}



 ‘You’ll get used to it in \textcolor{blue}{time,’} said the Caterpillar; and it put the

 hookah into its \textcolor{blue}{mouth} and began smoking again.



 This \textcolor{blue}{time} Alice \textcolor{BurntOrange}{waited} patiently until it chose to speak again. In

 a minute or two the Caterpillar took the hookah out of its \textcolor{blue}{mouth}

 and \textcolor{red}{yawned} once or twice, and shook itself. Then it got down off the

 mushroom, and \textcolor{red}{crawled} away in the grass, merely remarking as it went,

 ‘One side will make you \textcolor{BurntOrange}{grow} taller, and the other side will make you

 \textcolor{BurntOrange}{grow} shorter.’



 ‘One side of WHAT? The other side of WHAT?’ \textcolor{blue}{thought} Alice to herself.



 ‘Of the mushroom,’ said the Caterpillar, just as if she had asked it

 aloud; and in another moment it was out of sight.



 Alice remained looking thoughtfully at the mushroom for a minute, trying

 to make out which were the two sides of it; and as it was perfectly

 round, she \textcolor{green}{found} this a very \textcolor{red}{difficult} \textcolor{green}{question.} However, at last she

 stretched her arms round it as far as they would go, and \textcolor{red}{broke} off a bit

 of the edge with each hand.



 ‘And now which is which?’ she said to herself, and nibbled a little of

 the right-hand bit to try the effect: the next moment she felt a \textcolor{BurntOrange}{violent}

 blow underneath her chin: it had struck her foot!



 She was a \textcolor{BurntOrange}{good} \textcolor{BurntOrange}{deal} \textcolor{BurntOrange}{frightened} by this very \textcolor{blue}{sudden} \textcolor{red}{change,} but she felt

 that there was no \textcolor{blue}{time} to be \textcolor{BurntOrange}{lost,} as she was \textcolor{red}{shrinking} rapidly; so she

 set to work at once to \textcolor{green}{eat} some of the other bit. Her chin was pressed

 so closely against her foot, that there was hardly room to open her

 \textcolor{blue}{mouth;} but she did it at last, and \textcolor{green}{managed} to swallow a \textcolor{red}{morsel} of the

 lefthand bit.





 * * * * * * *



 * * * * * *



 * * * * * * *



 ‘Come, my head’s free at last!’ said Alice in a tone of \textcolor{BurntOrange}{delight,} which

 \textcolor{red}{changed} into \textcolor{BurntOrange}{alarm} in another moment, when she \textcolor{green}{found} that her \textcolor{green}{shoulders}

 were nowhere to be \textcolor{green}{found:} all she could see, when she looked down, was

 an \textcolor{green}{immense} length of neck, which seemed to rise like a \textcolor{red}{stalk} out of a

 \textcolor{green}{sea} of \textcolor{green}{green} leaves that lay far below her.



 ‘What CAN all that \textcolor{green}{green} stuff be?’ said Alice. ‘And where HAVE my

 \textcolor{green}{shoulders} got to? And oh, my poor hands, how is it I can’t see you?’

 She was moving them about as she \textcolor{red}{spoke,} but no \textcolor{blue}{result} seemed to follow,

 except a little shaking among the distant \textcolor{green}{green} leaves.



 As there seemed to be no \textcolor{blue}{chance} of getting her hands up to her head, she

 tried to get her head down to them, and was \textcolor{BurntOrange}{delighted} to find that her

 neck would bend about easily in any direction, like a \textcolor{red}{serpent.} She had

 just \textcolor{BurntOrange}{succeeded} in curving it down into a \textcolor{green}{graceful} zigzag, and was going

 to dive in among the leaves, which she \textcolor{green}{found} to be nothing but the \textcolor{BurntOrange}{tops}

 of the \textcolor{BurntOrange}{trees} under which she had been wandering, when a sharp \textcolor{red}{hiss} made

 her draw back in a \textcolor{blue}{hurry:} a large \textcolor{red}{pigeon} had flown into her face, and

 was \textcolor{red}{beating} her \textcolor{red}{violently} with its wings.



 \textcolor{red}{‘Serpent!’} \textcolor{BurntOrange}{screamed} the \textcolor{red}{Pigeon.}



 ‘I’m NOT a \textcolor{red}{serpent!’} said Alice indignantly. ‘Let me alone!’



 \textcolor{red}{‘Serpent,} I say again!’ repeated the \textcolor{red}{Pigeon,} but in a more \textcolor{red}{subdued} tone,

 and added with a \textcolor{green}{kind} of \textcolor{red}{sob,} ‘I’ve tried every way, and nothing seems

 to suit them!’



 ‘I haven’t the least idea what you’re \textcolor{green}{talking} about,’ said Alice.



 ‘I’ve tried the roots of \textcolor{BurntOrange}{trees,} and I’ve tried \textcolor{green}{banks,} and I’ve tried

 hedges,’ the \textcolor{red}{Pigeon} went on, without attending to her; ‘but those

 \textcolor{red}{serpents!} There’s no pleasing them!’



 Alice was more and more puzzled, but she \textcolor{blue}{thought} there was no use in

 saying anything more till the \textcolor{red}{Pigeon} had finished.



 ‘As if it wasn’t trouble enough hatching the eggs,’ said the \textcolor{red}{Pigeon;}

 ‘but I must be on the look-out for \textcolor{red}{serpents} night and day! Why, I

 haven’t had a wink of sleep these three weeks!’



 ‘I’m very sorry you’ve been annoyed,’ said Alice, who was beginning to

 see its meaning.



 ‘And just as I’d taken the highest \textcolor{BurntOrange}{tree} in the wood,’ continued the

 \textcolor{red}{Pigeon,} raising its voice to a \textcolor{BurntOrange}{shriek,} ‘and just as I was thinking I

 should be free of them at last, they must needs come wriggling down from

 the \textcolor{green}{sky!} Ugh, \textcolor{red}{Serpent!’}



 ‘But I’m NOT a \textcolor{red}{serpent,} I tell you!’ said Alice. ‘I’m a--I’m a--’



 ‘Well! WHAT are you?’ said the \textcolor{red}{Pigeon.} ‘I can see you’re trying to

 invent something!’



 ‘I--I’m a little girl,’ said Alice, rather doubtfully, as she remembered

 the number of \textcolor{red}{changes} she had gone through that day.



 ‘A likely story indeed!’ said the \textcolor{red}{Pigeon} in a tone of the deepest

 \textcolor{red}{contempt.} ‘I’ve seen a \textcolor{BurntOrange}{good} many little girls in my \textcolor{blue}{time,} but never ONE

 with such a neck as that! No, no! You’re a \textcolor{red}{serpent;} and there’s no use

 \textcolor{red}{denying} it. I suppose you’ll be telling me next that you never tasted an

 egg!’



 ‘I HAVE tasted eggs, certainly,’ said Alice, who was a very \textcolor{green}{truthful}

 \textcolor{BurntOrange}{child;} ‘but little girls \textcolor{green}{eat} eggs quite as much as \textcolor{red}{serpents} do, you

 know.’



 ‘I don’t believe it,’ said the \textcolor{red}{Pigeon;} ‘but if they do, why then they’re

 a \textcolor{green}{kind} of \textcolor{red}{serpent,} that’s all I can say.’



 This was such a new idea to Alice, that she was quite silent for a

 minute or two, which gave the \textcolor{red}{Pigeon} the \textcolor{BurntOrange}{opportunity} of adding, ‘You’re

 looking for eggs, I know THAT well enough; and what does it matter to me

 whether you’re a little girl or a \textcolor{red}{serpent?’}



 ‘It matters a \textcolor{BurntOrange}{good} \textcolor{BurntOrange}{deal} to ME,’ said Alice hastily; ‘but I’m not looking

 for eggs, as it happens; and if I was, I shouldn’t want YOURS: I don’t

 like them raw.’



 ‘Well, be off, then!’ said the \textcolor{red}{Pigeon} in a sulky tone, as it settled

 down again into its \textcolor{green}{nest.} Alice \textcolor{red}{crouched} down among the \textcolor{BurntOrange}{trees} as well as

 she could, for her neck kept getting entangled among the branches, and

 every now and then she had to stop and untwist it. After a while she

 remembered that she still held the pieces of mushroom in her hands, and

 she set to work very \textcolor{green}{carefully,} nibbling first at one and then at the

 other, and \textcolor{BurntOrange}{growing} sometimes taller and sometimes shorter, until she had

 \textcolor{BurntOrange}{succeeded} in bringing herself down to her \textcolor{green}{usual} height.



 It was so \textcolor{blue}{long} since she had been anything near the right size, that it

 felt quite strange at first; but she got used to it in a few minutes,

 and began \textcolor{green}{talking} to herself, as \textcolor{green}{usual.} ‘Come, there’s half my \textcolor{blue}{plan} done

 now! How puzzling all these \textcolor{red}{changes} are! I’m never sure what I’m going

 to be, from one minute to another! However, I’ve got back to my right

 size: the next thing is, to get into that \textcolor{green}{beautiful} garden--how IS that

 to be done, I wonder?’ As she said this, she came \textcolor{blue}{suddenly} upon an open

 place, with a little house in it about four feet high. ‘Whoever lives

 there,’ \textcolor{blue}{thought} Alice, ‘it’ll never do to come upon them THIS size: why,

 I should \textcolor{BurntOrange}{frighten} them out of their \textcolor{green}{wits!’} So she began nibbling at the

 righthand bit again, and did not venture to go near the house till she

 had brought herself down to nine inches high.









 CHAPTER VI. \textcolor{red}{Pig} and Pepper



 For a minute or two she stood looking at the house, and wondering what

 to do next, when \textcolor{blue}{suddenly} a footman in livery came running out of the

 wood--(she considered him to be a footman because he was in livery:

 otherwise, judging by his face only, she would have called him a

 fish)--and rapped loudly at the door with his knuckles. It was opened

 by another footman in livery, with a round face, and large eyes like a

 frog; and both footmen, Alice noticed, had powdered hair that \textcolor{green}{curled} all

 over their heads. She felt very curious to know what it was all about,

 and crept a little way out of the wood to listen.



 The Fish-Footman began by producing from under his arm a great \textcolor{blue}{letter,}

 nearly as large as himself, and this he handed over to the other,

 saying, in a solemn tone, ‘For the Duchess. An \textcolor{BurntOrange}{invitation} from the Queen

 to play croquet.’ The Frog-Footman repeated, in the same solemn tone,

 only \textcolor{red}{changing} the order of the \textcolor{green}{words} a little, ‘From the Queen. An

 \textcolor{BurntOrange}{invitation} for the Duchess to play croquet.’



 Then they both bowed low, and their \textcolor{green}{curls} got entangled together.



 Alice \textcolor{BurntOrange}{laughed} so much at this, that she had to run back into the

 wood for \textcolor{red}{fear} of their \textcolor{red}{hearing} her; and when she next peeped out the

 Fish-Footman was gone, and the other was sitting on the \textcolor{green}{ground} near the

 door, \textcolor{BurntOrange}{staring} stupidly up into the \textcolor{green}{sky.}



 Alice went timidly up to the door, and knocked.



 ‘There’s no sort of use in knocking,’ said the Footman, ‘and that for

 two \textcolor{green}{reasons.} First, because I’m on the same side of the door as you

 are; secondly, because they’re making such a \textcolor{red}{noise} inside, no one could

 possibly hear you.’ And certainly there was a most \textcolor{green}{extraordinary} \textcolor{red}{noise}

 going on within--a \textcolor{green}{constant} \textcolor{BurntOrange}{howling} and \textcolor{BurntOrange}{sneezing,} and every now and then

 a great \textcolor{BurntOrange}{crash,} as if a dish or kettle had been \textcolor{red}{broken} to pieces.



 ‘Please, then,’ said Alice, ‘how am I to get in?’



 ‘There might be some \textcolor{green}{sense} in your knocking,’ the Footman went on

 without attending to her, ‘if we had the door between us. For instance,

 if you were INSIDE, you might knock, and I could let you out, you know.’

 He was looking up into the \textcolor{green}{sky} all the \textcolor{blue}{time} he was speaking, and this

 Alice \textcolor{blue}{thought} decidedly uncivil. ‘But perhaps he can’t help it,’ she

 said to herself; ‘his eyes are so VERY nearly at the \textcolor{BurntOrange}{top} of his head.

 But at any rate he might answer questions.--How am I to get in?’ she

 repeated, aloud.



 ‘I shall sit here,’ the Footman remarked, ‘till \textcolor{blue}{tomorrow--’}



 At this moment the door of the house opened, and a large plate came

 skimming out, straight at the Footman’s head: it just grazed his \textcolor{red}{nose,}

 and \textcolor{red}{broke} to pieces against one of the \textcolor{BurntOrange}{trees} behind him.



 ‘--or next day, maybe,’ the Footman continued in the same tone, exactly

 as if nothing had \textcolor{blue}{happened.}



 ‘How am I to get in?’ asked Alice again, in a louder tone.



 ‘ARE you to get in at all?’ said the Footman. ‘That’s the first

 \textcolor{green}{question,} you know.’



 It was, no \textcolor{BurntOrange}{doubt:} only Alice did not like to be told so. ‘It’s really

 \textcolor{BurntOrange}{dreadful,’} she \textcolor{red}{muttered} to herself, ‘the way all the \textcolor{red}{creatures} \textcolor{red}{argue.}

 It’s enough to drive one \textcolor{red}{crazy!’}



 The Footman seemed to think this a \textcolor{BurntOrange}{good} \textcolor{BurntOrange}{opportunity} for repeating his

 remark, with variations. ‘I shall sit here,’ he said, ‘on and off, for

 days and days.’



 ‘But what am I to do?’ said Alice.



 ‘Anything you like,’ said the Footman, and began whistling.



 ‘Oh, there’s no use in \textcolor{green}{talking} to him,’ said Alice desperately: ‘he’s

 perfectly \textcolor{red}{idiotic!’} And she opened the door and went in.



 The door \textcolor{green}{led} right into a large kitchen, which was \textcolor{green}{full} of smoke from

 one end to the other: the Duchess was sitting on a three-legged stool in

 the middle, nursing a \textcolor{green}{baby;} the cook was leaning over the \textcolor{red}{fire,} stirring

 a large cauldron which seemed to be \textcolor{green}{full} of \textcolor{green}{soup.}



 ‘There’s certainly too much pepper in that \textcolor{green}{soup!’} Alice said to herself,

 as well as she could for \textcolor{BurntOrange}{sneezing.}



 There was certainly too much of it in the air. Even the Duchess

 \textcolor{BurntOrange}{sneezed} occasionally; and as for the \textcolor{green}{baby,} it was \textcolor{BurntOrange}{sneezing} and \textcolor{BurntOrange}{howling}

 alternately without a moment’s pause. The only things in the kitchen

 that did not \textcolor{BurntOrange}{sneeze,} were the cook, and a large cat which was sitting on

 the \textcolor{green}{hearth} and \textcolor{BurntOrange}{grinning} from ear to ear.



 ‘Please would you tell me,’ said Alice, a little timidly, for she was

 not quite sure whether it was \textcolor{BurntOrange}{good} manners for her to speak first, ‘why

 your cat \textcolor{BurntOrange}{grins} like that?’



 ‘It’s a Cheshire cat,’ said the Duchess, ‘and that’s why. \textcolor{red}{Pig!’}



 She said the last \textcolor{green}{word} with such \textcolor{blue}{sudden} \textcolor{red}{violence} that Alice quite

 jumped; but she saw in another moment that it was addressed to the \textcolor{green}{baby,}

 and not to her, so she took \textcolor{green}{courage,} and went on again:--



 ‘I didn’t know that Cheshire cats always \textcolor{BurntOrange}{grinned;} in \textcolor{green}{fact,} I didn’t know

 that cats COULD \textcolor{BurntOrange}{grin.’}



 ‘They all can,’ said the Duchess; ‘and most of ‘em do.’



 ‘I don’t know of any that do,’ Alice said very politely, feeling quite

 \textcolor{green}{pleased} to have got into a conversation.



 ‘You don’t know much,’ said the Duchess; ‘and that’s a \textcolor{green}{fact.’}



 Alice did not at all like the tone of this remark, and \textcolor{blue}{thought} it would

 be as well to introduce some other \textcolor{red}{subject} of conversation. While she

 was trying to fix on one, the cook took the cauldron of \textcolor{green}{soup} off the

 \textcolor{red}{fire,} and at once set to work throwing everything within her reach at

 the Duchess and the baby--the fire-irons came first; then followed a

 shower of saucepans, plates, and dishes. The Duchess took no notice of

 them even when they \textcolor{red}{hit} her; and the \textcolor{green}{baby} was \textcolor{BurntOrange}{howling} so much already,

 that it was quite \textcolor{red}{impossible} to say whether the blows \textcolor{red}{hurt} it or not.



 ‘Oh, PLEASE mind what you’re doing!’ \textcolor{red}{cried} Alice, jumping up and down in

 an \textcolor{red}{agony} of \textcolor{red}{terror.} ‘Oh, there goes his \textcolor{BurntOrange}{PRECIOUS} \textcolor{red}{nose’;} as an unusually

 large saucepan flew close by it, and very nearly carried it off.



 ‘If everybody minded their own business,’ the Duchess said in a \textcolor{red}{hoarse}

 \textcolor{red}{growl,} ‘the world would go round a \textcolor{BurntOrange}{deal} faster than it does.’



 ‘Which would NOT be an \textcolor{green}{advantage,’} said Alice, who felt very \textcolor{BurntOrange}{glad} to get

 an \textcolor{BurntOrange}{opportunity} of \textcolor{green}{showing} off a little of her \textcolor{green}{knowledge.} ‘Just think of

 what work it would make with the day and night! You see the earth takes

 twenty-four hours to turn round on its axis--’



 \textcolor{green}{‘Talking} of axes,’ said the Duchess, \textcolor{red}{‘chop} off her head!’



 Alice glanced rather anxiously at the cook, to see if she meant to take

 the hint; but the cook was busily stirring the \textcolor{green}{soup,} and seemed not to

 be listening, so she went on again: ‘Twenty-four hours, I THINK; or is

 it twelve? I--’



 ‘Oh, don’t \textcolor{red}{bother} ME,’ said the Duchess; ‘I never could abide figures!’

 And with that she began nursing her \textcolor{BurntOrange}{child} again, \textcolor{BurntOrange}{singing} a sort of

 lullaby to it as she did so, and giving it a \textcolor{BurntOrange}{violent} shake at the end of

 every line:



 ‘Speak roughly to your little \textcolor{red}{boy,}

 And beat him when he \textcolor{BurntOrange}{sneezes:}

 He only does it to \textcolor{red}{annoy,}

 Because he knows it \textcolor{BurntOrange}{teases.’}



 \textcolor{green}{CHORUS.}



 (In which the cook and the \textcolor{green}{baby} \textcolor{green}{joined):--}



 ‘Wow! wow! wow!’



 While the Duchess sang the second verse of the song, she kept tossing

 the \textcolor{green}{baby} \textcolor{red}{violently} up and down, and the poor little thing \textcolor{BurntOrange}{howled} so,

 that Alice could hardly hear the \textcolor{green}{words:--}



 ‘I speak severely to my \textcolor{red}{boy,}

 I beat him when he \textcolor{BurntOrange}{sneezes;}

 For he can thoroughly \textcolor{BurntOrange}{enjoy}

 The pepper when he \textcolor{BurntOrange}{pleases!’}



 \textcolor{green}{CHORUS.}



 ‘Wow! wow! wow!’



 ‘Here! you may \textcolor{green}{nurse} it a bit, if you like!’ the Duchess said to Alice,

 flinging the \textcolor{green}{baby} at her as she \textcolor{red}{spoke.} ‘I must go and get \textcolor{blue}{ready} to play

 croquet with the Queen,’ and she \textcolor{blue}{hurried} out of the room. The cook threw

 a frying-pan after her as she went out, but it just missed her.



 Alice caught the \textcolor{green}{baby} with some \textcolor{red}{difficulty,} as it was a queer-shaped

 little \textcolor{red}{creature,} and held out its arms and legs in all directions, ‘just

 like a star-fish,’ \textcolor{blue}{thought} Alice. The poor little thing was \textcolor{red}{snorting}

 like a steam-engine when she caught it, and kept doubling itself up and

 straightening itself out again, so that altogether, for the first minute

 or two, it was as much as she could do to hold it.



 As soon as she had made out the \textcolor{green}{proper} way of nursing it, (which was to

 twist it up into a sort of knot, and then keep tight hold of its right

 ear and left foot, so as to \textcolor{red}{prevent} its \textcolor{red}{undoing} itself,) she carried

 it out into the open air. ‘IF I don’t take this \textcolor{BurntOrange}{child} away with me,’

 \textcolor{blue}{thought} Alice, ‘they’re sure to \textcolor{red}{kill} it in a day or two: wouldn’t it be

 \textcolor{BurntOrange}{murder} to \textcolor{BurntOrange}{leave} it behind?’ She said the last \textcolor{green}{words} out loud, and the

 little thing grunted in reply (it had left off \textcolor{BurntOrange}{sneezing} by this \textcolor{blue}{time).}

 ‘Don’t grunt,’ said Alice; ‘that’s not at all a \textcolor{green}{proper} way of expressing

 yourself.’



 The \textcolor{green}{baby} grunted again, and Alice looked very anxiously into its face to

 see what was the matter with it. There could be no \textcolor{BurntOrange}{doubt} that it had

 a VERY turn-up \textcolor{red}{nose,} much more like a snout than a \textcolor{green}{real} \textcolor{red}{nose;} also its

 eyes were getting extremely \textcolor{red}{small} for a \textcolor{green}{baby:} altogether Alice did not

 like the look of the thing at all. ‘But perhaps it was only \textcolor{red}{sobbing,’}

 she \textcolor{blue}{thought,} and looked into its eyes again, to see if there were any

 tears.



 No, there were no tears. ‘If you’re going to turn into a \textcolor{red}{pig,} my \textcolor{green}{dear,’}

 said Alice, seriously, \textcolor{red}{‘I’ll} have nothing more to do with you. Mind

 now!’ The poor little thing sobbed again (or grunted, it was \textcolor{red}{impossible}

 to say which), and they went on for some while in silence.



 Alice was just beginning to think to herself, ‘Now, what am I to do with

 this \textcolor{red}{creature} when I get it home?’ when it grunted again, so \textcolor{red}{violently,}

 that she looked down into its face in some \textcolor{BurntOrange}{alarm.} This \textcolor{blue}{time} there could

 be NO \textcolor{red}{mistake} about it: it was neither more nor less than a \textcolor{red}{pig,} and she

 felt that it would be quite \textcolor{red}{absurd} for her to carry it further.



 So she set the little \textcolor{red}{creature} down, and felt quite relieved to see

 it trot away quietly into the wood. ‘If it had grown up,’ she said

 to herself, ‘it would have made a \textcolor{BurntOrange}{dreadfully} \textcolor{red}{ugly} \textcolor{BurntOrange}{child:} but it makes

 rather a handsome \textcolor{red}{pig,} I think.’ And she began thinking over other

 \textcolor{BurntOrange}{children} she knew, who might do very well as \textcolor{red}{pigs,} and was just saying

 to herself, ‘if one only knew the right way to \textcolor{red}{change} them--’ when she

 was a little \textcolor{BurntOrange}{startled} by seeing the Cheshire Cat sitting on a bough of a

 \textcolor{BurntOrange}{tree} a few yards off.



 The Cat only \textcolor{BurntOrange}{grinned} when it saw Alice. It looked good-natured, she

 \textcolor{blue}{thought:} still it had VERY \textcolor{blue}{long} \textcolor{red}{claws} and a great many teeth, so she

 felt that it ought to be \textcolor{BurntOrange}{treated} with \textcolor{BurntOrange}{respect.}



 ‘Cheshire \textcolor{red}{Puss,’} she began, rather timidly, as she did not at all know

 whether it would like the name: however, it only \textcolor{BurntOrange}{grinned} a little wider.

 ‘Come, it’s \textcolor{green}{pleased} so far,’ \textcolor{blue}{thought} Alice, and she went on. ‘Would you

 tell me, please, which way I ought to go from here?’



 ‘That depends a \textcolor{BurntOrange}{good} \textcolor{BurntOrange}{deal} on where you want to get to,’ said the Cat.



 ‘I don’t much care where--’ said Alice.



 ‘Then it doesn’t matter which way you go,’ said the Cat.



 ‘--so \textcolor{blue}{long} as I get SOMEWHERE,’ Alice added as an explanation.



 ‘Oh, you’re sure to do that,’ said the Cat, ‘if you only walk \textcolor{blue}{long}

 enough.’



 Alice felt that this could not be \textcolor{red}{denied,} so she tried another \textcolor{green}{question.}

 ‘What sort of people live about here?’



 ‘In THAT direction,’ the Cat said, waving its right paw round, ‘lives

 a Hatter: and in THAT direction,’ waving the other paw, ‘lives a \textcolor{green}{March}

 Hare. \textcolor{green}{Visit} either you like: they’re both \textcolor{red}{mad.’}



 ‘But I don’t want to go among \textcolor{red}{mad} people,’ Alice remarked.



 ‘Oh, you can’t help that,’ said the Cat: ‘we’re all \textcolor{red}{mad} here. I’m \textcolor{red}{mad.}

 You’re \textcolor{red}{mad.’}



 ‘How do you know I’m \textcolor{red}{mad?’} said Alice.



 ‘You must be,’ said the Cat, ‘or you wouldn’t have come here.’



 Alice didn’t think that \textcolor{green}{proved} it at all; however, she went on ‘And how

 do you know that you’re \textcolor{red}{mad?’}



 ‘To begin with,’ said the Cat, ‘a dog’s not \textcolor{red}{mad.} You \textcolor{BurntOrange}{grant} that?’



 ‘I suppose so,’ said Alice.



 ‘Well, then,’ the Cat went on, ‘you see, a dog \textcolor{red}{growls} when it’s \textcolor{red}{angry,}

 and wags its tail when it’s \textcolor{green}{pleased.} Now I \textcolor{red}{growl} when I’m \textcolor{green}{pleased,} and

 wag my tail when I’m \textcolor{red}{angry.} Therefore I’m \textcolor{red}{mad.’}



 ‘I call it \textcolor{green}{purring,} not \textcolor{red}{growling,’} said Alice.



 ‘Call it what you like,’ said the Cat. ‘Do you play croquet with the

 Queen to-day?’



 ‘I should like it very much,’ said Alice, ‘but I haven’t been \textcolor{BurntOrange}{invited}

 yet.’



 ‘You’ll see me there,’ said the Cat, and \textcolor{BurntOrange}{vanished.}



 Alice was not much \textcolor{blue}{surprised} at this, she was getting so used to queer

 things \textcolor{blue}{happening.} While she was looking at the place where it had been,

 it \textcolor{blue}{suddenly} appeared again.



 ‘By-the-bye, what became of the \textcolor{green}{baby?’} said the Cat. ‘I’d nearly

 \textcolor{red}{forgotten} to ask.’



 ‘It turned into a \textcolor{red}{pig,’} Alice quietly said, just as if it had come back

 in a natural way.



 ‘I \textcolor{blue}{thought} it would,’ said the Cat, and \textcolor{BurntOrange}{vanished} again.



 Alice \textcolor{BurntOrange}{waited} a little, half \textcolor{BurntOrange}{expecting} to see it again, but it did not

 appear, and after a minute or two she walked on in the direction in

 which the \textcolor{green}{March} Hare was said to live. ‘I’ve seen hatters before,’ she

 said to herself; ‘the \textcolor{green}{March} Hare will be much the most \textcolor{green}{interesting,} and

 perhaps as this is May it \textcolor{blue}{won’t} be \textcolor{BurntOrange}{raving} mad--at least not so \textcolor{red}{mad} as

 it was in \textcolor{green}{March.’} As she said this, she looked up, and there was the Cat

 again, sitting on a branch of a \textcolor{BurntOrange}{tree.}



 ‘Did you say \textcolor{red}{pig,} or fig?’ said the Cat.



 ‘I said \textcolor{red}{pig,’} replied Alice; ‘and I wish you wouldn’t keep appearing and

 \textcolor{blue}{vanishing} so \textcolor{blue}{suddenly:} you make one quite giddy.’



 ‘All right,’ said the Cat; and this \textcolor{blue}{time} it \textcolor{BurntOrange}{vanished} quite slowly,

 beginning with the end of the tail, and ending with the \textcolor{BurntOrange}{grin,} which

 remained some \textcolor{blue}{time} after the \textcolor{green}{rest} of it had gone.



 ‘Well! I’ve often seen a cat without a \textcolor{BurntOrange}{grin,’} \textcolor{blue}{thought} Alice; ‘but a \textcolor{BurntOrange}{grin}

 without a cat! It’s the most curious thing I ever saw in my life!’



 She had not gone much farther before she came in sight of the house

 of the \textcolor{green}{March} Hare: she \textcolor{blue}{thought} it must be the right house, because the

 chimneys were \textcolor{green}{shaped} like ears and the roof was thatched with fur. It

 was so large a house, that she did not like to go nearer till she had

 nibbled some more of the lefthand bit of mushroom, and raised herself to

 about two feet high: even then she walked up towards it rather timidly,

 saying to herself ‘Suppose it should be \textcolor{BurntOrange}{raving} \textcolor{red}{mad} after all! I almost

 wish I’d gone to see the Hatter instead!’









 CHAPTER VII. A \textcolor{red}{Mad} Tea-Party



 There was a table set out under a \textcolor{BurntOrange}{tree} in front of the house, and the

 \textcolor{green}{March} Hare and the Hatter were having tea at it: a Dormouse was sitting

 between them, fast asleep, and the other two were using it as a

 \textcolor{green}{cushion,} \textcolor{green}{resting} their \textcolor{red}{elbows} on it, and \textcolor{green}{talking} over its head. ‘Very

 \textcolor{red}{uncomfortable} for the Dormouse,’ \textcolor{blue}{thought} Alice; ‘only, as it’s asleep, I

 suppose it doesn’t mind.’



 The table was a large one, but the three were all crowded together at

 one corner of it: ‘No room! No room!’ they \textcolor{red}{cried} out when they saw Alice

 coming. ‘There’s PLENTY of room!’ said Alice indignantly, and she sat

 down in a large arm-chair at one end of the table.



 ‘Have some wine,’ the \textcolor{green}{March} Hare said in an \textcolor{green}{encouraging} tone.



 Alice looked all round the table, but there was nothing on it but tea.

 ‘I don’t see any wine,’ she remarked.



 ‘There isn’t any,’ said the \textcolor{green}{March} Hare.



 ‘Then it wasn’t very \textcolor{green}{civil} of you to \textcolor{green}{offer} it,’ said Alice angrily.



 ‘It wasn’t very \textcolor{green}{civil} of you to sit down without being \textcolor{BurntOrange}{invited,’} said

 the \textcolor{green}{March} Hare.



 ‘I didn’t know it was YOUR table,’ said Alice; ‘it’s laid for a great

 many more than three.’



 ‘Your hair wants cutting,’ said the Hatter. He had been looking at Alice

 for some \textcolor{blue}{time} with great \textcolor{BurntOrange}{curiosity,} and this was his first \textcolor{green}{speech.}



 ‘You should \textcolor{green}{learn} not to make \textcolor{green}{personal} remarks,’ Alice said with some

 severity; ‘it’s very rude.’



 The Hatter opened his eyes very wide on \textcolor{red}{hearing} this; but all he SAID

 was, ‘Why is a raven like a writing-desk?’



 ‘Come, we shall have some \textcolor{BurntOrange}{fun} now!’ \textcolor{blue}{thought} Alice. ‘I’m \textcolor{BurntOrange}{glad} they’ve

 begun asking riddles.--I believe I can \textcolor{blue}{guess} that,’ she added aloud.



 ‘Do you mean that you think you can find out the answer to it?’ said the

 \textcolor{green}{March} Hare.



 ‘Exactly so,’ said Alice.



 ‘Then you should say what you mean,’ the \textcolor{green}{March} Hare went on.



 ‘I do,’ Alice hastily replied; ‘at least--at least I mean what I

 say--that’s the same thing, you know.’



 ‘Not the same thing a bit!’ said the Hatter. ‘You might just as well say

 that “I see what I \textcolor{green}{eat”} is the same thing as “I \textcolor{green}{eat} what I see”!’



 ‘You might just as well say,’ added the \textcolor{green}{March} Hare, ‘that “I like what I

 get” is the same thing as “I get what I like”!’



 ‘You might just as well say,’ added the Dormouse, who seemed to be

 \textcolor{green}{talking} in his sleep, ‘that “I breathe when I sleep” is the same thing

 as “I sleep when I breathe”!’



 ‘It IS the same thing with you,’ said the Hatter, and here the

 conversation dropped, and the party sat silent for a minute, while Alice

 \textcolor{blue}{thought} over all she could remember about ravens and writing-desks,

 which wasn’t much.



 The Hatter was the first to \textcolor{blue}{break} the silence. ‘What day of the month

 is it?’ he said, turning to Alice: he had taken his \textcolor{BurntOrange}{watch} out of his

 pocket, and was looking at it uneasily, shaking it every now and then,

 and holding it to his ear.



 Alice considered a little, and then said ‘The fourth.’



 ‘Two days \textcolor{red}{wrong!’} sighed the Hatter. ‘I told you butter wouldn’t suit

 the works!’ he added looking angrily at the \textcolor{green}{March} Hare.



 ‘It was the BEST butter,’ the \textcolor{green}{March} Hare meekly replied.



 ‘Yes, but some crumbs must have got in as well,’ the Hatter \textcolor{red}{grumbled:}

 ‘you shouldn’t have put it in with the bread-knife.’



 The \textcolor{green}{March} Hare took the \textcolor{BurntOrange}{watch} and looked at it gloomily: then he dipped

 it into his cup of tea, and looked at it again: but he could think of

 nothing better to say than his first remark, ‘It was the BEST butter,

 you know.’



 Alice had been looking over his \textcolor{green}{shoulder} with some \textcolor{BurntOrange}{curiosity.} ‘What a

 funny \textcolor{BurntOrange}{watch!’} she remarked. ‘It tells the day of the month, and doesn’t

 tell what o’clock it is!’



 ‘Why should it?’ \textcolor{red}{muttered} the Hatter. ‘Does YOUR \textcolor{BurntOrange}{watch} tell you what

 year it is?’



 ‘Of course not,’ Alice replied very \textcolor{green}{readily:} ‘but that’s because it

 stays the same year for such a \textcolor{blue}{long} \textcolor{blue}{time} together.’



 ‘Which is just the \textcolor{red}{case} with MINE,’ said the Hatter.



 Alice felt \textcolor{BurntOrange}{dreadfully} puzzled. The Hatter’s remark seemed to have no

 sort of meaning in it, and yet it was certainly English. ‘I don’t quite

 understand you,’ she said, as politely as she could.



 ‘The Dormouse is asleep again,’ said the Hatter, and he poured a little

 \textcolor{red}{hot} tea upon its \textcolor{red}{nose.}



 The Dormouse shook its head impatiently, and said, without opening its

 eyes, ‘Of course, of course; just what I was going to remark myself.’



 ‘Have you \textcolor{blue}{guessed} the \textcolor{blue}{riddle} yet?’ the Hatter said, turning to Alice

 again.



 ‘No, I give it up,’ Alice replied: ‘what’s the answer?’



 ‘I haven’t the slightest idea,’ said the Hatter.



 ‘Nor I,’ said the \textcolor{green}{March} Hare.



 Alice sighed \textcolor{red}{wearily.} ‘I think you might do something better with the

 \textcolor{blue}{time,’} she said, ‘than \textcolor{red}{waste} it in asking \textcolor{blue}{riddles} that have no answers.’



 ‘If you knew \textcolor{blue}{Time} as well as I do,’ said the Hatter, ‘you wouldn’t \textcolor{green}{talk}

 about \textcolor{red}{wasting} IT. It’s HIM.’



 ‘I don’t know what you mean,’ said Alice.



 ‘Of course you don’t!’ the Hatter said, tossing his head contemptuously.

 ‘I \textcolor{BurntOrange}{dare} say you never even \textcolor{red}{spoke} to \textcolor{blue}{Time!’}



 ‘Perhaps not,’ Alice \textcolor{BurntOrange}{cautiously} replied: ‘but I know I have to beat \textcolor{blue}{time}

 when I \textcolor{green}{learn} \textcolor{BurntOrange}{music.’}



 ‘Ah! that \textcolor{green}{accounts} for it,’ said the Hatter. ‘He \textcolor{blue}{won’t} stand \textcolor{red}{beating.}

 Now, if you only kept on \textcolor{BurntOrange}{good} terms with him, he’d do almost anything

 you liked with the \textcolor{blue}{clock.} For instance, suppose it were nine o’clock in

 the morning, just \textcolor{blue}{time} to begin \textcolor{BurntOrange}{lessons:} you’d only have to whisper a

 hint to \textcolor{blue}{Time,} and round goes the \textcolor{blue}{clock} in a \textcolor{BurntOrange}{twinkling!} Half-past one,

 \textcolor{blue}{time} for \textcolor{green}{dinner!’}



 [‘I only wish it was,’ the \textcolor{green}{March} Hare said to itself in a whisper.)



 ‘That would be grand, certainly,’ said Alice thoughtfully: ‘but then--I

 shouldn’t be \textcolor{BurntOrange}{hungry} for it, you know.’



 ‘Not at first, perhaps,’ said the Hatter: ‘but you could keep it to

 half-past one as \textcolor{blue}{long} as you liked.’



 ‘Is that the way YOU \textcolor{green}{manage?’} Alice asked.



 The Hatter shook his head mournfully. ‘Not I!’ he replied. ‘We

 \textcolor{red}{quarrelled} last March--just before HE went \textcolor{red}{mad,} you know--’ (pointing

 with his tea spoon at the \textcolor{green}{March} Hare,) ‘--it was at the great concert

 given by the Queen of Hearts, and I had to \textcolor{BurntOrange}{sing}



 \textcolor{BurntOrange}{“Twinkle,} \textcolor{BurntOrange}{twinkle,} little bat!

 How I wonder what you’re at!”



 You know the song, perhaps?’



 ‘I’ve heard something like it,’ said Alice.



 ‘It goes on, you know,’ the Hatter continued, ‘in this way:--



 “Up above the world you fly,

 Like a tea-tray in the \textcolor{green}{sky.}

 \textcolor{BurntOrange}{Twinkle,} \textcolor{BurntOrange}{twinkle--“’}



 Here the Dormouse shook itself, and began \textcolor{BurntOrange}{singing} in its sleep \textcolor{BurntOrange}{‘Twinkle,}

 \textcolor{BurntOrange}{twinkle,} \textcolor{BurntOrange}{twinkle,} \textcolor{BurntOrange}{twinkle--’} and went on so \textcolor{blue}{long} that they had to pinch

 it to make it stop.



 ‘Well, I’d hardly finished the first verse,’ said the Hatter, ‘when the

 Queen jumped up and bawled out, “He’s \textcolor{BurntOrange}{murdering} the \textcolor{blue}{time!} Off with his

 head!”’



 ‘How \textcolor{BurntOrange}{dreadfully} \textcolor{red}{savage!’} \textcolor{blue}{exclaimed} Alice.



 ‘And ever since that,’ the Hatter went on in a \textcolor{red}{mournful} tone, ‘he \textcolor{blue}{won’t}

 do a thing I ask! It’s always six o’clock now.’



 A bright idea came into Alice’s head. ‘Is that the \textcolor{green}{reason} so many

 tea-things are put out here?’ she asked.



 ‘Yes, that’s it,’ said the Hatter with a sigh: ‘it’s always tea-time,

 and we’ve no \textcolor{blue}{time} to wash the things between whiles.’



 ‘Then you keep moving round, I suppose?’ said Alice.



 ‘Exactly so,’ said the Hatter: ‘as the things get used up.’



 ‘But what happens when you come to the beginning again?’ Alice ventured

 to ask.



 ‘Suppose we \textcolor{red}{change} the \textcolor{red}{subject,’} the \textcolor{green}{March} Hare \textcolor{BurntOrange}{interrupted,} \textcolor{red}{yawning.}

 ‘I’m getting tired of this. I \textcolor{BurntOrange}{vote} the \textcolor{BurntOrange}{young} lady tells us a story.’



 ‘I’m \textcolor{red}{afraid} I don’t know one,’ said Alice, rather alarmed at the

 proposal.



 ‘Then the Dormouse shall!’ they both \textcolor{red}{cried.} ‘Wake up, Dormouse!’ And

 they pinched it on both sides at once.



 The Dormouse slowly opened his eyes. ‘I wasn’t asleep,’ he said in a

 \textcolor{red}{hoarse,} \textcolor{red}{feeble} voice: ‘I heard every \textcolor{green}{word} you \textcolor{green}{fellows} were saying.’



 ‘Tell us a story!’ said the \textcolor{green}{March} Hare.



 ‘Yes, please do!’ pleaded Alice.



 ‘And be quick about it,’ added the Hatter, ‘or you’ll be asleep again

 before it’s done.’



 ‘Once upon a \textcolor{blue}{time} there were three little sisters,’ the Dormouse began

 in a great \textcolor{blue}{hurry;} ‘and their names were Elsie, Lacie, and Tillie; and

 they lived at the \textcolor{red}{bottom} of a well--’



 ‘What did they live on?’ said Alice, who always took a great \textcolor{green}{interest} in

 \textcolor{green}{questions} of \textcolor{green}{eating} and \textcolor{red}{drinking.}



 ‘They lived on treacle,’ said the Dormouse, after thinking a minute or

 two.



 ‘They couldn’t have done that, you know,’ Alice gently remarked; ‘they’d

 have been \textcolor{red}{ill.’}



 ‘So they were,’ said the Dormouse; ‘VERY \textcolor{red}{ill.’}



 Alice tried to \textcolor{BurntOrange}{fancy} to herself what such an \textcolor{green}{extraordinary} ways of

 living would be like, but it puzzled her too much, so she went on: ‘But

 why did they live at the \textcolor{red}{bottom} of a well?’



 ‘Take some more tea,’ the \textcolor{green}{March} Hare said to Alice, very \textcolor{green}{earnestly.}



 ‘I’ve had nothing yet,’ Alice replied in an \textcolor{red}{offended} tone, ‘so I can’t

 take more.’



 ‘You mean you can’t take LESS,’ said the Hatter: ‘it’s very easy to take

 MORE than nothing.’



 ‘Nobody asked YOUR opinion,’ said Alice.



 ‘Who’s making \textcolor{green}{personal} remarks now?’ the Hatter asked triumphantly.



 Alice did not quite know what to say to this: so she helped herself

 to some tea and bread-and-butter, and then turned to the Dormouse, and

 repeated her \textcolor{green}{question.} ‘Why did they live at the \textcolor{red}{bottom} of a well?’



 The Dormouse again took a minute or two to think about it, and then

 said, ‘It was a treacle-well.’



 ‘There’s no such thing!’ Alice was beginning very angrily, but the

 Hatter and the \textcolor{green}{March} Hare went ‘Sh! sh!’ and the Dormouse sulkily

 remarked, ‘If you can’t be \textcolor{green}{civil,} you’d better finish the story for

 yourself.’



 ‘No, please go on!’ Alice said very \textcolor{green}{humbly;} ‘I \textcolor{blue}{won’t} \textcolor{BurntOrange}{interrupt} again. I

 \textcolor{BurntOrange}{dare} say there may be ONE.’



 ‘One, indeed!’ said the Dormouse indignantly. However, he consented to

 go on. ‘And so these three little sisters--they were \textcolor{green}{learning} to draw,

 you know--’



 ‘What did they draw?’ said Alice, quite \textcolor{red}{forgetting} her \textcolor{green}{promise.}



 ‘Treacle,’ said the Dormouse, without considering at all this \textcolor{blue}{time.}



 ‘I want a \textcolor{green}{clean} cup,’ \textcolor{BurntOrange}{interrupted} the Hatter: ‘let’s all move one place

 on.’



 He moved on as he \textcolor{red}{spoke,} and the Dormouse followed him: the \textcolor{green}{March} Hare

 moved into the Dormouse’s place, and Alice rather unwillingly took

 the place of the \textcolor{green}{March} Hare. The Hatter was the only one who got any

 \textcolor{green}{advantage} from the \textcolor{red}{change:} and Alice was a \textcolor{BurntOrange}{good} \textcolor{BurntOrange}{deal} \textcolor{red}{worse} off than

 before, as the \textcolor{green}{March} Hare had just \textcolor{red}{upset} the milk-jug into his plate.



 Alice did not wish to \textcolor{red}{offend} the Dormouse again, so she began very

 \textcolor{BurntOrange}{cautiously:} ‘But I don’t understand. Where did they draw the treacle

 from?’



 ‘You can draw water out of a water-well,’ said the Hatter; ‘so I should

 think you could draw treacle out of a treacle-well--eh, \textcolor{red}{stupid?’}



 ‘But they were IN the well,’ Alice said to the Dormouse, not choosing to

 notice this last remark.



 ‘Of course they were’, said the Dormouse; ‘--well in.’



 This answer so \textcolor{red}{confused} poor Alice, that she let the Dormouse go on for

 some \textcolor{blue}{time} without \textcolor{BurntOrange}{interrupting} it.



 ‘They were \textcolor{green}{learning} to draw,’ the Dormouse went on, \textcolor{red}{yawning} and rubbing

 its eyes, for it was getting very sleepy; ‘and they drew all manner of

 things--everything that begins with an M--’



 ‘Why with an M?’ said Alice.



 ‘Why not?’ said the \textcolor{green}{March} Hare.



 Alice was silent.



 The Dormouse had closed its eyes by this \textcolor{blue}{time,} and was going off into

 a doze; but, on being pinched by the Hatter, it woke up again with

 a little \textcolor{BurntOrange}{shriek,} and went on: ‘--that begins with an M, such as

 mouse-traps, and the moon, and memory, and muchness--you know you say

 things are “much of a muchness”--did you ever see such a thing as a

 drawing of a muchness?’



 ‘Really, now you ask me,’ said Alice, very much \textcolor{red}{confused,} ‘I don’t

 think--’



 ‘Then you shouldn’t \textcolor{green}{talk,’} said the Hatter.



 This piece of rudeness was more than Alice could \textcolor{red}{bear:} she got up in

 great \textcolor{red}{disgust,} and walked off; the Dormouse \textcolor{red}{fell} asleep instantly, and

 neither of the others took the least notice of her going, though she

 looked back once or twice, half hoping that they would call after her:

 the last \textcolor{blue}{time} she saw them, they were trying to put the Dormouse into

 the teapot.



 ‘At any rate \textcolor{red}{I’ll} never go THERE again!’ said Alice as she picked her

 way through the wood. ‘It’s the stupidest tea-party I ever was at in all

 my life!’



 Just as she said this, she noticed that one of the \textcolor{BurntOrange}{trees} had a door

 \textcolor{green}{leading} right into it. ‘That’s very curious!’ she \textcolor{blue}{thought.} ‘But

 everything’s curious today. I think I may as well go in at once.’ And in

 she went.



 Once more she \textcolor{green}{found} herself in the \textcolor{blue}{long} hall, and close to the little

 glass table. ‘Now, \textcolor{red}{I’ll} \textcolor{green}{manage} better this \textcolor{blue}{time,’} she said to herself,

 and began by taking the little golden key, and unlocking the door that

 \textcolor{green}{led} into the \textcolor{green}{garden.} Then she went to work nibbling at the mushroom (she

 had kept a piece of it in her pocket) till she was about a foot high:

 then she walked down the little passage: and THEN--she \textcolor{green}{found} herself at

 last in the \textcolor{green}{beautiful} \textcolor{green}{garden,} among the bright flower-beds and the \textcolor{green}{cool}

 fountains.









 CHAPTER VIII. The Queen’s Croquet-Ground



 A large rose-tree stood near the entrance of the \textcolor{green}{garden:} the roses

 \textcolor{BurntOrange}{growing} on it were \textcolor{BurntOrange}{white,} but there were three gardeners at it, busily

 painting them red. Alice \textcolor{blue}{thought} this a very curious thing, and she went

 nearer to \textcolor{BurntOrange}{watch} them, and just as she came up to them she heard one of

 them say, ‘Look out now, Five! Don’t go \textcolor{blue}{splashing} paint over me like

 that!’



 ‘I couldn’t help it,’ said Five, in a sulky tone; ‘Seven jogged my

 \textcolor{red}{elbow.’}



 On which Seven looked up and said, ‘That’s right, Five! Always lay the

 \textcolor{red}{blame} on others!’



 ‘YOU’D better not \textcolor{green}{talk!’} said Five. ‘I heard the Queen say only

 yesterday you \textcolor{BurntOrange}{deserved} to be beheaded!’



 ‘What for?’ said the one who had spoken first.



 ‘That’s none of YOUR business, Two!’ said Seven.



 ‘Yes, it IS his business!’ said Five, ‘and \textcolor{red}{I’ll} tell him--it was for

 bringing the cook tulip-roots instead of onions.’



 Seven flung down his brush, and had just begun ‘Well, of all the \textcolor{red}{unjust}

 things--’ when his eye \textcolor{blue}{chanced} to \textcolor{red}{fall} upon Alice, as she stood \textcolor{BurntOrange}{watching}

 them, and he checked himself \textcolor{blue}{suddenly:} the others looked round also, and

 all of them bowed low.



 ‘Would you tell me,’ said Alice, a little timidly, ‘why you are painting

 those roses?’



 Five and Seven said nothing, but looked at Two. Two began in a low

 voice, ‘Why the \textcolor{green}{fact} is, you see, Miss, this here ought to have been a

 RED rose-tree, and we put a \textcolor{BurntOrange}{white} one in by \textcolor{red}{mistake;} and if the Queen

 was to find it out, we should all have our heads cut off, you know.

 So you see, Miss, we’re doing our best, afore she comes, to--’ At this

 moment Five, who had been anxiously looking across the \textcolor{green}{garden,} called

 out ‘The Queen! The Queen!’ and the three gardeners instantly threw

 themselves flat upon their faces. There was a sound of many footsteps,

 and Alice looked round, \textcolor{BurntOrange}{eager} to see the Queen.



 First came ten \textcolor{BurntOrange}{soldiers} carrying clubs; these were all \textcolor{green}{shaped} like

 the three gardeners, oblong and flat, with their hands and feet at the

 corners: next the ten courtiers; these were ornamented all over with

 \textcolor{green}{diamonds,} and walked two and two, as the \textcolor{BurntOrange}{soldiers} did. After these came

 the royal \textcolor{BurntOrange}{children;} there were ten of them, and the little \textcolor{green}{dears} came

 jumping merrily along hand in hand, in couples: they were all ornamented

 with hearts. Next came the guests, mostly \textcolor{green}{Kings} and Queens, and among

 them Alice recognised the \textcolor{BurntOrange}{White} Rabbit: it was \textcolor{green}{talking} in a \textcolor{blue}{hurried}

 \textcolor{BurntOrange}{nervous} manner, \textcolor{BurntOrange}{smiling} at everything that was said, and went by without

 noticing her. Then followed the Knave of Hearts, carrying the \textcolor{green}{King’s}

 crown on a crimson \textcolor{green}{velvet} \textcolor{green}{cushion;} and, last of all this grand

 \textcolor{BurntOrange}{procession,} came THE \textcolor{green}{KING} AND QUEEN OF HEARTS.



 Alice was rather \textcolor{red}{doubtful} whether she ought not to \textcolor{red}{lie} down on her face

 like the three gardeners, but she could not remember ever having heard

 of such a \textcolor{BurntOrange}{rule} at \textcolor{BurntOrange}{processions;} ‘and besides, what would be the use of

 a \textcolor{BurntOrange}{procession,’} \textcolor{blue}{thought} she, ‘if people had all to \textcolor{red}{lie} down upon their

 faces, so that they couldn’t see it?’ So she stood still where she was,

 and \textcolor{BurntOrange}{waited.}



 When the \textcolor{BurntOrange}{procession} came opposite to Alice, they all stopped and looked

 at her, and the Queen said severely ‘Who is this?’ She said it to the

 Knave of Hearts, who only bowed and \textcolor{BurntOrange}{smiled} in reply.



 \textcolor{red}{‘Idiot!’} said the Queen, tossing her head impatiently; and, turning to

 Alice, she went on, ‘What’s your name, \textcolor{BurntOrange}{child?’}



 ‘My name is Alice, so please your \textcolor{green}{Majesty,’} said Alice very politely;

 but she added, to herself, ‘Why, they’re only a pack of cards, after

 all. I needn’t be \textcolor{red}{afraid} of them!’



 ‘And who are THESE?’ said the Queen, pointing to the three gardeners who

 were \textcolor{red}{lying} round the rosetree; for, you see, as they were \textcolor{red}{lying} on their

 faces, and the pattern on their backs was the same as the \textcolor{green}{rest} of the

 pack, she could not tell whether they were gardeners, or \textcolor{BurntOrange}{soldiers,} or

 courtiers, or three of her own \textcolor{BurntOrange}{children.}



 ‘How should I know?’ said Alice, \textcolor{blue}{surprised} at her own \textcolor{green}{courage.} ‘It’s no

 business of MINE.’



 The Queen turned crimson with \textcolor{red}{fury,} and, after \textcolor{red}{glaring} at her for a

 moment like a \textcolor{BurntOrange}{wild} \textcolor{red}{beast,} \textcolor{BurntOrange}{screamed} ‘Off with her head! Off--’



 \textcolor{red}{‘Nonsense!’} said Alice, very loudly and decidedly, and the Queen was

 silent.



 The \textcolor{green}{King} laid his hand upon her arm, and timidly said ‘Consider, my

 \textcolor{green}{dear:} she is only a \textcolor{BurntOrange}{child!’}



 The Queen turned angrily away from him, and said to the Knave ‘Turn them

 over!’



 The Knave did so, very \textcolor{green}{carefully,} with one foot.



 ‘Get up!’ said the Queen, in a \textcolor{BurntOrange}{shrill,} loud voice, and the three

 gardeners instantly jumped up, and began bowing to the \textcolor{green}{King,} the Queen,

 the royal \textcolor{BurntOrange}{children,} and everybody else.



 \textcolor{BurntOrange}{‘Leave} off that!’ \textcolor{BurntOrange}{screamed} the Queen. ‘You make me giddy.’ And then,

 turning to the rose-tree, she went on, ‘What HAVE you been doing here?’



 ‘May it please your \textcolor{green}{Majesty,’} said Two, in a very \textcolor{BurntOrange}{humble} tone, going

 down on one knee as he \textcolor{red}{spoke,} ‘we were trying--’



 ‘I see!’ said the Queen, who had meanwhile been examining the roses.

 ‘Off with their heads!’ and the \textcolor{BurntOrange}{procession} moved on, three of the

 \textcolor{BurntOrange}{soldiers} remaining behind to execute the \textcolor{red}{unfortunate} gardeners, who ran

 to Alice for protection.



 ‘You shan’t be beheaded!’ said Alice, and she put them into a large

 flower-pot that stood near. The three \textcolor{BurntOrange}{soldiers} wandered about for a

 minute or two, looking for them, and then quietly \textcolor{green}{marched} off after the

 others.



 ‘Are their heads off?’ \textcolor{BurntOrange}{shouted} the Queen.



 ‘Their heads are gone, if it please your \textcolor{green}{Majesty!’} the \textcolor{BurntOrange}{soldiers} \textcolor{BurntOrange}{shouted}

 in reply.



 ‘That’s right!’ \textcolor{BurntOrange}{shouted} the Queen. ‘Can you play croquet?’



 The \textcolor{BurntOrange}{soldiers} were silent, and looked at Alice, as the \textcolor{green}{question} was

 evidently meant for her.



 ‘Yes!’ \textcolor{BurntOrange}{shouted} Alice.



 ‘Come on, then!’ roared the Queen, and Alice \textcolor{green}{joined} the \textcolor{BurntOrange}{procession,}

 wondering very much what would \textcolor{blue}{happen} next.



 ‘It’s--it’s a very fine day!’ said a \textcolor{red}{timid} voice at her side. She was

 walking by the \textcolor{BurntOrange}{White} Rabbit, who was peeping anxiously into her face.



 ‘Very,’ said Alice: ‘--where’s the Duchess?’



 \textcolor{green}{‘Hush!} \textcolor{green}{Hush!’} said the Rabbit in a low, \textcolor{blue}{hurried} tone. He looked

 anxiously over his \textcolor{green}{shoulder} as he \textcolor{red}{spoke,} and then raised himself upon

 tiptoe, put his \textcolor{blue}{mouth} close to her ear, and whispered ‘She’s under

 \textcolor{BurntOrange}{sentence} of \textcolor{BurntOrange}{execution.’}



 ‘What for?’ said Alice.



 ‘Did you say “What a \textcolor{red}{pity!”?’} the Rabbit asked.



 ‘No, I didn’t,’ said Alice: ‘I don’t think it’s at all a \textcolor{red}{pity.} I said

 “What for?”’



 ‘She boxed the Queen’s ears--’ the Rabbit began. Alice gave a little

 \textcolor{BurntOrange}{scream} of \textcolor{BurntOrange}{laughter.} ‘Oh, \textcolor{green}{hush!’} the Rabbit whispered in a \textcolor{BurntOrange}{frightened}

 tone. ‘The Queen will hear you! You see, she came rather \textcolor{red}{late,} and the

 Queen said--’



 ‘Get to your places!’ \textcolor{BurntOrange}{shouted} the Queen in a voice of thunder, and

 people began running about in all directions, \textcolor{red}{tumbling} up against each

 other; however, they got settled down in a minute or two, and the game

 began. Alice \textcolor{blue}{thought} she had never seen such a curious croquet-ground in

 her life; it was all ridges and \textcolor{red}{furrows;} the balls were live hedgehogs,

 the mallets live flamingoes, and the \textcolor{BurntOrange}{soldiers} had to double themselves

 up and to stand on their hands and feet, to make the arches.



 The chief \textcolor{red}{difficulty} Alice \textcolor{green}{found} at first was in \textcolor{green}{managing} her flamingo:

 she \textcolor{BurntOrange}{succeeded} in getting its body tucked away, comfortably enough, under

 her arm, with its legs hanging down, but generally, just as she had got

 its neck nicely straightened out, and was going to give the hedgehog a

 blow with its head, it WOULD twist itself round and look up in her face,

 with such a puzzled expression that she could not help bursting out

 \textcolor{BurntOrange}{laughing:} and when she had got its head down, and was going to begin

 again, it was very provoking to find that the hedgehog had unrolled

 itself, and was in the act of \textcolor{red}{crawling} away: besides all this, there was

 generally a ridge or \textcolor{red}{furrow} in the way wherever she wanted to send the

 hedgehog to, and, as the doubled-up \textcolor{BurntOrange}{soldiers} were always getting up

 and walking off to other parts of the \textcolor{green}{ground,} Alice soon came to the

 conclusion that it was a very \textcolor{red}{difficult} game indeed.



 The \textcolor{red}{players} all played at once without \textcolor{BurntOrange}{waiting} for turns, \textcolor{red}{quarrelling}

 all the while, and \textcolor{red}{fighting} for the hedgehogs; and in a very short

 \textcolor{blue}{time} the Queen was in a \textcolor{red}{furious} \textcolor{BurntOrange}{passion,} and went stamping about, and

 \textcolor{BurntOrange}{shouting} ‘Off with his head!’ or ‘Off with her head!’ about once in a

 minute.



 Alice began to feel very \textcolor{red}{uneasy:} to be sure, she had not as yet had any

 \textcolor{red}{dispute} with the Queen, but she knew that it might \textcolor{blue}{happen} any minute,

 ‘and then,’ \textcolor{blue}{thought} she, ‘what would become of me? They’re \textcolor{BurntOrange}{dreadfully}

 fond of beheading people here; the great wonder is, that there’s any one

 left \textcolor{BurntOrange}{alive!’}



 She was looking about for some way of \textcolor{BurntOrange}{escape,} and wondering whether she

 could get away without being seen, when she noticed a curious appearance

 in the air: it puzzled her very much at first, but, after \textcolor{BurntOrange}{watching} it

 a minute or two, she made it out to be a \textcolor{BurntOrange}{grin,} and she said to herself

 ‘It’s the Cheshire Cat: now I shall have somebody to \textcolor{green}{talk} to.’



 ‘How are you getting on?’ said the Cat, as soon as there was \textcolor{blue}{mouth}

 enough for it to speak with.



 Alice \textcolor{BurntOrange}{waited} till the eyes appeared, and then nodded. ‘It’s no use

 speaking to it,’ she \textcolor{blue}{thought,} ‘till its ears have come, or at least one

 of them.’ In another minute the whole head appeared, and then Alice put

 down her flamingo, and began an \textcolor{green}{account} of the game, feeling very \textcolor{BurntOrange}{glad}

 she had someone to listen to her. The Cat seemed to think that there was

 enough of it now in sight, and no more of it appeared.



 ‘I don’t think they play at all \textcolor{green}{fairly,’} Alice began, in rather a

 \textcolor{red}{complaining} tone, ‘and they all \textcolor{red}{quarrel} so \textcolor{BurntOrange}{dreadfully} one can’t hear

 oneself speak--and they don’t seem to have any \textcolor{BurntOrange}{rules} in particular;

 at least, if there are, nobody attends to them--and you’ve no idea how

 \textcolor{red}{confusing} it is all the things being \textcolor{BurntOrange}{alive;} for instance, there’s the

 arch I’ve got to go through next walking about at the other end of the

 ground--and I should have croqueted the Queen’s hedgehog just now, only

 it ran away when it saw mine coming!’



 ‘How do you like the Queen?’ said the Cat in a low voice.



 ‘Not at all,’ said Alice: ‘she’s so extremely--’ Just then she noticed

 that the Queen was close behind her, listening: so she went on,

 ‘--likely to win, that it’s hardly \textcolor{green}{worth} while finishing the game.’



 The Queen \textcolor{BurntOrange}{smiled} and passed on.



 ‘Who ARE you \textcolor{green}{talking} to?’ said the \textcolor{green}{King,} going up to Alice, and looking

 at the Cat’s head with great \textcolor{BurntOrange}{curiosity.}



 ‘It’s a \textcolor{green}{friend} of mine--a Cheshire Cat,’ said Alice: ‘allow me to

 introduce it.’



 ‘I don’t like the look of it at all,’ said the \textcolor{green}{King:} ‘however, it may

 \textcolor{BurntOrange}{kiss} my hand if it likes.’



 ‘I’d rather not,’ the Cat remarked.



 ‘Don’t be impertinent,’ said the \textcolor{green}{King,} ‘and don’t look at me like that!’

 He got behind Alice as he \textcolor{red}{spoke.}



 ‘A cat may look at a \textcolor{green}{king,’} said Alice. ‘I’ve read that in some book,

 but I don’t remember where.’



 ‘Well, it must be \textcolor{red}{removed,’} said the \textcolor{green}{King} very decidedly, and he called

 the Queen, who was passing at the moment, ‘My \textcolor{green}{dear!} I wish you would

 have this cat \textcolor{red}{removed!’}



 The Queen had only one way of settling all \textcolor{red}{difficulties,} great or \textcolor{red}{small.}

 ‘Off with his head!’ she said, without even looking round.



 \textcolor{red}{‘I’ll} fetch the \textcolor{red}{executioner} myself,’ said the \textcolor{green}{King} eagerly, and he

 \textcolor{blue}{hurried} off.



 Alice \textcolor{blue}{thought} she might as well go back, and see how the game was going

 on, as she heard the Queen’s voice in the distance, \textcolor{BurntOrange}{screaming} with

 \textcolor{BurntOrange}{passion.} She had already heard her \textcolor{BurntOrange}{sentence} three of the \textcolor{red}{players} to be

 executed for having missed their turns, and she did not like the look

 of things at all, as the game was in such \textcolor{red}{confusion} that she never knew

 whether it was her turn or not. So she went in search of her hedgehog.



 The hedgehog was engaged in a \textcolor{red}{fight} with another hedgehog, which seemed

 to Alice an \textcolor{green}{excellent} \textcolor{BurntOrange}{opportunity} for croqueting one of them with the

 other: the only \textcolor{red}{difficulty} was, that her flamingo was gone across to the

 other side of the \textcolor{green}{garden,} where Alice could see it trying in a \textcolor{red}{helpless}

 sort of way to fly up into a \textcolor{BurntOrange}{tree.}



 By the \textcolor{blue}{time} she had caught the flamingo and brought it back, the \textcolor{red}{fight}

 was over, and both the hedgehogs were out of sight: ‘but it doesn’t

 matter much,’ \textcolor{blue}{thought} Alice, ‘as all the arches are gone from this side

 of the \textcolor{green}{ground.’} So she tucked it away under her arm, that it might not

 \textcolor{BurntOrange}{escape} again, and went back for a little more conversation with her

 \textcolor{green}{friend.}



 When she got back to the Cheshire Cat, she was \textcolor{blue}{surprised} to find quite a

 large crowd collected round it: there was a \textcolor{red}{dispute} going on between

 the \textcolor{red}{executioner,} the \textcolor{green}{King,} and the Queen, who were all \textcolor{green}{talking} at once,

 while all the \textcolor{green}{rest} were quite silent, and looked very \textcolor{red}{uncomfortable.}



 The moment Alice appeared, she was \textcolor{blue}{appealed} to by all three to settle

 the \textcolor{green}{question,} and they repeated their \textcolor{red}{arguments} to her, though, as they

 all \textcolor{red}{spoke} at once, she \textcolor{green}{found} it very hard indeed to make out exactly

 what they said.



 The \textcolor{red}{executioner’s} \textcolor{red}{argument} was, that you couldn’t cut off a head unless

 there was a body to cut it off from: that he had never had to do such a

 thing before, and he wasn’t going to begin at HIS \textcolor{blue}{time} of life.



 The \textcolor{green}{King’s} \textcolor{red}{argument} was, that anything that had a head could be

 beheaded, and that you weren’t to \textcolor{green}{talk} \textcolor{red}{nonsense.}



 The Queen’s \textcolor{red}{argument} was, that if something wasn’t done about it in less

 than no \textcolor{blue}{time} \textcolor{red}{she’d} have everybody executed, all round. (It was this last

 remark that had made the whole party look so \textcolor{red}{grave} and \textcolor{BurntOrange}{anxious.)}



 Alice could think of nothing else to say but ‘It belongs to the Duchess:

 you’d better ask HER about it.’



 ‘She’s in \textcolor{red}{prison,’} the Queen said to the \textcolor{red}{executioner:} ‘fetch her here.’

 And the \textcolor{red}{executioner} went off like an arrow.



 The Cat’s head began fading away the moment he was gone, and,

 by the \textcolor{blue}{time} he had come back with the Duchess, it had entirely

 \textcolor{red}{disappeared;} so the \textcolor{green}{King} and the \textcolor{red}{executioner} ran wildly up and down

 looking for it, while the \textcolor{green}{rest} of the party went back to the game.









 CHAPTER IX. The Mock Turtle’s Story



 ‘You can’t think how \textcolor{BurntOrange}{glad} I am to see you again, you \textcolor{green}{dear} old thing!’

 said the Duchess, as she tucked her arm affectionately into Alice’s, and

 they walked off together.



 Alice was very \textcolor{BurntOrange}{glad} to find her in such a \textcolor{BurntOrange}{pleasant} temper, and \textcolor{blue}{thought}

 to herself that perhaps it was only the pepper that had made her so

 \textcolor{red}{savage} when they met in the kitchen.



 ‘When I’M a Duchess,’ she said to herself, (not in a very \textcolor{BurntOrange}{hopeful} tone

 though), ‘I \textcolor{blue}{won’t} have any pepper in my kitchen AT ALL. \textcolor{green}{Soup} does very

 well without--Maybe it’s always pepper that makes people hot-tempered,’

 she went on, very much \textcolor{green}{pleased} at having \textcolor{green}{found} out a new \textcolor{green}{kind} of

 \textcolor{BurntOrange}{rule,} ‘and vinegar that makes them sour--and camomile that makes

 them bitter--and--and barley-sugar and such things that make \textcolor{BurntOrange}{children}

 sweet-tempered. I only wish people knew that: then they wouldn’t be so

 \textcolor{red}{stingy} about it, you know--’



 She had quite \textcolor{red}{forgotten} the Duchess by this \textcolor{blue}{time,} and was a little

 \textcolor{BurntOrange}{startled} when she heard her voice close to her ear. ‘You’re thinking

 about something, my \textcolor{green}{dear,} and that makes you \textcolor{red}{forget} to \textcolor{green}{talk.} I can’t

 tell you just now what the \textcolor{BurntOrange}{moral} of that is, but I shall remember it in

 a bit.’



 ‘Perhaps it hasn’t one,’ Alice ventured to remark.



 ‘Tut, tut, \textcolor{BurntOrange}{child!’} said the Duchess. ‘Everything’s got a \textcolor{BurntOrange}{moral,} if only

 you can find it.’ And she squeezed herself up closer to Alice’s side as

 she \textcolor{red}{spoke.}



 Alice did not much like keeping so close to her: first, because the

 Duchess was VERY \textcolor{red}{ugly;} and secondly, because she was exactly the

 right height to \textcolor{green}{rest} her chin upon Alice’s \textcolor{green}{shoulder,} and it was an

 uncomfortably sharp chin. However, she did not like to be rude, so she

 \textcolor{red}{bore} it as well as she could.



 ‘The game’s going on rather better now,’ she said, by way of keeping up

 the conversation a little.



 ‘’Tis so,’ said the Duchess: ‘and the \textcolor{BurntOrange}{moral} of that is--“Oh, ‘tis \textcolor{green}{love,}

 ‘tis \textcolor{green}{love,} that makes the world go round!”’



 ‘Somebody said,’ Alice whispered, ‘that it’s done by everybody minding

 their own business!’



 ‘Ah, well! It means much the same thing,’ said the Duchess, digging her

 sharp little chin into Alice’s \textcolor{green}{shoulder} as she added, ‘and the \textcolor{BurntOrange}{moral}

 of THAT is--“Take care of the \textcolor{green}{sense,} and the sounds will take care of

 themselves.”’



 ‘How fond she is of finding \textcolor{BurntOrange}{morals} in things!’ Alice \textcolor{blue}{thought} to herself.



 ‘I \textcolor{BurntOrange}{dare} say you’re wondering why I don’t put my arm round your waist,’

 the Duchess said after a pause: ‘the \textcolor{green}{reason} is, that I’m \textcolor{red}{doubtful} about

 the temper of your flamingo. Shall I try the \textcolor{blue}{experiment?’}



 ‘HE might \textcolor{red}{bite,’} Alice \textcolor{BurntOrange}{cautiously} replied, not feeling at all \textcolor{BurntOrange}{anxious} to

 have the \textcolor{blue}{experiment} tried.



 ‘Very \textcolor{green}{true,’} said the Duchess: ‘flamingoes and mustard both \textcolor{red}{bite.} And

 the \textcolor{BurntOrange}{moral} of that is--“Birds of a feather flock together.”’



 ‘Only mustard isn’t a bird,’ Alice remarked.



 ‘Right, as \textcolor{green}{usual,’} said the Duchess: ‘what a clear way you have of

 putting things!’



 ‘It’s a mineral, I THINK,’ said Alice.



 ‘Of course it is,’ said the Duchess, who seemed \textcolor{blue}{ready} to \textcolor{green}{agree} to

 everything that Alice said; ‘there’s a large mustard-mine near here. And

 the \textcolor{BurntOrange}{moral} of that is--“The more there is of mine, the less there is of

 yours.”’



 ‘Oh, I know!’ \textcolor{blue}{exclaimed} Alice, who had not attended to this last remark,

 ‘it’s a vegetable. It doesn’t look like one, but it is.’



 ‘I quite \textcolor{green}{agree} with you,’ said the Duchess; ‘and the \textcolor{BurntOrange}{moral} of that

 is--“Be what you would seem to be”--or if you’d like it put more

 simply--“Never imagine yourself not to be otherwise than what it might

 appear to others that what you were or might have been was not otherwise

 than what you had been would have appeared to them to be otherwise.”’



 ‘I think I should understand that better,’ Alice said very politely, ‘if

 I had it written down: but I can’t quite follow it as you say it.’



 ‘That’s nothing to what I could say if I chose,’ the Duchess replied, in

 a \textcolor{green}{pleased} tone.



 \textcolor{BurntOrange}{‘Pray} don’t trouble yourself to say it any longer than that,’ said

 Alice.



 ‘Oh, don’t \textcolor{green}{talk} about trouble!’ said the Duchess. ‘I make you a \textcolor{BurntOrange}{present}

 of everything I’ve said as yet.’



 ‘A \textcolor{red}{cheap} sort of \textcolor{BurntOrange}{present!’} \textcolor{blue}{thought} Alice. ‘I’m \textcolor{BurntOrange}{glad} they don’t give

 \textcolor{BurntOrange}{birthday} \textcolor{BurntOrange}{presents} like that!’ But she did not venture to say it out

 loud.



 ‘Thinking again?’ the Duchess asked, with another dig of her sharp

 little chin.



 ‘I’ve a right to think,’ said Alice sharply, for she was beginning to

 feel a little \textcolor{red}{worried.}



 ‘Just about as much right,’ said the Duchess, ‘as \textcolor{red}{pigs} have to fly; and

 the m--’



 But here, to Alice’s great \textcolor{BurntOrange}{surprise,} the Duchess’s voice \textcolor{red}{died} away, even

 in the middle of her favourite \textcolor{green}{word} \textcolor{BurntOrange}{‘moral,’} and the arm that was linked

 into hers began to tremble. Alice looked up, and there stood the Queen

 in front of them, with her arms folded, \textcolor{red}{frowning} like a thunderstorm.



 ‘A fine day, your \textcolor{green}{Majesty!’} the Duchess began in a low, weak voice.



 ‘Now, I give you \textcolor{green}{fair} \textcolor{BurntOrange}{warning,’} \textcolor{BurntOrange}{shouted} the Queen, stamping on the

 \textcolor{green}{ground} as she \textcolor{red}{spoke;} ‘either you or your head must be off, and that in

 about half no \textcolor{blue}{time!} Take your \textcolor{green}{choice!’}



 The Duchess took her \textcolor{green}{choice,} and was gone in a moment.



 ‘Let’s go on with the game,’ the Queen said to Alice; and Alice was

 too much \textcolor{BurntOrange}{frightened} to say a \textcolor{green}{word,} but slowly followed her back to the

 croquet-ground.



 The other guests had taken \textcolor{green}{advantage} of the Queen’s \textcolor{red}{absence,} and were

 \textcolor{green}{resting} in the shade: however, the moment they saw her, they \textcolor{blue}{hurried}

 back to the game, the Queen merely remarking that a moment’s \textcolor{red}{delay} would

 cost them their lives.



 All the \textcolor{blue}{time} they were playing the Queen never left off \textcolor{red}{quarrelling} with

 the other \textcolor{red}{players,} and \textcolor{BurntOrange}{shouting} ‘Off with his head!’ or ‘Off with her

 head!’ Those whom she \textcolor{BurntOrange}{sentenced} were taken into \textcolor{green}{custody} by the \textcolor{BurntOrange}{soldiers,}

 who of course had to \textcolor{BurntOrange}{leave} off being arches to do this, so that by

 the end of half an hour or so there were no arches left, and all the

 \textcolor{red}{players,} except the \textcolor{green}{King,} the Queen, and Alice, were in \textcolor{green}{custody} and

 under \textcolor{BurntOrange}{sentence} of \textcolor{BurntOrange}{execution.}



 Then the Queen left off, quite out of breath, and said to Alice, ‘Have

 you seen the Mock Turtle yet?’



 ‘No,’ said Alice. ‘I don’t even know what a Mock Turtle is.’



 ‘It’s the thing Mock Turtle \textcolor{green}{Soup} is made from,’ said the Queen.



 ‘I never saw one, or heard of one,’ said Alice.



 ‘Come on, then,’ said the Queen, ‘and he shall tell you his history,’



 As they walked off together, Alice heard the \textcolor{green}{King} say in a low voice,

 to the company generally, ‘You are all \textcolor{green}{pardoned.’} ‘Come, THAT’S a \textcolor{BurntOrange}{good}

 thing!’ she said to herself, for she had felt quite \textcolor{red}{unhappy} at the

 number of \textcolor{BurntOrange}{executions} the Queen had ordered.



 They very soon came upon a Gryphon, \textcolor{red}{lying} fast asleep in the \textcolor{BurntOrange}{sun.}

 (IF you don’t know what a Gryphon is, look at the picture.) ‘Up, \textcolor{red}{lazy}

 thing!’ said the Queen, ‘and take this \textcolor{BurntOrange}{young} lady to see the Mock

 Turtle, and to hear his history. I must go back and see after some

 \textcolor{BurntOrange}{executions} I have ordered’; and she walked off, \textcolor{BurntOrange}{leaving} Alice alone with

 the Gryphon. Alice did not quite like the look of the \textcolor{red}{creature,} but on

 the whole she \textcolor{blue}{thought} it would be quite as \textcolor{green}{safe} to stay with it as to go

 after that \textcolor{red}{savage} Queen: so she \textcolor{BurntOrange}{waited.}



 The Gryphon sat up and rubbed its eyes: then it \textcolor{BurntOrange}{watched} the Queen till

 she was out of sight: then it \textcolor{BurntOrange}{chuckled.} ‘What \textcolor{BurntOrange}{fun!’} said the Gryphon,

 half to itself, half to Alice.



 ‘What IS the \textcolor{BurntOrange}{fun?’} said Alice.



 ‘Why, SHE,’ said the Gryphon. ‘It’s all her \textcolor{BurntOrange}{fancy,} that: they never

 executes nobody, you know. Come on!’



 ‘Everybody says “come on!” here,’ \textcolor{blue}{thought} Alice, as she went slowly

 after it: ‘I never was so ordered about in all my life, never!’



 They had not gone far before they saw the Mock Turtle in the distance,

 sitting sad and \textcolor{red}{lonely} on a little ledge of \textcolor{green}{rock,} and, as they came

 nearer, Alice could hear him sighing as if his heart would \textcolor{blue}{break.} She

 \textcolor{red}{pitied} him deeply. ‘What is his \textcolor{red}{sorrow?’} she asked the Gryphon, and the

 Gryphon answered, very nearly in the same \textcolor{green}{words} as before, ‘It’s all his

 \textcolor{BurntOrange}{fancy,} that: he hasn’t got no \textcolor{red}{sorrow,} you know. Come on!’



 So they went up to the Mock Turtle, who looked at them with large eyes

 \textcolor{green}{full} of tears, but said nothing.



 ‘This here \textcolor{BurntOrange}{young} lady,’ said the Gryphon, ‘she wants for to know your

 history, she do.’



 \textcolor{red}{‘I’ll} tell it her,’ said the Mock Turtle in a deep, \textcolor{red}{hollow} tone: ‘sit

 down, both of you, and don’t speak a \textcolor{green}{word} till I’ve finished.’



 So they sat down, and nobody \textcolor{red}{spoke} for some minutes. Alice \textcolor{blue}{thought} to

 herself, ‘I don’t see how he can EVEN finish, if he doesn’t begin.’ But

 she \textcolor{BurntOrange}{waited} patiently.



 ‘Once,’ said the Mock Turtle at last, with a deep sigh, ‘I was a \textcolor{green}{real}

 Turtle.’



 These \textcolor{green}{words} were followed by a very \textcolor{blue}{long} silence, \textcolor{red}{broken} only by an

 \textcolor{blue}{occasional} exclamation of ‘Hjckrrh!’ from the Gryphon, and the \textcolor{green}{constant}

 heavy \textcolor{red}{sobbing} of the Mock Turtle. Alice was very nearly getting up and

 saying, ‘Thank you, \textcolor{green}{sir,} for your \textcolor{green}{interesting} story,’ but she could

 not help thinking there MUST be more to come, so she sat still and said

 nothing.



 ‘When we were little,’ the Mock Turtle went on at last, more calmly,

 though still \textcolor{red}{sobbing} a little now and then, ‘we went to \textcolor{green}{school} in the

 \textcolor{green}{sea.} The \textcolor{green}{master} was an old Turtle--we used to call him Tortoise--’



 ‘Why did you call him Tortoise, if he wasn’t one?’ Alice asked.



 ‘We called him Tortoise because he \textcolor{green}{taught} us,’ said the Mock Turtle

 angrily: ‘really you are very \textcolor{red}{dull!’}



 ‘You ought to be \textcolor{red}{ashamed} of yourself for asking such a simple \textcolor{green}{question,’}

 added the Gryphon; and then they both sat silent and looked at poor

 Alice, who felt \textcolor{blue}{ready} to sink into the earth. At last the Gryphon said

 to the Mock Turtle, ‘Drive on, old \textcolor{green}{fellow!} Don’t be all day about it!’

 and he went on in these \textcolor{green}{words:}



 ‘Yes, we went to \textcolor{green}{school} in the \textcolor{green}{sea,} though you mayn’t believe it--’



 ‘I never said I didn’t!’ \textcolor{BurntOrange}{interrupted} Alice.



 ‘You did,’ said the Mock Turtle.



 ‘Hold your tongue!’ added the Gryphon, before Alice could speak again.

 The Mock Turtle went on.



 ‘We had the best of educations--in \textcolor{green}{fact,} we went to \textcolor{green}{school} every day--’



 ‘I’VE been to a day-school, too,’ said Alice; ‘you needn’t be so \textcolor{BurntOrange}{proud}

 as all that.’



 ‘With \textcolor{green}{extras?’} asked the Mock Turtle a little anxiously.



 ‘Yes,’ said Alice, ‘we \textcolor{green}{learned} French and \textcolor{BurntOrange}{music.’}



 ‘And washing?’ said the Mock Turtle.



 ‘Certainly not!’ said Alice indignantly.



 ‘Ah! then yours wasn’t a really \textcolor{BurntOrange}{good} \textcolor{green}{school,’} said the Mock Turtle in

 a tone of great \textcolor{green}{relief.} ‘Now at OURS they had at the end of the bill,

 “French, \textcolor{BurntOrange}{music,} AND WASHING--extra.”’



 ‘You couldn’t have wanted it much,’ said Alice; ‘living at the \textcolor{red}{bottom} of

 the \textcolor{green}{sea.’}



 ‘I couldn’t \textcolor{green}{afford} to \textcolor{green}{learn} it.’ said the Mock Turtle with a sigh. ‘I

 only took the regular course.’



 ‘What was that?’ inquired Alice.



 ‘Reeling and Writhing, of course, to begin with,’ the Mock Turtle

 replied; ‘and then the different branches of Arithmetic--Ambition,

 \textcolor{red}{Distraction,} Uglification, and \textcolor{red}{Derision.’}



 ‘I never heard of “Uglification,”’ Alice ventured to say. ‘What is it?’



 The Gryphon lifted up both its paws in \textcolor{BurntOrange}{surprise.} ‘What! Never heard of

 uglifying!’ it \textcolor{blue}{exclaimed.} ‘You know what to \textcolor{green}{beautify} is, I suppose?’



 ‘Yes,’ said Alice doubtfully: ‘it means--to--make--anything--prettier.’



 ‘Well, then,’ the Gryphon went on, ‘if you don’t know what to uglify is,

 you ARE a simpleton.’



 Alice did not feel \textcolor{green}{encouraged} to ask any more \textcolor{green}{questions} about it, so she

 turned to the Mock Turtle, and said ‘What else had you to \textcolor{green}{learn?’}



 ‘Well, there was \textcolor{blue}{Mystery,’} the Mock Turtle replied, counting off

 the \textcolor{red}{subjects} on his flappers, \textcolor{blue}{‘--Mystery,} \textcolor{red}{ancient} and modern, with

 Seaography: then Drawling--the Drawling-master was an old conger-eel,

 that used to come once a week: HE \textcolor{green}{taught} us Drawling, Stretching, and

 \textcolor{BurntOrange}{Fainting} in Coils.’



 ‘What was THAT like?’ said Alice.



 ‘Well, I can’t \textcolor{green}{show} it you myself,’ the Mock Turtle said: ‘I’m too

 \textcolor{red}{stiff.} And the Gryphon never learnt it.’



 ‘Hadn’t \textcolor{blue}{time,’} said the Gryphon: ‘I went to the \textcolor{green}{Classics} \textcolor{green}{master,} though.

 He was an old crab, HE was.’



 ‘I never went to him,’ the Mock Turtle said with a sigh: ‘he \textcolor{green}{taught}

 \textcolor{BurntOrange}{Laughing} and \textcolor{red}{Grief,} they used to say.’



 ‘So he did, so he did,’ said the Gryphon, sighing in his turn; and both

 \textcolor{red}{creatures} hid their faces in their paws.



 ‘And how many hours a day did you do \textcolor{BurntOrange}{lessons?’} said Alice, in a \textcolor{blue}{hurry} to

 \textcolor{red}{change} the \textcolor{red}{subject.}



 ‘Ten hours the first day,’ said the Mock Turtle: ‘nine the next, and so

 on.’



 ‘What a curious \textcolor{blue}{plan!’} \textcolor{blue}{exclaimed} Alice.



 ‘That’s the \textcolor{green}{reason} they’re called \textcolor{BurntOrange}{lessons,’} the Gryphon remarked:

 ‘because they \textcolor{BurntOrange}{lessen} from day to day.’



 This was quite a new idea to Alice, and she \textcolor{blue}{thought} it over a little

 before she made her next remark. ‘Then the eleventh day must have been a

 \textcolor{BurntOrange}{holiday?’}



 ‘Of course it was,’ said the Mock Turtle.



 ‘And how did you \textcolor{green}{manage} on the twelfth?’ Alice went on eagerly.



 ‘That’s enough about \textcolor{BurntOrange}{lessons,’} the Gryphon \textcolor{BurntOrange}{interrupted} in a very decided

 tone: ‘tell her something about the games now.’









 CHAPTER X. The Lobster Quadrille



 The Mock Turtle sighed deeply, and drew the back of one flapper across

 his eyes. He looked at Alice, and tried to speak, but for a minute or

 two \textcolor{red}{sobs} choked his voice. ‘Same as if he had a bone in his throat,’

 said the Gryphon: and it set to work shaking him and \textcolor{BurntOrange}{punching} him in

 the back. At last the Mock Turtle recovered his voice, and, with tears

 running down his cheeks, he went on again:--



 ‘You may not have lived much under the \textcolor{green}{sea--’} [‘I haven’t,’ said

 Alice)--‘and perhaps you were never even introduced to a lobster--’

 (Alice began to say ‘I once tasted--’ but checked herself hastily, and

 said ‘No, never’) ‘--so you can have no idea what a \textcolor{BurntOrange}{delightful} thing a

 Lobster Quadrille is!’



 ‘No, indeed,’ said Alice. ‘What sort of a \textcolor{green}{dance} is it?’



 ‘Why,’ said the Gryphon, ‘you first form into a line along the

 sea-shore--’



 ‘Two lines!’ \textcolor{red}{cried} the Mock Turtle. \textcolor{green}{‘Seals,} turtles, salmon, and so on;

 then, when you’ve cleared all the jelly-fish out of the way--’



 ‘THAT generally takes some \textcolor{blue}{time,’} \textcolor{BurntOrange}{interrupted} the Gryphon.



 ‘--you \textcolor{BurntOrange}{advance} twice--’



 ‘Each with a lobster as a \textcolor{green}{partner!’} \textcolor{red}{cried} the Gryphon.



 ‘Of course,’ the Mock Turtle said: \textcolor{BurntOrange}{‘advance} twice, set to \textcolor{green}{partners--’}



 \textcolor{red}{‘--change} lobsters, and retire in same order,’ continued the Gryphon.



 ‘Then, you know,’ the Mock Turtle went on, ‘you throw the--’



 ‘The lobsters!’ \textcolor{BurntOrange}{shouted} the Gryphon, with a \textcolor{red}{bound} into the air.



 ‘--as far out to \textcolor{green}{sea} as you can--’



 \textcolor{BurntOrange}{‘Swim} after them!’ \textcolor{BurntOrange}{screamed} the Gryphon.



 ‘Turn a somersault in the \textcolor{green}{sea!’} \textcolor{red}{cried} the Mock Turtle, capering wildly

 about.



 \textcolor{red}{‘Change} lobsters again!’ \textcolor{BurntOrange}{yelled} the Gryphon at the \textcolor{BurntOrange}{top} of its voice.



 ‘Back to \textcolor{green}{land} again, and that’s all the first figure,’ said the Mock

 Turtle, \textcolor{blue}{suddenly} dropping his voice; and the two \textcolor{red}{creatures,} who had been

 jumping about like \textcolor{red}{mad} things all this \textcolor{blue}{time,} sat down again very \textcolor{red}{sadly}

 and quietly, and looked at Alice.



 ‘It must be a very \textcolor{BurntOrange}{pretty} \textcolor{green}{dance,’} said Alice timidly.



 ‘Would you like to see a little of it?’ said the Mock Turtle.



 ‘Very much indeed,’ said Alice.



 ‘Come, let’s try the first figure!’ said the Mock Turtle to the Gryphon.

 ‘We can do without lobsters, you know. Which shall \textcolor{BurntOrange}{sing?’}



 ‘Oh, YOU \textcolor{BurntOrange}{sing,’} said the Gryphon. ‘I’ve \textcolor{red}{forgotten} the \textcolor{green}{words.’}



 So they began solemnly \textcolor{green}{dancing} round and round Alice, every now and

 then treading on her toes when they passed too close, and waving their

 forepaws to mark the \textcolor{blue}{time,} while the Mock Turtle sang this, very slowly

 and \textcolor{red}{sadly:--}



 ‘“Will you walk a little faster?” said a \textcolor{BurntOrange}{whiting} to a snail.

 “There’s a porpoise close behind us, and he’s treading on my tail.



 See how eagerly the lobsters and the turtles all \textcolor{BurntOrange}{advance!}

 They are \textcolor{BurntOrange}{waiting} on the shingle--will you come and \textcolor{green}{join} the \textcolor{green}{dance?}



 Will you, \textcolor{blue}{won’t} you, will you, \textcolor{blue}{won’t} you, will you \textcolor{green}{join} the \textcolor{green}{dance?}

 Will you, \textcolor{blue}{won’t} you, will you, \textcolor{blue}{won’t} you, \textcolor{blue}{won’t} you \textcolor{green}{join} the \textcolor{green}{dance?}



 “You can really have no \textcolor{green}{notion} how \textcolor{BurntOrange}{delightful} it will be

 When they take us up and throw us, with the lobsters, out to \textcolor{green}{sea!”}

 But the snail replied “Too far, too far!” and gave a look askance--

 Said he thanked the \textcolor{BurntOrange}{whiting} kindly, but he would not \textcolor{green}{join} the \textcolor{green}{dance.}



 Would not, could not, would not, could not, would not \textcolor{green}{join} the \textcolor{green}{dance.}

 Would not, could not, would not, could not, could not \textcolor{green}{join} the \textcolor{green}{dance.}



 ‘“What matters it how far we go?” his \textcolor{red}{scaly} \textcolor{green}{friend} replied.

 “There is another shore, you know, upon the other side.

 The further off from England the nearer is to France--

 Then turn not pale, beloved snail, but come and \textcolor{green}{join} the \textcolor{green}{dance.}



 Will you, \textcolor{blue}{won’t} you, will you, \textcolor{blue}{won’t} you, will you \textcolor{green}{join} the \textcolor{green}{dance?}

 Will you, \textcolor{blue}{won’t} you, will you, \textcolor{blue}{won’t} you, \textcolor{blue}{won’t} you \textcolor{green}{join} the \textcolor{green}{dance?”’}



 ‘Thank you, it’s a very \textcolor{green}{interesting} \textcolor{green}{dance} to \textcolor{BurntOrange}{watch,’} said Alice, feeling

 very \textcolor{BurntOrange}{glad} that it was over at last: ‘and I do so like that curious song

 about the \textcolor{BurntOrange}{whiting!’}



 ‘Oh, as to the \textcolor{BurntOrange}{whiting,’} said the Mock Turtle, ‘they--you’ve seen them,

 of course?’



 ‘Yes,’ said Alice, ‘I’ve often seen them at dinn--’ she checked herself

 hastily.



 ‘I don’t know where Dinn may be,’ said the Mock Turtle, ‘but if you’ve

 seen them so often, of course you know what they’re like.’



 ‘I believe so,’ Alice replied thoughtfully. ‘They have their tails in

 their mouths--and they’re all over crumbs.’



 ‘You’re \textcolor{red}{wrong} about the crumbs,’ said the Mock Turtle: ‘crumbs would all

 wash off in the \textcolor{green}{sea.} But they HAVE their tails in their \textcolor{blue}{mouths;} and the

 \textcolor{green}{reason} is--’ here the Mock Turtle \textcolor{red}{yawned} and shut his eyes.--‘Tell her

 about the \textcolor{green}{reason} and all that,’ he said to the Gryphon.



 ‘The \textcolor{green}{reason} is,’ said the Gryphon, ‘that they WOULD go with the lobsters

 to the \textcolor{green}{dance.} So they got thrown out to \textcolor{green}{sea.} So they had to \textcolor{red}{fall} a \textcolor{blue}{long}

 way. So they got their tails fast in their \textcolor{blue}{mouths.} So they couldn’t get

 them out again. That’s all.’



 ‘Thank you,’ said Alice, ‘it’s very \textcolor{green}{interesting.} I never knew so much

 about a \textcolor{BurntOrange}{whiting} before.’



 ‘I can tell you more than that, if you like,’ said the Gryphon. ‘Do you

 know why it’s called a \textcolor{BurntOrange}{whiting?’}



 ‘I never \textcolor{blue}{thought} about it,’ said Alice. ‘Why?’



 ‘IT DOES THE BOOTS AND SHOES.’ the Gryphon replied very solemnly.



 Alice was thoroughly puzzled. ‘Does the boots and shoes!’ she repeated

 in a wondering tone.



 ‘Why, what are YOUR shoes done with?’ said the Gryphon. ‘I mean, what

 makes them so shiny?’



 Alice looked down at them, and considered a little before she gave her

 answer. ‘They’re done with blacking, I believe.’



 ‘Boots and shoes under the \textcolor{green}{sea,’} the Gryphon went on in a deep voice,

 ‘are done with a \textcolor{BurntOrange}{whiting.} Now you know.’



 ‘And what are they made of?’ Alice asked in a tone of great \textcolor{BurntOrange}{curiosity.}



 ‘Soles and \textcolor{red}{eels,} of course,’ the Gryphon replied rather impatiently:

 ‘any shrimp could have told you that.’



 ‘If I’d been the \textcolor{BurntOrange}{whiting,’} said Alice, whose \textcolor{blue}{thoughts} were still running

 on the song, ‘I’d have said to the porpoise, “Keep back, please: we

 don’t want YOU with us!”’



 ‘They were \textcolor{BurntOrange}{obliged} to have him with them,’ the Mock Turtle said: ‘no

 \textcolor{green}{wise} fish would go anywhere without a porpoise.’



 ‘Wouldn’t it really?’ said Alice in a tone of great \textcolor{BurntOrange}{surprise.}



 ‘Of course not,’ said the Mock Turtle: ‘why, if a fish came to ME, and

 told me he was going a \textcolor{BurntOrange}{journey,} I should say “With what porpoise?”’



 ‘Don’t you mean “purpose”?’ said Alice.



 ‘I mean what I say,’ the Mock Turtle replied in an \textcolor{red}{offended} tone. And

 the Gryphon added ‘Come, let’s hear some of YOUR \textcolor{BurntOrange}{adventures.’}



 ‘I could tell you my adventures--beginning from this morning,’ said

 Alice a little timidly: ‘but it’s no use going back to yesterday,

 because I was a different person then.’



 \textcolor{green}{‘Explain} all that,’ said the Mock Turtle.



 ‘No, no! The \textcolor{BurntOrange}{adventures} first,’ said the Gryphon in an \textcolor{BurntOrange}{impatient} tone:

 ‘explanations take such a \textcolor{BurntOrange}{dreadful} \textcolor{blue}{time.’}



 So Alice began telling them her \textcolor{BurntOrange}{adventures} from the \textcolor{blue}{time} when she first

 saw the \textcolor{BurntOrange}{White} Rabbit. She was a little \textcolor{BurntOrange}{nervous} about it just at first,

 the two \textcolor{red}{creatures} got so close to her, one on each side, and opened

 their eyes and \textcolor{blue}{mouths} so VERY wide, but she \textcolor{BurntOrange}{gained} \textcolor{green}{courage} as she went

 on. Her listeners were perfectly \textcolor{BurntOrange}{quiet} till she got to the part about

 her repeating ‘YOU ARE OLD, \textcolor{green}{FATHER} WILLIAM,’ to the Caterpillar, and the

 \textcolor{green}{words} all coming different, and then the Mock Turtle drew a \textcolor{blue}{long} breath,

 and said ‘That’s very curious.’



 ‘It’s all about as curious as it can be,’ said the Gryphon.



 ‘It all came different!’ the Mock Turtle repeated thoughtfully. ‘I

 should like to hear her try and repeat something now. Tell her to

 begin.’ He looked at the Gryphon as if he \textcolor{blue}{thought} it had some \textcolor{green}{kind} of

 \textcolor{green}{authority} over Alice.



 ‘Stand up and repeat “‘TIS THE VOICE OF THE SLUGGARD,”’ said the

 Gryphon.



 ‘How the \textcolor{red}{creatures} order one about, and make one repeat \textcolor{BurntOrange}{lessons!’}

 \textcolor{blue}{thought} Alice; ‘I might as well be at \textcolor{green}{school} at once.’ However, she

 got up, and began to repeat it, but her head was so \textcolor{green}{full} of the Lobster

 Quadrille, that she hardly knew what she was saying, and the \textcolor{green}{words} came

 very queer indeed:--



 ‘’Tis the voice of the Lobster; I heard him declare,

 “You have baked me too brown, I must \textcolor{green}{sugar} my hair.”

 As a duck with its eyelids, so he with his \textcolor{red}{nose}

 Trims his \textcolor{red}{belt} and his buttons, and turns out his toes.’



 [later \textcolor{blue}{editions} continued as follows

 When the sands are all dry, he is gay as a lark,

 And will \textcolor{green}{talk} in \textcolor{red}{contemptuous} tones of the \textcolor{red}{Shark,}

 But, when the tide rises and \textcolor{red}{sharks} are around,

 His voice has a \textcolor{red}{timid} and tremulous sound.]



 ‘That’s different from what I used to say when I was a \textcolor{BurntOrange}{child,’} said the

 Gryphon.



 ‘Well, I never heard it before,’ said the Mock Turtle; ‘but it sounds

 uncommon \textcolor{red}{nonsense.’}



 Alice said nothing; she had sat down with her face in her hands,

 wondering if anything would EVER \textcolor{blue}{happen} in a natural way again.



 ‘I should like to have it \textcolor{green}{explained,’} said the Mock Turtle.



 ‘She can’t \textcolor{green}{explain} it,’ said the Gryphon hastily. ‘Go on with the next

 verse.’



 ‘But about his toes?’ the Mock Turtle persisted. ‘How COULD he turn them

 out with his \textcolor{red}{nose,} you know?’



 ‘It’s the first position in \textcolor{green}{dancing.’} Alice said; but was \textcolor{BurntOrange}{dreadfully}

 puzzled by the whole thing, and \textcolor{blue}{longed} to \textcolor{red}{change} the \textcolor{red}{subject.}



 ‘Go on with the next verse,’ the Gryphon repeated impatiently: ‘it

 begins “I passed by his \textcolor{green}{garden.”’}



 Alice did not \textcolor{BurntOrange}{dare} to \textcolor{red}{disobey,} though she felt sure it would all come

 \textcolor{red}{wrong,} and she went on in a trembling voice:--



 ‘I passed by his \textcolor{green}{garden,} and \textcolor{green}{marked,} with one eye,

 How the Owl and the Panther were \textcolor{BurntOrange}{sharing} a pie--’



 [later \textcolor{blue}{editions} continued as follows

 The Panther took pie-crust, and gravy, and meat,

 While the Owl had the dish as its \textcolor{BurntOrange}{share} of the \textcolor{BurntOrange}{treat.}

 When the pie was all finished, the Owl, as a \textcolor{green}{boon,}

 Was kindly permitted to pocket the spoon:

 While the Panther received knife and fork with a \textcolor{red}{growl,}

 And concluded the \textcolor{BurntOrange}{banquet--]}



 ‘What IS the use of repeating all that stuff,’ the Mock Turtle

 \textcolor{BurntOrange}{interrupted,} ‘if you don’t \textcolor{green}{explain} it as you go on? It’s by far the most

 \textcolor{red}{confusing} thing I ever heard!’



 ‘Yes, I think you’d better \textcolor{BurntOrange}{leave} off,’ said the Gryphon: and Alice was

 only too \textcolor{BurntOrange}{glad} to do so.



 ‘Shall we try another figure of the Lobster Quadrille?’ the Gryphon went

 on. ‘Or would you like the Mock Turtle to \textcolor{BurntOrange}{sing} you a song?’



 ‘Oh, a song, please, if the Mock Turtle would be so \textcolor{green}{kind,’} Alice

 replied, so eagerly that the Gryphon said, in a rather \textcolor{red}{offended} tone,

 ‘Hm! No accounting for tastes! \textcolor{BurntOrange}{Sing} her “Turtle \textcolor{green}{Soup,”} will you, old

 \textcolor{green}{fellow?’}



 The Mock Turtle sighed deeply, and began, in a voice sometimes choked

 with \textcolor{red}{sobs,} to \textcolor{BurntOrange}{sing} this:--



 \textcolor{green}{‘Beautiful} \textcolor{green}{Soup,} so rich and \textcolor{green}{green,}

 \textcolor{BurntOrange}{Waiting} in a \textcolor{red}{hot} tureen!

 Who for such dainties would not stoop?

 \textcolor{green}{Soup} of the evening, \textcolor{green}{beautiful} \textcolor{green}{Soup!}

 \textcolor{green}{Soup} of the evening, \textcolor{green}{beautiful} \textcolor{green}{Soup!}

 Beau--ootiful Soo--oop!

 Beau--ootiful Soo--oop!

 Soo--oop of the e--e--evening,

 \textcolor{green}{Beautiful,} \textcolor{green}{beautiful} \textcolor{green}{Soup!}



 \textcolor{green}{‘Beautiful} \textcolor{green}{Soup!} Who cares for fish,

 Game, or any other dish?

 Who would not give all else for two

 Pennyworth only of \textcolor{green}{beautiful} \textcolor{green}{Soup?}

 Pennyworth only of \textcolor{green}{beautiful} \textcolor{green}{Soup?}

 Beau--ootiful Soo--oop!

 Beau--ootiful Soo--oop!

 Soo--oop of the e--e--evening,

 \textcolor{green}{Beautiful,} \textcolor{green}{beauti--FUL} \textcolor{green}{SOUP!’}



 \textcolor{green}{‘Chorus} again!’ \textcolor{red}{cried} the Gryphon, and the Mock Turtle had just begun

 to repeat it, when a \textcolor{red}{cry} of ‘The trial’s beginning!’ was heard in the

 distance.



 ‘Come on!’ \textcolor{red}{cried} the Gryphon, and, taking Alice by the hand, it \textcolor{blue}{hurried}

 off, without \textcolor{BurntOrange}{waiting} for the end of the song.



 ‘What trial is it?’ Alice panted as she ran; but the Gryphon only

 answered ‘Come on!’ and ran the faster, while more and more faintly

 came, carried on the breeze that followed them, the \textcolor{red}{melancholy} \textcolor{green}{words:--}



 ‘Soo--oop of the e--e--evening,

 \textcolor{green}{Beautiful,} \textcolor{green}{beautiful} \textcolor{green}{Soup!’}









 CHAPTER XI. Who Stole the Tarts?



 The \textcolor{green}{King} and Queen of Hearts were seated on their \textcolor{green}{throne} when they

 \textcolor{blue}{arrived,} with a great crowd assembled about them--all sorts of little

 birds and \textcolor{red}{beasts,} as well as the whole pack of cards: the Knave was

 standing before them, in chains, with a \textcolor{BurntOrange}{soldier} on each side to \textcolor{BurntOrange}{guard}

 him; and near the \textcolor{green}{King} was the \textcolor{BurntOrange}{White} Rabbit, with a \textcolor{red}{trumpet} in one hand,

 and a scroll of parchment in the other. In the very middle of the \textcolor{BurntOrange}{court}

 was a table, with a large dish of tarts upon it: they looked so \textcolor{BurntOrange}{good,}

 that it made Alice quite \textcolor{BurntOrange}{hungry} to look at them--‘I wish they’d get the

 trial done,’ she \textcolor{blue}{thought,} ‘and hand round the refreshments!’ But there

 seemed to be no \textcolor{blue}{chance} of this, so she began looking at everything about

 her, to pass away the \textcolor{blue}{time.}



 Alice had never been in a \textcolor{BurntOrange}{court} of \textcolor{green}{justice} before, but she had read

 about them in books, and she was quite \textcolor{green}{pleased} to find that she knew

 the name of nearly everything there. ‘That’s the judge,’ she said to

 herself, ‘because of his great wig.’



 The judge, by the way, was the \textcolor{green}{King;} and as he wore his crown over the

 wig, (look at the frontispiece if you want to see how he did it,) he did

 not look at all comfortable, and it was certainly not becoming.



 ‘And that’s the jury-box,’ \textcolor{blue}{thought} Alice, ‘and those twelve \textcolor{red}{creatures,’}

 (she was \textcolor{BurntOrange}{obliged} to say \textcolor{red}{‘creatures,’} you see, because some of them were

 animals, and some were birds,) ‘I suppose they are the jurors.’ She said

 this last \textcolor{green}{word} two or three \textcolor{blue}{times} over to herself, being rather \textcolor{BurntOrange}{proud} of

 it: for she \textcolor{blue}{thought,} and \textcolor{green}{rightly} too, that very few little girls of her

 age knew the meaning of it at all. However, ‘jury-men’ would have done

 just as well.



 The twelve jurors were all writing very busily on \textcolor{green}{slates.} ‘What are they

 doing?’ Alice whispered to the Gryphon. ‘They can’t have anything to put

 down yet, before the trial’s begun.’



 ‘They’re putting down their names,’ the Gryphon whispered in reply, ‘for

 \textcolor{red}{fear} they should \textcolor{red}{forget} them before the end of the trial.’



 \textcolor{red}{‘Stupid} things!’ Alice began in a loud, \textcolor{red}{indignant} voice, but she stopped

 hastily, for the \textcolor{BurntOrange}{White} Rabbit \textcolor{red}{cried} out, ‘Silence in the \textcolor{BurntOrange}{court!’} and the

 \textcolor{green}{King} put on his \textcolor{BurntOrange}{spectacles} and looked anxiously round, to make out who

 was \textcolor{green}{talking.}



 Alice could see, as well as if she were looking over their \textcolor{green}{shoulders,}

 that all the jurors were writing down \textcolor{red}{‘stupid} things!’ on their \textcolor{green}{slates,}

 and she could even make out that one of them didn’t know how to spell

 \textcolor{red}{‘stupid,’} and that he had to ask his neighbour to tell him. ‘A nice

 \textcolor{red}{muddle} their slates’ll be in before the trial’s over!’ \textcolor{blue}{thought} Alice.



 One of the jurors had a pencil that squeaked. This of course, Alice

 could not stand, and she went round the \textcolor{BurntOrange}{court} and got behind him, and

 very soon \textcolor{green}{found} an \textcolor{BurntOrange}{opportunity} of taking it away. She did it so quickly

 that the poor little juror (it was Bill, the Lizard) could not make out

 at all what had become of it; so, after hunting all about for it, he was

 \textcolor{BurntOrange}{obliged} to write with one finger for the \textcolor{green}{rest} of the day; and this was

 of very little use, as it left no mark on the \textcolor{green}{slate.}



 ‘Herald, read the \textcolor{red}{accusation!’} said the \textcolor{green}{King.}



 On this the \textcolor{BurntOrange}{White} Rabbit blew three \textcolor{BurntOrange}{blasts} on the \textcolor{red}{trumpet,} and then

 unrolled the parchment scroll, and read as follows:--



 ‘The Queen of Hearts, she made some tarts,

 All on a summer day:

 The Knave of Hearts, he stole those tarts,

 And took them quite away!’



 ‘Consider your \textcolor{red}{verdict,’} the \textcolor{green}{King} said to the \textcolor{green}{jury.}



 ‘Not yet, not yet!’ the Rabbit hastily \textcolor{BurntOrange}{interrupted.} ‘There’s a great

 \textcolor{BurntOrange}{deal} to come before that!’



 ‘Call the first \textcolor{green}{witness,’} said the \textcolor{green}{King;} and the \textcolor{BurntOrange}{White} Rabbit blew three

 \textcolor{BurntOrange}{blasts} on the \textcolor{red}{trumpet,} and called out, ‘First \textcolor{green}{witness!’}



 The first \textcolor{green}{witness} was the Hatter. He came in with a teacup in one

 hand and a piece of bread-and-butter in the other. ‘I \textcolor{red}{beg} \textcolor{green}{pardon,} your

 \textcolor{green}{Majesty,’} he began, ‘for bringing these in: but I hadn’t quite finished

 my tea when I was sent for.’



 ‘You ought to have finished,’ said the \textcolor{green}{King.} ‘When did you begin?’



 The Hatter looked at the \textcolor{green}{March} Hare, who had followed him into the

 \textcolor{BurntOrange}{court,} arm-in-arm with the Dormouse. ‘Fourteenth of \textcolor{green}{March,} I think it

 was,’ he said.



 ‘Fifteenth,’ said the \textcolor{green}{March} Hare.



 ‘Sixteenth,’ added the Dormouse.



 ‘Write that down,’ the \textcolor{green}{King} said to the \textcolor{green}{jury,} and the \textcolor{green}{jury} eagerly

 wrote down all three dates on their \textcolor{green}{slates,} and then added them up, and

 reduced the answer to shillings and pence.



 ‘Take off your hat,’ the \textcolor{green}{King} said to the Hatter.



 ‘It isn’t mine,’ said the Hatter.



 \textcolor{red}{‘Stolen!’} the \textcolor{green}{King} \textcolor{blue}{exclaimed,} turning to the \textcolor{green}{jury,} who instantly made a

 memorandum of the \textcolor{green}{fact.}



 ‘I keep them to sell,’ the Hatter added as an explanation; ‘I’ve none of

 my own. I’m a hatter.’



 Here the Queen put on her \textcolor{BurntOrange}{spectacles,} and began \textcolor{BurntOrange}{staring} at the Hatter,

 who turned pale and fidgeted.



 ‘Give your evidence,’ said the \textcolor{green}{King;} ‘and don’t be \textcolor{BurntOrange}{nervous,} or \textcolor{red}{I’ll} have

 you executed on the spot.’



 This did not seem to \textcolor{green}{encourage} the \textcolor{green}{witness} at all: he kept shifting

 from one foot to the other, looking uneasily at the Queen, and in

 his \textcolor{red}{confusion} he bit a large piece out of his teacup instead of the

 bread-and-butter.



 Just at this moment Alice felt a very curious sensation, which puzzled

 her a \textcolor{BurntOrange}{good} \textcolor{BurntOrange}{deal} until she made out what it was: she was beginning to

 \textcolor{BurntOrange}{grow} larger again, and she \textcolor{blue}{thought} at first she would get up and \textcolor{BurntOrange}{leave}

 the \textcolor{BurntOrange}{court;} but on second \textcolor{blue}{thoughts} she decided to remain where she was as

 \textcolor{blue}{long} as there was room for her.



 ‘I wish you wouldn’t squeeze so.’ said the Dormouse, who was sitting

 next to her. ‘I can hardly breathe.’



 ‘I can’t help it,’ said Alice very meekly: ‘I’m \textcolor{BurntOrange}{growing.’}



 ‘You’ve no right to \textcolor{BurntOrange}{grow} here,’ said the Dormouse.



 ‘Don’t \textcolor{green}{talk} \textcolor{red}{nonsense,’} said Alice more boldly: ‘you know you’re \textcolor{BurntOrange}{growing}

 too.’



 ‘Yes, but I \textcolor{BurntOrange}{grow} at a reasonable pace,’ said the Dormouse: ‘not in that

 \textcolor{red}{ridiculous} fashion.’ And he got up very sulkily and \textcolor{red}{crossed} over to the

 other side of the \textcolor{BurntOrange}{court.}



 All this \textcolor{blue}{time} the Queen had never left off \textcolor{BurntOrange}{staring} at the Hatter, and,

 just as the Dormouse \textcolor{red}{crossed} the \textcolor{BurntOrange}{court,} she said to one of the \textcolor{green}{officers}

 of the \textcolor{BurntOrange}{court,} ‘Bring me the list of the singers in the last concert!’ on

 which the \textcolor{red}{wretched} Hatter trembled so, that he shook both his shoes off.



 ‘Give your evidence,’ the \textcolor{green}{King} repeated angrily, ‘or \textcolor{red}{I’ll} have you

 executed, whether you’re \textcolor{BurntOrange}{nervous} or not.’



 ‘I’m a poor man, your \textcolor{green}{Majesty,’} the Hatter began, in a trembling voice,

 ‘--and I hadn’t begun my tea--not above a week or so--and what with the

 bread-and-butter getting so thin--and the \textcolor{BurntOrange}{twinkling} of the tea--’



 ‘The \textcolor{BurntOrange}{twinkling} of the what?’ said the \textcolor{green}{King.}



 ‘It began with the tea,’ the Hatter replied.



 ‘Of course \textcolor{BurntOrange}{twinkling} begins with a T!’ said the \textcolor{green}{King} sharply. ‘Do you

 take me for a dunce? Go on!’



 ‘I’m a poor man,’ the Hatter went on, ‘and most things \textcolor{BurntOrange}{twinkled} after

 that--only the \textcolor{green}{March} Hare said--’



 ‘I didn’t!’ the \textcolor{green}{March} Hare \textcolor{BurntOrange}{interrupted} in a great \textcolor{blue}{hurry.}



 ‘You did!’ said the Hatter.



 ‘I \textcolor{red}{deny} it!’ said the \textcolor{green}{March} Hare.



 ‘He denies it,’ said the \textcolor{green}{King:} \textcolor{BurntOrange}{‘leave} out that part.’



 ‘Well, at any rate, the Dormouse said--’ the Hatter went on, looking

 anxiously round to see if he would \textcolor{red}{deny} it too: but the Dormouse \textcolor{red}{denied}

 nothing, being fast asleep.



 ‘After that,’ continued the Hatter, ‘I cut some more bread-and-butter--’



 ‘But what did the Dormouse say?’ one of the \textcolor{green}{jury} asked.



 ‘That I can’t remember,’ said the Hatter.



 ‘You MUST remember,’ remarked the \textcolor{green}{King,} ‘or \textcolor{red}{I’ll} have you executed.’



 The \textcolor{red}{miserable} Hatter dropped his teacup and bread-and-butter, and went

 down on one knee. ‘I’m a poor man, your \textcolor{green}{Majesty,’} he began.



 ‘You’re a very poor speaker,’ said the \textcolor{green}{King.}



 Here one of the guinea-pigs \textcolor{BurntOrange}{cheered,} and was \textcolor{BurntOrange}{immediately} \textcolor{red}{suppressed} by

 the \textcolor{green}{officers} of the \textcolor{BurntOrange}{court.} (As that is rather a hard \textcolor{green}{word,} I will just

 \textcolor{green}{explain} to you how it was done. They had a large canvas bag, which tied

 up at the \textcolor{blue}{mouth} with strings: into this they \textcolor{BurntOrange}{slipped} the guinea-pig,

 head first, and then sat upon it.)



 ‘I’m \textcolor{BurntOrange}{glad} I’ve seen that done,’ \textcolor{blue}{thought} Alice. ‘I’ve so often read

 in the newspapers, at the end of trials, “There was some \textcolor{blue}{attempts}

 at \textcolor{BurntOrange}{applause,} which was \textcolor{BurntOrange}{immediately} \textcolor{red}{suppressed} by the \textcolor{green}{officers} of the

 \textcolor{BurntOrange}{court,”} and I never understood what it meant till now.’



 ‘If that’s all you know about it, you may stand down,’ continued the

 \textcolor{green}{King.}



 ‘I can’t go no lower,’ said the Hatter: ‘I’m on the floor, as it is.’



 ‘Then you may SIT down,’ the \textcolor{green}{King} replied.



 Here the other guinea-pig \textcolor{BurntOrange}{cheered,} and was \textcolor{red}{suppressed.}



 ‘Come, that finished the guinea-pigs!’ \textcolor{blue}{thought} Alice. ‘Now we shall get

 on better.’



 ‘I’d rather finish my tea,’ said the Hatter, with an \textcolor{BurntOrange}{anxious} look at the

 Queen, who was \textcolor{green}{reading} the list of singers.



 ‘You may go,’ said the \textcolor{green}{King,} and the Hatter hurriedly left the \textcolor{BurntOrange}{court,}

 without even \textcolor{BurntOrange}{waiting} to put his shoes on.



 ‘--and just take his head off outside,’ the Queen added to one of the

 \textcolor{green}{officers:} but the Hatter was out of sight before the \textcolor{green}{officer} could get

 to the door.



 ‘Call the next \textcolor{green}{witness!’} said the \textcolor{green}{King.}



 The next \textcolor{green}{witness} was the Duchess’s cook. She carried the pepper-box in

 her hand, and Alice \textcolor{blue}{guessed} who it was, even before she got into the

 \textcolor{BurntOrange}{court,} by the way the people near the door began \textcolor{BurntOrange}{sneezing} all at once.



 ‘Give your evidence,’ said the \textcolor{green}{King.}



 ‘Shan’t,’ said the cook.



 The \textcolor{green}{King} looked anxiously at the \textcolor{BurntOrange}{White} Rabbit, who said in a low voice,

 ‘Your \textcolor{green}{Majesty} must cross-examine THIS \textcolor{green}{witness.’}



 ‘Well, if I must, I must,’ the \textcolor{green}{King} said, with a \textcolor{red}{melancholy} air, and,

 after folding his arms and \textcolor{red}{frowning} at the cook till his eyes were

 nearly out of sight, he said in a deep voice, ‘What are tarts made of?’



 ‘Pepper, mostly,’ said the cook.



 ‘Treacle,’ said a sleepy voice behind her.



 ‘Collar that Dormouse,’ the Queen \textcolor{BurntOrange}{shrieked} out. ‘Behead that Dormouse!

 Turn that Dormouse out of \textcolor{BurntOrange}{court!} \textcolor{red}{Suppress} him! Pinch him! Off with his

 whiskers!’



 For some minutes the whole \textcolor{BurntOrange}{court} was in \textcolor{red}{confusion,} getting the Dormouse

 turned out, and, by the \textcolor{blue}{time} they had settled down again, the cook had

 \textcolor{red}{disappeared.}



 ‘Never mind!’ said the \textcolor{green}{King,} with an air of great \textcolor{green}{relief.} ‘Call the next

 \textcolor{green}{witness.’} And he added in an undertone to the Queen, ‘Really, my \textcolor{green}{dear,}

 YOU must cross-examine the next \textcolor{green}{witness.} It quite makes my forehead

 \textcolor{red}{ache!’}



 Alice \textcolor{BurntOrange}{watched} the \textcolor{BurntOrange}{White} Rabbit as he \textcolor{red}{fumbled} over the list, feeling very

 curious to see what the next \textcolor{green}{witness} would be like, ‘--for they haven’t

 got much evidence YET,’ she said to herself. Imagine her \textcolor{BurntOrange}{surprise,} when

 the \textcolor{BurntOrange}{White} Rabbit read out, at the \textcolor{BurntOrange}{top} of his \textcolor{BurntOrange}{shrill} little voice, the

 name ‘Alice!’









 CHAPTER XII. Alice’s Evidence





 ‘Here!’ \textcolor{red}{cried} Alice, quite \textcolor{red}{forgetting} in the flurry of the moment how

 large she had grown in the last few minutes, and she jumped up in such

 a \textcolor{blue}{hurry} that she tipped over the jury-box with the edge of her skirt,

 \textcolor{red}{upsetting} all the jurymen on to the heads of the crowd below, and there

 they lay sprawling about, reminding her very much of a globe of goldfish

 she had \textcolor{blue}{accidentally} \textcolor{red}{upset} the week before.



 ‘Oh, I \textcolor{red}{BEG} your \textcolor{green}{pardon!’} she \textcolor{blue}{exclaimed} in a tone of great \textcolor{BurntOrange}{dismay,} and

 began \textcolor{green}{picking} them up again as quickly as she could, for the \textcolor{BurntOrange}{accident} of

 the goldfish kept running in her head, and she had a \textcolor{red}{vague} sort of idea

 that they must be collected at once and put back into the jury-box, or

 they would \textcolor{red}{die.}



 ‘The trial cannot proceed,’ said the \textcolor{green}{King} in a very \textcolor{red}{grave} voice, ‘until

 all the jurymen are back in their \textcolor{green}{proper} places--ALL,’ he repeated with

 great emphasis, looking hard at Alice as he said do.



 Alice looked at the jury-box, and saw that, in her \textcolor{blue}{haste,} she had put

 the Lizard in head downwards, and the poor little thing was waving its

 tail about in a \textcolor{red}{melancholy} way, being quite \textcolor{red}{unable} to move. She soon got

 it out again, and put it right; ‘not that it signifies much,’ she said

 to herself; ‘I should think it would be QUITE as much use in the trial

 one way up as the other.’



 As soon as the \textcolor{green}{jury} had a little recovered from the \textcolor{BurntOrange}{shock} of being

 \textcolor{red}{upset,} and their \textcolor{green}{slates} and pencils had been \textcolor{green}{found} and handed back to

 them, they set to work very diligently to write out a history of the

 \textcolor{BurntOrange}{accident,} all except the Lizard, who seemed too much overcome to do

 anything but sit with its \textcolor{blue}{mouth} open, gazing up into the roof of the

 \textcolor{BurntOrange}{court.}



 ‘What do you know about this business?’ the \textcolor{green}{King} said to Alice.



 ‘Nothing,’ said Alice.



 ‘Nothing WHATEVER?’ persisted the \textcolor{green}{King.}



 ‘Nothing whatever,’ said Alice.



 ‘That’s very \textcolor{green}{important,’} the \textcolor{green}{King} said, turning to the \textcolor{green}{jury.} They were

 just beginning to write this down on their \textcolor{green}{slates,} when the \textcolor{BurntOrange}{White} Rabbit

 \textcolor{BurntOrange}{interrupted:} \textcolor{red}{‘UNimportant,} your \textcolor{green}{Majesty} means, of course,’ he said in a

 very \textcolor{green}{respectful} tone, but \textcolor{red}{frowning} and making faces at him as he \textcolor{red}{spoke.}



 \textcolor{red}{‘UNimportant,} of course, I meant,’ the \textcolor{green}{King} hastily said, and went on

 to himself in an undertone,



 ‘important--unimportant--unimportant--important--’ as if he were trying

 which \textcolor{green}{word} sounded best.



 Some of the \textcolor{green}{jury} wrote it down \textcolor{green}{‘important,’} and some \textcolor{red}{‘unimportant.’}

 Alice could see this, as she was near enough to look over their \textcolor{green}{slates;}

 ‘but it doesn’t matter a bit,’ she \textcolor{blue}{thought} to herself.



 At this moment the \textcolor{green}{King,} who had been for some \textcolor{blue}{time} busily writing in

 his note-book, cackled out ‘Silence!’ and read out from his book, \textcolor{BurntOrange}{‘Rule}

 Forty-two. ALL PERSONS MORE THAN A MILE HIGH TO \textcolor{BurntOrange}{LEAVE} THE \textcolor{BurntOrange}{COURT.’}



 Everybody looked at Alice.



 ‘I’M not a mile high,’ said Alice.



 ‘You are,’ said the \textcolor{green}{King.}



 ‘Nearly two miles high,’ added the Queen.



 ‘Well, I shan’t go, at any rate,’ said Alice: ‘besides, that’s not a

 regular \textcolor{BurntOrange}{rule:} you invented it just now.’



 ‘It’s the oldest \textcolor{BurntOrange}{rule} in the book,’ said the \textcolor{green}{King.}



 ‘Then it ought to be Number One,’ said Alice.



 The \textcolor{green}{King} turned pale, and shut his note-book hastily. ‘Consider your

 \textcolor{red}{verdict,’} he said to the \textcolor{green}{jury,} in a low, trembling voice.



 ‘There’s more evidence to come yet, please your \textcolor{green}{Majesty,’} said the \textcolor{BurntOrange}{White}

 Rabbit, jumping up in a great \textcolor{blue}{hurry;} ‘this paper has just been picked

 up.’



 ‘What’s in it?’ said the Queen.



 ‘I haven’t opened it yet,’ said the \textcolor{BurntOrange}{White} Rabbit, ‘but it seems to be a

 \textcolor{blue}{letter,} written by the \textcolor{red}{prisoner} to--to somebody.’



 ‘It must have been that,’ said the \textcolor{green}{King,} ‘unless it was written to

 nobody, which isn’t \textcolor{green}{usual,} you know.’



 ‘Who is it directed to?’ said one of the jurymen.



 ‘It isn’t directed at all,’ said the \textcolor{BurntOrange}{White} Rabbit; ‘in \textcolor{green}{fact,} there’s

 nothing written on the OUTSIDE.’ He unfolded the paper as he \textcolor{red}{spoke,} and

 added ‘It isn’t a \textcolor{blue}{letter,} after all: it’s a set of verses.’



 ‘Are they in the \textcolor{red}{prisoner’s} handwriting?’ asked another of the jurymen.



 ‘No, they’re not,’ said the \textcolor{BurntOrange}{White} Rabbit, ‘and that’s the queerest thing

 about it.’ (The \textcolor{green}{jury} all looked puzzled.)



 ‘He must have imitated somebody else’s hand,’ said the \textcolor{green}{King.} (The \textcolor{green}{jury}

 all \textcolor{BurntOrange}{brightened} up again.)



 ‘Please your \textcolor{green}{Majesty,’} said the Knave, ‘I didn’t write it, and they

 can’t \textcolor{green}{prove} I did: there’s no name signed at the end.’



 ‘If you didn’t sign it,’ said the \textcolor{green}{King,} ‘that only makes the matter

 \textcolor{red}{worse.} You MUST have meant some \textcolor{red}{mischief,} or else you’d have signed your

 name like an \textcolor{BurntOrange}{honest} man.’



 There was a \textcolor{green}{general} \textcolor{BurntOrange}{clapping} of hands at this: it was the first really

 \textcolor{green}{clever} thing the \textcolor{green}{King} had said that day.



 ‘That PROVES his \textcolor{red}{guilt,’} said the Queen.



 ‘It proves nothing of the sort!’ said Alice. ‘Why, you don’t even know

 what they’re about!’



 ‘Read them,’ said the \textcolor{green}{King.}



 The \textcolor{BurntOrange}{White} Rabbit put on his \textcolor{BurntOrange}{spectacles.} ‘Where shall I begin, please

 your \textcolor{green}{Majesty?’} he asked.



 ‘Begin at the beginning,’ the \textcolor{green}{King} said gravely, ‘and go on till you

 come to the end: then stop.’



 These were the verses the \textcolor{BurntOrange}{White} Rabbit read:--



 ‘They told me you had been to her,

 And mentioned me to him:

 She gave me a \textcolor{BurntOrange}{good} character,

 But said I could not \textcolor{BurntOrange}{swim.}



 He sent them \textcolor{green}{word} I had not gone

 (We know it to be \textcolor{green}{true):}

 If she should push the matter on,

 What would become of you?



 I gave her one, they gave him two,

 You gave us three or more;

 They all returned from him to you,

 Though they were mine before.



 If I or she should \textcolor{blue}{chance} to be

 Involved in this affair,

 He \textcolor{green}{trusts} to you to set them free,

 Exactly as we were.



 My \textcolor{green}{notion} was that you had been

 (Before she had this fit)

 An \textcolor{red}{obstacle} that came between

 Him, and ourselves, and it.



 Don’t let him know she liked them best,

 For this must ever be

 A \textcolor{green}{secret,} kept from all the \textcolor{green}{rest,}

 Between yourself and me.’



 ‘That’s the most \textcolor{green}{important} piece of evidence we’ve heard yet,’ said the

 \textcolor{green}{King,} rubbing his hands; ‘so now let the \textcolor{green}{jury--’}



 ‘If any one of them can \textcolor{green}{explain} it,’ said Alice, (she had grown so large

 in the last few minutes that she wasn’t a bit \textcolor{red}{afraid} of \textcolor{BurntOrange}{interrupting}

 him,) \textcolor{red}{‘I’ll} give him sixpence. I don’t believe there’s an \textcolor{green}{atom} of

 meaning in it.’



 The \textcolor{green}{jury} all wrote down on their \textcolor{green}{slates,} ‘SHE doesn’t believe there’s an

 \textcolor{green}{atom} of meaning in it,’ but none of them \textcolor{blue}{attempted} to \textcolor{green}{explain} the paper.



 ‘If there’s no meaning in it,’ said the \textcolor{green}{King,} ‘that \textcolor{green}{saves} a world of

 trouble, you know, as we needn’t try to find any. And yet I don’t know,’

 he went on, spreading out the verses on his knee, and looking at them

 with one eye; ‘I seem to see some meaning in them, after all. “--SAID

 I COULD NOT \textcolor{BurntOrange}{SWIM--”} you can’t \textcolor{BurntOrange}{swim,} can you?’ he added, turning to the

 Knave.



 The Knave shook his head \textcolor{red}{sadly.} ‘Do I look like it?’ he said. (Which he

 certainly did NOT, being made entirely of cardboard.)



 ‘All right, so far,’ said the \textcolor{green}{King,} and he went on \textcolor{red}{muttering} over

 the verses to himself: ‘“WE KNOW IT TO BE \textcolor{green}{TRUE--”} that’s the \textcolor{green}{jury,} of

 course--“I GAVE HER ONE, THEY GAVE HIM TWO--” why, that must be what he

 did with the tarts, you know--’



 ‘But, it goes on “THEY ALL RETURNED FROM HIM TO YOU,”’ said Alice.



 ‘Why, there they are!’ said the \textcolor{green}{King} triumphantly, pointing to the tarts

 on the table. ‘Nothing can be clearer than THAT. Then again--“BEFORE SHE

 HAD THIS FIT--” you never had fits, my \textcolor{green}{dear,} I think?’ he said to the

 Queen.



 ‘Never!’ said the Queen \textcolor{red}{furiously,} throwing an inkstand at the Lizard

 as she \textcolor{red}{spoke.} (The \textcolor{red}{unfortunate} little Bill had left off writing on his

 \textcolor{green}{slate} with one finger, as he \textcolor{green}{found} it made no mark; but he now hastily

 began again, using the ink, that was trickling down his face, as \textcolor{blue}{long} as

 it lasted.)



 ‘Then the \textcolor{green}{words} don’t FIT you,’ said the \textcolor{green}{King,} looking round the \textcolor{BurntOrange}{court}

 with a \textcolor{BurntOrange}{smile.} There was a dead silence.



 ‘It’s a pun!’ the \textcolor{green}{King} added in an \textcolor{red}{offended} tone, and everybody \textcolor{BurntOrange}{laughed,}

 ‘Let the \textcolor{green}{jury} consider their \textcolor{red}{verdict,’} the \textcolor{green}{King} said, for about the

 twentieth \textcolor{blue}{time} that day.



 ‘No, no!’ said the Queen. \textcolor{BurntOrange}{‘Sentence} first--verdict afterwards.’



 ‘Stuff and \textcolor{red}{nonsense!’} said Alice loudly. ‘The idea of having the

 \textcolor{BurntOrange}{sentence} first!’



 ‘Hold your tongue!’ said the Queen, turning purple.



 ‘I \textcolor{blue}{won’t!’} said Alice.



 ‘Off with her head!’ the Queen \textcolor{BurntOrange}{shouted} at the \textcolor{BurntOrange}{top} of her voice. Nobody

 moved.



 ‘Who cares for you?’ said Alice, (she had grown to her \textcolor{green}{full} size by this

 \textcolor{blue}{time.)} ‘You’re nothing but a pack of cards!’



 At this the whole pack rose up into the air, and came flying down upon

 her: she gave a little \textcolor{BurntOrange}{scream,} half of \textcolor{BurntOrange}{fright} and half of \textcolor{red}{anger,} and

 tried to beat them off, and \textcolor{green}{found} herself \textcolor{red}{lying} on the \textcolor{green}{bank,} with her

 head in the lap of her sister, who was gently brushing away some dead

 leaves that had fluttered down from the \textcolor{BurntOrange}{trees} upon her face.



 ‘Wake up, Alice \textcolor{green}{dear!’} said her sister; ‘Why, what a \textcolor{blue}{long} sleep you’ve

 had!’



 ‘Oh, I’ve had such a curious dream!’ said Alice, and she told her

 sister, as well as she could remember them, all these strange \textcolor{BurntOrange}{Adventures}

 of hers that you have just been \textcolor{green}{reading} about; and when she had

 finished, her sister \textcolor{BurntOrange}{kissed} her, and said, ‘It WAS a curious dream,

 \textcolor{green}{dear,} certainly: but now run in to your tea; it’s getting \textcolor{red}{late.’} So

 Alice got up and ran off, thinking while she ran, as well she might,

 what a \textcolor{BurntOrange}{wonderful} dream it had been.



 But her sister sat still just as she left her, leaning her head on her

 hand, \textcolor{BurntOrange}{watching} the setting \textcolor{BurntOrange}{sun,} and thinking of little Alice and all her

 \textcolor{BurntOrange}{wonderful} \textcolor{BurntOrange}{Adventures,} till she too began dreaming after a fashion, and

 this was her dream:--



 First, she dreamed of little Alice herself, and once again the tiny

 hands were clasped upon her knee, and the bright \textcolor{BurntOrange}{eager} eyes were looking

 up into hers--she could hear the very tones of her voice, and see that

 queer little toss of her head to keep back the wandering hair that

 WOULD always get into her eyes--and still as she listened, or seemed to

 listen, the whole place around her became \textcolor{BurntOrange}{alive} with the strange \textcolor{red}{creatures}

 of her little sister’s dream.



 The \textcolor{blue}{long} grass rustled at her feet as the \textcolor{BurntOrange}{White} Rabbit \textcolor{blue}{hurried} by--the

 \textcolor{BurntOrange}{frightened} Mouse \textcolor{blue}{splashed} his way through the neighbouring pool--she

 could hear the rattle of the teacups as the \textcolor{green}{March} Hare and his \textcolor{green}{friends}

 \textcolor{BurntOrange}{shared} their never-ending meal, and the \textcolor{BurntOrange}{shrill} voice of the Queen

 ordering off her \textcolor{red}{unfortunate} guests to execution--once more the pig-baby

 was \textcolor{BurntOrange}{sneezing} on the Duchess’s knee, while plates and dishes crashed

 around it--once more the \textcolor{BurntOrange}{shriek} of the Gryphon, the squeaking of the

 Lizard’s slate-pencil, and the \textcolor{red}{choking} of the \textcolor{red}{suppressed} guinea-pigs,

 \textcolor{green}{filled} the air, mixed up with the distant \textcolor{red}{sobs} of the \textcolor{red}{miserable} Mock

 Turtle.



 So she sat on, with closed eyes, and half believed herself in

 Wonderland, though she knew she had but to open them again, and all

 would \textcolor{red}{change} to \textcolor{red}{dull} reality--the grass would be only rustling in the

 wind, and the \textcolor{green}{pool} rippling to the waving of the reeds--the rattling

 teacups would \textcolor{red}{change} to tinkling sheep-bells, and the Queen’s \textcolor{BurntOrange}{shrill}

 \textcolor{red}{cries} to the voice of the \textcolor{green}{shepherd} boy--and the \textcolor{BurntOrange}{sneeze} of the \textcolor{green}{baby,} the

 \textcolor{BurntOrange}{shriek} of the Gryphon, and all the other queer \textcolor{red}{noises,} would \textcolor{red}{change} (she

 knew) to the \textcolor{red}{confused} clamour of the busy farm-yard--while the lowing

 of the cattle in the distance would take the place of the Mock Turtle’s

 heavy \textcolor{red}{sobs.}



 Lastly, she pictured to herself how this same little sister of hers

 would, in the after-time, be herself a grown woman; and how she would

 keep, through all her riper years, the simple and \textcolor{green}{loving} heart of her

 \textcolor{green}{childhood:} and how she would gather about her other little \textcolor{BurntOrange}{children,} and

 make THEIR eyes bright and \textcolor{BurntOrange}{eager} with many a strange \textcolor{green}{tale,} perhaps even

 with the dream of Wonderland of \textcolor{blue}{long} ago: and how she would feel with

 all their simple \textcolor{red}{sorrows,} and find a pleasure in all their simple \textcolor{green}{joys,}

 remembering her own child-life, and the \textcolor{BurntOrange}{happy} summer days.



 THE END











 End of Project Gutenberg’s Alice’s \textcolor{BurntOrange}{Adventures} in Wonderland, by Lewis Carroll



 *** END OF THIS PROJECT GUTENBERG EBOOK ALICE’S \textcolor{BurntOrange}{ADVENTURES} IN WONDERLAND ***



 ***** This file should be named 11-0.txt or 11-0.zip *****

 This and all \textcolor{green}{associated} files of various formats will be \textcolor{green}{found} in:

 http://www.gutenberg.org/1/11/







 Updated \textcolor{blue}{editions} will replace the previous one--the old \textcolor{blue}{editions}

 will be renamed.



 \textcolor{green}{Creating} the works from \textcolor{BurntOrange}{public} domain print \textcolor{blue}{editions} means that no

 one owns a \textcolor{green}{United} States copyright in these works, so the \textcolor{green}{Foundation}

 (and you!) can \textcolor{red}{copy} and distribute it in the \textcolor{green}{United} States without

 \textcolor{green}{permission} and without \textcolor{BurntOrange}{paying} copyright \textcolor{green}{royalties.} \textcolor{green}{Special} \textcolor{BurntOrange}{rules,}

 set forth in the \textcolor{green}{General} Terms of Use part of this license, apply to

 copying and distributing Project Gutenberg-tm electronic works to

 \textcolor{green}{protect} the PROJECT GUTENBERG-tm concept and trademark. Project

 Gutenberg is a registered trademark, and may not be used if you

 charge for the eBooks, unless you receive specific \textcolor{green}{permission.} If you

 do not charge anything for \textcolor{red}{copies} of this eBook, complying with the

 \textcolor{BurntOrange}{rules} is very easy. You may use this eBook for nearly any purpose

 such as creation of derivative works, reports, performances and

 research. They may be \textcolor{blue}{modified} and printed and given away--you may do

 practically ANYTHING with \textcolor{BurntOrange}{public} domain eBooks. Redistribution is

 \textcolor{red}{subject} to the trademark license, especially commercial

 redistribution.







 *** \textcolor{blue}{START:} \textcolor{green}{FULL} LICENSE ***



 THE \textcolor{green}{FULL} PROJECT GUTENBERG LICENSE

 PLEASE READ THIS BEFORE YOU DISTRIBUTE OR USE THIS WORK



 To \textcolor{green}{protect} the Project Gutenberg-tm mission of promoting the free

 distribution of electronic works, by using or distributing this work

 (or any other work \textcolor{green}{associated} in any way with the phrase “Project

 Gutenberg”), you \textcolor{green}{agree} to comply with all the terms of the \textcolor{green}{Full} Project

 Gutenberg-tm License (available with this file or online at

 http://gutenberg.org/license).





 Section 1. \textcolor{green}{General} Terms of Use and Redistributing Project Gutenberg-tm

 electronic works



 1.A. By \textcolor{green}{reading} or using any part of this Project Gutenberg-tm

 electronic work, you indicate that you have read, understand, \textcolor{green}{agree} to

 and accept all the terms of this license and \textcolor{green}{intellectual} property

 (trademark/copyright) \textcolor{green}{agreement.} If you do not \textcolor{green}{agree} to abide by all

 the terms of this \textcolor{green}{agreement,} you must cease using and return or destroy

 all \textcolor{red}{copies} of Project Gutenberg-tm electronic works in your \textcolor{red}{possession.}

 If you paid a \textcolor{red}{fee} for obtaining a \textcolor{red}{copy} of or access to a Project

 Gutenberg-tm electronic work and you do not \textcolor{green}{agree} to be \textcolor{red}{bound} by the

 terms of this \textcolor{green}{agreement,} you may obtain a refund from the person or

 entity to whom you paid the \textcolor{red}{fee} as set forth in paragraph 1.E.8.



 1.B. “Project Gutenberg” is a registered trademark. It may only be

 used on or \textcolor{green}{associated} in any way with an electronic work by people who

 \textcolor{green}{agree} to be \textcolor{red}{bound} by the terms of this \textcolor{green}{agreement.} There are a few

 things that you can do with most Project Gutenberg-tm electronic works

 even without complying with the \textcolor{green}{full} terms of this \textcolor{green}{agreement.} See

 paragraph 1.C below. There are a lot of things you can do with Project

 Gutenberg-tm electronic works if you follow the terms of this \textcolor{green}{agreement}

 and help \textcolor{green}{preserve} free future access to Project Gutenberg-tm electronic

 works. See paragraph 1.E below.



 1.C. The Project Gutenberg Literary Archive \textcolor{green}{Foundation} (“the \textcolor{green}{Foundation”}

 or PGLAF), owns a compilation copyright in the collection of Project

 Gutenberg-tm electronic works. Nearly all the individual works in the

 collection are in the \textcolor{BurntOrange}{public} domain in the \textcolor{green}{United} States. If an

 individual work is in the \textcolor{BurntOrange}{public} domain in the \textcolor{green}{United} States and you are

 located in the \textcolor{green}{United} States, we do not claim a right to \textcolor{red}{prevent} you from

 copying, distributing, performing, displaying or \textcolor{green}{creating} derivative

 works \textcolor{green}{based} on the work as \textcolor{blue}{long} as all references to Project Gutenberg

 are \textcolor{red}{removed.} Of course, we \textcolor{BurntOrange}{hope} that you will support the Project

 Gutenberg-tm mission of promoting free access to electronic works by

 \textcolor{green}{freely} \textcolor{BurntOrange}{sharing} Project Gutenberg-tm works in \textcolor{green}{compliance} with the terms of

 this \textcolor{green}{agreement} for keeping the Project Gutenberg-tm name \textcolor{green}{associated} with

 the work. You can easily comply with the terms of this \textcolor{green}{agreement} by

 keeping this work in the same format with its attached \textcolor{green}{full} Project

 Gutenberg-tm License when you \textcolor{BurntOrange}{share} it without charge with others.



 1.D. The copyright \textcolor{green}{laws} of the place where you are located also \textcolor{green}{govern}

 what you can do with this work. Copyright \textcolor{green}{laws} in most countries are in

 a \textcolor{green}{constant} state of \textcolor{red}{change.} If you are outside the \textcolor{green}{United} States, check

 the \textcolor{green}{laws} of your country in addition to the terms of this \textcolor{green}{agreement}

 before downloading, copying, displaying, performing, distributing or

 \textcolor{green}{creating} derivative works \textcolor{green}{based} on this work or any other Project

 Gutenberg-tm work. The \textcolor{green}{Foundation} makes no representations concerning

 the copyright \textcolor{green}{status} of any work in any country outside the \textcolor{green}{United}

 States.



 1.E. Unless you have \textcolor{red}{removed} all references to Project Gutenberg:



 1.E.1. The following \textcolor{BurntOrange}{sentence,} with active links to, or other immediate

 access to, the \textcolor{green}{full} Project Gutenberg-tm License must appear \textcolor{green}{prominently}

 whenever any \textcolor{red}{copy} of a Project Gutenberg-tm work (any work on which the

 phrase “Project Gutenberg” appears, or with which the phrase “Project

 Gutenberg” is \textcolor{green}{associated)} is accessed, displayed, performed, viewed,

 \textcolor{red}{copied} or distributed:



 This eBook is for the use of anyone anywhere at no cost and with

 almost no \textcolor{red}{restrictions} whatsoever. You may \textcolor{red}{copy} it, give it away or

 re-use it under the terms of the Project Gutenberg License \textcolor{green}{included}

 with this eBook or online at www.gutenberg.org



 1.E.2. If an individual Project Gutenberg-tm electronic work is derived

 from the \textcolor{BurntOrange}{public} domain (does not contain a notice indicating that it is

 posted with \textcolor{green}{permission} of the copyright holder), the work can be \textcolor{red}{copied}

 and distributed to anyone in the \textcolor{green}{United} States without \textcolor{BurntOrange}{paying} any \textcolor{red}{fees}

 or charges. If you are redistributing or \textcolor{green}{providing} access to a work

 with the phrase “Project Gutenberg” \textcolor{green}{associated} with or appearing on the

 work, you must comply either with the requirements of paragraphs 1.E.1

 through 1.E.7 or obtain \textcolor{green}{permission} for the use of the work and the

 Project Gutenberg-tm trademark as set forth in paragraphs 1.E.8 or

 1.E.9.



 1.E.3. If an individual Project Gutenberg-tm electronic work is posted

 with the \textcolor{green}{permission} of the copyright holder, your use and distribution

 must comply with both paragraphs 1.E.1 through 1.E.7 and any additional

 terms imposed by the copyright holder. Additional terms will be linked

 to the Project Gutenberg-tm License for all works posted with the

 \textcolor{green}{permission} of the copyright holder \textcolor{green}{found} at the beginning of this work.



 1.E.4. Do not unlink or detach or \textcolor{red}{remove} the \textcolor{green}{full} Project Gutenberg-tm

 License terms from this work, or any files containing a part of this

 work or any other work \textcolor{green}{associated} with Project Gutenberg-tm.



 1.E.5. Do not \textcolor{red}{copy,} display, perform, distribute or redistribute this

 electronic work, or any part of this electronic work, without

 \textcolor{green}{prominently} displaying the \textcolor{BurntOrange}{sentence} set forth in paragraph 1.E.1 with

 active links or immediate access to the \textcolor{green}{full} terms of the Project

 Gutenberg-tm License.



 1.E.6. You may \textcolor{green}{convert} to and distribute this work in any binary,

 \textcolor{red}{compressed,} \textcolor{green}{marked} up, nonproprietary or proprietary form, \textcolor{green}{including} any

 \textcolor{green}{word} processing or hypertext form. However, if you \textcolor{green}{provide} access to or

 distribute \textcolor{red}{copies} of a Project Gutenberg-tm work in a format other than

 “Plain Vanilla ASCII” or other format used in the \textcolor{green}{official} version

 posted on the \textcolor{green}{official} Project Gutenberg-tm web site (www.gutenberg.org),

 you must, at no additional cost, \textcolor{red}{fee} or expense to the user, \textcolor{green}{provide} a

 \textcolor{red}{copy,} a means of exporting a \textcolor{red}{copy,} or a means of obtaining a \textcolor{red}{copy} upon

 request, of the work in its original “Plain Vanilla ASCII” or other

 form. Any alternate format must \textcolor{green}{include} the \textcolor{green}{full} Project Gutenberg-tm

 License as specified in paragraph 1.E.1.



 1.E.7. Do not charge a \textcolor{red}{fee} for access to, viewing, displaying,

 performing, copying or distributing any Project Gutenberg-tm works

 unless you comply with paragraph 1.E.8 or 1.E.9.



 1.E.8. You may charge a reasonable \textcolor{red}{fee} for \textcolor{red}{copies} of or \textcolor{green}{providing}

 access to or distributing Project Gutenberg-tm electronic works \textcolor{green}{provided}

 that



 - You \textcolor{BurntOrange}{pay} a \textcolor{green}{royalty} \textcolor{red}{fee} of 20% of the \textcolor{red}{gross} profits you derive from

 the use of Project Gutenberg-tm works calculated using the method

 you already use to calculate your applicable \textcolor{red}{taxes.} The \textcolor{red}{fee} is

 owed to the owner of the Project Gutenberg-tm trademark, but he

 has \textcolor{green}{agreed} to donate \textcolor{green}{royalties} under this paragraph to the

 Project Gutenberg Literary Archive \textcolor{green}{Foundation.} \textcolor{green}{Royalty} \textcolor{red}{payments}

 must be paid within 60 days following each date on which you

 \textcolor{BurntOrange}{prepare} (or are legally required to \textcolor{BurntOrange}{prepare)} your periodic \textcolor{red}{tax}

 returns. \textcolor{green}{Royalty} \textcolor{red}{payments} should be clearly \textcolor{green}{marked} as such and

 sent to the Project Gutenberg Literary Archive \textcolor{green}{Foundation} at the

 address specified in Section 4, \textcolor{green}{“Information} about \textcolor{green}{donations} to

 the Project Gutenberg Literary Archive \textcolor{green}{Foundation.”}



 - You \textcolor{green}{provide} a \textcolor{green}{full} refund of any \textcolor{BurntOrange}{money} paid by a user who notifies

 you in writing (or by e-mail) within 30 days of receipt that s/he

 does not \textcolor{green}{agree} to the terms of the \textcolor{green}{full} Project Gutenberg-tm

 License. You must require such a user to return or

 destroy all \textcolor{red}{copies} of the works \textcolor{BurntOrange}{possessed} in a physical medium

 and \textcolor{red}{discontinue} all use of and all access to other \textcolor{red}{copies} of

 Project Gutenberg-tm works.



 - You \textcolor{green}{provide,} in accordance with paragraph 1.F.3, a \textcolor{green}{full} refund of any

 \textcolor{BurntOrange}{money} paid for a work or a replacement \textcolor{red}{copy,} if a \textcolor{red}{defect} in the

 electronic work is discovered and reported to you within 90 days

 of receipt of the work.



 - You comply with all other terms of this \textcolor{green}{agreement} for free

 distribution of Project Gutenberg-tm works.



 1.E.9. If you wish to charge a \textcolor{red}{fee} or distribute a Project Gutenberg-tm

 electronic work or group of works on different terms than are set

 forth in this \textcolor{green}{agreement,} you must obtain \textcolor{green}{permission} in writing from

 both the Project Gutenberg Literary Archive \textcolor{green}{Foundation} and Michael

 Hart, the owner of the Project Gutenberg-tm trademark. \textcolor{green}{Contact} the

 \textcolor{green}{Foundation} as set forth in Section 3 below.



 1.F.



 1.F.1. Project Gutenberg \textcolor{BurntOrange}{volunteers} and employees expend \textcolor{green}{considerable}

 \textcolor{green}{effort} to identify, do copyright research on, transcribe and proofread

 \textcolor{BurntOrange}{public} domain works in \textcolor{green}{creating} the Project Gutenberg-tm

 collection. Despite these \textcolor{green}{efforts,} Project Gutenberg-tm electronic

 works, and the medium on which they may be \textcolor{BurntOrange}{stored,} may contain

 \textcolor{red}{“Defects,”} such as, but not \textcolor{red}{limited} to, incomplete, \textcolor{red}{inaccurate} or

 \textcolor{red}{corrupt} data, transcription \textcolor{red}{errors,} a copyright or other \textcolor{green}{intellectual}

 property \textcolor{red}{infringement,} a \textcolor{red}{defective} or \textcolor{red}{damaged} disk or other medium, a

 computer \textcolor{red}{virus,} or computer codes that \textcolor{red}{damage} or cannot be read by

 your equipment.



 1.F.2. \textcolor{red}{LIMITED} \textcolor{green}{WARRANTY,} DISCLAIMER OF \textcolor{red}{DAMAGES} - Except for the “Right

 of Replacement or Refund” described in paragraph 1.F.3, the Project

 Gutenberg Literary Archive \textcolor{green}{Foundation,} the owner of the Project

 Gutenberg-tm trademark, and any other party distributing a Project

 Gutenberg-tm electronic work under this \textcolor{green}{agreement,} \textcolor{BurntOrange}{disclaim} all

 liability to you for \textcolor{red}{damages,} costs and expenses, \textcolor{green}{including} \textcolor{green}{legal}

 \textcolor{red}{fees.} YOU \textcolor{green}{AGREE} THAT YOU HAVE NO \textcolor{BurntOrange}{REMEDIES} FOR \textcolor{red}{NEGLIGENCE,} STRICT

 LIABILITY, \textcolor{red}{BREACH} OF \textcolor{green}{WARRANTY} OR \textcolor{red}{BREACH} OF CONTRACT EXCEPT THOSE

 \textcolor{green}{PROVIDED} IN PARAGRAPH F3. YOU \textcolor{green}{AGREE} THAT THE \textcolor{green}{FOUNDATION,} THE

 TRADEMARK OWNER, AND ANY DISTRIBUTOR UNDER THIS \textcolor{green}{AGREEMENT} WILL NOT BE

 LIABLE TO YOU FOR \textcolor{green}{ACTUAL,} DIRECT, INDIRECT, CONSEQUENTIAL, \textcolor{red}{PUNITIVE} OR

 INCIDENTAL \textcolor{red}{DAMAGES} EVEN IF YOU GIVE NOTICE OF THE \textcolor{blue}{POSSIBILITY} OF SUCH

 \textcolor{red}{DAMAGE.}



 1.F.3. \textcolor{red}{LIMITED} RIGHT OF REPLACEMENT OR REFUND - If you discover a

 \textcolor{red}{defect} in this electronic work within 90 days of receiving it, you can

 receive a refund of the \textcolor{BurntOrange}{money} (if any) you paid for it by sending a

 written explanation to the person you received the work from. If you

 received the work on a physical medium, you must return the medium with

 your written explanation. The person or entity that \textcolor{green}{provided} you with

 the \textcolor{red}{defective} work may \textcolor{green}{elect} to \textcolor{green}{provide} a replacement \textcolor{red}{copy} in lieu of a

 refund. If you received the work electronically, the person or entity

 \textcolor{green}{providing} it to you may choose to give you a second \textcolor{BurntOrange}{opportunity} to

 receive the work electronically in lieu of a refund. If the second \textcolor{red}{copy}

 is also \textcolor{red}{defective,} you may \textcolor{red}{demand} a refund in writing without further

 \textcolor{BurntOrange}{opportunities} to fix the \textcolor{red}{problem.}



 1.F.4. Except for the \textcolor{red}{limited} right of replacement or refund set forth

 in paragraph 1.F.3, this work is \textcolor{green}{provided} to you ‘AS-IS’ WITH NO OTHER

 \textcolor{green}{WARRANTIES} OF ANY \textcolor{green}{KIND,} EXPRESS OR IMPLIED, \textcolor{green}{INCLUDING} BUT NOT \textcolor{red}{LIMITED} TO

 \textcolor{green}{WARRANTIES} OF MERCHANTIBILITY OR FITNESS FOR ANY PURPOSE.



 1.F.5. Some states do not allow disclaimers of certain implied

 \textcolor{green}{warranties} or the \textcolor{red}{exclusion} or limitation of certain types of \textcolor{red}{damages.}

 If any disclaimer or limitation set forth in this \textcolor{green}{agreement} violates the

 \textcolor{green}{law} of the state applicable to this \textcolor{green}{agreement,} the \textcolor{green}{agreement} shall be

 interpreted to make the \textcolor{green}{maximum} disclaimer or limitation permitted by

 the applicable state \textcolor{green}{law.} The \textcolor{red}{invalidity} or unenforceability of any

 provision of this \textcolor{green}{agreement} shall not void the remaining provisions.



 1.F.6. \textcolor{green}{INDEMNITY} - You \textcolor{green}{agree} to \textcolor{red}{indemnify} and hold the \textcolor{green}{Foundation,} the

 trademark owner, any agent or employee of the \textcolor{green}{Foundation,} anyone

 \textcolor{green}{providing} \textcolor{red}{copies} of Project Gutenberg-tm electronic works in accordance

 with this \textcolor{green}{agreement,} and any \textcolor{BurntOrange}{volunteers} \textcolor{green}{associated} with the \textcolor{BurntOrange}{production,}

 \textcolor{green}{promotion} and distribution of Project Gutenberg-tm electronic works,

 harmless from all liability, costs and expenses, \textcolor{green}{including} \textcolor{green}{legal} \textcolor{red}{fees,}

 that arise directly or indirectly from any of the following which you do

 or cause to occur: (a) distribution of this or any Project Gutenberg-tm

 work, (b) alteration, modification, or additions or \textcolor{red}{deletions} to any

 Project Gutenberg-tm work, and (c) any \textcolor{red}{Defect} you cause.





 Section 2. \textcolor{green}{Information} about the Mission of Project Gutenberg-tm



 Project Gutenberg-tm is \textcolor{BurntOrange}{synonymous} with the free distribution of

 electronic works in formats readable by the widest variety of computers

 \textcolor{green}{including} obsolete, old, middle-aged and new computers. It exists

 because of the \textcolor{green}{efforts} of hundreds of \textcolor{BurntOrange}{volunteers} and \textcolor{green}{donations} from

 people in all walks of life.



 \textcolor{BurntOrange}{Volunteers} and financial support to \textcolor{green}{provide} \textcolor{BurntOrange}{volunteers} with the

 \textcolor{green}{assistance} they need, is critical to reaching Project Gutenberg-tm’s

 goals and ensuring that the Project Gutenberg-tm collection will

 remain \textcolor{green}{freely} available for generations to come. In 2001, the Project

 Gutenberg Literary Archive \textcolor{green}{Foundation} was \textcolor{green}{created} to \textcolor{green}{provide} a secure

 and permanent future for Project Gutenberg-tm and future generations.

 To \textcolor{green}{learn} more about the Project Gutenberg Literary Archive \textcolor{green}{Foundation}

 and how your \textcolor{green}{efforts} and \textcolor{green}{donations} can help, see Sections 3 and 4

 and the \textcolor{green}{Foundation} web page at http://www.pglaf.org.





 Section 3. \textcolor{green}{Information} about the Project Gutenberg Literary Archive

 \textcolor{green}{Foundation}



 The Project Gutenberg Literary Archive \textcolor{green}{Foundation} is a non profit

 501(c)(3) \textcolor{green}{educational} \textcolor{green}{corporation} \textcolor{green}{organized} under the \textcolor{green}{laws} of the

 state of Mississippi and \textcolor{BurntOrange}{granted} \textcolor{red}{tax} exempt \textcolor{green}{status} by the Internal

 Revenue Service. The \textcolor{green}{Foundation’s} EIN or federal \textcolor{red}{tax} identification

 number is 64-6221541. Its 501(c)(3) \textcolor{blue}{letter} is posted at

 http://pglaf.org/fundraising. Contributions to the Project Gutenberg

 Literary Archive \textcolor{green}{Foundation} are \textcolor{red}{tax} deductible to the \textcolor{green}{full} extent

 permitted by U.S. federal \textcolor{green}{laws} and your state’s \textcolor{green}{laws.}



 The \textcolor{green}{Foundation’s} \textcolor{green}{principal} office is located at 4557 Melan Dr. S.

 Fairbanks, AK, 99712., but its \textcolor{BurntOrange}{volunteers} and employees are scattered

 throughout numerous locations. Its business office is located at

 809 North 1500 West, Salt Lake City, UT 84116, (801) 596-1887, email

 business@pglaf.org. Email \textcolor{green}{contact} links and up to date \textcolor{green}{contact}

 \textcolor{green}{information} can be \textcolor{green}{found} at the \textcolor{green}{Foundation’s} web site and \textcolor{green}{official}

 page at http://pglaf.org



 For additional \textcolor{green}{contact} \textcolor{green}{information:}

 Dr. Gregory B. Newby

 Chief Executive and \textcolor{green}{Director}

 gbnewby@pglaf.org





 Section 4. \textcolor{green}{Information} about \textcolor{green}{Donations} to the Project Gutenberg

 Literary Archive \textcolor{green}{Foundation}



 Project Gutenberg-tm depends upon and cannot \textcolor{green}{survive} without wide

 spread \textcolor{BurntOrange}{public} support and \textcolor{green}{donations} to carry out its mission of

 \textcolor{green}{increasing} the number of \textcolor{BurntOrange}{public} domain and licensed works that can be

 \textcolor{green}{freely} distributed in \textcolor{green}{machine} readable form \textcolor{green}{accessible} by the widest

 \textcolor{green}{array} of equipment \textcolor{green}{including} outdated equipment. Many \textcolor{red}{small} \textcolor{green}{donations}

 ($1 to $5,000) are particularly \textcolor{green}{important} to maintaining \textcolor{red}{tax} exempt

 \textcolor{green}{status} with the IRS.



 The \textcolor{green}{Foundation} is committed to complying with the \textcolor{green}{laws} \textcolor{green}{regulating}

 \textcolor{green}{charities} and \textcolor{BurntOrange}{charitable} \textcolor{green}{donations} in all 50 states of the \textcolor{green}{United}

 States. \textcolor{green}{Compliance} requirements are not uniform and it takes a

 \textcolor{green}{considerable} \textcolor{green}{effort,} much paperwork and many \textcolor{red}{fees} to meet and keep up

 with these requirements. We do not solicit \textcolor{green}{donations} in locations

 where we have not received written \textcolor{green}{confirmation} of \textcolor{green}{compliance.} To

 SEND \textcolor{green}{DONATIONS} or determine the \textcolor{green}{status} of \textcolor{green}{compliance} for any

 particular state \textcolor{green}{visit} http://pglaf.org



 While we cannot and do not solicit contributions from states where we

 have not met the solicitation requirements, we know of no \textcolor{red}{prohibition}

 against accepting unsolicited \textcolor{green}{donations} from donors in such states who

 approach us with \textcolor{green}{offers} to donate.



 International \textcolor{green}{donations} are gratefully accepted, but we cannot make

 any \textcolor{green}{statements} concerning \textcolor{red}{tax} treatment of \textcolor{green}{donations} received from

 outside the \textcolor{green}{United} States. U.S. \textcolor{green}{laws} alone \textcolor{red}{swamp} our \textcolor{red}{small} staff.



 Please check the Project Gutenberg Web pages for current \textcolor{green}{donation}

 methods and addresses. \textcolor{green}{Donations} are accepted in a number of other

 ways \textcolor{green}{including} checks, online \textcolor{red}{payments} and \textcolor{green}{credit} card \textcolor{green}{donations.}

 To donate, please \textcolor{green}{visit:} http://pglaf.org/donate





 Section 5. \textcolor{green}{General} \textcolor{green}{Information} About Project Gutenberg-tm electronic

 works.



 \textcolor{green}{Professor} Michael S. Hart is the originator of the Project Gutenberg-tm

 concept of a \textcolor{green}{library} of electronic works that could be \textcolor{green}{freely} \textcolor{BurntOrange}{shared}

 with anyone. For thirty years, he produced and distributed Project

 Gutenberg-tm eBooks with only a loose \textcolor{blue}{network} of \textcolor{BurntOrange}{volunteer} support.





 Project Gutenberg-tm eBooks are often \textcolor{green}{created} from several printed

 \textcolor{blue}{editions,} all of which are confirmed as \textcolor{BurntOrange}{Public} Domain in the U.S.

 unless a copyright notice is \textcolor{green}{included.} Thus, we do not necessarily

 keep eBooks in \textcolor{green}{compliance} with any particular paper \textcolor{blue}{edition.}





 Most people \textcolor{blue}{start} at our Web site which has the \textcolor{green}{main} PG search facility:



 http://www.gutenberg.org



 This Web site \textcolor{green}{includes} \textcolor{green}{information} about Project Gutenberg-tm,

 \textcolor{green}{including} how to make \textcolor{green}{donations} to the Project Gutenberg Literary

 Archive \textcolor{green}{Foundation,} how to help produce our new eBooks, and how to

 \textcolor{blue}{subscribe} to our email newsletter to hear about new eBooks.



